### 2013-01-08 jss/article.tex
beginning of article

\documentclass[article]{jss}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% declarations for jss.cls %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% almost as usual
\author{Joseph Kelly\\Harvard University \And 
        Hyung Suk Tak\\Harvard University \And
        Carl Morris\\ Harvard University}
\title{\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Joseph Kelly, Hyung Suk Tak, Carl Morris} %% comma-separated
\Plaintitle{Rgbp: Empirical Bayesian Hierarchical Modeling} %% without formatting
\Shorttitle{\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling} %% a short title (if necessary)

%% an abstract and keywords
\Abstract{
  Empirical Bayesian Hierarchical modeling for Gaussian, Binomial, and Poisson Data
}
\Keywords{keywords, comma-separated, not capitalized, \proglang{R}}
\Plainkeywords{keywords, comma-separated, not capitalized, r} %% without formatting
%% at least one keyword must be supplied

%% publication information
%% NOTE: Typically, this can be left commented and will be filled out by the technical editor
%% \Volume{50}
%% \Issue{9}
%% \Month{June}
%% \Year{2012}
%% \Submitdate{2012-06-04}
%% \Acceptdate{2012-06-04}

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Joseph Kelly\\
  Department of Statistics\\
  Harvard University\\
  1 Oxford Street, Cambridge, MA\\
  E-mail: \email{kelly2@fas.harvard.edu}\\
  URL: \url{http://www.people.fas.harvard.edu/~kelly2/}
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/512/507-7103
%% Fax: +43/512/507-2851

%% for those who use Sweave please include the following line (with % symbols):
%% need no \usepackage{Sweave.sty}

%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%% include your article here, just as usual
%% Note that you should use the \pkg{}, \proglang{} and \code{} commands.

\section[introduction]{Introduction}
%% Note: If there is markup in \(sub)section, then it has to be escape as above.

\section[estimation]{Estimation}
\subsection[adm]{Adjustment for Density Maximization}

\section[userguide]{User Guide}

\section[discussion]{Discussion}

\section[acknowledgments]{Acknowledgments}

\end{document}

### 2013-03-09 Rgbp/R/br.R
change

@@ -1,355 +1,0 @@
-BRInitialValue2ndLevelMeanKnown <- function(given) {
-  # This function makes the initial values needed to run BRIMM.
-  # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
-
-  if (given$prior.mean == 0) {
-    r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / var(given$sample.mean)
-  } else {
-    r.ini <- given$prior.mean * (1 - given$prior.mean) / var(given$sample.mean)
-  }
-
-  list(r.ini = r.ini, a.ini = -log(r.ini))
-}
-
-BRInitialValue2ndLevelMeanUnknown <- function(given) {
-  # This function makes the initial values needed to run BRIMM.
-  # "Un" means the descriptive second level mean (mean of Beta distribution) is unknown.
-
-  y <- given$sample.mean
-  z <- given$z
-  n <- given$n
-  x.ini <- given$x.ini
-
-  if (identical(x.ini, NA) & !given$intercept) {
-    print("In case we do not designate prior mean, at least one beta should be estimated 
-           (either intercept=T or at least one covariate is needed)")
-    stop()
-  } else if (identical(x.ini, NA) & given$intercept) {
-    x <- matrix(1, length(y), 1)
-    b.ini <- as.vector(log(mean(y) / (1 - mean(y))))
-  } else if (!identical(x.ini, NA) & given$intercept) {
-    x.ini <- as.matrix(x.ini)
-    xname <- paste("x.ini[, ", 1 : ncol(x.ini), "]", sep = "")
-    formula <- as.formula(paste("cbind(z, n - z) ~ ", paste(xname, collapse = "+")))
-    b.ini <- glm(formula, family = binomial)$coefficients
-    x <- as.matrix(cbind(rep(1, length(y)), x.ini))
-  } else if (!identical(x.ini, NA) & !given$intercept) {
-    x.ini <- as.matrix(x.ini)
[…]

### 2013-03-09 Rgbp/R/coverage.R

@@ -1,375 +1,0 @@
-
-coverage <- function(x, y, beta, X, mu0, nsim = 10, ...) {
-
-  # Rao-Blackwellized criterion
-  coverageRB <- matrix(NA, nr = length(x$se), nc = nsim)
-
-  # 1-0 criterion that is 1 if interval includes true parameter, 0 if not
-  coverage10 <- matrix(NA, nr = length(x$se), nc = nsim)
-
-  if (missing(y)) {
-    only.gbp.result <- T
-  } else {
-    only.gbp.result <- F
-  }
-
-  # if model=BRIMM	
-  if (x$model == "br") {
-    if (only.gbp.result) {
-      # 1. initial values
-      if (is.na(x$prior.mean) & identical(x$X, NA)) {
-        temp.x <- as.matrix(rep(1, length(x$se)))
-        betas <- as.vector(x$beta.new)
-        p0 <- exp(temp.x %*% betas) / (1 + exp(temp.x %*% betas))
-      } else if (is.na(x$prior.mean) & !identical(x$X, NA)) {
-        temp.x <- as.matrix(cbind(rep(1, length(x$se)), x$X))
-        betas <- as.vector(x$beta.new)
-        p0 <- exp(temp.x %*% betas) / (1 + exp(temp.x %*% betas))
-        X <- x$X
-      } else if (!is.na(x$prior.mean)) {
-        p0 <- x$prior.mean
-      }
-  
-      n <- x$se
-      r <- exp(-x$a.new)
-
-      # 2. generate p matrix
-      sim.p <- matrix(rbeta(length(n) * nsim, r * p0, r * (1 - p0)), nr = length(n))
-
-      # 3. generate z (data) matrix
-      sim.z <- matrix(rbinom(nrow(sim.p) * nsim, n, sim.p), nr = length(n))
-
-      # 4. simulation
-      for (i in 1 : nsim) {
-        tryCatch({
-          out <- if (is.na(x$prior.mean) & identical(x$X, NA)) {
-                   gbp(sim.z[, i], n, model = "br")
-                 } else if (is.na(x$prior.mean) & !identical(x$X, NA)) {
-                   gbp(sim.z[, i], n, X, model = "br")
-                 } else if (!is.na(x$prior.mean)) {
-                   gbp(sim.z[, i], n, mu0 = p0, model = "br")
-                 }
-
-          a1 <- r * p0 + sim.z[, i]
[…]

### 2013-03-09 Rgbp/R/gbp.R

@@ -1,323 +1,0 @@
-gbp <- function(x, ...) UseMethod("gbp")
-
-gbp.default <- function(x, y, covariates, mu0, model = "gr", intercept = T, Alpha = 0.95, ...) {
-  res <- switch(model, 
-                gr = gr(x, y, X = covariates, mu = mu0, Alpha = Alpha, intercept = intercept), 
-                br = br(x, y, X = covariates, prior.mean = mu0, intercept = intercept, Alpha = Alpha), 
-                pr = pr(x, y, X = covariates, prior.mean = mu0, intercept = intercept, Alpha = Alpha))
-  
-  class(res) <- "gbp"	
-  res
-}
-
-print.gbp <- function(x, ...) {
-  
-  if (is.na(x$prior.mean) & !identical(x$X, NA)) {
-
-	cova <- as.matrix(x$X)
-	colnames(cova) <- paste(1 : dim(cova)[2])
-    
-    if (x$model == "gr") {
-      temp <- data.frame(sample.mean = x$sample.mean, se = x$se, x = cova, prior.mean = x$prior.mean.hat,
-                         shrinkage = x$shrinkage, sd.shrinkage = x$sd.shrinkage, 
-                         post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
-                         post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
-    } else {
-      temp <- data.frame(sample.mean = x$sample.mean, n = x$se, x = cova, prior.mean = x$prior.mean.hat,
-                         shrinkage = x$shrinkage, sd.shrinkage = x$sd.shrinkage, 
-                         post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
-                         post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
-    }
-
-  } else if (is.na(x$prior.mean) & identical(x$X, NA)) { # if there are neither prior.mean and X assigned
-
-    if (x$model == "gr") {
-      temp <- data.frame(sample.mean = x$sample.mean, se = x$se, prior.mean = x$prior.mean.hat,
-                         shrinkage = x$shrinkage, sd.shrinkage = x$sd.shrinkage, 
-                         post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
-                         post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
-    } else {
-      temp <- data.frame(sample.mean = x$sample.mean, n = x$se, prior.mean = x$prior.mean.hat,
[…]

### 2013-03-09 Rgbp/R/gr.R

@@ -1,166 +1,0 @@
-#Note this R code fits the hierarchical normal-normal model using ADM
-#Author: Joseph Kelly
-
-gr<-function(y,se,X,mu,Alpha=0.95,intercept=T,eps=0.0001){
-	
-  ##define some values that will be used often
-  muknown <- !missing(mu)
-  if (!muknown) {
-    prior.mean <- NA
-  } else {
-	prior.mean <- mu
-  }
-  type <- 1
-  k <- length(y)
-  V <- se^2
-  if(missing(X)){
-    X.ini<-NA
-    X <- as.matrix(rep(1,k))
-  }else{
-    X <- X.ini <- as.matrix(X)
-    if(intercept)
-      X <- cbind(rep(1,k),X)
-  }
-	
-  ##optimize depending on if mu is specified. 
-  if(muknown){
-    r<-0
-    est <- optim(mean(log(V)),function(x){gr.ll.muknown(exp(x),y,V,mu,type)},lower=0,upper=Inf,control=list(fnscale=-1),method="L-BFGS-B",hessian=T)
-    est.var <- solve(-1*as.matrix(est$hessian))
-    Ahat <- exp(est$par)
-    Betahat<-NA
-    Betahatvar<-NA
-  }else{
-    r <- dim(X)[2]
-    est <- optim(mean(log(V)), function(x){gr.ll.muunknown(exp(x[1]),y,V,X,type)},control=list(fnscale=-1),method="L-BFGS-B",gr = function(x){derval(x,y,V,X)}, hessian=T)
-    est.var <- -1/est$hessian
-    Ahat <- exp(est$par[1])
-  }
-
-  ##calculate estimates
-  ninfo <- -1*as.matrix(est$hessian)[1,1]
-  Avar<-est.var[1,1]*Ahat^2
-  Bhat<-V/(V+Ahat)
-  a0<-ninfo/Bhat
-  a1<-ninfo/(1-Bhat)
-  v<-Bhat*(1-Bhat)/(a1+a0+1)
-  seB<-sqrt(v)
-  skewB<-2*(a0-a1)*sqrt(1+a0+a1)/(sqrt(a0*a1)*(2+a0+a1))
[…]

### 2013-03-09 Rgbp/R/pr.R

@@ -1,292 +1,0 @@
-PRInitialValue2ndLevelMeanKnown <- function(given) {
-  # This function makes the initial values needed to run PRIMM.
-  # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
- 
-  r.ini <- given$prior.mean / var(given$sample.mean)
-
-  list(a.ini = -log(r.ini))
-}
-
-PRInitialValue2ndLevelMeanUnknown <- function(given) {
-  # This function makes the initial values needed to run PRIMM.
-  # "Un" means the descriptive second level mean (mean of Beta distribution) is unknown.
-
-  y <- given$sample.mean
-  z <- given$z
-  n <- given$n
-  x.ini <- given$x.ini
-
-  if (identical(x.ini, NA) & !given$intercept) {
-    print("In case we do not designate prior mean, at least one beta should be estimated 
-           (either intercept=T or at least one covariate is needed)")
-    stop()
-  } else if (identical(x.ini, NA) & given$intercept) {
-    x <- matrix(1, length(y), 1)
-    b.ini <- mean(y)
-  } else if (!identical(x.ini, NA) & given$intercept) {
-    x.ini <- as.matrix(x.ini)
-    xname <- paste("x.ini[, ", 1 : ncol(x.ini), "]", sep = "")
-    formula <- as.formula(paste("z ~ ", paste(xname, collapse = "+")))
-    b.ini <- glm(formula, offset = log(n), family = poisson)$coefficients
-    x <- as.matrix(cbind(rep(1, length(y)), x.ini))
-  } else if (!identical(x.ini,NA) & !given$intercept) {
-    x.ini <- as.matrix(x.ini)
-    xname <- paste("x.ini[, ", 1 : ncol(x.ini), "]", sep = "")
-    formula <- as.formula(paste("z ~ ", paste(xname, collapse = "+"), "- 1"))
-    b.ini <- glm(formula, offset = log(n), family = poisson)$coefficients
-    x <- x.ini
-  }	
-
-  mu0.ini <- mean(exp(x %*% b.ini))
-  r.ini <- mu0.ini / var(y)
-
-  list(x = x, b.ini = b.ini, a.ini = -log(r.ini))
-}
-
[…]

### 2013-03-09 gbuild.sh

@@ -1,3 +1,0 @@
-#!/bin/sh
-R CMD build Rgbp
-R CMD check --as-cran Rgbp_*.tar.gz

### 2013-03-09 jss/article.tex
change

@@
 \author{Joseph Kelly\\Harvard University \And 
-        Hyung Suk Tak\\Harvard University \And
+        Hyungsuk Tak\\Harvard University \And
         Carl Morris\\ Harvard University}
@@
   E-mail: \email{kelly2@fas.harvard.edu}\\
-  URL: \url{http://www.people.fas.harvard.edu/~kelly2/}
+  URL: \url{http://www.people.fas.harvard.edu/~kelly2/}\\
+
+  Hyungsuk Tak\\
+  Department of Statistics\\
+  Harvard University\\
+  1 Oxford Street, Cambridge, MA\\
+  E-mail: \email{tak@fas.harvard.edu}\\
+
+  Carl Morris\\
+  Department of Statistics\\
+  Harvard University\\
+  1 Oxford Street, Cambridge, MA\\
+  E-mail: \email{morris@fas.harvard.edu}\\
 }
+
 %% It is also possible to add a telephone and fax number

### 2013-03-09 jss/article.tex
removing newton.R

@@
 \author{Joseph Kelly\\Harvard University \And 
-        Hyungsuk Tak\\Harvard University \And
-        Carl Morris\\ Harvard University}
+             Carl Morris\\ Harvard University\And
+             Hyungsuk Tak\\Harvard University }
 \title{\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling}
@@
 %% for pretty printing and a nice hypersummary also set:
-\Plainauthor{Joseph Kelly, Hyung Suk Tak, Carl Morris} %% comma-separated
+\Plainauthor{Joseph Kelly, Carl Morris, Hyung Suk Tak} %% comma-separated
 \Plaintitle{Rgbp: Empirical Bayesian Hierarchical Modeling} %% without formatting

### 2013-03-09 Rgbp/R/br.R
what is wrong

@@ -1,0 +1,355 @@
+BRInitialValue2ndLevelMeanKnown <- function(given) {
+  # This function makes the initial values needed to run BRIMM.
+  # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
+
+  if (given$prior.mean == 0) {
+    r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / var(given$sample.mean)
+  } else {
+    r.ini <- given$prior.mean * (1 - given$prior.mean) / var(given$sample.mean)
+  }
+
+  list(r.ini = r.ini, a.ini = -log(r.ini))
+}
+
+BRInitialValue2ndLevelMeanUnknown <- function(given) {
+  # This function makes the initial values needed to run BRIMM.
+  # "Un" means the descriptive second level mean (mean of Beta distribution) is unknown.
+
+  y <- given$sample.mean
+  z <- given$z
+  n <- given$n
+  x.ini <- given$x.ini
+
+  if (identical(x.ini, NA) & !given$intercept) {
+    print("In case we do not designate prior mean, at least one beta should be estimated 
+           (either intercept=T or at least one covariate is needed)")
+    stop()
+  } else if (identical(x.ini, NA) & given$intercept) {
+    x <- matrix(1, length(y), 1)
+    b.ini <- as.vector(log(mean(y) / (1 - mean(y))))
+  } else if (!identical(x.ini, NA) & given$intercept) {
+    x.ini <- as.matrix(x.ini)
+    xname <- paste("x.ini[, ", 1 : ncol(x.ini), "]", sep = "")
+    formula <- as.formula(paste("cbind(z, n - z) ~ ", paste(xname, collapse = "+")))
+    b.ini <- glm(formula, family = binomial)$coefficients
+    x <- as.matrix(cbind(rep(1, length(y)), x.ini))
+  } else if (!identical(x.ini, NA) & !given$intercept) {
+    x.ini <- as.matrix(x.ini)
[…]

### 2013-03-09 Rgbp/R/coverage.R

@@ -1,0 +1,375 @@
+
+coverage <- function(x, y, beta, X, mu0, nsim = 10, ...) {
+
+  # Rao-Blackwellized criterion
+  coverageRB <- matrix(NA, nrow = length(x$se), ncol = nsim)
+
+  # 1-0 criterion that is 1 if interval includes true parameter, 0 if not
+  coverage10 <- matrix(NA, nrow = length(x$se), ncol = nsim)
+
+  if (missing(y)) {
+    only.gbp.result <- T
+  } else {
+    only.gbp.result <- F
+  }
+
+  # if model=BRIMM	
+  if (x$model == "br") {
+    if (only.gbp.result) {
+      # 1. initial values
+      if (is.na(x$prior.mean) & identical(x$X, NA)) {
+        temp.x <- as.matrix(rep(1, length(x$se)))
+        betas <- as.vector(x$beta.new)
+        p0 <- exp(temp.x %*% betas) / (1 + exp(temp.x %*% betas))
+      } else if (is.na(x$prior.mean) & !identical(x$X, NA)) {
+        temp.x <- as.matrix(cbind(rep(1, length(x$se)), x$X))
+        betas <- as.vector(x$beta.new)
+        p0 <- exp(temp.x %*% betas) / (1 + exp(temp.x %*% betas))
+        X <- x$X
+      } else if (!is.na(x$prior.mean)) {
+        p0 <- x$prior.mean
+      }
+  
+      n <- x$se
+      r <- exp(-x$a.new)
+
+      # 2. generate p matrix
+      sim.p <- matrix(rbeta(length(n) * nsim, r * p0, r * (1 - p0)), nrow = length(n))
+
+      # 3. generate z (data) matrix
+      sim.z <- matrix(rbinom(nrow(sim.p) * nsim, n, sim.p), nrow = length(n))
+
+      # 4. simulation
+      for (i in 1 : nsim) {
+        tryCatch({
+          out <- if (is.na(x$prior.mean) & identical(x$X, NA)) {
+                   gbp(sim.z[, i], n, model = "br")
+                 } else if (is.na(x$prior.mean) & !identical(x$X, NA)) {
+                   gbp(sim.z[, i], n, X, model = "br")
+                 } else if (!is.na(x$prior.mean)) {
+                   gbp(sim.z[, i], n, mu0 = p0, model = "br")
+                 }
+
+          a1 <- r * p0 + sim.z[, i]
[…]

### 2013-03-09 Rgbp/R/gbp.R

@@ -1,0 +1,323 @@
+gbp <- function(x, ...) UseMethod("gbp")
+
+gbp.default <- function(x, y, covariates, mu0, model = "gr", intercept = T, Alpha = 0.95, ...) {
+  res <- switch(model, 
+                gr = gr(x, y, X = covariates, mu = mu0, Alpha = Alpha, intercept = intercept), 
+                br = br(x, y, X = covariates, prior.mean = mu0, intercept = intercept, Alpha = Alpha), 
+                pr = pr(x, y, X = covariates, prior.mean = mu0, intercept = intercept, Alpha = Alpha))
+  
+  class(res) <- "gbp"	
+  res
+}
+
+print.gbp <- function(x, ...) {
+  
+  if (is.na(x$prior.mean) & !identical(x$X, NA)) {
+
+	cova <- as.matrix(x$X)
+	colnames(cova) <- paste(1 : dim(cova)[2])
+    
+    if (x$model == "gr") {
+      temp <- data.frame(sample.mean = x$sample.mean, se = x$se, x = cova, prior.mean = x$prior.mean.hat,
+                         shrinkage = x$shrinkage, sd.shrinkage = x$sd.shrinkage, 
+                         post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
+                         post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
+    } else {
+      temp <- data.frame(sample.mean = x$sample.mean, n = x$se, x = cova, prior.mean = x$prior.mean.hat,
+                         shrinkage = x$shrinkage, sd.shrinkage = x$sd.shrinkage, 
+                         post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
+                         post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
+    }
+
+  } else if (is.na(x$prior.mean) & identical(x$X, NA)) { # if there are neither prior.mean and X assigned
+
+    if (x$model == "gr") {
+      temp <- data.frame(sample.mean = x$sample.mean, se = x$se, prior.mean = x$prior.mean.hat,
+                         shrinkage = x$shrinkage, sd.shrinkage = x$sd.shrinkage, 
+                         post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
+                         post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
+    } else {
+      temp <- data.frame(sample.mean = x$sample.mean, n = x$se, prior.mean = x$prior.mean.hat,
[…]

### 2013-03-09 Rgbp/R/gr.R

@@ -1,0 +1,166 @@
+#Note this R code fits the hierarchical normal-normal model using ADM
+#Author: Joseph Kelly
+
+gr<-function(y,se,X,mu,Alpha=0.95,intercept=T,eps=0.0001){
+	
+  ##define some values that will be used often
+  muknown <- !missing(mu)
+  if (!muknown) {
+    prior.mean <- NA
+  } else {
+	prior.mean <- mu
+  }
+  type <- 1
+  k <- length(y)
+  V <- se^2
+  if(missing(X)){
+    X.ini<-NA
+    X <- as.matrix(rep(1,k))
+  }else{
+    X <- X.ini <- as.matrix(X)
+    if(intercept)
+      X <- cbind(rep(1,k),X)
+  }
+	
+  ##optimize depending on if mu is specified. 
+  if(muknown){
+    r<-0
+    est <- optim(mean(log(V)),function(x){gr.ll.muknown(exp(x),y,V,mu,type)},lower=0,upper=Inf,control=list(fnscale=-1),method="L-BFGS-B",hessian=T)
+    est.var <- solve(-1*as.matrix(est$hessian))
+    Ahat <- exp(est$par)
+    Betahat<-NA
+    Betahatvar<-NA
+  }else{
+    r <- dim(X)[2]
+    est <- optim(mean(log(V)), function(x){gr.ll.muunknown(exp(x[1]),y,V,X,type)},control=list(fnscale=-1),method="L-BFGS-B",gr = function(x){derval(x,y,V,X)}, hessian=T)
+    est.var <- -1/est$hessian
+    Ahat <- exp(est$par[1])
+  }
+
+  ##calculate estimates
+  ninfo <- -1*as.matrix(est$hessian)[1,1]
+  Avar<-est.var[1,1]*Ahat^2
+  Bhat<-V/(V+Ahat)
+  a0<-ninfo/Bhat
+  a1<-ninfo/(1-Bhat)
+  v<-Bhat*(1-Bhat)/(a1+a0+1)
+  seB<-sqrt(v)
+  skewB<-2*(a0-a1)*sqrt(1+a0+a1)/(sqrt(a0*a1)*(2+a0+a1))
[…]

### 2013-03-09 Rgbp/R/pr.R

@@ -1,0 +1,292 @@
+PRInitialValue2ndLevelMeanKnown <- function(given) {
+  # This function makes the initial values needed to run PRIMM.
+  # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
+ 
+  r.ini <- given$prior.mean / var(given$sample.mean)
+
+  list(a.ini = -log(r.ini))
+}
+
+PRInitialValue2ndLevelMeanUnknown <- function(given) {
+  # This function makes the initial values needed to run PRIMM.
+  # "Un" means the descriptive second level mean (mean of Beta distribution) is unknown.
+
+  y <- given$sample.mean
+  z <- given$z
+  n <- given$n
+  x.ini <- given$x.ini
+
+  if (identical(x.ini, NA) & !given$intercept) {
+    print("In case we do not designate prior mean, at least one beta should be estimated 
+           (either intercept=T or at least one covariate is needed)")
+    stop()
+  } else if (identical(x.ini, NA) & given$intercept) {
+    x <- matrix(1, length(y), 1)
+    b.ini <- mean(y)
+  } else if (!identical(x.ini, NA) & given$intercept) {
+    x.ini <- as.matrix(x.ini)
+    xname <- paste("x.ini[, ", 1 : ncol(x.ini), "]", sep = "")
+    formula <- as.formula(paste("z ~ ", paste(xname, collapse = "+")))
+    b.ini <- glm(formula, offset = log(n), family = poisson)$coefficients
+    x <- as.matrix(cbind(rep(1, length(y)), x.ini))
+  } else if (!identical(x.ini,NA) & !given$intercept) {
+    x.ini <- as.matrix(x.ini)
+    xname <- paste("x.ini[, ", 1 : ncol(x.ini), "]", sep = "")
+    formula <- as.formula(paste("z ~ ", paste(xname, collapse = "+"), "- 1"))
+    b.ini <- glm(formula, offset = log(n), family = poisson)$coefficients
+    x <- x.ini
+  }	
+
+  mu0.ini <- mean(exp(x %*% b.ini))
+  r.ini <- mu0.ini / var(y)
+
+  list(x = x, b.ini = b.ini, a.ini = -log(r.ini))
+}
+
[…]

### 2013-04-06 jss/article.tex
paper on going

@@
              Hyungsuk Tak\\Harvard University }
-\title{\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling}
+\title{\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check}
 
@@
 \Plainauthor{Joseph Kelly, Carl Morris, Hyung Suk Tak} %% comma-separated
-\Plaintitle{Rgbp: Empirical Bayesian Hierarchical Modeling} %% without formatting
-\Shorttitle{\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling} %% a short title (if necessary)
+\Plaintitle{Rgbp: Bayesian Hierarchical Modeling and Frequentist Method Check} %% without formatting
 
 %% an abstract and keywords
-\Abstract{
-  Empirical Bayesian Hierarchical modeling for Gaussian, Binomial, and Poisson Data
-}
-\Keywords{keywords, comma-separated, not capitalized, \proglang{R}}
+\Abstract{Bayesian-frequentist reconciliation via Bayesian hierarchical modeling for Gaussian, Binomial, and Poisson data and frequentist method check for good coverage probability.}
+\Keywords{hierarchical model, multi-level model, random effects mixed model, method check, coverage probability, normal, binomial, poisson, shrinkage, \proglang{R}}
 \Plainkeywords{keywords, comma-separated, not capitalized, r} %% without formatting
@@
 
-  Hyungsuk Tak\\
-  Department of Statistics\\
-  Harvard University\\
-  1 Oxford Street, Cambridge, MA\\
-  E-mail: \email{tak@fas.harvard.edu}\\
-
   Carl Morris\\
@@
   E-mail: \email{morris@fas.harvard.edu}\\
+
+  Hyungsuk Tak\\
+  Department of Statistics\\
+  Harvard University\\
+  1 Oxford Street, Cambridge, MA\\
+  E-mail: \email{hyungsuk.tak@gmail.com}\\
+
 }
@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
+\pkg{Rgbp} uses Bayesian machinery to estimate a two-level model (a random-effects mixed model) and allows for a check of its frequentist properties via a repeated sampling procedure (which we call a "method check").
+It is found that even in small samples our procedure yields good frequency properties.
+Also, this package will be useful for Bayesians who want to see a non-informative reference point before and after constructing their full-Bayesian hierarchical model.
+For frequentists, it will provide confidence intervals of a random-effect mixed model with good repeated sampling properties.
 
-\section[estimation]{Estimation}
-\subsection[adm]{Adjustment for Density Maximization}
+\section[Feasible Data Types]{Three Feasible Types of Data }
+This package is intended to fit a multi-level model on the group-level (or unit-level) data in which each group-level (or unit-level) observation is believed to have the Normal, Poisson, or Binomial distribution.
+In this section, we will introduce three specific types of feasible datasets.
 
-\section[userguide]{User Guide}
+\subsection{Normal: 8 Schools' Data}
+Education Testing Service conducted randomized experiments in eight separate schools and obtained this dataset.
+It contains the coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) obtained after an analysis of covariance adjustment (Rubin, 1981).
+\begin{center}
+Table 1: The first four schools' data among 8 schools
+\\
+~
+\\
+\begin{tabular}{|c|c|c|}
+\hline
+School & Estimated Coaching Effect & Standard Error\\
+\hline
+A & 28 & 15\\
+\hline
+B & 8 & 10\\
+\hline
+C & -3 & 16\\
+\hline
+D & 7 & 11\\
+\hline
+\end{tabular}
+\end{center}
+~
 
-\section[discussion]{Discussion}
+In the original paper, each school's coaching effect has approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
+So, it is reasonable to think that each (group-level) coaching effect is distributed as independent Normal distribution with unknown mean and known standard error:  $y_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
+\\
+
+\pkg{Rgbp} includes this dataset and can be called by typing \code{data(schools)} on \proglang{R}.
+
+\subsection{Poisson: 31 Hospital Data}
+This dataset is about the medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 (Morris and Lysy, 2012).
+It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$).
+The Table 2 contains a few rows of this dataset.
+\begin{center}
+Table 2: The last four hospitals' data among 31 hospitals
+\\
+~
+\\
+\begin{tabular}{|c|c|c|}
+\hline
+Hospital Number & Number of Deaths & Number of Trials\\
+\hline
+28 & 25 & 914\\
+\hline
+29 & 20 & 940\\
+\hline
+30 & 35 & 1193\\
+\hline
+31 & 27 & 1340\\
+\hline
+\end{tabular}
+\end{center}
+~
+
+Considering the type of data, it will make sense to assume the number of deaths in each hospital has independent Poisson distribution with unknown parameter: $z_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j}), ~j=1, \ldots, 31,$ where $n_{j}$ can also be interpreted as an exposure (not necessarily an interger).
+\\
+
+This dataset is also included in the package and can be called by \code{data(hospital)} on \proglang{R}.
+
+\subsection{Binomial: 18 Baseball Data}
+This dataset contains information about batting averages of 18 major league players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
+The first four rows of this dataset is described in the following table.
+\begin{center}
+Table 3: The first four players' data among 18 players
+\\
+~
+\\
+\begin{tabular}{|c|c|c|c|}
+\hline
+Player Name & Number of Hits & Number of At-Bats &League\\
+\hline
+Roberto Clemente & 18 & 45 & National\\
+\hline
+Frank Robinson & 17 & 45 & American\\
+\hline
+Frank Howard & 16 & 45 & American\\
+\hline
+Jay Johnstone & 15 & 45 & American\\
+\hline
+\end{tabular}
+\end{center}
+~
+
+The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats: $z_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
+\\
+
+This dataset is also a part of the package and can be called on \proglang{R} by \code{data(baseball)}.
+
+\section[Multi-level Structure]{Multi-level Structure}
+Hierarchical model is a very powerful tool to (justification of hierarchical model for hierarchical data??)
+\\
+
+\code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy is a distribution of observed data and second-level is a conjugate prior distribution on the first-level parameter.
+Users can determine one of three types of multi-level models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets.
+\\
+
+\subsection[Normal-Normal]{Normal-Normal}
+\code{gbp} can construct a two-level Normal-Normal hierarchical model on the 8 school data.
+For reference,  $\sigma^{2}_{j}$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th school in the dataset.
+\begin{displaymath}
+y_{j}\vert \mu_{j} \stackrel{ind}{\sim}\textrm{Normal}(\mu_{j}, \sigma^{2}_{j}),
+\end{displaymath}
+\begin{displaymath}
+\mu_{j}\vert \beta, A\stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, A),
+\end{displaymath}
+
+where $\mu_{0j} =x_{j}'\beta,~j=1, \ldots, 8$, and a paramter with a zero sub-index represents it is a mean parameter of the prior (second-level) distribution.
+Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution.
+\begin{displaymath}
+\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})\sigma^{2}_{j}),
+\end{displaymath}
+where $B_{j}\equiv\frac{\sigma^{2}_{j}}{\sigma^{2}_{j} + A},~j=1, \ldots, 8$ is called a shrinkages and we will explain it in the following section.
+
+\subsection[Poisson-Gamma]{Poisson-Gamma}
+\code{gbp} is also able to build a Poisson-Gamma multi-level model on the 31 hospital data.
+Note that a constant multiplied to the notation representing Gamma distribution is a scale and a square bracket below indicates [mean, variance] of distribution.
+\begin{displaymath}
+z_{j}\vert \lambda_{j} \stackrel{ind}{\sim}\textrm{Poisson}(n_{j}\lambda_{j}),
+\end{displaymath}
+\begin{displaymath}
+\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(\lambda_{0j}r)\sim \textrm{Gamma}[\lambda_{0j}, ~\frac{\lambda_{0j}}{r}],
+\end{displaymath}
+
+where $\log(\lambda_{0j}) =x_{j}'\beta$, and $j=1, \ldots, 31$. Immediate posterior distribution of this Poisson-Gamma model is
+\begin{displaymath}
+\lambda_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0j} + z_{j})\sim\textrm{Gamma}[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}}],
+\end{displaymath}
+
+where $\lambda^{\ast}_{j} \equiv (1-B_{j})(\frac{z_{j}}{n_{j}}) + B_{j}\lambda_{0j},~\textrm{and}~ B_{j}\equiv \frac{r}{r+n_{j}},~ j=1, \ldots, 31$.
+
+\subsection[Binomial-Beta]{Binomial-Beta}
+Binomial-Beta hierarchical model is the last model that \code{gbp} can fit. Again, a square bracket below indicates [mean, variance] of distribution.
+\begin{displaymath}
+z_{j} \vert p_{0j}\stackrel{ind}{\sim}\textrm{Binomial}(n_{j}, ~p_{j}),
+\end{displaymath}
+\begin{displaymath}
+p_{j} \vert \beta, r\stackrel{ind}{\sim}\textrm{Beta}(rp_{0j},~ r(1-p_{0j}))\sim \textrm{Beta}[p_{0j}, ~\frac{p_{0j}(1-p_{0j})}{r + 1}],
+\end{displaymath}
+
+where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta~\textrm{and}~j=1, \ldots, 18$. Then posterior distribution is
+\begin{displaymath}
+p_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+z_{j},~r(1-p_{0j})+n_{j}-z_{j})\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
+\end{displaymath}
+where $p^{\ast}_{j}\equiv(1-B_{j})(\frac{z_{j}}{n_{j}})+B_{j}p_{0j},~ \textrm{and}~ B_{j}\equiv\frac{r}{r+n_{j}}$, $j=1,\ldots,18$.
+
+\subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
+Hyper-prior distribution indicates a distribution of the second-level parameters, which plays an important role in deriving a full posterior distribution of all the parameters.
+\code{gbp} sets a non-informative distribution on second-level parameters to let the data speak more about their estimation.
+\begin{displaymath}
+\beta \sim \textrm{flat on}~ \mathbf{R}^{m},~~A ~(\textrm{or}~ \frac{1}{r})\sim \textrm{Unif}(0, \infty),
+\end{displaymath}
+
+where $m$ is the number of regression coefficients.
+For $\beta$, it is reasonable choice to take flat (non-informative) distribution because the information about location gets informative as number of groups increases.
+Another flat prior on the hyper-prameter $A$ (or $1/r$) that we suggest here will guarantee a posterior propriety under the moderate conditions and will give users a good repeated sampling property.
+\\
+
+\section[Estimation]{Estimation}
+\subsection[Shrinkage Estimation]{Shrinkage Estimation}
+Estimating shrinkage is a key part of our work because as we can see posterior mean is a linear function of shrinkage and posterior variance is also a linear (Gaussian), quadratic (Poisson), or cubic (Binomial) function of shrinkage.
+Once we estimate it, we can approximate the posterior moments given only data, for example, $E(\mu_{j}\vert \textbf{y})$ for Gaussian model.
+\subsection[ADM]{Adjustment for Density Maximization}
+When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv\frac{\sigma^{2}}{\sigma^{2}+A}=B_{j}(A)$ for Gaussian and $B_{j}\equiv\frac{r}{r+n_{j}}=B_{j}(r)$ for Poisson and Binomial models.
+\\
+
+In this case, one way is to obtain an MLE of the variance component with its asymptotic Normal distribution and to use Delta method for asymptotic Normal distribution of shrinkage.
+But is the Normal approximation a good approximation for shrinkage that takes on values between 0 and 1?
+\\
+
+Here Adjustment for Density Maximization (Morris and Tang, 2011), called ADM, comes.
+It assumes the Beta distribution for shrinkage, which the authors believe is a much better approximation for it, and estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$.
+
+\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Moment Matching}
+After estimating two posterior moments, \code{gbp} reasonably approximates posterior distribution (given only data) by matching two moments with its parameters.
+The reason we use `reasonable' is that it is hard to find a closed form of posterior distribution given only data unless it is a Gaussian model.
+So, we assumed $p_{j}\vert \textrm{data}$ has also Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textrm{data})$ and $Var(p_{j}\vert \textrm{data})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.
+
+\section[Method Check]{Method Check}
+\subsection{Unbiased Coverage Probability}
+\subsection{Rao-Blackwellized Coverage Probability}
+\section[Example]{Example}
+\subsection[Known Prior Mean]{Known Prior Mean}
+Using 10 hospital data with PR
+\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
+Using 8 school data with GR
+\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
+Using 18 baseball data with BR
+
+\section[Discussion]{Discussion}
 
@@
 
+\section[Reference]{Reference}
+Efron, B. and Morris, C. (1975). Data Analysis Using Stein's Estimator and its Generalizations. \emph{Journal of the American Statistical Association}. \textbf{70}. 311-319.
+\\
+Rubin, D. B. (1981). Estimation in parallel randomized
+  experiments. \emph{Journal of Educational Statistics}. \textbf{6}. 377-401.
+\\
+Morris, C. and Tang, R. (2011). Estimating Random Effects via Adjustment for Density Maximization. \emph{Statistical Science}. \textbf{26}. 271-287.
+\\
+Morris, C. and Lysy, M. (2012). Shrinkage Estimation in Multilevel Normal Models. \emph{Statistical Science}. \textbf{27}. 115-134.
+\\
+
 \end{document}

### 2013-04-06 jss/article.tex
journal writing

@@
 Education Testing Service conducted randomized experiments in eight separate schools and obtained this dataset.
-It contains the coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) obtained after an analysis of covariance adjustment (Rubin, 1981).
-\begin{center}
-Table 1: The first four schools' data among 8 schools
-\\
-~
-\\
-\begin{tabular}{|c|c|c|}
-\hline
-School & Estimated Coaching Effect & Standard Error\\
-\hline
-A & 28 & 15\\
-\hline
-B & 8 & 10\\
-\hline
-C & -3 & 16\\
-\hline
-D & 7 & 11\\
-\hline
-\end{tabular}
-\end{center}
-~
+It contains the coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of eight schools obtained after an analysis of covariance adjustment (Rubin, 1981).
+\begin{CodeChunk}
+\begin{CodeInput}
+R> y  <- c(28,  8, -3,  7, -1,  1, 18, 12)
+R> se <- c(15, 10, 16, 11,  9, 11, 10, 18)
+\end{CodeInput}
+\end{CodeChunk}
 
 In the original paper, each school's coaching effect has approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
-So, it is reasonable to think that each (group-level) coaching effect is distributed as independent Normal distribution with unknown mean and known standard error:  $y_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
-\\
-
-\pkg{Rgbp} includes this dataset and can be called by typing \code{data(schools)} on \proglang{R}.
+So, it is reasonable to think that each (group-level) coaching effect is distributed as independent Normal distribution with unknown mean and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
+\pkg{Rgbp} includes this dataset and can be called by typing `\code{R> data(schools)}' on \proglang{R}.
 
@@
 It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$).
-The Table 2 contains a few rows of this dataset.
-\begin{center}
-Table 2: The last four hospitals' data among 31 hospitals
-\\
-~
-\\
-\begin{tabular}{|c|c|c|}
-\hline
-Hospital Number & Number of Deaths & Number of Trials\\
-\hline
-28 & 25 & 914\\
-\hline
-29 & 20 & 940\\
-\hline
-30 & 35 & 1193\\
-\hline
-31 & 27 & 1340\\
-\hline
-\end{tabular}
-\end{center}
-~
+The below code is an example of input based on the last ten hospital data.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> z <- c( 14,   9,  15,  13,  35,  26,  25,  20,   35,   27)
+R> n <- c(593, 602, 629, 636, 729, 849, 914, 940, 1193, 1340)
+\end{CodeInput}
+\end{CodeChunk}
 
-Considering the type of data, it will make sense to assume the number of deaths in each hospital has independent Poisson distribution with unknown parameter: $z_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j}), ~j=1, \ldots, 31,$ where $n_{j}$ can also be interpreted as an exposure (not necessarily an interger).
-\\
-
-This dataset is also included in the package and can be called by \code{data(hospital)} on \proglang{R}.
+Considering the type of data, it will make sense to assume the number of deaths in each hospital has independent Poisson distribution with unknown parameter: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j}), ~j=1, \ldots, 31,$ where $n_{j}$ can also be interpreted as an exposure (not necessarily an interger).
+This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.
 
@@
 This dataset contains information about batting averages of 18 major league players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
-The first four rows of this dataset is described in the following table.
-\begin{center}
-Table 3: The first four players' data among 18 players
-\\
-~
-\\
-\begin{tabular}{|c|c|c|c|}
-\hline
-Player Name & Number of Hits & Number of At-Bats &League\\
-\hline
-Roberto Clemente & 18 & 45 & National\\
-\hline
-Frank Robinson & 17 & 45 & American\\
-\hline
-Frank Howard & 16 & 45 & American\\
-\hline
-Jay Johnstone & 15 & 45 & American\\
-\hline
-\end{tabular}
-\end{center}
-~
-
-The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats: $z_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
-\\
-
-This dataset is also a part of the package and can be called on \proglang{R} by \code{data(baseball)}.
+Also, it has one binary covariate indicating whether a player was in the National league (1) or the American league (0).
+The code below shows a way to make inputs using the first 10 players.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11)
+R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
+R> x <- c( 1,  0,  0,  0,  0,  0,  1,  0,  1,  1) 
+\end{CodeInput}
+\end{CodeChunk}
+The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
+This dataset is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.
 
@@
 
-\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Moment Matching}
-After estimating two posterior moments, \code{gbp} reasonably approximates posterior distribution (given only data) by matching two moments with its parameters.
-The reason we use `reasonable' is that it is hard to find a closed form of posterior distribution given only data unless it is a Gaussian model.
-So, we assumed $p_{j}\vert \textrm{data}$ has also Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textrm{data})$ and $Var(p_{j}\vert \textrm{data})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.
+\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
+After estimating two posterior moments, \code{gbp} reasonably approximates posterior distribution given only data, \emph{i.e.}, ($\mu_{j}\vert \textrm{data}$), ($\lambda_{j}\vert \textrm{data}$), or ($p_{j}\vert \textrm{data}$), by matching two moments with its parameters.
+The reason we said `reasonablely approximates' is that it is hard to find a closed form of posterior distribution given only data unless it is a Gaussian model.
+So, we assumed $(p_{j}\vert \textrm{data})$ has also Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textrm{data})$ and $Var(p_{j}\vert \textrm{data})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.
 
 \section[Method Check]{Method Check}
+
+\subsection{Pseudo-data Generation Process}
 \subsection{Unbiased Coverage Probability}

### 2013-04-06 jss/article.tex
journal writing

@@
 \section[Method Check]{Method Check}
+Like the two sides of the same coin, checking a statistical model always comes with fitting a model.
+If a fitted model cannot pass a checking process, we usually go back to the fitting process and come back to checking process iteratively.
+In this sense, checking a fitted model is an interactive procedure for the model justification.
+\\
 
+There are two kinds of model justification process; one is a model check and the other is a method check.
+The model check is for the justification of a hierarchical modeling on a specific dataset.
+One possible question is, ``Can this dataset benefit from such a modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $(z_{j}\vert \beta, r)\sim\textrm{Negative-Binomial}$, for Poisson data to justify the second-level hierarchy.
+They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
+\\
+
+The other model justification process is the method check.
 \subsection{Pseudo-data Generation Process}
@@
 \section[Reference]{Reference}
-Efron, B. and Morris, C. (1975). Data Analysis Using Stein's Estimator and its Generalizations. \emph{Journal of the American Statistical Association}. \textbf{70}. 311-319.
+Christiansen, C.
+and Morris, C.
+(1996).
+``Fitting and Checking a Two-Level Poisson Model: Modeling Patient Mortality Rates in Heart Transplant Patients,'' in \emph{Bayesian Biostatistics}, eds.
+D.
+Berry and D.
+Stangl, New York: Marcel Dekker, pp.
+467-561.
 \\
-Rubin, D. B. (1981). Estimation in parallel randomized
-  experiments. \emph{Journal of Educational Statistics}. \textbf{6}. 377-401.
+Efron, B. and Morris, C. (1975). ``Data Analysis Using Stein's Estimator and its Generalizations.'' \emph{Journal of the American Statistical Association}. \textbf{70}. 311-319.
 \\
-Morris, C. and Tang, R. (2011). Estimating Random Effects via Adjustment for Density Maximization. \emph{Statistical Science}. \textbf{26}. 271-287.
+Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
 \\
-Morris, C. and Lysy, M. (2012). Shrinkage Estimation in Multilevel Normal Models. \emph{Statistical Science}. \textbf{27}. 115-134.
+Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
+\\
+Rubin, D. B. (1981). ``Estimation in parallel randomized
+  experiments.'' \emph{Journal of Educational Statistics}. \textbf{6}. 377-401.
 \\

### 2013-04-07 jss/article.tex
journal writing

@@
 
-The other model justification process is the method check.
+Once we are sure that the hierarchical modeling can add a huge value on our research, the next natural quetsion will be about the validity of interval estimates.
+``Does the confidence interval obtained via this Bayesian model-fitting process achieve pre-specified 100($1-\alpha$)\% confidence level for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point.
+
 \subsection{Pseudo-data Generation Process}

### 2013-04-07 jss/article.tex
writing journal theory almost done

@@
 For reference,  $\sigma^{2}_{j}$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th school in the dataset.
-\begin{displaymath}
+\begin{equation}
 y_{j}\vert \mu_{j} \stackrel{ind}{\sim}\textrm{Normal}(\mu_{j}, \sigma^{2}_{j}),
-\end{displaymath}
-\begin{displaymath}
+\end{equation}
+\begin{equation}
 \mu_{j}\vert \beta, A\stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, A),
-\end{displaymath}
+\end{equation}
 
@@
 Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution.
-\begin{displaymath}
+\begin{equation}
 \mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})\sigma^{2}_{j}),
-\end{displaymath}
+\end{equation}
 where $B_{j}\equiv\frac{\sigma^{2}_{j}}{\sigma^{2}_{j} + A},~j=1, \ldots, 8$ is called a shrinkages and we will explain it in the following section.
@@
 Note that a constant multiplied to the notation representing Gamma distribution is a scale and a square bracket below indicates [mean, variance] of distribution.
-\begin{displaymath}
+\begin{equation}
 z_{j}\vert \lambda_{j} \stackrel{ind}{\sim}\textrm{Poisson}(n_{j}\lambda_{j}),
-\end{displaymath}
-\begin{displaymath}
+\end{equation}
+\begin{equation}
 \lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(\lambda_{0j}r)\sim \textrm{Gamma}[\lambda_{0j}, ~\frac{\lambda_{0j}}{r}],
-\end{displaymath}
+\end{equation}
 
 where $\log(\lambda_{0j}) =x_{j}'\beta$, and $j=1, \ldots, 31$. Immediate posterior distribution of this Poisson-Gamma model is
-\begin{displaymath}
+\begin{equation}
 \lambda_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0j} + z_{j})\sim\textrm{Gamma}[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}}],
-\end{displaymath}
+\end{equation}
 
@@
 Binomial-Beta hierarchical model is the last model that \code{gbp} can fit. Again, a square bracket below indicates [mean, variance] of distribution.
-\begin{displaymath}
+\begin{equation}
 z_{j} \vert p_{0j}\stackrel{ind}{\sim}\textrm{Binomial}(n_{j}, ~p_{j}),
-\end{displaymath}
-\begin{displaymath}
+\end{equation}
+\begin{equation}
 p_{j} \vert \beta, r\stackrel{ind}{\sim}\textrm{Beta}(rp_{0j},~ r(1-p_{0j}))\sim \textrm{Beta}[p_{0j}, ~\frac{p_{0j}(1-p_{0j})}{r + 1}],
-\end{displaymath}
+\end{equation}
 
 where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta~\textrm{and}~j=1, \ldots, 18$. Then posterior distribution is
-\begin{displaymath}
+\begin{equation}
 p_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+z_{j},~r(1-p_{0j})+n_{j}-z_{j})\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
-\end{displaymath}
+\end{equation}
 where $p^{\ast}_{j}\equiv(1-B_{j})(\frac{z_{j}}{n_{j}})+B_{j}p_{0j},~ \textrm{and}~ B_{j}\equiv\frac{r}{r+n_{j}}$, $j=1,\ldots,18$.
@@
 \code{gbp} sets a non-informative distribution on second-level parameters to let the data speak more about their estimation.
-\begin{displaymath}
+\begin{equation}
 \beta \sim \textrm{flat on}~ \mathbf{R}^{m},~~A ~(\textrm{or}~ \frac{1}{r})\sim \textrm{Unif}(0, \infty),
-\end{displaymath}
+\end{equation}
 
@@
 ``Does the confidence interval obtained via this Bayesian model-fitting process achieve pre-specified 100($1-\alpha$)\% confidence level for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point.
+From now on, all the explanations will be based on the Binomial model.
 
 \subsection{Pseudo-data Generation Process}
+Figure 1 will be helpful to understand this process.
+As we can see in (8), the distribution of each true parameter ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(m\times1)}$, where $m$ is the number of regression coefficients.
+Once we fix these hyper-parameters at specific values, we can generate true parameters.
+Suppose we sampled 500 $\textbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\textbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$.
+Then, we can also generate $\{\textbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-dataset and $j$ does $j$-th player.
+Next, \code{coverage} fits the Binomial hierarchical model 500 times to obtain 500*18 interval estimates.
+Taking the first player as an example, we have 500 pairs of ($z_{i1}$, $p_{i1}$), $j=1,\ldots, 500$ and 500 interval estimates.
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=5cm]{process.png}
+\caption{Pseudo-data generating process}
+\end{center}
+\end{figure}
+
 \subsection{Unbiased Coverage Probability}
+Based on the generated pseudo-datasets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th interval estimate from $i$-th pseudo-dataset includes $p_{ij}$ and 0 otherwise.
+One way to estimate the coverage probability is to take average over those indicator variables.
+We call it an unbiased coverage probability estimate.
+For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first player.
 \subsection{Rao-Blackwellized Coverage Probability}
+Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$) as the Rao-Blackwellized coverage probability, where $r$ and $\beta$ were fixed at first (see 5.1).
+This expectation is the same as P$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where $\hat{p}_{ij, low}$ and $\hat{p}_{ij, upp}$ are interval estimates (numeric values).
+We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ is the Beta distribution in (9).
+For instance, the first player's Rao-Blackwellized coverage probability can be estimated by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
 \section[Example]{Example}

### 2013-04-07 jss/article.tex
typo

@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-\pkg{Rgbp} uses Bayesian machinery to estimate a two-level model (a random-effects mixed model) and allows for a check of its frequentist properties via a repeated sampling procedure (which we call a "method check").
+\pkg{Rgbp} uses Bayesian machinery to estimate a two-level model (a random-effects mixed model) and allows for a check of its frequentist properties via a repeated sampling procedure (which we call a ``method check").
 It is found that even in small samples our procedure yields good frequency properties.

### 2013-04-07 jss/article.tex
typo

@@
 In the original paper, each school's coaching effect has approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
-So, it is reasonable to think that each (group-level) coaching effect is distributed as independent Normal distribution with unknown mean and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
+So, it is reasonable to think that each (group-level) coaching effect is distributed as independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
 \pkg{Rgbp} includes this dataset and can be called by typing `\code{R> data(schools)}' on \proglang{R}.
@@
 
-Considering the type of data, it will make sense to assume the number of deaths in each hospital has independent Poisson distribution with unknown parameter: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j}), ~j=1, \ldots, 31,$ where $n_{j}$ can also be interpreted as an exposure (not necessarily an interger).
+Considering the type of data, it will make sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j}), ~j=1, \ldots, 31,$ where $n_{j}$ can also be interpreted as an exposure (not necessarily an interger).
 This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.
@@
 The code below shows a way to make inputs using the first 10 players.
+One covariate is an indicator variable which is 1 if a player was in the National league and 0 if American league.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
-The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
+The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown parameter $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
 This dataset is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.

### 2013-04-07 jss/article.tex
typo

@@
 
-where $\mu_{0j} =x_{j}'\beta,~j=1, \ldots, 8$, and a paramter with a zero sub-index represents it is a mean parameter of the prior (second-level) distribution.
-Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution.
+where $\mu_{0j} =x_{j}'\beta,~j=1, \ldots, 8$, and $x_{j}$ is $j$-th school's covariate vector ($m\times 1$).
+Also, $m$ is the number of regression coefficients, which is just 1 for an intercept term if there is no covariate.
+For reference, a paramter with a zero subscript represents a mean parameter of the prior (second-level) distribution.
+Also,  Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution.
 \begin{equation}

### 2013-04-07 jss/article.tex
typo

@@
 This dataset contains information about batting averages of 18 major league players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
-Also, it has one binary covariate indicating whether a player was in the National league (1) or the American league (0).
+Also, it has one binary covariate indicating whether a player was in the National league (1) or in the American league (0).
 The code below shows a way to make inputs using the first 10 players.
-One covariate is an indicator variable which is 1 if a player was in the National league and 0 if American league.
 \begin{CodeChunk}
@@
 \section[Multi-level Structure]{Multi-level Structure}
-Hierarchical model is a very powerful tool to (justification of hierarchical model for hierarchical data??)
-\\
-
+Multi-level model is a very powerful tool for explaining the hierarchical sturucture in data, for example, with student-level, school-level, and district-level information.
 \code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy is a distribution of observed data and second-level is a conjugate prior distribution on the first-level parameter.
@@
 
-where $\mu_{0j} =x_{j}'\beta,~j=1, \ldots, 8$, and $x_{j}$ is $j$-th school's covariate vector ($m\times 1$).
-Also, $m$ is the number of regression coefficients, which is just 1 for an intercept term if there is no covariate.
-For reference, a paramter with a zero subscript represents a mean parameter of the prior (second-level) distribution.
+where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($1\times m$), and $m$ is the number of regression coefficients which is just 1 for an intercept term if there is no covariate.
+For reference, a paramter with a zero subscript, $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution.
 Also,  Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution.
@@
 \end{equation}
-where $B_{j}\equiv\frac{\sigma^{2}_{j}}{\sigma^{2}_{j} + A},~j=1, \ldots, 8$ is called a shrinkages and we will explain it in the following section.
+where $B_{j}\equiv\frac{\sigma^{2}_{j}}{\sigma^{2}_{j} + A},~j=1, \ldots, 8$, is called a shrinkages.
 
@@
 \subsection[Shrinkage Estimation]{Shrinkage Estimation}
-Estimating shrinkage is a key part of our work because as we can see posterior mean is a linear function of shrinkage and posterior variance is also a linear (Gaussian), quadratic (Poisson), or cubic (Binomial) function of shrinkage.
-Once we estimate it, we can approximate the posterior moments given only data, for example, $E(\mu_{j}\vert \textbf{y})$ for Gaussian model.
+Estimating shrinkage is a key part of our work because as we can see the posterior means in (3), (6), and (9) are a linear function of shrinkage and the posterior variances are also a linear (Gaussian), quadratic (Poisson), or cubic (Binomial) function of shrinkage.
+Once we estimate it, we can approximate the posterior moments given only data by Adam's law, for example, $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ for Gaussian model and by Eve's law, for instance, $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$
 \subsection[ADM]{Adjustment for Density Maximization}
@@
 
-Here Adjustment for Density Maximization (Morris and Tang, 2011), called ADM, comes.
+Here the adjustment for density maximization (Morris and Tang, 2011), called ADM, comes.
 It assumes the Beta distribution for shrinkage, which the authors believe is a much better approximation for it, and estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$.
@@
 The reason we said `reasonablely approximates' is that it is hard to find a closed form of posterior distribution given only data unless it is a Gaussian model.
-So, we assumed $(p_{j}\vert \textrm{data})$ has also Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textrm{data})$ and $Var(p_{j}\vert \textrm{data})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.
+So, we assumed $(p_{j}\vert \textrm{data})$ had also Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textrm{data})$ and $Var(p_{j}\vert \textrm{data})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.
 
@@
 Based on the generated pseudo-datasets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th interval estimate from $i$-th pseudo-dataset includes $p_{ij}$ and 0 otherwise.
-One way to estimate the coverage probability is to take average over those indicator variables.
+One way to estimate the coverage probability is taking average over these indicator variables.
 We call it an unbiased coverage probability estimate.

### 2013-04-10 jss/article.tex
one more correction

@@
 
-\subsection{Normal: 8 Schools' Data}
+\subsection{Normal: 8 School Data}
 Education Testing Service conducted randomized experiments in eight separate schools and obtained this dataset.
@@
 
-Considering the type of data, it will make sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j}), ~j=1, \ldots, 31,$ where $n_{j}$ can also be interpreted as an exposure (not necessarily an interger).
+Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j}), ~j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger).
 This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.
@@
 The code below shows a way to make inputs using the first 10 players.
+If we have more than one covariate, for example, \code{x1} and \code{x2}, then `\code{R> x <- cbind(x1, x2)}' will be the right input of the \code{gbp} function.
 \begin{CodeChunk}
@@
 \section[Multi-level Structure]{Multi-level Structure}
-Multi-level model is a very powerful tool for explaining the hierarchical sturucture in data, for example, with student-level, school-level, and district-level information.
-\code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy is a distribution of observed data and second-level is a conjugate prior distribution on the first-level parameter.
+Our multi-level models, also called conditionally independent hierarchical models (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical sturucture in data.
+For example, we can think about the nation-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the league-level hierarchy for 18 baseball players.
+\code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter.
 Users can determine one of three types of multi-level models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets.
@@
 \code{gbp} is also able to build a Poisson-Gamma multi-level model on the 31 hospital data.
-Note that a constant multiplied to the notation representing Gamma distribution is a scale and a square bracket below indicates [mean, variance] of distribution.
+Note that a constant multiplied to the notation representing Gamma distribution below is a scale and a square bracket below indicates [mean, variance] of distribution.
 \begin{equation}
@@
 
-Once we are sure that the hierarchical modeling can add a huge value on our research, the next natural quetsion will be about the validity of interval estimates.
+Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates.
 ``Does the confidence interval obtained via this Bayesian model-fitting process achieve pre-specified 100($1-\alpha$)\% confidence level for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point.
@@
 Then, we can also generate $\{\textbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-dataset and $j$ does $j$-th player.
-Next, \code{coverage} fits the Binomial hierarchical model 500 times to obtain 500*18 interval estimates.
-Taking the first player as an example, we have 500 pairs of ($z_{i1}$, $p_{i1}$), $j=1,\ldots, 500$ and 500 interval estimates.
+Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\textbf{z}^{(i)}_{(18\times1)}, \textbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500*18 interval estimates.
+Taking the first player as an example, we have 500 pairs of ($z_{i1}$, $p_{i1}$), $j=1,\ldots, 500$, and 500 interval estimates.
 \begin{figure}[h]
@@
 This expectation is the same as P$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where $\hat{p}_{ij, low}$ and $\hat{p}_{ij, upp}$ are interval estimates (numeric values).
-We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ is the Beta distribution in (9).
-For instance, the first player's Rao-Blackwellized coverage probability can be estimated by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
+We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ in (9).
+Then, we can estimate the first player's coverage probability by Rao-Blackwellized coverage probability, for instance, $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
 \section[Example]{Example}

### 2013-04-12 Rgbp/R/coverage.R
removing min coverage

@@ -322,11 +322,9 @@ coverage <- function(gbp.object, A.or.r, reg.coef, covariates, mean.PriorDist, n
   # average coverage probability
   result <- round(rowMeans(coverageRB, na.rm = TRUE), 3)
   avr.cov <- round(mean(result), 3)
-  min.cov <- round(min(result), 3)
 
   result2 <- round(rowMeans(coverageU, na.rm = TRUE), 3)
   avr.cov2 <- round(mean(result2), 3)
-  min.cov2 <- round(min(result2), 3)
 
   # plotting coverage graph
   par(xaxs = "r", yaxs = "r", mai = c(1, 0.6, 1, 0.3))
@@ -341,29 +339,25 @@ coverage <- function(gbp.object, A.or.r, reg.coef, covariates, mean.PriorDist, n
                              "Blue Dotted Line: (Unbiased)",
                              paste("A =", round(A, 2)), 
                              paste("beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
-                             paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")"), 
-                             paste("MinCoverage =", min.cov, "(", min.cov2, ")")))
+                             paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     } else {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
                              "Blue Dotted Line: (Unbiased)",
                              paste("r =", round(r, 2)), 
                              paste("beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
-                             paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")"),
-                             paste("MinCoverage =", min.cov, "(", min.cov2, ")")))
+                             paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     }
   } else {  # if prior mean is assigned
     if (gbp.object$model == "gr") {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
                              "Blue Dotted Line: (Unbiased)",
                              paste("A =", round(A, 2)), 
-                             paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")"), 
-                             paste("MinCoverage =", min.cov, "(", min.cov2, ")")))
+                             paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     } else {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
[…]

### 2013-04-12 jss/article.tex
reference
baseball pic

@@
 
-Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j}), ~j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger).
+Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger).
 This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.
@@
 This dataset contains information about batting averages of 18 major league players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
-Also, it has one binary covariate indicating whether a player was in the National league (1) or in the American league (0).
-The code below shows a way to make inputs using the first 10 players.
+Also, it has two covariates, League and Position, showing in which league and in which position each player was.
+In this paper, we will use Position for a tutorial purpose.
+For convenience, we transform this variable into a binary indicator, which is 1 if a player was a outfielder and 0 otherwise.
+The code below shows a way to make inputs.
 If we have more than one covariate, for example, \code{x1} and \code{x2}, then `\code{R> x <- cbind(x1, x2)}' will be the right input of the \code{gbp} function.
@@
 \begin{CodeInput}
-R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11)
-R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
-R> x <- c( 1,  0,  0,  0,  0,  0,  1,  0,  1,  1) 
+R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
+R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
+R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
 \end{CodeInput}
@@
 \\
+
 Efron, B. and Morris, C. (1975). ``Data Analysis Using Stein's Estimator and its Generalizations.'' \emph{Journal of the American Statistical Association}. \textbf{70}. 311-319.
 \\
+
+Kass, R. and Steffey, D. (1989). ``Approximate Bayesian Inference in Conditionally Independent Hierarchical Models (Parametric
+Empirical Bayes Models).'' \emph{Journal of the American Statistical Association}. \textbf{84}. 717-726.
+\\
+
 Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
 \\
+
 Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
 \\
+
 Rubin, D. B. (1981). ``Estimation in parallel randomized

### 2013-04-12 jss/article.tex
introduction change

@@
 Our multi-level models, also called conditionally independent hierarchical models (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical sturucture in data.
-For example, we can think about the nation-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the league-level hierarchy for 18 baseball players.
+For example, we can think about a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players.
 \code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter.

### 2013-04-12 jss/article.tex
picture

@@
 This dataset contains information about batting averages of 18 major league players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
-Also, it has two covariates, League and Position, showing in which league and in which position each player was.
+Also, it has two covariates, League and Position, showing in which league and in which position each player was playing.
 In this paper, we will use Position for a tutorial purpose.
@@
 \section[Multi-level Structure]{Multi-level Structure}
-Our multi-level models, also called conditionally independent hierarchical models (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical sturucture in data.
+Our multi-level model, also called a conditionally independent hierarchical model (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical sturucture in data.
 For example, we can think about a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players.
@@
 
-where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($1\times m$), and $m$ is the number of regression coefficients which is just 1 for an intercept term if there is no covariate.
+where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients.
+Note that if there is no covariate then $m$ is 1 for an intercept term, making $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$.
 For reference, a paramter with a zero subscript, $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution.
@@
 Note that a constant multiplied to the notation representing Gamma distribution below is a scale and a square bracket below indicates [mean, variance] of distribution.
+And for notational consistency, let's define $y_{j}\equiv \frac{z_{j}}{n_{j}}$ for all $j$.
 \begin{equation}
@@
 \begin{equation}
-\lambda_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0j} + z_{j})\sim\textrm{Gamma}[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}}],
+\lambda_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0j} + n_{j}y_{j})\sim\textrm{Gamma}[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}}],
 \end{equation}
 
-where $\lambda^{\ast}_{j} \equiv (1-B_{j})(\frac{z_{j}}{n_{j}}) + B_{j}\lambda_{0j},~\textrm{and}~ B_{j}\equiv \frac{r}{r+n_{j}},~ j=1, \ldots, 31$.
+where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0j}$,  $B_{j}\equiv \frac{r}{r+n_{j}}$, and $y_{j}\equiv \frac{z_{j}}{n_{j}}$, $j=1, \ldots, 31$.
 
@@
 \begin{equation}
-z_{j} \vert p_{0j}\stackrel{ind}{\sim}\textrm{Binomial}(n_{j}, ~p_{j}),
+z_{j} \vert p_{j}\stackrel{ind}{\sim}\textrm{Binomial}(n_{j}, ~p_{j}),
 \end{equation}
@@
 \begin{equation}
-p_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+z_{j},~r(1-p_{0j})+n_{j}-z_{j})\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
+p_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}y_{j},~r(1-p_{0j})+n_{j}(1-y_{j})\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
 \end{equation}
-where $p^{\ast}_{j}\equiv(1-B_{j})(\frac{z_{j}}{n_{j}})+B_{j}p_{0j},~ \textrm{and}~ B_{j}\equiv\frac{r}{r+n_{j}}$, $j=1,\ldots,18$.
+where $p^{\ast}_{j}\equiv(1-B_{j})y_{j}+B_{j}p_{0j}$, $B_{j}\equiv\frac{r}{r+n_{j}}$, and $y_{j}\equiv\frac{z_{j}}{n_{j}}$, $j=1,\ldots,18$.
 
@@
 \begin{equation}
-\beta \sim \textrm{flat on}~ \mathbf{R}^{m},~~A ~(\textrm{or}~ \frac{1}{r})\sim \textrm{Unif}(0, \infty),
+\beta \sim \textrm{Uniform on}~ \mathbf{R}^{m},~~A ~(\textrm{or}~ \frac{1}{r})\sim \textrm{Uniform}(0, \infty),
 \end{equation}
@@
 where $m$ is the number of regression coefficients.
-For $\beta$, it is reasonable choice to take flat (non-informative) distribution because the information about location gets informative as number of groups increases.
+For $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets informative as number of groups increases.
 Another flat prior on the hyper-prameter $A$ (or $1/r$) that we suggest here will guarantee a posterior propriety under the moderate conditions and will give users a good repeated sampling property.
@@
 
-In this case, one way is to obtain an MLE of the variance component with its asymptotic Normal distribution and to use Delta method for asymptotic Normal distribution of shrinkage.
-But is the Normal approximation a good approximation for shrinkage that takes on values between 0 and 1?
+In this case, one way is to obtain an MLE of the variance component with its asymptotic Normal distribution and then to use Delta method for asymptotic Normal distribution of shrinkage.
+But is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1?
 \\
@@
 \section[Reference]{Reference}
+1.
 Christiansen, C.
@@
 
-Efron, B. and Morris, C. (1975). ``Data Analysis Using Stein's Estimator and its Generalizations.'' \emph{Journal of the American Statistical Association}. \textbf{70}. 311-319.
+2. Efron, B. and Morris, C. (1975). ``Data Analysis Using Stein's Estimator and its Generalizations.'' \emph{Journal of the American Statistical Association}. \textbf{70}. 311-319.
 \\
 
-Kass, R. and Steffey, D. (1989). ``Approximate Bayesian Inference in Conditionally Independent Hierarchical Models (Parametric
+3. Kass, R. and Steffey, D. (1989). ``Approximate Bayesian Inference in Conditionally Independent Hierarchical Models (Parametric
 Empirical Bayes Models).'' \emph{Journal of the American Statistical Association}. \textbf{84}. 717-726.
@@
 
-Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
+4. Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
 \\
 
-Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
+5. Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
 \\
 
-Rubin, D. B. (1981). ``Estimation in parallel randomized
+6. Rubin, D. B. (1981). ``Estimation in parallel randomized
   experiments.'' \emph{Journal of Educational Statistics}. \textbf{6}. 377-401.

### 2013-04-12 jss/article.tex
what changes?

@@
 Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\textbf{z}^{(i)}_{(18\times1)}, \textbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500*18 interval estimates.
-Taking the first player as an example, we have 500 pairs of ($z_{i1}$, $p_{i1}$), $j=1,\ldots, 500$, and 500 interval estimates.
+Taking the first player as an example, we have 500 pairs of ($z_{i1}$, $p_{i1}$), $i=1,\ldots, 500$, and 500 interval estimates.
 \begin{figure}[h]
@@
 \subsection{Unbiased Coverage Probability}
-Based on the generated pseudo-datasets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th interval estimate from $i$-th pseudo-dataset includes $p_{ij}$ and 0 otherwise.
+Based on the generated pseudo-datasets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th player's interval estimate from $i$-th pseudo-dataset includes $p_{ij}$ and 0 otherwise.
 One way to estimate the coverage probability is taking average over these indicator variables.
@@
 For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first player.
+
 \subsection{Rao-Blackwellized Coverage Probability}
-Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$) as the Rao-Blackwellized coverage probability, where $r$ and $\beta$ were fixed at first (see 5.1).
-This expectation is the same as P$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where $\hat{p}_{ij, low}$ and $\hat{p}_{ij, upp}$ are interval estimates (numeric values).
+Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were fixed at first (see 5.1) and $z_{ij}$ is a sufficient statistic.
+This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates (numeric values) on the $i$-th dataset.
 We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ in (9).
-Then, we can estimate the first player's coverage probability by Rao-Blackwellized coverage probability, for instance, $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
+Then, we can estimate the first player's coverage probability, for instance, by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
 \section[Example]{Example}

### 2013-04-12 Rgbp.Rcheck/Rgbp-Ex.R
what?

@@ -1,0 +1,1063 @@
+pkgname <- "Rgbp"
+source(file.path(R.home("share"), "R", "examples-header.R"))
+options(warn = 1)
+library('Rgbp')
+
+base::assign(".oldSearch", base::search(), pos = 'CheckExEnv')
+cleanEx()
+nameEx("Rgbp-package")
+### * Rgbp-package
+
+flush(stderr()); flush(stdout())
+
+### Name: Rgbp
+### Title: Bayesian Hierarchical Modeling and Frequentist Method Check
+### Aliases: Rgbp-package Rgbp
+### Keywords: package
+
+### ** Examples
+
+
+
+  # Loading datasets
+  data(schools)
+  y <- schools$y
+  se <- schools$se
+
+  # Arbitrary covariate for schools data
+  x2 <- rep(c(-1, 0, 1, 2), 2)
+  
+  # baseball data where z is Hits and n is AtBats
+  z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
+  n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
+
+  # One covariate: 1 if a player is in the National league
+  x1 <- c(1, 0, 0, 0, 0, 0, 1, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, 1)
+
+  ################################################################
+  # Gaussian Regression Interactive Multilevel Modeling (GRIMM) #
+  ################################################################
+
+    ####################################################################################
+    # If we do not have any covariate and do not know a mean of the prior distribution #
+    ####################################################################################
+
+    g <- gbp(y, se)
+    g
+    print(g, sort = FALSE)
+    summary(g)
+    plot(g)
+    plot(g, sort = FALSE)
+
+    ### when we want to simulate pseudo datasets considering the estimated values 
+    ### as true ones.
+    gcv <- coverage(g, nsim = 10)  
+
+    ### gcv$coverageRB, gcv$coverage10, gcv$average.coverageRB, gcv$average.coverage10,
+    ### gcv$minimum.coverageRB, gcv$minimum.coverage10, gcv$raw.resultRB, gcv$raw.result10.
+
+    ### when we want to simulate pseudo datasets based on different values of A and 
+    ### of a regression coefficient (intercept), 
+    ### not using estimated values as true ones.
[…]

### 2013-04-12 Rgbp/R/gbp.R
error in gbp plot

@@ -275,6 +275,7 @@ plot.gbp <- function(x, sort = TRUE, ...) {
   po.sd <- x$post.sd
   po.low <- x$post.intv.low
   po.upp <- x$post.intv.upp
+  xlabel <- "Indices (Groups) by the order of data input"
 
   if (sort == TRUE) {
     temp.data <- as.data.frame(cbind(y, se, pr.m, po.m, po.sd, po.low, po.upp))
@@ -297,7 +298,6 @@ plot.gbp <- function(x, sort = TRUE, ...) {
   index <- 1 : length(se)
   ylim.low <- ifelse(min(po.low, y) >= 0, 0.8 * min(po.low, y), 1.2 * min(po.low, y))
   ylim.upp <- ifelse(max(po.upp, y) >= 0, 1.2 * max(po.upp, y), 0.8 * max(po.upp, y))
-  xlabel <- "Indices (Groups) by the order of data input"
 
   par(mfrow = c(1, 2), xaxs = "r", yaxs = "r", mai = c(1, 0.6, 1, 0.3), las = 1, ps = 13,oma=c(0,5,0,0))
   

### 2013-04-12 jss/article.tex
error in gbp plot
pictures

@@
 \section[Example]{Example}
-\subsection[Known Prior Mean]{Known Prior Mean}
-Using 10 hospital data with PR
-\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
-Using 8 school data with GR
-\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
-Using 18 baseball data with BR
+\subsection[Known Second-level Mean]{Known Second-level Mean}
+What are the true rates, $\lambda_{j},~j=1,\ldots, 31$, governing the death-rates, $z_{j} / n_{j}$, of those 31 hospitals?
+
+We will use 31 hospital dataset that we introduced in 2.2.
+First of all, can we imagine a bigger population-level hierarchy?
+In other words, can we consider the true parameters as sampled from a bigger population distribution governing those parameters?
+In some cases, we might have information about the mean of the second-level.
+If we think about the 31 hospital dataset,
+As we said, we have data about the medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 (Morris and Lysy, 2012).
+It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$).
+The below code is an example of input based on the last ten hospital data.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.3]{hospital1.png}
+\caption{Shrinkage and interval plots of 31 hospitals in NY}
+\end{center}
+\end{figure}
+
+\subsection[Unknown Second-level Mean and No Covariate]{Unknown Second-level Mean and No Covariate}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.3]{school1.png}
+\caption{Shrinkage and interval plots of 8 schools}
+\end{center}
+\end{figure}
+
+\subsection[Unknown Second-level Mean and One Covariate]{Unknown Prior Mean and One Covariate}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.3]{baseball1.png}
+\caption{Shrinkage and interval plots of 18 baseball players}
+\end{center}
+\end{figure}
 

### 2013-04-12 Rgbp/R/gbp.R

@@ -351,10 +351,11 @@ plot.gbp <- function(x, sort = TRUE, ...) {
   par(xpd=NA)
   plot(1, type="n", axes=F, xlab="", ylab="")
   legend("topleft", pch = c(19, 1, NA, NA, NA,0), col = c(2, 1, 4,"darkviolet", "darkgreen",1), 
-         lwd = c(NA, NA, 2, 2, 2), c("posterior mean", "sample mean", "prior mean", se.or.n, "posterior sd", "crossover"),
+         lwd = c(NA, NA, 2, 2, 2), 
+         c("posterior mean", "sample mean", "prior mean", se.or.n, "posterior sd", "crossover"),
          seg.len = 0.5, bty = "n", inset = c(-0.175, 0))
  # legend("topleft", pch = c(19, 1, NA,NA), col = c(2, 1, 4,"darkviolet"), lwd = c(NA, NA, 2,2), c("posterior mean", "sample mean", "prior mean","se"), seg.len = 0.5, bty = "n")
-  par(xpd=FALSE)
+  par(xpd = FALSE)
 
 
 }

### 2013-04-13 jss/article.tex
removing sd.shrinkage

--- 2013-04-12 jss/article.tex
@@
 \section[Example]{Example}
-\subsection[Known Prior Mean]{Known Prior Mean}
-Using 10 hospital data with PR
-\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
-Using 8 school data with GR
-\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
-Using 18 baseball data with BR
+\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
+If you, living in the New York state (NY), were suffering from severe coronary heart disease (hopefully not), and were supposed to receive the coronary artery bypass graft (CABG) surgery, your concern might be each hospital's abililty to handle this surgery.
+\\
+
+For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths within a month of CABG surgeries and total number of patients receiving CABG surgeries in each hospital.
+In addition, suppose you could obtaion the state-level death rate of this surgery while you were looking for such information, which was 0.02.
+From this point, there are a lot of ways to explore those data to have an idea about each hospital's ability.
+\\
+
+One way we suggest here is a hierarchical modeling assuming that there is a bigger population-level hierarchy.
+In this case, for example, we presume that there is a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY.
+Then, we can consider the true death rates of those 31 hospitals were sampled from this state-level population distribution whose mean is 0.02.
+The validity of such an assumption can be checked (Christiansen and Morris, 1996).
+\\
+
+Once we are sure that the assumption of an additional hierarchy is reasonable, we start a model-fitting process.
+Since the true death rate after CABG surgery might be small and caseloads ($n_{j}$) look relatively much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data.
+Next, \code{gbp} will help us fit a multi-level model with the Gamma conjugate distribution for $\lambda_{j}$ on the second-level hierarchy whose mean is 0.02 ($\lambda_{0}=0.02$) as described in the section 3.2.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
+R> p
+\end{CodeInput}
+\begin{CodeOutput}
+Summary for whole observations:
+
+           sample.mean        n prior.mean shrinkage sd.shrinkage post.intv.low post.mean post.intv.upp post.sd
+1                0.045   67.000       0.02     0.834        0.056         0.011     0.024         0.042   0.008
+2                0.029   68.000       0.02     0.832        0.057         0.010     0.022         0.038   0.007
+3                0.024  210.000       0.02     0.616        0.095         0.011     0.021         0.035   0.006
+4                0.043  256.000       0.02     0.568        0.099         0.017     0.030         0.046   0.008
+5                0.033  269.000       0.02     0.556        0.099         0.015     0.026         0.041   0.007
+6                0.044  274.000       0.02     0.551        0.100         0.018     0.031         0.047   0.008
+7                0.043  278.000       0.02     0.548        0.100         0.018     0.030         0.047   0.007
+8                0.014  295.000       0.02     0.533        0.100         0.008     0.017         0.029   0.005
+9                0.029  347.000       0.02     0.492        0.101         0.014     0.024         0.038   0.006
+10               0.037  349.000       0.02     0.491        0.101         0.017     0.029         0.043   0.007
+11               0.039  358.000       0.02     0.484        0.101         0.018     0.030         0.045   0.007
+12               0.018  396.000       0.02     0.459        0.100         0.010     0.019         0.030   0.005
+13               0.028  431.000       0.02     0.438        0.099         0.015     0.024         0.037   0.006
+14               0.025  441.000       0.02     0.433        0.099         0.013     0.023         0.035   0.005
+15               0.027  477.000       0.02     0.414        0.098         0.015     0.024         0.036   0.006
+16               0.045  484.000       0.02     0.410        0.098         0.023     0.035         0.050   0.007
+17               0.030  494.000       0.02     0.405        0.097         0.016     0.026         0.039   0.006
+18               0.022  501.000       0.02     0.402        0.097         0.012     0.021         0.032   0.005
+19               0.028  505.000       0.02     0.400        0.097         0.015     0.025         0.036   0.005
+20               0.020  540.000       0.02     0.384        0.095         0.012     0.020         0.031   0.005
+21               0.028  563.000       0.02     0.374        0.094         0.016     0.025         0.037   0.005
+22               0.024  593.000       0.02     0.362        0.093         0.014     0.022         0.033   0.005
+23               0.015  602.000       0.02     0.358        0.093         0.010     0.017         0.026   0.004
+24               0.024  629.000       0.02     0.348        0.092         0.014     0.023         0.033   0.005
+25               0.020  636.000       0.02     0.346        0.091         0.012     0.020         0.030   0.005
+26               0.048  729.000       0.02     0.316        0.087         0.027     0.039         0.053   0.007
+27               0.031  849.000       0.02     0.284        0.082         0.019     0.028         0.038   0.005
+28               0.027  914.000       0.02     0.269        0.080         0.017     0.025         0.035   0.005
+29               0.021  940.000       0.02     0.264        0.079         0.014     0.021         0.030   0.004
+30               0.029 1193.000       0.02     0.220        0.070         0.020     0.027         0.036   0.004
+31               0.020 1340.000       0.02     0.201        0.065         0.014     0.020         0.027   0.003
+== Mean ==       0.029  517.032       0.02     0.438        0.091         0.015     0.025         0.037   0.006
+\end{CodeOutput}
+\end{CodeChunk}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.3]{hospital1.png}
+\caption{Shrinkage and interval plots of 31 hospitals in NY}
+\end{center}
+\end{figure}
+
+\subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.3]{school1.png}
+\caption{Shrinkage and interval plots of 8 schools}
+\end{center}
+\end{figure}
+
+\subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Prior Mean and One Covariate}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.3]{baseball1.png}
+\caption{Shrinkage and interval plots of 18 baseball players}
+\end{center}
+\end{figure}
 

### 2013-04-13 Rgbp/R/gbp.R

@@ -19,14 +19,12 @@ print.gbp <- function(x, sort = TRUE, ...) {
     
     if (x$model == "gr") {
       temp <- data.frame(sample.mean = x$sample.mean, se = x$se, x = cova, 
-                         prior.mean = x$prior.mean.hat,
-                         shrinkage = x$shrinkage, sd.shrinkage = x$sd.shrinkage, 
+                         prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
       temp <- data.frame(sample.mean = x$sample.mean, n = x$se, x = cova, 
-                         prior.mean = x$prior.mean.hat,
-                         shrinkage = x$shrinkage, sd.shrinkage = x$sd.shrinkage, 
+                         prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     }
@@ -35,13 +33,13 @@ print.gbp <- function(x, sort = TRUE, ...) {
   # if there are neither prior.mean and X assigned
 
     if (x$model == "gr") {
-      temp <- data.frame(sample.mean = x$sample.mean, se = x$se, prior.mean = x$prior.mean.hat,
-                         shrinkage = x$shrinkage, sd.shrinkage = x$sd.shrinkage, 
+      temp <- data.frame(sample.mean = x$sample.mean, se = x$se, 
+                         prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
-      temp <- data.frame(sample.mean = x$sample.mean, n = x$se, prior.mean = x$prior.mean.hat,
-                         shrinkage = x$shrinkage, sd.shrinkage = x$sd.shrinkage, 
+      temp <- data.frame(sample.mean = x$sample.mean, n = x$se, 
+                         prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
[…]

### 2013-04-13 Rgbp/R/gbp.R
changing name post.intv - > intv

@@ -20,13 +20,13 @@ print.gbp <- function(x, sort = TRUE, ...) {
     if (x$model == "gr") {
       temp <- data.frame(sample.mean = x$sample.mean, se = x$se, x = cova, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
-                         post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
-                         post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
+                         intv.low = x$post.intv.low, post.mean = x$post.mean, 
+                         intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
       temp <- data.frame(sample.mean = x$sample.mean, n = x$se, x = cova, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
-                         post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
-                         post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
+                         intv.low = x$post.intv.low, post.mean = x$post.mean, 
+                         intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     }
 
   } else if (any(is.na(x$prior.mean)) & identical(x$X, NA)) { 
@@ -35,13 +35,13 @@ print.gbp <- function(x, sort = TRUE, ...) {
     if (x$model == "gr") {
       temp <- data.frame(sample.mean = x$sample.mean, se = x$se, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
-                         post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
-                         post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
+                         intv.low = x$post.intv.low, post.mean = x$post.mean, 
+                         intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
       temp <- data.frame(sample.mean = x$sample.mean, n = x$se, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
-                         post.intv.low = x$post.intv.low, post.mean = x$post.mean, 
-                         post.intv.upp = x$post.intv.upp, post.sd = x$post.sd)
+                         intv.low = x$post.intv.low, post.mean = x$post.mean, 
+                         intv.upp = x$post.intv.upp, post.sd = x$post.sd)
[…]

### 2013-04-13 jss/article.tex
changing name sample.mean - > obs.mean

@@
 
-           sample.mean        n prior.mean shrinkage sd.shrinkage post.intv.low post.mean post.intv.upp post.sd
-1                0.045   67.000       0.02     0.834        0.056         0.011     0.024         0.042   0.008
-2                0.029   68.000       0.02     0.832        0.057         0.010     0.022         0.038   0.007
-3                0.024  210.000       0.02     0.616        0.095         0.011     0.021         0.035   0.006
-4                0.043  256.000       0.02     0.568        0.099         0.017     0.030         0.046   0.008
-5                0.033  269.000       0.02     0.556        0.099         0.015     0.026         0.041   0.007
-6                0.044  274.000       0.02     0.551        0.100         0.018     0.031         0.047   0.008
-7                0.043  278.000       0.02     0.548        0.100         0.018     0.030         0.047   0.007
-8                0.014  295.000       0.02     0.533        0.100         0.008     0.017         0.029   0.005
-9                0.029  347.000       0.02     0.492        0.101         0.014     0.024         0.038   0.006
-10               0.037  349.000       0.02     0.491        0.101         0.017     0.029         0.043   0.007
-11               0.039  358.000       0.02     0.484        0.101         0.018     0.030         0.045   0.007
-12               0.018  396.000       0.02     0.459        0.100         0.010     0.019         0.030   0.005
-13               0.028  431.000       0.02     0.438        0.099         0.015     0.024         0.037   0.006
-14               0.025  441.000       0.02     0.433        0.099         0.013     0.023         0.035   0.005
-15               0.027  477.000       0.02     0.414        0.098         0.015     0.024         0.036   0.006
-16               0.045  484.000       0.02     0.410        0.098         0.023     0.035         0.050   0.007
-17               0.030  494.000       0.02     0.405        0.097         0.016     0.026         0.039   0.006
-18               0.022  501.000       0.02     0.402        0.097         0.012     0.021         0.032   0.005
-19               0.028  505.000       0.02     0.400        0.097         0.015     0.025         0.036   0.005
-20               0.020  540.000       0.02     0.384        0.095         0.012     0.020         0.031   0.005
-21               0.028  563.000       0.02     0.374        0.094         0.016     0.025         0.037   0.005
-22               0.024  593.000       0.02     0.362        0.093         0.014     0.022         0.033   0.005
-23               0.015  602.000       0.02     0.358        0.093         0.010     0.017         0.026   0.004
-24               0.024  629.000       0.02     0.348        0.092         0.014     0.023         0.033   0.005
-25               0.020  636.000       0.02     0.346        0.091         0.012     0.020         0.030   0.005
-26               0.048  729.000       0.02     0.316        0.087         0.027     0.039         0.053   0.007
-27               0.031  849.000       0.02     0.284        0.082         0.019     0.028         0.038   0.005
-28               0.027  914.000       0.02     0.269        0.080         0.017     0.025         0.035   0.005
-29               0.021  940.000       0.02     0.264        0.079         0.014     0.021         0.030   0.004
-30               0.029 1193.000       0.02     0.220        0.070         0.020     0.027         0.036   0.004
-31               0.020 1340.000       0.02     0.201        0.065         0.014     0.020         0.027   0.003
-== Mean ==       0.029  517.032       0.02     0.438        0.091         0.015     0.025         0.037   0.006
+           sample.mean        n prior.mean shrinkage intv.low post.mean intv.upp post.sd
+1                0.045   67.000       0.02     0.834    0.011     0.024    0.042   0.008
+2                0.029   68.000       0.02     0.832    0.010     0.022    0.038   0.007
+3                0.024  210.000       0.02     0.616    0.011     0.021    0.035   0.006
+4                0.043  256.000       0.02     0.568    0.017     0.030    0.046   0.008
+5                0.033  269.000       0.02     0.556    0.015     0.026    0.041   0.007
+6                0.044  274.000       0.02     0.551    0.018     0.031    0.047   0.008
+7                0.043  278.000       0.02     0.548    0.018     0.030    0.047   0.007
+8                0.014  295.000       0.02     0.533    0.008     0.017    0.029   0.005
+9                0.029  347.000       0.02     0.492    0.014     0.024    0.038   0.006
+10               0.037  349.000       0.02     0.491    0.017     0.029    0.043   0.007
+11               0.039  358.000       0.02     0.484    0.018     0.030    0.045   0.007
+12               0.018  396.000       0.02     0.459    0.010     0.019    0.030   0.005
+13               0.028  431.000       0.02     0.438    0.015     0.024    0.037   0.006
+14               0.025  441.000       0.02     0.433    0.013     0.023    0.035   0.005
+15               0.027  477.000       0.02     0.414    0.015     0.024    0.036   0.006
+16               0.045  484.000       0.02     0.410    0.023     0.035    0.050   0.007
+17               0.030  494.000       0.02     0.405    0.016     0.026    0.039   0.006
+18               0.022  501.000       0.02     0.402    0.012     0.021    0.032   0.005
+19               0.028  505.000       0.02     0.400    0.015     0.025    0.036   0.005
+20               0.020  540.000       0.02     0.384    0.012     0.020    0.031   0.005
+21               0.028  563.000       0.02     0.374    0.016     0.025    0.037   0.005
+22               0.024  593.000       0.02     0.362    0.014     0.022    0.033   0.005
+23               0.015  602.000       0.02     0.358    0.010     0.017    0.026   0.004
+24               0.024  629.000       0.02     0.348    0.014     0.023    0.033   0.005
+25               0.020  636.000       0.02     0.346    0.012     0.020    0.030   0.005
+26               0.048  729.000       0.02     0.316    0.027     0.039    0.053   0.007
+27               0.031  849.000       0.02     0.284    0.019     0.028    0.038   0.005
+28               0.027  914.000       0.02     0.269    0.017     0.025    0.035   0.005
+29               0.021  940.000       0.02     0.264    0.014     0.021    0.030   0.004
+30               0.029 1193.000       0.02     0.220    0.020     0.027    0.036   0.004
+31               0.020 1340.000       0.02     0.201    0.014     0.020    0.027   0.003
+== Mean ==       0.029  517.032       0.02     0.438    0.015     0.025    0.037   0.006
 \end{CodeOutput}

### 2013-04-13 Rgbp/R/gbp.R

@@ -18,12 +18,12 @@ print.gbp <- function(x, sort = TRUE, ...) {
 	colnames(cova) <- paste(1 : dim(cova)[2])
     
     if (x$model == "gr") {
-      temp <- data.frame(sample.mean = x$sample.mean, se = x$se, x = cova, 
+      temp <- data.frame(obs.mean = x$sample.mean, se = x$se, x = cova, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
-      temp <- data.frame(sample.mean = x$sample.mean, n = x$se, x = cova, 
+      temp <- data.frame(obs.mean = x$sample.mean, n = x$se, x = cova, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
@@ -33,12 +33,12 @@ print.gbp <- function(x, sort = TRUE, ...) {
   # if there are neither prior.mean and X assigned
 
     if (x$model == "gr") {
-      temp <- data.frame(sample.mean = x$sample.mean, se = x$se, 
+      temp <- data.frame(obs.mean = x$sample.mean, se = x$se, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
-      temp <- data.frame(sample.mean = x$sample.mean, n = x$se, 
+      temp <- data.frame(obs.mean = x$sample.mean, n = x$se, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
@@ -47,12 +47,12 @@ print.gbp <- function(x, sort = TRUE, ...) {
 
   } else if (!any(is.na(x$prior.mean))) {
     if (x$model == "gr") {
-      temp <- data.frame(sample.mean = x$sample.mean, se = x$se, 
+      temp <- data.frame(obs.mean = x$sample.mean, se = x$se, 
[…]

### 2013-04-13 jss/article.tex
n - > round(n)

@@
 
-           sample.mean        n prior.mean shrinkage intv.low post.mean intv.upp post.sd
+         obs.mean        n prior.mean shrinkage intv.low post.mean intv.upp post.sd
 1           0.045   67.000       0.02     0.834    0.011     0.024    0.042   0.008
@@
 31          0.020 1340.000       0.02     0.201    0.014     0.020    0.027   0.003
-== Mean ==       0.029  517.032       0.02     0.438    0.015     0.025    0.037   0.006
+colMeans    0.029  517.032       0.02     0.438    0.015     0.025    0.037   0.006
+\end{CodeOutput}
+\begin{CodeInput}
+R> summary(p)
+\end{CodeInput}
+\begin{CodeOutput}
+Main summary:
+
+                  obs.mean        n prior.mean shrinkage intv.low post.mean intv.upp post.sd
+Unit w/ min(n)       0.045   67.000       0.02     0.834    0.011     0.024    0.042   0.008
+Unit w/ median(n)    0.045  484.000       0.02     0.410    0.023     0.035    0.050   0.007
+Unit w/ max(n)       0.020 1340.000       0.02     0.201    0.014     0.020    0.027   0.003
+Overall Mean         0.029  517.032       0.02     0.438    0.015     0.025    0.037   0.006
+
+Second-level Variance Component Estimation Summary:
+alpha = log(A) for Gaussian and log(1/r) for Binomial and Poisson data:
+
+  post.mode.alpha post.sd.alpha
+1          -5.818         0.411
 \end{CodeOutput}

### 2013-04-13 Rgbp/R/gbp.R

@@ -23,7 +23,7 @@ print.gbp <- function(x, sort = TRUE, ...) {
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
-      temp <- data.frame(obs.mean = x$sample.mean, n = x$se, x = cova, 
+      temp <- data.frame(obs.mean = x$sample.mean, n = round(x$se), x = cova, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
@@ -38,7 +38,7 @@ print.gbp <- function(x, sort = TRUE, ...) {
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
-      temp <- data.frame(obs.mean = x$sample.mean, n = x$se, 
+      temp <- data.frame(obs.mean = x$sample.mean, n = round(x$se), 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
@@ -52,7 +52,7 @@ print.gbp <- function(x, sort = TRUE, ...) {
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
-      temp <- data.frame(obs.mean = x$sample.mean, n = x$se, 
+      temp <- data.frame(obs.mean = x$sample.mean, n = round(x$se), 
                          prior.mean = x$prior.mean, shrinkage = x$shrinkage, 
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
@@ -84,7 +84,7 @@ summary.gbp <- function(object, ...) {
                          intv.low = object$post.intv.low, post.mean = object$post.mean, 
                          intv.upp = object$post.intv.upp, post.sd = object$post.sd)
     } else {
-      temp <- data.frame(obs.mean = object$sample.mean, n = object$se, x = cova, 
+      temp <- data.frame(obs.mean = object$sample.mean, n = round(object$se), x = cova, 
[…]

### 2013-04-13 Rgbp/R/gbp.R
digit adjustment

@@ -23,7 +23,7 @@ print.gbp <- function(x, sort = TRUE, ...) {
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
-      temp <- data.frame(obs.mean = x$sample.mean, n = round(x$se), x = cova, 
+      temp <- data.frame(obs.mean = x$sample.mean, n = x$se, x = cova, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
@@ -38,7 +38,7 @@ print.gbp <- function(x, sort = TRUE, ...) {
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
-      temp <- data.frame(obs.mean = x$sample.mean, n = round(x$se), 
+      temp <- data.frame(obs.mean = x$sample.mean, n = x$se, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
@@ -52,7 +52,7 @@ print.gbp <- function(x, sort = TRUE, ...) {
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
     } else {
-      temp <- data.frame(obs.mean = x$sample.mean, n = round(x$se), 
+      temp <- data.frame(obs.mean = x$sample.mean, n = x$se, 
                          prior.mean = x$prior.mean, shrinkage = x$shrinkage, 
                          intv.low = x$post.intv.low, post.mean = x$post.mean, 
                          intv.upp = x$post.intv.upp, post.sd = x$post.sd)
@@ -84,7 +84,7 @@ summary.gbp <- function(object, ...) {
                          intv.low = object$post.intv.low, post.mean = object$post.mean, 
                          intv.upp = object$post.intv.upp, post.sd = object$post.sd)
     } else {
-      temp <- data.frame(obs.mean = object$sample.mean, n = round(object$se), x = cova, 
+      temp <- data.frame(obs.mean = object$sample.mean, n = object$se, x = cova, 
[…]

### 2013-04-13 Rgbp/R/gbp.R
tamp -> temp

@@ -202,10 +202,10 @@ summary.gbp <- function(object, ...) {
   temp.mean <- colMeans(temp)
   
   if (object$model == "gr") {
-    tamp.mean[2] <- round(tamp.mean[2], 1)
+    temp.mean[2] <- round(temp.mean[2], 1)
     summary.table[, 2] <- round(summary.table[, 2], 1)
   } else {
-    tamp.mean[2] <- round(tamp.mean[2])
+    temp.mean[2] <- round(temp.mean[2])
     summary.table[, 2] <- round(summary.table[, 2])
   }
 

### 2013-04-13 Rgbp/R/gbp.R
digit adjustment

@@ -65,10 +65,16 @@ print.gbp <- function(x, sort = TRUE, ...) {
 
   temp.mean <- colMeans(temp)
   temp <- data.frame(rbind(temp, temp.mean), row.names = c(rownames(temp), "colMeans"))
+  temp <- round(temp, 3)
+  if (x$model == "gr") {
+    temp[, 2] <- round(temp.mean[, 2], 1)
+  } else {
+    temp[, 2] <- round(temp.mean[, 2])
+  }
 
   cat("Summary for whole observations: \n")
   cat("\n")
-  print(round(temp, 3))
+  print(temp)
 }
 
 summary.gbp <- function(object, ...) {

### 2013-04-13 Rgbp/R/gbp.R
digit adjustment

@@ -67,9 +67,9 @@ print.gbp <- function(x, sort = TRUE, ...) {
   temp <- data.frame(rbind(temp, temp.mean), row.names = c(rownames(temp), "colMeans"))
   temp <- round(temp, 3)
   if (x$model == "gr") {
-    temp[, 2] <- round(temp.mean[, 2], 1)
+    temp[, 2] <- round(temp[, 2], 1)
   } else {
-    temp[, 2] <- round(temp.mean[, 2])
+    temp[, 2] <- round(temp[, 2])
   }
 
   cat("Summary for whole observations: \n")

### 2013-04-13 jss/article.tex
picture3

--- 2013-04-13 jss/article.tex
@@
 
-           sample.mean        n prior.mean shrinkage intv.low post.mean intv.upp post.sd
-1                0.045   67.000       0.02     0.834    0.011     0.024    0.042   0.008
-2                0.029   68.000       0.02     0.832    0.010     0.022    0.038   0.007
-3                0.024  210.000       0.02     0.616    0.011     0.021    0.035   0.006
-4                0.043  256.000       0.02     0.568    0.017     0.030    0.046   0.008
-5                0.033  269.000       0.02     0.556    0.015     0.026    0.041   0.007
-6                0.044  274.000       0.02     0.551    0.018     0.031    0.047   0.008
-7                0.043  278.000       0.02     0.548    0.018     0.030    0.047   0.007
-8                0.014  295.000       0.02     0.533    0.008     0.017    0.029   0.005
-9                0.029  347.000       0.02     0.492    0.014     0.024    0.038   0.006
-10               0.037  349.000       0.02     0.491    0.017     0.029    0.043   0.007
-11               0.039  358.000       0.02     0.484    0.018     0.030    0.045   0.007
-12               0.018  396.000       0.02     0.459    0.010     0.019    0.030   0.005
-13               0.028  431.000       0.02     0.438    0.015     0.024    0.037   0.006
-14               0.025  441.000       0.02     0.433    0.013     0.023    0.035   0.005
-15               0.027  477.000       0.02     0.414    0.015     0.024    0.036   0.006
-16               0.045  484.000       0.02     0.410    0.023     0.035    0.050   0.007
-17               0.030  494.000       0.02     0.405    0.016     0.026    0.039   0.006
-18               0.022  501.000       0.02     0.402    0.012     0.021    0.032   0.005
-19               0.028  505.000       0.02     0.400    0.015     0.025    0.036   0.005
-20               0.020  540.000       0.02     0.384    0.012     0.020    0.031   0.005
-21               0.028  563.000       0.02     0.374    0.016     0.025    0.037   0.005
-22               0.024  593.000       0.02     0.362    0.014     0.022    0.033   0.005
-23               0.015  602.000       0.02     0.358    0.010     0.017    0.026   0.004
-24               0.024  629.000       0.02     0.348    0.014     0.023    0.033   0.005
-25               0.020  636.000       0.02     0.346    0.012     0.020    0.030   0.005
-26               0.048  729.000       0.02     0.316    0.027     0.039    0.053   0.007
-27               0.031  849.000       0.02     0.284    0.019     0.028    0.038   0.005
-28               0.027  914.000       0.02     0.269    0.017     0.025    0.035   0.005
-29               0.021  940.000       0.02     0.264    0.014     0.021    0.030   0.004
-30               0.029 1193.000       0.02     0.220    0.020     0.027    0.036   0.004
-31               0.020 1340.000       0.02     0.201    0.014     0.020    0.027   0.003
-== Mean ==       0.029  517.032       0.02     0.438    0.015     0.025    0.037   0.006
+         obs.mean    n prior.mean shrinkage intv.low post.mean intv.upp post.sd
+1           0.045   67       0.02     0.834    0.011     0.024    0.042   0.008
+2           0.029   68       0.02     0.832    0.010     0.022    0.038   0.007
+3           0.024  210       0.02     0.616    0.011     0.021    0.035   0.006
+4           0.043  256       0.02     0.568    0.017     0.030    0.046   0.008
+5           0.033  269       0.02     0.556    0.015     0.026    0.041   0.007
+6           0.044  274       0.02     0.551    0.018     0.031    0.047   0.008
+7           0.043  278       0.02     0.548    0.018     0.030    0.047   0.007
+8           0.014  295       0.02     0.533    0.008     0.017    0.029   0.005
+9           0.029  347       0.02     0.492    0.014     0.024    0.038   0.006
+10          0.037  349       0.02     0.491    0.017     0.029    0.043   0.007
+11          0.039  358       0.02     0.484    0.018     0.030    0.045   0.007
+12          0.018  396       0.02     0.459    0.010     0.019    0.030   0.005
+13          0.028  431       0.02     0.438    0.015     0.024    0.037   0.006
+14          0.025  441       0.02     0.433    0.013     0.023    0.035   0.005
+15          0.027  477       0.02     0.414    0.015     0.024    0.036   0.006
+16          0.045  484       0.02     0.410    0.023     0.035    0.050   0.007
+17          0.030  494       0.02     0.405    0.016     0.026    0.039   0.006
+18          0.022  501       0.02     0.402    0.012     0.021    0.032   0.005
+19          0.028  505       0.02     0.400    0.015     0.025    0.036   0.005
+20          0.020  540       0.02     0.384    0.012     0.020    0.031   0.005
+21          0.028  563       0.02     0.374    0.016     0.025    0.037   0.005
+22          0.024  593       0.02     0.362    0.014     0.022    0.033   0.005
+23          0.015  602       0.02     0.358    0.010     0.017    0.026   0.004
+24          0.024  629       0.02     0.348    0.014     0.023    0.033   0.005
+25          0.020  636       0.02     0.346    0.012     0.020    0.030   0.005
+26          0.048  729       0.02     0.316    0.027     0.039    0.053   0.007
+27          0.031  849       0.02     0.284    0.019     0.028    0.038   0.005
+28          0.027  914       0.02     0.269    0.017     0.025    0.035   0.005
+29          0.021  940       0.02     0.264    0.014     0.021    0.030   0.004
+30          0.029 1193       0.02     0.220    0.020     0.027    0.036   0.004
+31          0.020 1340       0.02     0.201    0.014     0.020    0.027   0.003
+colMeans    0.029  517       0.02     0.438    0.015     0.025    0.037   0.006
 \end{CodeOutput}
+\end{CodeChunk}
+For reference, we need to type `\code{R> print(p, sort = FALSE)}' instead of `\code{R> p}' to list the above output by the order of data input.
+`\code{R> p}' will automatically sort the output by the increasing order of $n_{j}$.
+\\
+
+The output contains information about sample mean (\code{obs.mean}), total number of trials (\code{n}), prior mean ($\lambda_{0}$), shrinkage, lower interval, posterior mean ($E(\lambda_{j}\vert \textbf{z})$), upper interval, and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{z})$).
+\\
+
+As we can see in (6), the posterior mean ($(1-B_{j})y_{j} + B_{j}\lambda_{0}$) is a linear function of shrinkage ($\equiv r / (r + n_{j})$), locating between the sample mean and prior mean ($\lambda_{0}=0.02$).
+It makes sense because $r$ can be interpreted as the amount of prior information; if the second level has more information than the first level, then the sample mean shrinks towards the prior mean more than 50\%.
+\\
+
+A function ``\code{summary}'' shows selective information on hospitals and more detailed estimation result as below.
+To be specific, it selectively displays estimation result of hospitals with minimum, median, and maximum values of $n_{j}$.
+Also, more specific estimation results, such as estimation result of $\alpha=\log(1/r)$, will follow.
+Note that if we fit a regression when we do not know the second-level mean unlike this example, the regression summary will appear.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> summary(p)
+\end{CodeInput}
+\begin{CodeOutput}
+Main summary:
+
+                  obs.mean    n prior.mean shrinkage intv.low post.mean intv.upp post.sd
+Unit w/ min(n)       0.045   67       0.02     0.834    0.011     0.024    0.042   0.008
+Unit w/ median(n)    0.045  484       0.02     0.410    0.023     0.035    0.050   0.007
+Unit w/ max(n)       0.020 1340       0.02     0.201    0.014     0.020    0.027   0.003
+Overall Mean         0.029  517       0.02     0.438    0.015     0.025    0.037   0.006
+
+Second-level Variance Component Estimation Summary:
+alpha = log(A) for Gaussian and log(1/r) for Binomial and Poisson data:
+
+  post.mode.alpha post.sd.alpha
+1          -5.818         0.411
+\end{CodeOutput}
+\end{CodeChunk}
+Since estimated $\alpha$ is -5.818, we can easily calculate $r=\textrm{exp}(5.818)=336$, which will be helpful for understanding how each shrinkage of hospital was determined by comparing this value to the amount of observed information ($n_{j}$).
+\\
+
+But bunch of numbers can sometimes distract us from the important point.
+In this sense, we also need a graphical summary that can give us valuable insight buried in pile of numbers and a function `\code{plot}' is exactly for this purpose.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> plot(p)
+\end{CodeInput}
 \end{CodeChunk}
@@
 \includegraphics[scale=0.3]{hospital1.png}
-\caption{Shrinkage and interval plots of 31 hospitals in NY}
 \end{center}
 \end{figure}
+The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
+And note that some hospitals' ranks have changed by shrinking much harder towards 0.02 than others.
+For example, the empty square at the crossing point of the first two lines indicates that seemingly safest hospital among 31 hospitals in terms of the observed sample mean was not actually safer than the second safest hospital.
+Without this hierarchical modeling, we might have made a wrong decision in choosing a hospital.
+\\
 
+The estimated 95\% intervals are displayed on the right-side plot.
+We can clearly see that all the posterior mean (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line).
+Although the fist interval does not include the observed sample mean, it can happen by chance considering these are 95\% intervals.
+Overall, this plot shows that as the sample size increases (size of dots) and as the posterior mean gets close to 0, the length of interval gets shorter.
 \subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}

### 2013-04-13 jss/article.tex
change pic

@@
 We can clearly see that all the posterior mean (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line).
+But the most important information from this plot would be the range of each hospital's true death rate.
+Overall, as the sample size increases (size of dots) and as the posterior mean gets close to 0, the length of interval gets shorter, which the formula of posterior variance (6) implies.
 Although the fist interval does not include the observed sample mean, it can happen by chance considering these are 95\% intervals.
-Overall, this plot shows that as the sample size increases (size of dots) and as the posterior mean gets close to 0, the length of interval gets shorter.
+Then, how reliable are these intervals?
+The method check will answer it.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> coverage(p, nsim = 10000)
+\end{CodeInput}
+\end{CodeChunk}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width = 6cm]{hospital3.png}
+\end{center}
+\end{figure}
+We generated 10,000 pseudo-datasets and estimated coverage probabilities in two ways, unbiased estimates (blue dashed line) and Rao-Blackwellized estimates. 
 \subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}

### 2013-04-13 Rgbp/R/coverage.R

@@ -336,13 +336,13 @@ coverage <- function(gbp.object, A.or.r, reg.coef, covariates, mean.PriorDist, n
   if (is.na(gbp.object$prior.mean)){
     if (gbp.object$model == "gr") {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dotted Line: (Unbiased)",
+                             "Blue Dashed Line: (Unbiased)",
                              paste("A =", round(A, 2)), 
                              paste("beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     } else {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dotted Line: (Unbiased)",
+                             "Blue Dashed Line: (Unbiased)",
                              paste("r =", round(r, 2)), 
                              paste("beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
@@ -350,12 +350,12 @@ coverage <- function(gbp.object, A.or.r, reg.coef, covariates, mean.PriorDist, n
   } else {  # if prior mean is assigned
     if (gbp.object$model == "gr") {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dotted Line: (Unbiased)",
+                             "Blue Dashed Line: (Unbiased)",
                              paste("A =", round(A, 2)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     } else {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dotted Line: (Unbiased)",
+                             "Blue Dashed Line: (Unbiased)",
                              paste("r =", round(r, 2)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     }

### 2013-04-13 jss/article.tex
hospital done

@@
 \end{figure}
-We generated 10,000 pseudo-datasets and estimated coverage probabilities in two ways, unbiased estimates (blue dashed line) and Rao-Blackwellized estimates. 
+We generated 10,000 pseudo-datasets and estimated coverage probabilities by unbiased estimates (a blue dashed line) and Rao-Blackwellized estimates (a red line).
+Both lines are indistingishable from the horizontal line at 0.95 and the overall average coverage rate is 0.951 based on both estimation methods.
+Finally, this method check showed that the interval estimates from our hierarchical modeling (with Bayesian framework) on this dataset had a very good repeated sampling property.
+
 \subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}

### 2013-04-13 jss/article.tex
correcting

@@
 
-Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger).
+Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger).
 This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.
@@
 \subsection{Binomial: 18 Baseball Data}
-This dataset contains information about batting averages of 18 major league players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
+This dataset contains information about batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
 Also, it has two covariates, League and Position, showing in which league and in which position each player was playing.
@@
 \end{CodeChunk}
-The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown parameter $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
+The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown true batting average $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
 This dataset is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.
@@
 where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients.
-Note that if there is no covariate then $m$ is 1 for an intercept term, making $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$.
-For reference, a paramter with a zero subscript, $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution.
-Also,  Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution.
+Note that if there is no covariate then $x_{j, (1\times1)}=1$ for an intercept term and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
+For reference, a paramter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean.
+Also,  Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution, which is the same as (1) $\times$ (2) up to a normalizing constant.
 \begin{equation}
@@
 \code{gbp} is also able to build a Poisson-Gamma multi-level model on the 31 hospital data.
-Note that a constant multiplied to the notation representing Gamma distribution below is a scale and a square bracket below indicates [mean, variance] of distribution.
-And for notational consistency, let's define $y_{j}\equiv \frac{z_{j}}{n_{j}}$ for all $j$.
+Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket below indicates [mean, variance] of distribution.
+And for notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ for all $j$.
 \begin{equation}
@@
 
-where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0j}$,  $B_{j}\equiv \frac{r}{r+n_{j}}$, and $y_{j}\equiv \frac{z_{j}}{n_{j}}$, $j=1, \ldots, 31$.
+where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0j}$,  $B_{j}\equiv r / (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1, \ldots, 31$.
 
@@
 Hyper-prior distribution indicates a distribution of the second-level parameters, which plays an important role in deriving a full posterior distribution of all the parameters.
-\code{gbp} sets a non-informative distribution on second-level parameters to let the data speak more about their estimation.
+\code{gbp} sets non-informative distributions on second-level parameters to let the data speak more about their estimation.
 \begin{equation}
@@
 where $m$ is the number of regression coefficients.
-For $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets informative as number of groups increases.
-Another flat prior on the hyper-prameter $A$ (or $1/r$) that we suggest here will guarantee a posterior propriety under the moderate conditions and will give users a good repeated sampling property.
+For $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases.
+Another flat prior on the second-level variance component  $A$ (or $1/r$) that we suggest here will guarantee a posterior propriety under the moderate conditions and will bring a good repeated sampling property to us.
 \\
@@
 \section[Estimation]{Estimation}
+
 \subsection[Shrinkage Estimation]{Shrinkage Estimation}
-Estimating shrinkage is a key part of our work because as we can see the posterior means in (3), (6), and (9) are a linear function of shrinkage and the posterior variances are also a linear (Gaussian), quadratic (Poisson), or cubic (Binomial) function of shrinkage.
-Once we estimate it, we can approximate the posterior moments given only data by Adam's law, for example, $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ for Gaussian model and by Eve's law, for instance, $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$
+Estimating shrinkage is a key part of our hierarchical modeling.
+As we can see in (3), (6), and (9), the posterior means are a linear function of shrinkage and the posterior variances are also a linear (Gaussian), quadratic (Poisson), or cubic (Binomial) function of shrinkage.
+It implies that we cannot obtain $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ without appropriate shrinkage estimation.
+
 \subsection[ADM]{Adjustment for Density Maximization}
@@
 
-In this case, one way is to obtain an MLE of the variance component with its asymptotic Normal distribution and then to use Delta method for asymptotic Normal distribution of shrinkage.
+In this case, the most common way is to obtain an MLE of the variance component with its asymptotic Normality and then to use Delta method for asymptotic Normal distribution of shrinkage, \emph{i.e.}, $\hat{B}_{j, MLE}=B_{j}(\hat{A}_{MLE})$.
 But is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1?
+Why do we fit a logistic regression, such as logit($p$) = $x^{T}\beta$, instead of fitting a linear regression, $p = x^{T}\beta$?
 \\
@@
 Here the adjustment for density maximization (Morris and Tang, 2011), called ADM, comes.
-It assumes the Beta distribution for shrinkage, which the authors believe is a much better approximation for it, and estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$.
+It assumes the Beta distribution for shrinkage because this distribution is also defined between 0 and 1.
+In the end, ADM  estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause.
+Please refer to Morris and Tang (2011) for more apparent advantages for using ADM.
+\\
+
+Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only data.
+Taking the Normal model as an example,  $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Adam's law and $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Eve's law.
+Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are a function of shrinkage in (3) and Adam's and Eve's laws are taking conditional expectation and variance over it given data.
 
 \subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
-After estimating two posterior moments, \code{gbp} reasonably approximates posterior distribution given only data, \emph{i.e.}, ($\mu_{j}\vert \textrm{data}$), ($\lambda_{j}\vert \textrm{data}$), or ($p_{j}\vert \textrm{data}$), by matching two moments with its parameters.
-The reason we said `reasonablely approximates' is that it is hard to find a closed form of posterior distribution given only data unless it is a Gaussian model.
-So, we assumed $(p_{j}\vert \textrm{data})$ had also Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textrm{data})$ and $Var(p_{j}\vert \textrm{data})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.
+After estimating two posterior moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, \code{gbp} reasonably approximates a posterior distribution given data, \emph{i.e.}, $p_{j}\vert \textbf{z}$ (or $\mu_{j}\vert \textbf{y}$, $\lambda_{j}\vert \textbf{z}$), by matching these two moments with its parameters.
+To be specific, we assumed $p_{j}\vert \textbf{z}$ had another Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.
 
@@
 Like the two sides of the same coin, checking a statistical model always comes with fitting a model.
-If a fitted model cannot pass a checking process, we usually go back to the fitting process and come back to checking process iteratively.
+If a fitted model cannot pass a checking process, we usually go back to the fitting process and come back to the checking process iteratively.
 In this sense, checking a fitted model is an interactive procedure for the model justification.
@@
 The model check is for the justification of a hierarchical modeling on a specific dataset.
-One possible question is, ``Can this dataset benefit from such a modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $(z_{j}\vert \beta, r)\sim\textrm{Negative-Binomial}$, for Poisson data to justify the second-level hierarchy.
+One possible question is, ``Can this dataset benefit from such a multi-level modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy.
 They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
@@
 
-Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates.
+Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates, the final product of this multi-level modeling.
 ``Does the confidence interval obtained via this Bayesian model-fitting process achieve pre-specified 100($1-\alpha$)\% confidence level for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point.
@@
 Figure 1 will be helpful to understand this process.
-As we can see in (8), the distribution of each true parameter ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(m\times1)}$, where $m$ is the number of regression coefficients.
-Once we fix these hyper-parameters at specific values, we can generate true parameters.
-Suppose we sampled 500 $\textbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\textbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$.
-Then, we can also generate $\{\textbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-dataset and $j$ does $j$-th player.
-Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\textbf{z}^{(i)}_{(18\times1)}, \textbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500*18 interval estimates.
-Taking the first player as an example, we have 500 pairs of ($z_{i1}$, $p_{i1}$), $i=1,\ldots, 500$, and 500 interval estimates.
+As we can see in (8), the distribution of each true batting average ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(m\times1)}$, where $m$ is the number of regression coefficients.
+So, once we fix these hyper-parameters at specific values, we can generate true batting averages.
+Suppose we sampled 500 $\mathbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\mathbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (8), where $r$ and $\beta$ are given.
+Then, we can also generate $\{\mathbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-dataset and $j$ does $j$-th player.
+Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\mathbf{z}^{(i)}_{(18\times1)}, \mathbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500$\times$18 interval estimates.
+After this generating process, as for the first player, we will have 500 pairs of ($z_{i1}$, $p_{i1}$) and 500 interval estimates, ($\hat{p}_{i1, low}, \hat{p}_{i1, upp}$), $i=1, \ldots, 500$.
 \begin{figure}[h]
@@
 \subsection{Rao-Blackwellized Coverage Probability}
-Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were fixed at first (see 5.1) and $z_{ij}$ is a sufficient statistic.
-This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates (numeric values) on the $i$-th dataset.
-We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ in (9).
-Then, we can estimate the first player's coverage probability, for instance, by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
+Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic.
+This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates on the $i$-th dataset.
+We can calculate this probability  because we know the distribution of $p_{ij} \vert z_{ij}, r, \beta$ in (9).
+Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ because we know $r$ and $\beta$.
+Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is way more accurate than the previous one.
 \section[Example]{Example}
 \subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
-If you, living in the New York state (NY), were suffering from severe coronary heart disease (hopefully not), and were supposed to receive the coronary artery bypass graft (CABG) surgery, your concern might be each hospital's abililty to handle this surgery.
+Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease (hopefully not).
+If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery.
+On top of that, if you can figure out each hospital's abililty to handle this surgery, it will be useful for your decision to choose a hospital.
 \\
@@
 For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths within a month of CABG surgeries and total number of patients receiving CABG surgeries in each hospital.
-In addition, suppose you could obtaion the state-level death rate of this surgery while you were looking for such information, which was 0.02.
-From this point, there are a lot of ways to explore those data to have an idea about each hospital's ability.
+In addition, while you were looking for such information, suppose you could know that the  state-level death rate per exposure of this surgery in the past ten years was 0.02.
 \\
 
-One way we suggest here is a hierarchical modeling assuming that there is a bigger population-level hierarchy.
-In this case, for example, we presume that there is a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY.
-Then, we can consider the true death rates of those 31 hospitals were sampled from this state-level population distribution whose mean is 0.02.
-The validity of such an assumption can be checked (Christiansen and Morris, 1996).
+The multi-level modeling that assumes a bigger population-level hierarchy will be insightful in this problem.
+Here, we presume a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY.
+This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution whose mean is 0.02.
+For reference, a model check can be useful for evaluating the validity of such a view point (Christiansen and Morris, 1996).
 \\

### 2013-04-13 jss/article.tex
intv.low - > low.intv

@@
 
-Once we are sure that the assumption of an additional hierarchy is reasonable, we start a model-fitting process.
-Since the true death rate after CABG surgery might be small and caseloads ($n_{j}$) look relatively much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data.
-Next, \code{gbp} will help us fit a multi-level model with the Gamma conjugate distribution for $\lambda_{j}$ on the second-level hierarchy whose mean is 0.02 ($\lambda_{0}=0.02$) as described in the section 3.2.
+Assuming an additional hierarchy is reasonable, a model-fitting process begins.
+Since the true death rate per exposure after CABG surgery might be small and the caseloads ($n_{j}$) look relatively much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data.
+Next, \code{gbp} will help us fit the Poisson multi-level model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.02 ($\lambda_{0}=0.02$) as described in 3.2 .
+For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via any regression.
 \begin{CodeChunk}

### 2013-04-13 Rgbp/R/gbp.R

@@ -20,13 +20,13 @@ print.gbp <- function(x, sort = TRUE, ...) {
     if (x$model == "gr") {
       temp <- data.frame(obs.mean = x$sample.mean, se = x$se, x = cova, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
-                         intv.low = x$post.intv.low, post.mean = x$post.mean, 
-                         intv.upp = x$post.intv.upp, post.sd = x$post.sd)
+                         low.intv = x$post.intv.low, post.mean = x$post.mean, 
+                         upp.intv = x$post.intv.upp, post.sd = x$post.sd)
     } else {
       temp <- data.frame(obs.mean = x$sample.mean, n = x$se, x = cova, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
-                         intv.low = x$post.intv.low, post.mean = x$post.mean, 
-                         intv.upp = x$post.intv.upp, post.sd = x$post.sd)
+                         low.intv = x$post.intv.low, post.mean = x$post.mean, 
+                         upp.intv = x$post.intv.upp, post.sd = x$post.sd)
     }
 
   } else if (any(is.na(x$prior.mean)) & identical(x$X, NA)) { 
@@ -35,13 +35,13 @@ print.gbp <- function(x, sort = TRUE, ...) {
     if (x$model == "gr") {
       temp <- data.frame(obs.mean = x$sample.mean, se = x$se, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
-                         intv.low = x$post.intv.low, post.mean = x$post.mean, 
-                         intv.upp = x$post.intv.upp, post.sd = x$post.sd)
+                         low.intv = x$post.intv.low, post.mean = x$post.mean, 
+                         upp.intv = x$post.intv.upp, post.sd = x$post.sd)
     } else {
       temp <- data.frame(obs.mean = x$sample.mean, n = x$se, 
                          prior.mean = x$prior.mean.hat, shrinkage = x$shrinkage, 
-                         intv.low = x$post.intv.low, post.mean = x$post.mean, 
-                         intv.upp = x$post.intv.upp, post.sd = x$post.sd)
+                         low.intv = x$post.intv.low, post.mean = x$post.mean, 
+                         upp.intv = x$post.intv.upp, post.sd = x$post.sd)
     }
 
 
[…]

### 2013-04-14 jss/article.tex
hospital done

@@
 Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates, the final product of this multi-level modeling.
-``Does the confidence interval obtained via this Bayesian model-fitting process achieve pre-specified 100($1-\alpha$)\% confidence level for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point.
+``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point.
 From now on, all the explanations will be based on the Binomial model.
@@
 
-         obs.mean    n prior.mean shrinkage intv.low post.mean intv.upp post.sd
+         obs.mean    n prior.mean shrinkage low.intv post.mean upp.intv post.sd
 1           0.045   67       0.02     0.834    0.011     0.024    0.042   0.008
@@
 \end{CodeChunk}
-For reference, we need to type `\code{R> print(p, sort = FALSE)}' instead of `\code{R> p}' to list the above output by the order of data input.
-`\code{R> p}' will automatically sort the output by the increasing order of $n_{j}$.
+For reference, we need to type `\code{R> print(p, sort = FALSE)}' instead of `\code{R> p}' in order to list hospitals by the order of data input in the above output.
+`\code{R> p}' automatically sorts the output by the increasing order of $n_{j}$.
 \\
 
-The output contains information about sample mean (\code{obs.mean}), total number of trials (\code{n}), prior mean ($\lambda_{0}$), shrinkage, lower interval, posterior mean ($E(\lambda_{j}\vert \textbf{z})$), upper interval, and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{z})$).
+The output contains information about sample mean (\code{obs.mean}), caseload (\code{n}), known prior mean ($\lambda_{0}$), shrinkage ($B_{j}$), lower interval, posterior mean ($E(\lambda_{j}\vert \textbf{z})$), upper interval, and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{z})$).
 \\
@@
 As we can see in (6), the posterior mean ($(1-B_{j})y_{j} + B_{j}\lambda_{0}$) is a linear function of shrinkage ($\equiv r / (r + n_{j})$), locating between the sample mean and prior mean ($\lambda_{0}=0.02$).
-It makes sense because $r$ can be interpreted as the amount of prior information; if the second level has more information than the first level, then the sample mean shrinks towards the prior mean more than 50\%.
+It makes sense because $r$ can be interpreted as the amount of prior information and $n_{j}$ as the amount of observed information.
+If the second level has more information than the first level, then the sample mean shrinks towards the prior mean more than 50\%.
+This point is clear in the above output; as caseload increases, shrinkage decreases, depending less on the prior information.
 \\
@@
 A function ``\code{summary}'' shows selective information on hospitals and more detailed estimation result as below.
-To be specific, it selectively displays estimation result of hospitals with minimum, median, and maximum values of $n_{j}$.
-Also, more specific estimation results, such as estimation result of $\alpha=\log(1/r)$, will follow.
-Note that if we fit a regression when we do not know the second-level mean unlike this example, the regression summary will appear.
+To be specific, it displays some hospitals (not all as above) with minimum, median, and maximum caseloads ($n_{j}$).
+On top of that, more specific estimation results, such as the estimation result of $\alpha\equiv\log(1/r)$, follow.
+Note that when we do not know the prior mean in advance unlike this hospital problem, \code{gbp} fits a regression model and the summary of regression fit will appear.
 \begin{CodeChunk}
@@
 
-But bunch of numbers can sometimes distract us from the important point.
-In this sense, we also need a graphical summary that can give us valuable insight buried in pile of numbers and a function `\code{plot}' is exactly for this purpose.
+We also need a graphical summary that can give us valuable insight buried in pile of numbers and a function `\code{plot}' is exactly for this purpose.
 \begin{CodeChunk}
@@
 The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
-And note that some hospitals' ranks have changed by shrinking much harder towards 0.02 than others.
-For example, the empty square at the crossing point of the first two lines indicates that seemingly safest hospital among 31 hospitals in terms of the observed sample mean was not actually safer than the second safest hospital.
+Note that some hospitals' ranks have changed by shrinking much harder towards 0.02 than others.
+For example, the empty square at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly safest hospital among 31 hospitals in terms of the observed sample mean was not actually safer than the second safest hospital.
 Without this hierarchical modeling, we might have made a wrong decision in choosing a hospital.
@@
 
+Intuitively, the result of multi-level modeling makes more sense than that of naive sample mean.
+For example, suppose there are two hospitals, whose sample means ($z_{j} / n_{j}$) are 0 and 0.01 and caseloads ($n_{j}$) are 1 and 100 each.
+Do you believe that the former hospital is better than the latter and are you going to choose the former hospital?
+Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge their true death rate per exposure with just one caseload.
+Though somewhat extreme, this is what happens for the two left-most hostpitals on the first plot and this is why hierarchical modeling is a reasonable choice for this dataset.
+\\
+
 The estimated 95\% intervals are displayed on the right-side plot.
-We can clearly see that all the posterior mean (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line).
-But the most important information from this plot would be the range of each hospital's true death rate.
-Overall, as the sample size increases (size of dots) and as the posterior mean gets close to 0, the length of interval gets shorter, which the formula of posterior variance (6) implies.
-Although the fist interval does not include the observed sample mean, it can happen by chance considering these are 95\% intervals.
-Then, how reliable are these intervals?
-The method check will answer it.
+We can clearly see that all the posterior means (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line).
+Overall, as the caseload (size of dots) increases towards the right and as the posterior mean gets closer to 0, the length of interval gets shorter, which the formula of posterior variance in (6) implies.
+But the most important information from this plot would be the visualized range of each hospital's true death rate per exposure.
+\\
+
+This plot can add one more valuable point, which we could not have noticed, to the previous plot based mostly on point estimates.
+Let's look at the 8th and the 31st hospitals on the graph.
+The point estimate of the true death rate per exposure of the 31st hospital is higher than the one of the 8th.
+But, the upper bound of interval estimate of this 31st hospital is lower than that of the 8th.
+This interval plot makes the 31st hospital emerge as one of your candidates.
+(Could you regard this 31st hospital as a possible candidate before you observe this plot?)
+\\
+
+Also it reveals that the 23rd hospital whose estimated true rate was the smallest has also the smallest upper bound.
+If you are a risk-avoider, this hospital will attract you most strongly.
+And if you already chose this 23rd hospital compared to the 8th from the shrinkage plot, your decision might become stronger at this point, excluding the 8th hospital with more certainty.
+\\
+
+Then, how reliable are these intervals? Does our procedure to generate interval estimates have good repeated sampling property? The method check below will answer this question.
 \begin{CodeChunk}
 \begin{CodeInput}
-R> coverage(p, nsim = 10000)
+R> pcv <- coverage(p, nsim = 10000)
 \end{CodeInput}
@@
 \begin{center}
-\includegraphics[width = 6cm]{hospital3.png}
+\includegraphics[width = 5.5cm]{hospital3.png}
 \end{center}
 \end{figure}
-We generated 10,000 pseudo-datasets and estimated coverage probabilities by unbiased estimates (a blue dashed line) and Rao-Blackwellized estimates (a red line).
-Both lines are indistingishable from the horizontal line at 0.95 and the overall average coverage rate is 0.951 based on both estimation methods.
-Finally, this method check showed that the interval estimates from our hierarchical modeling (with Bayesian framework) on this dataset had a very good repeated sampling property.
+This \code{coverage} function generated 10,000 pseudo-datasets assuming the estimated $r~(=336.37)$ as a given value.
+For reference, we can try any other value of $r$, for example $r=200$, by replacing above code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
+\\
+
+It estimated coverage probabilities by unbiased estimates (a blue dashed line) and Rao-Blackwellized estimates (a red line).
+Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 based on both estimation methods.
+Finally, this method check showed that the interval estimates from the suggested multi-level modeling on this particular dataset has a very good repeated sampling property, achieving pre-specified 95\% confidence level.
 

### 2013-04-14 Rgbp/R/gbp.R

@@ -72,7 +72,7 @@ print.gbp <- function(x, sort = TRUE, ...) {
     temp[, 2] <- round(temp[, 2])
   }
 
-  cat("Summary for whole observations: \n")
+  cat("Summary for whole units: \n")
   cat("\n")
   print(temp)
 }

### 2013-04-14 jss/article.tex
some corrections

@@
 
-Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger).
+Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger) and $\lambda_{j}$ as a true death rate per exposure.
 This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.
@@
 
-where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta~\textrm{and}~j=1, \ldots, 18$. Then posterior distribution is
+where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta~\textrm{and}~j=1, \ldots, 18$. Then, corresponding posterior distribution is
 \begin{equation}
-p_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}y_{j},~r(1-p_{0j})+n_{j}(1-y_{j})\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
+p_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}y_{j},~r(1-p_{0j})+n_{j}(1-y_{j}))\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
 \end{equation}
-where $p^{\ast}_{j}\equiv(1-B_{j})y_{j}+B_{j}p_{0j}$, $B_{j}\equiv\frac{r}{r+n_{j}}$, and $y_{j}\equiv\frac{z_{j}}{n_{j}}$, $j=1,\ldots,18$.
+where $p^{\ast}_{j}\equiv(1-B_{j})y_{j}+B_{j}p_{0j}$, $B_{j}\equiv r/ (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1,\ldots,18$.
 
@@
 For $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases.
-Another flat prior on the second-level variance component  $A$ (or $1/r$) that we suggest here will guarantee a posterior propriety under the moderate conditions and will bring a good repeated sampling property to us.
+Another flat prior on the second-level variance component  $A$ (or $1/r$) that we suggest here will guarantee a posterior propriety under moderate conditions and will bring a good repeated sampling property.
 \\
@@
 Taking the Normal model as an example,  $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Adam's law and $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Eve's law.
-Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are a function of shrinkage in (3) and Adam's and Eve's laws are taking conditional expectation and variance over it given data.
+Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are a function of shrinkage in (3) and Adam's and Eve's laws are taking conditional expectation and variance over them given data.
 
@@
 Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\mathbf{z}^{(i)}_{(18\times1)}, \mathbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500$\times$18 interval estimates.
-After this generating process, as for the first player, we will have 500 pairs of ($z_{i1}$, $p_{i1}$) and 500 interval estimates, ($\hat{p}_{i1, low}, \hat{p}_{i1, upp}$), $i=1, \ldots, 500$.
+After this generating process, as for the first player, we will have 500 pairs of ($z_{i1}$, $p_{i1}$) and 500 interval estimates, $\{(\hat{p}_{i1, low}, ~\hat{p}_{i1, upp}$), $i=1, \ldots, 500\}$.
 \begin{figure}[h]
@@
 Assuming an additional hierarchy is reasonable, a model-fitting process begins.
-Since the true death rate per exposure after CABG surgery might be small and the caseloads ($n_{j}$) look relatively much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data.
+Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) looks relatively much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data.
 Next, \code{gbp} will help us fit the Poisson multi-level model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.02 ($\lambda_{0}=0.02$) as described in 3.2 .
@@
 For reference, we need to type `\code{R> print(p, sort = FALSE)}' instead of `\code{R> p}' in order to list hospitals by the order of data input in the above output.
-`\code{R> p}' automatically sorts the output by the increasing order of $n_{j}$.
+`\code{R> p}' automatically sorts the output by the increasing order of caseload ($n_{j}$).
 \\
@@
 
-As we can see in (6), the posterior mean ($(1-B_{j})y_{j} + B_{j}\lambda_{0}$) is a linear function of shrinkage ($\equiv r / (r + n_{j})$), locating between the sample mean and prior mean ($\lambda_{0}=0.02$).
+As we can see in (6), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a linear function of shrinkage, $B_{j}\equiv r / (r + n_{j})$, locating between the sample mean and prior mean ($\lambda_{0}=0.02$).
 It makes sense because $r$ can be interpreted as the amount of prior information and $n_{j}$ as the amount of observed information.
@@
 \end{figure}
-The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
+The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means, empty dots on the upper line, are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
 Note that some hospitals' ranks have changed by shrinking much harder towards 0.02 than others.
-For example, the empty square at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly safest hospital among 31 hospitals in terms of the observed sample mean was not actually safer than the second safest hospital.
+For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly safest hospital among 31 hospitals in terms of the observed sample mean was not actually safer than the second safest hospital.
 Without this hierarchical modeling, we might have made a wrong decision in choosing a hospital.
@@
 Do you believe that the former hospital is better than the latter and are you going to choose the former hospital?
-Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge their true death rate per exposure with just one caseload.
+Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload.
 Though somewhat extreme, this is what happens for the two left-most hostpitals on the first plot and this is why hierarchical modeling is a reasonable choice for this dataset.
@@
 
-Also it reveals that the 23rd hospital whose estimated true rate was the smallest has also the smallest upper bound.
+Also it reveals that the 23rd hospital, whose estimated true rate was the smallest, has also the smallest upper bound.
 If you are a risk-avoider, this hospital will attract you most strongly.
@@
 \begin{center}
-\includegraphics[width = 5.5cm]{hospital3.png}
+\includegraphics[width = 5.5cm]{hospital2.png}
 \end{center}
@@
 Finally, this method check showed that the interval estimates from the suggested multi-level modeling on this particular dataset has a very good repeated sampling property, achieving pre-specified 95\% confidence level.
+\\
 
+Morris and Christiansen (1995) also look into this ranking problem, taking shrinkage into account.
 \subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}
@@
 
-4. Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
+4.
+Morris, C.
+and Christiansen, C.
+(1995).
+``Hierarchical Models for Ranking and for Identifying Ex- tremes, With Application,'' in \emph{Bayesian Statistics 5}, eds.
+J.
+Bernardo, J.
+Berger, A.
+Dawid, and A.
+Smith, New York: Oxford University Press, pp.
+277-296.
 \\
 
-5. Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
+5. Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
 \\
 
-6. Rubin, D. B. (1981). ``Estimation in parallel randomized
+6. Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
+\\
+
+7. Rubin, D. B. (1981). ``Estimation in parallel randomized
   experiments.'' \emph{Journal of Educational Statistics}. \textbf{6}. 377-401.

### 2013-04-14 Rgbp/R/coverage.R

@@ -328,8 +328,10 @@ coverage <- function(gbp.object, A.or.r, reg.coef, covariates, mean.PriorDist, n
 
   # plotting coverage graph
   par(xaxs = "r", yaxs = "r", mai = c(1, 0.6, 1, 0.3))
+  n.units <- length(gbp.object$se)
   plot(1 : length(gbp.object$se), result, ylim = c(0.7, 1), type = "l", col = 2, ylab = "",
-       xlab = "Group_i, i = 1, ..., k", main = "Estimated Coverage Probability for Each Group",
+       xlab = paste("Unit_j", ", ", "j = 1, ...,", n.units), 
+       main = "Estimated Coverage Probability for Each Unit",
        lwd = 3, lty = 1)
   abline(h = 0.95)
   points(1 : length(gbp.object$se), result2, type = "l", lty = 2, col = 4, lwd = 2)

### 2013-04-14 Rgbp/R/gbp.R

@@ -298,9 +298,9 @@ plot.gbp <- function(x, sort = TRUE, ...) {
     po.low <- temp.data[, 6]
     po.upp <- temp.data[, 7]
     if (x$model == "gr") {
-      xlabel <- "Indices (Groups) sorted by the order of se"
+      xlabel <- "Units sorted by the order of se"
     } else {
-      xlabel <- "Indices (Groups) sorted by the order of n"
+      xlabel <- "Units sorted by the order of n"
     }
   }
 

### 2013-04-14 Rgbp/R/gbp.R
small correction

@@ -298,9 +298,9 @@ plot.gbp <- function(x, sort = TRUE, ...) {
     po.low <- temp.data[, 6]
     po.upp <- temp.data[, 7]
     if (x$model == "gr") {
-      xlabel <- "Units sorted by the order of se"
+      xlabel <- "Units sorted by the increasing order of se"
     } else {
-      xlabel <- "Units sorted by the order of n"
+      xlabel <- "Units sorted by the increasing order of n"
     }
   }
 

### 2013-04-14 jss/article.tex
just before writing baseball

@@
 
-                  obs.mean    n prior.mean shrinkage intv.low post.mean intv.upp post.sd
-Unit w/ min(n)       0.045   67       0.02     0.834    0.011     0.024    0.042   0.008
-Unit w/ median(n)    0.045  484       0.02     0.410    0.023     0.035    0.050   0.007
-Unit w/ max(n)       0.020 1340       0.02     0.201    0.014     0.020    0.027   0.003
-Overall Mean         0.029  517       0.02     0.438    0.015     0.025    0.037   0.006
+                  obs.mean    n prior.mean shrinkage low.intv post.mean
+Unit w/ min(n)       0.045   67       0.02     0.834    0.011     0.024
+Unit w/ median(n)    0.045  484       0.02     0.410    0.023     0.035
+Unit w/ max(n)       0.020 1340       0.02     0.201    0.014     0.020
+Overall Mean         0.029  517       0.02     0.438    0.015     0.025
+
+                  upp.intv post.sd
+                     0.042   0.008
+                     0.050   0.007
+                     0.027   0.003
+                     0.037   0.006
 
@@
 \begin{center}
-\includegraphics[scale=0.3]{hospital1.png}
+\includegraphics[scale=0.25]{hospital1.png}
 \end{center}
 \end{figure}
+
 The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means, empty dots on the upper line, are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
@@
 
-Then, how reliable are these intervals? Does our procedure to generate interval estimates have good repeated sampling property? The method check below will answer this question.
+Then, how reliable are these intervals?
+Does our procedure to generate interval estimates have good repeated sampling property?
+The following method check will answer this question.
+The \code{coverage} function below generates 10,000 pseudo-datasets assuming the estimated $r~(=336.37)$ as a given value.
+For reference, we can try any other value of $r$, for example $r=200$, by replacing below code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
+
 \begin{CodeChunk}
@@
 \end{figure}
-This \code{coverage} function generated 10,000 pseudo-datasets assuming the estimated $r~(=336.37)$ as a given value.
-For reference, we can try any other value of $r$, for example $r=200$, by replacing above code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
+
+It estimated coverage probabilities by unbiased estimates (a blue dashed line) and Rao-Blackwellized estimates (a red line).
+Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 from the Rao-Blackwellized estimate and 0.95 from the unbiased estimate.
+Finally, this method check proved that the interval estimates from the suggested multi-level modeling on this particular dataset has a very good repeated sampling property, achieving pre-specified 95\% confidence level.
 \\
 
-It estimated coverage probabilities by unbiased estimates (a blue dashed line) and Rao-Blackwellized estimates (a red line).
-Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 based on both estimation methods.
-Finally, this method check showed that the interval estimates from the suggested multi-level modeling on this particular dataset has a very good repeated sampling property, achieving pre-specified 95\% confidence level.
+For reference, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is \code{R> gbp(z, n, Alpha = 0.9, model = "pr")}.
+Then, the function \code{coverage} will evaluate whether interval estimates achieve 90\% confidence level.
 \\
 
-Morris and Christiansen (1995) also look into this ranking problem, taking shrinkage into account.
+Morris and Christiansen (1995) also looked into a similar ranking problem in hierarchical modeling, taking shrinkage into account.
+\\
+
 \subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}
+\begin{CodeChunk}
+\begin{CodeInput}
+R> g <- gbp(y, se, model = "gr")
+R> g
+\end{CodeInput}
+\begin{CodeOutput}
+Summary for whole units:
+
+         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
+5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
+2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
+7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
+4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
+6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
+1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
+3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
+8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
+colMeans     8.75 12.5      8.168     0.552   -9.163     8.168   25.723   8.900
+\end{CodeOutput}
+\end{CodeChunk}
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> summary(g)
+\end{CodeInput}
+\begin{CodeOutput}
+Main summary:
+
+                    obs.mean   se prior.mean shrinkage low.intv post.mean
+Unit w/ min(se)        -1.00  9.0      8.168     0.408  -13.297     2.737
+Unit w/ median(se)1     1.00 11.0      8.168     0.507  -13.027     4.633
+Unit w/ median(se)2     7.00 11.0      8.168     0.507   -8.780     7.592
+Unit w/ max(se)        12.00 18.0      8.168     0.734  -10.208     9.189
+Overall Mean            8.75 12.5      8.168     0.552   -9.163     8.168
+
+                     upp.intv post.sd
+                       16.692   7.634
+                       20.131   8.441
+                       23.602   8.257
+                       29.939  10.227
+                       25.723   8.900
+
+Second-level Variance Component Estimation Summary:
+alpha = log(A) for Gaussian and log(1/r) for Binomial and Poisson data:
+
+  post.mode.alpha post.sd.alpha
+1           4.768         1.139
+
+Regression Summary:
+
+      estimate   se z.val p.val
+beta0    8.168 5.73 1.425 0.154
+\end{CodeOutput}
+\end{CodeChunk}
+
 \begin{figure}[h]
@@
 
+\begin{CodeChunk}
+\begin{CodeInput}
+R> gcv <- coverage(g, nsim = 10000)
+\end{CodeInput}
+\end{CodeChunk}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width = 5.5cm]{school2.png}
+\end{center}
+\end{figure}
+
 \subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Prior Mean and One Covariate}
+\begin{CodeChunk}
+\begin{CodeInput}
+R> b <- gbp(z, n, x, model = "br")
+R> b
+\end{CodeInput}
+\begin{CodeOutput}
+Summary for whole units:
+
+         obs.mean  n   X1 prior.mean shrinkage low.intv post.mean upp.intv post.sd
+1           0.400 45 1.00      0.310     0.715    0.248     0.335    0.429   0.046
+2           0.378 45 1.00      0.310     0.715    0.244     0.329    0.420   0.045
+3           0.356 45 1.00      0.310     0.715    0.240     0.323    0.411   0.044
+4           0.333 45 1.00      0.310     0.715    0.236     0.316    0.403   0.043
+5           0.311 45 1.00      0.310     0.715    0.230     0.310    0.396   0.042
+6           0.311 45 0.00      0.233     0.715    0.179     0.256    0.341   0.041
+7           0.289 45 0.00      0.233     0.715    0.175     0.249    0.331   0.040
+8           0.267 45 0.00      0.233     0.715    0.171     0.243    0.323   0.039
+9           0.244 45 0.00      0.233     0.715    0.166     0.237    0.315   0.038
+10          0.244 45 1.00      0.310     0.715    0.210     0.291    0.379   0.043
+11          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
+12          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
+13          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
+14          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375   0.044
+15          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375   0.044
+16          0.200 45 0.00      0.233     0.715    0.155     0.224    0.302   0.038
+17          0.178 45 0.00      0.233     0.715    0.148     0.218    0.297   0.038
+18          0.156 45 0.00      0.233     0.715    0.140     0.211    0.292   0.039
+colMeans    0.265 45 0.44      0.267     0.715    0.191     0.267    0.351   0.041
+\end{CodeOutput}
+\end{CodeChunk}
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> summary(b)
+\end{CodeInput}
+\begin{CodeOutput}
+Main summary:
+
+                          obs.mean  n   X1 prior.mean shrinkage low.intv
+Unit w/ min(obs.mean)        0.156 45 0.00      0.233     0.715    0.140
+Unit w/ median(obs.mean)1    0.244 45 0.00      0.233     0.715    0.166
+Unit w/ median(obs.mean)2    0.244 45 1.00      0.310     0.715    0.210
+Unit w/ max(obs.mean)        0.400 45 1.00      0.310     0.715    0.248
+Overall Mean                 0.265 45 0.44      0.267     0.715    0.191
+
+                         post.mean upp.intv post.sd
+                             0.211    0.292   0.039
+                             0.237    0.315   0.038
+                             0.291    0.379   0.043
+                             0.335    0.429   0.046
+                             0.267    0.351   0.041
+
+Second-level Variance Component Estimation Summary:
+alpha = log(A) for Gaussian and log(1/r) for Binomial and Poisson data:
+
+  post.mode.alpha post.sd.alpha
+1          -4.727         0.957
+
+Regression Summary:
+
+      estimate    se  z.val p.val
+beta0   -1.194 0.131 -9.129 0.000
+beta1    0.389 0.187  2.074 0.038
+\end{CodeOutput}
+\end{CodeChunk}
+
 \begin{figure}[h]
@@
 \caption{Shrinkage and interval plots of 18 baseball players}
+\end{center}
+\end{figure}
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> bcv <- coverage(b, nsim = 10000)
+\end{CodeInput}
+\end{CodeChunk}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width = 5.5cm]{baseball2.png}
 \end{center}

### 2013-04-14 Rgbp/R/gbp.R

@@ -66,10 +66,15 @@ print.gbp <- function(x, sort = TRUE, ...) {
   temp.mean <- colMeans(temp)
   temp <- data.frame(rbind(temp, temp.mean), row.names = c(rownames(temp), "colMeans"))
   temp <- round(temp, 3)
+
   if (x$model == "gr") {
     temp[, 2] <- round(temp[, 2], 1)
   } else {
     temp[, 2] <- round(temp[, 2])
+  }
+
+  if (any(is.na(x$prior.mean)) & !identical(x$X, NA)) {
+    temp[, 3] <- round(temp[, 3], 2)
   }
 
   cat("Summary for whole units: \n")

### 2013-04-14 jss/article.tex
baseball done

@@
 This plot can add one more valuable point, which we could not have noticed, to the previous plot based mostly on point estimates.
-Let's look at the 8th and the 31st hospitals on the graph.
+Let's look at the 8th and the 31st hospitals on the graph (or on the outcome for numeric reference).
 The point estimate of the true death rate per exposure of the 31st hospital is higher than the one of the 8th.
@@
 
-For reference, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is \code{R> gbp(z, n, Alpha = 0.9, model = "pr")}.
+For reference, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is \code{R> p <- gbp(z, n, Alpha = 0.9, model = "pr")}.
 Then, the function \code{coverage} will evaluate whether interval estimates achieve 90\% confidence level.
@@
 
-\begin{figure}[h]
-\begin{center}
-\includegraphics[scale=0.3]{school1.png}
-\caption{Shrinkage and interval plots of 8 schools}
-\end{center}
-\end{figure}
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[scale=0.3]{school1.png}
+%\caption{Shrinkage and interval plots of 8 schools}
+%\end{center}
+%\end{figure}
 
-\begin{CodeChunk}
-\begin{CodeInput}
-R> gcv <- coverage(g, nsim = 10000)
-\end{CodeInput}
-\end{CodeChunk}
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width = 5.5cm]{school2.png}
-\end{center}
-\end{figure}
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%R> gcv <- coverage(g, nsim = 10000)
+%\end{CodeInput}
+%\end{CodeChunk}
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width = 5.5cm]{school2.png}
+%\end{center}
+%\end{figure}
 
 \subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Prior Mean and One Covariate}
+In this example, suppose you read the New York Times published on 26 April 1970.
+One article in this magazine covered 18 baseball players' batting averages through their first official 45 at-bats of the 1970 season.
+And then, you became interested in their batting averages over the remaining season.
+How could you predict?
+For reference, the dataset  \code{baseball} has each player's batting average over the remaining season.
+\\
+
+First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this dataset.
+Assuming this distribution, we know that the sample mean (MLE) has many nice properties, one of which is uniformly minimum variance unbiased estimator (UMVUE), and is the simplest way to estimate their true batting averages.
+Can we say this is the best way to predict their batting averages?
+\\
+
+Efron and Morris (1975) said ``no,'' and suggested James-Stein estimator, making each players' sample mean shrink towards an estimated mean of the second-level prior distribution.
+They showed that this estimator was more than three times efficient than the sample mean under squared error loss.
+On top of that, a few years later Morris (1983) introduced interval estimates that could successfully catch the batting averages over the remaining season, which the MLE and its interval estimate could not.
+\\
+
+Our hierarchical modeling is a sequel to these researches, which can add one more unique value.
+Suppose you strongly believe that the outfielder's batting averages should be different from other positions' ones, not giving a credit to the assumption that all players' batting averages shrink towards the same mean.
+Instead, you want to assume two different prior distributions for outfielders and others, within which sharing information  and regressing toward the mean occur.
+Our hierarhcical modeling provides a way to incorporate such information (covariate) seamlessly into the second-level hierarchy.
+\\
+
+To be specific, it assumes there are one second-level hierarchy for outfielders and the other one for other positions.
+And it views true batting averages of outfielders as sampled from the former distribution and those of other positions from the latter.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
+Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.31 and 0.23.
+Also note that shrinkage estimates are the same for all players.
+It makes sense because shrinkage ($B_{j}\equiv r / (r+n_{j})$) is determined by the relative amount of information between the first-level and the second-level hierarchies.
+The fact that all players have the same amount of observed information ($n_{j}=45$) and the estimated $r=\textrm{exp}(4.727)=113$ from below summary tell why the estimated shrinkage is 0.715.
+\\
 
+As for the point estimates, we calculated squared error losses, $\sum_{j=1}^{18}(p_{j, remaining}-\hat{p}_{j})^{2}$, for three estimators, James-Stein (JS), ours, and sample mean.
+These values were 0.027, 0.031, and 0.086 each.
+Ours could not beat the JS that shrank all sample means towards one common estimated prior mean.
+But ours, which provides a more flexible way to model these data, was not much worse than JS and way better than sample mean under the squared error loss.
+\\
+
+One more thing to note is that the posterior standard deviation tends to be bigger among outfielders than among others.
+Let's see its formula in (9).
+We can notice that the estimated posterior mean is one factor that determines posterior variance because every player has the same at-bats ($n_{j}$) and $r$.
+As the posterior mean gets closer to 0.5, the posterior variance gets bigger and has highest value when the posterior mean is 0.5.
+Intuitively, it makes sense.
+If the probability of hit is 0.1, we can easily expect less hits.
+But if probability is 0.5, we are less certain whehter the at-bat would more likely lead to a hit or not, like a coin tossing.
+Our model is automatically reflecting on such uncertainty.
 \begin{CodeChunk}
@@
 
+This summary also includes the result of logistic regression fit because we did not know prior means in advance so that we had to estimate them via this logistic regression model.
+Let's look at the p-value of the indicator covariate (\code{beta1}).
+It shows that the two different prior distributions distinguishing outfielders from others was significantly different, supporting our assumption.
+\\
+
+Let's see shrinkage and 95\% interval plots for more intuition.
+It is obvious that sample means (empty dots) on the upper line shrink towards two different places.
+For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
+For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper line, there are short red lines toward five directions.
+It also means that the seemingly two lines crossing over others were actually three lines.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> plot(b)
+\end{CodeInput}
+\end{CodeChunk}
 \begin{figure}[h]
@@
 \includegraphics[scale=0.3]{baseball1.png}
-\caption{Shrinkage and interval plots of 18 baseball players}
 \end{center}
 \end{figure}
+
+The following 95\% interval plot shows us range of true batting average for each player.
+Note that observed sample means are all within the interval estimates.
+And these interval estimates also catched the batting averages over the ramaining season successfully, although the result was left out.
+\\
+
+Then, how much can we trust these interval estimates?
+The method check will answer it.
+The plot seems to indicate overcoverage.
+The estimated overall coverage probability is 0.974 based on the unbiased estimator and 0.973 based on the Rao-Blackwellization, at least satisfying the definition of the 95\% confidence level.
+\\
+
+Also, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 100000)}.
 
@@
 
-4.
+4. Morris, C. (1983). ``Parametric Empirical Bayes Inference: Theory and Applications.'' \emph{Journal of the American Statistical Association}. \textbf{78}. 47-55.
+\\
+
+5.
 Morris, C.
@@
 
-5. Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
+6. Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
 \\
 
-6. Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
+7. Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
 \\
 
-7. Rubin, D. B. (1981). ``Estimation in parallel randomized
+8. Rubin, D. B. (1981). ``Estimation in parallel randomized
   experiments.'' \emph{Journal of Educational Statistics}. \textbf{6}. 377-401.

### 2013-04-15 jss/article.tex
corrections

@@
 Suppose you strongly believe that the outfielder's batting averages should be different from other positions' ones, not giving a credit to the assumption that all players' batting averages shrink towards the same mean.
-Instead, you want to assume two different prior distributions for outfielders and others, within which sharing information  and regressing toward the mean occur.
-Our hierarhcical modeling provides a way to incorporate such information (covariate) seamlessly into the second-level hierarchy.
-\\
-
-To be specific, it assumes there are one second-level hierarchy for outfielders and the other one for other positions.
-And it views true batting averages of outfielders as sampled from the former distribution and those of other positions from the latter.
+Instead, you want to assume two different second-level hierarchies for outfielders and for other positions, within each of which sharing information and regressing toward the mean (RTTM) occur.
+This perspective considers true batting averages of outfielders as sampled from the one and those of other positions from the other.
+Our multi-level modeling provides a way to incorporate such information (covariate) seamlessly into the second-level hierarchy.
 \begin{CodeChunk}
@@
 We can notice that the estimated posterior mean is one factor that determines posterior variance because every player has the same at-bats ($n_{j}$) and $r$.
-As the posterior mean gets closer to 0.5, the posterior variance gets bigger and has highest value when the posterior mean is 0.5.
+As the posterior mean gets closer to 0.5, the posterior variance gets bigger and has the biggest value when the posterior mean is 0.5.
 Intuitively, it makes sense.
-If the probability of hit is 0.1, we can easily expect less hits.
-But if probability is 0.5, we are less certain whehter the at-bat would more likely lead to a hit or not, like a coin tossing.
+If a true batting average is 0.1, we can easily expect less hits.
+But if it is 0.5, we are less certain whether an at-bat would be more likely a hit or not, like a coin tossing.
 Our model is automatically reflecting on such uncertainty.
@@
 Let's look at the p-value of the indicator covariate (\code{beta1}).
-It shows that the two different prior distributions distinguishing outfielders from others was significantly different, supporting our assumption.
+It shows that the two different prior distributions distinguishing outfielders from other positions were significantly different, supporting our assumption.
+The positive sign of $\hat{\beta}_{1}$ reflects on the first five players, outfielders, whose observed batting averages were higher than others.
 \\
@@
 Let's see shrinkage and 95\% interval plots for more intuition.
-It is obvious that sample means (empty dots) on the upper line shrink towards two different places.
+It is obvious that sample means (empty dots) on the upper line shrink towards two different means, 0.31 and 0.23.
 For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
@@
 
-Also, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 100000)}.
+Also, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}.
 

### 2013-04-17 jss/article.tex
corrections
pic4

@@
 The estimated overall coverage probability is 0.974 based on the unbiased estimator and 0.973 based on the Rao-Blackwellization, at least satisfying the definition of the 95\% confidence level.
-\\
-
-Also, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}.
-
 \begin{CodeChunk}
@@
 R> bcv <- coverage(b, nsim = 10000)
+\end{CodeInput}
+\end{CodeChunk}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width = 5.5cm]{baseball2.png}
+\end{center}
+\end{figure}
+
+Also, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}.
+This adjustment option is helpful for checking coverage probability varying true parameter values.
+Using this option, we drew Rao-Blackwellized coverage estimates varying only true shrinkage from 0.01 to 0.99.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> shr <- seq(0.01, 0.99, by = 0.05)
+R> r.trial <- mean(n) * shr / (1 - shr)
+R> cov.save <- sapply (1 : length(r.trial), function(i){
+R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
+R>                        covariates = x1, nsim = 500)$average.coverageRB
+R>             })
+R> plot(shr, cov.save, type = "l", ylim = c(0.8, 1), xlab = "Shrinkage", 
+R>      ylab = "Rao-Blackwellized Coverage Estimate", lwd = 3, col = 2)
+R> abline(h = 0.95)
 \end{CodeInput}
@@
 (1995).
-``Hierarchical Models for Ranking and for Identifying Ex- tremes, With Application,'' in \emph{Bayesian Statistics 5}, eds.
+``Hierarchical Models for Ranking and for Identifying Extremes, With Application,'' in \emph{Bayesian Statistics 5}, eds.
 J.

### 2013-04-17 jss/article.tex
baseball correction

--- 2013-04-15 jss/article.tex
@@
 \end{figure}
+
+Next, we will check whether the estimated coverage probabilities are at least 95\% varying the true shrinkage values.
+Note that, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}.
+Using this adjustment option, we drew Rao-Blackwellized coverage estimates varying true shrinkage values from 0.01 to 0.99, fixing $\beta$ as estimated values.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> shr <- seq(0.01, 0.99, by = 0.05)
+R> r.trial <- mean(n) * shr / (1 - shr)
+R> cov.save <- sapply (1 : length(r.trial), function(i){
+R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
+R>                        covariates = x1, nsim = 500)$average.coverageRB
+R>             })
+R> plot(shr, cov.save, type = "l", ylim = c(0.8, 1), xlab = "Shrinkage",
+R>      ylab ="", main = "Rao-Blackwellized Coverage Estimate", lwd = 3,
+R>      col = 2)
+R> abline(h = 0.95)
+\end{CodeInput}
+\end{CodeChunk}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width = 5.5cm]{baseball4.png}
+\end{center}
+\end{figure}
+
+This graphs shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence level.
+Considering that our model is approximating the true distribution of shrinkage by ADM (Morris and Tang, 2011), this lack of 0.4\% might not be a severe defect of our model.
+The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j}))$, corresponding to $r=0$, makes parameters of the second-level distribution 0 (see (8)), and full shrinkage corresponds to $r=\infty$ that we cannot designate as an argument of \code{coverage} function.
+\\
 

### 2013-04-17 jss/article.tex
correction

@@
 The plot seems to indicate overcoverage.
-The estimated overall coverage probability is 0.974 based on the unbiased estimator and 0.973 based on the Rao-Blackwellization, at least satisfying the definition of the 95\% confidence level.
+The estimated overall coverage probability is 0.974 based on the unbiased estimator and 0.973 based on the Rao-Blackwellization, at least satisfying the definition of the 95\% confidence interval.
 \begin{CodeChunk}
@@
 
-This graphs shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence level.
+This graphs shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
 Considering that our model is approximating the true distribution of shrinkage by ADM (Morris and Tang, 2011), this lack of 0.4\% might not be a severe defect of our model.

### 2013-04-17 jss/article.tex
correction

@@
 This graphs shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
-Considering that our model is approximating the true distribution of shrinkage by ADM (Morris and Tang, 2011), this lack of 0.4\% might not be a severe defect of our model.
+Considering that our model is approximating the true distribution of shrinkage by ADM (Morris and Tang, 2011), our model still has a good repeated sampling property.
 The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j}))$, corresponding to $r=0$, makes parameters of the second-level distribution 0 (see (8)), and full shrinkage corresponds to $r=\infty$ that we cannot designate as an argument of \code{coverage} function.

### 2013-04-17 jss/article.tex
correction

@@
 Using this adjustment option, we drew Rao-Blackwellized coverage estimates varying true shrinkage values from 0.01 to 0.99, fixing $\beta$ as estimated values.
+\\
+
 \begin{CodeChunk}
 \begin{CodeInput}
-R> shr <- seq(0.01, 0.99, by = 0.05)
+R> shr <- seq(0.01, 0.99, length.out = 20)
 R> r.trial <- mean(n) * shr / (1 - shr)

### 2013-04-17 jss/article.tex
correction

@@
 For reference, we can try any other value of $r$, for example $r=200$, by replacing below code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
+\\
+
+Also, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is \code{R> p <- gbp(z, n, Alpha = 0.9, model = "pr")}.
+Then, the function \code{coverage} will evaluate whether interval estimates achieve 90\% confidence level.
+\\
 
@@
 Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 from the Rao-Blackwellized estimate and 0.95 from the unbiased estimate.
-Finally, this method check proved that the interval estimates from the suggested multi-level modeling on this particular dataset has a very good repeated sampling property, achieving pre-specified 95\% confidence level.
 \\
 
-For reference, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is \code{R> p <- gbp(z, n, Alpha = 0.9, model = "pr")}.
-Then, the function \code{coverage} will evaluate whether interval estimates achieve 90\% confidence level.
+These numbers are encouraging, but achieving at least 95\% coverage at one specific true value does not mean that our model has good repeated sampling property.
+We need to check whether coverage probabilities are at least 0.95 when the true parameter value ($r$) varies.
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> shr <- seq(0.01, 0.99, length.out = 20)
+R> r.trial <- mean(n) * shr / (1 - shr)
+R> cov.save <- sapply (1 : length(r.trial), function(i){
+R>               coverage(p, A.or.r = r.trial[i], mean.PriorDist = 0.02, 
+R>                        nsim = 500)$average.coverageRB
+R>             })
+R> plot(shr, cov.save, type = "l", ylim = c(0.8, 1), xlab = "Shrinkage",
+R>      ylab ="", main = "Rao-Blackwellized Coverage Estimate", lwd = 3,
+R>      col = 2)
+R> abline(h = 0.95)
+\end{CodeInput}
+\end{CodeChunk}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width = 5.5cm]{hospital3.png}
+\end{center}
+\end{figure}
+
+This plot shows that the estimated shrinkages are at least 0.947 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
+Note that our model is approximating the true distribution of shrinkage by ADM (see 4.2).
+Considering this point, we finally conclude that the interval estimates from the suggested multi-level modeling on this particular dataset has a very good repeated sampling property.
+\\
+
+The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j})=0)$, corresponding to $r=0$, makes the scale of the distribution go to $\infty$ (see (5)), and full shrinkage ($B_{j}=1$) corresponds to $r=\infty$ that we cannot designate as an argument of \code{coverage} function.
 \\
@@
 \\
-
-Let's see shrinkage and 95\% interval plots for more intuition.
-It is obvious that sample means (empty dots) on the upper line shrink towards two different means, 0.31 and 0.23.
-For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
-For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper line, there are short red lines toward five directions.
-It also means that the seemingly two lines crossing over others were actually three lines.
 \begin{CodeChunk}
@@
 
-The following 95\% interval plot shows us range of true batting average for each player.
+Let's see shrinkage and 95\% interval plots for more intuition.
+It is obvious that sample means (empty dots) on the upper line shrink towards two different means, 0.31 and 0.23.
+For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
+For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper line, there are short red lines toward five directions.
+It also means that the seemingly two lines crossing over others were actually three lines.
+\\
+
+The 95\% interval plot shows us range of true batting average for each player.
 Note that observed sample means are all within the interval estimates.
 And these interval estimates also catched the batting averages over the ramaining season successfully, although the result was left out.
-\\
+Then, how much can we trust these interval estimates?
+The following method check will answer it.
 
-Then, how much can we trust these interval estimates?
-The method check will answer it.
-The plot seems to indicate overcoverage.
-The estimated overall coverage probability is 0.974 based on the unbiased estimator and 0.973 based on the Rao-Blackwellization, at least satisfying the definition of the 95\% confidence interval.
 \begin{CodeChunk}
@@
 
-Next, we will check whether the estimated coverage probabilities are at least 95\% varying the true shrinkage values.
+The plot seems to indicate overcoverage.
+The estimated overall coverage probability is 0.974 based on the unbiased estimator and 0.973 based on the Rao-Blackwellization, at least satisfying the definition of the 95\% confidence interval.
+\\
+
+However, achieving at least 95\% coverage at specific true values of ($r$ and $\beta$) does not mean that our model has good repeated sampling property.
+So, as we did in 6.1, we will see at least in terms of varying $r$ whether coverage probabilities are at least 0.95 when the true shrinkage value ($B(r)$) varies, fixing $\beta$ at estimated values.
 Note that, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}.
-Using this adjustment option, we drew Rao-Blackwellized coverage estimates varying true shrinkage values from 0.01 to 0.99, fixing $\beta$ as estimated values.
-\\
 
@@
 
-This graphs shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
-Considering that our model is approximating the true distribution of shrinkage by ADM (Morris and Tang, 2011), our model still has a good repeated sampling property.
+This plot shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
+Considering that our model is approximating the true distribution of shrinkage by ADM (see 4.2), we finally conclude that the interval estimates from the suggested multi-level modeling on this particular dataset has a very good repeated sampling property.
+\\
+
 The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j}))$, corresponding to $r=0$, makes parameters of the second-level distribution 0 (see (8)), and full shrinkage corresponds to $r=\infty$ that we cannot designate as an argument of \code{coverage} function.

### 2013-04-17 jss/article.tex
correction

@@
 
-The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j})=0)$, corresponding to $r=0$, makes the scale of the distribution go to $\infty$ (see (5)), and full shrinkage ($B_{j}=1$) corresponds to $r=\infty$ that we cannot designate as an argument of \code{coverage} function.
+The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j})=0)$, corresponding to $r=0$, makes the scale of the distribution go to $\infty$ (see (5)), and full shrinkage ($B_{j}=1$) makes $r$ goes to $\infty$, not appropriate for an argument.
 \\
@@
 However, achieving at least 95\% coverage at specific true values of ($r$ and $\beta$) does not mean that our model has good repeated sampling property.
-So, as we did in 6.1, we will see at least in terms of varying $r$ whether coverage probabilities are at least 0.95 when the true shrinkage value ($B(r)$) varies, fixing $\beta$ at estimated values.
+So, as we did in other examples, we will see whether coverage probabilities are at least 0.95 when the true shrinkage value ($B(r)$) varies, fixing $\beta$ at estimated values.
 Note that, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}.
@@
 This plot shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
-Considering that our model is approximating the true distribution of shrinkage by ADM (see 4.2), we finally conclude that the interval estimates from the suggested multi-level modeling on this particular dataset has a very good repeated sampling property.
+Note that even this result does not guarantee good repeated sampling property because $\beta$ was fixed.
+But, this result can definitely be an encouraging sign for our model's good repeated sampling property.
 \\

### 2013-04-17 jss/article.tex
any correction?

@@
 However, achieving at least 95\% coverage at specific true values of ($r$ and $\beta$) does not mean that our model has good repeated sampling property.
-So, as we did in other examples, we will see whether coverage probabilities are at least 0.95 when the true shrinkage value ($B(r)$) varies, fixing $\beta$ at estimated values.
+So, as we did in previous examples, we will see whether coverage probabilities are at least 0.95 when the true shrinkage value ($B(r)$) varies, fixing $\beta$ at estimated values.
 Note that, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}.

### 2013-04-17 jss/article.tex
corrections

@@
 \Abstract{Bayesian-frequentist reconciliation via Bayesian hierarchical modeling for Gaussian, Binomial, and Poisson data and frequentist method check for good coverage probability.}
-\Keywords{hierarchical model, multi-level model, random effects mixed model, method check, coverage probability, normal, binomial, poisson, shrinkage, \proglang{R}}
+\Keywords{hierarchical model, multilevel model, random effects mixed model, method check, coverage probability, normal, binomial, poisson, shrinkage, \proglang{R}}
 \Plainkeywords{keywords, comma-separated, not capitalized, r} %% without formatting
@@
 \section[Feasible Data Types]{Three Feasible Types of Data }
-This package is intended to fit a multi-level model on the group-level (or unit-level) data in which each group-level (or unit-level) observation is believed to have the Normal, Poisson, or Binomial distribution.
+This package is intended to fit a multilevel model on the group-level (or unit-level) data in which each group-level (or unit-level) observation is believed to have the Normal, Poisson, or Binomial distribution.
 In this section, we will introduce three specific types of feasible datasets.
@@
 
-\section[Multi-level Structure]{Multi-level Structure}
-Our multi-level model, also called a conditionally independent hierarchical model (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical sturucture in data.
+\section[Multilevel Structure]{Multilevel Structure}
+Our multilevel model, also called a conditionally independent hierarchical model (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical sturucture in data.
 For example, we can think about a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players.
 \code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter.
-Users can determine one of three types of multi-level models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets.
+Users can determine one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets.
 \\
@@
 For reference, a paramter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean.
-Also,  Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution, which is the same as (1) $\times$ (2) up to a normalizing constant.
+Also,  based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution, which is the same as (1) $\times$ (2) up to a normalizing constant.
 \begin{equation}
@@
 \end{equation}
-where $B_{j}\equiv\frac{\sigma^{2}_{j}}{\sigma^{2}_{j} + A},~j=1, \ldots, 8$, is called a shrinkages.
+where $B_{j}\equiv\sigma^{2}_{j}/(\sigma^{2}_{j} + A),~j=1, \ldots, 8$, are called shrinkages.
 
 \subsection[Poisson-Gamma]{Poisson-Gamma}
-\code{gbp} is also able to build a Poisson-Gamma multi-level model on the 31 hospital data.
+\code{gbp} is also able to build a Poisson-Gamma multilevel model on the 31 hospital data.
 Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket below indicates [mean, variance] of distribution.
@@
 \subsection[ADM]{Adjustment for Density Maximization}
-When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv\frac{\sigma^{2}}{\sigma^{2}+A}=B_{j}(A)$ for Gaussian and $B_{j}\equiv\frac{r}{r+n_{j}}=B_{j}(r)$ for Poisson and Binomial models.
+When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv\sigma^{2}/(\sigma^{2}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
 \\
@@
 But is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1?
-Why do we fit a logistic regression, such as logit($p$) = $x^{T}\beta$, instead of fitting a linear regression, $p = x^{T}\beta$?
+If it is, why do we fit a logistic regression, such as logit($p$) = $x^{T}\beta$, instead of fitting a linear regression, $p = x^{T}\beta+\epsilon$?
 \\
@@
 In the end, ADM  estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause.
-Please refer to Morris and Tang (2011) for more apparent advantages for using ADM.
+Please refer to Morris and Tang (2011) for more apparent advantages of ADM.
 \\
@@
 The model check is for the justification of a hierarchical modeling on a specific dataset.
-One possible question is, ``Can this dataset benefit from such a multi-level modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy.
+One possible question is, ``Can this dataset benefit from such a multilevel modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy.
 They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
@@
 
-Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates, the final product of this multi-level modeling.
+Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates, the final product of this multilevel modeling.
 ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point.
@@
 Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ because we know $r$ and $\beta$.
-Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is way more accurate than the previous one.
+Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is more accurate than the previous one.
+
 \section[Example]{Example}
@@
 
-The multi-level modeling that assumes a bigger population-level hierarchy will be insightful in this problem.
+The multilevel modeling that assumes a bigger population-level hierarchy will be insightful in this problem.
 Here, we presume a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY.
@@
 Assuming an additional hierarchy is reasonable, a model-fitting process begins.
-Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) looks relatively much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data.
-Next, \code{gbp} will help us fit the Poisson multi-level model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.02 ($\lambda_{0}=0.02$) as described in 3.2 .
+Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data.
+Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.02 ($\lambda_{0}=0.02$) as described in 3.2 .
 For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via any regression.
@@
 \end{CodeChunk}
-Since estimated $\alpha$ is -5.818, we can easily calculate $r=\textrm{exp}(5.818)=336$, which will be helpful for understanding how each shrinkage of hospital was determined by comparing this value to the amount of observed information ($n_{j}$).
+Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which will be helpful for understanding how each shrinkage was determined by comparing this value to the amount of observed information ($n_{j}$).
 \\
@@
 
-Intuitively, the result of multi-level modeling makes more sense than that of naive sample mean.
+Intuitively, the result of multilevel modeling makes more sense than that of naive sample mean.
 For example, suppose there are two hospitals, whose sample means ($z_{j} / n_{j}$) are 0 and 0.01 and caseloads ($n_{j}$) are 1 and 100 each.
@@
 Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload.
-Though somewhat extreme, this is what happens for the two left-most hostpitals on the first plot and this is why hierarchical modeling is a reasonable choice for this dataset.
+Though somewhat extreme, this is what happened to the two left-most hostpitals in the first plot and this is why hierarchical modeling is a reasonable choice for this dataset.
 \\
@@
 We can clearly see that all the posterior means (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line).
+For reference, if we want to draw this plot by the order of data input, \code{plot(p, sort = FALSE)} is a right adjustment.
 Overall, as the caseload (size of dots) increases towards the right and as the posterior mean gets closer to 0, the length of interval gets shorter, which the formula of posterior variance in (6) implies.
@@
 R>             })
-R> plot(shr, cov.save, type = "l", ylim = c(0.8, 1), xlab = "Shrinkage",
-R>      ylab ="", main = "Rao-Blackwellized Coverage Estimate", lwd = 3,
-R>      col = 2)
-R> abline(h = 0.95)
 \end{CodeInput}
@@
 
+We plotted \code{cov.save} on \code{shr}, connecting dots.
 This plot shows that the estimated shrinkages are at least 0.947 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
 Note that our model is approximating the true distribution of shrinkage by ADM (see 4.2).
-Considering this point, we finally conclude that the interval estimates from the suggested multi-level modeling on this particular dataset has a very good repeated sampling property.
+Considering this point, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular dataset has a very good repeated sampling property.
 \\
@@
 First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this dataset.
-Assuming this distribution, we know that the sample mean (MLE) has many nice properties, one of which is uniformly minimum variance unbiased estimator (UMVUE), and is the simplest way to estimate their true batting averages.
-Can we say this is the best way to predict their batting averages?
+Assuming this distribution, we know that the sample mean (MLE) is an uniformly minimum variance unbiased estimator (UMVUE) with nice properties.
+And it is the simplest one to estimate their true batting averages.
+But can we say this is the best way to predict their batting averages?
 \\
@@
 They showed that this estimator was more than three times efficient than the sample mean under squared error loss.
-On top of that, a few years later Morris (1983) introduced interval estimates that could successfully catch the batting averages over the remaining season, which the MLE and its interval estimate could not.
+On top of that, a few years later Morris (1983) introduced interval estimates that could successfully catch the batting averages over the remaining season, which MLE and its interval estimate could not.
 \\
@@
 This perspective considers true batting averages of outfielders as sampled from the one and those of other positions from the other.
-Our multi-level modeling provides a way to incorporate such information (covariate) seamlessly into the second-level hierarchy.
+Our multilevel modeling provides a way to incorporate such information (covariate) seamlessly into the second-level hierarchy.
 \begin{CodeChunk}
@@
 
-However, achieving at least 95\% coverage at specific true values of ($r$ and $\beta$) does not mean that our model has good repeated sampling property.
+However, achieving at least 95\% coverage at specific true values of $r$ and $\beta$ does not mean that our model has good repeated sampling property.
 So, as we did in previous examples, we will see whether coverage probabilities are at least 0.95 when the true shrinkage value ($B(r)$) varies, fixing $\beta$ at estimated values.
@@
 
-This plot shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
+We drew \code{cov.save} on \code{shr}, conneting dots.
+It shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
 Note that even this result does not guarantee good repeated sampling property because $\beta$ was fixed.

### 2013-04-17 jss/article.tex
adding school coverage pic

@@
 
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%R> shr <- seq(0.01, 0.99, length.out = 20)
+%R> A.trial <- mean(n) * (1 - shr) / shr
+%R> cov.save <- sapply (1 : length(A.trial), function(i){
+%R>               coverage(g, A.or.r = A.trial[i], reg.coef = 8.168, 
+%R>                        nsim = 500)$average.coverageRB
+%R>             })
+%\end{CodeInput}
+%\end{CodeChunk}
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width = 5.5cm]{school3.png}
+%\end{center}
+%\end{figure}
+
 \subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Prior Mean and One Covariate}
@@
 R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
-R>                        covariates = x1, nsim = 500)$average.coverageRB
+R>                        covariates = x, nsim = 500)$average.coverageRB
 R>             })

### 2013-04-17 jss/article.tex
change and rechange

@@
 
-We plotted \code{cov.save} on \code{shr}, connecting dots.
-This plot shows that the estimated shrinkages are at least 0.947 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
+We plotted \code{cov.save} on \code{shr}, connecting dots (coverage probabilities).
+This plot shows that the estimated shrinkages are at least 0.947 (under 95\% only at one shrinkage value, 0.01) on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
 Note that our model is approximating the true distribution of shrinkage by ADM (see 4.2).
-Considering this point, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular dataset has a very good repeated sampling property.
+Considering it, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular dataset has a very good repeated sampling property.
 \\

### 2013-04-17 jss/article.tex
print change

@@
 
-\subsection{Normal: 8 School Data}
+\subsection{Normal: 8 Schools Data}
 Education Testing Service conducted randomized experiments in eight separate schools and obtained this dataset.
@@
 \begin{CodeInput}
-R> y  <- c(28,  8, -3,  7, -1,  1, 18, 12)
-R> se <- c(15, 10, 16, 11,  9, 11, 10, 18)
+R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
+R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
 \end{CodeInput}
@@
 In the original paper, each school's coaching effect has approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
-So, it is reasonable to think that each (group-level) coaching effect is distributed as independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
+So, it is reasonable to think that each (group-level) coaching effect is distributed as an independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
 \pkg{Rgbp} includes this dataset and can be called by typing `\code{R> data(schools)}' on \proglang{R}.
 
-\subsection{Poisson: 31 Hospital Data}
+\subsection{Poisson: 31 Hospitals Data}
 This dataset is about the medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 (Morris and Lysy, 2012).
@@
 
-\subsection{Binomial: 18 Baseball Data}
+\subsection{Binomial: 18 Baseball Players Data}
 This dataset contains information about batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
-Also, it has two covariates, League and Position, showing in which league and in which position each player was playing.
-In this paper, we will use Position for a tutorial purpose.
+Also, it has one covariate, Position, showing in which position each player was playing.
 For convenience, we transform this variable into a binary indicator, which is 1 if a player was a outfielder and 0 otherwise.
@@
 \code{gbp} can construct a two-level Normal-Normal hierarchical model on the 8 school data.
-For reference,  $\sigma^{2}_{j}$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th school in the dataset.
+For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th school in the dataset.
 \begin{equation}
-y_{j}\vert \mu_{j} \stackrel{ind}{\sim}\textrm{Normal}(\mu_{j}, \sigma^{2}_{j}),
+y_{j}\vert \mu_{j} \stackrel{ind}{\sim}\textrm{Normal}(\mu_{j}, V_{j}),
 \end{equation}
@@
 In the end, ADM  estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause.
-Please refer to Morris and Tang (2011) for more apparent advantages of ADM.
+Refer to Morris and Tang (2011) for additional apparent advantages of ADM.
 \\
@@
 Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates, the final product of this multilevel modeling.
-``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point.
+``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to check this point.
 From now on, all the explanations will be based on the Binomial model.
@@
 
-\subsection{Unbiased Coverage Probability}
+\subsection{Simple Unbiased Estimates of Coverage Probabilities}
 Based on the generated pseudo-datasets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th player's interval estimate from $i$-th pseudo-dataset includes $p_{ij}$ and 0 otherwise.
@@
 
-\subsection{Rao-Blackwellized Coverage Probability}
+\subsection{Rao-Blackwellized Unbiased estimates of Coverage Probabilities}
 Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic.
@@
 For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths within a month of CABG surgeries and total number of patients receiving CABG surgeries in each hospital.
-In addition, while you were looking for such information, suppose you could know that the  state-level death rate per exposure of this surgery in the past ten years was 0.02.
+In addition, while you were looking for such information, suppose one knew that the state-level death rate per exposure of this surgery in the past ten years was 0.02.
 \\
@@
 If the second level has more information than the first level, then the sample mean shrinks towards the prior mean more than 50\%.
-This point is clear in the above output; as caseload increases, shrinkage decreases, depending less on the prior information.
+This point is clear in the above output; as caseload increases, shrinkage decreases, depending less on the prior distribution.
 \\
@@
 \end{CodeChunk}
-Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which will be helpful for understanding how each shrinkage was determined by comparing this value to the amount of observed information ($n_{j}$).
+Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which will be helpful for understanding how each shrinkage was determined by comparing this value to the observed sample sizes, $n_{j}$.
 \\

### 2013-04-17 Rgbp/R/gbp.R

@@ -77,7 +77,16 @@ print.gbp <- function(x, sort = TRUE, ...) {
     temp[, 3] <- round(temp[, 3], 2)
   }
 
-  cat("Summary for whole units: \n")
+  if (sort == TRUE) {
+    if (x$model == "gr") {
+      cat("Summary for each unit (sorted by se): \n")
+    } else {
+      cat("Summary for each unit (sorted by n): \n")
+    }
+  } else {
+    cat("Summary for each unit: \n")
+  }
+
   cat("\n")
   print(temp)
 }

### 2013-04-17 jss/article.tex
sigma -> V

@@
 \begin{equation}
-\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})\sigma^{2}_{j}),
+\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}),
 \end{equation}
-where $B_{j}\equiv\sigma^{2}_{j}/(\sigma^{2}_{j} + A),~j=1, \ldots, 8$, are called shrinkages.
+where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, 8$, are called shrinkages.
 
@@
 \subsection[ADM]{Adjustment for Density Maximization}
-When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv\sigma^{2}/(\sigma^{2}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
+When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
 \\

### 2013-04-18 jss/article.tex
reflecting on Carl's comments

@@
 
-\subsection{Normal: 8 Schools Data}
+\subsection{Normal: 8 Schools}
 Education Testing Service conducted randomized experiments in eight separate schools and obtained this dataset.
@@
 
-\subsection{Poisson: 31 Hospitals Data}
+\subsection{Poisson: 31 Hospitals}
 This dataset is about the medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 (Morris and Lysy, 2012).
@@
 
-\subsection{Binomial: 18 Baseball Players Data}
+\subsection{Binomial: 18 Baseball Hitters}
 This dataset contains information about batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
@@
 
-where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients.
-Note that if there is no covariate then $x_{j, (1\times1)}=1$ for an intercept term and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
-For reference, a paramter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean.
-Also,  based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution, which is the same as (1) $\times$ (2) up to a normalizing constant.
+where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $\beta$ and $A$ are unknown, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients.
+Note that if there is no covariate then $x_{j}=1$ for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
+For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean.
+Also,  based on this conjugate prior distribution, it is easy to derive the corresponding posterior distribution, which is the same as the product of two distributions, (1) $\times$ (2), up to a normalizing constant.
 \begin{equation}
@@
 
-where $\log(\lambda_{0j}) =x_{j}'\beta$, and $j=1, \ldots, 31$. Immediate posterior distribution of this Poisson-Gamma model is
+where $\log(\lambda_{0j}) =x_{j}'\beta$, $j=1, \ldots, 31$, with two unknown hyper-parameters, $r$ and $\beta$. Immediate posterior distribution of this Poisson-Gamma model is
 \begin{equation}
@@
 
-where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta~\textrm{and}~j=1, \ldots, 18$. Then, corresponding posterior distribution is
+where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, 18$. Note that $r$ and $\beta$ are two unknown hyper-parameters. Then, corresponding posterior distribution is
 \begin{equation}
@@
 \begin{equation}
-\beta \sim \textrm{Uniform on}~ \mathbf{R}^{m},~~A ~(\textrm{or}~ \frac{1}{r})\sim \textrm{Uniform}(0, \infty),
+\beta \sim \textrm{Uniform on}~ \mathbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
 \end{equation}
@@
 For $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases.
-Another flat prior on the second-level variance component  $A$ (or $1/r$) that we suggest here will guarantee a posterior propriety under moderate conditions and will bring a good repeated sampling property.
+The next flat prior on the second-level variance component  $A$ (or $1/r$) was chosen to bring a good repeated sampling property and for a posterior propriety under moderate conditions.
 \\
@@
 \subsection[Shrinkage Estimation]{Shrinkage Estimation}
-Estimating shrinkage is a key part of our hierarchical modeling.
+Estimating shrinkage is a key part of this hierarchical modeling.
 As we can see in (3), (6), and (9), the posterior means are a linear function of shrinkage and the posterior variances are also a linear (Gaussian), quadratic (Poisson), or cubic (Binomial) function of shrinkage.
@@
 In the end, ADM  estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause.
-Refer to Morris and Tang (2011) for additional apparent advantages of ADM.
+Please refer to Morris and Tang (2011) for additional advantages of ADM.
 \\
@@
 
-\section[Method Check]{Method Check}
+\section[Method Checking]{Method Checking}
 Like the two sides of the same coin, checking a statistical model always comes with fitting a model.
@@
 ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to check this point.
-From now on, all the explanations will be based on the Binomial model.
+From now on, all the explanations will be based on the Binomial model because the idea is the same and can be easily applied to the other two models.
 
@@
 Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ because we know $r$ and $\beta$.
-Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is more accurate than the previous one.
+Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.
 
@@
 For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths within a month of CABG surgeries and total number of patients receiving CABG surgeries in each hospital.
-In addition, while you were looking for such information, suppose one knew that the state-level death rate per exposure of this surgery in the past ten years was 0.02.
+In addition, while one looks for such information, suppose one knows that the state-level death rate per exposure of this surgery is 0.020.
 \\
@@
 Here, we presume a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY.
-This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution whose mean is 0.02.
+This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution whose mean is 0.020.
 For reference, a model check can be useful for evaluating the validity of such a view point (Christiansen and Morris, 1996).
@@
 Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data.
-Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.02 ($\lambda_{0}=0.02$) as described in 3.2 .
+Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in 3.2 .
 For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via any regression.
@@
 If the second level has more information than the first level, then the sample mean shrinks towards the prior mean more than 50\%.
-This point is clear in the above output; as caseload increases, shrinkage decreases, depending less on the prior distribution.
+This point is clear in the above output because, as caseload increases, shrinkage decreases, depending less on the prior distribution.
 \\
@@
 \end{CodeChunk}
-Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which will be helpful for understanding how each shrinkage was determined by comparing this value to the observed sample sizes, $n_{j}$.
+Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which will be helpful for understanding how each shrinkage was estimated.
+For example,  the shrinkage estimate of the last hospital ($\hat{B}_{31}= 0.201$) whose observed sample size is 1340,  was calculated by 336 / (336 + 1340).
 \\
@@
 Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 from the Rao-Blackwellized estimate and 0.95 from the unbiased estimate.
+Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular dataset has a very good repeated sampling property.
 \\
 
-These numbers are encouraging, but achieving at least 95\% coverage at one specific true value does not mean that our model has good repeated sampling property.
-We need to check whether coverage probabilities are at least 0.95 when the true parameter value ($r$) varies.
+%These numbers are encouraging, but achieving at least 95\% coverage at %one specific true value does not mean that our model has good repeated %sampling property.
+We need to check whether coverage probabilities are %at least 0.95 when the true parameter value ($r$) varies.
 
-\begin{CodeChunk}
-\begin{CodeInput}
-R> shr <- seq(0.01, 0.99, length.out = 20)
-R> r.trial <- mean(n) * shr / (1 - shr)
-R> cov.save <- sapply (1 : length(r.trial), function(i){
-R>               coverage(p, A.or.r = r.trial[i], mean.PriorDist = 0.02, 
-R>                        nsim = 500)$average.coverageRB
-R>             })
-\end{CodeInput}
-\end{CodeChunk}
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width = 5.5cm]{hospital3.png}
-\end{center}
-\end{figure}
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%R> shr <- seq(0.01, 0.99, length.out = 20)
+%R> r.trial <- mean(n) * shr / (1 - shr)
+%R> cov.save <- sapply (1 : length(r.trial), function(i){
+%R>               coverage(p, A.or.r = r.trial[i], mean.PriorDist = 0.02, 
+%R>                        nsim = 500)$average.coverageRB
+%R>             })
+%\end{CodeInput}
+%\end{CodeChunk}
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width = 5.5cm]{hospital3.png}
+%\end{center}
+%\end{figure}
 
-We plotted \code{cov.save} on \code{shr}, connecting dots (coverage probabilities).
-This plot shows that the estimated shrinkages are at least 0.947 (under 95\% only at one shrinkage value, 0.01) on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
-Note that our model is approximating the true distribution of shrinkage by ADM (see 4.2).
-Considering it, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular dataset has a very good repeated sampling property.
-\\
+%We plotted \code{cov.save} on \code{shr}, connecting dots (coverage %probabilities).
+This plot shows that the estimated shrinkages are at least %0.947 (under 95\% only at one shrinkage value, 0.01) on the tried range %of true shrinkage values, slightly deviating from the definition of 95\% %confidence interval.
+Note that our model is approximating the true %distribution of shrinkage by ADM (see 4.2).
 
@@
 It makes sense because shrinkage ($B_{j}\equiv r / (r+n_{j})$) is determined by the relative amount of information between the first-level and the second-level hierarchies.
-The fact that all players have the same amount of observed information ($n_{j}=45$) and the estimated $r=\textrm{exp}(4.727)=113$ from below summary tell why the estimated shrinkage is 0.715.
+The fact that all players have the same amount of observed information ($n_{j}=45$) and $\hat{r}=\textrm{exp}(4.727)=113$ from below summary tell why the estimated shrinkage is 0.715 (=113 / (113 + 45)).
 \\
 
-As for the point estimates, we calculated squared error losses, $\sum_{j=1}^{18}(p_{j, remaining}-\hat{p}_{j})^{2}$, for three estimators, James-Stein (JS), ours, and sample mean.
-These values were 0.027, 0.031, and 0.086 each.
-Ours could not beat the JS that shrank all sample means towards one common estimated prior mean.
-But ours, which provides a more flexible way to model these data, was not much worse than JS and way better than sample mean under the squared error loss.
+For reference, we can run the Normal hierarchical model using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
+As for the point estimates, we calculated squared error losses, $\sum_{j=1}^{18}(p_{j, remaining}-\hat{p}_{j})^{2}$, using the estimates from the Binomial and Normal multilevel models and also using the sample mean (MLE).
+These values were 0.042, 0.043, and 0.086 each.
+Note that estimates from the Normal and Binomial models are twice better than MLE in terms of squared error loss.
+For reference, the shrinkage estimate of the Normal model was 0.708 slightly less than that of the Binomial.
 \\
@@
 Let's see shrinkage and 95\% interval plots for more intuition.
-It is obvious that sample means (empty dots) on the upper line shrink towards two different means, 0.31 and 0.23.
+It is obvious that sample means (empty dots) on the upper line shrink towards two different means, 0.310 and 0.233.
 For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
 For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper line, there are short red lines toward five directions.
-It also means that the seemingly two lines crossing over others were actually three lines.
+This symbol also means that the seemingly two lines crossing over others were actually three lines for those who were outfielders (10th, 14th, and 15th hitters) with observed batting averages far lower than the top five hitters.
+\\
+
+Note that the observed sample mean among outfielders is 0.308 and that among other positions is 0.231.
+But why are the estimated two prior means from this Binomial model 0.310 and 0.233 each?
+This can be attributed to the logistic regression which estimates prior mean by a non-linear logit function of $x'\beta$, causing a small bias (see 3.3).
+The Normal model can avoid this small bias because it uses a linear regression to estimate those prior means.
 \\
@@
 
-The plot seems to indicate overcoverage.
-The estimated overall coverage probability is 0.974 based on the unbiased estimator and 0.973 based on the Rao-Blackwellization, at least satisfying the definition of the 95\% confidence interval.
+The meaning of putting the \code{gbo} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values for generating pseudo-datasets.
 \\
 
-However, achieving at least 95\% coverage at specific true values of $r$ and $\beta$ does not mean that our model has good repeated sampling property.
+Finally, the estimated average coverage probability is 0.973 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval. 
+\\
+
+%However, achieving at least 95\% coverage at specific true values of $r$ and $\beta$ does not mean that our model has good repeated sampling property.
 So, as we did in previous examples, we will see whether coverage probabilities are at least 0.95 when the true shrinkage value ($B(r)$) varies, fixing $\beta$ at estimated values.
@@
 
-\begin{CodeChunk}
-\begin{CodeInput}
-R> shr <- seq(0.01, 0.99, length.out = 20)
-R> r.trial <- mean(n) * shr / (1 - shr)
-R> cov.save <- sapply (1 : length(r.trial), function(i){
-R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
-R>                        covariates = x, nsim = 500)$average.coverageRB
-R>             })
-\end{CodeInput}
-\end{CodeChunk}
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width = 5.5cm]{baseball4.png}
-\end{center}
-\end{figure}
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%R> shr <- seq(0.01, 0.99, length.out = 20)
+%R> r.trial <- mean(n) * shr / (1 - shr)
+%R> cov.save <- sapply (1 : length(r.trial), function(i){
+%R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
+%R>                        covariates = x, nsim = 500)$average.coverageRB
+%R>             })
+%\end{CodeInput}
+%\end{CodeChunk}
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width = 5.5cm]{baseball4.png}
+%\end{center}
+%\end{figure}
 
-We drew \code{cov.save} on \code{shr}, conneting dots.
+%We drew \code{cov.save} on \code{shr}, conneting dots.
 It shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
@@
 But, this result can definitely be an encouraging sign for our model's good repeated sampling property.
-\\
 
-The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j}))$, corresponding to $r=0$, makes parameters of the second-level distribution 0 (see (8)), and full shrinkage corresponds to $r=\infty$ that we cannot designate as an argument of \code{coverage} function.
-\\
+%The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j}))$, corresponding to $r=0$, makes parameters of the second-level distribution 0 (see (8)), and full shrinkage corresponds to $r=\infty$ that we cannot designate as an argument of \code{coverage} function.
 
 \section[Discussion]{Discussion}
-
+Bayes vs Freq, post.mean vs estimate, post.sd vs estimated standard error.
 \section[acknowledgments]{Acknowledgments}

### 2013-04-18 Rgbp.Rcheck/Rgbp-Ex.R
R manual correction

@@ -31,8 +31,8 @@ flush(stderr()); flush(stdout())
   z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
   n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
 
-  # One covariate: 1 if a player is in the National league
-  x1 <- c(1, 0, 0, 0, 0, 0, 1, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, 1)
+  # One covariate: 1 if a player is an outfielder and 0 otherwise
+  x1 <- c(1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0)
 
   ################################################################
   # Gaussian Regression Interactive Multilevel Modeling (GRIMM) #
@@ -328,8 +328,8 @@ flush(stderr()); flush(stdout())
   z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
   n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
 
-  # One covariate: 1 if a player is in the National league
-  x1 <- c(1, 0, 0, 0, 0, 0, 1, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, 1)
+  # One covariate: 1 if a player is an outfielder and 0 otherwise
+  x1 <- c(1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0)
   
   #################################################################
   # Gaussian Regression Interactive Multi-level Modeling (GRIMM) #
@@ -527,12 +527,12 @@ flush(stderr()); flush(stdout())
   # Arbitrary covariate for schools data
   x2 <- rep(c(-1, 0, 1, 2), 2)
   
-  # Baseball data where z is Hits and n is AtBats
+  # baseball data where z is Hits and n is AtBats
   z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
   n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
 
[…]

### 2013-04-19 jss/article.tex
change

@@
 Taking the Normal model as an example,  $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Adam's law and $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Eve's law.
-Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are a function of shrinkage in (3) and Adam's and Eve's laws are taking conditional expectation and variance over them given data.
+Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are a function of shrinkage (see (3)) and Adam's and Eve's laws are taking conditional expectation and variance over them given data, $\textbf{y}$.
+Since we have already estimated $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, fianlly we can estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.
 
 \subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
-After estimating two posterior moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, \code{gbp} reasonably approximates a posterior distribution given data, \emph{i.e.}, $p_{j}\vert \textbf{z}$ (or $\mu_{j}\vert \textbf{y}$, $\lambda_{j}\vert \textbf{z}$), by matching these two moments with its parameters.
-To be specific, we assumed $p_{j}\vert \textbf{z}$ had another Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.
+After estimating two posterior moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$ for the Binomial model, \code{gbp} reasonably approximates a posterior distribution given data, \emph{i.e.}, $p_{j}\vert \textbf{z}$ (or $\mu_{j}\vert \textbf{y}$, $\lambda_{j}\vert \textbf{z}$), by matching these two moments with its parameters.
+To be specific, we assumed $p_{j}\vert \textbf{z}$ had another Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, with two parameters, $a_{1}$ and $a_{0}$, of this assumed Beta distribution.
 
@@
 First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this dataset.
-Assuming this distribution, we know that the sample mean (MLE) is an uniformly minimum variance unbiased estimator (UMVUE) with nice properties.
+Assuming this distribution, we know that the sample mean (MLE) is an uniformly minimum variance unbiased estimator (UMVUE) with nice asymptotic properties.
 And it is the simplest one to estimate their true batting averages.
@@
 
-The meaning of putting the \code{gbo} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values for generating pseudo-datasets.
+The meaning of putting the \code{gbp} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values for generating pseudo-datasets.
 \\

### 2013-05-01 jss/article.tex
changes

@@
 \section[Feasible Data Types]{Three Feasible Types of Data }
-This package is intended to fit a multilevel model on the group-level (or unit-level) data in which each group-level (or unit-level) observation is believed to have the Normal, Poisson, or Binomial distribution.
-In this section, we will introduce three specific types of feasible datasets.
+This package is intended to fit a multilevel model on the group-level (or unit-level) data in which each group-level observation is believed to have the Normal, Poisson, or Binomial distribution.
+In this section, we will introduce three specific types of feasible data sets.
 
 \subsection{Normal: 8 Schools}
-Education Testing Service conducted randomized experiments in eight separate schools and obtained this dataset.
+Education Testing Service conducted randomized experiments in eight separate schools and obtained this data set.
 It contains the coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of eight schools obtained after an analysis of covariance adjustment (Rubin, 1981).
@@
 In the original paper, each school's coaching effect has approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
-So, it is reasonable to think that each (group-level) coaching effect is distributed as an independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
-\pkg{Rgbp} includes this dataset and can be called by typing `\code{R> data(schools)}' on \proglang{R}.
+So, it is reasonable to think that each school-level coaching effect is distributed as an independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
+\pkg{Rgbp} includes this data set and can be called by typing `\code{R> data(schools)}' on \proglang{R}.
 
 \subsection{Poisson: 31 Hospitals}
-This dataset is about the medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 (Morris and Lysy, 2012).
+This data set is about the medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 (Morris and Lysy, 2012).
 It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$).
@@
 Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger) and $\lambda_{j}$ as a true death rate per exposure.
-This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.
+This data set is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.
 
 \subsection{Binomial: 18 Baseball Hitters}
-This dataset contains information about batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
+This data set contains information about batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
 Also, it has one covariate, Position, showing in which position each player was playing.
@@
 The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown true batting average $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
-This dataset is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.
+This data set is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.
 
@@
 \code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter.
-Users can determine one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets.
+Users can determine one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their data sets.
 \\
@@
 \code{gbp} can construct a two-level Normal-Normal hierarchical model on the 8 school data.
-For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th school in the dataset.
+For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th school in the data set.
 \begin{equation}
@@
 For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean.
-Also,  based on this conjugate prior distribution, it is easy to derive the corresponding posterior distribution, which is the same as the product of two distributions, (1) $\times$ (2), up to a normalizing constant.
+Also,  based on this conjugate prior distribution, it is easy to derive the corresponding posterior distribution, which is the same as the product of two distributions, (1) and (2), up to a normalizing constant.
 \begin{equation}
@@
 For $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases.
-The next flat prior on the second-level variance component  $A$ (or $1/r$) was chosen to bring a good repeated sampling property and for a posterior propriety under moderate conditions.
+The next flat prior distribution of the second-level variance component $A$ (or $1/r$) was chosen to bring a good repeated sampling property and for a posterior propriety under moderate conditions.
 \\
@@
 In this case, the most common way is to obtain an MLE of the variance component with its asymptotic Normality and then to use Delta method for asymptotic Normal distribution of shrinkage, \emph{i.e.}, $\hat{B}_{j, MLE}=B_{j}(\hat{A}_{MLE})$.
-But is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1?
+But, is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1?
 If it is, why do we fit a logistic regression, such as logit($p$) = $x^{T}\beta$, instead of fitting a linear regression, $p = x^{T}\beta+\epsilon$?
@@
 Taking the Normal model as an example,  $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Adam's law and $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Eve's law.
-Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are a function of shrinkage (see (3)) and Adam's and Eve's laws are taking conditional expectation and variance over them given data, $\textbf{y}$.
+Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are functions of shrinkage (see (3)) and Adam's and Eve's laws are taking conditional expectation and variance over them given data, $\textbf{y}$.
 Since we have already estimated $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, fianlly we can estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.
@@
 There are two kinds of model justification process; one is a model check and the other is a method check.
-The model check is for the justification of a hierarchical modeling on a specific dataset.
-One possible question is, ``Can this dataset benefit from such a multilevel modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy.
+The model check is for the justification of a hierarchical modeling on a specific data set.
+One possible question is, ``Can this data set benefit from such a multilevel modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy.
 They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
@@
 Suppose we sampled 500 $\mathbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\mathbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (8), where $r$ and $\beta$ are given.
-Then, we can also generate $\{\mathbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-dataset and $j$ does $j$-th player.
+Then, we can also generate $\{\mathbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-data set and $j$ does $j$-th player.
 Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\mathbf{z}^{(i)}_{(18\times1)}, \mathbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500$\times$18 interval estimates.
@@
 \subsection{Simple Unbiased Estimates of Coverage Probabilities}
-Based on the generated pseudo-datasets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th player's interval estimate from $i$-th pseudo-dataset includes $p_{ij}$ and 0 otherwise.
+Based on the generated pseudo-data sets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th player's interval estimate from $i$-th pseudo-data set includes $p_{ij}$ and 0 otherwise.
 One way to estimate the coverage probability is taking average over these indicator variables.
-We call it an unbiased coverage probability estimate.
+We call it a simple unbiased coverage probability estimate.
 For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first player.
@@
 \subsection{Rao-Blackwellized Unbiased estimates of Coverage Probabilities}
-Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic.
-This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates on the $i$-th dataset.
+Rao-Blackwellization improves accuracy of an unbiased estimator by taking conditional expectation given a sufficient statistic.
+Based on this idea, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic.
+This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates on the $i$-th data set.
 We can calculate this probability  because we know the distribution of $p_{ij} \vert z_{ij}, r, \beta$ in (9).
-Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ because we know $r$ and $\beta$.
+Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ as long as $r$ and $\beta$ are known.
 Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.
 
-\section[Example]{Example}
+\section[Examples]{Examples}
 \subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
@@
 Assuming an additional hierarchy is reasonable, a model-fitting process begins.
-Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data.
+Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital, the Poisson distribution would be our first choice to describe the uncertainty in our data.
 Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in 3.2 .
-For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via any regression.
+For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression (see section 3.2).
 \begin{CodeChunk}
@@
 \begin{CodeOutput}
-Summary for whole observations:
+Summary for each unit (sorted by n):
 
@@
 
-The output contains information about sample mean (\code{obs.mean}), caseload (\code{n}), known prior mean ($\lambda_{0}$), shrinkage ($B_{j}$), lower interval, posterior mean ($E(\lambda_{j}\vert \textbf{z})$), upper interval, and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{z})$).
+The output contains information about sample mean (\code{obs.mean}), caseload (\code{n}), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower interval, posterior mean ($E(\lambda_{j}\vert \textbf{z})$), upper interval, and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{z})$).
 \\
@@
 On top of that, more specific estimation results, such as the estimation result of $\alpha\equiv\log(1/r)$, follow.
-Note that when we do not know the prior mean in advance unlike this hospital problem, \code{gbp} fits a regression model and the summary of regression fit will appear.
+Note that when we do not know the prior mean in advance unlike this hospital problem, \code{gbp} fits a linear regression for the Normal model, a log-linear regression for the Poisson model, or a logistic regression for the Binomial model and a summary of regression fit will appear.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
-Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which will be helpful for understanding how each shrinkage was estimated.
-For example,  the shrinkage estimate of the last hospital ($\hat{B}_{31}= 0.201$) whose observed sample size is 1340,  was calculated by 336 / (336 + 1340).
+Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which is a good indicator of how valuable and informative the hypothetical second-level hierarchy is.
+Note that $r$ can be interpreted as the amount of prior information, although we do not know its true value.
+So, \code{gbp} asked data how much credit they wanted to give to this hypothetical second-level hierarchy.
+$\hat{r}$ = 336 is the answer from the data.
+It means that observed sample means of hospitals whose caseloads are less than 336 will shrink toward the prior mean (0.020) more than 50\%.
+\\
+
+For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.834$) was calculated by 336 / (336 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.834)*0.045 + 0.834 * 0.020=0.024$.
+As for this hospital, using more information from the prior distribution makes sense because its observed amount of information (67) is far less than the amount of state-level information (336).
 \\
@@
 Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload.
-Though somewhat extreme, this is what happened to the two left-most hostpitals in the first plot and this is why hierarchical modeling is a reasonable choice for this dataset.
+Though somewhat extreme, this is what happened to the two left-most hostpitals in the first plot and this is why hierarchical modeling is a reasonable choice for this data set.
 \\
@@
 The following method check will answer this question.
-The \code{coverage} function below generates 10,000 pseudo-datasets assuming the estimated $r~(=336.37)$ as a given value.
+The \code{coverage} function below generates 10,000 pseudo-data sets assuming the estimated $r~(=336.37)$ as a given value.
 For reference, we can try any other value of $r$, for example $r=200$, by replacing below code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
@@
 Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 from the Rao-Blackwellized estimate and 0.95 from the unbiased estimate.
-Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular dataset has a very good repeated sampling property.
+Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular data set has a very good repeated sampling property.
 \\
@@
 How could you predict?
-For reference, the dataset  \code{baseball} has each player's batting average over the remaining season.
+For reference, the data set  \code{baseball} has each player's batting average over the remaining season.
 \\
 
-First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this dataset.
+First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this data set.
 Assuming this distribution, we know that the sample mean (MLE) is an uniformly minimum variance unbiased estimator (UMVUE) with nice asymptotic properties.
@@
 
-The meaning of putting the \code{gbp} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values for generating pseudo-datasets.
+The meaning of putting the \code{gbp} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values for generating pseudo-data sets.
 \\

### 2013-05-01 Rgbp/R/coverage.R

@@ -340,13 +340,13 @@ coverage <- function(gbp.object, A.or.r, reg.coef, covariates, mean.PriorDist, n
   if (is.na(gbp.object$prior.mean)){
     if (gbp.object$model == "gr") {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dashed Line: (Unbiased)",
+                             "Blue Dashed Line: (Simple Unbiased)",
                              paste("A =", round(A, 2)), 
                              paste("beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     } else {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dashed Line: (Unbiased)",
+                             "Blue Dashed Line: (Simple Unbiased)",
                              paste("r =", round(r, 2)), 
                              paste("beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
@@ -354,12 +354,12 @@ coverage <- function(gbp.object, A.or.r, reg.coef, covariates, mean.PriorDist, n
   } else {  # if prior mean is assigned
     if (gbp.object$model == "gr") {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dashed Line: (Unbiased)",
+                             "Blue Dashed Line: (Simple Unbiased)",
                              paste("A =", round(A, 2)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     } else {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dashed Line: (Unbiased)",
+                             "Blue Dashed Line: (Simple Unbiased)",
                              paste("r =", round(r, 2)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     }

### 2013-05-01 jss/article.tex
changes

@@
 If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery.
-On top of that, if you can figure out each hospital's abililty to handle this surgery, it will be useful for your decision to choose a hospital.
+On top of that, if you can figure out each hospital's abililty to handle this surgery, it will be useful for your decision in choosing a hospital.
 \\
@@
 For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.834$) was calculated by 336 / (336 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.834)*0.045 + 0.834 * 0.020=0.024$.
-As for this hospital, using more information from the prior distribution makes sense because its observed amount of information (67) is far less than the amount of state-level information (336).
+As for this hospital, using more information from the prior distribution is a sensible choice because its observed amount of information (67) is far less than the amount of state-level information (336).
 \\
@@
 Intuitively, the result of multilevel modeling makes more sense than that of naive sample mean.
-For example, suppose there are two hospitals, whose sample means ($z_{j} / n_{j}$) are 0 and 0.01 and caseloads ($n_{j}$) are 1 and 100 each.
-Do you believe that the former hospital is better than the latter and are you going to choose the former hospital?
+For example, suppose there are two hospitals, whose sample means ($z_{j} / n_{j}$) are 0 and 0.001 and caseloads ($n_{j}$) are 1 and 1000 each.
+Do you believe that the former hospital, whose observed death rate is 0, is better than the latter and are you going to choose the former hospital?
 Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload.
@@
 For reference, if we want to draw this plot by the order of data input, \code{plot(p, sort = FALSE)} is a right adjustment.
-Overall, as the caseload (size of dots) increases towards the right and as the posterior mean gets closer to 0, the length of interval gets shorter, which the formula of posterior variance in (6) implies.
-But the most important information from this plot would be the visualized range of each hospital's true death rate per exposure.
+Overall, as the caseload increases towards the right and as the posterior mean gets closer to 0, the length of interval gets shorter, which the formula of posterior variance in (6) implies.
 \\
 
-This plot can add one more valuable point, which we could not have noticed, to the previous plot based mostly on point estimates.
+This interval plot can give us one more valuable insight, which we could not have noticed.
 Let's look at the 8th and the 31st hospitals on the graph (or on the outcome for numeric reference).
@@
 The following method check will answer this question.
-The \code{coverage} function below generates 10,000 pseudo-data sets assuming the estimated $r~(=336.37)$ as a given value.
+The \code{coverage} function below generates 10,000 pseudo-data sets regarding the estimated $r~(=336.37)$ as a given true value.
 For reference, we can try any other value of $r$, for example $r=200$, by replacing below code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
@@
 
-Also, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is \code{R> p <- gbp(z, n, Alpha = 0.9, model = "pr")}.
+Also, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is \code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "pr")}.
 Then, the function \code{coverage} will evaluate whether interval estimates achieve 90\% confidence level.
@@
 
-It estimated coverage probabilities by unbiased estimates (a blue dashed line) and Rao-Blackwellized estimates (a red line).
-Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 from the Rao-Blackwellized estimate and 0.95 from the unbiased estimate.
-Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular data set has a very good repeated sampling property.
+It estimated coverage probabilities by simple unbiased estimates (a blue dashed line) and Rao-Blackwellized unbiased estimates (a red line).
+Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 from the Rao-Blackwellized estimate and 0.95 from the simple unbiased estimate.
+Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular data set has nice repeated sampling property.
 \\

### 2013-05-01 Rgbp.Rcheck/Rgbp-Ex.R

@@ -18,7 +18,6 @@ flush(stderr()); flush(stdout())
 ### ** Examples
 
 
-
   # Loading datasets
   data(schools)
   y <- schools$y

### 2013-05-01 Rgbp/R/coverage.R

@@ -340,13 +340,13 @@ coverage <- function(gbp.object, A.or.r, reg.coef, covariates, mean.PriorDist, n
   if (is.na(gbp.object$prior.mean)){
     if (gbp.object$model == "gr") {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dashed Line: (Simple Unbiased)",
+                             "Blue Dashed Line: (Simple)",
                              paste("A =", round(A, 2)), 
                              paste("beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     } else {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dashed Line: (Simple Unbiased)",
+                             "Blue Dashed Line: (Simple)",
                              paste("r =", round(r, 2)), 
                              paste("beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
@@ -354,12 +354,12 @@ coverage <- function(gbp.object, A.or.r, reg.coef, covariates, mean.PriorDist, n
   } else {  # if prior mean is assigned
     if (gbp.object$model == "gr") {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dashed Line: (Simple Unbiased)",
+                             "Blue Dashed Line: (Simple)",
                              paste("A =", round(A, 2)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     } else {
       legend("bottomleft", c("Red Line: Rao-Blackwellized",
-                             "Blue Dashed Line: (Simple Unbiased)",
+                             "Blue Dashed Line: (Simple)",
                              paste("r =", round(r, 2)), 
                              paste("AvgCoverage =", avr.cov, "(", avr.cov2, ")")))
     }

### 2013-05-01 jss/article.tex
changes

@@
 For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.834$) was calculated by 336 / (336 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.834)*0.045 + 0.834 * 0.020=0.024$.
-As for this hospital, using more information from the prior distribution is a sensible choice because its observed amount of information (67) is far less than the amount of state-level information (336).
+As for this hospital, using more information from the prior distribution is an appropriate choice because its observed amount of information (67) is far less than the amount of state-level information (336).
 \\
@@
 It estimated coverage probabilities by simple unbiased estimates (a blue dashed line) and Rao-Blackwellized unbiased estimates (a red line).
-Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 from the Rao-Blackwellized estimate and 0.95 from the simple unbiased estimate.
+Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate and 0.951 from the simple unbiased estimate.
 Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular data set has nice repeated sampling property.
@@
 
-The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j})=0)$, corresponding to $r=0$, makes the scale of the distribution go to $\infty$ (see (5)), and full shrinkage ($B_{j}=1$) makes $r$ goes to $\infty$, not appropriate for an argument.
-\\
+%The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j})=0)$, corresponding to $r=0$, makes the scale of the distribution go to $\infty$ (see (5)), and full shrinkage ($B_{j}=1$) makes $r$ goes to $\infty$, not appropriate for an argument.
 
@@
 \begin{CodeOutput}
-Summary for whole units:
+Summary for each unit (sorted by n):
 
@@
 First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this data set.
-Assuming this distribution, we know that the sample mean (MLE) is an uniformly minimum variance unbiased estimator (UMVUE) with nice asymptotic properties.
-And it is the simplest one to estimate their true batting averages.
+And we know that the sample mean (MLE) under this distribution is an uniformly minimum variance unbiased estimator (UMVUE) with nice asymptotic properties.
+It is also the simplest way to estimate their true batting averages.
 But can we say this is the best way to predict their batting averages?
@@
 Our hierarchical modeling is a sequel to these researches, which can add one more unique value.
-Suppose you strongly believe that the outfielder's batting averages should be different from other positions' ones, not giving a credit to the assumption that all players' batting averages shrink towards the same mean.
+Suppose you strongly believe that the outfielder's batting averages are different from other positions' ones, not giving a credit to the assumption that all players' batting averages shrink towards the same mean.
 Instead, you want to assume two different second-level hierarchies for outfielders and for other positions, within each of which sharing information and regressing toward the mean (RTTM) occur.
@@
 \end{CodeChunk}
-Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.31 and 0.23.
+Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233.
 Also note that shrinkage estimates are the same for all players.
@@
 For reference, we can run the Normal hierarchical model using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
-As for the point estimates, we calculated squared error losses, $\sum_{j=1}^{18}(p_{j, remaining}-\hat{p}_{j})^{2}$, using the estimates from the Binomial and Normal multilevel models and also using the sample mean (MLE).
+For comparison, we calculated squared error losses, $\sum_{j=1}^{18}(p_{j, remaining}-\hat{p}_{j})^{2}$, using the estimates from the Binomial and Normal multilevel models and also using the sample mean (MLE).
 These values were 0.042, 0.043, and 0.086 each.
 Note that estimates from the Normal and Binomial models are twice better than MLE in terms of squared error loss.
-For reference, the shrinkage estimate of the Normal model was 0.708 slightly less than that of the Binomial.
 \\
@@
 This can be attributed to the logistic regression which estimates prior mean by a non-linear logit function of $x'\beta$, causing a small bias (see 3.3).
-The Normal model can avoid this small bias because it uses a linear regression to estimate those prior means.
+The Normal model can avoid this small bias because it uses a linear regression to estimate these prior means.
 \\
 
-The 95\% interval plot shows us range of true batting average for each player.
-Note that observed sample means are all within the interval estimates.
+The 95\% interval plot shows us range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups.
+Let's see the 10th, 14th, and 15th players on the graph for example.
+They are outfielders but their batting averages (sample mean) are far worse than the first five outfielders.
+RTTM means that it can happen by their bad luck though in the long run their batting averages will come back to their expected ones as outfielders (blue horizontal line).
+The fact that their sample means are located at the lower part of their 95\% intervals supports this argument.
+So, their posterior means (red dots) can also be interpreted as their RTTM.
+\\
+
+One more thing to emphasize is that observed sample means are all within the interval estimates.
 And these interval estimates also catched the batting averages over the ramaining season successfully, although the result was left out.

### 2013-05-01 jss/article.tex
corrections

@@
 Education Testing Service conducted randomized experiments in eight separate schools and obtained this data set.
-It contains the coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of eight schools obtained after an analysis of covariance adjustment (Rubin, 1981).
+It contains the coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of eight schools (Rubin, 1981).
 \begin{CodeChunk}
@@
 
-In the original paper, each school's coaching effect has approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
+Each school's coaching effect has approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
 So, it is reasonable to think that each school-level coaching effect is distributed as an independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
@@
 where $m$ is the number of regression coefficients.
-For $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases.
+As for $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases.
 The next flat prior distribution of the second-level variance component $A$ (or $1/r$) was chosen to bring a good repeated sampling property and for a posterior propriety under moderate conditions.
@@
 Assuming an additional hierarchy is reasonable, a model-fitting process begins.
-Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital, the Poisson distribution would be our first choice to describe the uncertainty in our data.
+Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital, the Poisson distribution would be the first choice to describe the uncertainty in our data.
 Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in 3.2 .
@@
 Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which is a good indicator of how valuable and informative the hypothetical second-level hierarchy is.
-Note that $r$ can be interpreted as the amount of prior information, although we do not know its true value.
+As mentioned before, $r$ can be interpreted as the amount of prior information, although we do not know its true value.
 So, \code{gbp} asked data how much credit they wanted to give to this hypothetical second-level hierarchy.
@@
 Does our procedure to generate interval estimates have good repeated sampling property?
-The following method check will answer this question.
+The following method checking will answer this question.
 The \code{coverage} function below generates 10,000 pseudo-data sets regarding the estimated $r~(=336.37)$ as a given true value.
@@
 For reference, we can run the Normal hierarchical model using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
-For comparison, we calculated squared error losses, $\sum_{j=1}^{18}(p_{j, remaining}-\hat{p}_{j})^{2}$, using the estimates from the Binomial and Normal multilevel models and also using the sample mean (MLE).
-These values were 0.042, 0.043, and 0.086 each.
-Note that estimates from the Normal and Binomial models are twice better than MLE in terms of squared error loss.
+For comparison, we calculated squared error losses, $\sum_{j=1}^{18}(p_{j, remaining}-\hat{p}_{j})^{2}$, where $p_{j, remaining}$ is each player's batting average over the remaining season and $\hat{p}_{j}$ is estimate from the Binomial and Normal multilevel models and from the sample mean (MLE) using the first 45 at-bats.
+These values were 0.042, 0.043, and 0.086 each, indicating that estimates from the Normal and Binomial models are twice better than MLE in terms of squared error loss.
 \\
@@
 Let's see its formula in (9).
-We can notice that the estimated posterior mean is one factor that determines posterior variance because every player has the same at-bats ($n_{j}$) and $r$.
+We can notice that the estimated posterior mean is a critical factor that makes posterior variances different from each player because every player has the same at-bats ($n_{j}$) and $r$.
 As the posterior mean gets closer to 0.5, the posterior variance gets bigger and has the biggest value when the posterior mean is 0.5.
@@
 
-This summary also includes the result of logistic regression fit because we did not know prior means in advance so that we had to estimate them via this logistic regression model.
+This summary also includes the result of logistic regression fit because we did not know prior means in advance.
+We had to estimate them via this logistic regression model.
 Let's look at the p-value of the indicator covariate (\code{beta1}).
-It shows that the two different prior distributions distinguishing outfielders from other positions were significantly different, supporting our assumption.
+It shows that the two prior means distinguishing outfielders from other positions were significantly different, supporting your initial belief.
 The positive sign of $\hat{\beta}_{1}$ reflects on the first five players, outfielders, whose observed batting averages were higher than others.
@@
 For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper line, there are short red lines toward five directions.
-This symbol also means that the seemingly two lines crossing over others were actually three lines for those who were outfielders (10th, 14th, and 15th hitters) with observed batting averages far lower than the top five hitters.
+This symbol also means that the seemingly two lines crossing over others were actually three lines for those who were outfielders (10th, 14th, and 15th hitters).
 \\
 
-Note that the observed sample mean among outfielders is 0.308 and that among other positions is 0.231.
+For reference, the observed sample mean among outfielders is 0.308 and that among other positions is 0.231.
 But why are the estimated two prior means from this Binomial model 0.310 and 0.233 each?
@@
 Let's see the 10th, 14th, and 15th players on the graph for example.
-They are outfielders but their batting averages (sample mean) are far worse than the first five outfielders.
+They are outfielders but their batting averages (sample mean) are far lower than the first five outfielders.
 RTTM means that it can happen by their bad luck though in the long run their batting averages will come back to their expected ones as outfielders (blue horizontal line).
@@
 
-The meaning of putting the \code{gbp} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values for generating pseudo-data sets.
+The meaning of putting the \code{gbp} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values when it generates pseudo-data sets.
 \\

### 2013-05-01 jss/article.tex
corrections

@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-\pkg{Rgbp} uses Bayesian machinery to estimate a two-level model (a random-effects mixed model) and allows for a check of its frequentist properties via a repeated sampling procedure (which we call a ``method check").
+\pkg{Rgbp} uses Bayesian machinery to estimate a two-level model (a random-effects mixed model) and allows for a check of its frequentist properties via a repeated sampling procedure (which we call a ``method checking").
 It is found that even in small samples our procedure yields good frequency properties.
@@
 \includegraphics[scale=0.25]{hospital1.png}
+\caption{Shrinkage plot and 95\% interval plot}
 \end{center}
@@
 \includegraphics[width = 5.5cm]{hospital2.png}
+\caption{Coverage plot via method checking}
 \end{center}
@@
 \includegraphics[scale=0.3]{baseball1.png}
+\caption{Shrinkage plot and 95\% interval plot}
 \end{center}
@@
 \includegraphics[width = 5.5cm]{baseball2.png}
+\caption{Coverage plot via method checking}
 \end{center}

### 2013-05-29 jss/article.tex
fix spelling

@@
 
-Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger) and $\lambda_{j}$ as a true death rate per exposure.
+Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an integer) and $\lambda_{j}$ as a true death rate per exposure.
 This data set is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.
@@
 \section[Multilevel Structure]{Multilevel Structure}
-Our multilevel model, also called a conditionally independent hierarchical model (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical sturucture in data.
+Our multilevel model, also called a conditionally independent hierarchical model (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical structure in data.
 For example, we can think about a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players.
@@
 Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are functions of shrinkage (see (3)) and Adam's and Eve's laws are taking conditional expectation and variance over them given data, $\textbf{y}$.
-Since we have already estimated $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, fianlly we can estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.
+Since we have already estimated $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, finally we can estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.
 
@@
 
-Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates, the final product of this multilevel modeling.
+Once we are sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this multilevel modeling.
 ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to check this point.
@@
 Based on this idea, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic.
-This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates on the $i$-th data set.
+This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-Ch player's interval estimates on the $i$-th data set.
 We can calculate this probability  because we know the distribution of $p_{ij} \vert z_{ij}, r, \beta$ in (9).
@@
 If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery.
-On top of that, if you can figure out each hospital's abililty to handle this surgery, it will be useful for your decision in choosing a hospital.
+On top of that, if you can figure out each hospital's ability to handle this surgery, it will be useful for your decision in choosing a hospital.
 \\
@@
 Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload.
-Though somewhat extreme, this is what happened to the two left-most hostpitals in the first plot and this is why hierarchical modeling is a reasonable choice for this data set.
+Though somewhat extreme, this is what happened to the two left-most hospitals in the first plot and this is why hierarchical modeling is a reasonable choice for this data set.
 \\
@@
 Also it reveals that the 23rd hospital, whose estimated true rate was the smallest, has also the smallest upper bound.
-If you are a risk-avoider, this hospital will attract you most strongly.
+If you are a risk-adverse, this hospital will attract you most strongly.
 And if you already chose this 23rd hospital compared to the 8th from the shrinkage plot, your decision might become stronger at this point, excluding the 8th hospital with more certainty.
@@
 It estimated coverage probabilities by simple unbiased estimates (a blue dashed line) and Rao-Blackwellized unbiased estimates (a red line).
-Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate and 0.951 from the simple unbiased estimate.
+Both lines are indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate and 0.951 from the simple unbiased estimate.
 Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular data set has nice repeated sampling property.
@@
 One more thing to emphasize is that observed sample means are all within the interval estimates.
-And these interval estimates also catched the batting averages over the ramaining season successfully, although the result was left out.
+And these interval estimates also covered the batting averages over the remaining season successfully, although the result was left out.
 Then, how much can we trust these interval estimates?

### 2013-05-29 jss/article.tex
biblio plus edit to intro and three data

@@
              Hyungsuk Tak\\Harvard University }
-\title{\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check}
+\title{\pkg{Rgbp}: An R Package for Hierarchical Modeling and Method Checking}
 
@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-\pkg{Rgbp} uses Bayesian machinery to estimate a two-level model (a random-effects mixed model) and allows for a check of its frequentist properties via a repeated sampling procedure (which we call a ``method checking").
-It is found that even in small samples our procedure yields good frequency properties.
-Also, this package will be useful for Bayesians who want to see a non-informative reference point before and after constructing their full-Bayesian hierarchical model.
-For frequentists, it will provide confidence intervals of a random-effect mixed model with good repeated sampling properties.
+\pkg{Rgbp} is an R package for estimating and validating a two-level model (a random-effects mixed model).
+The estimation procedure utilizes Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``method checking").
+It is found that even in small samples our procedure yields good frequency properties in comparison to other methods such as Maximum Likelihood Estimation (MLE).
+This package will be useful for frequentists and Bayesians alike.
+Bayesians are able to use the package to see a non-informative reference point before and after constructing their full-Bayesian hierarchical model and frequentists, now have a procedure that will provide confidence intervals of a random-effect mixed model with good repeated sampling properties.
 
+%TODO: Do we want this here? Or just go straight into theory then follow with examples?
 \section[Feasible Data Types]{Three Feasible Types of Data }
-This package is intended to fit a multilevel model on the group-level (or unit-level) data in which each group-level observation is believed to have the Normal, Poisson, or Binomial distribution.
-In this section, we will introduce three specific types of feasible data sets.
+\pkg{Rgbp} is intended to fit a model where two levels of structure are assumed (unit and group levels).
+The model can be characterized by the distributional family assumed for the group level data and in the case of \pkg{Rgbp} this will be either the Normal, Poisson, or Binomial distribution.
+In this section, we will introduce three specific types of feasible data sets that illustrate this fact.
 
 \subsection{Normal: 8 Schools}
-Education Testing Service conducted randomized experiments in eight separate schools and obtained this data set.
-It contains the coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of eight schools (Rubin, 1981).
+The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching.
+The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \cite{1981}.
 \begin{CodeChunk}
@@
 
-Each school's coaching effect has approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
+Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
 So, it is reasonable to think that each school-level coaching effect is distributed as an independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
-\pkg{Rgbp} includes this data set and can be called by typing `\code{R> data(schools)}' on \proglang{R}.
+\pkg{Rgbp} includes this data set and can be called by the command `\code{data(schools)}' on \proglang{R}.
 
 \subsection{Poisson: 31 Hospitals}
-This data set is about the medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 (Morris and Lysy, 2012).
-It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$).
-The below code is an example of input based on the last ten hospital data.
+The following data are from medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 \cite{2012}.
+It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and the total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$).
+The following code is an example of input based on the last ten hospital data.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
-
-Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an integer) and $\lambda_{j}$ as a true death rate per exposure.
-This data set is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.
+Considering the type of data, it is reasonable to assume the number of deaths in each hospital follow independent Poisson distributions given an unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where, for each $j$, $n_{j}$ can be interpreted as an exposure (not necessarily an integer) and $\lambda_{j}$ as the true death rate per exposure.
+This data set is also included in the package and can be called by `\code{data(hospital)}' on \proglang{R}.
 
 \subsection{Binomial: 18 Baseball Hitters}
-This data set contains information about batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975).
-Also, it has one covariate, Position, showing in which position each player was playing.
-For convenience, we transform this variable into a binary indicator, which is 1 if a player was a outfielder and 0 otherwise.
-The code below shows a way to make inputs.
-If we have more than one covariate, for example, \code{x1} and \code{x2}, then `\code{R> x <- cbind(x1, x2)}' will be the right input of the \code{gbp} function.
+The following dataset contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \cite{1975}.
+In addition one covariate relating to the position each player was playing was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was a outfielder and 0 otherwise).
 \begin{CodeChunk}
@@
 The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown true batting average $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
-This data set is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.
+This data set is also a part of the package and can be called on \proglang{R} by `\code{data(baseball)}'.
 
 \section[Multilevel Structure]{Multilevel Structure}
-Our multilevel model, also called a conditionally independent hierarchical model (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical structure in data.
+Our multilevel model, also called a conditionally independent hierarchical model \cite{1989}, is a very powerful tool for exploring the hierarchical structure in data.
 For example, we can think about a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players.
@@
 
-Here the adjustment for density maximization (Morris and Tang, 2011), called ADM, comes.
+Here the adjustment for density maximization \cite{2011}, called ADM, comes.
 It assumes the Beta distribution for shrinkage because this distribution is also defined between 0 and 1.
 In the end, ADM  estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause.
-Please refer to Morris and Tang (2011) for additional advantages of ADM.
+Please refer to \cite{2011} for additional advantages of ADM.
 \\
@@
 
-Morris and Christiansen (1995) also looked into a similar ranking problem in hierarchical modeling, taking shrinkage into account.
+\cite{1995} also looked into a similar ranking problem in hierarchical modeling, taking shrinkage into account.
 \\
@@
 
-Efron and Morris (1975) said ``no,'' and suggested James-Stein estimator, making each players' sample mean shrink towards an estimated mean of the second-level prior distribution.
+\cite{1975} said ``no,'' and suggested James-Stein estimator, making each players' sample mean shrink towards an estimated mean of the second-level prior distribution.
 They showed that this estimator was more than three times efficient than the sample mean under squared error loss.
-On top of that, a few years later Morris (1983) introduced interval estimates that could successfully catch the batting averages over the remaining season, which MLE and its interval estimate could not.
+On top of that, a few years later \cite{1983} introduced interval estimates that could successfully catch the batting averages over the remaining season, which MLE and its interval estimate could not.
 \\
@@
 
-\section[Reference]{Reference}
-1.
-Christiansen, C.
-and Morris, C.
-(1996).
-``Fitting and Checking a Two-Level Poisson Model: Modeling Patient Mortality Rates in Heart Transplant Patients,'' in \emph{Bayesian Biostatistics}, eds.
-D.
-Berry and D.
-Stangl, New York: Marcel Dekker, pp.
-467-561.
-\\
-
-2. Efron, B. and Morris, C. (1975). ``Data Analysis Using Stein's Estimator and its Generalizations.'' \emph{Journal of the American Statistical Association}. \textbf{70}. 311-319.
-\\
-
-3. Kass, R. and Steffey, D. (1989). ``Approximate Bayesian Inference in Conditionally Independent Hierarchical Models (Parametric
-Empirical Bayes Models).'' \emph{Journal of the American Statistical Association}. \textbf{84}. 717-726.
-\\
-
-4. Morris, C. (1983). ``Parametric Empirical Bayes Inference: Theory and Applications.'' \emph{Journal of the American Statistical Association}. \textbf{78}. 47-55.
-\\
-
-5.
-Morris, C.
-and Christiansen, C.
-(1995).
-``Hierarchical Models for Ranking and for Identifying Extremes, With Application,'' in \emph{Bayesian Statistics 5}, eds.
-J.
-Bernardo, J.
-Berger, A.
-Dawid, and A.
-Smith, New York: Oxford University Press, pp.
-277-296.
-\\
-
-6. Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
-\\
-
-7. Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
-\\
-
-8. Rubin, D. B. (1981). ``Estimation in parallel randomized
-  experiments.'' \emph{Journal of Educational Statistics}. \textbf{6}. 377-401.
-\\
+\bibliography{bibliography}
 

### 2013-05-29 jss/article.tex
uhhh more changes

@@
 
-\section[Multilevel Structure]{Multilevel Structure}
-Our multilevel model, also called a conditionally independent hierarchical model \cite{1989}, is a very powerful tool for exploring the hierarchical structure in data.
-For example, we can think about a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players.
-\code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter.
-Users can determine one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their data sets.
-\\
+\section[Multilevel Structure]{Multilevel Structure} \label{multilevel}
+A two-level or multilevel model, also called a conditionally independent hierarchical model \cite{1989}, is a very powerful tool for exploring the hierarchical structure in data.
+For example, in the 8 schools dataset, we can imagine that there exists a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players.
+\code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter.
+The \code{gbp} function allows users to choose one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their data sets.
 
 \subsection[Normal-Normal]{Normal-Normal}
-\code{gbp} can construct a two-level Normal-Normal hierarchical model on the 8 school data.
-For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th school in the data set.
+The following is a general Normal-Normal hierarchical model.
+For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th group in the data set.
 \begin{equation}
@@
 
-where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $\beta$ and $A$ are unknown, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients.
+where $~j=1, \ldots k$, $\mu_{0j} = \mathbf{x}^{T}_{j} \mathbf{\beta}$, $x_{j}$ is $j$-th group's covariate vector ($m\times 1$), $m$ is the number of regression coefficients and $\mathbf{\beta}$ and $A$ are unknown.
 Note that if there is no covariate then $x_{j}=1$ for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
 For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean.
-Also,  based on this conjugate prior distribution, it is easy to derive the corresponding posterior distribution, which is the same as the product of two distributions, (1) and (2), up to a normalizing constant.
-\begin{equation}
+Based on this conjugate prior distribution it is easy to derive the corresponding posterior distribution
+\begin{equation} \label{normalpost}
 \mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}),
 \end{equation}
-where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, 8$, are called shrinkages.
+where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkages.
 
 \subsection[Poisson-Gamma]{Poisson-Gamma}
-\code{gbp} is also able to build a Poisson-Gamma multilevel model on the 31 hospital data.
+\code{gbp} is also able to build a Poisson-Gamma multilevel model.
 Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket below indicates [mean, variance] of distribution.
@@
 \begin{equation}
-\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(\lambda_{0j}r)\sim \textrm{Gamma}[\lambda_{0j}, ~\frac{\lambda_{0j}}{r}],
+\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(\lambda_{0j}r)\sim \textrm{Gamma} \left[\lambda_{0j}, ~\frac{\lambda_{0j}}{r} \right],
 \end{equation}
 
-where $\log(\lambda_{0j}) =x_{j}'\beta$, $j=1, \ldots, 31$, with two unknown hyper-parameters, $r$ and $\beta$. Immediate posterior distribution of this Poisson-Gamma model is
-\begin{equation}
-\lambda_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0j} + n_{j}y_{j})\sim\textrm{Gamma}[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}}],
+where $\log(\lambda_{0j}) =x_{j}'\beta$, $j=1, \ldots, k$, with two unknown hyper-parameters, $r$ and $\beta$. The posterior distribution of this Poisson-Gamma model is
+\begin{equation} \label{gammapost}
+\lambda_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0j} + n_{j}y_{j})\sim\textrm{Gamma} \left[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}} \right],
 \end{equation}
 
-where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0j}$,  $B_{j}\equiv r / (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1, \ldots, 31$.
+where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0j}$,  $B_{j}\equiv r / (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1, \ldots, k$.
 
@@
 \begin{equation}
-p_{j} \vert \beta, r\stackrel{ind}{\sim}\textrm{Beta}(rp_{0j},~ r(1-p_{0j}))\sim \textrm{Beta}[p_{0j}, ~\frac{p_{0j}(1-p_{0j})}{r + 1}],
+p_{j} \vert \beta, r\stackrel{ind}{\sim}\textrm{Beta}(rp_{0j},~ r(1-p_{0j}))\sim \textrm{Beta} \left[p_{0j}, ~\frac{p_{0j}(1-p_{0j})}{r + 1} \right],
 \end{equation}
 
-where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, 18$. Note that $r$ and $\beta$ are two unknown hyper-parameters. Then, corresponding posterior distribution is
-\begin{equation}
+where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$. Note that $r$ and $\beta$ are two unknown hyper-parameters. Then, corresponding posterior distribution is
+\begin{equation} \label{betapost}
 p_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}y_{j},~r(1-p_{0j})+n_{j}(1-y_{j}))\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
 \end{equation}
-where $p^{\ast}_{j}\equiv(1-B_{j})y_{j}+B_{j}p_{0j}$, $B_{j}\equiv r/ (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1,\ldots,18$.
+where $p^{\ast}_{j}\equiv(1-B_{j})y_{j}+B_{j}p_{0j}$, $B_{j}\equiv r/ (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1,\ldots,k$.
 
 \subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
-Hyper-prior distribution indicates a distribution of the second-level parameters, which plays an important role in deriving a full posterior distribution of all the parameters.
-\code{gbp} sets non-informative distributions on second-level parameters to let the data speak more about their estimation.
+In our examples the hyper-prior distribution is an assumed distribution on the second-level parameters and with the goal of objectivity in mind \code{gbp} assumes non-informative hyper-prior distributions.
 \begin{equation}
@@
 where $m$ is the number of regression coefficients.
-As for $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases.
-The next flat prior distribution of the second-level variance component $A$ (or $1/r$) was chosen to bring a good repeated sampling property and for a posterior propriety under moderate conditions.
-\\
+As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases.
+The next flat prior distribution of the second-level variance component $A$ (or $1/r$) was chosen for its good repeated sampling properties and for posterior propriety under moderate conditions.
 
@@
 \subsection[Shrinkage Estimation]{Shrinkage Estimation}
-Estimating shrinkage is a key part of this hierarchical modeling.
-As we can see in (3), (6), and (9), the posterior means are a linear function of shrinkage and the posterior variances are also a linear (Gaussian), quadratic (Poisson), or cubic (Binomial) function of shrinkage.
-It implies that we cannot obtain $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ without appropriate shrinkage estimation.
+Estimating the shrinkage factors ($B_1, \ldots B_k$) is the key estimation problem with the hierarchical models \code{gbp} assumes.
+As we can see in \ref{normalpost}, \ref{gammapost}, and \ref{betapost}, the posterior means are a linear function of the shrinkage factors and the posterior variances are also linear (Gaussian), quadratic (Poisson), or cubic (Binomial) functions.
+A natural method then to estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ is to first estimate the shrinkage factors.
 
 \subsection[ADM]{Adjustment for Density Maximization}
-When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
-\\
+It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
+Current popular methods of estimation via maximization (MLE or MAP) of these unknown shrinkage factors can result in estimates lying on the boundary of the parameter space.
+In the Normal-Normal model this situation typically arises when the variation within schools is greater than the variation between resulting in a parameter estimate of $\hat{A} = 0$.
+%TODO: Reference this!
+Maybe it's in the Lysy paper
 
-In this case, the most common way is to obtain an MLE of the variance component with its asymptotic Normality and then to use Delta method for asymptotic Normal distribution of shrinkage, \emph{i.e.}, $\hat{B}_{j, MLE}=B_{j}(\hat{A}_{MLE})$.
-But, is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1?
-If it is, why do we fit a logistic regression, such as logit($p$) = $x^{T}\beta$, instead of fitting a linear regression, $p = x^{T}\beta+\epsilon$?
-\\
+To continue with a maximization based estimation procedure but to steer clear of aforementioned issues we make us of adjustment for density maximization (ADM) \cite{2011}.
+In general ADM is a procedure to obtain estimates of posterior moments via maximization if the underlying posterior can be approximated by a Pearson family.
+For our purposes we can approximate the posterior distribution of a shrinkage factor with the Beta distribution allowing us to finally obtain estimates the posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause.
+Please refer to \cite{2011} for additional advantages of ADM.
 
-Here the adjustment for density maximization \cite{2011}, called ADM, comes.
-It assumes the Beta distribution for shrinkage because this distribution is also defined between 0 and 1.
-In the end, ADM  estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause.
-Please refer to \cite{2011} for additional advantages of ADM.
-\\
-
-Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only data.
-Taking the Normal model as an example,  $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Adam's law and $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Eve's law.
-Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are functions of shrinkage (see (3)) and Adam's and Eve's laws are taking conditional expectation and variance over them given data, $\textbf{y}$.
-Since we have already estimated $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, finally we can estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.
+Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only the data. Taking the Normal-Normal model as an example we note the following identities
+\begin{eqnarray}
+E(\mu_{j}\vert \textbf{y}) & = & E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y}) \\ 
+Var(\mu_{j}\vert \textbf{y}) & = & E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y}).
+\end{eqnarray}  
+Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are functions of the shrinkage factors (\ref{normalpost}) and since we have already can estimate $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, we can finally estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.
 
 \subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
-After estimating two posterior moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$ for the Binomial model, \code{gbp} reasonably approximates a posterior distribution given data, \emph{i.e.}, $p_{j}\vert \textbf{z}$ (or $\mu_{j}\vert \textbf{y}$, $\lambda_{j}\vert \textbf{z}$), by matching these two moments with its parameters.
-To be specific, we assumed $p_{j}\vert \textbf{z}$ had another Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, with two parameters, $a_{1}$ and $a_{0}$, of this assumed Beta distribution.
+After estimating the two posterior moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, \code{gbp} reasonably approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
+The Binomial-Beta model we approximate $p_{j}\vert \textbf{z}$ with a Beta distribution and for the Poisson-Gamma model we approximate $\lambda_{j}\vert \textbf{z}$ with a Gamma distribution.
+Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\mu_{j}\vert \textbf{y}$ with a skewed-t distribution.
+%TODO: should I put down the form of the skewed-t or just put a reference to it?
 
+%not sure we need this
+%To be specific, we assumed $p_{j}\vert \textbf{z}$ had another Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, with two parameters, $a_{1}$ and $a_{0}$, of this assumed Beta distribution.
+
+%TODO: Resume editing from here
 \section[Method Checking]{Method Checking}
 Like the two sides of the same coin, checking a statistical model always comes with fitting a model.
-If a fitted model cannot pass a checking process, we usually go back to the fitting process and come back to the checking process iteratively.
+If a fitted model cannot pass a validation or checking process, we usually go back and forth from estimation and checking steps iteratively.
 In this sense, checking a fitted model is an interactive procedure for the model justification.
-\\
 
-There are two kinds of model justification process; one is a model check and the other is a method check.
-The model check is for the justification of a hierarchical modeling on a specific data set.
-One possible question is, ``Can this data set benefit from such a multilevel modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy.
+There are two kinds of model justification processes; one is a model check and the other is a method check.
+The model check is for the justification of the model \ref{multilevel} on a specific data set.
+One possible question is, ``Can this data set benefit from such a multilevel modeling?'' \cite{1997} answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy.
 They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
-\\
 
@@
 On top of that, if you can figure out each hospital's ability to handle this surgery, it will be useful for your decision in choosing a hospital.
-\\
 
@@
 In addition, while one looks for such information, suppose one knows that the state-level death rate per exposure of this surgery is 0.020.
-\\
 
@@
 For reference, a model check can be useful for evaluating the validity of such a view point (Christiansen and Morris, 1996).
-\\
 
@@
 `\code{R> p}' automatically sorts the output by the increasing order of caseload ($n_{j}$).
-\\
 
 The output contains information about sample mean (\code{obs.mean}), caseload (\code{n}), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower interval, posterior mean ($E(\lambda_{j}\vert \textbf{z})$), upper interval, and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{z})$).
-\\
 
@@
 This point is clear in the above output because, as caseload increases, shrinkage decreases, depending less on the prior distribution.
-\\
 
@@
 It means that observed sample means of hospitals whose caseloads are less than 336 will shrink toward the prior mean (0.020) more than 50\%.
-\\
 
@@
 As for this hospital, using more information from the prior distribution is an appropriate choice because its observed amount of information (67) is far less than the amount of state-level information (336).
-\\
 
@@
 Without this hierarchical modeling, we might have made a wrong decision in choosing a hospital.
-\\
 
@@
 Though somewhat extreme, this is what happened to the two left-most hospitals in the first plot and this is why hierarchical modeling is a reasonable choice for this data set.
-\\
 
@@
 Overall, as the caseload increases towards the right and as the posterior mean gets closer to 0, the length of interval gets shorter, which the formula of posterior variance in (6) implies.
-\\
 
@@
 (Could you regard this 31st hospital as a possible candidate before you observe this plot?)
-\\
 
@@
 And if you already chose this 23rd hospital compared to the 8th from the shrinkage plot, your decision might become stronger at this point, excluding the 8th hospital with more certainty.
-\\
 
@@
 For reference, we can try any other value of $r$, for example $r=200$, by replacing below code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
-\\
 
@@
 Then, the function \code{coverage} will evaluate whether interval estimates achieve 90\% confidence level.
-\\
 
@@
 Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular data set has nice repeated sampling property.
-\\
 
@@
 \cite{1995} also looked into a similar ranking problem in hierarchical modeling, taking shrinkage into account.
-\\
 
@@
 For reference, the data set  \code{baseball} has each player's batting average over the remaining season.
-\\
 
@@
 But can we say this is the best way to predict their batting averages?
-\\
 
@@
 On top of that, a few years later \cite{1983} introduced interval estimates that could successfully catch the batting averages over the remaining season, which MLE and its interval estimate could not.
-\\
 
@@
 The fact that all players have the same amount of observed information ($n_{j}=45$) and $\hat{r}=\textrm{exp}(4.727)=113$ from below summary tell why the estimated shrinkage is 0.715 (=113 / (113 + 45)).
-\\
 
@@
 These values were 0.042, 0.043, and 0.086 each, indicating that estimates from the Normal and Binomial models are twice better than MLE in terms of squared error loss.
-\\
 
@@
 This symbol also means that the seemingly two lines crossing over others were actually three lines for those who were outfielders (10th, 14th, and 15th hitters).
-\\
 
@@
 The Normal model can avoid this small bias because it uses a linear regression to estimate these prior means.
-\\
 
@@
 So, their posterior means (red dots) can also be interpreted as their RTTM.
-\\
 
@@
 The meaning of putting the \code{gbp} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values when it generates pseudo-data sets.
-\\
 
 Finally, the estimated average coverage probability is 0.973 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.
-\\
 

### 2013-06-10 jss/article.tex
finally up to 8 schools example. Will do tomorrow morning
8 schools disc

@@
 
-\subsection{Normal: 8 Schools}
+\subsection{Normal: 8 Schools} \label{8schooldata}
 The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching.
@@
 
-%TODO: Resume editing from here
+%TODO: Haven't proof read method checking section yet
 \section[Method Checking]{Method Checking}
@@
 
+%TODO: Proof read Hospital and Baseball examples
 \section[Examples]{Examples}
@@
 R> summary(p)
-\end{CodeInput}
+\end{CodeInput}error:%20LaTeX%20Error:%20File%20`a4wide.sty'%20not%20found.
 \begin{CodeOutput}
@@
 \subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}
+As stated in \ref{8schooldata} the Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching.
+The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \cite{1981}.
 \begin{CodeChunk}
 \begin{CodeInput}
+R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
+R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
+\end{CodeInput}
+\end{CodeChunk}
+
+Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
+Hence, we can use \code{gbp} to fit this hierarchical model:
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> data(schools)
+R> attach(schools)
 R> g <- gbp(y, se, model = "gr")
@@
 \end{CodeChunk}
+The output from \code{gbp} provides an easy to read summary of the results of the estimation. Here we see that the posterior mean estimates are simply a linear combination
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> plot(g)
+\end{CodeInput}
+\end{CodeChunk}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.3]{school1.png}
+\caption{Shrinkage plot and 95\% interval plot for 8 schools}
+\end{center}
+\end{figure}
 
@@
 
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[scale=0.3]{school1.png}
-%\caption{Shrinkage and interval plots of 8 schools}
-%\end{center}
-%\end{figure}
-
-%\begin{CodeChunk}
-%\begin{CodeInput}
-%R> gcv <- coverage(g, nsim = 10000)
-%\end{CodeInput}
-%\end{CodeChunk}
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width = 5.5cm]{school2.png}
-%\end{center}
-%\end{figure}
+\begin{CodeChunk}
+\begin{CodeInput}
+R> gcv <- coverage(g, nsim = 10000)
+\end{CodeInput}
+\end{CodeChunk}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width = 5.5cm]{school2.png}
+\caption{Coverage plot via method checking for 8 schools}
+\end{center}
+\end{figure}
 

### 2013-06-18 jss/article.tex
starting up

@@
 \begin{document}
-
 %% include your article here, just as usual
@@
 R> summary(p)
-\end{CodeInput}error:%20LaTeX%20Error:%20File%20`a4wide.sty'%20not%20found.
+\end{CodeInput}
 \begin{CodeOutput}
@@
 Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
-Hence, we can use \code{gbp} to fit this hierarchical model:
+Hence, we can use \code{gbp} to fit a Normal-Normal hierarchical model:
 
@@
 \end{CodeChunk}
-The output from \code{gbp} provides an easy to read summary of the results of the estimation. Here we see that the posterior mean estimates are simply a linear combination
+The output from \code{gbp} provides an easy to read summary of the results of the estimation. There seems to be little evidence
 

### 2013-06-18 jss/article.tex
discussion

@@
 \end{CodeChunk}
-The output from \code{gbp} provides an easy to read summary of the results of the estimation. There seems to be little evidence
+The output from \code{gbp} provides an easy to read summary of the results of the estimation.
+From this there seems to be little evidence that the training provided much of an added benefit with every school's $95\%$ posterior interval containing 0.
+\pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in \ref{8schoolsplot}.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[h] \label{8schoolsplot}
 \begin{center}
@@
 \end{figure}
+
+Plotting the results provides a visual aid to understanding but is only largely beneficial when the number of groups $(k)$ is small.
+In the case where the number of groups is large \pkg{Rgbp} provides a summary feature:
 
@@
 
+An integral part of fitting any model is to check the method of estimation.
+Namely we can generate new pseudo-data from our assumed model by fixing the hyper-parameter values ($A$ and $\mu_0$ in this example) at their estimates.
+It is then possible to simulate ``true'' $\theta_i$ for each group $i$ and re-fit the model many times to estimate the coverage probabilities of our procedure.
+
 \begin{CodeChunk}
@@
 \end{CodeChunk}
-\begin{figure}[h]
+\begin{figure}[h] \label{schoolcoverage}
 \begin{center}
@@
 \end{figure}
+
+As seen in \ref{schoolcoverage} the desired $95\%$ coverage probability was achieved for each group in this example.
 
@@
 \section[Discussion]{Discussion}
-Bayes vs Freq, post.mean vs estimate, post.sd vs estimated standard error.
+\pkg{Rgbp} is an R package for estimating and validating a two-level hierarchical model.
+The package aims to provide a procedure that is not only fast and easy to use but has good frequency properties and can be used in many scenarios.
+The package provides ``method checking'' functionality to examine repeated sampling properties and provides
+
+The estimation procedure utilizes Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``method checking").
+It is found that even in small samples our procedure yields good frequency properties in comparison to other methods such as Maximum Likelihood Estimation (MLE).
+This package will be useful for frequentists and Bayesians alike.
+Bayesians are able to use the package to see a non-informative reference point before and after constructing their full-Bayesian hierarchical model and frequentists, now have a procedure that will provide confidence intervals of a random-effect mixed model with good repeated sampling properties.
+
 \section[acknowledgments]{Acknowledgments}

### 2013-06-18 jss/article.tex
disc written

@@
 The package aims to provide a procedure that is not only fast and easy to use but has good frequency properties and can be used in many scenarios.
-The package provides ``method checking'' functionality to examine repeated sampling properties and provides
+The package provides ``method checking'' functionality to examine repeated sampling properties and test that the method is valid at a particular parameter value.
 
-The estimation procedure utilizes Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``method checking").
-It is found that even in small samples our procedure yields good frequency properties in comparison to other methods such as Maximum Likelihood Estimation (MLE).
-This package will be useful for frequentists and Bayesians alike.
-Bayesians are able to use the package to see a non-informative reference point before and after constructing their full-Bayesian hierarchical model and frequentists, now have a procedure that will provide confidence intervals of a random-effect mixed model with good repeated sampling properties.
+In addition to good frequency properties Bayesians will be able to use the package to see the results from a non-informative reference point.
+This allows the user to examine whether it is worth to implement a full Bayesian model (which is often more time consuming).
+
+Due to the fact that the estimation procedures in \pkg{Rgbp} rely on differentiation the package is extremely quick in fitting the available models.
+This makes the package ideal to be used in simulation studies where a hierarchical model needs to be fitted at every iteration and where running a full Bayesian model (via MCMC) would be computationally impractical.
+
+In short the \pkg{Rgbp} is an R package that utilizes Bayesian machinery to provide a method of estimating two-level hierarchical models from many families in a fast and computationally efficient manner.
 

### 2013-06-20 jss/article.tex
typos

@@
 %% for pretty printing and a nice hypersummary also set:
-\Plainauthor{Joseph Kelly, Carl Morris, Hyung Suk Tak} %% comma-separated
-\Plaintitle{Rgbp: Bayesian Hierarchical Modeling and Frequentist Method Check} %% without formatting
+\Plainauthor{Joseph Kelly, Carl Morris, Hyungsuk Tak} %% comma-separated
+\Plaintitle{Rgbp: An R Package for Hierarchical modeling and Method Checking} %% without formatting
 
@@
 
-where $~j=1, \ldots k$, $\mu_{0j} = \mathbf{x}^{T}_{j} \mathbf{\beta}$, $x_{j}$ is $j$-th group's covariate vector ($m\times 1$), $m$ is the number of regression coefficients and $\mathbf{\beta}$ and $A$ are unknown.
+where $~j=1, \ldots k$, $\mu_{0j} = x^{T}_{j} \mathbf{\beta}$, $x_{j}$ is the $j$-th group's covariate vector ($m\times 1$), $m$ is the number of regression coefficients and $\mathbf{\beta}$ and $A$ are unknown.
 Note that if there is no covariate then $x_{j}=1$ for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
@@
 
-To continue with a maximization based estimation procedure but to steer clear of aforementioned issues we make us of adjustment for density maximization (ADM) \cite{2011}.
+To continue with a maximization-based estimation procedure but to steer clear of aforementioned issues we make use of adjustment for density maximization (ADM) \cite{2011}.
 In general ADM is a procedure to obtain estimates of posterior moments via maximization if the underlying posterior can be approximated by a Pearson family.
-For our purposes we can approximate the posterior distribution of a shrinkage factor with the Beta distribution allowing us to finally obtain estimates the posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause.
+For our purposes we can approximate the posterior distribution of a shrinkage factor with the Beta distribution allowing us to finally obtain estimates of the posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause.
 Please refer to \cite{2011} for additional advantages of ADM.
@@
 After estimating the two posterior moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, \code{gbp} reasonably approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
-The Binomial-Beta model we approximate $p_{j}\vert \textbf{z}$ with a Beta distribution and for the Poisson-Gamma model we approximate $\lambda_{j}\vert \textbf{z}$ with a Gamma distribution.
+For the Binomial-Beta model we approximate $p_{j}\vert \textbf{z}$ with a Beta distribution and for the Poisson-Gamma model we approximate $\lambda_{j}\vert \textbf{z}$ with a Gamma distribution.
 Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\mu_{j}\vert \textbf{y}$ with a skewed-t distribution.
@@
 
-There are two kinds of model justification processes; one is a model check and the other is a method check.
-The model check is for the justification of the model \ref{multilevel} on a specific data set.
-One possible question is, ``Can this data set benefit from such a multilevel modeling?'' \cite{1997} answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy.
+There are two kinds of model justification processes; one is a model checking and the other is a method checking.
+The model checking is for the justification of the model \ref{multilevel} on a specific data set.
+One possible question is, ``Can this data set benefit from such a multilevel modeling?'' \cite{1997} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
 They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
@@
 ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to check this point.
-From now on, all the explanations will be based on the Binomial model because the idea is the same and can be easily applied to the other two models.
+From now on, all the explanations will be based on the Binomial model using the baseball data because the idea is the same and can be easily applied to the other two models.
 
@@
 Figure 1 will be helpful to understand this process.
-As we can see in (8), the distribution of each true batting average ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(m\times1)}$, where $m$ is the number of regression coefficients.
+As we can see in (8), the distribution of each true batting average ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(2\times1)}$.
 So, once we fix these hyper-parameters at specific values, we can generate true batting averages.
 Suppose we sampled 500 $\mathbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\mathbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (8), where $r$ and $\beta$ are given.
-Then, we can also generate $\{\mathbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-data set and $j$ does $j$-th player.
+Then, we can also generate $\{\mathbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates the $i$-th pseudo-data set and $j$ does the $j$-th player.
 Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\mathbf{z}^{(i)}_{(18\times1)}, \mathbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500$\times$18 interval estimates.
@@
 \subsection{Simple Unbiased Estimates of Coverage Probabilities}
-Based on the generated pseudo-data sets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th player's interval estimate from $i$-th pseudo-data set includes $p_{ij}$ and 0 otherwise.
+Based on the generated pseudo-data sets, let's define an indicator variable, $I_{ij}$, which is 1 if the $j$-th player's interval estimate from the $i$-th pseudo-data set includes $p_{ij}$ and 0 otherwise.
 One way to estimate the coverage probability is taking average over these indicator variables.
@@
 Based on this idea, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic.
-This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-Ch player's interval estimates on the $i$-th data set.
+This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is the $j$-th player's interval estimates on the $i$-th data set.
 We can calculate this probability  because we know the distribution of $p_{ij} \vert z_{ij}, r, \beta$ in (9).
@@
 \subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
-Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease (hopefully not).
+Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease.
 If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery.
@@
 If the second level has more information than the first level, then the sample mean shrinks towards the prior mean more than 50\%.
-This point is clear in the above output because, as caseload increases, shrinkage decreases, depending less on the prior distribution.
+This point is clear in the above output because, as caseload increases, shrinkage decreases, depending less on the second level information.
 
@@
 As mentioned before, $r$ can be interpreted as the amount of prior information, although we do not know its true value.
-So, \code{gbp} asked data how much credit they wanted to give to this hypothetical second-level hierarchy.
-$\hat{r}$ = 336 is the answer from the data.
+So, \code{gbp} asked the data how much credit they wanted to give to this hypothetical second-level hierarchy and $\hat{r}$ = 336 was their answer.
 It means that observed sample means of hospitals whose caseloads are less than 336 will shrink toward the prior mean (0.020) more than 50\%.
@@
 \end{CodeChunk}
-The output from \code{gbp} provides an easy to read summary of the results of the estimation.
+The output from \code{gbp} provides an easy way to read summary of the results of the estimation.
 From this there seems to be little evidence that the training provided much of an added benefit with every school's $95\%$ posterior interval containing 0.

### 2013-06-26 jss/article.tex
changes

@@
 %% an abstract and keywords
-\Abstract{Bayesian-frequentist reconciliation via Bayesian hierarchical modeling for Gaussian, Binomial, and Poisson data and frequentist method check for good coverage probability.}
-\Keywords{hierarchical model, multilevel model, random effects mixed model, method check, coverage probability, normal, binomial, poisson, shrinkage, \proglang{R}}
+\Abstract{
+\pkg{Rgbp} is an R package for estimating and validating a two-level model (a random-effects mixed model).
+The estimation procedure utilizes Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``method checking").
+It is found that \pkg{Rgb} characterized by such Bayesian-frequentist reconciliation has strong points of both sides, working well in small samples and yielding good coverage probability.
+Following three examples for Gaussian, Poisson and Binomial data support this argument.}
+\Keywords{hierarchical model, multilevel model, random effects mixed model, method checking, coverage probability, Normal, Poisson, Binomial,  shrinkage, \proglang{R}}
 \Plainkeywords{keywords, comma-separated, not capitalized, r} %% without formatting
@@
 
-%TODO: Do we want this here? Or just go straight into theory then follow with examples?
-\section[Feasible Data Types]{Three Feasible Types of Data }
-\pkg{Rgbp} is intended to fit a model where two levels of structure are assumed (unit and group levels).
+%\section[Feasible Data Types]{Three Feasible Types of Data }
+%\pkg{Rgbp} is intended to fit a model where two levels of structure are assumed (unit and group levels).
 The model can be characterized by the distributional family assumed for the group level data and in the case of \pkg{Rgbp} this will be either the Normal, Poisson, or Binomial distribution.
@@
 
-\subsection{Normal: 8 Schools} \label{8schooldata}
-The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching.
+%\subsection{Normal: 8 Schools} \label{8schooldata}
+%The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching.
 The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \cite{1981}.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
-R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
-\end{CodeInput}
-\end{CodeChunk}
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
+%R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
+%\end{CodeInput}
+%\end{CodeChunk}
 
-Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
+%Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
 So, it is reasonable to think that each school-level coaching effect is distributed as an independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
@@
 
-\subsection{Poisson: 31 Hospitals}
-The following data are from medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 \cite{2012}.
+%\subsection{Poisson: 31 Hospitals}
+%The following data are from medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 \cite{2012}.
 It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and the total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$).
 The following code is an example of input based on the last ten hospital data.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> z <- c( 14,   9,  15,  13,  35,  26,  25,  20,   35,   27)
-R> n <- c(593, 602, 629, 636, 729, 849, 914, 940, 1193, 1340)
-\end{CodeInput}
-\end{CodeChunk}
-Considering the type of data, it is reasonable to assume the number of deaths in each hospital follow independent Poisson distributions given an unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where, for each $j$, $n_{j}$ can be interpreted as an exposure (not necessarily an integer) and $\lambda_{j}$ as the true death rate per exposure.
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%R> z <- c( 14,   9,  15,  13,  35,  26,  25,  20,   35,   27)
+%R> n <- c(593, 602, 629, 636, 729, 849, 914, 940, 1193, 1340)
+%\end{CodeInput}
+%\end{CodeChunk}
+%Considering the type of data, it is reasonable to assume the number of deaths in each hospital follow independent Poisson distributions given an unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where, for each $j$, $n_{j}$ can be interpreted as an exposure (not necessarily an integer) and $\lambda_{j}$ as the true death rate per exposure.
 This data set is also included in the package and can be called by `\code{data(hospital)}' on \proglang{R}.
 
-\subsection{Binomial: 18 Baseball Hitters}
-The following dataset contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \cite{1975}.
-In addition one covariate relating to the position each player was playing was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was a outfielder and 0 otherwise).
-\begin{CodeChunk}
-\begin{CodeInput}
-R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
-R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
-R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
-\end{CodeInput}
-\end{CodeChunk}
-The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown true batting average $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
+%\subsection{Binomial: 18 Baseball Hitters}
+%The following dataset contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \cite{1975}.
+In addition one covariate relating to the position each player was playing was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was an outfielder and 0 otherwise).
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  %8,  7)
+%R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, %45, 45)
+%R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
+%\end{CodeInput}
+%\end{CodeChunk}
+%The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown true batting average $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
 This data set is also a part of the package and can be called on \proglang{R} by `\code{data(baseball)}'.
@@
 A two-level or multilevel model, also called a conditionally independent hierarchical model \cite{1989}, is a very powerful tool for exploring the hierarchical structure in data.
-For example, in the 8 schools dataset, we can imagine that there exists a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players.
+For example, we can imagine that there exists a district-level hierarchy (bigger population) for observed school-level data, or a state-level hierarchy for observed hospital data in a certain state.
+
 \code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter.
@@
 The following is a general Normal-Normal hierarchical model.
-For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th group in the data set.
+For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates the \emph{j}-th group among \emph{k} groups in the data set.
 \begin{equation}
@@
 
-where $~j=1, \ldots k$, $\mu_{0j} = x^{T}_{j} \mathbf{\beta}$, $x_{j}$ is the $j$-th group's covariate vector ($m\times 1$), $m$ is the number of regression coefficients and $\mathbf{\beta}$ and $A$ are unknown.
+where $\mu_{0j} = x^{T}_{j} \mathbf{\beta}$, $j=1, \ldots k$, $x_{j}$ is the $j$-th group's covariate vector ($m\times 1$), $m$ is the number of regression coefficients and both $\mathbf{\beta}$ and $A$ are unknown.
 Note that if there is no covariate then $x_{j}=1$ for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
@@
 \begin{equation} \label{normalpost}
-\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}),
+\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}~),
 \end{equation}
@@
 
-where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$. Note that $r$ and $\beta$ are two unknown hyper-parameters. Then, corresponding posterior distribution is
+where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $r$ and $\beta$ are two unknown hyper-parameters. Then, corresponding posterior distribution is
 \begin{equation} \label{betapost}
@@
 where $m$ is the number of regression coefficients.
-As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases.
+As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the location gets plentiful as the number of groups (\emph{k}) increases.
 The next flat prior distribution of the second-level variance component $A$ (or $1/r$) was chosen for its good repeated sampling properties and for posterior propriety under moderate conditions.
@@
 Estimating the shrinkage factors ($B_1, \ldots B_k$) is the key estimation problem with the hierarchical models \code{gbp} assumes.
-As we can see in \ref{normalpost}, \ref{gammapost}, and \ref{betapost}, the posterior means are a linear function of the shrinkage factors and the posterior variances are also linear (Gaussian), quadratic (Poisson), or cubic (Binomial) functions.
+As we can see in (\ref{normalpost}), (\ref{gammapost}), and (\ref{betapost}), the posterior means are a linear function of the shrinkage factors and the posterior variances are also linear (Gaussian), quadratic (Poisson), or cubic (Binomial) functions.
 A natural method then to estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ is to first estimate the shrinkage factors.
+%TODO: If we cite somgthing, (Morris, 2011) might be appropriate format to me, but in our case it looks Morris (2011), which is confusing.
 
@@
 Current popular methods of estimation via maximization (MLE or MAP) of these unknown shrinkage factors can result in estimates lying on the boundary of the parameter space.
-In the Normal-Normal model this situation typically arises when the variation within schools is greater than the variation between resulting in a parameter estimate of $\hat{A} = 0$.
-%TODO: Reference this!
-Maybe it's in the Lysy paper
+In the Normal-Normal model \cite{2012} this situation typically arises when the within-group variation is greater than the between-group variation resulting in a parameter estimate of $\hat{A} = 0$.
 
@@
 
-Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only the data. Taking the Normal-Normal model as an example we note the following identities
+Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only the data ($\textbf{y}$).
+Taking the Normal-Normal model as an example we note the following identities
 \begin{eqnarray}
-E(\mu_{j}\vert \textbf{y}) & = & E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y}) \\ 
-Var(\mu_{j}\vert \textbf{y}) & = & E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y}).
+E(\mu_{j}\vert \textbf{y}) & = & E(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}) =E((1-B_{j})y_{j}+B_{j}\mu_{0j}\vert \textbf{y}).\\ 
+Var(\mu_{j}\vert \textbf{y}) & = & E(Var(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}).
 \end{eqnarray}  
-Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are functions of the shrinkage factors (\ref{normalpost}) and since we have already can estimate $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, we can finally estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.
+Note that both $E(\mu_{j}\vert \textbf{y}, \beta, A)$ and $Var(\mu_{j}\vert \textbf{y}, \beta, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}) and since we can estimate $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, we can finally estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.
 
 \subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
-After estimating the two posterior moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, \code{gbp} reasonably approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
+After estimating the two posterior moments, for example $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$, \code{gbp} reasonably approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
 For the Binomial-Beta model we approximate $p_{j}\vert \textbf{z}$ with a Beta distribution and for the Poisson-Gamma model we approximate $\lambda_{j}\vert \textbf{z}$ with a Gamma distribution.
 Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\mu_{j}\vert \textbf{y}$ with a skewed-t distribution.
+
 %TODO: should I put down the form of the skewed-t or just put a reference to it?
@@
 
+% TODO: Here, Christiansen and Morris (1997) seems appropriate format
 There are two kinds of model justification processes; one is a model checking and the other is a method checking.
@@
 Once we are sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this multilevel modeling.
-``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to check this point.
-From now on, all the explanations will be based on the Binomial model using the baseball data because the idea is the same and can be easily applied to the other two models.
+``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating peudo-dataset and estimating coverage probability.
+
+For reference, the explanation will be based on Normal-Normal model because the idea can be easily applied to other two models.
 
@@
 Figure 1 will be helpful to understand this process.
-As we can see in (8), the distribution of each true batting average ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(2\times1)}$.
-So, once we fix these hyper-parameters at specific values, we can generate true batting averages.
-Suppose we sampled 500 $\mathbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\mathbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (8), where $r$ and $\beta$ are given.
-Then, we can also generate $\{\mathbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates the $i$-th pseudo-data set and $j$ does the $j$-th player.
-Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\mathbf{z}^{(i)}_{(18\times1)}, \mathbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500$\times$18 interval estimates.
-After this generating process, as for the first player, we will have 500 pairs of ($z_{i1}$, $p_{i1}$) and 500 interval estimates, $\{(\hat{p}_{i1, low}, ~\hat{p}_{i1, upp}$), $i=1, \ldots, 500\}$.
+As we can see in (\ref{normalpost}), the distribution of each true parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$.
+So, once we fix these hyper-parameters at specific values, we can generate true parameters.
+Suppose we sampled 500 $\mathbf{\mu}_{(k\times1)}$'s, \emph{i.e.}, $\{\mathbf{\mu}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (2), where $A$ and $\beta$ are given.
+Then, we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each $\mu_{ij},$ where $i$ indicates the $i$-th pseudo-data set and $j$ does the $j$-th group.
+
 \begin{figure}[h]
@@
 
-\subsection{Simple Unbiased Estimates of Coverage Probabilities}
-Based on the generated pseudo-data sets, let's define an indicator variable, $I_{ij}$, which is 1 if the $j$-th player's interval estimate from the $i$-th pseudo-data set includes $p_{ij}$ and 0 otherwise.
+\subsection{Coverage Estimation Process}
+Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 peudo-datasets in order to obtain 500$\times$k interval estimates.
+
+\subsubsection{Simple Unbiased Estimates of Coverage Probabilities}
+Let's define an indicator variable, $I_{ij}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu_{ij}$ and 0 otherwise.
 One way to estimate the coverage probability is taking average over these indicator variables.
 We call it a simple unbiased coverage probability estimate.
-For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first player.
+For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first group.
 
-\subsection{Rao-Blackwellized Unbiased estimates of Coverage Probabilities}
+\subsubsection{Rao-Blackwellized Unbiased estimates of Coverage Probabilities}
 Rao-Blackwellization improves accuracy of an unbiased estimator by taking conditional expectation given a sufficient statistic.
-Based on this idea, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic.
-This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is the $j$-th player's interval estimates on the $i$-th data set.
-We can calculate this probability  because we know the distribution of $p_{ij} \vert z_{ij}, r, \beta$ in (9).
-Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ as long as $r$ and $\beta$ are known.
-Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.
+Based on this idea, we define $E(I_{ij}\vert y_{ij}, A, \beta$), where $A$ and $\beta$ were given at first (see 4.1) and $y_{ij}$ is a sufficient statistic.
+This expectation is the same as Pr$(\hat{\mu}_{ij, low}\le \mu_{ij} \le\hat{\mu}_{ij, upp}\vert y_{ij}, A, \beta)$, where ($\hat{\mu}_{ij, low}$, $\hat{\mu}_{ij, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
+We can calculate this probability  because we know the distribution of $\mu_{ij} \vert y_{ij}, A, \beta$ in (\ref{normalpost}).
+Note that conditioning on $y_{ij}$ is equivalent to conditioning on $\mathbf{y}$ as long as $A$ and $\beta$ are known.
+Then, we can estimate the first group's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert y_{i1}, A, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.
 
-%TODO: Proof read Hospital and Baseball examples
 \section[Examples]{Examples}
 \subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
-Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease.
-If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery.
-On top of that, if you can figure out each hospital's ability to handle this surgery, it will be useful for your decision in choosing a hospital.
+Suppose a person living in the New York state (NY) has been suffering from severe coronary heart disease.
+If this person is supposed to receive the coronary artery bypass graft (CABG) surgery soon, he or she might want to find the most reliable hospital for dealing with such a surgery.
+On top of that, if this person can figure out each hospital's ability to handle this surgery, it will be useful for choosing a hospital.
 
-For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths within a month of CABG surgeries and total number of patients receiving CABG surgeries in each hospital.
+For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
+The following code is an example of input based on the last ten hospital data.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> z <- c( 14,   9,  15,  13,  35,  26,  25,  20,   35,   27)
+R> n <- c(593, 602, 629, 636, 729, 849, 914, 940, 1193, 1340)
+\end{CodeInput}
+\end{CodeChunk}
+
 In addition, while one looks for such information, suppose one knows that the state-level death rate per exposure of this surgery is 0.020.
@@
 The multilevel modeling that assumes a bigger population-level hierarchy will be insightful in this problem.
-Here, we presume a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY.
+Here, we presume a state-level (NY) hierarchy governing the true death rates ($\lambda$) of CABG surgery of all the hospitals in NY.
 This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution whose mean is 0.020.
-For reference, a model check can be useful for evaluating the validity of such a view point (Christiansen and Morris, 1996).
 
@@
 Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital, the Poisson distribution would be the first choice to describe the uncertainty in our data.
-Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in 3.2 .
+Note that caseload  ($n_{j}$) can be interpreted as an exposure, which is not necessarily an integer.
+
+Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in 2.2 .
 For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression (see section 3.2).
@@
 \begin{CodeInput}
+R> data(hospital)
+R> z <- hospital$z
+R> n <- hospital$n
 R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
@@
 
-The output contains information about sample mean (\code{obs.mean}), caseload (\code{n}), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower interval, posterior mean ($E(\lambda_{j}\vert \textbf{z})$), upper interval, and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{z})$).
+The output contains information about sample mean ($y_{j}$), caseload ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower bound of interval estimate ($\hat{\lambda}_{low}$), posterior mean ($\hat{\lambda}=E(\lambda_{j}\vert \textbf{z})$), upper bound of interval estimate ($\hat{\lambda}_{upp}$), and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{z})$).
 
@@
 Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which is a good indicator of how valuable and informative the hypothetical second-level hierarchy is.
-As mentioned before, $r$ can be interpreted as the amount of prior information, although we do not know its true value.
-So, \code{gbp} asked the data how much credit they wanted to give to this hypothetical second-level hierarchy and $\hat{r}$ = 336 was their answer.
 It means that observed sample means of hospitals whose caseloads are less than 336 will shrink toward the prior mean (0.020) more than 50\%.
-
 For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.834$) was calculated by 336 / (336 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.834)*0.045 + 0.834 * 0.020=0.024$.
@@
 For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly safest hospital among 31 hospitals in terms of the observed sample mean was not actually safer than the second safest hospital.
-Without this hierarchical modeling, we might have made a wrong decision in choosing a hospital.
 
@@
 This interval plot makes the 31st hospital emerge as one of your candidates.
-(Could you regard this 31st hospital as a possible candidate before you observe this plot?)
 
@@
 It estimated coverage probabilities by simple unbiased estimates (a blue dashed line) and Rao-Blackwellized unbiased estimates (a red line).
-Both lines are indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate and 0.951 from the simple unbiased estimate.
-Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular data set has nice repeated sampling property.
+Both lines are indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate.
+This result shows that the interval estimates from the suggested multilevel modeling on this particular data set have nice repeated sampling property.
 
@@
 \subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}
+% TODO: As stated in ??
 As stated in \ref{8schooldata} the Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching.
@@
 \end{figure}
-
+%TODO: wrong reference. you mean 'As seen in Figure 5' below?
 As seen in \ref{schoolcoverage} the desired $95\%$ coverage probability was achieved for each group in this example.
@@
 \subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Prior Mean and One Covariate}
-In this example, suppose you read the New York Times published on 26 April 1970.
-One article in this magazine covered 18 baseball players' batting averages through their first official 45 at-bats of the 1970 season.
-And then, you became interested in their batting averages over the remaining season.
-How could you predict?
-For reference, the data set  \code{baseball} has each player's batting average over the remaining season.
+%The New York Times published on 26 April 1970 covered 18 baseball players' batting averages through their first official 45 at-bats of the 1970 season.
+And then we became interested in their batting averages over the remaining season.
 
-First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this data set.
-And we know that the sample mean (MLE) under this distribution is an uniformly minimum variance unbiased estimator (UMVUE) with nice asymptotic properties.
-It is also the simplest way to estimate their true batting averages.
-But can we say this is the best way to predict their batting averages?
+The following dataset from the New York Times published on 26 April 1970 contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \cite{1975}.
+In addition one covariate relating to the position of each player was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was an outfielder and 0 otherwise).
+\begin{CodeChunk}
+\begin{CodeInput}
+R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
+R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
+R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
+\end{CodeInput}
+\end{CodeChunk}
 
-\cite{1975} said ``no,'' and suggested James-Stein estimator, making each players' sample mean shrink towards an estimated mean of the second-level prior distribution.
-They showed that this estimator was more than three times efficient than the sample mean under squared error loss.
-On top of that, a few years later \cite{1983} introduced interval estimates that could successfully catch the batting averages over the remaining season, which MLE and its interval estimate could not.
+The data indicate that independent Binomial distribution is appropriate probability distribution for describing each player's number of hits among 45 at-bats conditioning on the unknown true batting average, \emph{i.e.}, $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
+For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
 
-Our hierarchical modeling is a sequel to these researches, which can add one more unique value.
-Suppose you strongly believe that the outfielder's batting averages are different from other positions' ones, not giving a credit to the assumption that all players' batting averages shrink towards the same mean.
-Instead, you want to assume two different second-level hierarchies for outfielders and for other positions, within each of which sharing information and regressing toward the mean (RTTM) occur.
-This perspective considers true batting averages of outfielders as sampled from the one and those of other positions from the other.
-Our multilevel modeling provides a way to incorporate such information (covariate) seamlessly into the second-level hierarchy.
+Suppose we are interested in their true batting averages and believe that the outfielder's batting averages are different from other positions' ones.
+So, it is desirable to assume two different second-level hierarchies for outfielders and for other positions, within each of which sharing information and regressing toward the mean (RTTM) occur.
+Our multilevel modeling provides a way to incorporate such information (position) seamlessly into the second-level hierarchy.
+
 \begin{CodeChunk}
@@
 
-For reference, we can run the Normal hierarchical model using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
-For comparison, we calculated squared error losses, $\sum_{j=1}^{18}(p_{j, remaining}-\hat{p}_{j})^{2}$, where $p_{j, remaining}$ is each player's batting average over the remaining season and $\hat{p}_{j}$ is estimate from the Binomial and Normal multilevel models and from the sample mean (MLE) using the first 45 at-bats.
-These values were 0.042, 0.043, and 0.086 each, indicating that estimates from the Normal and Binomial models are twice better than MLE in terms of squared error loss.
-
-One more thing to note is that the posterior standard deviation tends to be bigger among outfielders than among others.
+Note that the posterior standard deviation tends to be bigger among outfielders than among others.
 Let's see its formula in (9).
@@
 We had to estimate them via this logistic regression model.
-Let's look at the p-value of the indicator covariate (\code{beta1}).
-It shows that the two prior means distinguishing outfielders from other positions were significantly different, supporting your initial belief.
-The positive sign of $\hat{\beta}_{1}$ reflects on the first five players, outfielders, whose observed batting averages were higher than others.
+Let's look at the p-value of the indicator covariate.
+It shows that the two prior means distinguishing outfielders from other positions were significantly different (p-value = 0.038), supporting our initial belief.
+The positive sign of $\hat{\beta}_{1}$ indicates that the mean batting average for all the outfielders tends to be higher than that for those in the other positions.
 \\
@@
 RTTM means that it can happen by their bad luck though in the long run their batting averages will come back to their expected ones as outfielders (blue horizontal line).
-The fact that their sample means are located at the lower part of their 95\% intervals supports this argument.
+The fact that their sample means are closer to the lower part of their 95\% intervals supports this argument.
 So, their posterior means (red dots) can also be interpreted as their RTTM.

### 2013-06-26 jss/article.tex
changes

@@
 It is found that \pkg{Rgb} characterized by such Bayesian-frequentist reconciliation has strong points of both sides, working well in small samples and yielding good coverage probability.
-Following three examples for Gaussian, Poisson and Binomial data support this argument.}
+Following three examples for Gaussian, Poisson and Binomial data validate this point.}
 \Keywords{hierarchical model, multilevel model, random effects mixed model, method checking, coverage probability, Normal, Poisson, Binomial,  shrinkage, \proglang{R}}
@@
 A two-level or multilevel model, also called a conditionally independent hierarchical model \cite{1989}, is a very powerful tool for exploring the hierarchical structure in data.
-For example, we can imagine that there exists a district-level hierarchy (bigger population) for observed school-level data, or a state-level hierarchy for observed hospital data in a certain state.
+For example, we can imagine that there exists a district-level hierarchy (bigger population) for observed school-level data, or a state-level hierarchy for observed hospital-level data in a certain state.
 
 \code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter.
-The \code{gbp} function allows users to choose one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their data sets.
+The \code{gbp} function allows users to choose one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets.
 
@@
 The following is a general Normal-Normal hierarchical model.
-For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates the \emph{j}-th group among \emph{k} groups in the data set.
+For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates the \emph{j}-th group among \emph{k} groups in the dataset.
 \begin{equation}
@@
 \begin{equation}
-\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(\lambda_{0j}r)\sim \textrm{Gamma} \left[\lambda_{0j}, ~\frac{\lambda_{0j}}{r} \right],
+\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(r\lambda_{0j})\sim \textrm{Gamma} \left[\lambda_{0j}, ~\frac{\lambda_{0j}}{r} \right],
 \end{equation}
@@
 \begin{equation} \label{gammapost}
-\lambda_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0j} + n_{j}y_{j})\sim\textrm{Gamma} \left[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}} \right],
+\lambda_{j}\vert \textbf{y}, \beta, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0j} + n_{j}y_{j})\sim\textrm{Gamma} \left[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}} \right],
 \end{equation}
@@
 \begin{equation} \label{betapost}
-p_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}y_{j},~r(1-p_{0j})+n_{j}(1-y_{j}))\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
+p_{j}\vert \textbf{y}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}y_{j},~r(1-p_{0j})+n_{j}(1-y_{j}))\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
 \end{equation}
@@
 Current popular methods of estimation via maximization (MLE or MAP) of these unknown shrinkage factors can result in estimates lying on the boundary of the parameter space.
-In the Normal-Normal model \cite{2012} this situation typically arises when the within-group variation is greater than the between-group variation resulting in a parameter estimate of $\hat{A} = 0$.
+In the Normal-Normal model this situation typically arises when the within-group variation is greater than the between-group variation resulting in a parameter estimate of $\hat{A} = 0$ \cite{2012}.
 
@@
 There are two kinds of model justification processes; one is a model checking and the other is a method checking.
-The model checking is for the justification of the model \ref{multilevel} on a specific data set.
-One possible question is, ``Can this data set benefit from such a multilevel modeling?'' \cite{1997} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
+The model checking is for the justification of the multilevel model on a specific dataset.
+One possible question is, ``Can this dataset benefit from such a multilevel modeling?'' \cite{1997} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
 They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
 
-Once we are sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this multilevel modeling.
+Once we make sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this multilevel modeling.
 ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating peudo-dataset and estimating coverage probability.
 
-For reference, the explanation will be based on Normal-Normal model because the idea can be easily applied to other two models.
+For reference, the explanation will be based on Normal-Normal model because the idea can be easily applied to the other two models.
 
@@
 Suppose we sampled 500 $\mathbf{\mu}_{(k\times1)}$'s, \emph{i.e.}, $\{\mathbf{\mu}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (2), where $A$ and $\beta$ are given.
-Then, we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each $\mu_{ij},$ where $i$ indicates the $i$-th pseudo-data set and $j$ does the $j$-th group.
+Then, we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each $\mu_{ij},$ where $i$ indicates the $i$-th pseudo-dataset and $j$ does the $j$-th group.
 
@@
 \subsection{Coverage Estimation Process}
-Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 peudo-datasets in order to obtain 500$\times$k interval estimates.
+Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 peudo-datasets in order to obtain 500$\times k$ interval estimates.
 
@@
 
-For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
+For this purpose, this person gathered data of 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
 The following code is an example of input based on the last ten hospital data.
@@
 Assuming an additional hierarchy is reasonable, a model-fitting process begins.
-Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital, the Poisson distribution would be the first choice to describe the uncertainty in our data.
+We know the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital.
+Then the independent Poisson distribution, \emph{i.e.},  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be the first choice to describe the uncertainty in our data.
 Note that caseload  ($n_{j}$) can be interpreted as an exposure, which is not necessarily an integer.
 
-Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in 2.2 .
+Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in the section 2.2.
 For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression (see section 3.2).
@@
 Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload.
-Though somewhat extreme, this is what happened to the two left-most hospitals in the first plot and this is why hierarchical modeling is a reasonable choice for this data set.
+Though somewhat extreme, this is what happened to the two left-most hospitals in the first plot and this is why hierarchical modeling is a reasonable choice for this dataset.
 
@@
 We can clearly see that all the posterior means (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line).
-For reference, if we want to draw this plot by the order of data input, \code{plot(p, sort = FALSE)} is a right adjustment.
-Overall, as the caseload increases towards the right and as the posterior mean gets closer to 0, the length of interval gets shorter, which the formula of posterior variance in (6) implies.
+For reference, if we want to draw this plot by the order of data input, \code{plot(p, sort = FALSE)} is the right adjustment.
 
@@
 The following method checking will answer this question.
-The \code{coverage} function below generates 10,000 pseudo-data sets regarding the estimated $r~(=336.37)$ as a given true value.
+The \code{coverage} function below generates 10,000 pseudo-datasets regarding the estimated $r~(=336.37)$ as a given true value.
 For reference, we can try any other value of $r$, for example $r=200$, by replacing below code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
@@
 Both lines are indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate.
-This result shows that the interval estimates from the suggested multilevel modeling on this particular data set have nice repeated sampling property.
+This result shows that the interval estimates from the suggested multilevel modeling on this particular dataset have nice repeated sampling property.
 
@@
 
-The data indicate that independent Binomial distribution is appropriate probability distribution for describing each player's number of hits among 45 at-bats conditioning on the unknown true batting average, \emph{i.e.}, $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
+The data indicate that independent Binomial distribution is appropriate probability distribution for describing each player's number of hits ($z_{j}$) among 45 at-bats conditioning on the unknown true batting average, \emph{i.e.}, $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
 For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
@@
 For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper line, there are short red lines toward five directions.
-This symbol also means that the seemingly two lines crossing over others were actually three lines for those who were outfielders (10th, 14th, and 15th hitters).
 
@@
 
-One more thing to emphasize is that observed sample means are all within the interval estimates.
-And these interval estimates also covered the batting averages over the remaining season successfully, although the result was left out.
 Then, how much can we trust these interval estimates?
-The following method check will answer it.
+The following method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values when it generates pseudo-datasets will answer it.
 
@@
 \end{figure}
-
-The meaning of putting the \code{gbp} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values when it generates pseudo-data sets.
 

### 2013-07-10 jss/article.tex
paper
editting paper

@@
 It is found that \pkg{Rgb} characterized by such Bayesian-frequentist reconciliation has strong points of both sides, working well in small samples and yielding good coverage probability.
-Following three examples for Gaussian, Poisson and Binomial data validate this point.}
+Following three examples for Gaussian, Poisson and Binomial data will validate this point.}
 \Keywords{hierarchical model, multilevel model, random effects mixed model, method checking, coverage probability, Normal, Poisson, Binomial,  shrinkage, \proglang{R}}
@@
 \begin{eqnarray}
-E(\mu_{j}\vert \textbf{y}) & = & E(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}) =E((1-B_{j})y_{j}+B_{j}\mu_{0j}\vert \textbf{y}).\\ 
+E(\mu_{j}\vert \textbf{y}) & = & E(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}), \\
 Var(\mu_{j}\vert \textbf{y}) & = & E(Var(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}).
@@
 
-The output contains information about sample mean ($y_{j}$), caseload ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower bound of interval estimate ($\hat{\lambda}_{low}$), posterior mean ($\hat{\lambda}=E(\lambda_{j}\vert \textbf{z})$), upper bound of interval estimate ($\hat{\lambda}_{upp}$), and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{z})$).
+The output contains information about sample mean ($y_{j}$), caseload ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower bound of interval estimate ($\hat{\lambda}_{low}$), posterior mean ($\hat{\lambda}=E(\lambda_{j}\vert \textbf{y})$), upper bound of interval estimate ($\hat{\lambda}_{upp}$), and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{y})$).
 
@@
 
-The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means, empty dots on the upper line, are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
+The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means, empty dots on the upper horizontal line, are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
 Note that some hospitals' ranks have changed by shrinking much harder towards 0.02 than others.
-For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly safest hospital among 31 hospitals in terms of the observed sample mean was not actually safer than the second safest hospital.
+For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly the safest hospital among 31 hospitals in terms of the observed death ratio was not actually safer than seemingly the second safest hospital.
 
@@
 \begin{CodeOutput}
-Summary for each unit (sorted by n):
+Summary for each unit (sorted by se):
 
@@
 
-Note that the posterior standard deviation tends to be bigger among outfielders than among others.
+%Note that the posterior standard deviation tends to be bigger among outfielders than among others.
 Let's see its formula in (9).
@@
 Our model is automatically reflecting on such uncertainty.
+
+The below summary includes the result of logistic regression fit because we did not know prior means in advance.
+We had to estimate them via this logistic regression model.
+Let's look at the p-value of the indicator covariate.
+It shows that the two prior means distinguishing outfielders from other positions were significantly different (p-value = 0.038), supporting our initial belief.
+The positive sign of $\hat{\beta}_{1}$ indicates that the mean batting average for all the outfielders tends to be higher than that for those in the other positions.
+
 \begin{CodeChunk}
@@
 
-This summary also includes the result of logistic regression fit because we did not know prior means in advance.
-We had to estimate them via this logistic regression model.
-Let's look at the p-value of the indicator covariate.
-It shows that the two prior means distinguishing outfielders from other positions were significantly different (p-value = 0.038), supporting our initial belief.
-The positive sign of $\hat{\beta}_{1}$ indicates that the mean batting average for all the outfielders tends to be higher than that for those in the other positions.
-\\
+Now, let's see following shrinkage and 95\% interval plots for more intuition.
+It is obvious that sample means (empty dots) on the upper line shrink towards two different means, 0.310 and 0.233.
+For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
+For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper horizontal line, there are short red lines toward five directions.
+
 \begin{CodeChunk}
@@
 
-Let's see shrinkage and 95\% interval plots for more intuition.
-It is obvious that sample means (empty dots) on the upper line shrink towards two different means, 0.310 and 0.233.
-For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
-For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper line, there are short red lines toward five directions.
-
-For reference, the observed sample mean among outfielders is 0.308 and that among other positions is 0.231.
+%For reference, the observed sample mean among outfielders is 0.308 and that among other positions is 0.231.
 But why are the estimated two prior means from this Binomial model 0.310 and 0.233 each?
@@
 Let's see the 10th, 14th, and 15th players on the graph for example.
-They are outfielders but their batting averages (sample mean) are far lower than the first five outfielders.
+They are outfielders but their observed batting averages are far lower than the first five outfielders.
 RTTM means that it can happen by their bad luck though in the long run their batting averages will come back to their expected ones as outfielders (blue horizontal line).
@@
 The following method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values when it generates pseudo-datasets will answer it.
+For reference, if we want to try different true parameters, the appropriate code will be \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 10000)} instead of below one.
 

### 2013-07-10 Rgbp/R/br.R

@@ -589,7 +589,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95,
                    post.intv.upp = post.res$post.intv.upp, model="br", X = X, 
                    beta.new = a.res$beta.new, beta.var = a.res$beta.var,
                    intercept = intercept, a.new = a.res$a.new, a.var = a.res$a.var, Alpha = Alpha,
-                   weight = NA)
+                   weight = NA, p = NA)
     output
 ######
   } else {
@@ -644,7 +644,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95,
                    post.mean = p.mean, post.sd = p.sd, 
                    prior.mean.hat = p0.mean, post.intv.low = intv[1, ], 
                    post.intv.upp = intv[2, ], model="br", X = X, 
-                   beta.new = b.mean, beta.var = b.var, weight = weight,
+                   beta.new = b.mean, beta.var = b.var, weight = weight, p = sampling.res$p.IS,
                    intercept = intercept, a.new = a.mean, a.var = a.var, Alpha = Alpha)
     output
   }

### 2013-07-10 Rgbp/R/pr.R

@@ -22,7 +22,7 @@ PRInitialValue2ndLevelMeanUnknown <- function(given) {
     stop()
   } else if (identical(x.ini, NA) & given$intercept) {
     x <- matrix(1, length(y), 1)
-    b.ini <- mean(y)
+    b.ini <- log(mean(y))
   } else if (!identical(x.ini, NA) & given$intercept) {
     x.ini <- as.matrix(x.ini)
     xname <- paste("x.ini[, ", 1 : ncol(x.ini), "]", sep = "")

### 2013-07-17 jss/article.tex
proofreading

@@
 \Abstract{
-\pkg{Rgbp} is an R package for estimating and validating a two-level model (a random-effects mixed model).
-The estimation procedure utilizes Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``method checking").
-It is found that \pkg{Rgb} characterized by such Bayesian-frequentist reconciliation has strong points of both sides, working well in small samples and yielding good coverage probability.
-Following three examples for Gaussian, Poisson and Binomial data will validate this point.}
+\pkg{Rgbp} is an R package that utilizes Bayesian machinery to provide a method of estimating two-level hierarchical models (also called random-effects mixed models) for Normal, Poisson, and Binomial data in a fast and computationally efficient manner.
+Good frequency property is another feature of \pkg{Rgbp}, which can be validated via its repeated sampling procedure called ``method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have strong points of both sides, working well in small samples and yielding good coverage probabilities for its interval estimates.}
 \Keywords{hierarchical model, multilevel model, random effects mixed model, method checking, coverage probability, Normal, Poisson, Binomial,  shrinkage, \proglang{R}}
@@
 %The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching.
-The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \cite{1981}.
+The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \citep{1981}.
 %\begin{CodeChunk}
@@
 %\subsection{Poisson: 31 Hospitals}
-%The following data are from medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 \cite{2012}.
+%The following data are from medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 \citep{2012}.
 It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and the total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$).
@@
 %\subsection{Binomial: 18 Baseball Hitters}
-%The following dataset contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \cite{1975}.
+%The following dataset contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \citep{1975}.
 In addition one covariate relating to the position each player was playing was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was an outfielder and 0 otherwise).
@@
 \section[Multilevel Structure]{Multilevel Structure} \label{multilevel}
-A two-level or multilevel model, also called a conditionally independent hierarchical model \cite{1989}, is a very powerful tool for exploring the hierarchical structure in data.
+A two-level or multilevel model, also called a conditionally independent hierarchical model \citep{1989}, is a very powerful tool for exploring the hierarchical structure in data.
 For example, we can imagine that there exists a district-level hierarchy (bigger population) for observed school-level data, or a state-level hierarchy for observed hospital-level data in a certain state.
@@
 \subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
-In our examples the hyper-prior distribution is an assumed distribution on the second-level parameters and with the goal of objectivity in mind \code{gbp} assumes non-informative hyper-prior distributions.
+The hyper-prior distribution is an assumed distribution on the second-level parameters and with the goal of objectivity in mind \code{gbp} assumes non-informative hyper-prior distributions.
 \begin{equation}
@@
 \subsection[Shrinkage Estimation]{Shrinkage Estimation}
-Estimating the shrinkage factors ($B_1, \ldots B_k$) is the key estimation problem with the hierarchical models \code{gbp} assumes.
+Estimating the shrinkage factors ($B_1, \ldots, B_k$) is the key estimation problem with the hierarchical models \code{gbp} assumes.
 As we can see in (\ref{normalpost}), (\ref{gammapost}), and (\ref{betapost}), the posterior means are a linear function of the shrinkage factors and the posterior variances are also linear (Gaussian), quadratic (Poisson), or cubic (Binomial) functions.
 A natural method then to estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ is to first estimate the shrinkage factors.
-%TODO: If we cite somgthing, (Morris, 2011) might be appropriate format to me, but in our case it looks Morris (2011), which is confusing.
 
@@
 Current popular methods of estimation via maximization (MLE or MAP) of these unknown shrinkage factors can result in estimates lying on the boundary of the parameter space.
-In the Normal-Normal model this situation typically arises when the within-group variation is greater than the between-group variation resulting in a parameter estimate of $\hat{A} = 0$ \cite{2012}.
+In the Normal-Normal model this situation typically arises when the within-group variation is greater than the between-group variation resulting in a parameter estimate of $\hat{A} = 0$ \citep{2012}.
 
-To continue with a maximization-based estimation procedure but to steer clear of aforementioned issues we make use of adjustment for density maximization (ADM) \cite{2011}.
+To continue with a maximization-based estimation procedure but to steer clear of aforementioned issues we make use of adjustment for density maximization (ADM) \citep{2011}.
 In general ADM is a procedure to obtain estimates of posterior moments via maximization if the underlying posterior can be approximated by a Pearson family.
@@
 \subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
-After estimating the two posterior moments, for example $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$, \code{gbp} reasonably approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
+After estimating the two posterior moments, for example $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$, \code{gbp} approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
 For the Binomial-Beta model we approximate $p_{j}\vert \textbf{z}$ with a Beta distribution and for the Poisson-Gamma model we approximate $\lambda_{j}\vert \textbf{z}$ with a Gamma distribution.
@@
 
-% TODO: Here, Christiansen and Morris (1997) seems appropriate format
 There are two kinds of model justification processes; one is a model checking and the other is a method checking.
@@
 
-For reference, the explanation will be based on Normal-Normal model because the idea can be easily applied to the other two models.
+From now on, the explanation will be based on Normal-Normal model because the idea can be easily applied to the other two models.
 
@@
 This expectation is the same as Pr$(\hat{\mu}_{ij, low}\le \mu_{ij} \le\hat{\mu}_{ij, upp}\vert y_{ij}, A, \beta)$, where ($\hat{\mu}_{ij, low}$, $\hat{\mu}_{ij, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
-We can calculate this probability  because we know the distribution of $\mu_{ij} \vert y_{ij}, A, \beta$ in (\ref{normalpost}).
+We can calculate this probability  because we know the distribution of ($\mu_{ij} \vert y_{ij}, A, \beta$) in (\ref{normalpost}).
 Note that conditioning on $y_{ij}$ is equivalent to conditioning on $\mathbf{y}$ as long as $A$ and $\beta$ are known.
@@
 We know the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital.
-Then the independent Poisson distribution, \emph{i.e.},  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be the first choice to describe the uncertainty in our data.
+Then the independent Poisson distribution, \emph{i.e.},  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be the first choice to describe the uncertainty in these data.
 Note that caseload  ($n_{j}$) can be interpreted as an exposure, which is not necessarily an integer.
@@
 Also, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is \code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "pr")}.
-Then, the function \code{coverage} will evaluate whether interval estimates achieve 90\% confidence level.
+Then, the below code will evaluate whether interval estimates achieve 90\% confidence level.
 
@@
 \subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}
-% TODO: As stated in ??
-As stated in \ref{8schooldata} the Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching.
-The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \cite{1981}.
+
+The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching.
+The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \citep{1981}.
 \begin{CodeChunk}
@@
 
-The following dataset from the New York Times published on 26 April 1970 contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \cite{1975}.
+The following dataset from the New York Times published on 26 April 1970 contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \citep{1975}.
 In addition one covariate relating to the position of each player was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was an outfielder and 0 otherwise).
@@
 Also note that shrinkage estimates are the same for all players.
-It makes sense because shrinkage ($B_{j}\equiv r / (r+n_{j})$) is determined by the relative amount of information between the first-level and the second-level hierarchies.
+It makes sense because shrinkage ($B_{j}\equiv r / (r+n_{j})$) is determined solely by the relative amount of information between the first-level and the second-level hierarchies.
 The fact that all players have the same amount of observed information ($n_{j}=45$) and $\hat{r}=\textrm{exp}(4.727)=113$ from below summary tell why the estimated shrinkage is 0.715 (=113 / (113 + 45)).
@@
 RTTM means that it can happen by their bad luck though in the long run their batting averages will come back to their expected ones as outfielders (blue horizontal line).
-The fact that their sample means are closer to the lower part of their 95\% intervals supports this argument.
-So, their posterior means (red dots) can also be interpreted as their RTTM.
+So, their posterior means (red dots) can be interpreted as their RTTM.
 
@@
 
-In short the \pkg{Rgbp} is an R package that utilizes Bayesian machinery to provide a method of estimating two-level hierarchical models from many families in a fast and computationally efficient manner.
-
 \section[acknowledgments]{Acknowledgments}

### 2013-07-22 jss/article.tex
small thing
ok

@@
 \pkg{Rgbp} is an R package that utilizes Bayesian machinery to provide a method of estimating two-level hierarchical models (also called random-effects mixed models) for Normal, Poisson, and Binomial data in a fast and computationally efficient manner.
-Good frequency property is another feature of \pkg{Rgbp}, which can be validated via its repeated sampling procedure called ``method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have strong points of both sides, working well in small samples and yielding good coverage probabilities for its interval estimates.}
+The method leads to good frequency properties that can be validated via its repeated sampling procedure called ``method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable both sides of the aisle, working well in small samples and yielding good coverage probabilities for its interval estimates.}
 \Keywords{hierarchical model, multilevel model, random effects mixed model, method checking, coverage probability, Normal, Poisson, Binomial,  shrinkage, \proglang{R}}
@@
 It is found that even in small samples our procedure yields good frequency properties in comparison to other methods such as Maximum Likelihood Estimation (MLE).
+
 This package will be useful for frequentists and Bayesians alike.
@@
 \code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter.
-The \code{gbp} function allows users to choose one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets.
+The \code{gbp} function allows users to choose one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta.
 
 \subsection[Normal-Normal]{Normal-Normal}
-The following is a general Normal-Normal hierarchical model.
+The following is the general Normal-Normal hierarchical model assumed by \code{gbp}.
 For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates the \emph{j}-th group among \emph{k} groups in the dataset.
@@
 \subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
-The hyper-prior distribution is an assumed distribution on the second-level parameters and with the goal of objectivity in mind \code{gbp} assumes non-informative hyper-prior distributions.
+The hyper-prior distribution is an assumed distribution on the second-level parameters. With the goal of objectivity in mind \code{gbp} assumes the following non-informative hyper-prior distributions:
 \begin{equation}
@@
 As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the location gets plentiful as the number of groups (\emph{k}) increases.
-The next flat prior distribution of the second-level variance component $A$ (or $1/r$) was chosen for its good repeated sampling properties and for posterior propriety under moderate conditions.
+The next flat prior distribution of the second-level variance component $A$ (or $1/r$) is chosen for its good repeated sampling properties and for posterior propriety under moderate conditions.
 
@@
 For the Binomial-Beta model we approximate $p_{j}\vert \textbf{z}$ with a Beta distribution and for the Poisson-Gamma model we approximate $\lambda_{j}\vert \textbf{z}$ with a Gamma distribution.
-Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\mu_{j}\vert \textbf{y}$ with a skewed-t distribution.
+Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\mu_{j}\vert \textbf{y}$ with a skewed-Normal distribution.
 
@@
 \section[Method Checking]{Method Checking}
-Like the two sides of the same coin, checking a statistical model always comes with fitting a model.
+Like the two sides of the same coin, checking a statistical model comes hand in hand with fitting the model.
 If a fitted model cannot pass a validation or checking process, we usually go back and forth from estimation and checking steps iteratively.
@@
 Once we make sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this multilevel modeling.
-``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating peudo-dataset and estimating coverage probability.
+``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating pseudo-dataset and estimating coverage probability.
 
@@
 \subsection{Coverage Estimation Process}
-Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 peudo-datasets in order to obtain 500$\times k$ interval estimates.
+Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 pseudo-datasets in order to obtain 500$\times k$ interval estimates.
 
@@
 Let's define an indicator variable, $I_{ij}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu_{ij}$ and 0 otherwise.
-One way to estimate the coverage probability is taking average over these indicator variables.
+One way to estimate the coverage probability is taking averages over these indicator variables.
 We call it a simple unbiased coverage probability estimate.
@@
 
-For this purpose, this person gathered data of 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
+For this purpose, data was gathered from 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
 The following code is an example of input based on the last ten hospital data.
@@
 \begin{figure}[h] 
+\label{fig:hospital_coverage}
 \begin{center}
@@
 
-It estimated coverage probabilities by simple unbiased estimates (a blue dashed line) and Rao-Blackwellized unbiased estimates (a red line).
+In \ref{fig:hospital_coverage} we see two estimated coverage probabilities: a simple unbiased estimate (a blue dashed line) and an Rao-Blackwellized unbiased estimate (a red line).
 Both lines are indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate.
@@
 
-\cite{1995} also looked into a similar ranking problem in hierarchical modeling, taking shrinkage into account.
+It is noted that \cite{1995} also investigated a similar ranking problem in hierarchical modeling, taking shrinkage into account.
 
@@
 \end{CodeChunk}
-\begin{figure}[h] \label{schoolcoverage}
+\begin{figure}[h] 
 \begin{center}
@@
 \end{center}
+\label{schoolcoverage}
 \end{figure}

### 2013-07-22 jss/article.tex
more proof reading

@@
 \subsection{Pseudo-data Generation Process}
-Figure 1 will be helpful to understand this process.
+Figure \ref{fig:pseudo} will be helpful to understand this process.
 As we can see in (\ref{normalpost}), the distribution of each true parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$.
@@
 \caption{Pseudo-data generating process}
+\label{fig:pseudo}
 \end{center}
@@
 \caption{Shrinkage plot and 95\% interval plot}
+\label{fig:hospshr}
 \end{center}
@@
 
-The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means, empty dots on the upper horizontal line, are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
+In Figure \ref{fig:hospshr} The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means, empty dots on the upper horizontal line, are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
 Note that some hospitals' ranks have changed by shrinking much harder towards 0.02 than others.
@@
 \begin{figure}[h] 
-\label{fig:hospital_coverage}
 \begin{center}
@@
 \caption{Coverage plot via method checking}
+\label{fig:hospital_coverage}
 \end{center}
@@
 From this there seems to be little evidence that the training provided much of an added benefit with every school's $95\%$ posterior interval containing 0.
-\pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in \ref{8schoolsplot}.
+\pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in Figure \ref{fig:8schoolsplot}.
 
@@
 
-\begin{figure}[h] \label{8schoolsplot}
+\begin{figure}[h] 
 \begin{center}
@@
 \caption{Shrinkage plot and 95\% interval plot for 8 schools}
+\label{fig:8schoolsplot}
 \end{center}
@@
 \caption{Coverage plot via method checking for 8 schools}
+\label{fig:schoolcoverage}
 \end{center}
-\label{schoolcoverage}
 \end{figure}
 %TODO: wrong reference. you mean 'As seen in Figure 5' below?
-As seen in \ref{schoolcoverage} the desired $95\%$ coverage probability was achieved for each group in this example.
+As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ coverage probability was achieved for each group in this example.
 
@@
 \caption{Shrinkage plot and 95\% interval plot}
+\label{fig:baseball}
 \end{center}
@@
 
-The 95\% interval plot shows us range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups.
+In Figure \ref{fig:baseball} the 95\% interval plot shows us range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups.
 Let's see the 10th, 14th, and 15th players on the graph for example.
@@
 \caption{Coverage plot via method checking}
+\label{fig:baseball2}
 \end{center}
@@
 
-Finally, the estimated average coverage probability is 0.973 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.
+Finally, in Figure \ref{fig:baseball2}, we see that the estimated average coverage probability is 0.973 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.
 

### 2013-07-22 jss/article.tex
ack
fix
small change

@@
 
-\subsubsection{Rao-Blackwellized Unbiased estimates of Coverage Probabilities}
+\subsubsection{Rao-Blackwellized Unbiased Estimates of Coverage Probabilities}
 Rao-Blackwellization improves accuracy of an unbiased estimator by taking conditional expectation given a sufficient statistic.
@@
 \caption{Coverage plot via method checking}
-\label{fig:hospital_coverage}
+\label{fig:hospitalcoverage}
 \end{center}
@@
 
-In \ref{fig:hospital_coverage} we see two estimated coverage probabilities: a simple unbiased estimate (a blue dashed line) and an Rao-Blackwellized unbiased estimate (a red line).
+In Figure \ref{fig:hospitalcoverage} we see two estimated coverage probabilities: a simple unbiased estimate (a blue dashed line) and an Rao-Blackwellized unbiased estimate (a red line).
 Both lines are indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate.
@@
 \end{figure}
-%TODO: wrong reference. you mean 'As seen in Figure 5' below?
+
 As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ coverage probability was achieved for each group in this example.
@@
 \section[acknowledgments]{Acknowledgments}
-
+The authors would like to thank Phil Everson and the 2012 class of Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
 \bibliography{bibliography}

### 2013-07-23 jss/article.tex
order

@@
 \author{Joseph Kelly\\Harvard University \And 
-             Carl Morris\\ Harvard University\And
-             Hyungsuk Tak\\Harvard University }
+             Hyungsuk Tak\\Harvard University\And
+             Carl Morris\\ Harvard University}
 \title{\pkg{Rgbp}: An R Package for Hierarchical Modeling and Method Checking}
@@
 
+  Hyungsuk Tak\\
+  Department of Statistics\\
+  Harvard University\\
+  1 Oxford Street, Cambridge, MA\\
+  E-mail: \email{tak@fas.harvard.edu}\\
+
   Carl Morris\\
@@
   E-mail: \email{morris@fas.harvard.edu}\\
-
-  Hyungsuk Tak\\
-  Department of Statistics\\
-  Harvard University\\
-  1 Oxford Street, Cambridge, MA\\
-  E-mail: \email{hyungsuk.tak@gmail.com}\\
-
 }
@@
 We call it a simple unbiased coverage probability estimate.
-For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first group.
+For example, $\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first group.
 

### 2013-07-24 jss/article.tex
4.1 and 4.2

@@
 For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates the \emph{j}-th group among \emph{k} groups in the dataset.
-\begin{equation}
+\begin{equation}\label{normalobs}
 y_{j}\vert \mu_{j} \stackrel{ind}{\sim}\textrm{Normal}(\mu_{j}, V_{j}),
 \end{equation}
-\begin{equation}
+\begin{equation}\label{normalprior}
 \mu_{j}\vert \beta, A\stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, A),
@@
 So, once we fix these hyper-parameters at specific values, we can generate true parameters.
-Suppose we sampled 500 $\mathbf{\mu}_{(k\times1)}$'s, \emph{i.e.}, $\{\mathbf{\mu}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (2), where $A$ and $\beta$ are given.
-Then, we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each $\mu_{ij},$ where $i$ indicates the $i$-th pseudo-dataset and $j$ does the $j$-th group.
+Suppose we generated 500 {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (\ref{normalprior}), where $A$ and $\beta$ are given.
+Then using (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}, $ where $i$ indicates the $i$-th simulation.
 
@@
 \subsection{Coverage Estimation Process}
-Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 pseudo-datasets in order to obtain 500$\times k$ interval estimates.
+Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 pseudo-datasets in order to obtain 500$\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, 500$\}.
+And then within each group, it will check simply how often the interval estimates include true parameters, or calculate Rao-Blackwellized coverage estimate.
 
 \subsubsection{Simple Unbiased Estimates of Coverage Probabilities}
-Let's define an indicator variable, $I_{ij}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu_{ij}$ and 0 otherwise.
-One way to estimate the coverage probability is taking averages over these indicator variables.
-We call it a simple unbiased coverage probability estimate.
-For example, $\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first group.
+Let's define an indicator variable, $I^{(i)}_{j}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu^{(i)}_{j}$ and 0 otherwise.
+One way to estimate the coverage probability is taking a sample mean of these indicator variables within each group (averaging over all $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ possible under given $A$ and $\beta$.
+We call it a simple unbiased estimate of coverage probability.
+For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased estimate of coverage probability for the first group, averaging over all $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500$, possible under the fixed $A$ and $\beta$.
+As the number of pseudo-datasets increases, this simple estimate will converge to $P(\mu_{1}\in(\hat{\mu}_{1,~low},~\hat{\mu}_{1,~upp}) \vert A, \beta)$.
 
 \subsubsection{Rao-Blackwellized Unbiased Estimates of Coverage Probabilities}
-Rao-Blackwellization improves accuracy of an unbiased estimator by taking conditional expectation given a sufficient statistic.
-Based on this idea, we define $E(I_{ij}\vert y_{ij}, A, \beta$), where $A$ and $\beta$ were given at first (see 4.1) and $y_{ij}$ is a sufficient statistic.
-This expectation is the same as Pr$(\hat{\mu}_{ij, low}\le \mu_{ij} \le\hat{\mu}_{ij, upp}\vert y_{ij}, A, \beta)$, where ($\hat{\mu}_{ij, low}$, $\hat{\mu}_{ij, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
-We can calculate this probability  because we know the distribution of ($\mu_{ij} \vert y_{ij}, A, \beta$) in (\ref{normalpost}).
-Note that conditioning on $y_{ij}$ is equivalent to conditioning on $\mathbf{y}$ as long as $A$ and $\beta$ are known.
-Then, we can estimate the first group's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert y_{i1}, A, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.
+Rao-Blackwellization improves accuracy of an unbiased estimator by taking a conditional expectation given a sufficient statistic.
+Based on this idea, we define $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ were given at first (see 4.1) and $y^{(i)}_{j}$ is a sufficient statistic of the $j$-th group in the $i$-th pseudo-dataset.
+This expectation is the same as Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
+We can calculate this probability  because we know the distribution of ($\mu^{(i)}_{j} \vert y^{(i)}_{j}, A, \beta$) in (\ref{normalpost}).
+Note that conditioning on $y^{(i)}_{j}$ is equivalent to conditioning on $\mathbf{y}^{(i)}_{(k\times1)}$ as long as $A$ and $\beta$ are known.
+Then, we can estimate the first group's coverage probability by $\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.
 

### 2013-07-25 jss/article.tex
small changes

@@
 where $m$ is the number of regression coefficients.
-As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the location gets plentiful as the number of groups (\emph{k}) increases.
+As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the second-level mean gets plentiful as the number of groups (\emph{k}) increases.
 The next flat prior distribution of the second-level variance component $A$ (or $1/r$) is chosen for its good repeated sampling properties and for posterior propriety under moderate conditions.
@@
 After estimating the two posterior moments, for example $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$, \code{gbp} approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
-For the Binomial-Beta model we approximate $p_{j}\vert \textbf{z}$ with a Beta distribution and for the Poisson-Gamma model we approximate $\lambda_{j}\vert \textbf{z}$ with a Gamma distribution.
-Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\mu_{j}\vert \textbf{y}$ with a skewed-Normal distribution.
+For the Binomial-Beta model we approximate the posterior distribution of $p_{j}$, \emph{i.e.} $\pi(p_{j}\vert \textbf{y})$, with a Beta distribution and for the Poisson-Gamma model we approximate $\pi(\lambda_{j}\vert \textbf{y})$ with a Gamma distribution.
+Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\pi(\mu_{j}\vert \textbf{y})$ with a skewed-Normal distribution.
 
@@
 Let's define an indicator variable, $I^{(i)}_{j}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu^{(i)}_{j}$ and 0 otherwise.
-One way to estimate the coverage probability is taking a sample mean of these indicator variables within each group (averaging over all $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ possible under given $A$ and $\beta$.
+One way to estimate the coverage probability is taking a sample mean of these indicator variables within each group, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ under fixed $A$ and $\beta$.
 We call it a simple unbiased estimate of coverage probability.
-For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased estimate of coverage probability for the first group, averaging over all $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500$, possible under the fixed $A$ and $\beta$.
-As the number of pseudo-datasets increases, this simple estimate will converge to $P(\mu_{1}\in(\hat{\mu}_{1,~low},~\hat{\mu}_{1,~upp}) \vert A, \beta)$.
+For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased estimate of coverage probability for the first group, accounting for possible $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given specific $A$ and $\beta$.
+As the number of pseudo-datasets increases, this simple estimate will converge to the true coverage probability given $A$ and $\beta$.
 
@@
 Rao-Blackwellization improves accuracy of an unbiased estimator by taking a conditional expectation given a sufficient statistic.
-Based on this idea, we define $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ were given at first (see 4.1) and $y^{(i)}_{j}$ is a sufficient statistic of the $j$-th group in the $i$-th pseudo-dataset.
+Based on this idea, we define $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ were given at first and $y^{(i)}_{j}$ is a sufficient statistic of the $j$-th group in the $i$-th pseudo-dataset.
 This expectation is the same as Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
@@
 Note that conditioning on $y^{(i)}_{j}$ is equivalent to conditioning on $\mathbf{y}^{(i)}_{(k\times1)}$ as long as $A$ and $\beta$ are known.
-Then, we can estimate the first group's coverage probability by $\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.
+Then, we can estimate the first group's coverage probability by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but more accurate than the previous simple estimator.
 
@@
 
-The output contains information about sample mean ($y_{j}$), caseload ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower bound of interval estimate ($\hat{\lambda}_{low}$), posterior mean ($\hat{\lambda}=E(\lambda_{j}\vert \textbf{y})$), upper bound of interval estimate ($\hat{\lambda}_{upp}$), and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{y})$).
+The output contains information about observed death ratio ($y_{j}$), caseload ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower bound of interval estimate ($\hat{\lambda}_{j, low}$), posterior mean ($\hat{\lambda}=E(\lambda_{j}\vert \textbf{y})$), upper bound of interval estimate ($\hat{\lambda}_{j, upp}$), and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{y})$).
 
-As we can see in (6), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a linear function of shrinkage, $B_{j}\equiv r / (r + n_{j})$, locating between the sample mean and prior mean ($\lambda_{0}=0.02$).
+As we can see in (\ref{gammapost}), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a linear function of shrinkage, $B_{j}\equiv r / (r + n_{j})$, locating between the sample mean and prior mean ($\lambda_{0}=0.02$).
 It makes sense because $r$ can be interpreted as the amount of prior information and $n_{j}$ as the amount of observed information.
@@
 
-A function ``\code{summary}'' shows selective information on hospitals and more detailed estimation result as below.
+A function \code{summary} shows selective information on hospitals and more detailed estimation result as below.
 To be specific, it displays some hospitals (not all as above) with minimum, median, and maximum caseloads ($n_{j}$).
@@
 
-We also need a graphical summary that can give us valuable insight buried in pile of numbers and a function `\code{plot}' is exactly for this purpose.
+We also need a graphical summary that can give us valuable insight buried in pile of numbers and a function \code{plot} is exactly for this purpose.
 \begin{CodeChunk}
@@
 
-In Figure \ref{fig:hospshr} The regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means, empty dots on the upper horizontal line, are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
+In Figure \ref{fig:hospshr} the regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means, empty dots on the upper horizontal line, are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
 Note that some hospitals' ranks have changed by shrinking much harder towards 0.02 than others.
-For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly the safest hospital among 31 hospitals in terms of the observed death ratio was not actually safer than seemingly the second safest hospital.
+For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly the safest hospital among 31 hospitals in terms of the observed death ratio is not actually safer than seemingly the second safest hospital.
 
 Intuitively, the result of multilevel modeling makes more sense than that of naive sample mean.
-For example, suppose there are two hospitals, whose sample means ($z_{j} / n_{j}$) are 0 and 0.001 and caseloads ($n_{j}$) are 1 and 1000 each.
+For example, suppose there are two hospitals, whose observed death ratios ($y_{j}$) are 0 and 0.001 and caseloads ($n_{j}$) are 1 and 1000 each.
 Do you believe that the former hospital, whose observed death rate is 0, is better than the latter and are you going to choose the former hospital?
@@
 
-Also, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is \code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "pr")}.
-Then, the below code will evaluate whether interval estimates achieve 90\% confidence level.
+Also, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is `\code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "pr")}.'  Then, the below code will evaluate whether interval estimates achieve 90\% confidence level.
 
@@
 \includegraphics[width = 5.5cm]{hospital2.png}
-\caption{Coverage plot via method checking}
+\caption{Coverage plot via method checking for 31 hospitals}
 \label{fig:hospitalcoverage}
@@
 
-\subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Prior Mean and One Covariate}
+\subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Second-level Mean and One Covariate}
 %The New York Times published on 26 April 1970 covered 18 baseball players' batting averages through their first official 45 at-bats of the 1970 season.
@@
 Now, let's see following shrinkage and 95\% interval plots for more intuition.
-It is obvious that sample means (empty dots) on the upper line shrink towards two different means, 0.310 and 0.233.
+It is obvious that sample means (empty dots) on the upper horizontal line shrink towards two different means, 0.310 and 0.233.
 For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
@@
 They are outfielders but their observed batting averages are far lower than the first five outfielders.
-RTTM means that it can happen by their bad luck though in the long run their batting averages will come back to their expected ones as outfielders (blue horizontal line).
+RTTM means that it can happen by their bad luck though in the long run their batting averages will come back to their expected ones as outfielders (blue horizontal lines).
 So, their posterior means (red dots) can be interpreted as their RTTM.
@@
 \includegraphics[width = 5.5cm]{baseball2.png}
-\caption{Coverage plot via method checking}
+\caption{Coverage plot via method checking for 18 players}
 \label{fig:baseball2}
@@
 The package aims to provide a procedure that is not only fast and easy to use but has good frequency properties and can be used in many scenarios.
-The package provides ``method checking'' functionality to examine repeated sampling properties and test that the method is valid at a particular parameter value.
+The package provides ``method checking'' functionality to examine repeated sampling properties and test that the method is valid at a wide range of parameter values.
 

### 2013-07-28 jss/article.tex
changes

@@
              Carl Morris\\ Harvard University}
-\title{\pkg{Rgbp}: An R Package for Hierarchical Modeling and Method Checking}
+\title{\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling}
 
@@
 \Abstract{
-\pkg{Rgbp} is an R package that utilizes Bayesian machinery to provide a method of estimating two-level hierarchical models (also called random-effects mixed models) for Normal, Poisson, and Binomial data in a fast and computationally efficient manner.
-The method leads to good frequency properties that can be validated via its repeated sampling procedure called ``method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable both sides of the aisle, working well in small samples and yielding good coverage probabilities for its interval estimates.}
-\Keywords{hierarchical model, multilevel model, random effects mixed model, method checking, coverage probability, Normal, Poisson, Binomial,  shrinkage, \proglang{R}}
+\pkg{Rgbp} is an R package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner.
+The main products of this package are point and interval estimates for the true parameters, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable both sides of the aisle, working well in small samples and yielding good coverage probabilities for its interval estimates.}
+\Keywords{hierarchical model, multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, gaussian, poisson, binomial,  shrinkage}
 \Plainkeywords{keywords, comma-separated, not capitalized, r} %% without formatting
@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-\pkg{Rgbp} is an R package for estimating and validating a two-level model (a random-effects mixed model).
-The estimation procedure utilizes Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``method checking").
+\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model (R$\ddot{\textrm{o}}$nneg${\aa}$rd et al, 2010), producing point and interval estiates of the true parameters.
+The estimation procedure utilizes approximate Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking").
 It is found that even in small samples our procedure yields good frequency properties in comparison to other methods such as Maximum Likelihood Estimation (MLE).
@@
 This package will be useful for frequentists and Bayesians alike.
-Bayesians are able to use the package to see a non-informative reference point before and after constructing their full-Bayesian hierarchical model and frequentists, now have a procedure that will provide confidence intervals of a random-effect mixed model with good repeated sampling properties.
+Bayesians are able to use the package to see a non-informative reference point before and after constructing their full-Bayesian hierarchical model and frequentists, now have a procedure that will provide confidence intervals of a conjugate hierarchical generalized llinear model with good repeated sampling properties.
 
@@
 
-\code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter.
+\code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate distribution on the first-level parameter.
 The \code{gbp} function allows users to choose one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta.
 
-\subsection[Normal-Normal]{Normal-Normal}
+\subsection[Normal-Normal]{Normal-Normal (`g'=Gaussian data)}
 The following is the general Normal-Normal hierarchical model assumed by \code{gbp}.
@@
 
-\subsection[Poisson-Gamma]{Poisson-Gamma}
+\subsection[Poisson-Gamma]{Poisson-Gamma (`p'=Poisson data)}
 \code{gbp} is also able to build a Poisson-Gamma multilevel model.
-Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket below indicates [mean, variance] of distribution.
-And for notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ for all $j$.
+Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket [, ] below indicates [mean, variance] of distribution.
+And for notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimates of $\lambda_{j}$, where $j=1, \ldots, k$.
 \begin{equation}
@@
 
-\subsection[Binomial-Beta]{Binomial-Beta}
+\subsection[Binomial-Beta]{Binomial-Beta (`b'=Binomial data)}
 Binomial-Beta hierarchical model is the last model that \code{gbp} can fit. Again, a square bracket below indicates [mean, variance] of distribution.
@@
 
-where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $r$ and $\beta$ are two unknown hyper-parameters. Then, corresponding posterior distribution is
+where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $r$ and $\beta$ are two unknown hyper-parameters. Then corresponding posterior distribution given unknown $(r, \beta)$ is
 \begin{equation} \label{betapost}
@@
 \subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
-The hyper-prior distribution is an assumed distribution on the second-level parameters. With the goal of objectivity in mind \code{gbp} assumes the following non-informative hyper-prior distributions:
+Our hyper-prior distribution is an assumed distribution on the second-level parameters. With the goal of objectivity in mind \code{gbp} assumes the following non-informative hyper-prior distributions:
 \begin{equation}
@@
 As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the second-level mean gets plentiful as the number of groups (\emph{k}) increases.
-The next flat prior distribution of the second-level variance component $A$ (or $1/r$) is chosen for its good repeated sampling properties and for posterior propriety under moderate conditions.
+The next flat prior distribution of the second-level variance component $A$ (or $1/r$) is chosen for its good repeated sampling properties for point and interval estimates of the true parameter $\{\mu_{j}\}$ over 2-level model \citep{2011}, and for posterior propriety under moderate conditions.
 
@@
 Estimating the shrinkage factors ($B_1, \ldots, B_k$) is the key estimation problem with the hierarchical models \code{gbp} assumes.
-As we can see in (\ref{normalpost}), (\ref{gammapost}), and (\ref{betapost}), the posterior means are a linear function of the shrinkage factors and the posterior variances are also linear (Gaussian), quadratic (Poisson), or cubic (Binomial) functions.
+As we can see in (\ref{normalpost}), (\ref{gammapost}), and (\ref{betapost}), the posterior means are a linear function of the shrinkage factors ($B_{j}$) and the posterior variances are also linear (Gaussian), quadratic (Poisson), or cubic (Binomial) functions.
 A natural method then to estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ is to first estimate the shrinkage factors.
 
-\subsection[ADM]{Adjustment for Density Maximization}
+\subsection[ADM]{Approximation via Adjustment for Density Maximization}
 It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
@@
 
-To continue with a maximization-based estimation procedure but to steer clear of aforementioned issues we make use of adjustment for density maximization (ADM) \citep{2011}.
+To continue with a maximization-based estimation procedure but to steer clear of aforementioned issues we make use of adjustment for density maximization (ADM) (another citation) \citep{1997, 2011}.
 In general ADM is a procedure to obtain estimates of posterior moments via maximization if the underlying posterior can be approximated by a Pearson family.
 For our purposes we can approximate the posterior distribution of a shrinkage factor with the Beta distribution allowing us to finally obtain estimates of the posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause.
-Please refer to \cite{2011} for additional advantages of ADM.
+See \cite{2011} for additional advantages of ADM.
 
@@
 %TODO: Haven't proof read method checking section yet
-\section[Method Checking]{Method Checking}
+\section[Frequency Method Checking]{Frequency Method Checking}
 Like the two sides of the same coin, checking a statistical model comes hand in hand with fitting the model.
@@
 So, once we fix these hyper-parameters at specific values, we can generate true parameters.
-Suppose we generated 500 {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (\ref{normalprior}), where $A$ and $\beta$ are given.
+Suppose we generated 500 $(=N_{sim}$) {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (\ref{normalprior}), where $A$ and $\beta$ are given.
 Then using (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}, $ where $i$ indicates the $i$-th simulation.
@@
 Let's define an indicator variable, $I^{(i)}_{j}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu^{(i)}_{j}$ and 0 otherwise.
-One way to estimate the coverage probability is taking a sample mean of these indicator variables within each group, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ under fixed $A$ and $\beta$.
-We call it a simple unbiased estimate of coverage probability.
-For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased estimate of coverage probability for the first group, accounting for possible $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given specific $A$ and $\beta$.
-As the number of pseudo-datasets increases, this simple estimate will converge to the true coverage probability given $A$ and $\beta$.
+Then \code{coverage} estimates the coverage probability via the sample mean of these indicator variables for each group, $j$, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ for given $A$ and $\beta$.
+This provides it a simple unbiased estimate of the $k$ coverage probabilities.
+For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased estimate of coverage probability for the first group ($j=1$), accounting for possible $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given a specific $(A, \beta)$.
+As the number of pseudo-datasets increases, this simple estimate converges to the true coverage probability of the first group given $A$ and $\beta$.
 
@@
 Rao-Blackwellization improves accuracy of an unbiased estimator by taking a conditional expectation given a sufficient statistic.
-Based on this idea, we define $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ were given at first and $y^{(i)}_{j}$ is a sufficient statistic of the $j$-th group in the $i$-th pseudo-dataset.
+Based on this idea, we define $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset.
 This expectation is the same as Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
@@
 Note that conditioning on $y^{(i)}_{j}$ is equivalent to conditioning on $\mathbf{y}^{(i)}_{(k\times1)}$ as long as $A$ and $\beta$ are known.
-Then, we can estimate the first group's coverage probability by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but more accurate than the previous simple estimator.
+Then, we estimate the first group's coverage probability by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$.
 
@@
 For this purpose, data was gathered from 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
-The following code is an example of input based on the last ten hospital data.
+And \pkg{Rgbp} will provide point and interval estimates of the true death ratio for each hospital so that one can choose the safest hospital.
+The following code is an example of input based on the last ten hospital data ($j=22, 23, \ldots, 31$).
 \begin{CodeChunk}
@@
 \includegraphics[width = 5.5cm]{hospital2.png}
-\caption{Coverage plot via method checking for 31 hospitals}
+\caption{Coverage plot via frequency method checking for 31 hospitals}
 \label{fig:hospitalcoverage}
@@
 Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
-Hence, we can use \code{gbp} to fit a Normal-Normal hierarchical model:
+Hence, we can use \code{gbp} to fit a Normal-Normal hierarchical model to produce point and interval estimates of the true coaching effect for each school:
 
@@
 \includegraphics[width = 5.5cm]{school2.png}
-\caption{Coverage plot via method checking for 8 schools}
+\caption{Coverage plot via frequency method checking for 8 schools}
 \label{fig:schoolcoverage}
@@
 The data indicate that independent Binomial distribution is appropriate probability distribution for describing each player's number of hits ($z_{j}$) among 45 at-bats conditioning on the unknown true batting average, \emph{i.e.}, $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
+Our goal is to estimate point and interval estimates of true batting average for each player.
 For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
 
-Suppose we are interested in their true batting averages and believe that the outfielder's batting averages are different from other positions' ones.
+Suppose we believe that the outfielder's batting averages are different from other positions' ones.
 So, it is desirable to assume two different second-level hierarchies for outfielders and for other positions, within each of which sharing information and regressing toward the mean (RTTM) occur.
@@
 Then, how much can we trust these interval estimates?
-The following method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values when it generates pseudo-datasets will answer it.
+The following frequency method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values when it generates pseudo-datasets will answer it.
 For reference, if we want to try different true parameters, the appropriate code will be \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 10000)} instead of below one.
@@
 \includegraphics[width = 5.5cm]{baseball2.png}
-\caption{Coverage plot via method checking for 18 players}
+\caption{Coverage plot via frequency method checking for 18 players}
 \label{fig:baseball2}
@@
 The package aims to provide a procedure that is not only fast and easy to use but has good frequency properties and can be used in many scenarios.
-The package provides ``method checking'' functionality to examine repeated sampling properties and test that the method is valid at a wide range of parameter values.
+The package provides ``frequency method checking'' functionality to examine repeated sampling properties and test that the method is valid at a wide range of parameter values.
 

### 2013-07-29 jss/article.tex
proofreading

@@
 As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the second-level mean gets plentiful as the number of groups (\emph{k}) increases.
-The next flat prior distribution of the second-level variance component $A$ (or $1/r$) is chosen for its good repeated sampling properties for point and interval estimates of the true parameter $\{\mu_{j}\}$ over 2-level model \citep{2011}, and for posterior propriety under moderate conditions.
+The next flat prior distribution of the second-level variance component $A$ (or $1/r$) is chosen for its good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, $\{\lambda_{j}\}$, or $\{p_{j}\}$ over 2-level model \citep{2011}, and for posterior propriety under moderate conditions.
 
@@
 Let's define an indicator variable, $I^{(i)}_{j}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu^{(i)}_{j}$ and 0 otherwise.
-Then \code{coverage} estimates the coverage probability via the sample mean of these indicator variables for each group, $j$, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ for given $A$ and $\beta$.
-This provides it a simple unbiased estimate of the $k$ coverage probabilities.
+Then \code{coverage} estimates the coverage probability via the sample mean of these indicator variables for each group $j$, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ for given $A$ and $\beta$.
+This provides a simple unbiased estimate of the $k$ coverage probabilities.
 For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased estimate of coverage probability for the first group ($j=1$), accounting for possible $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given a specific $(A, \beta)$.
@@
 
-For this purpose, data was gathered from 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
-And \pkg{Rgbp} will provide point and interval estimates of the true death ratio for each hospital so that one can choose the safest hospital.
+For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
+Using these data, \pkg{Rgbp} provides point and interval estimates of the true death ratio for each hospital so that one can choose the safest hospital.
 The following code is an example of input based on the last ten hospital data ($j=22, 23, \ldots, 31$).
@@
 Intuitively, the result of multilevel modeling makes more sense than that of naive sample mean.
-For example, suppose there are two hospitals, whose observed death ratios ($y_{j}$) are 0 and 0.001 and caseloads ($n_{j}$) are 1 and 1000 each.
+For example, suppose there are two hospitals, whose observed death ratios ($y_{j}$) are 0 and 0.001 and caseloads ($n_{j}$) are 10 and 1000 each.
 Do you believe that the former hospital, whose observed death rate is 0, is better than the latter and are you going to choose the former hospital?
-Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload.
+Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just ten caseloads.
 Though somewhat extreme, this is what happened to the two left-most hospitals in the first plot and this is why hierarchical modeling is a reasonable choice for this dataset.
@@
 The package aims to provide a procedure that is not only fast and easy to use but has good frequency properties and can be used in many scenarios.
-The package provides ``frequency method checking'' functionality to examine repeated sampling properties and test that the method is valid at a wide range of parameter values.
+The package provides ``frequency method checking'' functionality to examine repeated sampling properties and test that the method is valid at given hyper-parameter values.
 

### 2013-07-30 jss/article.tex
reference

@@
 As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the second-level mean gets plentiful as the number of groups (\emph{k}) increases.
-The next flat prior distribution of the second-level variance component $A$ (or $1/r$) is chosen for its good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, $\{\lambda_{j}\}$, or $\{p_{j}\}$ over 2-level model \citep{2011}, and for posterior propriety under moderate conditions.
+The next flat prior distribution of the second-level variance component $A$ (or $1/r$) is chosen for its good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, $\{\lambda_{j}\}$, or $\{p_{j}\}$ over 2-level model, and for posterior propriety under moderate conditions \citep{2011}.
 

### 2013-07-30 jss/article.tex
bibliography fixed

@@
   1 Oxford Street, Cambridge, MA\\
-  E-mail: \email{tak@fas.harvard.edu}\\
+  E-mail: \email{hyungsuk.tak@gmail.com}\\
 
@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model (R$\ddot{\textrm{o}}$nneg${\aa}$rd et al, 2010), producing point and interval estiates of the true parameters.
+\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010}, producing point and interval estiates of the true parameters.
 The estimation procedure utilizes approximate Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking").
@@
 
-To continue with a maximization-based estimation procedure but to steer clear of aforementioned issues we make use of adjustment for density maximization (ADM) (another citation) \citep{1997, 2011}.
+To continue with a maximization-based estimation procedure but to steer clear of aforementioned issues we make use of adjustment for density maximization (ADM) \citep{1997, carl1988, 2011}.
 In general ADM is a procedure to obtain estimates of posterior moments via maximization if the underlying posterior can be approximated by a Pearson family.

### 2013-07-31 jss/article.tex
revision after the meeting

@@
 \pkg{Rgbp} is an R package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner.
-The main products of this package are point and interval estimates for the true parameters, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable both sides of the aisle, working well in small samples and yielding good coverage probabilities for its interval estimates.}
-\Keywords{hierarchical model, multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, gaussian, poisson, binomial,  shrinkage}
+The main products of this package are point and interval estimates for the true parameters, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.}
+\Keywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage}
 \Plainkeywords{keywords, comma-separated, not capitalized, r} %% without formatting
@@
 This package will be useful for frequentists and Bayesians alike.
-Bayesians are able to use the package to see a non-informative reference point before and after constructing their full-Bayesian hierarchical model and frequentists, now have a procedure that will provide confidence intervals of a conjugate hierarchical generalized llinear model with good repeated sampling properties.
+Bayesians are able to use the package to see results for a non-informative reference prior before and after constructing their own Bayesian hierarchical model.
+Frequentists will have a procedure that meets or exceeds their confidence specification and repeated sampling.
 
@@
 \section[Multilevel Structure]{Multilevel Structure} \label{multilevel}
-A two-level or multilevel model, also called a conditionally independent hierarchical model \citep{1989}, is a very powerful tool for exploring the hierarchical structure in data.
+A two-level or multilevel model, also called a conditionally independent hierarchical model \citep{1989}, is a powerful tool for exploring the hierarchical structure in data.
 For example, we can imagine that there exists a district-level hierarchy (bigger population) for observed school-level data, or a state-level hierarchy for observed hospital-level data in a certain state.
 
-\code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate distribution on the first-level parameter.
-The \code{gbp} function allows users to choose one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta.
+\code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level has distributions of observed data and whose second-level has conjugate distributions on the first-level parameters.
+The \code{gbp} function allows users to choose one of three types of multilevel models, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta.
 
-\subsection[Normal-Normal]{Normal-Normal (`g'=Gaussian data)}
+\subsection[Normal-Normal]{Normal-Normal (``g''=Gaussian data)}
 The following is the general Normal-Normal hierarchical model assumed by \code{gbp}.
@@
 
-\subsection[Poisson-Gamma]{Poisson-Gamma (`p'=Poisson data)}
+\subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}
 \code{gbp} is also able to build a Poisson-Gamma multilevel model.
-Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket [, ] below indicates [mean, variance] of distribution.
-And for notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimates of $\lambda_{j}$, where $j=1, \ldots, k$.
+Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket [, ] below indicates [mean, variance] of a distribution.
+For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$, where $j=1, \ldots, k$.
 \begin{equation}
@@
 \end{equation}
-\begin{equation}
+\begin{equation}\label{gammaprior}
 \lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(r\lambda_{0j})\sim \textrm{Gamma} \left[\lambda_{0j}, ~\frac{\lambda_{0j}}{r} \right],
@@
 
-\subsection[Binomial-Beta]{Binomial-Beta (`b'=Binomial data)}
-Binomial-Beta hierarchical model is the last model that \code{gbp} can fit. Again, a square bracket below indicates [mean, variance] of distribution.
+Note that the variance in (\ref{gammaprior}) is linear in the mean, whereas a slightly different Poisson-Gamma specification \citep{1997} has been used elsewhere e.g.
+that makes the variance in (\ref{gammaprior}) quardratic.
+
+\subsection[Binomial-Beta]{Binomial-Beta (``b''=Binomial data)}
+Binomial-Beta hierarchical model is the last model that \code{gbp} can fit. Again, a square bracket below indicates [mean, variance] of a distribution.
 \begin{equation}
@@
 
-where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $r$ and $\beta$ are two unknown hyper-parameters. Then corresponding posterior distribution given unknown $(r, \beta)$ is
+where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $r$ and $\beta$ are two unknown hyper-parameters. Then corresponding posterior distribution given  $r$ and $\beta)$ is
 \begin{equation} \label{betapost}
@@
 \subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
-Our hyper-prior distribution is an assumed distribution on the second-level parameters. With the goal of objectivity in mind \code{gbp} assumes the following non-informative hyper-prior distributions:
+A hyper-prior distribution is a distribution assigned to the second-level parameters.
+With the goal of objectivity in mind our choice for hyper priors with \code{gbp} assumes the following non-informative hyper-prior distributions:
 \begin{equation}
@@
 where $m$ is the number of regression coefficients.
-As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the second-level mean gets plentiful as the number of groups (\emph{k}) increases.
-The next flat prior distribution of the second-level variance component $A$ (or $1/r$) is chosen for its good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, $\{\lambda_{j}\}$, or $\{p_{j}\}$ over 2-level model, and for posterior propriety under moderate conditions \citep{2011}.
+As for $\beta$, the flat non-informative distribution above is a common choice.
+In the Gaussian case, the flat prior distribution on the second level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
+In the other two cases, Poisson and Binomial, the distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Unif($0, \infty$) for the Gaussian.
+We will show the efficiency of this assignment  in the examples in section 5.
 
@@
 Estimating the shrinkage factors ($B_1, \ldots, B_k$) is the key estimation problem with the hierarchical models \code{gbp} assumes.
-As we can see in (\ref{normalpost}), (\ref{gammapost}), and (\ref{betapost}), the posterior means are a linear function of the shrinkage factors ($B_{j}$) and the posterior variances are also linear (Gaussian), quadratic (Poisson), or cubic (Binomial) functions.
+As we can see in (\ref{normalpost}), (\ref{gammapost}), and (\ref{betapost}), the posterior means are a linear function of the shrinkage factors ($B_{j}$) and the posterior variances are linear (Gaussian), quadratic (Poisson), and  approximately cubic (Binomial) functions of $B_{j}$.
 A natural method then to estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ is to first estimate the shrinkage factors.
@@
 It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
-Current popular methods of estimation via maximization (MLE or MAP) of these unknown shrinkage factors can result in estimates lying on the boundary of the parameter space.
-In the Normal-Normal model this situation typically arises when the within-group variation is greater than the between-group variation resulting in a parameter estimate of $\hat{A} = 0$ \citep{2012}.
+A common approach to approximate the distribution of $B_{j}$ is to find its MLE $\hat{B}_{j}(\hat{A}_{MLE})$ (or  $\hat{B}_{j}(\hat{r}_{MLE})$) and to use its asymptotic Normality.
+But MLE can result in estimates lying on the boundary of the parameter space, and its asymptotic Gaussian distribution is defined on $(-\infty, \infty)$ whereas $B_{j}$ is bounded between 0 and 1.
 
-To continue with a maximization-based estimation procedure but to steer clear of aforementioned issues we make use of adjustment for density maximization (ADM) \citep{1997, carl1988, 2011}.
-In general ADM is a procedure to obtain estimates of posterior moments via maximization if the underlying posterior can be approximated by a Pearson family.
-For our purposes we can approximate the posterior distribution of a shrinkage factor with the Beta distribution allowing us to finally obtain estimates of the posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause.
-See \cite{2011} for additional advantages of ADM.
+To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of adjustment for density maximization (ADM) \citep{carl1988, 1997, 2011}.
+For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, \emph{i.e.}  of $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without the boundary issues that MLE encounters.
+See \cite{2011}.
 
-Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only the data ($\textbf{y}$).
-Taking the Normal-Normal model as an example we note the following identities
+\subsection[Posterior Moment Estimation]{Posterior Moment Estimation}
+
+Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of true parameters given only the data ($\textbf{y}$).
+Taking the Normal-Normal model as an example, it estimates $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by the following identities
 \begin{eqnarray}
 E(\mu_{j}\vert \textbf{y}) & = & E(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}), \\
-Var(\mu_{j}\vert \textbf{y}) & = & E(Var(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}).
+Var(\mu_{j}\vert \textbf{y}) & = & E(Var(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}),
 \end{eqnarray}  
-Note that both $E(\mu_{j}\vert \textbf{y}, \beta, A)$ and $Var(\mu_{j}\vert \textbf{y}, \beta, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}) and since we can estimate $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, we can finally estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.
+where both $E(\mu_{j}\vert \textbf{y}, \beta, A)$ and $Var(\mu_{j}\vert \textbf{y}, \beta, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}).
 
@@
 After estimating the two posterior moments, for example $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$, \code{gbp} approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
-For the Binomial-Beta model we approximate the posterior distribution of $p_{j}$, \emph{i.e.} $\pi(p_{j}\vert \textbf{y})$, with a Beta distribution and for the Poisson-Gamma model we approximate $\pi(\lambda_{j}\vert \textbf{y})$ with a Gamma distribution.
+For the Binomial-Beta model we approximate the posterior distribution of $p_{j}$, $\pi(p_{j}\vert \textbf{y})$, with a Beta distribution and for the Poisson-Gamma model we approximate $\pi(\lambda_{j}\vert \textbf{y})$ with a Gamma distribution.
 Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\pi(\mu_{j}\vert \textbf{y})$ with a skewed-Normal distribution.
@@
 This provides a simple unbiased estimate of the $k$ coverage probabilities.
-For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased estimate of coverage probability for the first group ($j=1$), accounting for possible $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given a specific $(A, \beta)$.
+For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased estimate of coverage probability for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given a specific $(A, \beta)$.
 As the number of pseudo-datasets increases, this simple estimate converges to the true coverage probability of the first group given $A$ and $\beta$.
@@
 Rao-Blackwellization improves accuracy of an unbiased estimator by taking a conditional expectation given a sufficient statistic.
-Based on this idea, we define $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset.
+Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset.
 This expectation is the same as Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
@@
 The following code is an example of input based on the last ten hospital data ($j=22, 23, \ldots, 31$).
+Throughout this paper, the symbol `\code{R>}' represents a command prompt that you should not type on \proglang{R}.
 \begin{CodeChunk}

### 2013-07-31 jss/article.tex
all changes

@@
 R> data(hospital)
-R> z <- hospital$z
+R> z <- hospital$d
 R> n <- hospital$n
@@
 This result shows that the interval estimates from the suggested multilevel modeling on this particular dataset have nice repeated sampling property.
+For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.
 
@@
 
-As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ coverage probability was achieved for each group in this example.
+As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example.
+For reference, it took 188 seconds for 10,000 simulations  on one of authors' MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU.
+In MCMC, the exact simulation would be too time-consuming.
+One could compare curve in Figure \ref{fig:schoolcoverage} with a curve from MCMC.
 
@@
 Finally, in Figure \ref{fig:baseball2}, we see that the estimated average coverage probability is 0.973 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.
+As for the running time, it took 243 seconds for MacBook Pro equipped with a 2.3 GHz dual-core Interl i5 CPU to execute 10,000 simulations.
 
@@
 \section[acknowledgments]{Acknowledgments}
-The authors would like to thank Phil Everson and the 2012 class of Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
+The authors would like to thank Phil Everson, Cindy Christiansen, and the 2012 class of Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
+
 \bibliography{bibliography}

### 2013-07-31 jss/article.tex
small

@@
 As for $\beta$, the flat non-informative distribution above is a common choice.
-In the Gaussian case, the flat prior distribution on the second level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
+In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
 In the other two cases, Poisson and Binomial, the distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Unif($0, \infty$) for the Gaussian.
@@
 If the second level has more information than the first level, then the sample mean shrinks towards the prior mean more than 50\%.
-This point is clear in the above output because, as caseload increases, shrinkage decreases, depending less on the second level information.
+This point is clear in the above output because, as caseload increases, shrinkage decreases, depending less on the second-level information.
 

### 2013-08-02 jss/article.tex
lots of edits

@@
 \documentclass[article]{jss}
+
+%%uncomment line below for double-spacing
+%%\linespread{2}
 
@@
 See \cite{2011}.
+>>>>>>> 3c705aa06ceadc1c8ebef0446e4039dc98866b97
 
@@
 \subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
-Suppose a person living in the New York state (NY) has been suffering from severe coronary heart disease.
-If this person is supposed to receive the coronary artery bypass graft (CABG) surgery soon, he or she might want to find the most reliable hospital for dealing with such a surgery.
-On top of that, if this person can figure out each hospital's ability to handle this surgery, it will be useful for choosing a hospital.
+In this example we take the perspective of a person living in the state of New York (NY) and has been suffering from severe coronary heart disease.
+If this person is supposed to receive a coronary artery bypass graft (CABG) surgery soon, he or she might want to find the most reliable hospital for dealing with such a surgery.
 
 For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
-Using these data, \pkg{Rgbp} provides point and interval estimates of the true death ratio for each hospital so that one can choose the safest hospital.
+Using these data, \pkg{Rgbp} provides point and interval estimates of the true death ratio for each hospital so that one can choose the most reliable hospital.
 The following code is an example of input based on the last ten hospital data ($j=22, 23, \ldots, 31$).
@@
 
-In addition, while one looks for such information, suppose one knows that the state-level death rate per exposure of this surgery is 0.020.
+There are two extreme perspectives that the patient could take in this example.
+The first being that each hospital is identical in their ability to undertake CABG surgeries, in which case the choice of hospitals is irrelevant and the data could be pooled in order to estimate the death rate.
+The second, is that the hospitals are totally unrelated in which case the death rate estimate for each hospital would only be a function of the observed data for that particular hospital.
+These hospitals, however, are all subject to the same rules and regulations enforced by the federal and state governments and that there is likely similarities between hospitals.
+As such, a multilevel model seems to be a reasonable approach.
 
-The multilevel modeling that assumes a bigger population-level hierarchy will be insightful in this problem.
-Here, we presume a state-level (NY) hierarchy governing the true death rates ($\lambda$) of CABG surgery of all the hospitals in NY.
-This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution whose mean is 0.020.
+The patient can then presume a state-level (NY) hierarchy governing the true death rates ($\lambda$) of CABG surgery for all the hospitals in NY.
+This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution.
+In this example it is assumed that the true state-level death rate is known to be 0.020.
 
-Assuming an additional hierarchy is reasonable, a model-fitting process begins.
-We know the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital.
-Then the independent Poisson distribution, \emph{i.e.},  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be the first choice to describe the uncertainty in these data.
+As the state-level death rate is small we can conclude that the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital.
+Thus, the independent Poisson distribution, \emph{i.e.},  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be an ideal choice to describe these data.
 Note that caseload  ($n_{j}$) can be interpreted as an exposure, which is not necessarily an integer.
@@
 
-As we can see in (\ref{gammapost}), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a linear function of shrinkage, $B_{j}\equiv r / (r + n_{j})$, locating between the sample mean and prior mean ($\lambda_{0}=0.02$).
-It makes sense because $r$ can be interpreted as the amount of prior information and $n_{j}$ as the amount of observed information.
-If the second level has more information than the first level, then the sample mean shrinks towards the prior mean more than 50\%.
-This point is clear in the above output because, as caseload increases, shrinkage decreases, depending less on the second-level information.
+As we can see in (\ref{gammapost}), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a convex combination of the sample mean and prior mean ($\lambda_{0}=0.02$) with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight.
+This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree of prior and observed information respectively.
+If the second level has more information than the first level, then the estimator will shrink towards the prior mean more than 50\%.
+This is clear in this example because, as caseload increases, shrinkage decreases, depending less on the second-level information.
 
@@
 To be specific, it displays some hospitals (not all as above) with minimum, median, and maximum caseloads ($n_{j}$).
-On top of that, more specific estimation results, such as the estimation result of $\alpha\equiv\log(1/r)$, follow.
-Note that when we do not know the prior mean in advance unlike this hospital problem, \code{gbp} fits a linear regression for the Normal model, a log-linear regression for the Poisson model, or a logistic regression for the Binomial model and a summary of regression fit will appear.
+On top of that, more specific estimation results, such as the result of $\alpha\equiv\log(1/r)$, follow.
+Note that when we do not know the prior mean in advance unlike this hospital problem, \code{gbp} fits a linear regression for the Normal model, a log-linear regression for the Poisson model, or a logistic regression for the Binomial model.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
-Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which is a good indicator of how valuable and informative the hypothetical second-level hierarchy is.
+From the output of \code{Rgbp} we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which is a good indicator of how valuable and informative the hypothetical second-level hierarchy is.
 It means that observed sample means of hospitals whose caseloads are less than 336 will shrink toward the prior mean (0.020) more than 50\%.
 For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.834$) was calculated by 336 / (336 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.834)*0.045 + 0.834 * 0.020=0.024$.
-As for this hospital, using more information from the prior distribution is an appropriate choice because its observed amount of information (67) is far less than the amount of state-level information (336).
+As for this hospital, using more information from the prior distribution is an appropriate choice because the observed amount of information (67) is far less than the amount of state-level information (336).
 
-We also need a graphical summary that can give us valuable insight buried in pile of numbers and a function \code{plot} is exactly for this purpose.
+To obtain a graphical summary the function \code{plot} can be used, as seen in \ref{fig:hospshr}.
+
 \begin{CodeChunk}
@@
 
-Intuitively, the result of multilevel modeling makes more sense than that of naive sample mean.
+Multilevel modeling gives the patient the ability to borrow information across groups.
 For example, suppose there are two hospitals, whose observed death ratios ($y_{j}$) are 0 and 0.001 and caseloads ($n_{j}$) are 10 and 1000 each.
-Do you believe that the former hospital, whose observed death rate is 0, is better than the latter and are you going to choose the former hospital?
+Treating the hospitals as unrelated, the patient may conclude that the former hospital, whose observed death rate is 0, is superior than the latter.
 Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just ten caseloads.
-Though somewhat extreme, this is what happened to the two left-most hospitals in the first plot and this is why hierarchical modeling is a reasonable choice for this dataset.
 
-The estimated 95\% intervals are displayed on the right-side plot.
+In Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed on the right-hand side.
 We can clearly see that all the posterior means (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line).
-For reference, if we want to draw this plot by the order of data input, \code{plot(p, sort = FALSE)} is the right adjustment.
+For reference, to draw this plot by the order of data input the command, \code{plot(p, sort = FALSE)}, can be used.
 
-This interval plot can give us one more valuable insight, which we could not have noticed.
+From the output provided by \code{gbp} it can be seen that a reasonable choice of a hospital for the patient is hospital 23.
+Although hospital 8 has a smaller observed mean the fact that hospital 23 has a much higher caseload means that we borrow less information from other hospitals.
+The result being that the upper bound of the $95\%$ interval is smaller.
+
+% This interval plot provides one more valuable insight, which we could not have noticed.
 Let's look at the 8th and the 31st hospitals on the graph (or on the outcome for numeric reference).
@@
 
-Also it reveals that the 23rd hospital, whose estimated true rate was the smallest, has also the smallest upper bound.
+% Also it reveals that the 23rd hospital, whose estimated true rate was the smallest, has also the smallest upper bound.
 If you are a risk-adverse, this hospital will attract you most strongly.
@@
 
-Then, how reliable are these intervals?
-Does our procedure to generate interval estimates have good repeated sampling property?
-The following method checking will answer this question.
-The \code{coverage} function below generates 10,000 pseudo-datasets regarding the estimated $r~(=336.37)$ as a given true value.
-For reference, we can try any other value of $r$, for example $r=200$, by replacing below code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
+When fitting a model it is always a good idea to question how reliable the estimation procedure is.
+For example, does our procedure generate interval estimates that have good repeated sampling properties?
+To answer this question the \code{coverage} function generates pseudo-datasets regarding the estimated $r~(=336.37)$ as a given true value.
+For reference, we can try any other value of $r$, for example $r=200$, by replacing the code below with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
 
-Also, \code{gbp} can give us interval estimates with different confidence level, for example 90\%,  and the appropriate code adjustment is `\code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "pr")}.'  Then, the below code will evaluate whether interval estimates achieve 90\% confidence level.
+Also, \code{gbp} can provide interval estimates with different confidence levels, for example 90\%,  and the appropriate code adjustment is `\code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "pr")}.'  Then, the below code will evaluate whether interval estimates achieve the 90\% confidence level.
 
@@
 In Figure \ref{fig:hospitalcoverage} we see two estimated coverage probabilities: a simple unbiased estimate (a blue dashed line) and an Rao-Blackwellized unbiased estimate (a red line).
-Both lines are indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate.
-This result shows that the interval estimates from the suggested multilevel modeling on this particular dataset have nice repeated sampling property.
+Both lines are practically indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate.
+This result shows that the interval estimates for this particular dataset have a good repeated sampling property.
 For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.

### 2013-08-02 jss/article.tex
edits

@@
 
-\section[Multilevel Structure]{Multilevel Structure} \label{multilevel}
+\section[Hierarchical Structure]{Hierarchical Structure} \label{hierarchical}
 A two-level or multilevel model, also called a conditionally independent hierarchical model \citep{1989}, is a powerful tool for exploring the hierarchical structure in data.
@@
 \code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level has distributions of observed data and whose second-level has conjugate distributions on the first-level parameters.
-The \code{gbp} function allows users to choose one of three types of multilevel models, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta.
+The \code{gbp} function allows users to choose one of three types of hierarchical models, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta.
 
@@
 \subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}
-\code{gbp} is also able to build a Poisson-Gamma multilevel model.
+\code{gbp} is also able to build a Poisson-Gamma hierarchical model.
 Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket [, ] below indicates [mean, variance] of a distribution.
@@
 Note that the variance in (\ref{gammaprior}) is linear in the mean, whereas a slightly different Poisson-Gamma specification \citep{1997} has been used elsewhere e.g.
-that makes the variance in (\ref{gammaprior}) quardratic.
+that makes the variance in (\ref{gammaprior}) quadratic.
 
@@
 For the Binomial-Beta model we approximate the posterior distribution of $p_{j}$, $\pi(p_{j}\vert \textbf{y})$, with a Beta distribution and for the Poisson-Gamma model we approximate $\pi(\lambda_{j}\vert \textbf{y})$ with a Gamma distribution.
-Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\pi(\mu_{j}\vert \textbf{y})$ with a skewed-Normal distribution.
+Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\pi(\mu_{j}\vert \textbf{y})$ with a skewed-Normal distribution \citep{sn2013}.
 
-%TODO: should I put down the form of the skewed-t or just put a reference to it?
-
-%not sure we need this
-%To be specific, we assumed $p_{j}\vert \textbf{z}$ had another Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, with two parameters, $a_{1}$ and $a_{0}$, of this assumed Beta distribution.
-
-%TODO: Haven't proof read method checking section yet
 \section[Frequency Method Checking]{Frequency Method Checking}
@@
 There are two kinds of model justification processes; one is a model checking and the other is a method checking.
-The model checking is for the justification of the multilevel model on a specific dataset.
-One possible question is, ``Can this dataset benefit from such a multilevel modeling?'' \cite{1997} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
+The model checking is for the justification of the hierarchical model on a specific dataset.
+One possible question is, ``Can this dataset benefit from such a hierarchical modeling?'' \cite{1997} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
 They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
 
-Once we make sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this multilevel modeling.
+Once we make sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this hierarchical modeling.
 ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating pseudo-dataset and estimating coverage probability.
@@
 \subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
+\label{sec:ex:hosp}
 In this example we take the perspective of a person living in the state of New York (NY) and has been suffering from severe coronary heart disease.
@@
 Using these data, \pkg{Rgbp} provides point and interval estimates of the true death ratio for each hospital so that one can choose the most reliable hospital.
-The following code is an example of input based on the last ten hospital data ($j=22, 23, \ldots, 31$).
-Throughout this paper, the symbol `\code{R>}' represents a command prompt that you should not type on \proglang{R}.
+The data can be loaded into R using the following code:
 \begin{CodeChunk}
 \begin{CodeInput}
-R> z <- c( 14,   9,  15,  13,  35,  26,  25,  20,   35,   27)
-R> n <- c(593, 602, 629, 636, 729, 849, 914, 940, 1193, 1340)
+R> z <- c( 3, 2, 5, 11, 9, 12, 12, 4, 10, 13, 14, 7, 12, 11, 13, 22, 15, 
+          11, 14, 11, 16, 14, 9, 15, 13, 35, 26, 25, 20, 35, 27)
+R> n <- c(67, 68, 210, 256, 269, 274, 278, 295, 347, 349, 358, 396, 431,
+         441, 477, 484, 494, 501, 505, 540, 563, 593, 602, 629, 636, 729,
+         849, 914, 940, 1193, 1340)
 \end{CodeInput}
 \end{CodeChunk}
+or
+\begin{CodeChunk}
+\begin{CodeInput}
+R> data(hospitals)
+\end{CodeInput}
+\end{CodeChunk}
+
+Note that throughout this paper, the symbol `\code{R>}' represents a command prompt that you should not type on \proglang{R}.
 
@@
 These hospitals, however, are all subject to the same rules and regulations enforced by the federal and state governments and that there is likely similarities between hospitals.
-As such, a multilevel model seems to be a reasonable approach.
+As such, a hierarchical model seems to be a reasonable approach.
 
@@
 
-Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in the section 2.2.
+Next, \code{gbp} will help us fit the Poisson hierarchical model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in the section 2.2.
 For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression (see section 3.2).
@@
 
-Multilevel modeling gives the patient the ability to borrow information across groups.
+Hierarchical modeling gives the patient the ability to borrow information across groups.
 For example, suppose there are two hospitals, whose observed death ratios ($y_{j}$) are 0 and 0.001 and caseloads ($n_{j}$) are 10 and 1000 each.
@@
 This result shows that the interval estimates for this particular dataset have a good repeated sampling property.
-For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.
+
+% For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.
 
@@
 Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
-Hence, we can use \code{gbp} to fit a Normal-Normal hierarchical model to produce point and interval estimates of the true coaching effect for each school:
+It is assumed that the mean for each score is drawn from a common normal distribution and hence, we can use \code{gbp} to fit this Normal-Normal hierarchical model.
 
@@
 \end{CodeChunk}
-The output from \code{gbp} provides an easy way to read summary of the results of the estimation.
-From this there seems to be little evidence that the training provided much of an added benefit with every school's $95\%$ posterior interval containing 0.
+The output from \code{gbp} provides an easy to read summary of the results of the estimation.
+In the Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_i = V_i/(V_i + A)$ and as such those schools whose variation within the school is less than between the variation schools will shrink greater than $50\%$.
+The results provide by \code{gpb} suggests that there is little evidence that the training provided much of an added benefit with every school's $95\%$ posterior interval containing 0.
 \pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in Figure \ref{fig:8schoolsplot}.
@@
 Namely we can generate new pseudo-data from our assumed model by fixing the hyper-parameter values ($A$ and $\mu_0$ in this example) at their estimates.
-It is then possible to simulate ``true'' $\theta_i$ for each group $i$ and re-fit the model many times to estimate the coverage probabilities of our procedure.
+It is then possible to simulate ``true'' $\theta_i$ for each group $i$ and re-fit the model numerous times to estimate the coverage probabilities of our procedure.
 
@@
 As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example.
-For reference, it took 188 seconds for 10,000 simulations  on one of authors' MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU.
+
+% For reference, it took 188 seconds for 10,000 simulations  on one of authors' MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU.
 In MCMC, the exact simulation would be too time-consuming.
@@
 
-The data indicate that independent Binomial distribution is appropriate probability distribution for describing each player's number of hits ($z_{j}$) among 45 at-bats conditioning on the unknown true batting average, \emph{i.e.}, $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
-Our goal is to estimate point and interval estimates of true batting average for each player.
-For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
+Conditioning on the true batting average for each player we assume that the at-bats are independent and therefore, $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
+Our goal is to estimate point and interval estimates of the true batting average, $p_{j}$, for each player.
+%For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
 
-Suppose we believe that the outfielder's batting averages are different from other positions' ones.
-So, it is desirable to assume two different second-level hierarchies for outfielders and for other positions, within each of which sharing information and regressing toward the mean (RTTM) occur.
-Our multilevel modeling provides a way to incorporate such information (position) seamlessly into the second-level hierarchy.
+Suppose, also, that we observed a covariate indicating whether each player is an outfielder or not.
+It is reasonable to assume that the batting averages for outfielders are different from non-outfielders and therefore we assume different second-level hierarchies for outfielders and for other positions.
+Within each of which information is shared and regression towards the mean (RTTM) occurs.
+\code{gbp} provides a way to incorporate such information (position) seamlessly into the second-level hierarchy.
 
@@
 Finally, in Figure \ref{fig:baseball2}, we see that the estimated average coverage probability is 0.973 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.
-As for the running time, it took 243 seconds for MacBook Pro equipped with a 2.3 GHz dual-core Interl i5 CPU to execute 10,000 simulations.
+
+% As for the running time, it took 243 seconds for MacBook Pro equipped with a 2.3 GHz dual-core Interl i5 CPU to execute 10,000 simulations.
 

### 2013-08-02 jss/article.tex
up to In Figure 6 the 95% interval plot

@@
 Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233.
-Also note that shrinkage estimates are the same for all players.
-It makes sense because shrinkage ($B_{j}\equiv r / (r+n_{j})$) is determined solely by the relative amount of information between the first-level and the second-level hierarchies.
-The fact that all players have the same amount of observed information ($n_{j}=45$) and $\hat{r}=\textrm{exp}(4.727)=113$ from below summary tell why the estimated shrinkage is 0.715 (=113 / (113 + 45)).
+Also note that the shrinkage estimates are the same for all players due to the fact that they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($B_{j}\equiv r / (r+n_{j})$ = $\equiv exp(4.727) / (exp(4.727)+45)$ = 0.715).
 
@@
 
-The below summary includes the result of logistic regression fit because we did not know prior means in advance.
-We had to estimate them via this logistic regression model.
-Let's look at the p-value of the indicator covariate.
-It shows that the two prior means distinguishing outfielders from other positions were significantly different (p-value = 0.038), supporting our initial belief.
-The positive sign of $\hat{\beta}_{1}$ indicates that the mean batting average for all the outfielders tends to be higher than that for those in the other positions.
-
+In problems where a covariate is present \code{gbp} provides a regression summary (in this example logistic regression)
 \begin{CodeChunk}
@@
 \end{CodeChunk}
+
+We see that the two prior means distinguishing outfielders from other positions were significantly different (p-value = 0.038), supporting our initial belief.
+The positive sign of $\hat{\beta}_{1}$ indicates that the mean batting average for all the outfielders tends to be higher than that for those in the other positions.
 

### 2013-08-03 jss/article.tex
changes

@@
 R> data(hospitals)
+R> z <- hospitals$d
+R> n <- hospitals$n
 \end{CodeInput}
@@
 \begin{CodeInput}
-R> data(hospital)
-R> z <- hospital$d
-R> n <- hospital$n
 R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
@@
 
-Due to the fact that the estimation procedures in \pkg{Rgbp} rely on differentiation the package is extremely quick in fitting the available models.
+Due to the fact that the estimation procedures in \pkg{Rgbp} rely on derivatives, the package is extremely quick in fitting the available models.
 This makes the package ideal to be used in simulation studies where a hierarchical model needs to be fitted at every iteration and where running a full Bayesian model (via MCMC) would be computationally impractical.
@@
 \section[acknowledgments]{Acknowledgments}
-The authors would like to thank Phil Everson, Cindy Christiansen, and the 2012 class of Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
+The authors thank Prof Phil Everson of Swarthmore and the 2012 class of Harvard's Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
 

### 2013-08-03 jss/article.tex
changes

@@
 This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree of prior and observed information respectively.
-If the second level has more information than the first level, then the estimator will shrink towards the prior mean more than 50\%.
+If the second level has more information than the first level, \emph{i.e.} ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the estimator will shrink towards the prior mean more than 50\%.
 This is clear in this example because, as caseload increases, shrinkage decreases, depending less on the second-level information.
@@
 From the output provided by \code{gbp} it can be seen that a reasonable choice of a hospital for the patient is hospital 23.
-Although hospital 8 has a smaller observed mean the fact that hospital 23 has a much higher caseload means that we borrow less information from other hospitals.
+Although hospital 8 has a smaller observed mean the fact that hospital 23 has a much higher caseload means that we borrow relatively less information from other hospitals.
 The result being that the upper bound of the $95\%$ interval is smaller.
@@
 Both lines are practically indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate.
-This result shows that the interval estimates for this particular dataset have a good repeated sampling property.
+This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling.
 

### 2013-08-03 Rgbp/R/coverage.R
code coverage

@@ -410,8 +410,8 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 10) {
 
 
   # print output
-  output <- list(coverageRB = result, coverageU = result2, 
-                 average.coverageRB = avr.cov, average.coverageU = avr.cov2, 
-                 raw.resultRB = coverageRB, raw.resultU = coverageU)
+  output <- list(coverageRB = result, coverageS = result2, 
+                 average.coverageRB = avr.cov, average.coverageS = avr.cov2, 
+                 raw.resultRB = coverageRB, raw.resultS = coverageU)
   return(output)
 }

### 2013-08-05 jss/article.tex
chagnes

@@
 To answer this question the \code{coverage} function generates pseudo-datasets regarding the estimated $r~(=336.37)$ as a given true value.
-For reference, we can try any other value of $r$, for example $r=200$, by replacing the code below with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
+For reference, we can try any other value of $r$, for example $r=200$, by replacing the code below with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 1000)}.
 
@@
 \begin{CodeInput}
-R> pcv <- coverage(p, nsim = 10000)
+R> pcv <- coverage(p, nsim = 1000)
 \end{CodeInput}
@@
 
-In Figure \ref{fig:hospitalcoverage} we see two estimated coverage probabilities: a simple unbiased estimate (a blue dashed line) and an Rao-Blackwellized unbiased estimate (a red line).
-Both lines are practically indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate.
+In Figure \ref{fig:hospitalcoverage} we see three lines; one is a red line connecting Rao-Blackwellized unbiased estimates for 31 hospitals; another is a dashed blue line connecting simple unbiased estimates for those hospitals; a black horizontal line indicating the confidence level, 0.95.
+
+The estimated overall average coverage rate is 0.950 from both Rao-Blackwellized and simple unbiased estimates.
 This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling.
+Note that this estimate depends on the given true value of $r$ and the assumption that the model is true.
 
+If we want to check average Rao-Blackwellized unbiased estimates of coverage rate for each hospital, the following code gives us 31 estimates.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> pcv$coverageRB
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.950 0.950 0.950 0.951 0.950 0.950 0.951 0.950 0.950 0.950 0.951 0.951 
+[13] 0.950 0.950 0.950 0.950 0.951 0.950 0.950 0.950 0.950 0.951 0.950 0.950 
+[25] 0.951 0.950 0.951 0.950 0.951 0.951 0.950
+\end{CodeOutput}
+\end{CodeChunk}
+
+As for average simple unbiased estimates of coverage rate for each hospital, we can type the code below to obtain 31 estimates. 
+\begin{CodeChunk}
+\begin{CodeInput}
+R> pcv$coverageS
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.949 0.953 0.946 0.955 0.957 0.939 0.956 0.957 0.944 0.952 0.956 0.955 
+[13] 0.949 0.957 0.948 0.954 0.951 0.934 0.956 0.943 0.959 0.952 0.949 0.964 
+[25] 0.949 0.953 0.941 0.938 0.941 0.956 0.951
+\end{CodeOutput}
+\end{CodeChunk}
+
+The last thing to mention is the accuracy of Rao-Blackwellized unbiased estimates compared to that of simple one.
+Taking the first hospital as an example, we can calculate the sample variance of 1,000 Rao-Blackwellized unbiased estimates for the first hospital and that of 1,000 simple ones by typing following code.
+For reference, \code{raw.resultRB} and \code{raw.resultS} in \code{pcv} contains all the individual simulation results.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> var(pcv$raw.resultRB[1, ])
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.002031225
+\end{CodeOutput}
+\begin{CodeInput}
+R> var(pcv$raw.resultS[1, ])
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.04844745
+\end{CodeOutput}
+\end{CodeChunk}
+
+It shows that Rao-Blackwellized unbiased estimate is about 24 times more accurate than simple one.
+Also, as the number of simulation increases (for example 10,000), the zig-zagging blue line will be closer to the red line.
 % For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.
@@
 R> data(schools)
-R> attach(schools)
 R> g <- gbp(y, se, model = "gr")
@@
 \begin{CodeInput}
-R> gcv <- coverage(g, nsim = 10000)
+R> gcv <- coverage(g, nsim = 1000)
 \end{CodeInput}
@@
 As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example.
+Here, all the coverage estimates depend on the given true values of $A$ and $\beta_{0}$, and the assumption that the model is true.
+
+Average Rao-Blackwellized unbiased estimates of coverage rate for each school can be seen as below.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> gcv$coverageRB
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.966 0.957 0.966 0.962 0.960 0.961 0.960 0.969
+\end{CodeOutput}
+\end{CodeChunk}
+
+As for average simple unbiased estimates of coverage rate for each school, 
+\begin{CodeChunk}
+\begin{CodeInput}
+R> gcv$coverageS
+\end{CodeInput}
+\begin{CodeOutput}
+[1] 0.970 0.943 0.957 0.968 0.956 0.969 0.961 0.976
+\end{CodeOutput}
+\end{CodeChunk}
+
+Finally  when it comes to the first school,  Rao-Blackwellized unbiased estimate is about 24 times more accurate than simple one.
+It is based on the ratio of the sample variances of individual 1,000 estimates from two approaches.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> var(pcv$raw.resultS[1, ]) / var(pcv$raw.resultRB[1, ])
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 23.85134
+\end{CodeOutput}
+\end{CodeChunk}
 
@@
 The following frequency method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values when it generates pseudo-datasets will answer it.
-For reference, if we want to try different true parameters, the appropriate code will be \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 10000)} instead of below one.
+For reference, if we want to try different true parameters, the appropriate code will be \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of below one.
 
@@
 \begin{CodeInput}
-R> bcv <- coverage(b, nsim = 10000)
+R> bcv <- coverage(b, nsim = 1000)
 \end{CodeInput}
@@
 
-Finally, in Figure \ref{fig:baseball2}, we see that the estimated average coverage probability is 0.973 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.
+Finally, in Figure \ref{fig:baseball2}, we see that the estimated average coverage probability is 0.972 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.
+Each coverage estimate depends on given true values of $r$ and $\beta_{(2\times1)}$, and the assumption that the model is true.
 
+The average Rao-Blackwellized unbiased estimates of coverage rate for each player follows.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> bcv$coverageRB
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.972 0.972 0.973 0.972 0.972 0.970 0.974 0.972 0.973 0.973 0.973 0.970 
+[13] 0.972 0.972 0.973 0.972 0.973 0.972
+\end{CodeOutput}
+\end{CodeChunk}
+
+And also average simple unbiased estimates of coverage rate for each player can be obtained.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> bcv$coverageS
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.969 0.967 0.973 0.980 0.970 0.974 0.965 0.976 0.969 0.972 0.980 0.972 
+[13] 0.957 0.969 0.972 0.982 0.978 0.984
+\end{CodeOutput}
+\end{CodeChunk}
+
+Finally,  we see that Rao-Blackwellized unbiased estimate for the first player is about 26 times more accurate than simple one.
+It is based on the ratio of the sample variances of individual estimates from two approaches.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> var(bcv$raw.resultS[1, ]) / var(bcv$raw.resultRB[1, ])
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 25.64346
+\end{CodeOutput}
+\end{CodeChunk}
 % As for the running time, it took 243 seconds for MacBook Pro equipped with a 2.3 GHz dual-core Interl i5 CPU to execute 10,000 simulations.

### 2013-08-05 Rgbp/R/coverage.R

@@ -5,7 +5,7 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 10) {
   coverageRB <- matrix(NA, nrow = length(gbp.object$se), ncol = nsim)
 
   # 1-0 criterion that is 1 if interval includes true parameter, 0 if not
-  coverageU <- matrix(NA, nrow = length(gbp.object$se), ncol = nsim)
+  coverageS <- matrix(NA, nrow = length(gbp.object$se), ncol = nsim)
 
   if (missing(A.or.r)) {
     only.gbp.result <- TRUE
@@ -77,7 +77,7 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 10) {
           low <- out$post.intv.low
           upp <- out$post.intv.upp
           coverageRB[, i] <- pbeta(upp, a1, a0) - pbeta(low, a1, a0)
-          coverageU[, i] <- ifelse(low <= sim.p[, i] & sim.p[, i] <= upp, 1, 0)
+          coverageS[, i] <- ifelse(low <= sim.p[, i] & sim.p[, i] <= upp, 1, 0)
 
         }, error = function(x) {
                      print(c(i,"error"))
@@ -144,7 +144,7 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 10) {
           low <- out$post.intv.low
           upp <- out$post.intv.upp
           coverageRB[, i] <- pbeta(upp, a1, a0) - pbeta(low, a1, a0)
-          coverageU[, i] <- ifelse(low <= sim.p[, i] & sim.p[, i] <= upp, 1, 0)
+          coverageS[, i] <- ifelse(low <= sim.p[, i] & sim.p[, i] <= upp, 1, 0)
 
         }, error = function(x) {
                      print(c(i,"error"))
@@ -197,7 +197,7 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 10) {
           low <- out$post.intv.low
           upp <- out$post.intv.upp
           coverageRB[, i] <- pgamma(upp, sh, rt) - pgamma(low, sh, rt)
-          coverageU[, i] <- ifelse(low <= sim.lambda[, i] & sim.lambda[, i] <= upp, 1, 0)
+          coverageS[, i] <- ifelse(low <= sim.lambda[, i] & sim.lambda[, i] <= upp, 1, 0)
 
[…]

### 2013-08-05 Rgbp/R/gbp.R

@@ -1,15 +1,15 @@
 ######
 gbp <- function(x, w, covariates, mean.PriorDist, model, intercept, Alpha, n.IS, trial.scale) UseMethod("gbp")
 ######
-gbp.default <- function(x, w, covariates, mean.PriorDist, model = "gr", 
+gbp.default <- function(x, w, covariates, mean.PriorDist, model = "gaussian", 
                         intercept = TRUE, Alpha = 0.95, 
                         n.IS = 0, trial.scale = 2.5) {
 ######
   res <- switch(model, 
-           gr = gr(x, w, X = covariates, mu = mean.PriorDist, Alpha = Alpha, intercept = intercept), 
-           br = br(x, w, X = covariates, prior.mean = mean.PriorDist, intercept = intercept, Alpha = Alpha,
-                   n.IS = n.IS, trial.scale = trial.scale), 
-           pr = pr(x, w, X = covariates, prior.mean = mean.PriorDist, intercept = intercept, Alpha = Alpha))
+       gaussian = gr(x, w, X = covariates, mu = mean.PriorDist, Alpha = Alpha, intercept = intercept), 
+       binomial = br(x, w, X = covariates, prior.mean = mean.PriorDist, intercept = intercept, Alpha = Alpha,
+                     n.IS = n.IS, trial.scale = trial.scale), 
+       poisson = pr(x, w, X = covariates, prior.mean = mean.PriorDist, intercept = intercept, Alpha = Alpha))
   
   class(res) <- "gbp"	
   res

### 2013-08-05 mcmc/gaussian.R
changes

@@ -19,13 +19,13 @@ rstan_schools <- function(y, sigma){
   }
   parameters {
     real mu; 
-    real<lower=0> tau;
+    real<lower=0> tausq;
     real eta[J];
   }
   transformed parameters {
     real theta[J];
     for (j in 1:J)
-      theta[j] <- mu + tau * eta[j];
+      theta[j] <- mu + sqrt(tausq) * eta[j];
   }
   model {
     eta ~ normal(0, 1);

### 2013-08-05 jss/article.tex
changing gr, pr, br

@@
 \begin{CodeInput}
-R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
+R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "poisson")
 R> p
@@
 R> data(schools)
-R> g <- gbp(y, se, model = "gr")
+R> g <- gbp(y, se, model = "gaussian")
 R> g
@@
 \begin{CodeInput}
-R> b <- gbp(z, n, x, model = "br")
+R> b <- gbp(z, n, x, model = "binomial")
 R> b

### 2013-08-05 Rgbp/R/coverage.R
gr, pr, br changes

@@ -52,21 +52,21 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 10) {
 ######
           if(IS == 0) {
             out <- if (is.na(gbp.object$prior.mean) & identical(gbp.object$X, NA)) {
-                     gbp(sim.z[, i], n, model = "br", Alpha = gbp.object$Alpha)
+                     gbp(sim.z[, i], n, model = "binomial", Alpha = gbp.object$Alpha)
                    } else if (is.na(gbp.object$prior.mean) & !identical(gbp.object$X, NA)) {
-                     gbp(sim.z[, i], n, X, model = "br", Alpha = gbp.object$Alpha)
+                     gbp(sim.z[, i], n, X, model = "binomial", Alpha = gbp.object$Alpha)
                    } else if (!is.na(gbp.object$prior.mean)) {
-                     gbp(sim.z[, i], n, mean.PriorDist = p0, model = "br", Alpha = gbp.object$Alpha)
+                     gbp(sim.z[, i], n, mean.PriorDist = p0, model = "binomial", Alpha = gbp.object$Alpha)
                    }
           } else {
             out <- if (is.na(gbp.object$prior.mean) & identical(gbp.object$X, NA)) {
-                     gbp(sim.z[, i], n, model = "br", Alpha = gbp.object$Alpha,
+                     gbp(sim.z[, i], n, model = "binomial", Alpha = gbp.object$Alpha,
                          n.IS = length(gbp.object$weight))
                    } else if (is.na(gbp.object$prior.mean) & !identical(gbp.object$X, NA)) {
-                     gbp(sim.z[, i], n, X, model = "br", Alpha = gbp.object$Alpha,
+                     gbp(sim.z[, i], n, X, model = "binomial", Alpha = gbp.object$Alpha,
                          n.IS = length(gbp.object$weight))
                    } else if (!is.na(gbp.object$prior.mean)) {
-                     gbp(sim.z[, i], n, mean.PriorDist = p0, model = "br", Alpha = gbp.object$Alpha, 
+                     gbp(sim.z[, i], n, mean.PriorDist = p0, model = "binomial", Alpha = gbp.object$Alpha, 
                          n.IS = length(gbp.object$weight))
                    }
           }
@@ -119,22 +119,22 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 10) {
 ######
[…]

### 2013-08-14 jss/article.tex

@@
 
-\subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}
+\subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}\label{poissonsubsec}
 \code{gbp} is also able to build a Poisson-Gamma hierarchical model.
@@
 
-where $\log(\lambda_{0j}) =x_{j}'\beta$, $j=1, \ldots, k$, with two unknown hyper-parameters, $r$ and $\beta$. The posterior distribution of this Poisson-Gamma model is
+where $\log(\lambda_{0j}) =x_{j}'\beta$, $j=1, \ldots, k$, with two unknown hyper-parameters, $\beta$ and $r$. The posterior distribution of this Poisson-Gamma model given these hyper-parameters is
 \begin{equation} \label{gammapost}
@@
 
-where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $r$ and $\beta$ are two unknown hyper-parameters. Then corresponding posterior distribution given  $r$ and $\beta)$ is
+where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $\beta$ and $r$ are two unknown hyper-parameters. Then corresponding posterior distribution given  $\beta$ and $r$ is
 \begin{equation} \label{betapost}
@@
 A hyper-prior distribution is a distribution assigned to the second-level parameters.
-With the goal of objectivity in mind our choice for hyper priors with \code{gbp} assumes the following non-informative hyper-prior distributions:
+With the goal of objectivity in mind our choice for hyper-priors with \code{gbp} assumes the following non-informative hyper-prior distributions:
 \begin{equation}
@@
 In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
-In the other two cases, Poisson and Binomial, the distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Unif($0, \infty$) for the Gaussian.
+In the other two cases, Poisson and Binomial, the distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian.
 We will show the efficiency of this assignment  in the examples in section 5.
@@
 
-\subsection[ADM]{Approximation via Adjustment for Density Maximization}
+\subsection[ADM]{Approximation via Adjustment for Density Maximization}\label{ADM}
 It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
 A common approach to approximate the distribution of $B_{j}$ is to find its MLE $\hat{B}_{j}(\hat{A}_{MLE})$ (or  $\hat{B}_{j}(\hat{r}_{MLE})$) and to use its asymptotic Normality.
-But MLE can result in estimates lying on the boundary of the parameter space, and its asymptotic Gaussian distribution is defined on $(-\infty, \infty)$ whereas $B_{j}$ is bounded between 0 and 1.
+But its asymptotic Gaussian distribution is defined on $(-\infty, \infty)$ whereas $B_{j}$ is bounded between 0 and 1, and MLE can result in estimates lying on the boundary of the parameter space.
 
@@
 See \cite{2011}.
->>>>>>> 3c705aa06ceadc1c8ebef0446e4039dc98866b97
 
@@
 where both $E(\mu_{j}\vert \textbf{y}, \beta, A)$ and $Var(\mu_{j}\vert \textbf{y}, \beta, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}).
+We then estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by plugging-in approximately estimated two posterior moments of shrinkage factors.
 
@@
 Once we make sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this hierarchical modeling.
-``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating pseudo-dataset and estimating coverage probability.
+``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating pseudo-datasets and estimating coverage probabilities.
 
@@
 Using these data, \pkg{Rgbp} provides point and interval estimates of the true death ratio for each hospital so that one can choose the most reliable hospital.
-The data can be loaded into R using the following code:
+The data can be loaded into R using the following code.
+Note that throughout this paper, the symbol `\code{R>}' below represents a command prompt that you should not type on \proglang{R}.
+
 \begin{CodeChunk}
@@
 
-Note that throughout this paper, the symbol `\code{R>}' represents a command prompt that you should not type on \proglang{R}.
-
 There are two extreme perspectives that the patient could take in this example.
@@
 
-Next, \code{gbp} will help us fit the Poisson hierarchical model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in the section 2.2.
-For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression (see section 3.2).
+Next, \code{gbp} will help us fit the Poisson hierarchical model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in the section \ref{poissonsubsec}.
+For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression.
 \begin{CodeChunk}
@@
 
-The output contains information about observed death ratio ($y_{j}$), caseload ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower bound of interval estimate ($\hat{\lambda}_{j, low}$), posterior mean ($\hat{\lambda}=E(\lambda_{j}\vert \textbf{y})$), upper bound of interval estimate ($\hat{\lambda}_{j, upp}$), and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{y})$).
+The output contains information about observed death ratio ($y_{j}$), caseload ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower bound of interval estimate ($\hat{\lambda}_{j, low}$), posterior mean ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bound of interval estimate ($\hat{\lambda}_{j, upp}$), and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{y})$).
 
@@
 \end{CodeChunk}
-From the output of \code{Rgbp} we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which is a good indicator of how valuable and informative the hypothetical second-level hierarchy is.
+From the output of \code{summary} we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which is a good indicator of how valuable and informative the hypothetical second-level hierarchy is.
 It means that observed sample means of hospitals whose caseloads are less than 336 will shrink toward the prior mean (0.020) more than 50\%.
@@
 
-To obtain a graphical summary the function \code{plot} can be used, as seen in \ref{fig:hospshr}.
+To obtain a graphical summary the function \code{plot} can be used, as seen in Figure \ref{fig:hospshr}.
 
@@
 \includegraphics[scale=0.25]{hospital1.png}
-\caption{Shrinkage plot and 95\% interval plot}
+\caption{Shrinkage plot and 95\% interval plot for 31 hospitals}
 \label{fig:hospshr}
@@
 
-Also, \code{gbp} can provide interval estimates with different confidence levels, for example 90\%,  and the appropriate code adjustment is `\code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "pr")}.'  Then, the below code will evaluate whether interval estimates achieve the 90\% confidence level.
+Also, \code{gbp} can provide interval estimates with different confidence levels, for example 90\%,  and the appropriate code adjustment is `\code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "poisson")}.'  Then, the below code will evaluate whether interval estimates achieve the 90\% confidence level.
 
@@
 
-In Figure \ref{fig:hospitalcoverage} we see three lines; one is a red line connecting Rao-Blackwellized unbiased estimates for 31 hospitals; another is a dashed blue line connecting simple unbiased estimates for those hospitals; a black horizontal line indicating the confidence level, 0.95.
+In Figure \ref{fig:hospitalcoverage} we see three lines; one is a red line connecting Rao-Blackwellized unbiased estimates for 31 hospitals; another is a dashed blue line connecting simple unbiased estimates for those hospitals; the other is a black horizontal line indicating the confidence level, 0.95.
 
@@
 This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling.
-Note that this estimate depends on the given true value of $r$ and the assumption that the model is true.
+Note that these estimates depend on the given true value of $r$ and the assumption that the model is true.
 
-If we want to check average Rao-Blackwellized unbiased estimates of coverage rate for each hospital, the following code gives us 31 estimates.
+If we want to check average Rao-Blackwellized unbiased estimates for each hospital, the following code gives us such estimates.
 \begin{CodeChunk}
@@
 
-As for average simple unbiased estimates of coverage rate for each hospital, we can type the code below to obtain 31 estimates. 
+As for average simple unbiased estimates for each hospital, we can type the code below.
 \begin{CodeChunk}
@@
 
-The last thing to mention is the accuracy of Rao-Blackwellized unbiased estimates compared to that of simple one.
+One more thing to mention is the accuracy of Rao-Blackwellized unbiased estimates compared to that of simple ones.
 Taking the first hospital as an example, we can calculate the sample variance of 1,000 Rao-Blackwellized unbiased estimates for the first hospital and that of 1,000 simple ones by typing following code.
-For reference, \code{raw.resultRB} and \code{raw.resultS} in \code{pcv} contains all the individual simulation results.
+For reference, \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual simulation results.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
+or
+\begin{CodeChunk}
+\begin{CodeInput}
+R> data(schools)
+R> y  <- schools$y
+R> se <- schools$se
+\end{CodeInput}
+\end{CodeChunk}
 
@@
 \begin{CodeInput}
-R> data(schools)
 R> g <- gbp(y, se, model = "gaussian")
@@
 
-As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example.
-Here, all the coverage estimates depend on the given true values of $A$ and $\beta_{0}$, and the assumption that the model is true.
+As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (black horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example.
+Note that all the coverage estimates depend on the given true values of $A$ and $\beta_{0}$, and the assumption that the model is true.
 
-Average Rao-Blackwellized unbiased estimates of coverage rate for each school can be seen as below.
+In addition, average Rao-Blackwellized unbiased estimates for each school can be seen as below.
 \begin{CodeChunk}
@@
 
-As for average simple unbiased estimates of coverage rate for each school, 
+As for average simple unbiased estimates for each school, 
 \begin{CodeChunk}
@@
 
-Finally  when it comes to the first school,  Rao-Blackwellized unbiased estimate is about 24 times more accurate than simple one.
-It is based on the ratio of the sample variances of individual 1,000 estimates from two approaches.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> var(pcv$raw.resultS[1, ]) / var(pcv$raw.resultRB[1, ])
-\end{CodeInput}
-\begin{CodeOutput}
- [1] 23.85134
-\end{CodeOutput}
-\end{CodeChunk}
+All the individual simulation results are saved in \code{pcv$raw.resultRB} and \code{pcv$raw.resultS}, in which each row is about each school.
 
@@
 R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
+\end{CodeInput}
+\end{CodeChunk}
+or
+\begin{CodeChunk}
+\begin{CodeInput}
+R> data(baseball)
+R> z <- baseball[, 4]
+R> n <- baseball[, 3]
+R> x <- ifelse(baseball$Position == "fielder", 1, 0)
 \end{CodeInput}
@@
 Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233.
-Also note that the shrinkage estimates are the same for all players due to the fact that they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($B_{j}\equiv r / (r+n_{j})$ = $\equiv exp(4.727) / (exp(4.727)+45)$ = 0.715).
+Also note that the shrinkage estimates are the same for all players due to the fact that they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($\hat{B}_{j}\equiv \hat{r} / (\hat{r}+45)$ = $e^{4.727} / (e^{4.727}+45)$ = 0.715).
+The estimation results including $\hat{r}=e^{4.727}$ follows.
 
@@
 
-In problems where a covariate is present \code{gbp} provides a regression summary (in this example logistic regression)
+%In problems where a covariate is present \code{gbp} provides a regression summary (in this example logistic regression)
 \begin{CodeChunk}
@@
 
-We see that the two prior means distinguishing outfielders from other positions were significantly different (p-value = 0.038), supporting our initial belief.
+We see that the two prior means distinguishing outfielders from other positions are significantly different (p-value = 0.038), supporting our initial belief.
 The positive sign of $\hat{\beta}_{1}$ indicates that the mean batting average for all the outfielders tends to be higher than that for those in the other positions.
@@
 Now, let's see following shrinkage and 95\% interval plots for more intuition.
-It is obvious that sample means (empty dots) on the upper horizontal line shrink towards two different means, 0.310 and 0.233.
+It is obvious that sample means (empty dots) on the upper horizontal line shrink towards two different means, 0.233 and 0.310.
 For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
@@
 \includegraphics[scale=0.3]{baseball1.png}
-\caption{Shrinkage plot and 95\% interval plot}
+\caption{Shrinkage plot and 95\% interval plot for 18 baseball players}
 \label{fig:baseball}
@@
 Then, how much can we trust these interval estimates?
-The following frequency method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values when it generates pseudo-datasets will answer it.
-For reference, if we want to try different true parameters, the appropriate code will be \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of below one.
+The following frequency method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values will answer it.
+For reference, if we want to try different true values, the appropriate code will be \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of below one.
 
@@
 Finally, in Figure \ref{fig:baseball2}, we see that the estimated average coverage probability is 0.972 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.
-Each coverage estimate depends on given true values of $r$ and $\beta_{(2\times1)}$, and the assumption that the model is true.
+Note that each coverage estimate depends on given true values of $r$ and $\beta_{(2\times1)}$, and the assumption that the model is true.
 
-The average Rao-Blackwellized unbiased estimates of coverage rate for each player follows.
+The average Rao-Blackwellized unbiased estimates for each player follows.
 \begin{CodeChunk}
@@
 
-And also average simple unbiased estimates of coverage rate for each player can be obtained.
+And average simple unbiased estimates for each player are
 \begin{CodeChunk}
@@
 
-Finally,  we see that Rao-Blackwellized unbiased estimate for the first player is about 26 times more accurate than simple one.
+All the individual simulation results are saved in \code{bcv$raw.resultRB} and \code{bcv$raw.resultS}, in which each row is about each player.
+
+%Finally,  we see that Rao-Blackwellized unbiased estimate for the first player is about 26 times more accurate than simple one.
 It is based on the ratio of the sample variances of individual estimates from two approaches.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> var(bcv$raw.resultS[1, ]) / var(bcv$raw.resultRB[1, ])
-\end{CodeInput}
-\begin{CodeOutput}
- [1] 25.64346
-\end{CodeOutput}
-\end{CodeChunk}
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%R> var(bcv$raw.resultS[1, ]) / var(bcv$raw.resultRB[1, ])
+%\end{CodeInput}
+%\begin{CodeOutput}
+% [1] 25.64346
+%\end{CodeOutput}
+%\end{CodeChunk}
 % As for the running time, it took 243 seconds for MacBook Pro equipped with a 2.3 GHz dual-core Interl i5 CPU to execute 10,000 simulations.
@@
 \pkg{Rgbp} is an R package for estimating and validating a two-level hierarchical model.
-The package aims to provide a procedure that is not only fast and easy to use but has good frequency properties and can be used in many scenarios.
+The package aims to provide a procedure that is not only fast and easy to use but has good frequency properties and can be used in many scenarios for estimating point and interval estimates of true parameters.
 The package provides ``frequency method checking'' functionality to examine repeated sampling properties and test that the method is valid at given hyper-parameter values.
 
-In addition to good frequency properties Bayesians will be able to use the package to see the results from a non-informative reference point.
+%In addition to good frequency properties Bayesians will be able to use the package to see the results from a non-informative reference point.
 This allows the user to examine whether it is worth to implement a full Bayesian model (which is often more time consuming).
@@
 Due to the fact that the estimation procedures in \pkg{Rgbp} rely on derivatives, the package is extremely quick in fitting the available models.
-This makes the package ideal to be used in simulation studies where a hierarchical model needs to be fitted at every iteration and where running a full Bayesian model (via MCMC) would be computationally impractical.
+This makes the package ideal to be used in simulation studies where a hierarchical model needs to be fitted at every iteration and where running a Bayesian model via MCMC would be computationally impractical.
 
 \section[acknowledgments]{Acknowledgments}
-The authors thank Prof Phil Everson of Swarthmore and the 2012 class of Harvard's Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
+The authors thank Professor Phil Everson of Swarthmore and the 2012 class of Harvard's Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
 

### 2013-08-15 Rgbp/R/gr.R
gr changed

@@ -81,14 +81,13 @@ gr<-function(y,se,X,mu,Alpha=0.95,intercept=T,eps=0.0001){
 	
   ## calculate CIs using skewed normal
   ## TODO: use apply not loop
-  snparam <- matrix(nrow=length(thetahat),ncol=3)
-  skewedmat <- c()
-  for(i in 1:length(thetahat)){    
-    snparam[i,] <- gr.cp.to.dp(c(thetahat[i],shat[i],sign(skew[i])*min(abs(skew[i]),0.94)))
-    row <- c(qsn((1-Alpha)/2,snparam[i,1],snparam[i,2],snparam[i,3]),thetahat[i],qsn(1-(1-Alpha)/2,snparam[i,1],snparam[i,2],snparam[i,3]))
-    skewedmat <- rbind(skewedmat,row)
-  }
-  skewedmat <- as.matrix(skewedmat)
+  tmp <- lapply(1:length(thetahat), function(i){
+    snparam <- gr.cp.to.dp(c(thetahat[i],shat[i],sign(skew[i])*min(abs(skew[i]),0.94)))
+    row <- c(qsn((1-Alpha)/2,snparam),thetahat[i],qsn(1-(1-Alpha)/2,snparam))
+    return(row)
+  })
+  skewedmat <- as.matrix(do.call("rbind", tmp))
+
   
   ## return output
   ## TODO: discuss with Tak and sync output

### 2013-08-15 profiler.R

@@ -1,0 +1,6 @@
+library(Rgbp)
+data(schools)
+Rprof("gr.out")
+lapply(1:1000,function(x){gbp(schools$y, schools$se)})
+Rprof(NULL)
+summaryRprof("gr.out")

### 2013-08-15 qinstall.R

@@ -1,3 +1,3 @@
 #!/usr/bin/R
-install.packages("Rgbp_1.0.0.tar.gz",repos=NULL,type="source")
+install.packages("Rgbp_1.0.1.tar.gz",repos=NULL,type="source")
 library(Rgbp)

### 2013-08-20 Rgbp/R/gr.R
ok

@@ -84,7 +84,7 @@ gr<-function(y,se,X,mu,Alpha=0.95,intercept=T,eps=0.0001){
   
   tmp <- lapply(1:length(thetahat), function(i){
     snparam <- as.numeric(gr.cp.to.dp(c(thetahat[i],shat[i],sign(skew[i])*min(abs(skew[i]),0.94))))
-    row <- c(qsn((1-Alpha)/2,snparam[1], snparam[2], snparam[3]),thetahat[i],qsn(1-(1-Alpha)/2,snparam[1], snparam[2], snparam[3]))
+    row <- c(qsn((1-Alpha)/2,snparam[1], snparam[2], snparam[3], engine = "biv.nt.prob"),thetahat[i],qsn(1-(1-Alpha)/2,snparam[1], snparam[2], snparam[3], engine = "biv.nt.prob"))
     return(row)
   })
   skewedmat <- as.matrix(do.call("rbind", tmp))

### 2013-08-20 jss/article.tex
paper

@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010}, producing point and interval estiates of the true parameters.
+\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} or called a conditionally independent hierarchical model \citep{1989}, producing point and interval estimates of the true parameters.
 The estimation procedure utilizes approximate Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking").
@@
 \section[Hierarchical Structure]{Hierarchical Structure} \label{hierarchical}
-A two-level or multilevel model, also called a conditionally independent hierarchical model \citep{1989}, is a powerful tool for exploring the hierarchical structure in data.
+A two-level or multilevel model is a powerful tool for exploring the hierarchical structure in data.
 For example, we can imagine that there exists a district-level hierarchy (bigger population) for observed school-level data, or a state-level hierarchy for observed hospital-level data in a certain state.
@@
 Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket [, ] below indicates [mean, variance] of a distribution.
-For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$, where $j=1, \ldots, k$.
+For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$ for the $j$-th group.
 \begin{equation}
@@
 
-where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0j}$,  $B_{j}\equiv r / (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1, \ldots, k$.
+where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0j}$ and   $B_{j}\equiv r / (r+n_{j})$ for $j=1, \ldots, k$.
 
@@
 To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of adjustment for density maximization (ADM) \citep{carl1988, 1997, 2011}.
-For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, \emph{i.e.}  of $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without the boundary issues that MLE encounters.
+For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, \emph{i.e.}  of $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$, where the notation $\textbf{y}$ represents observed data, without the boundary issues that MLE encounters.
 See \cite{2011}.
@@
 The model checking is for the justification of the hierarchical model on a specific dataset.
-One possible question is, ``Can this dataset benefit from such a hierarchical modeling?'' \cite{1997} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
+One possible question is, ``Can this dataset benefit from such a hierarchical modeling?'' \cite{modelchecking1996} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
 They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
@@
 There are two extreme perspectives that the patient could take in this example.
-The first being that each hospital is identical in their ability to undertake CABG surgeries, in which case the choice of hospitals is irrelevant and the data could be pooled in order to estimate the death rate.
-The second, is that the hospitals are totally unrelated in which case the death rate estimate for each hospital would only be a function of the observed data for that particular hospital.
-These hospitals, however, are all subject to the same rules and regulations enforced by the federal and state governments and that there is likely similarities between hospitals.
-As such, a hierarchical model seems to be a reasonable approach.
+The first is that each hospital is identical in their ability to undertake CABG surgeries, in which case the choice of hospitals is irrelevant and the data could be pooled in order to estimate the common death rate for all hospitals (complete pooling).
+The second, is that the hospitals are totally unrelated in which case the death rate estimate for each hospital would only be a function of the observed data for that particular hospital (no pooling).
+
+However, in reality, these hospitals are neither completely the same nor different.
+For example, doctor' ability and experience for dealing with such a surgery vary according to each hospital.
+At the same time, these hospitals are all subject to the same rules and regulations enforced by the federal and state governments.
+The hierarchical model provides a happy medium accounting for such a difference and similarity altogether (partial pooling).
 
@@
 This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution.
-In this example it is assumed that the true state-level death rate is known to be 0.020.
+In this example it is assumed that the mean of such state-level death rate distribution is known to be 0.020 ($\lambda_{0}$).
 
@@
 
-Hierarchical modeling gives the patient the ability to borrow information across groups.
-For example, suppose there are two hospitals, whose observed death ratios ($y_{j}$) are 0 and 0.001 and caseloads ($n_{j}$) are 10 and 1000 each.
-Treating the hospitals as unrelated, the patient may conclude that the former hospital, whose observed death rate is 0, is superior than the latter.
-Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just ten caseloads.
+Intuitively, switching ranks for these two hospitals makes sense.
+To be specific, their observed death ratios ($y_{j}$, $j=8, 23$) are 0.014 and 0.015 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602 each.
+Considering solely the observed death ratios may lead to an unfair comparison because the latter hospital handled more than twice caseloads.
+\pkg{Rgbp} accounts for this caseload difference, making the estimate of true death rate for the former hospital shrink toward the state-level mean ($\lambda_{0}$=0.02) much harder than that for the latter hospital.
+This is what happened to the two left-most hospitals in the first plot.
 
@@
 
-From the output provided by \code{gbp} it can be seen that a reasonable choice of a hospital for the patient is hospital 23.
+This interval plot confirms that the 23rd hospital has the lowest upper bound for the true death rate, not to mention the lowest point estimate.
+Also it reveals that the 31st hospital may be the second safest because its upper bound of 95\% interval estimate for the true death rate is lower than the 8th hospital's one.
+
+%From the output provided by \code{gbp} it can be seen that a reasonable choice of a hospital for the patient is hospital 23.
 Although hospital 8 has a smaller observed mean the fact that hospital 23 has a much higher caseload means that we borrow relatively less information from other hospitals.
@@
 
-% This interval plot provides one more valuable insight, which we could not have noticed.
+%provides one more point, which we could not have noticed.
 Let's look at the 8th and the 31st hospitals on the graph (or on the outcome for numeric reference).
@@
 
-When fitting a model it is always a good idea to question how reliable the estimation procedure is.
-For example, does our procedure generate interval estimates that have good repeated sampling properties?
+Then, how reliable are these intervals?
+Does our procedure generate interval estimates that have good repeated sampling properties?
 To answer this question the \code{coverage} function generates pseudo-datasets regarding the estimated $r~(=336.37)$ as a given true value.
@@
 
-The estimated overall average coverage rate is 0.950 from both Rao-Blackwellized and simple unbiased estimates.
+The estimated overall average coverage rate across all the hospitals is 0.950 from both Rao-Blackwellized and simple unbiased estimates.
 This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling.
@@
 \begin{CodeInput}
-R> var(pcv$raw.resultRB[1, ])
+R> var(pcv$raw.resultRB[1, ]) / 1000
 \end{CodeInput}
 \begin{CodeOutput}
- [1] 0.002031225
+ [1] 0.000002031225
 \end{CodeOutput}
 \begin{CodeInput}
-R> var(pcv$raw.resultS[1, ])
+R> var(pcv$raw.resultS[1, ]) / 1000
 \end{CodeInput}
 \begin{CodeOutput}
- [1] 0.04844745
+ [1] 0.00004844745
 \end{CodeOutput}
@@
 It shows that Rao-Blackwellized unbiased estimate is about 24 times more accurate than simple one.
-Also, as the number of simulation increases (for example 10,000), the zig-zagging blue line will be closer to the red line.
+Also, as the number of simulation increases, the zig-zagging blue line is expected to be closer to the red line.
 % For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.
@@
 
-All the individual simulation results are saved in \code{pcv$raw.resultRB} and \code{pcv$raw.resultS}, in which each row is about each school.
+All the individual simulation results are saved in \code{gcv$raw.resultRB} and \code{gcv$raw.resultS}, in which each row is about each school.
 
@@
 Conditioning on the true batting average for each player we assume that the at-bats are independent and therefore, $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
-Our goal is to estimate point and interval estimates of the true batting average, $p_{j}$, for each player.
+Our goal is to estimate point and interval estimates of the true batting average, $p_{j}$, for each player, considering additional information on whether the player is an outfielder or not.
+\code{gbp} provides a way to incorporate such information seamlessly into the second-level hierarchy so that information is shared and regression towards the mean (RTTM) occurs within outfielders and non-outfielders separately.
 %For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
-
-Suppose, also, that we observed a covariate indicating whether each player is an outfielder or not.
-It is reasonable to assume that the batting averages for outfielders are different from non-outfielders and therefore we assume different second-level hierarchies for outfielders and for other positions.
-Within each of which information is shared and regression towards the mean (RTTM) occurs.
-\code{gbp} provides a way to incorporate such information (position) seamlessly into the second-level hierarchy.
 
@@
 
-We see that the two prior means distinguishing outfielders from other positions are significantly different (p-value = 0.038), supporting our initial belief.
-The positive sign of $\hat{\beta}_{1}$ indicates that the mean batting average for all the outfielders tends to be higher than that for those in the other positions.
+We see that the two prior means distinguishing outfielders from other positions are significantly different (p-value = 0.038).
+Also, the positive sign of $\hat{\beta}_{1}$ indicates that the population mean batting average for all the outfielders tends to be higher than that for those in the other positions (estimated odds ratio = exp(0.389)=1.48).
 
@@
 The following frequency method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values will answer it.
-For reference, if we want to try different true values, the appropriate code will be \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of below one.
+For reference, if we want to try different true values for example 100 for $r$ and (-1, 0.2) for $(\beta_{0}, \beta_{1})$, the appropriate code will be \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of below one.
 

### 2013-08-20 jss/article.tex
correction on 19 Aug

@@
 \label{sec:ex:hosp}
-In this example we take the perspective of a person living in the state of New York (NY) and has been suffering from severe coronary heart disease.
-If this person is supposed to receive a coronary artery bypass graft (CABG) surgery soon, he or she might want to find the most reliable hospital for dealing with such a surgery.
+In this example we adopt the perspective of a person living in the state of New York (NY) who has been suffering from severe coronary heart disease.
+If this person must receive coronary artery bypass graft (CABG) surgery soon, he or she might want to find the most reliable hospital for that.
 
-For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
-Using these data, \pkg{Rgbp} provides point and interval estimates of the true death ratio for each hospital so that one can choose the most reliable hospital.
-The data can be loaded into R using the following code.
-Note that throughout this paper, the symbol `\code{R>}' below represents a command prompt that you should not type on \proglang{R}.
+For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($\textbf{z}_{(31\times1)}$) for a specified period after CABG surgeries and total number of patients ($\textbf{n}_{(31\times1)}$) receiving CABG surgeries in each hospital.
+For reference, caseloads ($n_{j}$) can be interpreted as exposures, not necessarily integers.
+These data can be loaded into R using the following code.
+Note that throughout this paper, the symbol `\code{R>}' represents a command prompt (not to be typed into \proglang{R}).
+
+%For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($z$) for a specified period after CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
+Suppose one knows that the state-level death rate per exposure of this surgery is 0.030 ($\lambda_{0}$).
+Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the true death proportion for each hospital so that one can evaluate the hospital reliabilities.
+
+%These data, $\textbf{z}_{(31\times1)}$ and $\textbf{n}_{(31\times1)}$, can be loaded into R using the following code.
+Note that throughout this paper, the symbol `\code{R>}' represents a command prompt (not to be typed into \proglang{R}).
 
@@
 \begin{CodeInput}
-R> z <- c( 3, 2, 5, 11, 9, 12, 12, 4, 10, 13, 14, 7, 12, 11, 13, 22, 15, 
-          11, 14, 11, 16, 14, 9, 15, 13, 35, 26, 25, 20, 35, 27)
-R> n <- c(67, 68, 210, 256, 269, 274, 278, 295, 347, 349, 358, 396, 431,
+R> z <- c(  3,  2,   5,  11,   9,  12,  12,   4,  10,  13,  14,   7,  12,
+          11,  13,  22,  15,  11,  14,  11,  16,  14,   9,  15,  13,  35,
+          26,  25,  20,  35,  27)
+R> n <- c( 67, 68, 210, 256, 269, 274, 278, 295, 347, 349, 358, 396, 431,
          441, 477, 484, 494, 501, 505, 540, 563, 593, 602, 629, 636, 729,
@@
 R> data(hospitals)
-R> z <- hospitals$d
+R> z <- hospitals$d # variable name for the number of deaths is d in dataset
 R> n <- hospitals$n
@@
 
-There are two extreme perspectives that the patient could take in this example.
-The first is that each hospital is identical in their ability to undertake CABG surgeries, in which case the choice of hospitals is irrelevant and the data could be pooled in order to estimate the common death rate for all hospitals (complete pooling).
-The second, is that the hospitals are totally unrelated in which case the death rate estimate for each hospital would only be a function of the observed data for that particular hospital (no pooling).
+In addition, suppose one knows that the state-level death rate per exposure of this surgery is 0.030 ($\lambda_{0}$).
+Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the true death proportion for each hospital so that one can evaluate the hospital reliabilities.
 
-However, in reality, these hospitals are neither completely the same nor different.
-For example, doctor' ability and experience for dealing with such a surgery vary according to each hospital.
-At the same time, these hospitals are all subject to the same rules and regulations enforced by the federal and state governments.
-The hierarchical model provides a happy medium accounting for such a difference and similarity altogether (partial pooling).
+The independent Poisson distribution, \emph{i.e.},  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be an ideal choice to describe these data based on the Poisson approximation when $\lambda$ is small and $n$ is relatively big.
 
-The patient can then presume a state-level (NY) hierarchy governing the true death rates ($\lambda$) of CABG surgery for all the hospitals in NY.
-This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution.
-In this example it is assumed that the mean of such state-level death rate distribution is known to be 0.020 ($\lambda_{0}$).
-
-As the state-level death rate is small we can conclude that the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital.
-Thus, the independent Poisson distribution, \emph{i.e.},  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be an ideal choice to describe these data.
-Note that caseload  ($n_{j}$) can be interpreted as an exposure, which is not necessarily an integer.
-
-Next, \code{gbp} will help us fit the Poisson hierarchical model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in the section \ref{poissonsubsec}.
+Next, \code{gbp} will help us fit the Poisson hierarchical model with the Gamma conjugate prior distribution as the NY state-level population distribution of the true death rates ($\lambda_{j}$) whose mean is 0.030 ($\lambda_{0}=0.030$).
 For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression.
@@
 \begin{CodeInput}
-R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "poisson")
+R> p <- gbp(z, n, mean.PriorDist = 0.03, model = "poisson")
 R> p
@@
          obs.mean    n prior.mean shrinkage low.intv post.mean upp.intv post.sd
-1           0.045   67       0.02     0.834    0.011     0.024    0.042   0.008
-2           0.029   68       0.02     0.832    0.010     0.022    0.038   0.007
-3           0.024  210       0.02     0.616    0.011     0.021    0.035   0.006
-4           0.043  256       0.02     0.568    0.017     0.030    0.046   0.008
-5           0.033  269       0.02     0.556    0.015     0.026    0.041   0.007
-6           0.044  274       0.02     0.551    0.018     0.031    0.047   0.008
-7           0.043  278       0.02     0.548    0.018     0.030    0.047   0.007
-8           0.014  295       0.02     0.533    0.008     0.017    0.029   0.005
-9           0.029  347       0.02     0.492    0.014     0.024    0.038   0.006
-10          0.037  349       0.02     0.491    0.017     0.029    0.043   0.007
-11          0.039  358       0.02     0.484    0.018     0.030    0.045   0.007
-12          0.018  396       0.02     0.459    0.010     0.019    0.030   0.005
-13          0.028  431       0.02     0.438    0.015     0.024    0.037   0.006
-14          0.025  441       0.02     0.433    0.013     0.023    0.035   0.005
-15          0.027  477       0.02     0.414    0.015     0.024    0.036   0.006
-16          0.045  484       0.02     0.410    0.023     0.035    0.050   0.007
-17          0.030  494       0.02     0.405    0.016     0.026    0.039   0.006
-18          0.022  501       0.02     0.402    0.012     0.021    0.032   0.005
-19          0.028  505       0.02     0.400    0.015     0.025    0.036   0.005
-20          0.020  540       0.02     0.384    0.012     0.020    0.031   0.005
-21          0.028  563       0.02     0.374    0.016     0.025    0.037   0.005
-22          0.024  593       0.02     0.362    0.014     0.022    0.033   0.005
-23          0.015  602       0.02     0.358    0.010     0.017    0.026   0.004
-24          0.024  629       0.02     0.348    0.014     0.023    0.033   0.005
-25          0.020  636       0.02     0.346    0.012     0.020    0.030   0.005
-26          0.048  729       0.02     0.316    0.027     0.039    0.053   0.007
-27          0.031  849       0.02     0.284    0.019     0.028    0.038   0.005
-28          0.027  914       0.02     0.269    0.017     0.025    0.035   0.005
-29          0.021  940       0.02     0.264    0.014     0.021    0.030   0.004
-30          0.029 1193       0.02     0.220    0.020     0.027    0.036   0.004
-31          0.020 1340       0.02     0.201    0.014     0.020    0.027   0.003
-colMeans    0.029  517       0.02     0.438    0.015     0.025    0.037   0.006
+1          0.0448   67       0.03     0.911   0.0199    0.0313   0.0454 0.00653
+2          0.0294   68       0.03     0.910   0.0189    0.0299   0.0435 0.00631
+3          0.0238  210       0.03     0.765   0.0185    0.0285   0.0407 0.00566
+4          0.0430  256       0.03     0.728   0.0225    0.0335   0.0467 0.00619
+5          0.0335  269       0.03     0.718   0.0208    0.0310   0.0432 0.00573
+6          0.0438  274       0.03     0.714   0.0229    0.0339   0.0472 0.00621
+7          0.0432  278       0.03     0.711   0.0228    0.0338   0.0469 0.00617
+8          0.0136  295       0.03     0.699   0.0157    0.0250   0.0366 0.00534
+9          0.0288  347       0.03     0.663   0.0200    0.0296   0.0410 0.00536
+10         0.0372  349       0.03     0.662   0.0222    0.0325   0.0446 0.00571
+11         0.0391  358       0.03     0.656   0.0228    0.0331   0.0454 0.00579
+12         0.0177  396       0.03     0.633   0.0165    0.0255   0.0363 0.00506
+13         0.0278  431       0.03     0.613   0.0200    0.0292   0.0400 0.00511
+14         0.0249  441       0.03     0.608   0.0191    0.0280   0.0387 0.00502
+15         0.0273  477       0.03     0.589   0.0199    0.0289   0.0394 0.00499
+16         0.0455  484       0.03     0.585   0.0256    0.0364   0.0491 0.00601
+17         0.0304  494       0.03     0.580   0.0211    0.0302   0.0409 0.00506
+18         0.0220  501       0.03     0.577   0.0180    0.0266   0.0369 0.00483
+19         0.0277  505       0.03     0.575   0.0202    0.0290   0.0395 0.00494
+20         0.0204  540       0.03     0.559   0.0173    0.0258   0.0358 0.00474
+21         0.0284  563       0.03     0.548   0.0206    0.0293   0.0395 0.00485
+22         0.0236  593       0.03     0.535   0.0187    0.0270   0.0369 0.00466
+23         0.0150  602       0.03     0.532   0.0147    0.0230   0.0329 0.00466
+24         0.0238  629       0.03     0.521   0.0188    0.0271   0.0368 0.00460
+25         0.0204  636       0.03     0.518   0.0173    0.0254   0.0351 0.00455
+26         0.0480  729       0.03     0.484   0.0286    0.0393   0.0516 0.00587
+27         0.0306  849       0.03     0.446   0.0223    0.0303   0.0397 0.00445
+28         0.0274  914       0.03     0.428   0.0208    0.0285   0.0374 0.00423
+29         0.0213  940       0.03     0.421   0.0176    0.0249   0.0335 0.00407
+30         0.0293 1193       0.03     0.364   0.0223    0.0296   0.0379 0.00397
+31         0.0201 1340       0.03     0.338   0.0170    0.0235   0.0310 0.00360
+colMeans           517       0.03     0.600   0.0201    0.0293   0.0403 0.00517
 \end{CodeOutput}
@@
 For reference, we need to type `\code{R> print(p, sort = FALSE)}' instead of `\code{R> p}' in order to list hospitals by the order of data input in the above output.
-`\code{R> p}' automatically sorts the output by the increasing order of caseload ($n_{j}$).
+`\code{R> p}' automatically sorts the output by the increasing order of caseload ($n_{j}$), as shown above.
 
-The output contains information about observed death ratio ($y_{j}$), caseload ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower bound of interval estimate ($\hat{\lambda}_{j, low}$), posterior mean ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bound of interval estimate ($\hat{\lambda}_{j, upp}$), and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{y})$).
+The output contains information about observed death ratios ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds of interval estimates ($\hat{\lambda}_{j, low}$), posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds of interval estimates ($\hat{\lambda}_{j, upp}$), and standard deviations of posterior distribution3 ($sd(\lambda_{j}\vert \textbf{y})$).
 
 As we can see in (\ref{gammapost}), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a convex combination of the sample mean and prior mean ($\lambda_{0}=0.02$) with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight.
-This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree of prior and observed information respectively.
+This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree (sample sizes) of prior and observed information respectively.
 If the second level has more information than the first level, \emph{i.e.} ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the estimator will shrink towards the prior mean more than 50\%.
-This is clear in this example because, as caseload increases, shrinkage decreases, depending less on the second-level information.
+This is clear because, as caseload increases, shrinkage decreases, depending less on the second-level information.
 
-A function \code{summary} shows selective information on hospitals and more detailed estimation result as below.
+A function \code{summary} shows selective information on hospitals and more detailed estimation results, as below.
 To be specific, it displays some hospitals (not all as above) with minimum, median, and maximum caseloads ($n_{j}$).
-On top of that, more specific estimation results, such as the result of $\alpha\equiv\log(1/r)$, follow.
-Note that when we do not know the prior mean in advance unlike this hospital problem, \code{gbp} fits a linear regression for the Normal model, a log-linear regression for the Poisson model, or a logistic regression for the Binomial model.
+On top of that, more specific estimation results, such as the posterior mode and standard deviation of $\alpha\equiv\log(1/r)$, follow.
+When we do not know the prior mean in advance, unlike this hospital problem, \code{gbp} always fits the natural link, \emph{i.e.} a linear regression for the Normal model, a log-linear regression for the Poisson model, and a logistic regression for the Binomial model.
 \begin{CodeChunk}
@@
                     obs.mean    n prior.mean shrinkage low.intv post.mean
-Unit w/ min(n)       0.045   67       0.02     0.834    0.011     0.024
-Unit w/ median(n)    0.045  484       0.02     0.410    0.023     0.035
-Unit w/ max(n)       0.020 1340       0.02     0.201    0.014     0.020
-Overall Mean         0.029  517       0.02     0.438    0.015     0.025
+Unit with min(n)      0.0448   67       0.03     0.911   0.0199    0.0313   
+Unit with median(n)   0.0455  484       0.03     0.585   0.0256    0.0364   
+Unit with max(n)      0.0201 1340       0.03     0.338   0.0170    0.0235   
+Overall Mean                  517       0.03     0.600   0.0201    0.0293
 
                     upp.intv  post.sd
-                     0.042   0.008
-                     0.050   0.007
-                     0.027   0.003
-                     0.037   0.006
+                      0.0454  0.00653
+                      0.0491  0.00601
+                      0.0310  0.00360
+                      0.0403  0.00517
 
 Second-level Variance Component Estimation Summary:
-alpha = log(A) for Gaussian and log(1/r) for Binomial and Poisson data:
+alpha = log(A) for Gaussian or alpha = log(1/r) for Binomial and Poisson data:
 
-  post.mode.alpha post.sd.alpha
-1          -5.818         0.411
+  post.mode.alpha post.sd.alpha post.mode.r
+1           -6.53         0.576         684
 \end{CodeOutput}
 \end{CodeChunk}
-From the output of \code{summary} we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which is a good indicator of how valuable and informative the hypothetical second-level hierarchy is.
-It means that observed sample means of hospitals whose caseloads are less than 336 will shrink toward the prior mean (0.020) more than 50\%.
-For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.834$) was calculated by 336 / (336 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.834)*0.045 + 0.834 * 0.020=0.024$.
-As for this hospital, using more information from the prior distribution is an appropriate choice because the observed amount of information (67) is far less than the amount of state-level information (336).
+The output of \code{summary} also provides $\hat{r}=\textrm{exp}(6.53)=684$, which is an indicator of how valuable and informative the hypothetical second-level hierarchy is.
+It means that observed sample means of hospitals whose caseloads are less than 684 will shrink toward the prior mean (0.030) more than 50\%.
+For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.911$) was calculated by 684 / (684 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.911)*0.0448 + 0.911 * 0.030=0.0313$.
+As for this hospital, using more information from the prior distribution is an appropriate choice because the observed amount of information (67) is far less than the amount of state-level information (684).
 
@@
 \begin{center}
-\includegraphics[scale=0.25]{hospital1.png}
+\includegraphics[width = 3in]{hospital1.png}
 \caption{Shrinkage plot and 95\% interval plot for 31 hospitals}
@@
 
-In Figure \ref{fig:hospshr} the regression towards the mean (RTTM) is obvious in the left-side graph; the observed sample means, empty dots on the upper horizontal line, are shrinking towards the known second-level mean (a blue vertical line at 0.02) to the different extents.
-Note that some hospitals' ranks have changed by shrinking much harder towards 0.02 than others.
+In Figure \ref{fig:hospshr} the regression towards the mean (RTTM) is obvious in the first graph; the observed sample means, empty dots on the upper horizontal line, are shrinking towards the known second-level mean (a blue vertical line at 0.030) to the different extents.
+Note that some hospitals' ranks have changed by shrinking much harder towards 0.030 than others.
 For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly the safest hospital among 31 hospitals in terms of the observed death ratio is not actually safer than seemingly the second safest hospital.
@@
 Intuitively, switching ranks for these two hospitals makes sense.
-To be specific, their observed death ratios ($y_{j}$, $j=8, 23$) are 0.014 and 0.015 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602 each.
-Considering solely the observed death ratios may lead to an unfair comparison because the latter hospital handled more than twice caseloads.
-\pkg{Rgbp} accounts for this caseload difference, making the estimate of true death rate for the former hospital shrink toward the state-level mean ($\lambda_{0}$=0.02) much harder than that for the latter hospital.
+To be specific, their observed death ratios ($y_{j}$, $j=8, 23$) are 0.0136 and 0.0150 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602 each.
+Considering solely the observed death ratios may lead to an unfair comparison because the latter hospital handled twice the caseload.
+\pkg{Rgbp} accounts for this caseload difference, making the true death rate estimate for the former hospital shrink toward the state-level mean ($\lambda_{0}$=0.030) much harder than that for the latter hospital.
 This is what happened to the two left-most hospitals in the first plot.
 
-In Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed on the right-hand side.
-We can clearly see that all the posterior means (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line).
-For reference, to draw this plot by the order of data input the command, \code{plot(p, sort = FALSE)}, can be used.
+But the point estimates are not enough to evaluate hospital reliabilities because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other.
+In the second plot of Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed on the right-hand side.
+We see that each posterior mean (red dot) is between the sample mean (empty dot) and the second-level mean (a blue horizontal line).
+For reference, we could have plotted this 95\% interval plot by the order of data input via \code{plot(p, sort = FALSE)}.
 
-This interval plot confirms that the 23rd hospital has the lowest upper bound for the true death rate, not to mention the lowest point estimate.
+This 95\% interval plot reveals that the 31st hospital has the lowest upper bound of 95\% interval estimate, although its point estimate ($\hat{\lambda}_{31}=0.0235$) is slightly bigger than that of the 23rd hospital ($\hat{\lambda}_{23}=0.0230$).
+Let's see the details of these two hospitals.
+The observed death rates for these two hopitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
+The 31st hospital has twice the caseload, which leads to borrowing less information from the NY state-level hierarchy (or shrinking less toward the state-level mean, 0.030) with much more precision.
+
+%and What happened is that Since the 23rd hospital has the lowest upper bound for the true death rate, not to mention the lowest point estimate.
 Also it reveals that the 31st hospital may be the second safest because its upper bound of 95\% interval estimate for the true death rate is lower than the 8th hospital's one.
@@
 
-Then, how reliable are these intervals?
-Does our procedure generate interval estimates that have good repeated sampling properties?
+Based on the point and interval estimates, the 31st hospital seems the most reliable one among all the candidates.
+But when fitting a model it is always a good idea to question how reliable the estimation procedure is.
+For example, does our procedure generate interval estimates that have good repeated sampling properties?
 To answer this question the \code{coverage} function generates pseudo-datasets regarding the estimated $r~(=336.37)$ as a given true value.
@@
 
-Also, \code{gbp} can provide interval estimates with different confidence levels, for example 90\%,  and the appropriate code adjustment is `\code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.02, model = "poisson")}.'  Then, the below code will evaluate whether interval estimates achieve the 90\% confidence level.
+Then, how reliable are these intervals?
+Does our procedure generate interval estimates that have good repeated sampling properties?
+To answer this question the \code{coverage} function generates pseudo-datasets assuming the estimated $r~(=336.37)$ is a true value.
+We also could try any other value of $r$, for example $r=200$, by adding another argument, \code{A.or.r = 200}, into the code below; \code{R> pcv <- coverage(p, A.or.r = 200, nsim = 1000)}.
+
+Also, \code{gbp} provides interval estimates with different confidence levels, for example 90\%.
+For this, we need to go back to the model fitting code, adding another argument, \code{Alpha = 0.9}; \code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.03, model = "poisson")}.
+Then, the code below will evaluate whether interval estimates achieve the 90\% confidence level.
 
@@
 
-The estimated overall average coverage rate across all the hospitals is 0.950 from both Rao-Blackwellized and simple unbiased estimates.
+The estimated overall average coverage rate across all the hospitals is 0.955 from both Rao-Blackwellized.
 This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling.
-Note that these estimates depend on the given true value of $r$ and the assumption that the model is true.
+Note that these estimates depend on the given true value of $r$, the known prior mean, and the assumption that the model is true.
 
@@
 \begin{CodeOutput}
- [1] 0.950 0.950 0.950 0.951 0.950 0.950 0.951 0.950 0.950 0.950 0.951 0.951 
-[13] 0.950 0.950 0.950 0.950 0.951 0.950 0.950 0.950 0.950 0.951 0.950 0.950 
-[25] 0.951 0.950 0.951 0.950 0.951 0.951 0.950
+ [1] 0.956 0.957 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.955 
+[13] 0.955 0.956 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 0.955 0.955 
+[25] 0.955 0.954 0.954 0.954 0.954 0.953 0.953
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.949 0.953 0.946 0.955 0.957 0.939 0.956 0.957 0.944 0.952 0.956 0.955 
-[13] 0.949 0.957 0.948 0.954 0.951 0.934 0.956 0.943 0.959 0.952 0.949 0.964 
-[25] 0.949 0.953 0.941 0.938 0.941 0.956 0.951
+ [1] 0.955 0.959 0.955 0.949 0.944 0.955 0.960 0.947 0.948 0.962 0.967 0.962 
+[13] 0.957 0.959 0.961 0.958 0.957 0.948 0.963 0.963 0.967 0.955 0.968 0.948 
+[25] 0.965 0.947 0.955 0.946 0.957 0.948 0.948
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.000002031225
+ [1] 0.00000245
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.00004844745
+ [1] 0.00004302
 \end{CodeOutput}
@@
 
-It shows that Rao-Blackwellized unbiased estimate is about 24 times more accurate than simple one.
-Also, as the number of simulation increases, the zig-zagging blue line is expected to be closer to the red line.
+It shows that Rao-Blackwellized unbiased estimate is about 18 times more accurate than simple one.
+Also, as the number of simulation increases, the zig-zagging blue line is expected to converge to the red line by the law of large numbers.
 % For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.
@@
          obs.mean  n   X1 prior.mean shrinkage low.intv post.mean upp.intv post.sd
-1           0.400 45 1.00      0.310     0.715    0.248     0.335    0.429   0.046
-2           0.378 45 1.00      0.310     0.715    0.244     0.329    0.420   0.045
-3           0.356 45 1.00      0.310     0.715    0.240     0.323    0.411   0.044
-4           0.333 45 1.00      0.310     0.715    0.236     0.316    0.403   0.043
-5           0.311 45 1.00      0.310     0.715    0.230     0.310    0.396   0.042
-6           0.311 45 0.00      0.233     0.715    0.179     0.256    0.341   0.041
-7           0.289 45 0.00      0.233     0.715    0.175     0.249    0.331   0.040
-8           0.267 45 0.00      0.233     0.715    0.171     0.243    0.323   0.039
-9           0.244 45 0.00      0.233     0.715    0.166     0.237    0.315   0.038
-10          0.244 45 1.00      0.310     0.715    0.210     0.291    0.379   0.043
-11          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
-12          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
-13          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
-14          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375   0.044
-15          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375   0.044
-16          0.200 45 0.00      0.233     0.715    0.155     0.224    0.302   0.038
-17          0.178 45 0.00      0.233     0.715    0.148     0.218    0.297   0.038
-18          0.156 45 0.00      0.233     0.715    0.140     0.211    0.292   0.039
-colMeans    0.265 45 0.44      0.267     0.715    0.191     0.267    0.351   0.041
-\end{CodeOutput}
+1           0.400 45 1.00      0.310     0.715    0.248     0.335    0.429  0.0462
+2           0.378 45 1.00      0.310     0.715    0.244     0.329    0.420  0.0448
+3           0.356 45 1.00      0.310     0.715    0.240     0.323    0.411  0.0437
+4           0.333 45 1.00      0.310     0.715    0.236     0.316    0.403  0.0429
+5           0.311 45 1.00      0.310     0.715    0.230     0.310    0.396  0.0424
+6           0.311 45 0.00      0.233     0.715    0.179     0.256    0.341  0.0415
+7           0.289 45 0.00      0.233     0.715    0.175     0.249    0.331  0.0400
+8           0.267 45 0.00      0.233     0.715    0.171     0.243    0.323  0.0388
+9           0.244 45 0.00      0.233     0.715    0.166     0.237    0.315  0.0380
+10          0.244 45 1.00      0.310     0.715    0.210     0.291    0.379  0.0432
+11          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
+12          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
+13          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
+14          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375  0.0441
+15          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375  0.0441
+16          0.200 45 0.00      0.233     0.715    0.155     0.224    0.302  0.0377
+17          0.178 45 0.00      0.233     0.715    0.148     0.218    0.297  0.0381
+18          0.156 45 0.00      0.233     0.715    0.140     0.211    0.292  0.0389
+colMeans          45 0.44      0.267     0.715    0.191     0.267    0.351  0.0410\end{CodeOutput}
 \end{CodeChunk}
 Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233.
-Also note that the shrinkage estimates are the same for all players due to the fact that they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($\hat{B}_{j}\equiv \hat{r} / (\hat{r}+45)$ = $e^{4.727} / (e^{4.727}+45)$ = 0.715).
-The estimation results including $\hat{r}=e^{4.727}$ follows.
+Also note that the shrinkage estimates are the same for all players due to the fact that they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($\hat{B}_{j}\equiv \hat{r} / (\hat{r}+45)$ = $113 / (113+45)$ = 0.715).
+The estimation results including $\hat{r}=113$ follows.
 
@@
                             obs.mean  n    X1 prior.mean shrinkage low.intv 
-Unit w/ min(obs.mean)        0.156 45 0.00      0.233     0.715    0.140
-Unit w/ median(obs.mean)1    0.244 45 0.00      0.233     0.715    0.166
-Unit w/ median(obs.mean)2    0.244 45 1.00      0.310     0.715    0.210
-Unit w/ max(obs.mean)        0.400 45 1.00      0.310     0.715    0.248
-Overall Mean                 0.265 45 0.44      0.267     0.715    0.191
+Unit with min(obs.mean)        0.156 45 0.000      0.233     0.715    0.140     
+Unit with median(obs.mean)1    0.244 45 0.000      0.233     0.715    0.166     
+Unit with median(obs.mean)2    0.244 45 1.000      0.310     0.715    0.210     
+Unit with max(obs.mean)        0.400 45 1.000      0.310     0.715    0.248     
+Overall Mean                         45 0.444      0.267     0.715    0.191
 
                             post.mean upp.intv post.sd
-                             0.211    0.292   0.039
-                             0.237    0.315   0.038
-                             0.291    0.379   0.043
-                             0.335    0.429   0.046
-                             0.267    0.351   0.041
+                                0.211    0.292  0.0389
+                                0.237    0.315  0.0380
+                                0.291    0.379  0.0432
+                                0.335    0.429  0.0462
+                                0.267    0.351  0.0410
 
 Second-level Variance Component Estimation Summary:
-alpha = log(A) for Gaussian and log(1/r) for Binomial and Poisson data:
+alpha = log(A) for Gaussian or alpha =  log(1/r) for Binomial and Poisson data:
 
-  post.mode.alpha post.sd.alpha
-1          -4.727         0.957
+  post.mode.alpha post.sd.alpha post.mode.r
+1           -4.73         0.957         113
 
@@
 \begin{center}
-\includegraphics[scale=0.3]{baseball1.png}
+\includegraphics[width = 3in]{baseball1.png}
 \caption{Shrinkage plot and 95\% interval plot for 18 baseball players}
@@
 The following frequency method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values will answer it.
-For reference, if we want to try different true values for example 100 for $r$ and (-1, 0.2) for $(\beta_{0}, \beta_{1})$, the appropriate code will be \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of below one.
+For reference, if we want to try different true values, either 100 for $r$ or (-1, 0.2) for $(\beta_{0}, \beta_{1})$, the additional arguments are \code{A.or.r = 100} and \code{reg.coef = c(-1, 0.2)}; \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of the code below.
 

### 2013-08-20 jss/article.tex
small correction

@@
 For example, does our procedure generate interval estimates that have good repeated sampling properties?
-To answer this question the \code{coverage} function generates pseudo-datasets regarding the estimated $r~(=336.37)$ as a given true value.
-For reference, we can try any other value of $r$, for example $r=200$, by replacing the code below with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 1000)}.
-
-Then, how reliable are these intervals?
-Does our procedure generate interval estimates that have good repeated sampling properties?
-To answer this question the \code{coverage} function generates pseudo-datasets assuming the estimated $r~(=336.37)$ is a true value.
-We also could try any other value of $r$, for example $r=200$, by adding another argument, \code{A.or.r = 200}, into the code below; \code{R> pcv <- coverage(p, A.or.r = 200, nsim = 1000)}.
+To answer this question the \code{coverage} function generates pseudo-datasets assuming the estimated $r~(=683.53)$ is a true value.
+For reference, We also could try any other value of $r$, for example $r=600$, by adding another argument, \code{A.or.r = 600}, into the code below; \code{R> pcv <- coverage(p, A.or.r = 600, nsim = 1000)}.
 

### 2013-08-20 profiler.R
arhhh

@@ -4,3 +4,10 @@ Rprof("gr.out")
 lapply(1:1000,function(x){gbp(schools$y, schools$se)})
 Rprof(NULL)
 summaryRprof("gr.out")
+
+
+Rprof("qsn.out")
+lapply(1:10000,function(x){qsn(0.75, 1, 2, 1,engine = "T.Owen")})
+Rprof(NULL)
+summaryRprof("qsn.out")
+

### 2013-08-20 Rgbp/R/gbp.R
mistake in print.gbp

@@ -71,7 +71,7 @@ print.gbp <- function(x, sort = TRUE, ...) {
   temp.mean <- colMeans(temp)
   temp <- data.frame(rbind(temp, temp.mean), row.names = c(rownames(temp), "colMeans"))
   temp[, 1] <- format.default(temp[, 1], digits = 3, nsmall = 3)
-  temp[length(n) + 1, 1] <- ""
+  temp[dim(temp)[1], 1] <- ""
 
   if (x$model == "gr") {
     temp[, 2] <- round(temp[, 2], 1)

### 2013-08-20 jss/article.tex
small correction2
any chanage

@@
 We see that each posterior mean (red dot) is between the sample mean (empty dot) and the second-level mean (a blue horizontal line).
-For reference, we could have plotted this 95\% interval plot by the order of data input via \code{plot(p, sort = FALSE)}.
+For reference, we could plot this 95\% interval plot by the order of data input via \code{plot(p, sort = FALSE)}.
 
@@
 8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
-colMeans     8.75 12.5      8.168     0.552   -9.163     8.168   25.723   8.900
+colMeans          12.5      8.168     0.552   -9.163     8.168   25.723   8.900
 \end{CodeOutput}
@@
 \begin{center}
-\includegraphics[scale=0.3]{school1.png}
+\includegraphics[width = 3in]{school1.png}
 \caption{Shrinkage plot and 95\% interval plot for 8 schools}
@@
                       obs.mean   se prior.mean shrinkage low.intv post.mean
-Unit w/ min(se)        -1.00  9.0      8.168     0.408  -13.297     2.737
-Unit w/ median(se)1     1.00 11.0      8.168     0.507  -13.027     4.633
-Unit w/ median(se)2     7.00 11.0      8.168     0.507   -8.780     7.592
-Unit w/ max(se)        12.00 18.0      8.168     0.734  -10.208     9.189
-Overall Mean            8.75 12.5      8.168     0.552   -9.163     8.168
+Unit with min(se)        -1.00  9.0       8.17     0.408   -13.30      2.74     
+Unit with median(se)1     1.00 11.0       8.17     0.507   -13.03      4.63     
+Unit with median(se)2     7.00 11.0       8.17     0.507    -8.78      7.59     
+Unit with max(se)        12.00 18.0       8.17     0.734   -10.21      9.19     
+Overall Mean                   12.5       8.17     0.552    -9.16      8.17
 
                       upp.intv post.sd
-                       16.692   7.634
-                       20.131   8.441
-                       23.602   8.257
-                       29.939  10.227
-                       25.723   8.900
+                          16.7    7.63
+                          20.1    8.44
+                          23.6    8.26
+                          29.9   10.23
+                          25.7    8.90
 
 Second-level Variance Component Estimation Summary:
-alpha = log(A) for Gaussian and log(1/r) for Binomial and Poisson data:
+alpha = log(A) for Gaussian or alpha =  log(1/r) for Binomial and Poisson data:
 
-  post.mode.alpha post.sd.alpha
-1           4.768         1.139
+  post.mode.alpha post.sd.alpha post.mode.A
+1            4.77          1.14         118
 
@@
 18          0.156 45 0.00      0.233     0.715    0.140     0.211    0.292  0.0389
-colMeans          45 0.44      0.267     0.715    0.191     0.267    0.351  0.0410\end{CodeOutput}
+colMeans          45 0.44      0.267     0.715    0.191     0.267    0.351  0.0410
+\end{CodeOutput}
 \end{CodeChunk}

### 2013-08-20 Rgbp/R/gbp.R

@@ -70,7 +70,7 @@ print.gbp <- function(x, sort = TRUE, ...) {
 
   temp.mean <- colMeans(temp)
   temp <- data.frame(rbind(temp, temp.mean), row.names = c(rownames(temp), "colMeans"))
-  temp[, 1] <- format.default(temp[, 1], digits = 3, nsmall = 3)
+  temp[, 1] <- format.default(temp[, 1], digits = 3)
   temp[dim(temp)[1], 1] <- ""
 
   if (x$model == "gr") {
@@ -239,7 +239,7 @@ summary.gbp <- function(object, ...) {
 
   summary.table <- data.frame(rbind(summary.table, temp.mean), 
                               row.names = c(rownames(summary.table), "Overall Mean"))
-  summary.table[, 1] <- format.default(summary.table[, 1], digits = 3, nsmall = 3)
+  summary.table[, 1] <- format.default(summary.table[, 1], digits = 3)
   summary.table[dim(summary.table)[1], 1] <- ""
 
   post.mode.alpha <- object$a.new

### 2013-08-21 jss/article.tex
correction on 20 Aug

@@
 \begin{center}
-\includegraphics[width=5cm]{process.png}
+\includegraphics[width=6cm]{process.png}
 \caption{Pseudo-data generating process}
@@
 
-\subsubsection{Simple Unbiased Estimates of Coverage Probabilities}
+\subsubsection{Simple Unbiased Coverage Estimates}
 Let's define an indicator variable, $I^{(i)}_{j}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu^{(i)}_{j}$ and 0 otherwise.
 Then \code{coverage} estimates the coverage probability via the sample mean of these indicator variables for each group $j$, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ for given $A$ and $\beta$.
-This provides a simple unbiased estimate of the $k$ coverage probabilities.
-For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased estimate of coverage probability for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given a specific $(A, \beta)$.
-As the number of pseudo-datasets increases, this simple estimate converges to the true coverage probability of the first group given $A$ and $\beta$.
+This provides $k$ simple unbiased coverage estimates.
+For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given a specific $(A, \beta)$.
+As the number of pseudo-datasets increases, this simple unbiased coverage estimate converges to the true coverage probability of the first group given $A$ and $\beta$.
 
-\subsubsection{Rao-Blackwellized Unbiased Estimates of Coverage Probabilities}
+\subsubsection{Rao-Blackwellized Unbiased Coverage Estimates}
 Rao-Blackwellization improves accuracy of an unbiased estimator by taking a conditional expectation given a sufficient statistic.
@@
 
-The output contains information about observed death ratios ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds of interval estimates ($\hat{\lambda}_{j, low}$), posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds of interval estimates ($\hat{\lambda}_{j, upp}$), and standard deviations of posterior distribution3 ($sd(\lambda_{j}\vert \textbf{y})$).
+The output contains information about observed death ratios ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds (2.5\% percentiles of posterior distributions if 95\% confidence level is given) of interval estimates ($\hat{\lambda}_{j, low}$), posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds (97.5\% percentiles of posterior distributions) of interval estimates ($\hat{\lambda}_{j, upp}$), and standard deviations of posterior distributions ($sd(\lambda_{j}\vert \textbf{y})$).
 
-As we can see in (\ref{gammapost}), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a convex combination of the sample mean and prior mean ($\lambda_{0}=0.02$) with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight.
+As we can see in (\ref{gammapost}), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a convex combination of the sample mean and prior mean ($\lambda_{0}=0.030$) with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight.
 This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree (sample sizes) of prior and observed information respectively.
@@
 \begin{center}
-\includegraphics[width = 3in]{hospital1.png}
+\includegraphics[width = 6in]{hospital1.png}
 \caption{Shrinkage plot and 95\% interval plot for 31 hospitals}
@@
 Intuitively, switching ranks for these two hospitals makes sense.
-To be specific, their observed death ratios ($y_{j}$, $j=8, 23$) are 0.0136 and 0.0150 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602 each.
-Considering solely the observed death ratios may lead to an unfair comparison because the latter hospital handled twice the caseload.
+To be specific, their observed death rates ($y_{j}$, $j=8, 23$) are 0.0136 and 0.0150 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602 each.
+Considering solely the observed death rates may lead to an unfair comparison because the latter hospital handled twice the caseload.
 \pkg{Rgbp} accounts for this caseload difference, making the true death rate estimate for the former hospital shrink toward the state-level mean ($\lambda_{0}$=0.030) much harder than that for the latter hospital.
@@
 But the point estimates are not enough to evaluate hospital reliabilities because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other.
-In the second plot of Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed on the right-hand side.
+In the second plot of Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed.
 We see that each posterior mean (red dot) is between the sample mean (empty dot) and the second-level mean (a blue horizontal line).
@@
 \begin{center}
-\includegraphics[width = 5.5cm]{hospital2.png}
+\includegraphics[width = 3.5in]{hospital2.png}
 \caption{Coverage plot via frequency method checking for 31 hospitals}
@@
 
-In Figure \ref{fig:hospitalcoverage} we see three lines; one is a red line connecting Rao-Blackwellized unbiased estimates for 31 hospitals; another is a dashed blue line connecting simple unbiased estimates for those hospitals; the other is a black horizontal line indicating the confidence level, 0.95.
+In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level, the smooth red curve connects Rao-Blackwellized (RB) unbiased coverage estimates for 31 hospitals, and the dashed zagged blue curve passes simple unbiased coverage estimates for these hospitals.
+As the number of simulations increases, the zig-zagging blue curve would be closer to the smooth red curve by the law of large numbers.
 
-The estimated overall average coverage rate across all the hospitals is 0.955 from both Rao-Blackwellized.
+The overall RB unbiased coverage estimate across all the hospitals is 0.955.
+And none of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads ($n_{j}$).
 This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling.
@@
 
-If we want to check average Rao-Blackwellized unbiased estimates for each hospital, the following code gives us such estimates.
+The following code provides 31 RB unbiased coverage estimates for each hospital.
 \begin{CodeChunk}
@@
 
-As for average simple unbiased estimates for each hospital, we can type the code below.
+And the code below calculates 31 simple unbiased coverage estimates for each hospital.
 \begin{CodeChunk}
@@
 
-One more thing to mention is the accuracy of Rao-Blackwellized unbiased estimates compared to that of simple ones.
-Taking the first hospital as an example, we can calculate the sample variance of 1,000 Rao-Blackwellized unbiased estimates for the first hospital and that of 1,000 simple ones by typing following code.
-For reference, \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual simulation results.
+The function \code{coverage} also calculates the standard errors for each hospital's RB unbiased coverage estimate defined as the square root of $S^{2}_{RB, j}/N_{sim}$, where $S^{2}_{RB, j}$ is the sample variance of 1,000 RB unbiased coverage estimates for the $j$-th hospital.
+The following code provides 31 standard errors.
 \begin{CodeChunk}
 \begin{CodeInput}
-R> var(pcv$raw.resultRB[1, ]) / 1000
+R> pcv$se.coverageRB
 \end{CodeInput}
 \begin{CodeOutput}
- [1] 0.00000245
+ [1] 0.0015 0.0015 0.0013 0.0012 0.0012 0.0012 0.0012 0.0012 0.0011 0.0011 0.0011 
+[12] 0.0011 0.0010 0.0010 0.0010 0.0010 0.0011 0.0010 0.0010 0.0010 0.0009 0.0010 
+[23] 0.0009 0.0009 0.0009 0.0009 0.0008 0.0008 0.0007 0.0006 0.0006
 \end{CodeOutput}
+\end{CodeChunk}
+Similarly, 31 standard errors for each simple unbiased coverage estimate are
+\begin{CodeChunk}
 \begin{CodeInput}
-R> var(pcv$raw.resultS[1, ]) / 1000
+R> pcv$se.coverageS
 \end{CodeInput}
 \begin{CodeOutput}
- [1] 0.00004302
+[1] 0.0063 0.0060 0.0071 0.0063 0.0059 0.0066 0.0063 0.0068 0.0060 0.0076 0.0063 
+[12] 0.0059 0.0066 0.0072 0.0070 0.0074 0.0060 0.0062 0.0065 0.0065 0.0075 0.0072 
+[23] 0.0061 0.0067 0.0064 0.0065 0.0061 0.0072 0.0067 0.0070 0.0065
 \end{CodeOutput}
@@
 
-It shows that Rao-Blackwellized unbiased estimate is about 18 times more accurate than simple one.
-Also, as the number of simulation increases, the zig-zagging blue line is expected to converge to the red line by the law of large numbers.
+Taking the first hospital as an example, the variance of RB unbiased coverage estimate is about 18 times smaller than that of simple one.
+It means that 1,000 RB unbiased coverage estimates are as efficient as 18,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.
+
+For reference, \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual simulation results.
 % For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.
@@
 
-It is noted that \cite{1995} also investigated a similar ranking problem in hierarchical modeling, taking shrinkage into account.
+\cite{1995} also investigated a similar ranking problem in hierarchical modeling, taking shrinkage into account.
 
@@
 
-Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
-It is assumed that the mean for each score is drawn from a common normal distribution and hence, we can use \code{gbp} to fit this Normal-Normal hierarchical model.
+Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known.
+At the second hierarchy, the mean for each school is assumed to be drawn from a common Normal distribution and hence, we can use the Gaussian component of \code{gbp} to fit this Normal-Normal hierarchical model.
 
@@
 \end{CodeChunk}
-The output from \code{gbp} provides an easy to read summary of the results of the estimation.
-In the Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_i = V_i/(V_i + A)$ and as such those schools whose variation within the school is less than between the variation schools will shrink greater than $50\%$.
-The results provide by \code{gpb} suggests that there is little evidence that the training provided much of an added benefit with every school's $95\%$ posterior interval containing 0.
-\pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in Figure \ref{fig:8schoolsplot}.
+This output from \code{gbp} summarizes the results.
+In this Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_i = V_i/(V_i + A)$.
+As such schools whose variation within the school ($V_{j}$) is less than the between variation ($A$) schools will shrink greater than $50\%$.
+The results provided by \code{gpb} suggests that there is little evidence that the training provided much added benefit because every school's $95\%$ posterior interval contains 0.
 
@@
 \begin{center}
-\includegraphics[width = 3in]{school1.png}
+\includegraphics[width = 6in]{school1.png}
 \caption{Shrinkage plot and 95\% interval plot for 8 schools}
@@
 
+\pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in Figure \ref{fig:8schoolsplot}.
 Plotting the results provides a visual aid to understanding but is only largely beneficial when the number of groups $(k)$ is small.
@@
 
-An integral part of fitting any model is to check the method of estimation.
-Namely we can generate new pseudo-data from our assumed model by fixing the hyper-parameter values ($A$ and $\mu_0$ in this example) at their estimates.
-It is then possible to simulate ``true'' $\theta_i$ for each group $i$ and re-fit the model numerous times to estimate the coverage probabilities of our procedure.
+The method check, assuming the model is correct, generates new pseudo-data from our assumed model.
+It starts by fixing the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\beta}_0$ in this example).
+We then simulate ``true'' $\theta_j$ for each group $j$ and re-fit the model 1,000 times to estimate the coverage probabilities of our procedure.
 
@@
 \begin{center}
-\includegraphics[width = 5.5cm]{school2.png}
+\includegraphics[width = 3.5in]{school2.png}
 \caption{Coverage plot via frequency method checking for 8 schools}
@@
 As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (black horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example.
-Note that all the coverage estimates depend on the given true values of $A$ and $\beta_{0}$, and the assumption that the model is true.
+Note that all the coverage estimates depend on the chosen true values of $A$ and $\beta_{0}$, and the assumption that the model is valid.
 
-In addition, average Rao-Blackwellized unbiased estimates for each school can be seen as below.
+In addition, Rao-Blackwellized (RB) unbiased coverage estimates for each school can be gotten with the command below.
 \begin{CodeChunk}
@@
 
-All the individual simulation results are saved in \code{gcv$raw.resultRB} and \code{gcv$raw.resultS}, in which each row is about each school.
+All the simulation results (0-1 coverage and RB coverage estimates) are saved in two $8\times1,000$ matrices, \code{gcv$raw.resultRB} and \code{gcv$raw.resultS}, each row of which is about each school.
 
@@
 We see that the two prior means distinguishing outfielders from other positions are significantly different (p-value = 0.038).
-Also, the positive sign of $\hat{\beta}_{1}$ indicates that the population mean batting average for all the outfielders tends to be higher than that for those in the other positions (estimated odds ratio = exp(0.389)=1.48).
+Also, the positive sign of $\hat{\beta}_{1}$ indicates that the population mean batting average for all outfielders tends to be higher than that for those in the other positions (estimated odds ratio = exp(0.389)=1.48).
 
@@
 \begin{center}
-\includegraphics[width = 3in]{baseball1.png}
+\includegraphics[width = 6in]{baseball1.png}
 \caption{Shrinkage plot and 95\% interval plot for 18 baseball players}
@@
 \begin{center}
-\includegraphics[width = 5.5cm]{baseball2.png}
+\includegraphics[width = 3.5in]{baseball2.png}
 \caption{Coverage plot via frequency method checking for 18 players}
@@
 
-Finally, in Figure \ref{fig:baseball2}, we see that the estimated average coverage probability is 0.972 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.
-Note that each coverage estimate depends on given true values of $r$ and $\beta_{(2\times1)}$, and the assumption that the model is true.
+Finally, in Figure \ref{fig:baseball2}, we see that the overall Rao-Blackwellized unbiased coverage estimate is 0.972 (across all the players), conservatively satisfying the definition of the 95\% confidence interval.
+Note that each coverage estimate depends on given true values of $r$ and $\beta_{(2\times1)}$, and the assumption that the model is valid.
 
-The average Rao-Blackwellized unbiased estimates for each player follows.
+The Rao-Blackwellized unbiased coverage estimates and their standard errors for each player follow.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
+\begin{CodeChunk}
+\begin{CodeInput}
+R> bcv$se.coverageRB
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.0012 0.0013 0.0012 0.0012 0.0013 0.0011 0.0011 0.0009 0.0012 0.0013 
+[11] 0.0010 0.0013 0.0010 0.0012 0.0015 0.0010 0.0010 0.0011
+\end{CodeOutput}
+\end{CodeChunk}
 
-And average simple unbiased estimates for each player are
+And simple unbiased coverage estimates and their standard errors for each player are
 \begin{CodeChunk}
@@
 \end{CodeChunk}
+\begin{CodeChunk}
+\begin{CodeInput}
+R> bcv$se.coverageRB
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.0045 0.0059 0.0066 0.0049 0.0052 0.0044 0.0042 0.0054 0.0056 0.0053 0.0049 
+[11] 0.0056 0.0042 0.0049 0.0056 0.0057 0.0052 0.0052
+\end{CodeOutput}
+\end{CodeChunk}
 
-All the individual simulation results are saved in \code{bcv$raw.resultRB} and \code{bcv$raw.resultS}, in which each row is about each player.
+All the simulation results are saved in two $18\times1,000$ matrices, \code{bcv$raw.resultRB} and \code{bcv$raw.resultS}, each row of which is about each player.
 

### 2013-08-21 Rgbp/R/coverage.R

@@ -538,9 +538,10 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 10) {
   # average coverage probability
   result <- round(rowMeans(coverageRB, na.rm = TRUE), 3)
   avr.cov <- round(mean(result), 3)
-
+  se.cov <- round(sqrt(apply(coverageRB, 1, var) / nsim), 4)
   result2 <- round(rowMeans(coverageS, na.rm = TRUE), 3)
   avr.cov2 <- round(mean(result2), 3)
+  se.cov2 <- round(sqrt(apply(coverageS, 1, var) / nsim), 4)
 
   # plotting coverage graph
   par(xaxs = "r", yaxs = "r", mai = c(1, 0.6, 1, 0.3))
@@ -635,6 +636,7 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 10) {
   # print output
   output <- list(coverageRB = result, coverageS = result2, 
                  average.coverageRB = avr.cov, average.coverageS = avr.cov2, 
+                 se.coverageRB = se.cov, se.coverageS = se.cov2, 
                  raw.resultRB = coverageRB, raw.resultS = coverageS)
   return(output)
 }

### 2013-08-28 jss/article.tex
edit

@@
 
-The output contains information about observed death ratios ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds (2.5\% percentiles of posterior distributions if 95\% confidence level is given) of interval estimates ($\hat{\lambda}_{j, low}$), posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds (97.5\% percentiles of posterior distributions) of interval estimates ($\hat{\lambda}_{j, upp}$), and standard deviations of posterior distributions ($sd(\lambda_{j}\vert \textbf{y})$).
+The output contains information about observed death ratios ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds of interval estimates ($\hat{\lambda}_{j, low}$, 2.5\% percentiles of posterior distributions if 95\% confidence level is given), posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds  of interval estimates ($\hat{\lambda}_{j, upp}$, 97.5\% percentiles of posterior distributions), and standard deviations of posterior distributions ($sd(\lambda_{j}\vert \textbf{y})$).
 
@@
 The observed death rates for these two hopitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
-The 31st hospital has twice the caseload, which leads to borrowing less information from the NY state-level hierarchy (or shrinking less toward the state-level mean, 0.030) with much more precision.
+The 31st hospital has twice the caseload, which leads to borrowing less information from the NY state-level hierarchy (or shrinking less toward the state-level mean, 0.030) with smaller variance.
 
@@
 Also, \code{gbp} provides interval estimates with different confidence levels, for example 90\%.
-For this, we need to go back to the model fitting code, adding another argument, \code{Alpha = 0.9}; \code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.03, model = "poisson")}.
+For this, we need to go back to the code for fitting the model, adding another argument, \code{Alpha = 0.9}; \code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.03, model = "poisson")}.
 Then, the code below will evaluate whether interval estimates achieve the 90\% confidence level.
@@
 Taking the first hospital as an example, the variance of RB unbiased coverage estimate is about 18 times smaller than that of simple one.
-It means that 1,000 RB unbiased coverage estimates are as efficient as 18,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.
+It means that 1,000 RB unbiased coverage estimates are as precise as 18,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.
 
@@
 This output from \code{gbp} summarizes the results.
-In this Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_i = V_i/(V_i + A)$.
+In this Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_j = V_j/(V_j + A)$.
 As such schools whose variation within the school ($V_{j}$) is less than the between variation ($A$) schools will shrink greater than $50\%$.
@@
 
-Now, let's see following shrinkage and 95\% interval plots for more intuition.
-It is obvious that sample means (empty dots) on the upper horizontal line shrink towards two different means, 0.233 and 0.310.
-For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
-For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper horizontal line, there are short red lines toward five directions.
-
 \begin{CodeChunk}
@@
 \end{figure}
+
+Now, let's see following shrinkage and 95\% interval plots for more intuition.
+It is obvious that sample means (empty dots) on the upper horizontal line shrink towards two different means, 0.233 and 0.310.
+For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
+For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper horizontal line, there are short red lines toward five directions.
 

### 2013-08-28 jss/article.tex
edit
double space
minor 8schools edits

@@
 %%uncomment line below for double-spacing
-%%\linespread{2}
+\linespread{2}
 
@@
 In this Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_j = V_j/(V_j + A)$.
-As such schools whose variation within the school ($V_{j}$) is less than the between variation ($A$) schools will shrink greater than $50\%$.
-The results provided by \code{gpb} suggests that there is little evidence that the training provided much added benefit because every school's $95\%$ posterior interval contains 0.
+As such, schools whose variation within the school ($V_{j}$) is less than the between variation ($A$) schools will shrink greater than $50\%$.
+The results provided by \code{gpb} suggests that there is little evidence that the training provided much added benefit due to the fact that every school's $95\%$ posterior interval contains 0.
 
@@
 \begin{CodeInput}
-R> bcv$se.coverageRB
+R> bcv$se.coverageS
 \end{CodeInput}

### 2013-08-29 jss/article.tex
back
edit2

@@
 %%uncomment line below for double-spacing
-\linespread{2}
+%\linespread{1}
 
@@
 Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 pseudo-datasets in order to obtain 500$\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, 500$\}.
-And then within each group, it will check simply how often the interval estimates include true parameters, or calculate Rao-Blackwellized coverage estimate.
+Here, we introduce both simple and Rao-Blackwellized unbiased coverage estimators but \code{coverage} displays only Rao-Blackwellized one.
 
@@
 Then \code{coverage} estimates the coverage probability via the sample mean of these indicator variables for each group $j$, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ for given $A$ and $\beta$.
+\begin{equation}
+\bar{I}_{j}\equiv \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{j},~ j=1, 2, \ldots, k.
+\end{equation}
+
 This provides $k$ simple unbiased coverage estimates.
-For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given a specific $(A, \beta)$.
-As the number of pseudo-datasets increases, this simple unbiased coverage estimate converges to the true coverage probability of the first group given $A$ and $\beta$.
+For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given specific values of $A$ and $\beta$.
+
+Each indicator has the independent and identically distributed (\emph{iid}) Bernoulli($p_{cov, j}$) distribution, where $p_{cov, j}$ is the true coverage probability for the $j$-th group depending on specific values of $A$ and $\beta$.
+
+So, its unbiased variance estimator  for $Var(\bar{I}_{j})$ is simply the sample variance of indicators over the number of simulations.
+\begin{equation}
+\widehat{Var}(\bar{I}_{j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}(I^{(i)}_{j}-\bar{I}_{j})^{2},~ j=1, 2, \ldots, k.
+\end{equation}
 
 \subsubsection{Rao-Blackwellized Unbiased Coverage Estimates}
-Rao-Blackwellization improves accuracy of an unbiased estimator by taking a conditional expectation given a sufficient statistic.
+Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (sufficient statistic) into consideration.
 Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset.
-This expectation is the same as Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
+\begin{equation}\label{RB}
+\bar{I}_{RB, j}\equiv \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta),~ j=1, 2, \ldots, k.
+\end{equation}
+
+The expectation in (\ref{RB}) is the same as Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
 We can calculate this probability  because we know the distribution of ($\mu^{(i)}_{j} \vert y^{(i)}_{j}, A, \beta$) in (\ref{normalpost}).
 Note that conditioning on $y^{(i)}_{j}$ is equivalent to conditioning on $\mathbf{y}^{(i)}_{(k\times1)}$ as long as $A$ and $\beta$ are known.
-Then, we estimate the first group's coverage probability by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$.
+
+For example, we estimate the first group's coverage probability (that depend on specific $A$ and $\beta$) by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased for $p_{cov, 1}$ but with smaller variance than the previous simple estimator, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$.
+
+Under the setting where one dataset ($\mathbf{y}^{(i)}_{(k\times1)}$) is simulated per one true parameter set ({\boldmath $\mu$}$^{(i)}_{(k\times1)})$, the unbiased variance estimator for Var($\bar{I}_{RB, j}$) follows.
+\begin{equation}
+\widehat{Var}(\bar{I}_{RB, j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}\bigg(E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta)-\bar{I}_{RB, j}\bigg)^{2},~ j=1, 2, \ldots, k.
+\end{equation}
 
@@
 
-For reference, \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual simulation results.
+For reference, two $31 \times 1,000$ matrices \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual estimates.
 % For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.
@@
 
-As for average simple unbiased estimates for each school, 
-\begin{CodeChunk}
-\begin{CodeInput}
-R> gcv$coverageS
-\end{CodeInput}
-\begin{CodeOutput}
-[1] 0.970 0.943 0.957 0.968 0.956 0.969 0.961 0.976
-\end{CodeOutput}
-\end{CodeChunk}
-
-All the simulation results (0-1 coverage and RB coverage estimates) are saved in two $8\times1,000$ matrices, \code{gcv$raw.resultRB} and \code{gcv$raw.resultS}, each row of which is about each school.
+All the individual RB coverage estimates are saved in the $8\times1,000$ matrix, \code{gcv$raw.resultRB}, each row of which is about each school.
 
@@
 
-Now, let's see following shrinkage and 95\% interval plots for more intuition.
+Now, let's see the shrinkage and 95\% interval plots for more intuition in Figure \ref{fig:baseball}.
 It is obvious that sample means (empty dots) on the upper horizontal line shrink towards two different means, 0.233 and 0.310.
@@
 
-In Figure \ref{fig:baseball} the 95\% interval plot shows us range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups.
+The 95\% interval plot shows us range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups.
 Let's see the 10th, 14th, and 15th players on the graph for example.
@@
 
-And simple unbiased coverage estimates and their standard errors for each player are
-\begin{CodeChunk}
-\begin{CodeInput}
-R> bcv$coverageS
-\end{CodeInput}
-\begin{CodeOutput}
- [1] 0.969 0.967 0.973 0.980 0.970 0.974 0.965 0.976 0.969 0.972 0.980 0.972 
-[13] 0.957 0.969 0.972 0.982 0.978 0.984
-\end{CodeOutput}
-\end{CodeChunk}
-\begin{CodeChunk}
-\begin{CodeInput}
-R> bcv$se.coverageS
-\end{CodeInput}
-\begin{CodeOutput}
- [1] 0.0045 0.0059 0.0066 0.0049 0.0052 0.0044 0.0042 0.0054 0.0056 0.0053 0.0049 
-[11] 0.0056 0.0042 0.0049 0.0056 0.0057 0.0052 0.0052
-\end{CodeOutput}
-\end{CodeChunk}
-
-All the simulation results are saved in two $18\times1,000$ matrices, \code{bcv$raw.resultRB} and \code{bcv$raw.resultS}, each row of which is about each player.
+All the simulation results are saved in the $18\times1,000$ matrix, \code{bcv$raw.resultRB}, each row of which is for each player.
 

### 2013-08-29 jss/article.tex
edit3

@@
 
-In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level, the smooth red curve connects Rao-Blackwellized (RB) unbiased coverage estimates for 31 hospitals, and the dashed zagged blue curve passes simple unbiased coverage estimates for these hospitals.
-As the number of simulations increases, the zig-zagging blue curve would be closer to the smooth red curve by the law of large numbers.
+In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level and the smooth red curve connects Rao-Blackwellized (RB) unbiased coverage estimates for 31 hospitals.
 

### 2013-08-29 jss/article.tex
edit3

@@
 
-The overall RB unbiased coverage estimate across all the hospitals is 0.955.
+The overall RB unbiased coverage estimate across all the hospitals is 0.954.
 And none of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads ($n_{j}$).
@@
 \begin{CodeOutput}
- [1] 0.956 0.957 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.955 
-[13] 0.955 0.956 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 0.955 0.955 
-[25] 0.955 0.954 0.954 0.954 0.954 0.953 0.953
+ [1] 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 0.954 0.955 
+[13] 0.954 0.955 0.954 0.954 0.954 0.955 0.954 0.954 0.954 0.954 0.954 0.954 
+[25] 0.953 0.954 0.953 0.953 0.954 0.952 0.952
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.955 0.959 0.955 0.949 0.944 0.955 0.960 0.947 0.948 0.962 0.967 0.962 
-[13] 0.957 0.959 0.961 0.958 0.957 0.948 0.963 0.963 0.967 0.955 0.968 0.948 
-[25] 0.965 0.947 0.955 0.946 0.957 0.948 0.948
+ [1] 0.960 0.953 0.956 0.952 0.957 0.957 0.960 0.949 0.949 0.944 0.951 0.947 
+[13] 0.949 0.958 0.958 0.959 0.953 0.954 0.953 0.955 0.956 0.952 0.953 0.959 
+[25] 0.945 0.945 0.953 0.946 0.953 0.948 0.955
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.0015 0.0015 0.0013 0.0012 0.0012 0.0012 0.0012 0.0012 0.0011 0.0011 0.0011 
-[12] 0.0011 0.0010 0.0010 0.0010 0.0010 0.0011 0.0010 0.0010 0.0010 0.0009 0.0010 
-[23] 0.0009 0.0009 0.0009 0.0009 0.0008 0.0008 0.0007 0.0006 0.0006
+ [1] 0.0016 0.0016 0.0014 0.0013 0.0013 0.0013 0.0013 0.0013 0.0013 0.0013 0.0012 
+[12] 0.0012 0.0012 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0010
+[23] 0.0010 0.0010 0.0010 0.0009 0.0009 0.0008 0.0008 0.0007 0.0007
 \end{CodeOutput}
@@
 \begin{CodeOutput}
-[1] 0.0063 0.0060 0.0071 0.0063 0.0059 0.0066 0.0063 0.0068 0.0060 0.0076 0.0063 
-[12] 0.0059 0.0066 0.0072 0.0070 0.0074 0.0060 0.0062 0.0065 0.0065 0.0075 0.0072 
-[23] 0.0061 0.0067 0.0064 0.0065 0.0061 0.0072 0.0067 0.0070 0.0065
+ [1] 0.0062 0.0067 0.0065 0.0068 0.0064 0.0064 0.0062 0.0070 0.0070 0.0073 0.0068 
+[12] 0.0071 0.0070 0.0063 0.0063 0.0063 0.0067 0.0066 0.0067 0.0066 0.0065 0.0068
+[23] 0.0067 0.0063 0.0072 0.0072 0.0067 0.0072 0.0067 0.0070 0.0066
 \end{CodeOutput}
@@
 
-Taking the first hospital as an example, the variance of RB unbiased coverage estimate is about 18 times smaller than that of simple one.
-It means that 1,000 RB unbiased coverage estimates are as precise as 18,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.
+Taking the first hospital as an example, the variance of RB unbiased coverage estimate is about 15 times smaller than that of simple one.
+It means that 1,000 RB unbiased coverage estimates are as precise as 15,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.
 
@@
 
-In addition, Rao-Blackwellized (RB) unbiased coverage estimates for each school can be gotten with the command below.
+In addition, Rao-Blackwellized (RB) unbiased coverage estimate and its standard error for each school can be gotten with the command below.
 \begin{CodeChunk}
@@
 \begin{CodeOutput}
- [1] 0.966 0.957 0.966 0.962 0.960 0.961 0.960 0.969
+ [1] 0.964 0.958 0.964 0.960 0.956 0.959 0.958 0.966
+\end{CodeOutput}
+\end{CodeChunk}
+\begin{CodeChunk}
+\begin{CodeInput}
+R> gcv$se.coverageRB
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.0014 0.0013 0.0016 0.0014 0.0014 0.0012 0.0012 0.0017
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.972 0.972 0.973 0.972 0.972 0.970 0.974 0.972 0.973 0.973 0.973 0.970 
-[13] 0.972 0.972 0.973 0.972 0.973 0.972
+ [1] 0.973 0.973 0.974 0.971 0.971 0.973 0.972 0.973 0.972 0.973 0.971 0.973 
+[13] 0.971 0.972 0.974 0.972 0.972 0.973
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.0012 0.0013 0.0012 0.0012 0.0013 0.0011 0.0011 0.0009 0.0012 0.0013 
-[11] 0.0010 0.0013 0.0010 0.0012 0.0015 0.0010 0.0010 0.0011
+ [1] 0.0010 0.0011 0.0011 0.0013 0.0012 0.0011 0.0012 0.0011 0.0012 0.0010 
+[11] 0.0013 0.0012 0.0013 0.0013 0.0010 0.0010 0.0010 0.0010
 \end{CodeOutput}

### 2013-08-30 jss/article.tex
acknowl

--- 2013-08-29 jss/article.tex
@@
 %%uncomment line below for double-spacing
-%\linespread{1}
+\linespread{2}
 
@@
 Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 pseudo-datasets in order to obtain 500$\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, 500$\}.
-Here, we introduce both simple and Rao-Blackwellized unbiased coverage estimators but \code{coverage} displays only Rao-Blackwellized one.
+And then within each group, it will check simply how often the interval estimates include true parameters, or calculate Rao-Blackwellized coverage estimate.
 
@@
 Then \code{coverage} estimates the coverage probability via the sample mean of these indicator variables for each group $j$, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ for given $A$ and $\beta$.
-\begin{equation}
-\bar{I}_{j}\equiv \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{j},~ j=1, 2, \ldots, k.
-\end{equation}
-
 This provides $k$ simple unbiased coverage estimates.
-For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given specific values of $A$ and $\beta$.
-
-Each indicator has the independent and identically distributed (\emph{iid}) Bernoulli($p_{cov, j}$) distribution, where $p_{cov, j}$ is the true coverage probability for the $j$-th group depending on specific values of $A$ and $\beta$.
-
-So, its unbiased variance estimator  for $Var(\bar{I}_{j})$ is simply the sample variance of indicators over the number of simulations.
-\begin{equation}
-\widehat{Var}(\bar{I}_{j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}(I^{(i)}_{j}-\bar{I}_{j})^{2},~ j=1, 2, \ldots, k.
-\end{equation}
+For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given a specific $(A, \beta)$.
+As the number of pseudo-datasets increases, this simple unbiased coverage estimate converges to the true coverage probability of the first group given $A$ and $\beta$.
 
 \subsubsection{Rao-Blackwellized Unbiased Coverage Estimates}
-Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (sufficient statistic) into consideration.
+Rao-Blackwellization improves accuracy of an unbiased estimator by taking a conditional expectation given a sufficient statistic.
 Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset.
-\begin{equation}\label{RB}
-\bar{I}_{RB, j}\equiv \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta),~ j=1, 2, \ldots, k.
-\end{equation}
-
-The expectation in (\ref{RB}) is the same as Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
+This expectation is the same as Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
 We can calculate this probability  because we know the distribution of ($\mu^{(i)}_{j} \vert y^{(i)}_{j}, A, \beta$) in (\ref{normalpost}).
 Note that conditioning on $y^{(i)}_{j}$ is equivalent to conditioning on $\mathbf{y}^{(i)}_{(k\times1)}$ as long as $A$ and $\beta$ are known.
-
-For example, we estimate the first group's coverage probability (that depend on specific $A$ and $\beta$) by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased for $p_{cov, 1}$ but with smaller variance than the previous simple estimator, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$.
-
-Under the setting where one dataset ($\mathbf{y}^{(i)}_{(k\times1)}$) is simulated per one true parameter set ({\boldmath $\mu$}$^{(i)}_{(k\times1)})$, the unbiased variance estimator for Var($\bar{I}_{RB, j}$) follows.
-\begin{equation}
-\widehat{Var}(\bar{I}_{RB, j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}\bigg(E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta)-\bar{I}_{RB, j}\bigg)^{2},~ j=1, 2, \ldots, k.
-\end{equation}
+Then, we estimate the first group's coverage probability by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$.
 
@@
 
-For reference, two $31 \times 1,000$ matrices \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual estimates.
+For reference, \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual simulation results.
 % For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.
@@
 
-All the individual RB coverage estimates are saved in the $8\times1,000$ matrix, \code{gcv$raw.resultRB}, each row of which is about each school.
+As for average simple unbiased estimates for each school, 
+\begin{CodeChunk}
+\begin{CodeInput}
+R> gcv$coverageS
+\end{CodeInput}
+\begin{CodeOutput}
+[1] 0.970 0.943 0.957 0.968 0.956 0.969 0.961 0.976
+\end{CodeOutput}
+\end{CodeChunk}
+
+All the simulation results (0-1 coverage and RB coverage estimates) are saved in two $8\times1,000$ matrices, \code{gcv$raw.resultRB} and \code{gcv$raw.resultS}, each row of which is about each school.
 
@@
 
-Now, let's see the shrinkage and 95\% interval plots for more intuition in Figure \ref{fig:baseball}.
+Now, let's see following shrinkage and 95\% interval plots for more intuition.
 It is obvious that sample means (empty dots) on the upper horizontal line shrink towards two different means, 0.233 and 0.310.
@@
 
-All the simulation results are saved in the $18\times1,000$ matrix, \code{bcv$raw.resultRB}, each row of which is for each player.
+And simple unbiased coverage estimates and their standard errors for each player are
+\begin{CodeChunk}
+\begin{CodeInput}
+R> bcv$coverageS
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.969 0.967 0.973 0.980 0.970 0.974 0.965 0.976 0.969 0.972 0.980 0.972 
+[13] 0.957 0.969 0.972 0.982 0.978 0.984
+\end{CodeOutput}
+\end{CodeChunk}
+\begin{CodeChunk}
+\begin{CodeInput}
+R> bcv$se.coverageS
+\end{CodeInput}
+\begin{CodeOutput}
+ [1] 0.0045 0.0059 0.0066 0.0049 0.0052 0.0044 0.0042 0.0054 0.0056 0.0053 0.0049 
+[11] 0.0056 0.0042 0.0049 0.0056 0.0057 0.0052 0.0052
+\end{CodeOutput}
+\end{CodeChunk}
+
+All the simulation results are saved in two $18\times1,000$ matrices, \code{bcv$raw.resultRB} and \code{bcv$raw.resultS}, each row of which is about each player.
 
@@
 \section[acknowledgments]{Acknowledgments}
-The authors thank Professor Phil Everson of Swarthmore and the 2012 class of Harvard's Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
+The authors thank Professor Cindy Christiansen, Professor Phil Everson and the 2012 class of Harvard's Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
 

### 2013-08-30 mcmc/gaussian.R

@@ -1,5 +1,4 @@
 library(rstan)
-library(parallel)
 
 args <- commandArgs(TRUE)
 if (length(args)==0){
@@ -37,7 +36,7 @@ rstan_schools <- function(y, sigma){
                       y = y,
                       sigma = sigma)
 
-  fit <- stan(model_code = schools_code, data = schools_dat, iter = 1000, chains = 4)
+  fit <- stan(model_code = schools_code, data = schools_dat, iter = 20000, chains = 2)
   return(fit)
 }
 
@@ -76,8 +75,6 @@ mu0 <- 8.168
 A <- 117.71
 k <- 8
 sigma <- c(9, 10, 10, 11, 11, 15, 16, 18)
-##nits <- 1000
 
-## out <- mclapply(1:nits, schools.sim, mu0 = mu0, A = A, k = k, sigma = sigma, mc.cores = 3)
 out <- schools.sim(s, mu0 = mu0, A = A, k = k, sigma = sigma)
 save(out, file=paste("output/mcmcout",s,".RData", sep = ""))

### 2013-08-30 jss/article.tex
some edits

@@
 
-The following dataset from the New York Times published on 26 April 1970 contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \citep{1975}.
-In addition one covariate relating to the position of each player was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was an outfielder and 0 otherwise).
+The following dataset from the New York Times published on 26 April 1970 contains information on the batting averages and positions (outfielder=1,otherwise=0) of 18 major league baseball players through their first 45 official at-bats of the 1970 season \citep{1975}.
+
 \begin{CodeChunk}
@@
 R> data(baseball)
-R> z <- baseball[, 4]
-R> n <- baseball[, 3]
+R> z <- baseball$Hits
+R> n <- baseball$At.Bats
 R> x <- ifelse(baseball$Position == "fielder", 1, 0)
@@
 \end{CodeChunk}
-
+%$
 Conditioning on the true batting average for each player we assume that the at-bats are independent and therefore, $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
-Our goal is to estimate point and interval estimates of the true batting average, $p_{j}$, for each player, considering additional information on whether the player is an outfielder or not.
-\code{gbp} provides a way to incorporate such information seamlessly into the second-level hierarchy so that information is shared and regression towards the mean (RTTM) occurs within outfielders and non-outfielders separately.
+Our goal is to obtain point and interval estimates of the true batting average, $p_{j}$, for each player, considering the additional information on whether the player is an outfielder or not.
+\code{gbp} provides a way to incorporate such covariate information seamlessly into the second-level hierarchy so that information is shared and regression towards the mean (RTTM) occurs within outfielders and non-outfielders separately.
 %For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
@@
 \end{CodeInput}
+%$
 \begin{CodeOutput}
@@
 
+%$
+
 All the simulation results are saved in the $18\times1,000$ matrix, \code{bcv$raw.resultRB}, each row of which is for each player.
+
+%$
 
@@
 
-Due to the fact that the estimation procedures in \pkg{Rgbp} rely on derivatives, the package is extremely quick in fitting the available models.
-This makes the package ideal to be used in simulation studies where a hierarchical model needs to be fitted at every iteration and where running a Bayesian model via MCMC would be computationally impractical.
+As an alternative to other derivative based estimation methods such as MLE and REML \pkg{Rgbp} utilizes ADM.
+In addition to be benefits outlined in this paper ADM based models typically have non-random output and so the model can easily be reproduced and compared.
+ADM can also be used
+
+\begin{enumerate}
+\item to initialize an MCMC to speed up time to convergence.
+\item to check the validity of the code of an MCMC program.
+\item as evaluated modules in object-oriented programming.
+\item for preliminary data analyses.
+\item as a demo that a particular prior gives adequate coverage.
+\item for computational speed.
+\item for frequentist procedure checking (via bootstrapping).
+\item for model checking.
+\item to see if there is any reason to develop and use a more precise shrinkage method.
+\item as an envelope for accept-reject and importance sampling possibly leading to higher acceptance ratios than standard envelopes. 
+\end{enumerate}
 

### 2013-08-30 jss/article.tex
up to betas significantly diff

@@
 Conditioning on the true batting average for each player we assume that the at-bats are independent and therefore, $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
-Our goal is to obtain point and interval estimates of the true batting average, $p_{j}$, for each player, considering the additional information on whether the player is an outfielder or not.
-\code{gbp} provides a way to incorporate such covariate information seamlessly into the second-level hierarchy so that information is shared and regression towards the mean (RTTM) occurs within outfielders and non-outfielders separately.
+Our goal is to obtain point and interval estimates of the true batting average, $p_{j}$, for each player, whilst considering the additional information on whether the player is an outfielder or not.
+\code{gbp} provides a way to incorporate such covariate information seamlessly into the second-level hierarchy such that information is shared and regression towards the mean (RTTM) occurs within outfielders and non-outfielders separately.
 %For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
@@
 \end{CodeChunk}
-Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233.
-Also note that the shrinkage estimates are the same for all players due to the fact that they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($\hat{B}_{j}\equiv \hat{r} / (\hat{r}+45)$ = $113 / (113+45)$ = 0.715).
-The estimation results including $\hat{r}=113$ follows.
+% Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233. Also
+Note that the shrinkage estimates are the same for all players due to the fact that they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($\hat{B}_{j}\equiv \hat{r} / (\hat{r}+45)$ = $113 / (113+45)$ = 0.715).
 
@@
 
-We see that the two prior means distinguishing outfielders from other positions are significantly different (p-value = 0.038).
+From the output summary we see that the two prior means distinguishing outfielders from other positions are statistically significantly different (p-value = 0.038).
 Also, the positive sign of $\hat{\beta}_{1}$ indicates that the population mean batting average for all outfielders tends to be higher than that for those in the other positions (estimated odds ratio = exp(0.389)=1.48).

### 2013-08-30 jss/article.tex
edits up to discussion

@@
 
-\subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}
+\subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate} \label{sec:ex:8schools}
 
@@
 
-Now, let's see the shrinkage and 95\% interval plots for more intuition in Figure \ref{fig:baseball}.
-It is obvious that sample means (empty dots) on the upper horizontal line shrink towards two different means, 0.233 and 0.310.
+It is evident in the shrinkage and 95\% interval plots in Figure \ref{fig:baseball} that shrinkage occurs from the sample means (empty dots) on the upper horizontal line towards the two prior means, 0.233 and 0.310.
 For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
@@
 
-The 95\% interval plot shows us range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups.
-Let's see the 10th, 14th, and 15th players on the graph for example.
-They are outfielders but their observed batting averages are far lower than the first five outfielders.
-RTTM means that it can happen by their bad luck though in the long run their batting averages will come back to their expected ones as outfielders (blue horizontal lines).
-So, their posterior means (red dots) can be interpreted as their RTTM.
-
-Then, how much can we trust these interval estimates?
-The following frequency method checking that regards the estimated values, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values will answer it.
-For reference, if we want to try different true values, either 100 for $r$ or (-1, 0.2) for $(\beta_{0}, \beta_{1})$, the additional arguments are \code{A.or.r = 100} and \code{reg.coef = c(-1, 0.2)}; \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of the code below.
+The 95\% interval plot shows the range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups.
+The 10th, 14th, and 15th players, for example, are outfielders but their observed batting averages are far lower than the first five outfielders.
+RTTM suggests that in the long run their batting averages will shrink toward the expected prior means as outfielders (blue horizontal lines).
+
+As in the previous examples in Sections \ref{sec:ex:hosp} and \ref{sec:ex:8schools} to check the level of trust in these interval estimates a method check can be undertaken by assuming the estimates, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, are true values.
+For reference, to do the method check at different true values additional arguments can be specified in the coverage function.
 

### 2013-09-02 jss/article.tex
discussion done

@@
 %%uncomment line below for double-spacing
-%\linespread{1}
+\linespread{2}
+\setlength{\parskip}{1.5cm}%
 
@@
 \section[Discussion]{Discussion}
-\pkg{Rgbp} is an R package for estimating and validating a two-level hierarchical model.
-The package aims to provide a procedure that is not only fast and easy to use but has good frequency properties and can be used in many scenarios for estimating point and interval estimates of true parameters.
-The package provides ``frequency method checking'' functionality to examine repeated sampling properties and test that the method is valid at given hyper-parameter values.
+\pkg{Rgbp} is an R package for estimating and validating two-level Gaussian, Poisson and Binomial hierarchical models.
+The package aims to provide a procedure that is computationally efficient with good frequency properties and includes ``method checking'' functionality to examine repeated sampling properties and test that the method is valid at given hyper-parameter values.
+
+As an alternative to other derivative based estimation methods such as MLE and REML \pkg{Rgbp} provides point and interval estimates of true parameters using the ADM framework.
+Using the ADM framework in conjunction with the specified choice of priors safeguards from cases of overshrinkage and undercoverage that the aforementioned methods suffer from.
 
@@
 
-As an alternative to other derivative based estimation methods such as MLE and REML \pkg{Rgbp} utilizes ADM.
-In addition to be benefits outlined in this paper ADM based models typically have non-random output and so the model can easily be reproduced and compared.
-ADM can also be used
+A benefit of \pkg{Rgbp} is that it produces non-random output, unlike most MCMC methods,  and so results can easily be reproduced and compared across studies.
+In addition to being a standalone analysis tool the package can be used as an aid or a tool in a broader estimation procedure.
+Such as being used to
 
@@
 \item as a demo that a particular prior gives adequate coverage.
-\item for computational speed.
 \item for frequentist procedure checking (via bootstrapping).
@@
 \item to see if there is any reason to develop and use a more precise shrinkage method.
-\item as an envelope for accept-reject and importance sampling possibly leading to higher acceptance ratios than standard envelopes. 
+
+%%these are more ADM than RGBP
+%%\item for computational speed.
+%%\item as an envelope for accept-reject and importance sampling possibly leading to higher acceptance ratios than standard envelopes. 
 \end{enumerate}
+
+\pkg{Rgbp} provides a computationally efficient estimation procedure for Gaussian, Poisson and Binomial hierarchical models.
+An extension to Rgbp, that is underway, is to include functionality for fitting Gamma hierarchical models.
 

### 2013-09-03 jss/article.tex
edit by Tak on 3 Sep

@@
 So, once we fix these hyper-parameters at specific values, we can generate true parameters.
-Suppose we generated 500 $(=N_{sim}$) {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (\ref{normalprior}), where $A$ and $\beta$ are given.
-Then using (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}, $ where $i$ indicates the $i$-th simulation.
+Suppose we generated 500 $(=N_{sim}$) {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (\ref{normalprior}), where $A$ and $\beta$ are given and the superscript $(i)$ indicates the $i$-th simulation.
+Then using (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.
 
@@
 
-So, its unbiased variance estimator  for $Var(\bar{I}_{j})$ is simply the sample variance of indicators over the number of simulations.
+Then, its unbiased variance estimator  for $Var(\bar{I}_{j})$ is simply the sample variance of indicators over the number of simulations.
 \begin{equation}
@@
 \subsubsection{Rao-Blackwellized Unbiased Coverage Estimates}
-Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (sufficient statistic) into consideration.
+Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (sufficient statistic) into account.
 Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset.
@@
 
-Taking the first hospital as an example, the variance of RB unbiased coverage estimate is about 15 times smaller than that of simple one.
+Taking the first hospital as an example, the variance estimate of RB unbiased coverage estimate is about 15 times smaller than that of simple one.
 It means that 1,000 RB unbiased coverage estimates are as precise as 15,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.
@@
 
-It is evident in the shrinkage and 95\% interval plots in Figure \ref{fig:baseball} that shrinkage occurs from the sample means (empty dots) on the upper horizontal line towards the two prior means, 0.233 and 0.310.
+It is evident in the shrinkage plot in Figure \ref{fig:baseball} that shrinkage occurs from the sample means (empty dots) on the upper horizontal line towards the two prior means, 0.233 and 0.310.
 For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
@@
 As in the previous examples in Sections \ref{sec:ex:hosp} and \ref{sec:ex:8schools} to check the level of trust in these interval estimates a method check can be undertaken by assuming the estimates, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, are true values.
-For reference, to do the method check at different true values additional arguments can be specified in the coverage function.
 
@@
 \end{figure}
+
+For reference, to do the method check at different true values additional arguments can be specified in the coverage function.
+For example, if we want to try different true values, either 100 for $r$ or (-1, 0.2) for $(\beta_{0}, \beta_{1})$, the additional arguments are \code{A.or.r = 100} and \code{reg.coef = c(-1, 0.2)}; \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of the above code.
 
@@
 In addition to being a standalone analysis tool the package can be used as an aid or a tool in a broader estimation procedure.
-Such as being used to
+Such as being used
 
@@
 \item as a demo that a particular prior gives adequate coverage.
-\item for frequentist procedure checking (via bootstrapping).
+\item for frequentist procedure checking.
 \item for model checking.

### 2013-09-03 jss/article.tex
Tak edit on 3 Sep

@@
 \begin{CodeOutput}
- [1] 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 0.954 0.955 
-[13] 0.954 0.955 0.954 0.954 0.954 0.955 0.954 0.954 0.954 0.954 0.954 0.954 
-[25] 0.953 0.954 0.953 0.953 0.954 0.952 0.952
+ [1] 0.956 0.956 0.956 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 
+[13] 0.955 0.954 0.954 0.954 0.954 0.954 0.955 0.954 0.954 0.953 0.953 0.953
+[25] 0.954 0.954 0.954 0.953 0.953 0.953 0.952
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.960 0.953 0.956 0.952 0.957 0.957 0.960 0.949 0.949 0.944 0.951 0.947 
-[13] 0.949 0.958 0.958 0.959 0.953 0.954 0.953 0.955 0.956 0.952 0.953 0.959 
-[25] 0.945 0.945 0.953 0.946 0.953 0.948 0.955
+ [1] 0.947 0.952 0.963 0.961 0.957 0.957 0.959 0.952 0.957 0.957 0.941 0.958 
+[13] 0.954 0.962 0.935 0.940 0.955 0.952 0.951 0.941 0.955 0.952 0.954 0.946 
+[25] 0.942 0.952 0.958 0.945 0.938 0.958 0.948
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.0016 0.0016 0.0014 0.0013 0.0013 0.0013 0.0013 0.0013 0.0013 0.0013 0.0012 
-[12] 0.0012 0.0012 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0010
-[23] 0.0010 0.0010 0.0010 0.0009 0.0009 0.0008 0.0008 0.0007 0.0007
+ [1] 0.0017 0.0017 0.0014 0.0014 0.0014 0.0014 0.0014 0.0014 0.0013 0.0013 0.0013 
+[12] 0.0013 0.0012 0.0012 0.0012 0.0012 0.0011 0.0012 0.0011 0.0011 0.0011 0.0011
+[23] 0.0010 0.0011 0.0010 0.0010 0.0009 0.0009 0.0009 0.0007 0.0007
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.0062 0.0067 0.0065 0.0068 0.0064 0.0064 0.0062 0.0070 0.0070 0.0073 0.0068 
-[12] 0.0071 0.0070 0.0063 0.0063 0.0063 0.0067 0.0066 0.0067 0.0066 0.0065 0.0068
-[23] 0.0067 0.0063 0.0072 0.0072 0.0067 0.0072 0.0067 0.0070 0.0066
-\end{CodeOutput}
-\end{CodeChunk}
-
-Taking the first hospital as an example, the variance estimate of RB unbiased coverage estimate is about 15 times smaller than that of simple one.
-It means that 1,000 RB unbiased coverage estimates are as precise as 15,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.
+ [1] 0.0071 0.0068 0.0060 0.0061 0.0064 0.0064 0.0063 0.0068 0.0064 0.0064 0.0075 
+[12] 0.0063 0.0066 0.0060 0.0078 0.0075 0.0066 0.0068 0.0068 0.0075 0.0066 0.0068 
+[23] 0.0066 0.0072 0.0074 0.0068 0.0063 0.0072 0.0076 0.0063 0.0070
+\end{CodeOutput}
+\end{CodeChunk}
+
+Taking the first hospital as an example, the variance estimate of RB unbiased coverage estimate is about 17 times smaller than that of simple one.
+It means that 1,000 RB unbiased coverage estimates are as precise as 17,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.
 
@@
 \begin{CodeOutput}
- [1] 0.964 0.958 0.964 0.960 0.956 0.959 0.958 0.966
+ [1] 0.966 0.959 0.967 0.960 0.959 0.962 0.960 0.966
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.0014 0.0013 0.0016 0.0014 0.0014 0.0012 0.0012 0.0017
+ [1] 0.0013 0.0012 0.0013 0.0013 0.0011 0.0011 0.0010 0.0017
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.973 0.973 0.974 0.971 0.971 0.973 0.972 0.973 0.972 0.973 0.971 0.973 
-[13] 0.971 0.972 0.974 0.972 0.972 0.973
+ [1] 0.972 0.973 0.973 0.973 0.972 0.972 0.972 0.972 0.973 0.972 0.973 0.972 
+[13] 0.973 0.973 0.971 0.973 0.971 0.973
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.0010 0.0011 0.0011 0.0013 0.0012 0.0011 0.0012 0.0011 0.0012 0.0010 
-[11] 0.0013 0.0012 0.0013 0.0013 0.0010 0.0010 0.0010 0.0010
+ [1] 0.0015 0.0011 0.0012 0.0011 0.0015 0.0012 0.0012 0.0010 0.0011 0.0012 
+[11] 0.0010 0.0012 0.0010 0.0011 0.0013 0.0011 0.0013 0.0010
 \end{CodeOutput}

### 2013-09-10 jss/article.tex
adjusting space to 0.5
edit Normal structure

@@
 %%uncomment line below for double-spacing
-\linespread{2}
-\setlength{\parskip}{1.5cm}%
+\linespread{1}
+\setlength{\parskip}{0.5cm}%
 
@@
 
-where $\mu_{0j} = x^{T}_{j} \mathbf{\beta}$, $j=1, \ldots k$, $x_{j}$ is the $j$-th group's covariate vector ($m\times 1$), $m$ is the number of regression coefficients and both $\mathbf{\beta}$ and $A$ are unknown.
-Note that if there is no covariate then $x_{j}=1$ for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
+where $\mu_{0j} = x^{T}_{j} \mathbf{\beta}_{(m\times1)}=\beta_{0}+\beta_{1}x_{1, j} + \cdots + \beta_{m-1}x_{m-1, j}$, $j=1, \ldots k$ and $m$ is the number of regression coefficients including an intercept term.
+The notation $x_{j}^{T}=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $m\times 1$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
+Both $\mathbf{\beta}_{(m\times1)}$ and the second-level variance $A$ are unknown.
+Note that if there is no covariate then $x_{j}=1$ just for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
 For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean.

### 2013-09-11 jss/article.tex
updates

--- 2013-09-03 jss/article.tex
@@
 %%uncomment line below for double-spacing
-\linespread{2}
-\setlength{\parskip}{1.5cm}%
-
+%\linespread{2}
+%\setlength{\parskip}{1.5cm}%
+\setlength\parindent{24pt}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkages.
+By integrating over $\mu_{j}$ for $j = 1 \ldots k$ a marginal distribution, useful for model checking (Section \ref{discussion}), can be derived
+\begin{equation} \label{normalmarginal}
+y_{j}\vert \beta, A \stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, V_{j} + A). 
+\end{equation}
 
@@
 The results provided by \code{gpb} suggests that there is little evidence that the training provided much added benefit due to the fact that every school's $95\%$ posterior interval contains 0.
+In the case where the number of groups is large \pkg{Rgbp} provides a summary feature:
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> summary(g)
+\end{CodeInput}
+\begin{CodeOutput}
+Main summary:
+
+                      obs.mean   se prior.mean shrinkage low.intv post.mean
+Unit with min(se)        -1.00  9.0       8.17     0.408   -13.30      2.74     
+Unit with median(se)1     1.00 11.0       8.17     0.507   -13.03      4.63     
+Unit with median(se)2     7.00 11.0       8.17     0.507    -8.78      7.59     
+Unit with max(se)        12.00 18.0       8.17     0.734   -10.21      9.19     
+Overall Mean                   12.5       8.17     0.552    -9.16      8.17
+
+                      upp.intv post.sd
+                          16.7    7.63
+                          20.1    8.44
+                          23.6    8.26
+                          29.9   10.23
+                          25.7    8.90
+
+Second-level Variance Component Estimation Summary:
+alpha = log(A) for Gaussian or alpha =  log(1/r) for Binomial and Poisson data:
+
+  post.mode.alpha post.sd.alpha post.mode.A
+1            4.77          1.14         118
+
+Regression Summary:
+
+      estimate   se z.val p.val
+beta0    8.168 5.73 1.425 0.154
+\end{CodeOutput}
+\end{CodeChunk}
+The summary provides results regarding the second level hierarchy parameters.
+It can be seen that the estimate of the second level mean, \code{beta0}, is not significantly different from 0 suggesting that there was no effect of the coaching program on SAT math scores.
+
+\pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in Figure \ref{fig:8schoolsplot}.
+Plotting the results provides a visual aid to understanding but is only largely beneficial when the number of groups $(k)$ is small.
 
@@
 \end{figure}
-
-\pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in Figure \ref{fig:8schoolsplot}.
-Plotting the results provides a visual aid to understanding but is only largely beneficial when the number of groups $(k)$ is small.
-In the case where the number of groups is large \pkg{Rgbp} provides a summary feature:
-
-\begin{CodeChunk}
-\begin{CodeInput}
-R> summary(g)
-\end{CodeInput}
-\begin{CodeOutput}
-Main summary:
-
-                      obs.mean   se prior.mean shrinkage low.intv post.mean
-Unit with min(se)        -1.00  9.0       8.17     0.408   -13.30      2.74     
-Unit with median(se)1     1.00 11.0       8.17     0.507   -13.03      4.63     
-Unit with median(se)2     7.00 11.0       8.17     0.507    -8.78      7.59     
-Unit with max(se)        12.00 18.0       8.17     0.734   -10.21      9.19     
-Overall Mean                   12.5       8.17     0.552    -9.16      8.17
-
-                      upp.intv post.sd
-                          16.7    7.63
-                          20.1    8.44
-                          23.6    8.26
-                          29.9   10.23
-                          25.7    8.90
-
-Second-level Variance Component Estimation Summary:
-alpha = log(A) for Gaussian or alpha =  log(1/r) for Binomial and Poisson data:
-
-  post.mode.alpha post.sd.alpha post.mode.A
-1            4.77          1.14         118
-
-Regression Summary:
-
-      estimate   se z.val p.val
-beta0    8.168 5.73 1.425 0.154
-\end{CodeOutput}
-\end{CodeChunk}
 
@@
 
-\section[Discussion]{Discussion}
+\section[Discussion]{Discussion and Summary} \label{discussion}
 \pkg{Rgbp} is an R package for estimating and validating two-level Gaussian, Poisson and Binomial hierarchical models.
@@
 Using the ADM framework in conjunction with the specified choice of priors safeguards from cases of overshrinkage and undercoverage that the aforementioned methods suffer from.
+% (TODO: need citation).
 
@@
 
-A benefit of \pkg{Rgbp} is that it produces non-random output, unlike most MCMC methods,  and so results can easily be reproduced and compared across studies.
+A benefit of \pkg{Rgbp} is that it produces non-random output and so results can easily be reproduced and compared across studies.
 In addition to being a standalone analysis tool the package can be used as an aid or a tool in a broader estimation procedure.
-Such as being used
-
-\begin{enumerate}
-\item to initialize an MCMC to speed up time to convergence.
-\item to check the validity of the code of an MCMC program.
-\item as evaluated modules in object-oriented programming.
-\item for preliminary data analyses.
-\item as a demo that a particular prior gives adequate coverage.
-\item for frequentist procedure checking.
-\item for model checking.
-\item to see if there is any reason to develop and use a more precise shrinkage method.
-
-%%these are more ADM than RGBP
-%%\item for computational speed.
-%%\item as an envelope for accept-reject and importance sampling possibly leading to higher acceptance ratios than standard envelopes. 
-\end{enumerate}
-
-\pkg{Rgbp} provides a computationally efficient estimation procedure for Gaussian, Poisson and Binomial hierarchical models.
+For example, convergence of an MCMC can be increased by using the point estimates from \pkg{Rgbp} to initialize the chain.
+
+Due to the speed and ease of use \pkg{Rgbp} can be used as a method of preliminary data analysis.
+The results of which may inform the statistician whether a more intensive (in terms of coding and computational time) but more precise method (such as MCMC) should be used.
+
+In addition to the built in ``method checking'' procedure the package can be used to undergo ``model checking''.
+For example, in GRIMM the point estimates from the package can be substituted into the marginal distribution \ref{normalmarginal} to check whether the data marginally follow this distribution.
+If certain modeling assumptions have been violated a more sophisticated model can be assumed and implemented by other means.
+
+to initialize an MCMC to speed up time to convergence. to check the validity of the code of an MCMC program.
+
+as a demo that a particular prior gives adequate coverage. for frequentist procedure checking.
+
+% \pkg{Rgbp} provides a computationally efficient estimation procedure for Gaussian, Poisson and Binomial hierarchical models.
 An extension to Rgbp, that is underway, is to include functionality for fitting Gamma hierarchical models.

### 2013-09-11 Rgbp/R/gr.R

@@ -81,18 +81,15 @@ gr<-function(y,se,X,mu,Alpha=0.95,intercept=T,eps=0.0001){
 	
   ## calculate CIs using skewed normal
   ## TODO: use apply not loop
-  
-  tmp <- lapply(1:length(thetahat), function(i){
-    snparam <- as.numeric(gr.cp.to.dp(c(thetahat[i],shat[i],sign(skew[i])*min(abs(skew[i]),0.94))))
-    row <- c(qsn((1-Alpha)/2,snparam[1], snparam[2], snparam[3], engine = "biv.nt.prob"),thetahat[i],qsn(1-(1-Alpha)/2,snparam[1], snparam[2], snparam[3], engine = "biv.nt.prob"))
-    return(row)
-  })
+
+  snparam <- lapply(1:length(thetahat), function(i){as.numeric(gr.cp.to.dp(c(thetahat[i],shat[i],sign(skew[i])*min(abs(skew[i]),0.94))))})
+  tmp <- lapply(1:length(thetahat), function(i){c(qsn((1-Alpha)/2,snparam[[i]][1], snparam[[i]][2], snparam[[i]][3], engine = "biv.nt.prob"),thetahat[i],qsn(1-(1-Alpha)/2,snparam[[i]][1], snparam[[i]][2], snparam[[i]][3], engine = "biv.nt.prob"))})
   skewedmat <- as.matrix(do.call("rbind", tmp))
 
   
   ## return output
   ## TODO: discuss with Tak and sync output
-  output<- list(sample.mean=y,se=se,prior.mean=prior.mean, prior.mean.hat = mu,shrinkage=Bhat,sd.shrinkage=seB,post.intv.low=skewedmat[,1],post.mean=thetahat,post.intv.upp=skewedmat[,3],post.sd=shat,model="gr",X=X.ini,beta.new=Betahat,beta.var=Betahatvar,intercept=intercept,a.new=log(Ahat),a.var=est.var[1,1], Alpha = Alpha, weight = NA)
[…]

### 2013-09-11 mcmc/gaussian.R

@@ -1,4 +1,5 @@
 library(rstan)
+set_cppo("fast")
 
 args <- commandArgs(TRUE)
 if (length(args)==0){
@@ -7,7 +8,9 @@ if (length(args)==0){
   s <- as.numeric(args[1])
 }
 print(paste("Core number",s, "started at", date()))
-
+s <- sample(1:1000000,1)
+if(file.exists(paste("output/mcmcout",s,".RData", sep = "")))
+  stop("file exists")
 
 rstan_schools <- function(y, sigma){
   schools_code <- '

### 2013-09-11 mcmc/post.R

@@ -1,7 +1,9 @@
 library(Rgbp)
-
-nits <- 1000
-results <- lapply(1:nits, function(s){load(file=paste("output/mcmcout",s,".RData", sep = ""));return(out)})
+file.names <- list.files("output/")
+results <- lapply(file.names, function(s){out <- NULL;try({load(paste("output/",s,sep=""))});return(out)})
+results <- results[!unlist(lapply(results, is.null))]
+nits <- length(results)
+print(nits)
 ind <- as.numeric(apply(do.call("rbind",lapply(results,function(x){x$coverage.ind})),2,mean))
 rb <- apply(do.call("rbind",lapply(results,function(x){x$coverage.RB})),2,mean)
 

### 2013-09-11 jss/article.tex
discussion done

@@
 
-where $\mu_{0j} = x^{T}_{j} \mathbf{\beta}$, $j=1, \ldots k$, $x_{j}$ is the $j$-th group's covariate vector ($m\times 1$), $m$ is the number of regression coefficients and both $\mathbf{\beta}$ and $A$ are unknown.
-Note that if there is no covariate then $x_{j}=1$ for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
+where $\mu_{0j} = x^{T}_{j} \mathbf{\beta}_{(m\times1)}=\beta_{0}+\beta_{1}x_{1, j} + \cdots + \beta_{m-1}x_{m-1, j}$, $j=1, \ldots k$ and $m$ is the number of regression coefficients including an intercept term.
+The notation $x_{j}^{T}=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $m\times 1$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
+Both $\mathbf{\beta}_{(m\times1)}$ and the second-level variance $A$ are unknown.
+Note that if there is no covariate then $x_{j}=1$ just for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
 For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean.
 Based on this conjugate prior distribution it is easy to derive the corresponding posterior distribution
+
 \begin{equation} \label{normalpost}
@@
 In addition to being a standalone analysis tool the package can be used as an aid or a tool in a broader estimation procedure.
-For example, convergence of an MCMC can be increased by using the point estimates from \pkg{Rgbp} to initialize the chain.
-
-Due to the speed and ease of use \pkg{Rgbp} can be used as a method of preliminary data analysis.
+For example, by checking the similarity of output of \pkg{Rgbp} and that of another estimation procedure (such as MCMC) the package can be used as a confirmatory tool to check whether the alternative procedure has been implemented correctly.
+In addition, the parameter estimates obtained via \pkg{Rgbp} can be used to initialize a MCMC thus increasing time to convergence.
+Note, however, that this is only valid when the same model under both procedures is assumed.
+
+Due to the speed and ease of use \pkg{Rgbp} can be utilized as a method of preliminary data analysis.
 The results of which may inform the statistician whether a more intensive (in terms of coding and computational time) but more precise method (such as MCMC) should be used.
+As the package assumes non-informative priors the results can be used as reference point to see whether implementing a more sophisticated model, perhaps with informative priors, should be used.
 
@@
 
-to initialize an MCMC to speed up time to convergence. to check the validity of the code of an MCMC program.
-
-as a demo that a particular prior gives adequate coverage. for frequentist procedure checking.
-
 % \pkg{Rgbp} provides a computationally efficient estimation procedure for Gaussian, Poisson and Binomial hierarchical models.

### 2013-09-11 jss/article.tex
discuss edits

@@
 Due to the speed and ease of use \pkg{Rgbp} can be utilized as a method of preliminary data analysis.
-The results of which may inform the statistician whether a more intensive (in terms of coding and computational time) but more precise method (such as MCMC) should be used.
+The results of which may inform the statistician whether a more intensive (in terms of implementation and computational time) but more precise method (such as MCMC) should be used.
 As the package assumes non-informative priors the results can be used as reference point to see whether implementing a more sophisticated model, perhaps with informative priors, should be used.
@@
 In addition to the built in ``method checking'' procedure the package can be used to undergo ``model checking''.
-For example, in GRIMM the point estimates from the package can be substituted into the marginal distribution \ref{normalmarginal} to check whether the data marginally follow this distribution.
+For example, in GRIMM, the point estimates from the package can be substituted into the marginal distribution in Equation \ref{normalmarginal} to check whether the data marginally follow this distribution.
 If certain modeling assumptions have been violated a more sophisticated model can be assumed and implemented by other means.

### 2013-09-11 jss/article.tex
done

--- 2013-09-11 jss/article.tex
@@
 \section[Discussion]{Discussion and Summary} \label{discussion}
-\pkg{Rgbp} is an R package for estimating and validating two-level Gaussian, Poisson and Binomial hierarchical models.
-The package aims to provide a procedure that is computationally efficient with good frequency properties and includes ``method checking'' functionality to examine repeated sampling properties and test that the method is valid at given hyper-parameter values.
-
-As an alternative to other derivative based estimation methods such as MLE and REML \pkg{Rgbp} provides point and interval estimates of true parameters using the ADM framework.
-Using the ADM framework in conjunction with the specified choice of priors safeguards from cases of overshrinkage and undercoverage that the aforementioned methods suffer from.
+\pkg{Rgbp} is an R package for estimating and validating two-level Gaussian, Binomial and Poisson hierarchical models.
+The package aims to provide a procedure that is computationally efficient with good frequency properties and includes ``method checking'' functionality to examine repeated sampling properties and to test that the method is valid at specified hyper-parameter values.
+
+As an alternative to other derivative based estimation methods such as MLE and REML, \pkg{Rgbp} provides point and interval estimates of parameters using ADM.
+Using the ADM approach, with our specified choice of priors, protects from cases of overshrinkage and undercoverage from which the aforementioned methods suffer from.
 % (TODO: need citation).
@@
 
-A benefit of \pkg{Rgbp} is that it produces non-random output and so results can easily be reproduced and compared across studies.
-In addition to being a standalone analysis tool the package can be used as an aid or a tool in a broader estimation procedure.
-For example, by checking the similarity of output of \pkg{Rgbp} and that of another estimation procedure (such as MCMC) the package can be used as a confirmatory tool to check whether the alternative procedure has been implemented correctly.
-In addition, the parameter estimates obtained via \pkg{Rgbp} can be used to initialize a MCMC thus increasing time to convergence.
-Note, however, that this is only valid when the same model under both procedures is assumed.
-
-Due to the speed and ease of use \pkg{Rgbp} can be utilized as a method of preliminary data analysis.
-The results of which may inform the statistician whether a more intensive (in terms of coding and computational time) but more precise method (such as MCMC) should be used.
-As the package assumes non-informative priors the results can be used as reference point to see whether implementing a more sophisticated model, perhaps with informative priors, should be used.
+A benefit of \pkg{Rgbp} is that it produces non-random output and so results easily can be reproduced and compared across studies.
+In addition to being a standalone analysis tool the package can be used as an aid in a broader estimation procedure.
+For example, by checking the similarity of output of \pkg{Rgbp} and that of another estimation procedure (such as MCMC) the package can be used as a confirmatory tool to check whether the alternative procedure has been programmed correctly.
+In addition, the parameter estimates obtained via \pkg{Rgbp} can be used to initialize a MCMC thus decreasing time to convergence.
+% Note, however, that this is only valid when the same model under both procedures is assumed.
+
+Due to it's speed and ease of use, \pkg{Rgbp} can be used for as a method of preliminary data analysis.
+Such results may tell the statistician whether a more intensive (in terms of implementation and computational time) but more precise method (such as MCMC) is needed.
+
+%As the package assumes non-informative priors the results can be used as reference point to see whether implementing a more sophisticated model, perhaps with informative priors, should be used.
 
 In addition to the built in ``method checking'' procedure the package can be used to undergo ``model checking''.
-For example, in GRIMM the point estimates from the package can be substituted into the marginal distribution \ref{normalmarginal} to check whether the data marginally follow this distribution.
-If certain modeling assumptions have been violated a more sophisticated model can be assumed and implemented by other means.
+For example, in GRIMM, the point estimates from the package can be substituted into the marginal distribution in (\ref{normalmarginal}) to check whether the data marginally follow this distribution.
 

### 2013-09-12 jss/article.tex
half edit

@@
 \pkg{Rgbp} is an R package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner.
-The main products of this package are point and interval estimates for the true parameters, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.}
+The main products of this package are point and interval estimates for each group's parameter, $\mu_{j}$ for Gaussian, $\lambda_{j}$ for Poisson, or $p_{j}$ for Binomial model, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.}
 \Keywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage}
@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} or called a conditionally independent hierarchical model \citep{1989}, producing point and interval estimates of the true parameters.
+\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} or called a conditionally independent hierarchical model \citep{1989}, producing point and interval estimates of  parameters.
 The estimation procedure utilizes approximate Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking").
@@
 %\end{CodeChunk}
-%Considering the type of data, it is reasonable to assume the number of deaths in each hospital follow independent Poisson distributions given an unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where, for each $j$, $n_{j}$ can be interpreted as an exposure (not necessarily an integer) and $\lambda_{j}$ as the true death rate per exposure.
+%Considering the type of data, it is reasonable to assume the number of deaths in each hospital follow independent Poisson distributions given an unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where, for each $j$, $n_{j}$ can be interpreted as an exposure (not necessarily an integer) and $\lambda_{j}$ as  death rate per exposure.
 This data set is also included in the package and can be called by `\code{data(hospital)}' on \proglang{R}.
@@
 
-where $\mu_{0j} = x^{T}_{j} \mathbf{\beta}_{(m\times1)}=\beta_{0}+\beta_{1}x_{1, j} + \cdots + \beta_{m-1}x_{m-1, j}$, $j=1, \ldots k$ and $m$ is the number of regression coefficients including an intercept term.
+where $\mu_{0j} = x_{j}' \mathbf{\beta}_{(m\times1)}=\beta_{0}+\beta_{1}x_{1, j} + \cdots + \beta_{m-1}x_{m-1, j}$, $j=1, \ldots k$ and $m$ is the number of regression coefficients including an intercept term.
 The notation $x_{j}^{T}=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $m\times 1$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
@@
 \code{gbp} is also able to build a Poisson-Gamma hierarchical model.
+For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$ for the $j$-th group, where  $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials.
+The notation $r$ represents the amount of prior information as $n_{j}$ does the amount of observed information.
 Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket [, ] below indicates [mean, variance] of a distribution.
-For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$ for the $j$-th group.
 \begin{equation}
@@
 
-where $\log(\lambda_{0j}) =x_{j}'\beta$, $j=1, \ldots, k$, with two unknown hyper-parameters, $\beta$ and $r$. The posterior distribution of this Poisson-Gamma model given these hyper-parameters is
+where $\log(\lambda_{0j}) =x_{j}'\beta$, $j=1, \ldots, k$, with two unknown hyper-parameters, $\beta_{(m\times1)}$ and $r$.
+The posterior distribution of this Poisson-Gamma model given these hyper-parameters is
 \begin{equation} \label{gammapost}
@@
 \subsection[Binomial-Beta]{Binomial-Beta (``b''=Binomial data)}
-Binomial-Beta hierarchical model is the last model that \code{gbp} can fit. Again, a square bracket below indicates [mean, variance] of a distribution.
+Binomial-Beta hierarchical model is the last model that \code{gbp} can fit.
+Again, $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials of the $j$-th group and the square bracket [, ] below indicates [mean, variance] of a distribution.
 \begin{equation}
@@
 
-where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $\beta$ and $r$ are two unknown hyper-parameters. Then corresponding posterior distribution given  $\beta$ and $r$ is
+where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $\beta_{(m\times1)}$ and $r$ are two unknown hyper-parameters.
+Then corresponding posterior distribution given  $\beta_{(m\times1)}$ and $r$ is
 \begin{equation} \label{betapost}
@@
 As for $\beta$, the flat non-informative distribution above is a common choice.
-In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
+In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of the parameters $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
 In the other two cases, Poisson and Binomial, the distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian.
@@
 After estimating the two posterior moments, for example $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$, \code{gbp} approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
-For the Binomial-Beta model we approximate the posterior distribution of $p_{j}$, $\pi(p_{j}\vert \textbf{y})$, with a Beta distribution and for the Poisson-Gamma model we approximate $\pi(\lambda_{j}\vert \textbf{y})$ with a Gamma distribution.
-Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\pi(\mu_{j}\vert \textbf{y})$ with a skewed-Normal distribution \citep{sn2013}.
+For the Normal-Normal model we actually estimate the first three moments and approximate $\pi(\mu_{j}\vert \textbf{y})$ with a skewed-Normal distribution \citep{sn2013}.
+For the Poisson-Gamma model we approximate $\pi(\lambda_{j}\vert \textbf{y})$ with a Gamma distribution and finally for the Binomial-Beta model we approximate the posterior distribution of $p_{j}$, $\pi(p_{j}\vert \textbf{y})$, with a Beta distribution.
 
@@
 One possible question is, ``Can this dataset benefit from such a hierarchical modeling?'' \cite{modelchecking1996} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
-They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
+They found that their data had more variation than expected of the first-level Poisson distribution and two-level Poisson hierarchical model could successfully account for such additional variation.
 
@@
 Figure \ref{fig:pseudo} will be helpful to understand this process.
-As we can see in (\ref{normalpost}), the distribution of each true parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$.
-So, once we fix these hyper-parameters at specific values, we can generate true parameters.
-Suppose we generated 500 $(=N_{sim}$) {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (\ref{normalprior}), where $A$ and $\beta$ are given and the superscript $(i)$ indicates the $i$-th simulation.
-Then using (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.
+As we can see in (\ref{normalpost}), the distribution of each parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$.
+So, once we fix these hyper-parameters at specific values, we can generate as many parameters as we want.
+Suppose we generated 500 $(=N_{sim}$) {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (\ref{normalprior}), where values of $A$ and $\beta$ are specifically given and the superscript $(i)$ indicates the $i$-th simulation.
+Then using the distribution of observed data in (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.
+Note that we generate one dataset per one parameter set.
 
@@
 Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 pseudo-datasets in order to obtain 500$\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, 500$\}.
-Here, we introduce both simple and Rao-Blackwellized unbiased coverage estimators but \code{coverage} displays only Rao-Blackwellized one.
+Here, we introduce both simple and Rao-Blackwellized unbiased coverage estimators but the function \code{coverage} in \pkg{Rgbp} displays only the Rao-Blackwellized one.
 
@@
 
-The expectation in (\ref{RB}) is the same as Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
+The expectation part in (\ref{RB}) is Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
 We can calculate this probability  because we know the distribution of ($\mu^{(i)}_{j} \vert y^{(i)}_{j}, A, \beta$) in (\ref{normalpost}).
@@
 
-For example, we estimate the first group's coverage probability (that depend on specific $A$ and $\beta$) by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased for $p_{cov, 1}$ but with smaller variance than the previous simple estimator, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$.
+For example, we estimate the first group's true coverage probability $p_{cov, 1}$ (that depend on specific values of $A$ and $\beta$) by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$.
 
@@
 Suppose one knows that the state-level death rate per exposure of this surgery is 0.030 ($\lambda_{0}$).
-Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the true death proportion for each hospital so that one can evaluate the hospital reliabilities.
+Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of   for each hospital so that one can evaluate the hospital reliabilities.
 
@@
 In addition, suppose one knows that the state-level death rate per exposure of this surgery is 0.030 ($\lambda_{0}$).
-Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the true death proportion for each hospital so that one can evaluate the hospital reliabilities.
+Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the death rate for each hospital so that one can evaluate the hospital reliabilities.
 
@@
 
-Next, \code{gbp} will help us fit the Poisson hierarchical model with the Gamma conjugate prior distribution as the NY state-level population distribution of the true death rates ($\lambda_{j}$) whose mean is 0.030 ($\lambda_{0}=0.030$).
+Next, \code{gbp} will help us fit the Poisson hierarchical model with the Gamma conjugate prior distribution as the NY state-level population distribution of the death rates ($\lambda_{j}$) whose mean is 0.030 ($\lambda_{0}=0.030$).
 For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression.
@@
 Considering solely the observed death rates may lead to an unfair comparison because the latter hospital handled twice the caseload.
-\pkg{Rgbp} accounts for this caseload difference, making the true death rate estimate for the former hospital shrink toward the state-level mean ($\lambda_{0}$=0.030) much harder than that for the latter hospital.
+\pkg{Rgbp} accounts for this caseload difference, making the death rate estimate for the former hospital shrink toward the state-level mean ($\lambda_{0}$=0.030) much harder than that for the latter hospital.
 This is what happened to the two left-most hospitals in the first plot.
@@
 
-%and What happened is that Since the 23rd hospital has the lowest upper bound for the true death rate, not to mention the lowest point estimate.
-Also it reveals that the 31st hospital may be the second safest because its upper bound of 95\% interval estimate for the true death rate is lower than the 8th hospital's one.
+%and What happened is that Since the 23rd hospital has the lowest upper bound for  death rate, not to mention the lowest point estimate.
+Also it reveals that the 31st hospital may be the second safest because its upper bound of 95\% interval estimate for  death rate is lower than the 8th hospital's one.
 
@@
 Let's look at the 8th and the 31st hospitals on the graph (or on the outcome for numeric reference).
-The point estimate of the true death rate per exposure of the 31st hospital is higher than the one of the 8th.
+The point estimate of  death rate per exposure of the 31st hospital is higher than the one of the 8th.
 But, the upper bound of interval estimate of this 31st hospital is lower than that of the 8th.
@@
 %These numbers are encouraging, but achieving at least 95\% coverage at %one specific true value does not mean that our model has good repeated %sampling property.
-We need to check whether coverage probabilities are %at least 0.95 when the true parameter value ($r$) varies.
+We need to check whether coverage probabilities are %at least 0.95 when  parameter value ($r$) varies.
 
@@
 This plot shows that the estimated shrinkages are at least %0.947 (under 95\% only at one shrinkage value, 0.01) on the tried range %of true shrinkage values, slightly deviating from the definition of 95\% %confidence interval.
-Note that our model is approximating the true %distribution of shrinkage by ADM (see 4.2).
+Note that our model is approximating  %distribution of shrinkage by ADM (see 4.2).
 

### 2013-09-12 jss/article.tex
edit until error

@@
 For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$ for the $j$-th group, where  $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials.
+For this Poisson model $n_{j}$ can be interpreted as the exposure of the $j$-th group,  not necessarily an interger.
 The notation $r$ represents the amount of prior information as $n_{j}$ does the amount of observed information.
@@
 In addition, suppose one knows that the state-level death rate per exposure of this surgery is 0.030 ($\lambda_{0}$).
-Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the death rate for each hospital so that one can evaluate the hospital reliabilities.
-
-The independent Poisson distribution, \emph{i.e.},  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be an ideal choice to describe these data based on the Poisson approximation when $\lambda$ is small and $n$ is relatively big.
-
-Next, \code{gbp} will help us fit the Poisson hierarchical model with the Gamma conjugate prior distribution as the NY state-level population distribution of the death rates ($\lambda_{j}$) whose mean is 0.030 ($\lambda_{0}=0.030$).
+Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the true death rate ($\lambda_{j}$) for each hospital so that one can evaluate the hospital reliabilities.
+
+The independent Poisson distribution, \emph{i.e.},  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be an ideal choice to describe these data based on the Poisson approximation when $\lambda$ is small and $n$ is relatively large.
+
+Next, \code{gbp} fits the Poisson hierarchical model with the Gamma conjugate prior distribution as the NY state-level population distribution of the death rates whose mean is 0.030 ($\lambda_{0}=0.030$).
 For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression.
@@
 \end{CodeChunk}
+
 For reference, we need to type `\code{R> print(p, sort = FALSE)}' instead of `\code{R> p}' in order to list hospitals by the order of data input in the above output.
@@
 
-The output contains information about observed death ratios ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds of interval estimates ($\hat{\lambda}_{j, low}$, 2.5\% percentiles of posterior distributions if 95\% confidence level is given), posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds  of interval estimates ($\hat{\lambda}_{j, upp}$, 97.5\% percentiles of posterior distributions), and standard deviations of posterior distributions ($sd(\lambda_{j}\vert \textbf{y})$).
+The output contains information about observed death rates ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds of interval estimates ($\hat{\lambda}_{j, low}$, 2.5\% percentiles of posterior distributions if 95\% confidence level is given), posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds  of interval estimates ($\hat{\lambda}_{j, upp}$, 97.5\% percentiles of posterior distributions), and standard deviations of posterior distributions ($sd(\lambda_{j}\vert \textbf{y})$).
 
@@
 If the second level has more information than the first level, \emph{i.e.} ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the estimator will shrink towards the prior mean more than 50\%.
-This is clear because, as caseload increases, shrinkage decreases, depending less on the second-level information.
+This is clear because, as caseload increases, shrinkage decreases, depending less on the NY state-level (second-level) information.
 
@@
 Note that some hospitals' ranks have changed by shrinking much harder towards 0.030 than others.
-For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly the safest hospital among 31 hospitals in terms of the observed death ratio is not actually safer than seemingly the second safest hospital.
+For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly the safest hospital among 31 hospitals in terms of the observed death rate is not actually safer than seemingly the second safest hospital.
 
@@
 The 31st hospital has twice the caseload, which leads to borrowing less information from the NY state-level hierarchy (or shrinking less toward the state-level mean, 0.030) with smaller variance.
+Based on the point and interval estimates, the 31st hospital seems the most reliable one among all candidates.
 
@@
 
-Based on the point and interval estimates, the 31st hospital seems the most reliable one among all the candidates.
 But when fitting a model it is always a good idea to question how reliable the estimation procedure is.
@@
 To answer this question the \code{coverage} function generates pseudo-datasets assuming the estimated $r~(=683.53)$ is a true value.
-For reference, We also could try any other value of $r$, for example $r=600$, by adding another argument, \code{A.or.r = 600}, into the code below; \code{R> pcv <- coverage(p, A.or.r = 600, nsim = 1000)}.
+For reference, we can designate any other value of $r$, for example $r=600$, by adding another argument, \code{A.or.r = 600}, into the code below; \code{R> pcv <- coverage(p, A.or.r = 600, nsim = 1000)}.
 

### 2013-09-12 jss/article.tex
edit after error

@@
 The following is the general Normal-Normal hierarchical model assumed by \code{gbp}.
-For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates the \emph{j}-th group among \emph{k} groups in the dataset.
+For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known, and subscript \emph{j} indicates the \emph{j}-th group among \emph{k} groups in the dataset.
 \begin{equation}\label{normalobs}
@@
 Then, its unbiased variance estimator  for $Var(\bar{I}_{j})$ is simply the sample variance of indicators over the number of simulations.
-\begin{equation}
+\begin{equation}\label{svar}
 \widehat{Var}(\bar{I}_{j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}(I^{(i)}_{j}-\bar{I}_{j})^{2},~ j=1, 2, \ldots, k.
@@
 Under the setting where one dataset ($\mathbf{y}^{(i)}_{(k\times1)}$) is simulated per one true parameter set ({\boldmath $\mu$}$^{(i)}_{(k\times1)})$, the unbiased variance estimator for Var($\bar{I}_{RB, j}$) follows.
-\begin{equation}
+\begin{equation}\label{RBvar}
 \widehat{Var}(\bar{I}_{RB, j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}\bigg(E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta)-\bar{I}_{RB, j}\bigg)^{2},~ j=1, 2, \ldots, k.
@@
 
-And the code below calculates 31 simple unbiased coverage estimates for each hospital.
+And the code below shows 31 simple unbiased coverage estimates for each hospital.
 \begin{CodeChunk}
@@
 
-The function \code{coverage} also calculates the standard errors for each hospital's RB unbiased coverage estimate defined as the square root of $S^{2}_{RB, j}/N_{sim}$, where $S^{2}_{RB, j}$ is the sample variance of 1,000 RB unbiased coverage estimates for the $j$-th hospital.
-The following code provides 31 standard errors.
+The function \code{coverage} also calculates the standard errors for each hospital's RB unbiased coverage estimate defined in (\ref{RBvar}).
+The following code provides 31 standard errors for RB estimates.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
-Similarly, 31 standard errors for each simple unbiased coverage estimate are
+Similarly, 31 standard errors for each simple unbiased coverage estimate defined in (\ref{svar}) are
 \begin{CodeChunk}
@@
 Taking the first hospital as an example, the variance estimate of RB unbiased coverage estimate is about 17 times smaller than that of simple one.
-It means that 1,000 RB unbiased coverage estimates are as precise as 17,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.
+It means that 1,000 RB unbiased coverage estimates are as precise as 17,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital, $p_{cov, 1}$.
 

### 2013-09-12 jss/article.tex
edit2 after error

@@
 In this Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_j = V_j/(V_j + A)$.
-As such, schools whose variation within the school ($V_{j}$) is less than the between variation ($A$) schools will shrink greater than $50\%$.
+As such, schools whose variation within the school ($V_{j}$) is less than the between school variation ($A$) will shrink greater than $50\%$.
 The results provided by \code{gpb} suggests that there is little evidence that the training provided much added benefit due to the fact that every school's $95\%$ posterior interval contains 0.
@@
 The method check, assuming the model is correct, generates new pseudo-data from our assumed model.
-It starts by fixing the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\beta}_0$ in this example).
+It starts by fixing the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\beta}_0$ in this example) unless these are specified.
 We then simulate ``true'' $\theta_j$ for each group $j$ and re-fit the model 1,000 times to estimate the coverage probabilities of our procedure.
@@
 
-From the output summary we see that the two prior means distinguishing outfielders from other positions are statistically significantly different (p-value = 0.038).
+From the output of \code{summary} we see that the two prior means distinguishing outfielders from other positions are significantly different (p-value = 0.038).
 Also, the positive sign of $\hat{\beta}_{1}$ indicates that the population mean batting average for all outfielders tends to be higher than that for those in the other positions (estimated odds ratio = exp(0.389)=1.48).
@@
 It is evident in the shrinkage plot in Figure \ref{fig:baseball} that shrinkage occurs from the sample means (empty dots) on the upper horizontal line towards the two prior means, 0.233 and 0.310.
-For reference, the red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
+For reference, the short red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
 For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper horizontal line, there are short red lines toward five directions.
@@
 The 10th, 14th, and 15th players, for example, are outfielders but their observed batting averages are far lower than the first five outfielders.
-RTTM suggests that in the long run their batting averages will shrink toward the expected prior means as outfielders (blue horizontal lines).
+Their observed batting averages close to their lower limits of interval estimates tells us it can happen by their bad luck.
+RTTM suggests that in the long run their batting averages will shrink towards the expected prior mean as outfielders (blue horizontal lines).
 

### 2013-09-12 jss/article.tex
edit3 after error

@@
 where $\mu_{0j} = x_{j}' \mathbf{\beta}_{(m\times1)}=\beta_{0}+\beta_{1}x_{1, j} + \cdots + \beta_{m-1}x_{m-1, j}$, $j=1, \ldots k$ and $m$ is the number of regression coefficients including an intercept term.
-The notation $x_{j}^{T}=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $m\times 1$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
+The notation $x_{j}'=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $m\times 1$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
 Both $\mathbf{\beta}_{(m\times1)}$ and the second-level variance $A$ are unknown.
@@
 
-The method check, assuming the model is correct, generates new pseudo-data from our assumed model.
+The frequency method checking, assuming the model is correct, generates new pseudo-data from our assumed model.
 It starts by fixing the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\beta}_0$ in this example) unless these are specified.
@@
 The 10th, 14th, and 15th players, for example, are outfielders but their observed batting averages are far lower than the first five outfielders.
-Their observed batting averages close to their lower limits of interval estimates tells us it can happen by their bad luck.
-RTTM suggests that in the long run their batting averages will shrink towards the expected prior mean as outfielders (blue horizontal lines).
-
-As in the previous examples in Sections \ref{sec:ex:hosp} and \ref{sec:ex:8schools} to check the level of trust in these interval estimates a method check can be undertaken by assuming the estimates, $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, are true values.
+It can be due to their bad luck because their observed batting averages are close to their lower bounds of interval estimates (left tail area).
+RTTM suggests that their batting averages will shrink towards the expected prior mean of outfielders (0.310) in the long run.
+
+As in the previous examples in Section \ref{sec:ex:hosp} and \ref{sec:ex:8schools}, in order to check the level of trust in these interval estimates, we can proceed to frequency method checking by assuming the estimates, 112.95 for $\hat{r}$ and (-1.194, ~0.389) for $\hat{\beta}'$, are given values.
 
@@
 
-For reference, to do the method check at different true values additional arguments can be specified in the coverage function.
-For example, if we want to try different true values, either 100 for $r$ or (-1, 0.2) for $(\beta_{0}, \beta_{1})$, the additional arguments are \code{A.or.r = 100} and \code{reg.coef = c(-1, 0.2)}; \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)} instead of the above code.
+For reference, to do the frequency method checking at different true values, we need to specify additional arguments in the coverage function.
+For example, if we want to try different true values, either 100 for $r$ or (-1, 0.2) for $(\beta_{0}, \beta_{1})$, the additional arguments are \code{A.or.r = 100} and \code{reg.coef = c(-1, 0.2)}; \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)}.
 

### 2013-09-12 jss/article.tex
edit done by Tak

@@
 \pkg{Rgbp} is an R package for estimating and validating two-level Gaussian, Binomial and Poisson hierarchical models.
-The package aims to provide a procedure that is computationally efficient with good frequency properties and includes ``method checking'' functionality to examine repeated sampling properties and to test that the method is valid at specified hyper-parameter values.
-
-As an alternative to other derivative based estimation methods such as MLE and REML, \pkg{Rgbp} provides point and interval estimates of parameters using ADM.
-Using the ADM approach, with our specified choice of priors, protects from cases of overshrinkage and undercoverage from which the aforementioned methods suffer from.
-% (TODO: need citation).
+The package aims to provide a procedure that is computationally efficient with good frequency properties and includes ``frequency method checking'' functionality to examine repeated sampling properties and to test that the method is valid at specified hyper-parameter values.
+
+As an alternative to other maximization based estimation methods such as MLE and REML, \pkg{Rgbp} provides point and interval estimates of parameters via ADM.
+Using the ADM approach, with our specified choice of priors, protects from cases of overshrinkage and undercoverage from which the aforementioned methods suffer from \citep{accuracy1988}.
 
@@
 
-A benefit of \pkg{Rgbp} is that it produces non-random output and so results easily can be reproduced and compared across studies.
+A benefit of \pkg{Rgbp} is that it produces non-random output and so results are easily reproduced and compared across studies.
 In addition to being a standalone analysis tool the package can be used as an aid in a broader estimation procedure.
@@
 Due to it's speed and ease of use, \pkg{Rgbp} can be used for as a method of preliminary data analysis.
-Such results may tell the statistician whether a more intensive (in terms of implementation and computational time) but more precise method (such as MCMC) is needed.
+Such results may tell statisticians and practitioners alike whether a more intensive method in terms of implementation and computational time, such as MCMC, is needed.
 
@@
 
-In addition to the built in ``method checking'' procedure the package can be used to undergo ``model checking''.
-For example, in GRIMM, the point estimates from the package can be substituted into the marginal distribution in (\ref{normalmarginal}) to check whether the data marginally follow this distribution.
+In addition to the built in ``frequency method checking'' procedure the package can be used to undergo ``model checking''.
+For example, in the Gaussian model, the point estimates of $A$ and $\beta$ from the package are substituted into the marginal distribution in (\ref{normalmarginal}).
+And then we can check whether this maginal distribution explains the data better than the observed data distribution in (\ref{normalobs}).
+If better, e.g.
+in terms of data variation, we can benefit from the two-level hierarchical modeling on the dataset considered.
 

### 2013-09-12 jss/article.tex
fixes

@@
 This package will be useful for frequentists and Bayesians alike.
-Bayesians are able to use the package to see results for a non-informative reference prior before and after constructing their own Bayesian hierarchical model.
-Frequentists will have a procedure that meets or exceeds their confidence specification and repeated sampling.
+Bayesians are able to use the package to see results for a non-informative reference prior before and after constructing their own Bayesian hierarchical model and frequentists will have a procedure with good repeated sampling properties.
 
@@
 
-Each indicator has the independent and identically distributed (\emph{iid}) Bernoulli($p_{cov, j}$) distribution, where $p_{cov, j}$ is the true coverage probability for the $j$-th group depending on specific values of $A$ and $\beta$.
+Each indicator has an independent and identically distributed (\emph{iid}) Bernoulli($p_{cov, j}$) distribution, where $p_{cov, j}$ is the true coverage probability for the $j$-th group depending on specific values of $A$ and $\beta$.
+%For reference, even if we sample $L$ datasets per one parameter set, $L\cdot N_{sim}$ indicators $I^{(i, l)}_{j}, i = 1, \ldots, N_{sim}, l = 1, \ldots, L$, have still $iid$ Bernoulli($p_{cov, j}$) distribution.
 
@@
 \begin{center}
-\includegraphics[width = 3.5in]{hospital2.png}
+\includegraphics[width = 3in]{hospital2.png}
 \caption{Coverage plot via frequency method checking for 31 hospitals}
@@
 The frequency method checking, assuming the model is correct, generates new pseudo-data from our assumed model.
-It starts by fixing the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\beta}_0$ in this example) unless these are specified.
-We then simulate ``true'' $\theta_j$ for each group $j$ and re-fit the model 1,000 times to estimate the coverage probabilities of our procedure.
+Unless otherwise specified, the procedure fixes the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\beta}_0$ in this example) and then simulates ``true'' $\theta_j$ for each group $j$.
+The model is then estimated and this is repeated an \code{nsim} number of times to estimate the coverage probabilities of the procedure.
 
@@
 \begin{center}
-\includegraphics[width = 3.5in]{school2.png}
+\includegraphics[width = 3in]{school2.png}
 \caption{Coverage plot via frequency method checking for 8 schools}
@@
 The 10th, 14th, and 15th players, for example, are outfielders but their observed batting averages are far lower than the first five outfielders.
-It can be due to their bad luck because their observed batting averages are close to their lower bounds of interval estimates (left tail area).
+This can likely be attributed to their bad luck because their observed batting averages are close to the lower bounds of their interval estimates.
 RTTM suggests that their batting averages will shrink towards the expected prior mean of outfielders (0.310) in the long run.
@@
 \begin{center}
-\includegraphics[width = 3.5in]{baseball2.png}
+\includegraphics[width = 3in]{baseball2.png}
 \caption{Coverage plot via frequency method checking for 18 players}
@@
 In addition to the built in ``frequency method checking'' procedure the package can be used to undergo ``model checking''.
-For example, in the Gaussian model, the point estimates of $A$ and $\beta$ from the package are substituted into the marginal distribution in (\ref{normalmarginal}).
-And then we can check whether this maginal distribution explains the data better than the observed data distribution in (\ref{normalobs}).
-If better, e.g.
-in terms of data variation, we can benefit from the two-level hierarchical modeling on the dataset considered.
+For example, in the Gaussian hierarchical model, the assumed marginal distribution of the data is given in (\ref{normalmarginal}).
+By substituting the point estimates of $A$ and $\beta$ from the package into this marginal distribution a test can be constructed to see whether the data follow the marginal distribution suggested by the hierarchical model.
 

### 2013-09-17 jss/article.tex
random effect

@@
 \pkg{Rgbp} is an R package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner.
-The main products of this package are point and interval estimates for each group's parameter, $\mu_{j}$ for Gaussian, $\lambda_{j}$ for Poisson, or $p_{j}$ for Binomial model, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.}
+The main products of this package are point and interval estimates for each group's random effect, $\mu_{j}$ for Gaussian, $\lambda_{j}$ for Poisson, or $p_{j}$ for Binomial model, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.}
 \Keywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage}
@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} or called a conditionally independent hierarchical model \citep{1989}, producing point and interval estimates of  parameters.
+\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} or called a conditionally independent hierarchical model \citep{1989}, producing point and interval estimates of  random effects.
 The estimation procedure utilizes approximate Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking").
@@
 As for $\beta$, the flat non-informative distribution above is a common choice.
-In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of the parameters $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
+In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of random effects $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
 In the other two cases, Poisson and Binomial, the distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian.

### 2013-10-23 jss/article.tex
removing PR1

@@
 \subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}\label{poissonsubsec}
-\code{gbp} is also able to build a Poisson-Gamma hierarchical model.
+\code{gbp} is also able to build a Poisson-Gamma hierarchical model, though its usage is limited to the case where the second-level mean is known ($m=0$).
 For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$ for the $j$-th group, where  $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials.
@@
 \begin{equation}\label{gammaprior}
-\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(r\lambda_{0j})\sim \textrm{Gamma} \left[\lambda_{0j}, ~\frac{\lambda_{0j}}{r} \right],
-\end{equation}
-
-where $\log(\lambda_{0j}) =x_{j}'\beta$, $j=1, \ldots, k$, with two unknown hyper-parameters, $\beta_{(m\times1)}$ and $r$.
-The posterior distribution of this Poisson-Gamma model given these hyper-parameters is
+\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(r\lambda_{0})\sim \textrm{Gamma} \left[\lambda_{0}, ~\frac{\lambda_{0}}{r} \right],
+\end{equation}
+
+where $\lambda_{0}$, the second-level mean, is known a priori and $r$ is the only unknown hyper-parameter. The posterior distribution of this Poisson-Gamma model given this hyper-parameter $r$ is
 \begin{equation} \label{gammapost}
-\lambda_{j}\vert \textbf{y}, \beta, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0j} + n_{j}y_{j})\sim\textrm{Gamma} \left[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}} \right],
-\end{equation}
-
-where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0j}$ and   $B_{j}\equiv r / (r+n_{j})$ for $j=1, \ldots, k$.
+\lambda_{j}\vert \textbf{y}, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0} + n_{j}y_{j})\sim\textrm{Gamma} \left[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}} \right],
+\end{equation}
+
+where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0}$ and   $B_{j}\equiv r / (r+n_{j})$ for $j=1, \ldots, k$.
 
@@
 Again, $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials of the $j$-th group and the square bracket [, ] below indicates [mean, variance] of a distribution.
+Unlike the Poisson-Gamma model, the second-level mean is either known ($m=0$) or unknown ($m\ge1$) a priori.
 \begin{equation}
@@
 
-where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $\beta_{(m\times1)}$ and $r$ are two unknown hyper-parameters.
+where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$, and $\beta_{(m\times1)}$ and $r$ are unknown hyper-parameters.
 Then corresponding posterior distribution given  $\beta_{(m\times1)}$ and $r$ is
@@
 Next, \code{gbp} fits the Poisson hierarchical model with the Gamma conjugate prior distribution as the NY state-level population distribution of the death rates whose mean is 0.030 ($\lambda_{0}=0.030$).
-For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression.
+For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean (the second-level mean) via regression for this Poisson-Gamma model.
 \begin{CodeChunk}

### 2013-11-01 jss/article.tex
correction
new edits

@@
 %\setlength{\parskip}{1.5cm}%
-\setlength\parindent{24pt}
+%\setlength\parindent{24pt}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of random effects $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
-In the other two cases, Poisson and Binomial, the distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian.
-We will show the efficiency of this assignment  in the examples in section 5.
+\\
+
+In the other two cases, Poisson and Binomial, the prior distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian.
+As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if $k\ge2$ and a covariate matrix has a full rank.
+The Poisson model, however, can have such posterior propriety if $k\ge2$ and the second-level mean is known.
+The efficiency of these priors is explored in the examples in section 5.
 

### 2013-11-06 jss/article.tex
edit

--- 2013-10-23 jss/article.tex
@@
 In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of random effects $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
-In the other two cases, Poisson and Binomial, the distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian.
-We will show the efficiency of this assignment  in the examples in section 5.
+\\
+
+In the other two cases, Poisson and Binomial, the flat prior distribution on $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian.
+As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$) has a full rank ($rank(X)=m$).
+The Poisson model, however, can have such posterior propriety if there are two groups whose observed values are greater than 0 and the second-level mean ($\lambda_0$) is known.
+The efficiency of these priors is explored in the examples in section 5.
 

### 2013-11-06 Rgbp/R/pr.R
pr correction

@@ -52,29 +52,25 @@ PRAlphaEst2ndLevelMeanKnown <- function(given, ini) {
   k <- length(n)
   a.ini <- ini$a.ini
 
-  PRDerivAlpha <- function(a) {
-    # The first and second order derivatives of log likelihood with respect to alpha
+  PRLogLikKn <- function (a) { 
     zam <- z + exp(-a) * mu0
     am <- exp(-a) * mu0
-
-    const1 <- ((digamma(zam) -  digamma(am) + n / (exp(-a) + n) - log(1 + n * exp(a))) * mu0
-               - z / (exp(-a) + n))
-    const3 <- (const1 + z * exp(-a) / (exp(-a) + n)^2 + mu0 * n / (n + exp(-a)) 
-               - n * am / (exp(-a) + n)^2 + am * mu0 * (trigamma(zam) - trigamma(am)))
-
-    out <- c(1 - exp(-a) * sum(const1), exp(-a) * sum(const3))
-    out
+    if (any(c(am, zam) <= 0)) {
+      print("The components of lgamma should be positive")
+      stop()
+    } else {
+      sum(dnbinom(z, size = am, prob = exp(-a) / (exp(-a) + n), log=T))
+    }
   }
 
-  dif <- 1
-  eps <- 0.0001
-  while (abs(dif) > eps) { 
-    out1 <- PRDerivAlpha(a.ini)
-    score <- out1[1]
-    hessian <- out1[2]
-    dif <- score / hessian
-    a.ini <- a.ini - dif
+  PostAlpha <- function(a) {
+    a + PRLogLikKn(a)
   }
+
+  a.temp <- optim(a.ini, PostAlpha, control = list(fnscale = -1), method= "L-BFGS-B",
+                  hessian = TRUE,  lower = -Inf, upper = Inf)
+  a.new <- a.temp$par
+  a.hess <- a.temp$hessian
 
   list(a.new = a.ini, a.var = - 1/ hessian)
 }

### 2013-11-06 Rgbp/R/pr.R
pr correction2

@@ -59,7 +59,7 @@ PRAlphaEst2ndLevelMeanKnown <- function(given, ini) {
       print("The components of lgamma should be positive")
       stop()
     } else {
-      sum(dnbinom(z, size = am, prob = exp(-a) / (exp(-a) + n), log=T))
+      sum(dnbinom(z, size = am, prob = exp(-a) / (exp(-a) + n), log = T))
     }
   }
 
@@ -72,7 +72,7 @@ PRAlphaEst2ndLevelMeanKnown <- function(given, ini) {
   a.new <- a.temp$par
   a.hess <- a.temp$hessian
 
-  list(a.new = a.ini, a.var = - 1/ hessian)
+  list(a.new = a.ini, a.var = - 1/ a.hess)
 }
 
 PRAlphaBetaEst2ndLevelMeanUnknown <- function(given, ini) {

### 2013-11-06 jss/article.tex
edit

@@
 Note that the variance in (\ref{gammaprior}) is linear in the mean, whereas a slightly different Poisson-Gamma specification \citep{1997} has been used elsewhere e.g.
-that makes the variance in (\ref{gammaprior}) quadratic.
+that makes the variances in (\ref{gammaprior}) and (\ref{gammapost}) quadratic functions of the mean respectively.
 
@@
 In the other two cases, Poisson and Binomial, the flat prior distribution on $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian.
-As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$) has a full rank ($rank(X)=m$).
+As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$), if any,  has a full rank ($rank(X)=m$).
 The Poisson model, however, can have such posterior propriety if there are two groups whose observed values are greater than 0 and the second-level mean ($\lambda_0$) is known.

### 2013-11-06 jss/article.tex
small mod

--- 2013-11-01 jss/article.tex
@@
 
-In the other two cases, Poisson and Binomial, the prior distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian.
+In the other two cases, Poisson and Binomial, the improper prior uniform distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian.
 As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if $k\ge2$ and a covariate matrix has a full rank.

### 2013-11-08 jss/article.tex
edit

--- 2013-11-06 jss/article.tex
@@
 As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$), if any,  has a full rank ($rank(X)=m$).
-The Poisson model, however, can have such posterior propriety if there are two groups whose observed values are greater than 0 and the second-level mean ($\lambda_0$) is known.
+\\
+
+The Poisson model can have such posterior propriety if there are two groups whose observed values exceed 0 and the second-level mean ($\lambda_0$) is known.
+If $\lambda_0$ is unknown, the posterior distribution for the Poisson model is improper and this model should not be used.
+However, the Binomial model can still be used  instead because the Poisson distribution is just the approximation to the Binomial distribution.
 The efficiency of these priors is explored in the examples in section 5.

### 2013-11-08 jss/article.tex
edit

@@
 In the other two cases, Poisson and Binomial, the flat prior distribution on $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian.
-As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$), if any,  has a full rank ($rank(X)=m$).
+As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$), if any,  has full rank ($rank(X)=m$).
 \\

### 2013-11-12 jss/article.tex
package done

@@
 The main products of this package are point and interval estimates for each group's random effect, $\mu_{j}$ for Gaussian, $\lambda_{j}$ for Poisson, or $p_{j}$ for Binomial model, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.}
-\Keywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage}
-\Plainkeywords{keywords, comma-separated, not capitalized, r} %% without formatting
+\Keywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, R}
+\Plainkeywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, R} 
+%% without formatting
 %% at least one keyword must be supplied
@@
 
-This package will be useful for frequentists and Bayesians alike.
-Bayesians are able to use the package to see results for a non-informative reference prior before and after constructing their own Bayesian hierarchical model and frequentists will have a procedure with good repeated sampling properties.
-
-%\section[Feasible Data Types]{Three Feasible Types of Data }
-%\pkg{Rgbp} is intended to fit a model where two levels of structure are assumed (unit and group levels).
-The model can be characterized by the distributional family assumed for the group level data and in the case of \pkg{Rgbp} this will be either the Normal, Poisson, or Binomial distribution.
-In this section, we will introduce three specific types of feasible data sets that illustrate this fact.
-
-%\subsection{Normal: 8 Schools} \label{8schooldata}
-%The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching.
-The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \citep{1981}.
-%\begin{CodeChunk}
-%\begin{CodeInput}
-%R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
-%R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
-%\end{CodeInput}
-%\end{CodeChunk}
-
-%Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated.
-So, it is reasonable to think that each school-level coaching effect is distributed as an independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$.
-\pkg{Rgbp} includes this data set and can be called by the command `\code{data(schools)}' on \proglang{R}.
-
-%\subsection{Poisson: 31 Hospitals}
-%The following data are from medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 \citep{2012}.
-It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and the total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$).
-The following code is an example of input based on the last ten hospital data.
-%\begin{CodeChunk}
-%\begin{CodeInput}
-%R> z <- c( 14,   9,  15,  13,  35,  26,  25,  20,   35,   27)
-%R> n <- c(593, 602, 629, 636, 729, 849, 914, 940, 1193, 1340)
-%\end{CodeInput}
-%\end{CodeChunk}
-%Considering the type of data, it is reasonable to assume the number of deaths in each hospital follow independent Poisson distributions given an unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where, for each $j$, $n_{j}$ can be interpreted as an exposure (not necessarily an integer) and $\lambda_{j}$ as  death rate per exposure.
-This data set is also included in the package and can be called by `\code{data(hospital)}' on \proglang{R}.
-
-%\subsection{Binomial: 18 Baseball Hitters}
-%The following dataset contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \citep{1975}.
-In addition one covariate relating to the position each player was playing was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was an outfielder and 0 otherwise).
-%\begin{CodeChunk}
-%\begin{CodeInput}
-%R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  %8,  7)
-%R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, %45, 45)
-%R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
-%\end{CodeInput}
-%\end{CodeChunk}
-%The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown true batting average $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$.
-This data set is also a part of the package and can be called on \proglang{R} by `\code{data(baseball)}'.
+This package is useful for both frequentists and Bayesians.
+Bayesians are able to use the package to see results for a non-informative reference prior before and after constructing their own Bayesian hierarchical model and frequentists are provided with a procedure with good repeated sampling properties.
 
@@
 The notation $r$ represents the amount of prior information as $n_{j}$ does the amount of observed information.
-Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket [, ] below indicates [mean, variance] of a distribution.
+Note that the constant, $1/r$, multiplied to the Gamma distribution below is a scaling factor and the square brackets indicates the [mean, variance] of a distribution.
 \begin{equation}
@@
 In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of random effects $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
-\\
 
@@
 As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$), if any,  has full rank ($rank(X)=m$).
-\\
 
@@
 
-%For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($z$) for a specified period after CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital.
-Suppose one knows that the state-level death rate per exposure of this surgery is 0.030 ($\lambda_{0}$).
-Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of   for each hospital so that one can evaluate the hospital reliabilities.
-
-%These data, $\textbf{z}_{(31\times1)}$ and $\textbf{n}_{(31\times1)}$, can be loaded into R using the following code.
-Note that throughout this paper, the symbol `\code{R>}' represents a command prompt (not to be typed into \proglang{R}).
-
 \begin{CodeChunk}
@@
           26,  25,  20,  35,  27)
-R> n <- c( 67, 68, 210, 256, 269, 274, 278, 295, 347, 349, 358, 396, 431,
+R> n <- c(67,  68, 210, 256, 269, 274, 278, 295, 347, 349, 358, 396, 431,
          441, 477, 484, 494, 501, 505, 540, 563, 593, 602, 629, 636, 729,
@@
 
-%and What happened is that Since the 23rd hospital has the lowest upper bound for  death rate, not to mention the lowest point estimate.
-Also it reveals that the 31st hospital may be the second safest because its upper bound of 95\% interval estimate for  death rate is lower than the 8th hospital's one.
-
-%From the output provided by \code{gbp} it can be seen that a reasonable choice of a hospital for the patient is hospital 23.
-Although hospital 8 has a smaller observed mean the fact that hospital 23 has a much higher caseload means that we borrow relatively less information from other hospitals.
-The result being that the upper bound of the $95\%$ interval is smaller.
-
-%provides one more point, which we could not have noticed.
-Let's look at the 8th and the 31st hospitals on the graph (or on the outcome for numeric reference).
-The point estimate of  death rate per exposure of the 31st hospital is higher than the one of the 8th.
-But, the upper bound of interval estimate of this 31st hospital is lower than that of the 8th.
-This interval plot makes the 31st hospital emerge as one of your candidates.
-
-% Also it reveals that the 23rd hospital, whose estimated true rate was the smallest, has also the smallest upper bound.
-If you are a risk-adverse, this hospital will attract you most strongly.
-And if you already chose this 23rd hospital compared to the 8th from the shrinkage plot, your decision might become stronger at this point, excluding the 8th hospital with more certainty.
-
 But when fitting a model it is always a good idea to question how reliable the estimation procedure is.
@@
 For reference, two $31 \times 1,000$ matrices \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual estimates.
-% For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.
-
-%These numbers are encouraging, but achieving at least 95\% coverage at %one specific true value does not mean that our model has good repeated %sampling property.
-We need to check whether coverage probabilities are %at least 0.95 when  parameter value ($r$) varies.
-
-%\begin{CodeChunk}
-%\begin{CodeInput}
-%R> shr <- seq(0.01, 0.99, length.out = 20)
-%R> r.trial <- mean(n) * shr / (1 - shr)
-%R> cov.save <- sapply (1 : length(r.trial), function(i){
-%R>               coverage(p, A.or.r = r.trial[i], mean.PriorDist = 0.02, 
-%R>                        nsim = 500)$average.coverageRB
-%R>             })
-%\end{CodeInput}
-%\end{CodeChunk}
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width = 5.5cm]{hospital3.png}
-%\end{center}
-%\end{figure}
-
-%We plotted \code{cov.save} on \code{shr}, connecting dots (coverage %probabilities).
-This plot shows that the estimated shrinkages are at least %0.947 (under 95\% only at one shrinkage value, 0.01) on the tried range %of true shrinkage values, slightly deviating from the definition of 95\% %confidence interval.
-Note that our model is approximating  %distribution of shrinkage by ADM (see 4.2).
-
-%The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j})=0)$, corresponding to $r=0$, makes the scale of the distribution go to $\infty$ (see (5)), and full shrinkage ($B_{j}=1$) makes $r$ goes to $\infty$, not appropriate for an argument.
 
@@
 \subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Second-level Mean and One Covariate}
-%The New York Times published on 26 April 1970 covered 18 baseball players' batting averages through their first official 45 at-bats of the 1970 season.
-And then we became interested in their batting averages over the remaining season.
 
@@
 
-%Note that the posterior standard deviation tends to be bigger among outfielders than among others.
-Let's see its formula in (9).
-We can notice that the estimated posterior mean is a critical factor that makes posterior variances different from each player because every player has the same at-bats ($n_{j}$) and $r$.
-As the posterior mean gets closer to 0.5, the posterior variance gets bigger and has the biggest value when the posterior mean is 0.5.
-Intuitively, it makes sense.
-If a true batting average is 0.1, we can easily expect less hits.
-But if it is 0.5, we are less certain whether an at-bat would be more likely a hit or not, like a coin tossing.
-Our model is automatically reflecting on such uncertainty.
-
-%In problems where a covariate is present \code{gbp} provides a regression summary (in this example logistic regression)
 \begin{CodeChunk}
@@
 
-%Finally,  we see that Rao-Blackwellized unbiased estimate for the first player is about 26 times more accurate than simple one.
-It is based on the ratio of the sample variances of individual estimates from two approaches.
-%\begin{CodeChunk}
-%\begin{CodeInput}
-%R> var(bcv$raw.resultS[1, ]) / var(bcv$raw.resultRB[1, ])
-%\end{CodeInput}
-%\begin{CodeOutput}
-% [1] 25.64346
-%\end{CodeOutput}
-%\end{CodeChunk}
-% As for the running time, it took 243 seconds for MacBook Pro equipped with a 2.3 GHz dual-core Interl i5 CPU to execute 10,000 simulations.
-
-%However, achieving at least 95\% coverage at specific true values of $r$ and $\beta$ does not mean that our model has good repeated sampling property.
-So, as we did in previous examples, we will see whether coverage probabilities are at least 0.95 when the true shrinkage value ($B(r)$) varies, fixing $\beta$ at estimated values.
-Note that, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}.
-
-%\begin{CodeChunk}
-%\begin{CodeInput}
-%R> shr <- seq(0.01, 0.99, length.out = 20)
-%R> r.trial <- mean(n) * shr / (1 - shr)
-%R> cov.save <- sapply (1 : length(r.trial), function(i){
-%R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
-%R>                        covariates = x, nsim = 500)$average.coverageRB
-%R>             })
-%\end{CodeInput}
-%\end{CodeChunk}
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width = 5.5cm]{baseball4.png}
-%\end{center}
-%\end{figure}
-
-%We drew \code{cov.save} on \code{shr}, conneting dots.
-It shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval.
-Note that even this result does not guarantee good repeated sampling property because $\beta$ was fixed.
-But, this result can definitely be an encouraging sign for our model's good repeated sampling property.
-
-%The reason we tried true shrinkage values between 0.01 and 0.99 is that no shriankge ($\equiv r / (r + n_{j}))$, corresponding to $r=0$, makes parameters of the second-level distribution 0 (see (8)), and full shrinkage corresponds to $r=\infty$ that we cannot designate as an argument of \code{coverage} function.
-
 \section[Discussion]{Discussion and Summary} \label{discussion}
@@
 Using the ADM approach, with our specified choice of priors, protects from cases of overshrinkage and undercoverage from which the aforementioned methods suffer from \citep{accuracy1988}.
-
-%In addition to good frequency properties Bayesians will be able to use the package to see the results from a non-informative reference point.
-This allows the user to examine whether it is worth to implement a full Bayesian model (which is often more time consuming).
 
@@
 
-%As the package assumes non-informative priors the results can be used as reference point to see whether implementing a more sophisticated model, perhaps with informative priors, should be used.
-
 In addition to the built in ``frequency method checking'' procedure the package can be used to undergo ``model checking''.
@@
 By substituting the point estimates of $A$ and $\beta$ from the package into this marginal distribution a test can be constructed to see whether the data follow the marginal distribution suggested by the hierarchical model.
-
-% \pkg{Rgbp} provides a computationally efficient estimation procedure for Gaussian, Poisson and Binomial hierarchical models.
-An extension to Rgbp, that is underway, is to include functionality for fitting Gamma hierarchical models.
 

### 2013-11-12 Rgbp/R/gbp.R

@@ -4,6 +4,12 @@ gbp <- function(x, w, covariates, mean.PriorDist, model, intercept, Alpha, n.IS,
 gbp.default <- function(x, w, covariates, mean.PriorDist, model = "gaussian", 
                         intercept = TRUE, Alpha = 0.95, 
                         n.IS = 0, trial.scale = 2.5, normal.CI = FALSE) {
+
+  ##input checks
+  if((abs(max(x) - min(x)) == 0) & (abs(max(w) - min(w)) == 0) & missing(mean.PriorDist))
+    stop("Groups have identical data. This program can not yet give reliable results for this data.")
+  
+  
 ######
   res <- switch(model, 
        gaussian = gr(x, w, X = covariates, mu = mean.PriorDist, Alpha = Alpha, intercept = intercept, normal.CI = normal.CI), 

### 2013-11-12 jss/article.tex
warning added + art changes

@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} or called a conditionally independent hierarchical model \citep{1989}, producing point and interval estimates of  random effects.
+\pkg{Rgbp} is an R package for estimating and validating a two-level model, also known as a conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} or a conditionally independent hierarchical model \citep{1989}, producing point and interval estimates of  random effects.
 The estimation procedure utilizes approximate Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking").
@@
 The notation $x_{j}'=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $m\times 1$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
-Both $\mathbf{\beta}_{(m\times1)}$ and the second-level variance $A$ are unknown.
-Note that if there is no covariate then $x_{j}=1$ just for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
+It is assumed that the second-level variance $A$ is unknown and that $\mathbf{\beta}_{(m\times1)}$ is also unknown unless specified otherwise.
+Note that if there are no covariates then $x_{j}=1$, ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
 For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean.
@@
 If $\lambda_0$ is unknown, the posterior distribution for the Poisson model is improper and this model should not be used.
-However, the Binomial model can still be used  instead because the Poisson distribution is just the approximation to the Binomial distribution.
+In the case where the Poisson model is as an approximation to the Binomial and the exposures, $n_j$, are known then the Binomial model should be used as an alternative to the Poisson.
 The efficiency of these priors is explored in the examples in section 5.

### 2013-11-12 Rgbp/R/gbp.R

@@ -8,6 +8,9 @@ gbp.default <- function(x, w, covariates, mean.PriorDist, model = "gaussian",
   ##input checks
   if((abs(max(x) - min(x)) == 0) & (abs(max(w) - min(w)) == 0) & missing(mean.PriorDist))
     stop("Groups have identical data. This program can not yet give reliable results for this data.")
+
+  if(model == "poisson" & missing(mean.PriorDist))
+    warning("Model is Poisson and the prior mean is unknown. This program can not yet give reliable results for this data. If the Poisson is being used as an approximation to the Binomial and the exposures are known then please assume a Binomial model")
   
   
 ######

### 2013-11-12 qinstall.R

@@ -1,3 +1,3 @@
 #!/usr/bin/R
-install.packages("Rgbp_1.0.2.tar.gz",repos=NULL,type="source")
+install.packages("Rgbp_1.0.3.tar.gz",repos=NULL,type="source")
 library(Rgbp)

### 2013-11-15 jss/article.tex
edit

@@
 
-The output contains information about observed death rates ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds of interval estimates ($\hat{\lambda}_{j, low}$, 2.5\% percentiles of posterior distributions if 95\% confidence level is given), posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds  of interval estimates ($\hat{\lambda}_{j, upp}$, 97.5\% percentiles of posterior distributions), and standard deviations of posterior distributions ($sd(\lambda_{j}\vert \textbf{y})$).
+The output contains information about observed death rates ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds of interval estimates ($\hat{\lambda}_{j, low}$, 2.5\% percentiles of the approximate posterior distributions if 95\% confidence level is given), approximate posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds  of interval estimates ($\hat{\lambda}_{j, upp}$, 97.5\% percentiles of the approximate posterior distributions), and standard deviations of the approximate posterior distributions ($sd(\lambda_{j}\vert \textbf{y})$).
 
@@
 On top of that, more specific estimation results, such as the posterior mode and standard deviation of $\alpha\equiv\log(1/r)$, follow.
-When we do not know the prior mean in advance, unlike this hospital problem, \code{gbp} always fits the natural link, \emph{i.e.} a linear regression for the Normal model, a log-linear regression for the Poisson model, and a logistic regression for the Binomial model.
 \begin{CodeChunk}
@@
 
-For reference, two $31 \times 1,000$ matrices \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual estimates.
+For reference, two $31 \times 1,000$ matrices \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual estimates, $I^{(i)}_{j}$ and $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta)$.
 
@@
 
-From the output of \code{summary} we see that the two prior means distinguishing outfielders from other positions are significantly different (p-value = 0.038).
+From the \code{Regression Summary}, one of the outputs of \code{summary}, we see that the two prior means distinguishing outfielders from other positions are significantly different (p-value for $\hat{\beta}_1$= 0.038).
 Also, the positive sign of $\hat{\beta}_{1}$ indicates that the population mean batting average for all outfielders tends to be higher than that for those in the other positions (estimated odds ratio = exp(0.389)=1.48).

### 2013-11-15 Rgbp/R/br.R
IS

@@ -424,58 +424,58 @@ BRIS <- function(given, ini, a.res, n.IS = 5000, df.IS = 4, trial.scale = 2.5) {
   }
 
   optimax <- optimize(SkewedNormal, lower = -10, upper = 0, maximum = TRUE)$maximum
-  a.IS <- rsn(n.IS, location = a.new + abs(a.new - optimax), scale = trial.scale, shape = -3)
+  a.IS <- rsn(n.IS * 10, location = a.new + abs(a.new - optimax), scale = trial.scale, shape = -3)
   a.IS.den <- dsn(a.IS, location = a.new + abs(a.new - optimax), 
                   scale = trial.scale, shape = -3)
 
-  beta.IS.temp <- sapply(1 : n.IS, function(t) { 
+  beta.IS.temp <- sapply(1 : (n.IS * 10), function(t) { 
                     BetaHatSubAlpha(a.IS[t])
                   })
 
-  beta.IS.mean <- sapply(1 : n.IS, function(t) {
+  beta.IS.mean <- sapply(1 : (n.IS * 10), function(t) {
                      beta.IS.temp[, t]$beta.new
                    })
 
-  beta.IS.vCov <- sapply(1 : n.IS, function(t) {
+  beta.IS.vCov <- sapply(1 : (n.IS * 10), function(t) {
                      -solve(beta.IS.temp[, t]$beta.hessian)
                   })
 
   if(m == 1) {
-    beta.IS <- sapply(1 : n.IS, function(t) {
+    beta.IS <- sapply(1 : (n.IS * 10), function(t) {
                  beta.IS.mean[t] + sqrt(beta.IS.vCov[t] * (df.IS - 2) / df.IS) * rt(1, df = df.IS)
                })
 
-    beta.IS.den <- sapply(1 : n.IS, function(t) {
+    beta.IS.den <- sapply(1 : (n.IS * 10), function(t) {
       dt( (beta.IS[t] - beta.IS.mean[t]) / sqrt(beta.IS.vCov[t] * (df.IS - 2) / df.IS), df = df.IS) /
       sqrt(beta.IS.vCov[t] * (df.IS - 2) / df.IS)
     })
 
-    ab.logpost <- sapply(1 : n.IS, function(t) { 
+    ab.logpost <- sapply(1 : (n.IS * 10), function(t) { 
[…]

### 2013-11-15 Rgbp/R/br.R
error fix

@@ -42,7 +42,7 @@ BRInitialValue2ndLevelMeanUnknown <- function(given) {
   }	
 
   p0.ini <- mean(exp(x %*% b.ini) / (1 + exp(x %*% b.ini)))
-  r.ini <- p0.ini * (1 - p0.ini) / var(y) 
+  r.ini <- p0.ini * (1 - p0.ini) / (var(y) + 1)
   list(x = x, b.ini = b.ini, a.ini = -log(r.ini))
 }
 
@@ -194,7 +194,6 @@ BRAlphaBetaEst2ndLevelMeanUnknown <- function(given, ini) {
     b.sub.a <-  BetaHatSubAlpha(a)$beta.new
     a + BRLogLikUn(a, b.sub.a) - 0.5 * log(det(-BRDerivBeta2order(a, b.sub.a)))
   }
-
   a.temp <- optim(a.ini, MarginalPostAlpha, control = list(fnscale = -1), method= "L-BFGS-B",
                   hessian = TRUE,  lower = -Inf, upper = Inf)
   a.new <- a.temp$par

### 2013-11-15 Rgbp/R/pr.R
error fix 2

@@ -2,7 +2,7 @@ PRInitialValue2ndLevelMeanKnown <- function(given) {
   # This function makes the initial values needed to run PRIMM.
   # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
  
-  r.ini <- given$prior.mean / var(given$sample.mean)
+  r.ini <- given$prior.mean / (var(given$sample.mean)+1)
 
   list(a.ini = -log(r.ini))
 }

### 2013-11-15 Rgbp/R/br.R
edit

@@ -3,9 +3,9 @@ BRInitialValue2ndLevelMeanKnown <- function(given) {
   # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
 
   if (given$prior.mean == 0) {
-    r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / var(given$sample.mean)
+    r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / (var(given$sample.mean) + 1)
   } else {
-    r.ini <- given$prior.mean * (1 - given$prior.mean) / var(given$sample.mean)
+    r.ini <- given$prior.mean * (1 - given$prior.mean) / (var(given$sample.mean) + 1)
   }
 
   list(r.ini = r.ini, a.ini = -log(r.ini))

### 2013-11-15 Rgbp/R/pr.R

@@ -2,7 +2,7 @@ PRInitialValue2ndLevelMeanKnown <- function(given) {
   # This function makes the initial values needed to run PRIMM.
   # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
  
-  r.ini <- given$prior.mean / (var(given$sample.mean)+1)
+  r.ini <- given$prior.mean / (var(given$sample.mean) + 1)
 
   list(a.ini = -log(r.ini))
 }
@@ -38,7 +38,7 @@ PRInitialValue2ndLevelMeanUnknown <- function(given) {
   }	
 
   mu0.ini <- mean(exp(x %*% b.ini))
-  r.ini <- mu0.ini / var(y)
+  r.ini <- mu0.ini / (var(y) + 1)
 
   list(x = x, b.ini = b.ini, a.ini = -log(r.ini))
 }

### 2013-11-15 Rgbp/R/br.R
nothing

@@ -13,8 +13,8 @@ BRInitialValue2ndLevelMeanKnown <- function(given) {
       r.ini <- given$prior.mean * (1 - given$prior.mean) / (var(given$sample.mean) + 1)
     } else {
       r.ini <- given$prior.mean * (1 - given$prior.mean) / var(given$sample.mean)
+    }
   }
-
   list(r.ini = r.ini, a.ini = -log(r.ini))
 }
 
@@ -54,7 +54,7 @@ BRInitialValue2ndLevelMeanUnknown <- function(given) {
     r.ini <- p0.ini * (1 - p0.ini) / (var(y) + 1)
   } else {
     r.ini <- p0.ini * (1 - p0.ini) / var(y)
-
+  }
   list(x = x, b.ini = b.ini, a.ini = -log(r.ini))
 }
 

### 2013-11-15 Rgbp/R/br.R
coding

@@ -3,13 +3,13 @@ BRInitialValue2ndLevelMeanKnown <- function(given) {
   # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
 
   if (given$prior.mean == 0) {
-    if(all(given$sample.mean) == mean(given$sample.mean)) {
+    if(all(given$sample.mean == mean(given$sample.mean))) {
       r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / (var(given$sample.mean) + 1)
     } else {
       r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / var(given$sample.mean)
     }
   } else {
-    if(all(given$sample.mean) == mean(given$sample.mean)) {
+    if(all(given$sample.mean == mean(given$sample.mean))) {
       r.ini <- given$prior.mean * (1 - given$prior.mean) / (var(given$sample.mean) + 1)
     } else {
       r.ini <- given$prior.mean * (1 - given$prior.mean) / var(given$sample.mean)
@@ -50,7 +50,7 @@ BRInitialValue2ndLevelMeanUnknown <- function(given) {
 
   p0.ini <- mean(exp(x %*% b.ini) / (1 + exp(x %*% b.ini)))
 
-  if(all(y) == mean(y)) {
+  if(all(y == mean(y))) {
     r.ini <- p0.ini * (1 - p0.ini) / (var(y) + 1)
   } else {
     r.ini <- p0.ini * (1 - p0.ini) / var(y)

### 2013-11-15 Rgbp/R/gbp.R

@@ -6,9 +6,6 @@ gbp.default <- function(x, w, covariates, mean.PriorDist, model = "gaussian",
                         n.IS = 0, trial.scale = 2.5, normal.CI = FALSE) {
 
   ##input checks
-  if((abs(max(x) - min(x)) == 0) & (abs(max(w) - min(w)) == 0) & missing(mean.PriorDist))
-    stop("Groups have identical data. This program can not yet give reliable results for this data.")
-
   if(model == "poisson" & missing(mean.PriorDist))
     warning("Model is Poisson and the prior mean is unknown. This program can not yet give reliable results for this data. If the Poisson is being used as an approximation to the Binomial and the exposures are known then please assume a Binomial model")
   

### 2013-11-15 Rgbp/R/pr.R

@@ -2,7 +2,7 @@ PRInitialValue2ndLevelMeanKnown <- function(given) {
   # This function makes the initial values needed to run PRIMM.
   # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
  
-  if (all(given$sample.mean) == mean(given$sample.mean)) {
+  if (all(given$sample.mean == mean(given$sample.mean))) {
     r.ini <- given$prior.mean / (var(given$sample.mean) + 1)
   } else {
     r.ini <- given$prior.mean / var(given$sample.mean)
@@ -43,7 +43,7 @@ PRInitialValue2ndLevelMeanUnknown <- function(given) {
 
   mu0.ini <- mean(exp(x %*% b.ini))
 
-  if (all(y) == mean(y)) {
+  if (all(y == mean(y))) {
     r.ini <- mu0.ini / (var(y) + 1)
   } else {
     r.ini <- mu0.ini / var(y)
@@ -61,27 +61,28 @@ PRAlphaEst2ndLevelMeanKnown <- function(given, ini) {
   k <- length(n)
   a.ini <- ini$a.ini
 
-  PRLogLikKn <- function (a) { 
-    zam <- z + exp(-a) * mu0
-    am <- exp(-a) * mu0
-    if (any(c(am, zam) <= 0)) {
-      print("The components of lgamma should be positive")
-      stop()
-    } else {
-      sum(dnbinom(z, size = am, prob = exp(-a) / (exp(-a) + n), log = T))
-    }
+  PRDerivAlpha <- function(a) {
+    zam <- z + exp(-a) * mu0
+    am <- exp(-a) * mu0
+    const1 <- ((digamma(zam) -  digamma(am) + n / (exp(-a) + n) - log(1 + n * exp(a))) * mu0
+               - z / (exp(-a) + n))
+    const3 <- (const1 + z * exp(-a) / (exp(-a) + n)^2 + mu0 * n / (n + exp(-a))
+               - n * am / (exp(-a) + n)^2 + am * mu0 * (trigamma(zam) - trigamma(am)))
+    out <- c(1 - exp(-a) * sum(const1), exp(-a) * sum(const3))
+    out
+  }
+
+  dif <- 1
+  eps <- 0.0001
+  while (abs(dif) > eps) {
+    out1 <- PRDerivAlpha(a.ini)
+    score <- out1[1]
+    hessian <- out1[2]
[…]

### 2013-11-15 Rgbp/R/pr.R
coding2

@@ -53,8 +53,6 @@ PRInitialValue2ndLevelMeanUnknown <- function(given) {
 }
 
 PRAlphaEst2ndLevelMeanKnown <- function(given, ini) {
-  # Alpha estimation of PRIMM when the descriptive second level mean is known
-
   z <- given$z
   n <- given$n
   mu0 <- given$prior.mean
@@ -67,10 +65,10 @@ PRAlphaEst2ndLevelMeanKnown <- function(given, ini) {
     const1 <- ((digamma(zam) -  digamma(am) + n / (exp(-a) + n) - log(1 + n * exp(a))) * mu0
                - z / (exp(-a) + n))
     const3 <- (const1 + z * exp(-a) / (exp(-a) + n)^2 + mu0 * n / (n + exp(-a))
-               - n * am / (exp(-a) + n)^2 + am * mu0 * (trigamma(zam) - trigamma(am)))
+              - n * am / (exp(-a) + n)^2 + am * mu0 * (trigamma(zam) - trigamma(am)))
     out <- c(1 - exp(-a) * sum(const1), exp(-a) * sum(const3))
     out
-  }
+  }
 
   dif <- 1
   eps <- 0.0001

### 2013-11-15 Rgbp/R/pr.R
coding3

@@ -53,6 +53,7 @@ PRInitialValue2ndLevelMeanUnknown <- function(given) {
 }
 
 PRAlphaEst2ndLevelMeanKnown <- function(given, ini) {
+
   z <- given$z
   n <- given$n
   mu0 <- given$prior.mean

### 2013-11-15 Rgbp/R/pr.R
coding4

@@ -51,7 +51,6 @@ PRInitialValue2ndLevelMeanUnknown <- function(given) {
 
   list(x = x, b.ini = b.ini, a.ini = -log(r.ini))
 }
-
 PRAlphaEst2ndLevelMeanKnown <- function(given, ini) {
 
   z <- given$z
@@ -60,28 +59,28 @@ PRAlphaEst2ndLevelMeanKnown <- function(given, ini) {
   k <- length(n)
   a.ini <- ini$a.ini
 
-  PRDerivAlpha <- function(a) {
-    zam <- z + exp(-a) * mu0
-    am <- exp(-a) * mu0
-    const1 <- ((digamma(zam) -  digamma(am) + n / (exp(-a) + n) - log(1 + n * exp(a))) * mu0
-               - z / (exp(-a) + n))
-    const3 <- (const1 + z * exp(-a) / (exp(-a) + n)^2 + mu0 * n / (n + exp(-a))
-              - n * am / (exp(-a) + n)^2 + am * mu0 * (trigamma(zam) - trigamma(am)))
-    out <- c(1 - exp(-a) * sum(const1), exp(-a) * sum(const3))
+  PRDerivAlpha <- function(a) {
+    zam <- z + exp(-a) * mu0
+    am <- exp(-a) * mu0
+    const1 <- ((digamma(zam) - digamma(am) + n / (exp(-a) + n) - log(1 + n * exp(a))) * mu0
+               - z / (exp(-a) + n))
+    const3 <- (const1 + z * exp(-a) / (exp(-a) + n)^2 + mu0 * n / (n + exp(-a))
+              - n * am / (exp(-a) + n)^2 + am * mu0 * (trigamma(zam) - trigamma(am)))
+    out <- c(1 - exp(-a) * sum(const1), exp(-a) * sum(const3))
     out
   }
 
-  dif <- 1
-  eps <- 0.0001
-  while (abs(dif) > eps) {
-    out1 <- PRDerivAlpha(a.ini)
-    score <- out1[1]
-    hessian <- out1[2]
-    dif <- score / hessian
-    a.ini <- a.ini - dif
+  dif <- 1
+  eps <- 0.0001
+  while (abs(dif) > eps) {
+    out1 <- PRDerivAlpha(a.ini)
+    score <- out1[1]
+    hessian <- out1[2]
+    dif <- score / hessian
+    a.ini <- a.ini - dif
   }
 
[…]

### 2013-11-15 Rgbp/R/br.R
code

@@ -4,13 +4,13 @@ BRInitialValue2ndLevelMeanKnown <- function(given) {
 
   if (given$prior.mean == 0) {
     if(all(given$sample.mean == mean(given$sample.mean))) {
-      r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / (var(given$sample.mean) + 1)
+      r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / (var(given$sample.mean) + 0.1)
     } else {
       r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / var(given$sample.mean)
     }
   } else {
     if(all(given$sample.mean == mean(given$sample.mean))) {
-      r.ini <- given$prior.mean * (1 - given$prior.mean) / (var(given$sample.mean) + 1)
+      r.ini <- given$prior.mean * (1 - given$prior.mean) / (var(given$sample.mean) + 0.1)
     } else {
       r.ini <- given$prior.mean * (1 - given$prior.mean) / var(given$sample.mean)
     }
@@ -51,7 +51,7 @@ BRInitialValue2ndLevelMeanUnknown <- function(given) {
   p0.ini <- mean(exp(x %*% b.ini) / (1 + exp(x %*% b.ini)))
 
   if(all(y == mean(y))) {
-    r.ini <- p0.ini * (1 - p0.ini) / (var(y) + 1)
+    r.ini <- p0.ini * (1 - p0.ini) / (var(y) + 0.1)
   } else {
     r.ini <- p0.ini * (1 - p0.ini) / var(y)
   }
@@ -134,6 +134,8 @@ BRAlphaBetaEst2ndLevelMeanUnknown <- function(given, ini) {
     nzaq <- n - z + exp(-a) * q
     ap <- exp(-a) * p 
     aq <- exp(-a) * q
+    vec <- rep(NA, k)
+    diagm <- rep(NA, k)
     if (any(c(ap, aq, zap, nzaq) == 0)) {
       vec[(ap == 0 | aq == 0 | zap == 0 | nzaq == 0)] <- 0
       tmp <- !(ap == 0 | aq == 0 | zap == 0 | nzaq == 0)
@@ -143,19 +145,19 @@ BRAlphaBetaEst2ndLevelMeanUnknown <- function(given, ini) {
[…]

### 2013-11-20 jss/article.tex
code
edits

@@
   E-mail: \email{kelly2@fas.harvard.edu}\\
-  URL: \url{http://www.people.fas.harvard.edu/~kelly2/}\\
 
@@
 The notation $x_{j}'=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $m\times 1$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
-It is assumed that the second-level variance $A$ is unknown and that $\mathbf{\beta}_{(m\times1)}$ is also unknown unless specified otherwise.
+It is assumed that the second-level variance $A$ is unknown and that $\mathbf{\beta}_{(m\times1)}$ is also unknown unless otherwise specified.
 Note that if there are no covariates then $x_{j}=1$, ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
@@
 \end{equation}
-where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkages.
+where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkage factors.
 By integrating over $\mu_{j}$ for $j = 1 \ldots k$ a marginal distribution, useful for model checking (Section \ref{discussion}), can be derived
@@
 \subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}\label{poissonsubsec}
-\code{gbp} is also able to build a Poisson-Gamma hierarchical model, though its usage is limited to the case where the second-level mean is known ($m=0$).
+\code{gbp} is also capable of estimating a Poisson-Gamma hierarchical model, though its usage is limited to the case where the second-level mean is known ($m=0$).
 For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$ for the $j$-th group, where  $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials.
-For this Poisson model $n_{j}$ can be interpreted as the exposure of the $j$-th group,  not necessarily an interger.
+For this Poisson model $n_{j}$ can be interpreted as the exposure of the $j$-th group,  not necessarily an integer.
 The notation $r$ represents the amount of prior information as $n_{j}$ does the amount of observed information.
@@
 \begin{CodeInput}
-R> data(hospitals)
-R> z <- hospitals$d # variable name for the number of deaths is d in dataset
-R> n <- hospitals$n
+R> data(hospital)
+R> z <- hospital$d # variable name for the number of deaths is d in dataset
+R> n <- hospital$n
 \end{CodeInput}
@@
 In addition, suppose one knows that the state-level death rate per exposure of this surgery is 0.030 ($\lambda_{0}$).
-Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the true death rate ($\lambda_{j}$) for each hospital so that one can evaluate the hospital reliabilities.
+Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the true death rate ($\lambda_{j}$) so that one can evaluate each hospital's reliability.
 
@@
 
-\subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate} \label{sec:ex:8schools}
+\subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean with No Covariates} \label{sec:ex:8schools}
 
@@
 
-Due to it's speed and ease of use, \pkg{Rgbp} can be used for as a method of preliminary data analysis.
+Due to its speed and ease of use, \pkg{Rgbp} can be used for as a method of preliminary data analysis.
 Such results may tell statisticians and practitioners alike whether a more intensive method in terms of implementation and computational time, such as MCMC, is needed.

### 2013-11-22 jss/article.tex
coverage default changed to 100. Article edits

@@
 
-%%uncomment line below for double-spacing
-%\linespread{2}
-%\setlength{\parskip}{1.5cm}%
-%\setlength\parindent{24pt}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$ for the $j$-th group, where  $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials.
-For this Poisson model $n_{j}$ can be interpreted as the exposure of the $j$-th group,  not necessarily an integer.
-The notation $r$ represents the amount of prior information as $n_{j}$ does the amount of observed information.
+For this Poisson model $n_{j}$ can be interpreted as the exposure of the $j$-th group and is not necessarily an integer.
+The notation $r$ represents the amount of prior information and $n_{j}$ represents the amount of observed information.
 Note that the constant, $1/r$, multiplied to the Gamma distribution below is a scaling factor and the square brackets indicates the [mean, variance] of a distribution.
@@
 
-where $\lambda_{0}$, the second-level mean, is known a priori and $r$ is the only unknown hyper-parameter. The posterior distribution of this Poisson-Gamma model given this hyper-parameter $r$ is
+where $\lambda_{0}$, the second-level mean, is known a priori and $r$ is the only unknown hyper-parameter. The posterior distribution of this Poisson-Gamma model given the hyper-parameter $r$ is
 \begin{equation} \label{gammapost}
@@
 
-Note that the variance in (\ref{gammaprior}) is linear in the mean, whereas a slightly different Poisson-Gamma specification \citep{1997} has been used elsewhere e.g.
-that makes the variances in (\ref{gammaprior}) and (\ref{gammapost}) quadratic functions of the mean respectively.
+Note that the variance in (\ref{gammaprior}) is linear in the mean, whereas a slightly different Poisson-Gamma specification has been used elsewhere \citep{1997} that makes the variances in (\ref{gammaprior}) and (\ref{gammapost}) quadratic functions of the mean respectively .
 
 \subsection[Binomial-Beta]{Binomial-Beta (``b''=Binomial data)}
-Binomial-Beta hierarchical model is the last model that \code{gbp} can fit.
-Again, $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials of the $j$-th group and the square bracket [, ] below indicates [mean, variance] of a distribution.
+The Binomial-Beta hierarchical model is the last model that \code{gbp} can fit.
+Again, $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials of the $j$-th group and the square bracket [, ] below indicates the [mean, variance] of a distribution.
 Unlike the Poisson-Gamma model, the second-level mean is either known ($m=0$) or unknown ($m\ge1$) a priori.
@@
 where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$, and $\beta_{(m\times1)}$ and $r$ are unknown hyper-parameters.
-Then corresponding posterior distribution given  $\beta_{(m\times1)}$ and $r$ is
+Then the corresponding posterior distribution given  $\beta_{(m\times1)}$ and $r$ is
 \begin{equation} \label{betapost}
@@
 A hyper-prior distribution is a distribution assigned to the second-level parameters.
-With the goal of objectivity in mind our choice for hyper-priors with \code{gbp} assumes the following non-informative hyper-prior distributions:
+With the goal of objectivity in mind our choice for hyper-priors assumes the following non-informative distributions:
 \begin{equation}
@@
 where $m$ is the number of regression coefficients.
-As for $\beta$, the flat non-informative distribution above is a common choice.
+As for $\beta$, the flat non-informative distribution above is a common choice to ensure good frequency properties.
 In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of random effects $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
@@
 It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
-A common approach to approximate the distribution of $B_{j}$ is to find its MLE $\hat{B}_{j}(\hat{A}_{MLE})$ (or  $\hat{B}_{j}(\hat{r}_{MLE})$) and to use its asymptotic Normality.
-But its asymptotic Gaussian distribution is defined on $(-\infty, \infty)$ whereas $B_{j}$ is bounded between 0 and 1, and MLE can result in estimates lying on the boundary of the parameter space.
+A common approach to approximate the distribution of $B_{j}$ is to find its MLE $B_{j}(\hat{A}_{MLE})$ (or  $B_{j}(\hat{r}_{MLE})$) and to use its asymptotic Normality.
+This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $0 < B_{j} < 1$ and hence in small sample sizes this approximation can be quite flawed and can even result in point estimates lying on the boundary of the parameter space.
 
@@
 
-Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of true parameters given only the data ($\textbf{y}$).
+Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of the random effects given only the data ($\textbf{y}$).
 Taking the Normal-Normal model as an example, it estimates $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by the following identities
@@
 where both $E(\mu_{j}\vert \textbf{y}, \beta, A)$ and $Var(\mu_{j}\vert \textbf{y}, \beta, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}).
-We then estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by plugging-in approximately estimated two posterior moments of shrinkage factors.
+We then estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by plugging-in the approximately estimated two posterior moments of shrinkage factors.
 
@@
 
-There are two kinds of model justification processes; one is a model checking and the other is a method checking.
+There are two kinds of model justification processes; one is model checking and the other is method checking.
 The model checking is for the justification of the hierarchical model on a specific dataset.
-One possible question is, ``Can this dataset benefit from such a hierarchical modeling?'' \cite{modelchecking1996} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
+One possible question is, ``Can this dataset benefit from such hierarchical modeling?'' \cite{modelchecking1996} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
 They found that their data had more variation than expected of the first-level Poisson distribution and two-level Poisson hierarchical model could successfully account for such additional variation.
 
-Once we make sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this hierarchical modeling.
-``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating pseudo-datasets and estimating coverage probabilities.
+Once we make sure that the hierarchical model is appropriate for our data, the following question will be about the validity of the interval estimates, ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating pseudo-datasets and estimating coverage probabilities.
 
-From now on, the explanation will be based on Normal-Normal model because the idea can be easily applied to the other two models.
+From now on, the explanation will be based on the Normal-Normal model because the idea can be easily applied to the other two models.
 
@@
 So, once we fix these hyper-parameters at specific values, we can generate as many parameters as we want.
-Suppose we generated 500 $(=N_{sim}$) {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (\ref{normalprior}), where values of $A$ and $\beta$ are specifically given and the superscript $(i)$ indicates the $i$-th simulation.
-Then using the distribution of observed data in (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.
+Suppose we generated an $N_{sim}$ (default: $N_{sim} = 100$) number of {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$ from the prior distribution in (\ref{normalprior}), where values of $A$ and $\beta$ are specifically given and the superscript $(i)$ indicates the $i$-th simulation.
+Then using the distribution of observed data in (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.
 Note that we generate one dataset per one parameter set.
@@
 \subsection{Coverage Estimation Process}
-Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 pseudo-datasets in order to obtain 500$\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, 500$\}.
+Next, \code{coverage} fits the Normal-Normal model an $N_{sim}$ number of times using the $N_{sim}$ pseudo-datasets in order to obtain $N_{sim}$ $\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, N_{sim}$\}.
 Here, we introduce both simple and Rao-Blackwellized unbiased coverage estimators but the function \code{coverage} in \pkg{Rgbp} displays only the Rao-Blackwellized one.
@@
 This provides $k$ simple unbiased coverage estimates.
-For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given specific values of $A$ and $\beta$.
+For example, $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, N_{sim},$ given specific values of $A$ and $\beta$.
 
@@
 \subsubsection{Rao-Blackwellized Unbiased Coverage Estimates}
-Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (sufficient statistic) into account.
+Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (the sufficient statistic) into account.
 Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset.
@@
 
-For example, we estimate the first group's true coverage probability $p_{cov, 1}$ (that depend on specific values of $A$ and $\beta$) by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$.
+For example, we estimate the first group's true coverage probability $p_{cov, 1}$ (which depends on specific values of $A$ and $\beta$) by $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{1}$.
 
@@
 In this example we adopt the perspective of a person living in the state of New York (NY) who has been suffering from severe coronary heart disease.
-If this person must receive coronary artery bypass graft (CABG) surgery soon, he or she might want to find the most reliable hospital for that.
+If this person must receive coronary artery bypass graft (CABG) surgery soon, he or she might want to find the most reliable hospital for such a procedure.
 
-For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($\textbf{z}_{(31\times1)}$) for a specified period after CABG surgeries and total number of patients ($\textbf{n}_{(31\times1)}$) receiving CABG surgeries in each hospital.
-For reference, caseloads ($n_{j}$) can be interpreted as exposures, not necessarily integers.
-These data can be loaded into R using the following code.
-Note that throughout this paper, the symbol `\code{R>}' represents a command prompt (not to be typed into \proglang{R}).
+For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($\textbf{z}_{(31\times1)}$) for a specified period after CABG surgeries and the total number of patients ($\textbf{n}_{(31\times1)}$) receiving CABG surgeries in each hospital.
+For reference, caseloads ($n_{j}$) can be interpreted as exposures.
+These data can be loaded into R using the following code where the symbol `\code{R>}' represents a command prompt and is not to be typed into \proglang{R}.
 
@@
 
-But the point estimates are not enough to evaluate hospital reliabilities because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other.
+But the point estimates are not enough to evaluate hospital reliability because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other.
 In the second plot of Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed.
@@
 Let's see the details of these two hospitals.
-The observed death rates for these two hopitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
+The observed death rates for these two hospitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
 The 31st hospital has twice the caseload, which leads to borrowing less information from the NY state-level hierarchy (or shrinking less toward the state-level mean, 0.030) with smaller variance.

### 2013-11-22 Rgbp/R/coverage.R

@@ -1,5 +1,5 @@
 
-coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 10) {
+coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 100) {
 
   # Rao-Blackwellized criterion
   coverageRB <- matrix(NA, nrow = length(gbp.object$se), ncol = nsim)

### 2013-11-22 jss/article.tex
last edits. just need to change process.png

@@
 Note that some hospitals' ranks have changed by shrinking much harder towards 0.030 than others.
-For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly the safest hospital among 31 hospitals in terms of the observed death rate is not actually safer than seemingly the second safest hospital.
+For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly the safest hospital among 31 hospitals in terms of the observed death rate is not the safest in terms of the estimated posterior means.
 
@@
 \pkg{Rgbp} accounts for this caseload difference, making the death rate estimate for the former hospital shrink toward the state-level mean ($\lambda_{0}$=0.030) much harder than that for the latter hospital.
-This is what happened to the two left-most hospitals in the first plot.
 
-But the point estimates are not enough to evaluate hospital reliability because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other.
+Note that the point estimates are not enough to evaluate hospital reliability because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other.
 In the second plot of Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed.
@@
 
-This 95\% interval plot reveals that the 31st hospital has the lowest upper bound of 95\% interval estimate, although its point estimate ($\hat{\lambda}_{31}=0.0235$) is slightly bigger than that of the 23rd hospital ($\hat{\lambda}_{23}=0.0230$).
-Let's see the details of these two hospitals.
+This 95\% interval plot reveals that the 31st hospital has the lowest upper bound even though its point estimate ($\hat{\lambda}_{31}=0.0235$) is slightly bigger than that of the 23rd hospital ($\hat{\lambda}_{23}=0.0230$).
 The observed death rates for these two hospitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
@@
 
-But when fitting a model it is always a good idea to question how reliable the estimation procedure is.
+When fitting a model it is always a good idea to question how reliable the estimation procedure is.
 For example, does our procedure generate interval estimates that have good repeated sampling properties?
@@
 
-Also, \code{gbp} provides interval estimates with different confidence levels, for example 90\%.
+In addition, \code{gbp} also provides interval estimates with different confidence levels, for example 90\%.
 For this, we need to go back to the code for fitting the model, adding another argument, \code{Alpha = 0.9}; \code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.03, model = "poisson")}.
@@
 In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level and the smooth red curve connects Rao-Blackwellized (RB) unbiased coverage estimates for 31 hospitals.
-
 The overall RB unbiased coverage estimate across all the hospitals is 0.954.
@@
 
-The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching.
+The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (groups) to test whether students (units) SAT scores are effected by coaching.
 The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \citep{1981}.
@@
 
-Due to its speed and ease of use, \pkg{Rgbp} can be used for as a method of preliminary data analysis.
+Due to its speed and ease of use, \pkg{Rgbp} can be used as a method of preliminary data analysis.
 Such results may tell statisticians and practitioners alike whether a more intensive method in terms of implementation and computational time, such as MCMC, is needed.

### 2013-11-22 jss/article.tex
just process.png to go!

@@
 \begin{equation}
+  \label{eq:hyper}
 \beta \sim \textrm{Uniform on}~ \mathbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
@@
 
-The Poisson model can have such posterior propriety if there are two groups whose observed values exceed 0 and the second-level mean ($\lambda_0$) is known.
-If $\lambda_0$ is unknown, the posterior distribution for the Poisson model is improper and this model should not be used.
-In the case where the Poisson model is as an approximation to the Binomial and the exposures, $n_j$, are known then the Binomial model should be used as an alternative to the Poisson.
+The Poisson model with hyper-prior in (\ref{eq:hyper}) provides posterior propriety if there are two groups whose observed values exceed 0 and the second-level mean ($\lambda_0$) is known ($m=0$).
+However, if $\lambda_0$ is unknown $(m \geq 1)$ the posterior distribution for the Poisson model is improper with hyper-prior in (\ref{eq:hyper}) and this model should not be used.
+In cases where the Poisson model is used because it is an approximation to the Binomial, then we recommend staying with the Binomial model with the same hyper-prior distribution.
 The efficiency of these priors is explored in the examples in section 5.

### 2013-11-22 jss/article.tex
plot

--- 2013-11-22 jss/article.tex
@@
 
+%%uncomment line below for double-spacing
+%\linespread{2}
+%\setlength{\parskip}{1.5cm}%
+%\setlength\parindent{24pt}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   E-mail: \email{kelly2@fas.harvard.edu}\\
+  URL: \url{http://www.people.fas.harvard.edu/~kelly2/}\\
 
@@
 The notation $x_{j}'=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $m\times 1$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
-It is assumed that the second-level variance $A$ is unknown and that $\mathbf{\beta}_{(m\times1)}$ is also unknown unless otherwise specified.
+It is assumed that the second-level variance $A$ is unknown and that $\mathbf{\beta}_{(m\times1)}$ is also unknown unless specified otherwise.
 Note that if there are no covariates then $x_{j}=1$, ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
@@
 \end{equation}
-where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkage factors.
+where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkages.
 By integrating over $\mu_{j}$ for $j = 1 \ldots k$ a marginal distribution, useful for model checking (Section \ref{discussion}), can be derived
@@
 \subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}\label{poissonsubsec}
-\code{gbp} is also capable of estimating a Poisson-Gamma hierarchical model, though its usage is limited to the case where the second-level mean is known ($m=0$).
+\code{gbp} is also able to build a Poisson-Gamma hierarchical model, though its usage is limited to the case where the second-level mean is known ($m=0$).
 For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$ for the $j$-th group, where  $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials.
-For this Poisson model $n_{j}$ can be interpreted as the exposure of the $j$-th group and is not necessarily an integer.
-The notation $r$ represents the amount of prior information and $n_{j}$ represents the amount of observed information.
+For this Poisson model $n_{j}$ can be interpreted as the exposure of the $j$-th group,  not necessarily an interger.
+The notation $r$ represents the amount of prior information as $n_{j}$ does the amount of observed information.
 Note that the constant, $1/r$, multiplied to the Gamma distribution below is a scaling factor and the square brackets indicates the [mean, variance] of a distribution.
@@
 
-where $\lambda_{0}$, the second-level mean, is known a priori and $r$ is the only unknown hyper-parameter. The posterior distribution of this Poisson-Gamma model given the hyper-parameter $r$ is
+where $\lambda_{0}$, the second-level mean, is known a priori and $r$ is the only unknown hyper-parameter. The posterior distribution of this Poisson-Gamma model given this hyper-parameter $r$ is
 \begin{equation} \label{gammapost}
@@
 
-Note that the variance in (\ref{gammaprior}) is linear in the mean, whereas a slightly different Poisson-Gamma specification has been used elsewhere \citep{1997} that makes the variances in (\ref{gammaprior}) and (\ref{gammapost}) quadratic functions of the mean respectively .
+Note that the variance in (\ref{gammaprior}) is linear in the mean, whereas a slightly different Poisson-Gamma specification \citep{1997} has been used elsewhere e.g.
+that makes the variances in (\ref{gammaprior}) and (\ref{gammapost}) quadratic functions of the mean respectively.
 
 \subsection[Binomial-Beta]{Binomial-Beta (``b''=Binomial data)}
-The Binomial-Beta hierarchical model is the last model that \code{gbp} can fit.
-Again, $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials of the $j$-th group and the square bracket [, ] below indicates the [mean, variance] of a distribution.
+Binomial-Beta hierarchical model is the last model that \code{gbp} can fit.
+Again, $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials of the $j$-th group and the square bracket [, ] below indicates [mean, variance] of a distribution.
 Unlike the Poisson-Gamma model, the second-level mean is either known ($m=0$) or unknown ($m\ge1$) a priori.
@@
 where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$, and $\beta_{(m\times1)}$ and $r$ are unknown hyper-parameters.
-Then the corresponding posterior distribution given  $\beta_{(m\times1)}$ and $r$ is
+Then corresponding posterior distribution given  $\beta_{(m\times1)}$ and $r$ is
 \begin{equation} \label{betapost}
@@
 A hyper-prior distribution is a distribution assigned to the second-level parameters.
-With the goal of objectivity in mind our choice for hyper-priors assumes the following non-informative distributions:
+With the goal of objectivity in mind our choice for hyper-priors with \code{gbp} assumes the following non-informative hyper-prior distributions:
 \begin{equation}
@@
 where $m$ is the number of regression coefficients.
-As for $\beta$, the flat non-informative distribution above is a common choice to ensure good frequency properties.
+As for $\beta$, the flat non-informative distribution above is a common choice.
 In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of random effects $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
@@
 It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
-A common approach to approximate the distribution of $B_{j}$ is to find its MLE $B_{j}(\hat{A}_{MLE})$ (or  $B_{j}(\hat{r}_{MLE})$) and to use its asymptotic Normality.
-This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $0 < B_{j} < 1$ and hence in small sample sizes this approximation can be quite flawed and can even result in point estimates lying on the boundary of the parameter space.
+A common approach to approximate the distribution of $B_{j}$ is to find its MLE $\hat{B}_{j}(\hat{A}_{MLE})$ (or  $\hat{B}_{j}(\hat{r}_{MLE})$) and to use its asymptotic Normality.
+But its asymptotic Gaussian distribution is defined on $(-\infty, \infty)$ whereas $B_{j}$ is bounded between 0 and 1, and MLE can result in estimates lying on the boundary of the parameter space.
 
@@
 
-Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of the random effects given only the data ($\textbf{y}$).
+Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of true parameters given only the data ($\textbf{y}$).
 Taking the Normal-Normal model as an example, it estimates $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by the following identities
@@
 where both $E(\mu_{j}\vert \textbf{y}, \beta, A)$ and $Var(\mu_{j}\vert \textbf{y}, \beta, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}).
-We then estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by plugging-in the approximately estimated two posterior moments of shrinkage factors.
+We then estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by plugging-in approximately estimated two posterior moments of shrinkage factors.
 
@@
 
-There are two kinds of model justification processes; one is model checking and the other is method checking.
+There are two kinds of model justification processes; one is a model checking and the other is a method checking.
 The model checking is for the justification of the hierarchical model on a specific dataset.
-One possible question is, ``Can this dataset benefit from such hierarchical modeling?'' \cite{modelchecking1996} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
+One possible question is, ``Can this dataset benefit from such a hierarchical modeling?'' \cite{modelchecking1996} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
 They found that their data had more variation than expected of the first-level Poisson distribution and two-level Poisson hierarchical model could successfully account for such additional variation.
 
-Once we make sure that the hierarchical model is appropriate for our data, the following question will be about the validity of the interval estimates, ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating pseudo-datasets and estimating coverage probabilities.
+Once we make sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this hierarchical modeling.
+``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating pseudo-datasets and estimating coverage probabilities.
 
-From now on, the explanation will be based on the Normal-Normal model because the idea can be easily applied to the other two models.
+From now on, the explanation will be based on Normal-Normal model because the idea can be easily applied to the other two models.
 
@@
 So, once we fix these hyper-parameters at specific values, we can generate as many parameters as we want.
-Suppose we generated an $N_{sim}$ (default: $N_{sim} = 100$) number of {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$ from the prior distribution in (\ref{normalprior}), where values of $A$ and $\beta$ are specifically given and the superscript $(i)$ indicates the $i$-th simulation.
-Then using the distribution of observed data in (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.
+Suppose we generated 500 $(=N_{sim}$) {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (\ref{normalprior}), where values of $A$ and $\beta$ are specifically given and the superscript $(i)$ indicates the $i$-th simulation.
+Then using the distribution of observed data in (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.
 Note that we generate one dataset per one parameter set.
@@
 \begin{center}
-\includegraphics[width=6cm]{process.png}
+\includegraphics[width=7cm]{process.png}
 \caption{Pseudo-data generating process}
@@
 \subsection{Coverage Estimation Process}
-Next, \code{coverage} fits the Normal-Normal model an $N_{sim}$ number of times using the $N_{sim}$ pseudo-datasets in order to obtain $N_{sim}$ $\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, N_{sim}$\}.
+Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 pseudo-datasets in order to obtain 500$\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, 500$\}.
 Here, we introduce both simple and Rao-Blackwellized unbiased coverage estimators but the function \code{coverage} in \pkg{Rgbp} displays only the Rao-Blackwellized one.
@@
 This provides $k$ simple unbiased coverage estimates.
-For example, $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, N_{sim},$ given specific values of $A$ and $\beta$.
+For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given specific values of $A$ and $\beta$.
 
@@
 \subsubsection{Rao-Blackwellized Unbiased Coverage Estimates}
-Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (the sufficient statistic) into account.
+Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (sufficient statistic) into account.
 Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset.
@@
 
-For example, we estimate the first group's true coverage probability $p_{cov, 1}$ (which depends on specific values of $A$ and $\beta$) by $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{1}$.
+For example, we estimate the first group's true coverage probability $p_{cov, 1}$ (that depend on specific values of $A$ and $\beta$) by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$.
 
@@
 In this example we adopt the perspective of a person living in the state of New York (NY) who has been suffering from severe coronary heart disease.
-If this person must receive coronary artery bypass graft (CABG) surgery soon, he or she might want to find the most reliable hospital for such a procedure.
+If this person must receive coronary artery bypass graft (CABG) surgery soon, he or she might want to find the most reliable hospital for that.
 
-For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($\textbf{z}_{(31\times1)}$) for a specified period after CABG surgeries and the total number of patients ($\textbf{n}_{(31\times1)}$) receiving CABG surgeries in each hospital.
-For reference, caseloads ($n_{j}$) can be interpreted as exposures.
-These data can be loaded into R using the following code where the symbol `\code{R>}' represents a command prompt and is not to be typed into \proglang{R}.
+For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($\textbf{z}_{(31\times1)}$) for a specified period after CABG surgeries and total number of patients ($\textbf{n}_{(31\times1)}$) receiving CABG surgeries in each hospital.
+For reference, caseloads ($n_{j}$) can be interpreted as exposures, not necessarily integers.
+These data can be loaded into R using the following code.
+Note that throughout this paper, the symbol `\code{R>}' represents a command prompt (not to be typed into \proglang{R}).
 
@@
 In addition, suppose one knows that the state-level death rate per exposure of this surgery is 0.030 ($\lambda_{0}$).
-Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the true death rate ($\lambda_{j}$) so that one can evaluate each hospital's reliability.
+Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the true death rate ($\lambda_{j}$) for each hospital so that one can evaluate the hospital reliabilities.
 
@@
 
-But the point estimates are not enough to evaluate hospital reliability because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other.
+But the point estimates are not enough to evaluate hospital reliabilities because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other.
 In the second plot of Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed.
@@
 Let's see the details of these two hospitals.
-The observed death rates for these two hospitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
+The observed death rates for these two hopitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
 The 31st hospital has twice the caseload, which leads to borrowing less information from the NY state-level hierarchy (or shrinking less toward the state-level mean, 0.030) with smaller variance.
@@
 
-\subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean with No Covariates} \label{sec:ex:8schools}
+\subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate} \label{sec:ex:8schools}
 
@@
 
-Due to its speed and ease of use, \pkg{Rgbp} can be used for as a method of preliminary data analysis.
+Due to it's speed and ease of use, \pkg{Rgbp} can be used for as a method of preliminary data analysis.
 Such results may tell statisticians and practitioners alike whether a more intensive method in terms of implementation and computational time, such as MCMC, is needed.

### 2014-01-28 qinstall.R
nothing

@@ -1,3 +1,3 @@
 #!/usr/bin/R
-install.packages("Rgbp_1.0.3.tar.gz",repos=NULL,type="source")
+install.packages("Rgbp_1.0.4.tar.gz",repos=NULL,type="source")
 library(Rgbp)

### 2014-01-28 jss/article.tex
data() fix
replication script

--- 2013-11-22 jss/article.tex
@@
 
-\section[introduction]{Introduction}
+\section[Introduction]{Introduction}
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
@@
 Note that if there are no covariates then $x_{j}=1$, ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
-For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean.
+For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, i.e., a prior mean.
 Based on this conjugate prior distribution it is easy to derive the corresponding posterior distribution
@@
 \subsection[ADM]{Approximation via Adjustment for Density Maximization}\label{ADM}
-It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
+It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, i.e., $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
 A common approach to approximate the distribution of $B_{j}$ is to find its MLE $B_{j}(\hat{A}_{MLE})$ (or  $B_{j}(\hat{r}_{MLE})$) and to use its asymptotic Normality.
@@
 To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of adjustment for density maximization (ADM) \citep{carl1988, 1997, 2011}.
-For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, \emph{i.e.}  of $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$, where the notation $\textbf{y}$ represents observed data, without the boundary issues that MLE encounters.
+For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, i.e.,  of $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$, where the notation $\textbf{y}$ represents observed data, without the boundary issues that MLE encounters.
 See \cite{2011}.
@@
 So, once we fix these hyper-parameters at specific values, we can generate as many parameters as we want.
-Suppose we generated an $N_{sim}$ (default: $N_{sim} = 100$) number of {\boldmath $\mu$}$_{(k\times1)}$'s, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$ from the prior distribution in (\ref{normalprior}), where values of $A$ and $\beta$ are specifically given and the superscript $(i)$ indicates the $i$-th simulation.
+Suppose we generated an $N_{sim}$ (default: $N_{sim} = 100$) number of {\boldmath $\mu$}$_{(k\times1)}$'s, (i.e., \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$), from the prior distribution in (\ref{normalprior}), where values of $A$ and $\beta$ are specifically given and the superscript $(i)$ indicates the $i$-th simulation.
 Then using the distribution of observed data in (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.
@@
 \begin{CodeInput}
-R> data(hospital)
+R> data("hospital")
 R> z <- hospital$d # variable name for the number of deaths is d in dataset
@@
 
-The independent Poisson distribution, \emph{i.e.},  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be an ideal choice to describe these data based on the Poisson approximation when $\lambda$ is small and $n$ is relatively large.
+The independent Poisson distribution, i.e.,  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be an ideal choice to describe these data based on the Poisson approximation when $\lambda$ is small and $n$ is relatively large.
 
@@
 This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree (sample sizes) of prior and observed information respectively.
-If the second level has more information than the first level, \emph{i.e.} ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the estimator will shrink towards the prior mean more than 50\%.
+If the second level has more information than the first level, i.e., ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the estimator will shrink towards the prior mean more than 50\%.
 This is clear because, as caseload increases, shrinkage decreases, depending less on the NY state-level (second-level) information.
@@
 \begin{CodeInput}
-R> data(schools)
+R> data("schools")
 R> y  <- schools$y
@@
 
-Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known.
+Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, i.e., standard error of each school is assumed to be known.
 At the second hierarchy, the mean for each school is assumed to be drawn from a common Normal distribution and hence, we can use the Gaussian component of \code{gbp} to fit this Normal-Normal hierarchical model.
@@
 \begin{CodeInput}
-R> data(baseball)
+R> data("baseball")
 R> z <- baseball$Hits

### 2014-01-28 jss/replication.R

@@ -1,0 +1,69 @@
+################################################################################
+###  Load Package
+################################################################################
+library("Rgbp")
+
+
+################################################################################
+###  5.1. 31 Hospitals: Known Second-level mean
+################################################################################
+z <- c( 3,   2,   5,  11,   9,  12,  12,   4,  10,  13,  14,   7,  12,
+          11,  13,  22,  15,  11,  14,  11,  16,  14,   9,  15,  13,  35,
+          26,  25,  20,  35,  27)
+n <- c(67,  68, 210, 256, 269, 274, 278, 295, 347, 349, 358, 396, 431,
+         441, 477, 484, 494, 501, 505, 540, 563, 593, 602, 629, 636, 729,
+         849, 914, 940, 1193, 1340)
+## or 
+data("hospital")
+z <- hospital$d # variable name for the number of deaths is d in dataset
+n <- hospital$n
+
+p <- gbp(z, n, mean.PriorDist = 0.03, model = "poisson")
+p
+summary(p)
+plot(p)
+pcv <- coverage(p, nsim = 1000)
+pcv$coverageRB
+pcv$coverageS
+pcv$se.coverageRB
+pcv$se.coverageS
+
+
+################################################################################
+###  5.2. 8 Schools: Unknown Second-level Mean with No Covariates
+################################################################################
+y <- c(12, -3, 28, 7, 1, 8, 18, -1)
+se <- c(18, 16, 15, 11, 11, 10, 10, 9)
+## or
+data("schools")
+y <- schools$y
+se <- schools$se
+
+g <- gbp(y, se, model = "gaussian")
+g
+summary(g)
+plot(g)
+gcv <- coverage(g, nsim = 1000)
+gcv$coverageRB
+gcv$se.coverageRB
+
+
+################################################################################
+###  5.3. 18 Baseball Players: Unknown Second-level Mean and One Covariate
+################################################################################
+z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10, 9, 8, 7)
+n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
+x <- c( 1, 1, 1, 1, 1, 0, 0, 0, 0, 1, 0, 0, 0, 1, 1, 0, 0, 0)
+##or
[…]

### 2014-04-21 Rgbp/R/coverage.R
coverage plot

@@ -660,7 +660,7 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 100) {
   # plotting coverage graph
   par(xaxs = "r", yaxs = "r", mai = c(1, 0.6, 1, 0.3))
   n.units <- length(gbp.object$se)
-  plot(1 : length(gbp.object$se), result, ylim = c(0.6, 1), type = "l", col = 2, ylab = "",
+  plot(1 : length(gbp.object$se), result, ylim = c(0.6, 1), type = "b", col = 2, ylab = "",
        xlab = paste("Unit_j", ", ", "j = 1, ...,", n.units), 
        main = "Estimated Coverage Probability for Each Unit",
        lwd = 3, lty = 1)

### 2014-04-21 Rgbp/R/coverage.R
coverage plot2

@@ -658,10 +658,11 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 100) {
   effective.n <- nsim - sum(is.na(coverageS[1, ]))
 
   # plotting coverage graph
-  par(xaxs = "r", yaxs = "r", mai = c(1, 0.6, 1, 0.3))
+  par(xaxs = "r", yaxs = "r", mai = c(1, 0.9, 1, 0.3), las = 1)
   n.units <- length(gbp.object$se)
-  plot(1 : length(gbp.object$se), result, ylim = c(0.6, 1), type = "b", col = 2, ylab = "",
-       xlab = paste("Unit_j", ", ", "j = 1, ...,", n.units), 
+  plot(1 : length(gbp.object$se), result, ylim = c(0.6, 1), type = "b", col = 2,
+       ylab = "Coverage Estimates",
+       xlab = paste("Unit_ j", ", ", "j = 1, ...,", n.units), 
        main = "Estimated Coverage Probability for Each Unit",
        lwd = 3, lty = 1)
   abline(h = gbp.object$Alpha)
@@ -669,7 +670,7 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 100) {
   if (is.na(gbp.object$prior.mean) & missing(mean.PriorDist)) {
     if (gbp.object$model == "gr") {
       legend("bottomleft", c(paste("Model: Gaussian"), 
-                             "Red Line: RB coverage estimates",
+                             "Red Circles: RB coverage estimates",
                              paste("# of Simulations per Unit: ", effective.n),
                              paste("Given True A =", round(A, 2)), 
                              paste("Given True beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
@@ -677,7 +678,7 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 100) {
     } else {
       modelspec <- ifelse(gbp.object$model == "br", "Binomial", "Poisson")
       legend("bottomleft", c(paste("Model: ", modelspec), 
-                             "Red Line: RB coverage estimates",
+                             "Red Circles: RB coverage estimates",
                              paste("# of Simulations per Unit: ", effective.n),
                              paste("Given True r =", round(r, 2)), 
                              paste("Given True beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
[…]

### 2014-04-21 jss/article.tex
paper and graphs

@@
 \begin{CodeInput}
-R> data("hospital")
+R> data(hospital)
 R> z <- hospital$d # variable name for the number of deaths is d in dataset
@@
 \begin{center}
-\includegraphics[width = 6in]{hospital1.png}
+\includegraphics[width = 3.2in]{hospital1.png}
 \caption{Shrinkage plot and 95\% interval plot for 31 hospitals}
@@
 In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level and the smooth red curve connects Rao-Blackwellized (RB) unbiased coverage estimates for 31 hospitals.
-The overall RB unbiased coverage estimate across all the hospitals is 0.954.
+The overall RB unbiased coverage estimate across all the hospitals is 0.953.
 And none of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads ($n_{j}$).
@@
 \begin{CodeOutput}
- [1] 0.956 0.956 0.956 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 
-[13] 0.955 0.954 0.954 0.954 0.954 0.954 0.955 0.954 0.954 0.953 0.953 0.953
-[25] 0.954 0.954 0.954 0.953 0.953 0.953 0.952
+ [1] 0.955 0.954 0.955 0.954 0.954 0.954 0.954 0.954 0.954 0.954 0.954 0.954
+[13] 0.954 0.953 0.953 0.954 0.953 0.954 0.954 0.953 0.953 0.953 0.954 0.953
+[25] 0.953 0.953 0.952 0.953 0.952 0.952 0.952
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.947 0.952 0.963 0.961 0.957 0.957 0.959 0.952 0.957 0.957 0.941 0.958 
-[13] 0.954 0.962 0.935 0.940 0.955 0.952 0.951 0.941 0.955 0.952 0.954 0.946 
-[25] 0.942 0.952 0.958 0.945 0.938 0.958 0.948
+ [1] 0.949 0.960 0.958 0.958 0.950 0.945 0.960 0.953 0.960 0.956 0.955 0.946 
+[13] 0.955 0.954 0.960 0.965 0.955 0.952 0.960 0.956 0.959 0.955 0.964 0.960 
+[25] 0.945 0.942 0.947 0.960 0.940 0.946 0.956
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.0017 0.0017 0.0014 0.0014 0.0014 0.0014 0.0014 0.0014 0.0013 0.0013 0.0013 
-[12] 0.0013 0.0012 0.0012 0.0012 0.0012 0.0011 0.0012 0.0011 0.0011 0.0011 0.0011
-[23] 0.0010 0.0011 0.0010 0.0010 0.0009 0.0009 0.0009 0.0007 0.0007
+ [1] 0.0016 0.0016 0.0014 0.0014 0.0013 0.0013 0.0013 0.0013 0.0012 0.0013 0.0012 
+[12] 0.0012 0.0011 0.0011 0.00110.0011 0.0011 0.0011 0.0011 0.0011 0.0010 0.0010 
+[23] 0.0010 0.0010 0.0010 0.0009 0.0009 0.0008 0.0008 0.0007 0.0007
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.0071 0.0068 0.0060 0.0061 0.0064 0.0064 0.0063 0.0068 0.0064 0.0064 0.0075 
-[12] 0.0063 0.0066 0.0060 0.0078 0.0075 0.0066 0.0068 0.0068 0.0075 0.0066 0.0068 
-[23] 0.0066 0.0072 0.0074 0.0068 0.0063 0.0072 0.0076 0.0063 0.0070
+ [1] 0.0070 0.0062 0.0063 0.0063 0.0069 0.0072 0.0062 0.0067 0.0062 0.0065 0.0066
+[12] 0.0072 0.0066 0.0066 0.0062 0.0058 0.0066 0.0068 0.0062 0.0065 0.0063 0.0066 
+[23] 0.0059 0.0062 0.0072 0.0074 0.0071 0.0062 0.0075 0.0072 0.0065
 \end{CodeOutput}
@@
 
-Taking the first hospital as an example, the variance estimate of RB unbiased coverage estimate is about 17 times smaller than that of simple one.
+Taking the first hospital as an example, the variance estimate of RB unbiased coverage estimate is about 19 times smaller than that of simple one.
 It means that 1,000 RB unbiased coverage estimates are as precise as 17,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital, $p_{cov, 1}$.
@@
 \begin{CodeInput}
-R> data("schools")
+R> data(schools)
 R> y  <- schools$y
@@
 \begin{center}
-\includegraphics[width = 6in]{school1.png}
+\includegraphics[width = 3.2in]{school1.png}
 \caption{Shrinkage plot and 95\% interval plot for 8 schools}
@@
 \begin{CodeInput}
-R> data("baseball")
+R> data(baseball)
 R> z <- baseball$Hits
@@
 \begin{center}
-\includegraphics[width = 6in]{baseball1.png}
+\includegraphics[width = 3.2in]{baseball1.png}
 \caption{Shrinkage plot and 95\% interval plot for 18 baseball players}
@@
 \begin{CodeOutput}
- [1] 0.972 0.973 0.973 0.973 0.972 0.972 0.972 0.972 0.973 0.972 0.973 0.972 
-[13] 0.973 0.973 0.971 0.973 0.971 0.973
+ [1] 0.971 0.973 0.972 0.972 0.970 0.973 0.973 0.974 0.973 0.973 0.971 0.973 
+[13] 0.973 0.972 0.972 0.971 0.973 0.971
 \end{CodeOutput}
@@
 \begin{CodeOutput}
- [1] 0.0015 0.0011 0.0012 0.0011 0.0015 0.0012 0.0012 0.0010 0.0011 0.0012 
-[11] 0.0010 0.0012 0.0010 0.0011 0.0013 0.0011 0.0013 0.0010
+ [1] 0.0015 0.0012 0.0013 0.0014 0.0016 0.0010 0.0012 0.0010 0.0010 0.0013 
+[11] 0.0015 0.0013 0.0019 0.0013 0.0014 0.0015 0.0011 0.0014
 \end{CodeOutput}

### 2014-04-21 jss/article.tex
typo
any change

@@
 \begin{equation}\label{gammaprior}
-\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(r\lambda_{0})\sim \textrm{Gamma} \left[\lambda_{0}, ~\frac{\lambda_{0}}{r} \right],
+\lambda_{j}\vert r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(r\lambda_{0})\sim \textrm{Gamma} \left[\lambda_{0}, ~\frac{\lambda_{0}}{r} \right],
 \end{equation}
@@
 Figure \ref{fig:pseudo} will be helpful to understand this process.
-As we can see in (\ref{normalpost}), the distribution of each parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$.
+As we can see in (\ref{normalprior}), the distribution of each parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$.
 So, once we fix these hyper-parameters at specific values, we can generate as many parameters as we want.
@@
 \subsection{Coverage Estimation Process}
-Next, \code{coverage} fits the Normal-Normal model an $N_{sim}$ number of times using the $N_{sim}$ pseudo-datasets in order to obtain $N_{sim}$ $\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, N_{sim}$\}.
+Next, \code{coverage} fits the Normal-Normal model  $N_{sim}$ number of times using the $N_{sim}$ pseudo-datasets in order to obtain $N_{sim}$ $\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, N_{sim}$\}.
 Here, we introduce both simple and Rao-Blackwellized unbiased coverage estimators but the function \code{coverage} in \pkg{Rgbp} displays only the Rao-Blackwellized one.
@@
 Note that some hospitals' ranks have changed by shrinking much harder towards 0.030 than others.
-For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that seemingly the safest hospital among 31 hospitals in terms of the observed death rate is not the safest in terms of the estimated posterior means.
+For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that  the seemingly safest hospital among 31 hospitals in terms of the observed death rate is probably not the safest in terms of the estimated posterior means.
 
@@
 
-In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level and the smooth red curve connects Rao-Blackwellized (RB) unbiased coverage estimates for 31 hospitals.
+In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level and the red circles indicate Rao-Blackwellized (RB) unbiased coverage estimates for 31 hospitals.
 The overall RB unbiased coverage estimate across all the hospitals is 0.953.
@@
 Taking the first hospital as an example, the variance estimate of RB unbiased coverage estimate is about 19 times smaller than that of simple one.
-It means that 1,000 RB unbiased coverage estimates are as precise as 17,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital, $p_{cov, 1}$.
+It means that 1,000 RB unbiased coverage estimates are as precise as 19,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital, $p_{cov, 1}$.
 

### 2015-02-27 jss/article.tex
R and JSS style corrections

@@
              Carl Morris\\ Harvard University}
-\title{\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling}
+\title{\pkg{Rgbp}: An \proglang{R} Package for Gaussian, Poisson, and Binomial Hierarchical Modeling}
 
@@
 \Abstract{
-\pkg{Rgbp} is an R package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner.
+\pkg{Rgbp} is an \proglang{R} package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner.
 The main products of this package are point and interval estimates for each group's random effect, $\mu_{j}$ for Gaussian, $\lambda_{j}$ for Poisson, or $p_{j}$ for Binomial model, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.}
-\Keywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, R}
+\Keywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, \proglang{R}}
 \Plainkeywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, R} 
@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-\pkg{Rgbp} is an R package for estimating and validating a two-level model, also known as a conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} or a conditionally independent hierarchical model \citep{1989}, producing point and interval estimates of  random effects.
+\pkg{Rgbp} is an \proglang{R} package for estimating and validating a two-level model, also known as a conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} or a conditionally independent hierarchical model \citep{1989}, producing point and interval estimates of  random effects.
 The estimation procedure utilizes approximate Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking").
@@
 
-\section[Hierarchical Structure]{Hierarchical Structure} \label{hierarchical}
+\section[Hierarchical Structure]{Hierarchical structure} \label{hierarchical}
 A two-level or multilevel model is a powerful tool for exploring the hierarchical structure in data.
@@
 
-where $\mu_{0j} = x_{j}' \mathbf{\beta}_{(m\times1)}=\beta_{0}+\beta_{1}x_{1, j} + \cdots + \beta_{m-1}x_{m-1, j}$, $j=1, \ldots k$ and $m$ is the number of regression coefficients including an intercept term.
-The notation $x_{j}'=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $m\times 1$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
+where $\mu_{0j} = x_{j}^\top \mathbf{\beta}_{(m\times1)}=\beta_{0}+\beta_{1}x_{1, j} + \cdots + \beta_{m-1}x_{m-1, j}$, $j=1, \ldots k$ and $m$ is the number of regression coefficients including an intercept term.
+The notation $x_{j}^\top=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $m\times 1$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
 It is assumed that the second-level variance $A$ is unknown and that $\mathbf{\beta}_{(m\times1)}$ is also unknown unless otherwise specified.
@@
 
-where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$, and $\beta_{(m\times1)}$ and $r$ are unknown hyper-parameters.
+where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}^\top\beta, ~j=1, \ldots, k$, and $\beta_{(m\times1)}$ and $r$ are unknown hyper-parameters.
 Then the corresponding posterior distribution given  $\beta_{(m\times1)}$ and $r$ is
@@
 
-\subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
+\subsection[Hyper-prior distribution]{Hyper-prior Distribution}
 A hyper-prior distribution is a distribution assigned to the second-level parameters.
@@
 
-\subsection[Shrinkage Estimation]{Shrinkage Estimation}
+\subsection[Shrinkage estimation]{Shrinkage Estimation}
 Estimating the shrinkage factors ($B_1, \ldots, B_k$) is the key estimation problem with the hierarchical models \code{gbp} assumes.
@@
 
-\subsection[ADM]{Approximation via Adjustment for Density Maximization}\label{ADM}
+\subsection[ADM]{Approximation via adjustment for density maximization}\label{ADM}
 It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, i.e., $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
@@
 
-\subsection[Posterior Moment Estimation]{Posterior Moment Estimation}
+\subsection[Posterior moment estimation]{Posterior Moment Estimation}
 
@@
 
-\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
+\subsection[Approximation to posterior distribution by moment matching]{Approximation to Posterior Distribution via Matching Moments}
 After estimating the two posterior moments, for example $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$, \code{gbp} approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
@@
 
-\section[Frequency Method Checking]{Frequency Method Checking}
+\section[Frequency method checking]{Frequency Method Checking}
 Like the two sides of the same coin, checking a statistical model comes hand in hand with fitting the model.
@@
 
-\subsection{Pseudo-data Generation Process}
+\subsection{Pseudo-data generation process}
 Figure \ref{fig:pseudo} will be helpful to understand this process.
@@
 
-\subsection{Coverage Estimation Process}
+\subsection{Coverage estimation process}
 Next, \code{coverage} fits the Normal-Normal model  $N_{sim}$ number of times using the $N_{sim}$ pseudo-datasets in order to obtain $N_{sim}$ $\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, N_{sim}$\}.
@@
 
-\subsubsection{Simple Unbiased Coverage Estimates}
+\subsubsection{Simple unbiased coverage estimates}
 Let's define an indicator variable, $I^{(i)}_{j}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu^{(i)}_{j}$ and 0 otherwise.
@@
 
-\subsubsection{Rao-Blackwellized Unbiased Coverage Estimates}
+\subsubsection{Rao-Blackwellized unbiased coverage estimates}
 Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (the sufficient statistic) into account.
@@
 \section[Examples]{Examples}
-\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
+\subsection[Known Second-level Mean]{Data of 31 hospitals with a known second-level mean}
 \label{sec:ex:hosp}
@@
 For reference, caseloads ($n_{j}$) can be interpreted as exposures.
-These data can be loaded into R using the following code where the symbol `\code{R>}' represents a command prompt and is not to be typed into \proglang{R}.
+These data can be loaded into \proglang{R} using the following code where the symbol `\code{R>}' represents a command prompt and is not to be typed into \proglang{R}.
 
@@
 \begin{CodeInput}
-R> data(hospital)
-R> z <- hospital$d # variable name for the number of deaths is d in dataset
+R> data(``hospital'')
+R> z <- hospital$d
 R> n <- hospital$n
@@
 
-\subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean with No Covariates} \label{sec:ex:8schools}
+\subsection[Unknown Second-level Mean and No Covariate]{Data of 8 schools with unknown second-level mean with no covariates} \label{sec:ex:8schools}
 
@@
 \begin{CodeInput}
-R> data(schools)
+R> data(``schools'')
 R> y  <- schools$y
@@
 
-\subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Second-level Mean and One Covariate}
+\subsection[Unknown Second-level Mean and One Covariate]{Data of 18 baseball players with unknown second-level mean and one covariate}
 
@@
 \begin{CodeInput}
-R> data(baseball)
+R> data(``baseball'')
 R> z <- baseball$Hits
@@
 
-As in the previous examples in Section \ref{sec:ex:hosp} and \ref{sec:ex:8schools}, in order to check the level of trust in these interval estimates, we can proceed to frequency method checking by assuming the estimates, 112.95 for $\hat{r}$ and (-1.194, ~0.389) for $\hat{\beta}'$, are given values.
+As in the previous examples in Section \ref{sec:ex:hosp} and \ref{sec:ex:8schools}, in order to check the level of trust in these interval estimates, we can proceed to frequency method checking by assuming the estimates, 112.95 for $\hat{r}$ and (-1.194, ~0.389) for $\hat{\beta}$, are given values.
 
@@
 
-\section[Discussion]{Discussion and Summary} \label{discussion}
-\pkg{Rgbp} is an R package for estimating and validating two-level Gaussian, Binomial and Poisson hierarchical models.
+\section[Discussion]{Discussion and summary} \label{discussion}
+\pkg{Rgbp} is an \proglang{R} package for estimating and validating two-level Gaussian, Binomial and Poisson hierarchical models.
 The package aims to provide a procedure that is computationally efficient with good frequency properties and includes ``frequency method checking'' functionality to examine repeated sampling properties and to test that the method is valid at specified hyper-parameter values.

### 2015-02-27 Rgbp/R/coverage.R

@@ -605,81 +605,81 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 100) {
   par(xaxs = "r", yaxs = "r", mai = c(1, 0.9, 1, 0.3), las = 1)
   n.units <- length(gbp.object$se)
   plot(1 : length(gbp.object$se), result, ylim = c(0.6, 1), type = "b", col = 2,
-       ylab = "Coverage Estimates",
-       xlab = paste("Unit_ j", ", ", "j = 1, ...,", n.units), 
-       main = "Estimated Coverage Probability for Each Unit",
+       ylab = "Coverage estimate",
+       xlab = paste("Group_ j", ", ", "j = 1, ...,", n.units), 
+       main = "Estimated coverage probability for each group",
        lwd = 3, lty = 1)
   abline(h = gbp.object$Alpha)
 
   if (is.na(gbp.object$prior.mean) & missing(mean.PriorDist)) {
     if (gbp.object$model == "gr") {
-      legend("bottomleft", c(paste("Model: Gaussian"), 
-                             "Red Circles: RB coverage estimates",
-                             paste("# of Simulations per Unit: ", effective.n),
-                             paste("Given True A =", round(A, 2)), 
-                             paste("Given True beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
-                             paste("Overall Coverage =", avr.cov)))
+      legend("bottomleft", c(paste("Model: Normal-Normal"), 
+                             "Red circles: RB coverage estimates",
+                             paste("# of simulations per group: ", effective.n),
+                             paste("A for data generation: ", round(A, 2)), 
+                             paste("beta", 0 : (length(betas) - 1), " for data generation: ", round(betas, 3)), 
+                             paste("Overall coverage: ", avr.cov)))
     } else {
-      modelspec <- ifelse(gbp.object$model == "br", "Binomial", "Poisson")
+      modelspec <- ifelse(gbp.object$model == "br", "Binomial-Beta", "Poisson-Gamma")
       legend("bottomleft", c(paste("Model: ", modelspec), 
-                             "Red Circles: RB coverage estimates",
-                             paste("# of Simulations per Unit: ", effective.n),
-                             paste("Given True r =", round(r, 2)), 
-                             paste("Given True beta", 0 : (length(betas) - 1), "=", round(betas, 3)), 
-                             paste("Overall Coverage =", avr.cov)))
+                             "Red circles: RB coverage estimates",
[…]

### 2015-02-27 Rgbp/R/gbp.R

@@ -94,12 +94,12 @@ print.gbp <- function(x, sort = TRUE, ...) {
 
   if (sort == TRUE) {
     if (x$model == "gr") {
-      cat("Summary for each unit (sorted by se): \n")
+      cat("Summary for each group (sorted by the ascending order of se): \n")
     } else {
-      cat("Summary for each unit (sorted by n): \n")
+      cat("Summary for each group (sorted by  the ascending order of n): \n")
     }
   } else {
-    cat("Summary for each unit: \n")
+    cat("Summary for each group: \n")
   }
 
   cat("\n")
@@ -167,25 +167,25 @@ summary.gbp <- function(object, ...) {
       summary.table <- temp2[c(1, (dim(temp2)[1] + 1) / 2, dim(temp2)[1]), ]
       number.of.medians <- dim(summary.table)[1] - 2
       if (number.of.medians == 1) {
-        row.names(summary.table) <- c("Unit with min(obs.mean)", 
-                                      "Unit with median(obs.mean)", 
-                                      "Unit with max(obs.mean)")
+        row.names(summary.table) <- c("Group with min(obs.mean)", 
+                                      "Group with median(obs.mean)", 
+                                      "Group with max(obs.mean)")
       } else {  # if there are more than one median
-        row.names(summary.table) <- c("Unit with min(obs.mean)", 
-                                     paste("Unit with median(obs.mean)", 1 : number.of.medians, sep = ""),
-                                     "Unit with max(obs.mean)")
+        row.names(summary.table) <- c("Group with min(obs.mean)", 
+                                     paste("Group with median(obs.mean)", 1 : number.of.medians, sep = ""),
+                                     "Group with max(obs.mean)")
       }
     } else {  # if number of groups is even
       summary.table <- temp2[c(1, dim(temp2)[1] / 2, dim(temp2)[1] / 2 + 1, dim(temp2)[1]), ]
       number.of.medians <- dim(summary.table)[1] - 2
       if (number.of.medians == 1) {
-        row.names(summary.table) <- c("Unit with min(obs.mean)", 
-                                      "Unit with median(obs.mean)", 
-                                      "Unit with max(obs.mean)")
+        row.names(summary.table) <- c("Group with min(obs.mean)", 
+                                      "Group with median(obs.mean)", 
[…]

### 2015-04-27 jss/article.tex
any changes
paper_apr27_1

@@
 \documentclass[article]{jss}
-
+\usepackage{amsthm, amsmath}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %% almost as usual
-\author{Joseph Kelly\\Harvard University \And 
-             Hyungsuk Tak\\Harvard University\And
+\author{Hyungsuk Tak\\Harvard University \And 
+             Joseph Kelly\\Google\And
              Carl Morris\\ Harvard University}
@@
 \Abstract{
-\pkg{Rgbp} is an \proglang{R} package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner.
+\pkg{Rgbp} is an \proglang{R} package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for over-dispersed Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner.
 The main products of this package are point and interval estimates for each group's random effect, $\mu_{j}$ for Gaussian, $\lambda_{j}$ for Poisson, or $p_{j}$ for Binomial model, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.}
@@
 For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known, and subscript \emph{j} indicates the \emph{j}-th group among \emph{k} groups in the dataset.
-\begin{equation}\label{normalobs}
-y_{j}\vert \mu_{j} \stackrel{ind}{\sim}\textrm{Normal}(\mu_{j}, V_{j}),
-\end{equation}
-\begin{equation}\label{normalprior}
-\mu_{j}\vert \beta, A\stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, A),
-\end{equation}
+\begin{eqnarray}
+y_{j}\vert \mu_{j} & \stackrel{ind}{\sim} &\textrm{Normal}(\mu_{j}, V_{j}),\label{normalobs}\\
+\mu_{j}\vert \boldsymbol{\beta}, A & \stackrel{ind}{\sim} &\textrm{Normal}(\mu_{0j}, A),\label{normalprior}
+\end{eqnarray}
 
-where $\mu_{0j} = x_{j}^\top \mathbf{\beta}_{(m\times1)}=\beta_{0}+\beta_{1}x_{1, j} + \cdots + \beta_{m-1}x_{m-1, j}$, $j=1, \ldots k$ and $m$ is the number of regression coefficients including an intercept term.
-The notation $x_{j}^\top=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $m\times 1$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
-It is assumed that the second-level variance $A$ is unknown and that $\mathbf{\beta}_{(m\times1)}$ is also unknown unless otherwise specified.
+where $\mu_{0j} = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{0}+\beta_{1}x_{1, j} + \cdots + \beta_{m-1}x_{m-1, j}$, $j=1, 2, \ldots k$ and $m$ is the number of regression coefficients including an intercept term.
+The notation $\boldsymbol{x}_j^\top=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $1\times m$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
+It is assumed that the second-level variance $A$ is unknown and that $\boldsymbol{\beta}_{(m\times1)}$ is also unknown unless otherwise specified.
 Note that if there are no covariates then $x_{j}=1$, ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
@@
 \begin{equation} \label{normalpost}
-\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}~),
+\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}~),
 \end{equation}
 where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkage factors.
-By integrating over $\mu_{j}$ for $j = 1 \ldots k$ a marginal distribution, useful for model checking (Section \ref{discussion}), can be derived
-\begin{equation} \label{normalmarginal}
-y_{j}\vert \beta, A \stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, V_{j} + A). 
-\end{equation}
+
+%By integrating over $\mu_{j}$ for $j = 1 \ldots k$ a marginal distribution, useful for model checking (Section \ref{discussion}), can be derived
+%\begin{equation} \label{normalmarginal}
+%y_{j}\vert \boldsymbol{\beta}, A \stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, V_{j} + A). 
+%\end{equation}
 
@@
 \code{gbp} is also capable of estimating a Poisson-Gamma hierarchical model, though its usage is limited to the case where the second-level mean is known ($m=0$).
-For notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$ for the $j$-th group, where  $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials.
+For notational consistency, let's define $\bar{y}_{j}\equiv y_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$ for the $j$-th group, where  $y_{j}$ is the number of successes (or failures) out of $n_{j}$ trials.
 For this Poisson model $n_{j}$ can be interpreted as the exposure of the $j$-th group and is not necessarily an integer.
 The notation $r$ represents the amount of prior information and $n_{j}$ represents the amount of observed information.
-Note that the constant, $1/r$, multiplied to the Gamma distribution below is a scaling factor and the square brackets indicates the [mean, variance] of a distribution.
-\begin{equation}
-z_{j}\vert \lambda_{j} \stackrel{ind}{\sim}\textrm{Poisson}(n_{j}\lambda_{j}),
-\end{equation}
-\begin{equation}\label{gammaprior}
-\lambda_{j}\vert r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(r\lambda_{0})\sim \textrm{Gamma} \left[\lambda_{0}, ~\frac{\lambda_{0}}{r} \right],
-\end{equation}
-
+%Note that the constant, $1/r$, multiplied to the Gamma distribution below is a scaling factor and the square brackets indicates the [mean, variance] of a distribution. 
+\begin{eqnarray}
+y_j\vert \lambda_j &\stackrel{indep.}{\sim} & \textrm{Poisson}(n_{j}\lambda_{j}),\\
+\lambda_{j}\vert r &\stackrel{i.i.d.}{\sim}& \textrm{Gamma}(r\lambda_{0}, r),
+\end{eqnarray}
 where $\lambda_{0}$, the second-level mean, is known a priori and $r$ is the only unknown hyper-parameter. The posterior distribution of this Poisson-Gamma model given the hyper-parameter $r$ is
 \begin{equation} \label{gammapost}
-\lambda_{j}\vert \textbf{y}, r \stackrel{ind}{\sim}\frac{1}{r + n_{j}}\textrm{Gamma}(r\lambda_{0} + n_{j}y_{j})\sim\textrm{Gamma} \left[\lambda^{\ast}_{j},~\frac{\lambda^{\ast}_{j}}{r+n_{j}} \right],
-\end{equation}
-
-where $\lambda^{\ast}_{j} \equiv (1-B_{j})y_{j} + B_{j}\lambda_{0}$ and   $B_{j}\equiv r / (r+n_{j})$ for $j=1, \ldots, k$.
+\lambda_j\vert \boldsymbol{y}, r \stackrel{ind}{\sim}\textrm{Gamma}(r\lambda_{0} + n_{j}\bar{y}_{j}, r + n_j),\end{equation}
+where its posterior mean is $(1-B_{j})y_{j} + B_{j}\lambda_{0}$ and   $B_{j}\equiv r / (r+n_{j})$ for $j=1, 2, \ldots, k$.
 
@@
 The Binomial-Beta hierarchical model is the last model that \code{gbp} can fit.
-Again, $z_{j}$ is the number of successes (or failures) out of $n_{j}$ trials of the $j$-th group and the square bracket [, ] below indicates the [mean, variance] of a distribution.
+The notation $y_{j}$ is the number of successes (or failures) out of $n_{j}$ trials of the $j$-th group.
 Unlike the Poisson-Gamma model, the second-level mean is either known ($m=0$) or unknown ($m\ge1$) a priori.
-\begin{equation}
-z_{j} \vert p_{j}\stackrel{ind}{\sim}\textrm{Binomial}(n_{j}, ~p_{j}),
+\begin{eqnarray}
+y_{j} \vert p_{j} &\stackrel{indep.}{\sim}& \textrm{Binomial}(n_{j}, ~p_{j}),\\
+p_{j} \vert \boldsymbol{\beta}, r &\stackrel{indep.}{\sim}&\textrm{Beta}(rp_{0j},~ r(1-p_{0j})),
+\end{eqnarray}
+
+where $p_{0j}=\exp(\boldsymbol{x}_j^\top\boldsymbol{\beta})/(1+\exp(\boldsymbol{x}_j^\top\boldsymbol{\beta}))$ for $j=1, 2, \ldots, k$.
+The hyper-parameters $\boldsymbol{\beta}_{(m\times1)}$ and $r$ are unknown.
+Then the corresponding posterior distribution of random effect $j$ given  data, $\boldsymbol{\beta}_{(m\times1)}$, and $r$ is
+\begin{equation} \label{betapost}
+p_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}\bar{y}_{j},~r(1-p_{0j})+n_{j}(1-\bar{y}_{j})),
 \end{equation}
-\begin{equation}
-p_{j} \vert \beta, r\stackrel{ind}{\sim}\textrm{Beta}(rp_{0j},~ r(1-p_{0j}))\sim \textrm{Beta} \left[p_{0j}, ~\frac{p_{0j}(1-p_{0j})}{r + 1} \right],
-\end{equation}
-
-where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}^\top\beta, ~j=1, \ldots, k$, and $\beta_{(m\times1)}$ and $r$ are unknown hyper-parameters.
-Then the corresponding posterior distribution given  $\beta_{(m\times1)}$ and $r$ is
-\begin{equation} \label{betapost}
-p_{j}\vert \textbf{y}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}y_{j},~r(1-p_{0j})+n_{j}(1-y_{j}))\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
-\end{equation}
-where $p^{\ast}_{j}\equiv(1-B_{j})y_{j}+B_{j}p_{0j}$, $B_{j}\equiv r/ (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1,\ldots,k$.
+where its posterior mean is $(1-B_{j})\bar{y}_{j}+B_{j}p_{0j}$, $B_{j}\equiv r/ (r+n_{j})$, and $\bar{y}_{j}\equiv y_{j} / n_{j}$.
 
@@
   \label{eq:hyper}
-\beta \sim \textrm{Uniform on}~ \mathbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
+\boldsymbol{\beta} \sim \textrm{Uniform on}~ \boldsymbol{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
 \end{equation}
@@
 where $m$ is the number of regression coefficients.
-As for $\beta$, the flat non-informative distribution above is a common choice to ensure good frequency properties.
+As for $\boldsymbol{\beta}$, the flat non-informative distribution above is a common choice to ensure good frequency properties.
 In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of random effects $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
@@
 As we can see in (\ref{normalpost}), (\ref{gammapost}), and (\ref{betapost}), the posterior means are a linear function of the shrinkage factors ($B_{j}$) and the posterior variances are linear (Gaussian), quadratic (Poisson), and  approximately cubic (Binomial) functions of $B_{j}$.
-A natural method then to estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ is to first estimate the shrinkage factors.
+A natural method then to estimate $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$ is to first estimate the shrinkage factors.
 
@@
 To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of adjustment for density maximization (ADM) \citep{carl1988, 1997, 2011}.
-For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, i.e.,  of $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$, where the notation $\textbf{y}$ represents observed data, without the boundary issues that MLE encounters.
+For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, i.e.,  of $E(B_{j}\vert\boldsymbol{y})$ and $Var(B_{j}\vert\boldsymbol{y})$, where the notation $\boldsymbol{y}$ represents observed data, without the boundary issues that MLE encounters.
 See \cite{2011}.
@@
 
-Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of the random effects given only the data ($\textbf{y}$).
-Taking the Normal-Normal model as an example, it estimates $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by the following identities
+Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of the random effects given only the data ($\boldsymbol{y}$).
+Taking the Normal-Normal model as an example, it estimates $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$ by the following identities
 \begin{eqnarray}
-E(\mu_{j}\vert \textbf{y}) & = & E(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}), \\
-Var(\mu_{j}\vert \textbf{y}) & = & E(Var(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}),
+E(\mu_{j}\vert \boldsymbol{y}) & = & E(E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y}), \\
+Var(\mu_{j}\vert \boldsymbol{y}) & = & E(Var(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y})+Var(E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y}),
 \end{eqnarray}  
-where both $E(\mu_{j}\vert \textbf{y}, \beta, A)$ and $Var(\mu_{j}\vert \textbf{y}, \beta, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}).
-We then estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ by plugging-in the approximately estimated two posterior moments of shrinkage factors.
+where both $E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)$ and $Var(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}).
+We then estimate $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$ by plugging-in the approximately estimated two posterior moments of shrinkage factors.
 
 \subsection[Approximation to posterior distribution by moment matching]{Approximation to Posterior Distribution via Matching Moments}
-After estimating the two posterior moments, for example $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$, \code{gbp} approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
-For the Normal-Normal model we actually estimate the first three moments and approximate $\pi(\mu_{j}\vert \textbf{y})$ with a skewed-Normal distribution \citep{sn2013}.
-For the Poisson-Gamma model we approximate $\pi(\lambda_{j}\vert \textbf{y})$ with a Gamma distribution and finally for the Binomial-Beta model we approximate the posterior distribution of $p_{j}$, $\pi(p_{j}\vert \textbf{y})$, with a Beta distribution.
+After estimating the two posterior moments, for example $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$, \code{gbp} approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
+For the Normal-Normal model we actually estimate the first three moments and approximate $\pi(\mu_{j}\vert \boldsymbol{y})$ with a skewed-Normal distribution \citep{sn2013}.
+For the Poisson-Gamma model we approximate $\pi(\lambda_{j}\vert \boldsymbol{y})$ with a Gamma distribution and finally for the Binomial-Beta model we approximate the posterior distribution of $p_{j}$, $\pi(p_{j}\vert \boldsymbol{y})$, with a Beta distribution.
 
@@
 Figure \ref{fig:pseudo} will be helpful to understand this process.
-As we can see in (\ref{normalprior}), the distribution of each parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$.
+As we can see in (\ref{normalprior}), the distribution of each parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\boldsymbol{\beta}_{(m\times1)}$.
 So, once we fix these hyper-parameters at specific values, we can generate as many parameters as we want.
-Suppose we generated an $N_{sim}$ (default: $N_{sim} = 100$) number of {\boldmath $\mu$}$_{(k\times1)}$'s, (i.e., \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$), from the prior distribution in (\ref{normalprior}), where values of $A$ and $\beta$ are specifically given and the superscript $(i)$ indicates the $i$-th simulation.
-Then using the distribution of observed data in (\ref{normalobs}), we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.
+Suppose we generated an $N_{sim}$ (default: $N_{sim} = 100$) number of {\boldmath $\mu$}$_{(k\times1)}$'s, (i.e., \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$), from the prior distribution in (\ref{normalprior}), where values of $A$ and $\boldsymbol{\beta}$ are specifically given and the superscript $(i)$ indicates the $i$-th simulation.
+Then using the distribution of observed data in (\ref{normalobs}), we can also generate $\{\boldsymbol{y}^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.
 Note that we generate one dataset per one parameter set.
@@
 Let's define an indicator variable, $I^{(i)}_{j}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu^{(i)}_{j}$ and 0 otherwise.
-Then \code{coverage} estimates the coverage probability via the sample mean of these indicator variables for each group $j$, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ for given $A$ and $\beta$.
+Then \code{coverage} estimates the coverage probability via the sample mean of these indicator variables for each group $j$, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ for given $A$ and $\boldsymbol{\beta}$.
 \begin{equation}
@@
 This provides $k$ simple unbiased coverage estimates.
-For example, $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, N_{sim},$ given specific values of $A$ and $\beta$.
+For example, $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, N_{sim},$ given specific values of $A$ and $\boldsymbol{\beta}$.
 
-Each indicator has an independent and identically distributed (\emph{iid}) Bernoulli($p_{cov, j}$) distribution, where $p_{cov, j}$ is the true coverage probability for the $j$-th group depending on specific values of $A$ and $\beta$.
+Each indicator has an independent and identically distributed (\emph{iid}) Bernoulli($p_{cov, j}$) distribution, where $p_{cov, j}$ is the true coverage probability for the $j$-th group depending on specific values of $A$ and $\boldsymbol{\beta}$.
 %For reference, even if we sample $L$ datasets per one parameter set, $L\cdot N_{sim}$ indicators $I^{(i, l)}_{j}, i = 1, \ldots, N_{sim}, l = 1, \ldots, L$, have still $iid$ Bernoulli($p_{cov, j}$) distribution.
@@
 Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (the sufficient statistic) into account.
-Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset.
+Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \boldsymbol{\beta}$), where $A$ and $\boldsymbol{\beta}$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset.
 \begin{equation}\label{RB}
-\bar{I}_{RB, j}\equiv \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta),~ j=1, 2, \ldots, k.
+\bar{I}_{RB, j}\equiv \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \boldsymbol{\beta}),~ j=1, 2, \ldots, k.
 \end{equation}
 
-The expectation part in (\ref{RB}) is Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
-We can calculate this probability  because we know the distribution of ($\mu^{(i)}_{j} \vert y^{(i)}_{j}, A, \beta$) in (\ref{normalpost}).
-Note that conditioning on $y^{(i)}_{j}$ is equivalent to conditioning on $\mathbf{y}^{(i)}_{(k\times1)}$ as long as $A$ and $\beta$ are known.
+The expectation part in (\ref{RB}) is Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \boldsymbol{\beta})$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
+We can calculate this probability  because we know the distribution of ($\mu^{(i)}_{j} \vert y^{(i)}_{j}, A, \boldsymbol{\beta}$) in (\ref{normalpost}).
+Note that conditioning on $y^{(i)}_{j}$ is equivalent to conditioning on $\boldsymbol{y}^{(i)}_{(k\times1)}$ as long as $A$ and $\boldsymbol{\beta}$ are known.
 
-For example, we estimate the first group's true coverage probability $p_{cov, 1}$ (which depends on specific values of $A$ and $\beta$) by $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{1}$.
+For example, we estimate the first group's true coverage probability $p_{cov, 1}$ (which depends on specific values of $A$ and $\boldsymbol{\beta}$) by $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \boldsymbol{\beta})$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{1}$.
 
-Under the setting where one dataset ($\mathbf{y}^{(i)}_{(k\times1)}$) is simulated per one true parameter set ({\boldmath $\mu$}$^{(i)}_{(k\times1)})$, the unbiased variance estimator for Var($\bar{I}_{RB, j}$) follows.
+Under the setting where one dataset ($\boldsymbol{y}^{(i)}_{(k\times1)}$) is simulated per one true parameter set ({\boldmath $\mu$}$^{(i)}_{(k\times1)})$, the unbiased variance estimator for Var($\bar{I}_{RB, j}$) follows.
 \begin{equation}\label{RBvar}
-\widehat{Var}(\bar{I}_{RB, j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}\bigg(E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta)-\bar{I}_{RB, j}\bigg)^{2},~ j=1, 2, \ldots, k.
+\widehat{Var}(\bar{I}_{RB, j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}\bigg(E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \boldsymbol{\beta})-\bar{I}_{RB, j}\bigg)^{2},~ j=1, 2, \ldots, k.
 \end{equation}
@@
 
-The output contains information about observed death rates ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds of interval estimates ($\hat{\lambda}_{j, low}$, 2.5\% percentiles of the approximate posterior distributions if 95\% confidence level is given), approximate posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds  of interval estimates ($\hat{\lambda}_{j, upp}$, 97.5\% percentiles of the approximate posterior distributions), and standard deviations of the approximate posterior distributions ($sd(\lambda_{j}\vert \textbf{y})$).
+The output contains information about observed death rates ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds of interval estimates ($\hat{\lambda}_{j, low}$, 2.5\% percentiles of the approximate posterior distributions if 95\% confidence level is given), approximate posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \boldsymbol{y})$), upper bounds  of interval estimates ($\hat{\lambda}_{j, upp}$, 97.5\% percentiles of the approximate posterior distributions), and standard deviations of the approximate posterior distributions ($sd(\lambda_{j}\vert \boldsymbol{y})$).
 
@@
 
-For reference, two $31 \times 1,000$ matrices \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual estimates, $I^{(i)}_{j}$ and $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta)$.
+For reference, two $31 \times 1,000$ matrices \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual estimates, $I^{(i)}_{j}$ and $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \boldsymbol{\beta})$.
 
@@
 The frequency method checking, assuming the model is correct, generates new pseudo-data from our assumed model.
-Unless otherwise specified, the procedure fixes the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\beta}_0$ in this example) and then simulates ``true'' $\theta_j$ for each group $j$.
+Unless otherwise specified, the procedure fixes the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\boldsymbol{\beta}}_0$ in this example) and then simulates ``true'' $\theta_j$ for each group $j$.
 The model is then estimated and this is repeated an \code{nsim} number of times to estimate the coverage probabilities of the procedure.
@@
 
-As in the previous examples in Section \ref{sec:ex:hosp} and \ref{sec:ex:8schools}, in order to check the level of trust in these interval estimates, we can proceed to frequency method checking by assuming the estimates, 112.95 for $\hat{r}$ and (-1.194, ~0.389) for $\hat{\beta}$, are given values.
+As in the previous examples in Section \ref{sec:ex:hosp} and \ref{sec:ex:8schools}, in order to check the level of trust in these interval estimates, we can proceed to frequency method checking by assuming the estimates, 112.95 for $\hat{r}$ and (-1.194, ~0.389) for $\hat{\boldsymbol{\beta}}$, are given values.
 
@@
 For example, in the Gaussian hierarchical model, the assumed marginal distribution of the data is given in (\ref{normalmarginal}).
-By substituting the point estimates of $A$ and $\beta$ from the package into this marginal distribution a test can be constructed to see whether the data follow the marginal distribution suggested by the hierarchical model.
+By substituting the point estimates of $A$ and $\boldsymbol{\beta}$ from the package into this marginal distribution a test can be constructed to see whether the data follow the marginal distribution suggested by the hierarchical model.
 

### 2015-05-04 jss/article_v2.tex
edit

--- 2015-04-27 jss/article.tex
@@
              Carl Morris\\ Harvard University}
-\title{\pkg{Rgbp}: An \proglang{R} Package for Gaussian, Poisson, and Binomial Hierarchical Modeling}
+\title{\pkg{Rgbp}: An \proglang{R} Package for Conjugate Gaussian, Poisson, and Binomial Hierarchical Modeling and Frequency Method Checking on Overdispersed Data}
 
 %% for pretty printing and a nice hypersummary also set:
-\Plainauthor{Joseph Kelly, Carl Morris, Hyungsuk Tak} %% comma-separated
-\Plaintitle{Rgbp: An R Package for Hierarchical modeling and Method Checking} %% without formatting
-
+\Plainauthor{Hyungsuk Tak, Joseph Kelly, Carl Morris} %% comma-separated
+\Plaintitle{Rgbp: Hierarchical Modeling and Frequency Method Checking} %% without formatting
+\Shorttitle{\pkg{Rgbp}: Hierarchical Modeling and Frequency Method Checking on over dispersed data} %% a short title (if necessary)
 %% an abstract and keywords
 \Abstract{
-\pkg{Rgbp} is an \proglang{R} package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for over-dispersed Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner.
-The main products of this package are point and interval estimates for each group's random effect, $\mu_{j}$ for Gaussian, $\lambda_{j}$ for Poisson, or $p_{j}$ for Binomial model, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.}
-\Keywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, \proglang{R}}
+\pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data and evaluates whether the resulting approximate Bayesian interval estimates for random effects meet the nominal confidence levels via frequency coverage evaluation.
+The data that \pkg{Rgbp} assumes comprise observed sufficient statistic for each group's random effect, such as an average or a proportion of each group, without population-level data.
+The approximate Bayesian tool equipped with the adjustment for density maximization \citep{tang2011} produces approximate point and interval estimates for model parameters including second-level variance component, regression coefficients, and each group's random effect.
+For the Binomial data, the package provides an option to produce  posterior samples of all the model parameters via the acceptance-rejection method.
+The package provides a quick way to evaluate coverage rates of the resultant Bayesian interval estimates for random effects via a parametric bootstrapping, which we call  ``frequency method checking."  }
+%It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.
+\Keywords{overdispersion, hierarchical model, adjustment for density maximization, repeated sampling coverage evaluation, \proglang{R}}
 \Plainkeywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, R} 
@@
 \Address{
-  Joseph Kelly\\
-  Department of Statistics\\
-  Harvard University\\
-  1 Oxford Street, Cambridge, MA\\
-  E-mail: \email{kelly2@fas.harvard.edu}\\
-
   Hyungsuk Tak\\
@@
   E-mail: \email{hyungsuk.tak@gmail.com}\\
+
+  Joseph Kelly\\
+  Google\\
+  76 Ninth Avenue, New York, NY\\
+  E-mail: \email{josephkelly@google.com}\\
 
@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-\pkg{Rgbp} is an \proglang{R} package for estimating and validating a two-level model, also known as a conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} or a conditionally independent hierarchical model \citep{1989}, producing point and interval estimates of  random effects.
-The estimation procedure utilizes approximate Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking").
+Gaussian, Poisson, or Binomial data from several independent groups sometimes have more variation than the assumed Gaussian, Poisson, or Binomial distributions.
+To account for the extra-variability, called overdispersion, a two-level hierarchical model regards the first-level mean parameters as random effects that come from an exchangeable or non-exchangeable population-level conjugate prior distribution.
+The observed data are sufficient statistics for the random effects, such as averages or proportions, obtained from several independent groups.
+The model can incorporate covariate information of each group via a linear, log-linear, or logistic regression according to the data type, which results in a non-exchangeable conjugate prior distribution.
+
+The package \pkg{Rgbp} fits the two-level models on overdispersed data using the adjustment for density maximization \citep{tang2011}, a generalization of a commonly-used restricted maximum likelihood estimation (REML).
+ and that  The population-level data    of several independent groups are ubiquo
+\pkg{Rgbp} is an \proglang{R} package to estimate and validate a two-level model based on  overdispersed  Gaussian, Poisson and Binomial data.
+The estimation procedure adopts the adjustment for density maximization \citep{tang2011} for approximate Bayesian point and interval estimates for random effects and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking").
 It is found that even in small samples our procedure yields good frequency properties in comparison to other methods such as Maximum Likelihood Estimation (MLE).
+
+, producing point and interval estimates of second-level variance component, regression coefficients, and random effects.
 

### 2015-05-05 jss/article_v2.tex
introduction of paper

@@
 \pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data and evaluates whether the resulting approximate Bayesian interval estimates for random effects meet the nominal confidence levels via frequency coverage evaluation.
-The data that \pkg{Rgbp} assumes comprise observed sufficient statistic for each group's random effect, such as an average or a proportion of each group, without population-level data.
-The approximate Bayesian tool equipped with the adjustment for density maximization \citep{tang2011} produces approximate point and interval estimates for model parameters including second-level variance component, regression coefficients, and each group's random effect.
+The data that \pkg{Rgbp} assumes comprise observed sufficient statistics for each random effect, such as an average or a proportion, without population-level data.
+The approximate Bayesian tool equipped with the adjustment for density maximization produces approximate point and interval estimates for model parameters including second-level variance component, regression coefficients, and random effects.
 For the Binomial data, the package provides an option to produce  posterior samples of all the model parameters via the acceptance-rejection method.
@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-Gaussian, Poisson, or Binomial data from several independent groups sometimes have more variation than the assumed Gaussian, Poisson, or Binomial distributions.
-To account for the extra-variability, called overdispersion, a two-level hierarchical model regards the first-level mean parameters as random effects that come from an exchangeable or non-exchangeable population-level conjugate prior distribution.
-The observed data are sufficient statistics for the random effects, such as averages or proportions, obtained from several independent groups.
-The model can incorporate covariate information of each group via a linear, log-linear, or logistic regression according to the data type, which results in a non-exchangeable conjugate prior distribution.
+Gaussian, Poisson, or Binomial data from several independent groups sometimes have more variation than the assumed Gaussian, Poisson, or Binomial distributions on the first-level observed data.
+To account for the extra-variability, called overdispersion, a two-level hierarchical model regards first-level mean parameters as random effects that come from a population-level conjugate prior distribution.
+The conjugate prior distribution is exchangeable if no covariates are available and non-exchangeable if the model incorporates covariate information of each group via a linear, log-linear, or logistic regression according to the data type.
 
-The package \pkg{Rgbp} fits the two-level models on overdispersed data using the adjustment for density maximization \citep{tang2011}, a generalization of a commonly-used restricted maximum likelihood estimation (REML).
- and that  The population-level data    of several independent groups are ubiquo
-\pkg{Rgbp} is an \proglang{R} package to estimate and validate a two-level model based on  overdispersed  Gaussian, Poisson and Binomial data.
-The estimation procedure adopts the adjustment for density maximization \citep{tang2011} for approximate Bayesian point and interval estimates for random effects and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking").
-It is found that even in small samples our procedure yields good frequency properties in comparison to other methods such as Maximum Likelihood Estimation (MLE).
+With an assumption of homogeneity within each group, the observed data are sufficient statistics for the random effects, such as averages or proportions, possibly together with each group's covariate information.
+This type of  data is common for a biological analysis on litter data, a meta analysis, or small area estimation problems.
+For these data, the two-level model that \pkg{Rgbp} assumes can be considered as a conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} without any fixed effects.
 
-, producing point and interval estimates of second-level variance component, regression coefficients, and random effects.
+\pkg{Rgbp} takes a Bayesian approach with our special improper hyper-prior distributions on hyper-parameters, the parameters of the conjugate prior distribution.
+The hyper-prior distributions lead to Stein's harmonic prior known to produce good repeated sampling coverage properties of the Bayesian interval estimates for random effects in a two-level Gaussian hierarchical model \citep{tang2011, morris2012}.
+We apply the hyper-prior distributions to Poisson and Binomial hierarchical models.
+The goal of our hierarchical modeling is to compare random effects among groups by their Bayesian point and interval estimates that have good frequency properties.
 
-This package is useful for both frequentists and Bayesians.
+When it comes to fitting the model, \pkg{Rgbp} adopts the adjustment for density maximization \citep{carl1988, 1997, tang2011} (ADM), a generalization of a commonly-used restricted maximum likelihood method (REML).
+The ADM uses Beta distributions to approximate the posterior distributions of shrinkage factors, functions of a second-level variance component, via maximization like a Delta method that uses a Normal distribution to obtain the approximate distribution of a function of a parameter with its MLE and observed information plugged-in.
+The ADM is more appropriate than the Delta method (or REML) because the support of each shrinkage factor is between 0 and 1, not ($-\infty,~\infty$).
+Also, the ADM is free of boundary effects that REML suffers from (e.g.
+a zero estimate for the second-level variance component).
+Using the approximate estimates for the posterior mean and variance of the shrinkage factors, \pkg{Rgbp} obtains  approximate posterior mean and variance of the random effect.
+Finally, \pkg{Rgbp} approximates the posterior distributions of random effects by a Pearson family distribution whose two parameters are matched to the estimated posterior mean and variance of random effects.
+
+For the Gaussian hierarchical model, \pkg{Rgbp} approximates the posterior distribution of the random effects by a skewed Normal distribution whose three parameters are matched to the first three posterior moment estimates for random effects.
+For the Binomial  model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters including second-level variance component, logistic regression coefficients, and random effects,  via an acceptance-rejection method instead of the approximate tool.
+
+In addition to fitting hierarchical models, \pkg{Rgbp} provides a quick way to evaluate the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects.
+It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for similar multilevel models, such as \pkg{hglm} for conjugate hierarchical generalized models, \pkg{arm} for Bayesian hierarchical models, and \pkg{hbsae} for hierarchical Bayesian small area estimation.
+The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping that generates mock data sets given hyper-parameter values and estimates the coverage rates.
+
+%This package is useful for both frequentist and Bayesian.
 Bayesians are able to use the package to see results for a non-informative reference prior before and after constructing their own Bayesian hierarchical model and frequentists are provided with a procedure with good repeated sampling properties.
@@
 
-To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of adjustment for density maximization (ADM) \citep{carl1988, 1997, 2011}.
+To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of adjustment for density maximization (ADM) \citep{carl1988, 1997, tang2011}.
 For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, i.e.,  of $E(B_{j}\vert\boldsymbol{y})$ and $Var(B_{j}\vert\boldsymbol{y})$, where the notation $\boldsymbol{y}$ represents observed data, without the boundary issues that MLE encounters.

### 2015-05-05 jss/article.tex
introduction and abstract

@@
              Carl Morris\\ Harvard University}
-\title{\pkg{Rgbp}: An \proglang{R} Package for Gaussian, Poisson, and Binomial Hierarchical Modeling}
+\title{\pkg{Rgbp}: An \proglang{R} Package for Gaussian, Binomial, and Poisson Hierarchical Modeling}
 
 %% for pretty printing and a nice hypersummary also set:
-\Plainauthor{Joseph Kelly, Carl Morris, Hyungsuk Tak} %% comma-separated
-\Plaintitle{Rgbp: An R Package for Hierarchical modeling and Method Checking} %% without formatting
+\Plainauthor{Hyungsuk Tak, Joseph Kelly, Carl Morris} %% comma-separated
+\Plaintitle{Rgbp: An R Package for Hierarchical modeling and Frequency Method Checking} %% without formatting
 
@@
 \Abstract{
-\pkg{Rgbp} is an \proglang{R} package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for over-dispersed Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner.
-The main products of this package are point and interval estimates for each group's random effect, $\mu_{j}$ for Gaussian, $\lambda_{j}$ for Poisson, or $p_{j}$ for Binomial model, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking."  It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.}
-\Keywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, \proglang{R}}
+\pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for over-dispersed Gaussian, Binomial, and Poisson data in a fast and computationally efficient manner.
+The main products of this package are point and interval estimates for each group's random effect, $\mu_j$ for Gaussian, $\lambda_j$ for Poisson, or $p_j$ for Binomial model, whose good frequency properties can be validated via its repeated sampling procedure called ``frequency method checking.'' It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.
+}
+%It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.
+\Keywords{overdispersion, hierarchical model, adjustment for density maximization, repeated sampling coverage evaluation, \proglang{R}}
 \Plainkeywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, R} 

### 2015-05-05 jss/article_v2.tex
introduction and abstract

@@
 \Abstract{
-\pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data and evaluates whether the resulting approximate Bayesian interval estimates for random effects meet the nominal confidence levels via frequency coverage evaluation.
-The data that \pkg{Rgbp} assumes comprise observed sufficient statistics for each random effect, such as an average or a proportion, without population-level data.
+\pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data and evaluates repeated sampling frequency property of the resulting approximate Bayesian interval estimates for random effects.
+The main goal of \pkg{Rgb} is to produce Bayesian interval estimates for the random effects that meet the nominal confidence level, and the package uses special improper hyper-prior distributions for that purpose.
+The data that \pkg{Rgbp} assumes comprise observed sufficient statistics for each random effect, such as averages or proportions, without population-level data.
 The approximate Bayesian tool equipped with the adjustment for density maximization produces approximate point and interval estimates for model parameters including second-level variance component, regression coefficients, and random effects.
 For the Binomial data, the package provides an option to produce  posterior samples of all the model parameters via the acceptance-rejection method.
-The package provides a quick way to evaluate coverage rates of the resultant Bayesian interval estimates for random effects via a parametric bootstrapping, which we call  ``frequency method checking."  }
+The package provides a quick way to check whether the resultant Bayesian interval estimates for the random effects meet the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
 %It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.
@@
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
-Gaussian, Poisson, or Binomial data from several independent groups sometimes have more variation than the assumed Gaussian, Poisson, or Binomial distributions on the first-level observed data.
+Gaussian, Poisson, or Binomial data from several independent groups sometimes have more variation than the assumed Gaussian, Poisson, or Binomial distributions of the first-level observed data.
 To account for the extra-variability, called overdispersion, a two-level hierarchical model regards first-level mean parameters as random effects that come from a population-level conjugate prior distribution.
@@
 With an assumption of homogeneity within each group, the observed data are sufficient statistics for the random effects, such as averages or proportions, possibly together with each group's covariate information.
-This type of  data is common for a biological analysis on litter data, a meta analysis, or small area estimation problems.
-For these data, the two-level model that \pkg{Rgbp} assumes can be considered as a conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010} without any fixed effects.
+This type of  data is common for a biological analysis on litter data, a meta analysis on independent studies, or small area estimation problems.
+For these data, the two-level model that \pkg{Rgbp} assumes can be considered as a conjugate hierarchical generalized linear model \citep{lee1996hierarchical, hglm2006} where each random effect has a conjugate prior distribution.
 
-\pkg{Rgbp} takes a Bayesian approach with our special improper hyper-prior distributions on hyper-parameters, the parameters of the conjugate prior distribution.
+\pkg{Rgbp} takes a Bayesian approach with our special improper hyper-prior distributions on hyper-parameters, the parameters of the conjugate prior distribution, to produce  Bayesian interval   estimates for the random effects that achieve nominal confidence levels.
 The hyper-prior distributions lead to Stein's harmonic prior known to produce good repeated sampling coverage properties of the Bayesian interval estimates for random effects in a two-level Gaussian hierarchical model \citep{tang2011, morris2012}.
 We apply the hyper-prior distributions to Poisson and Binomial hierarchical models.
-The goal of our hierarchical modeling is to compare random effects among groups by their Bayesian point and interval estimates that have good frequency properties.
+%The main goal of our Bayesian hierarchical models is to compare random effects between groups by their Bayesian interval estimates that have good frequency properties.
 
-When it comes to fitting the model, \pkg{Rgbp} adopts the adjustment for density maximization \citep{carl1988, 1997, tang2011} (ADM), a generalization of a commonly-used restricted maximum likelihood method (REML).
-The ADM uses Beta distributions to approximate the posterior distributions of shrinkage factors, functions of a second-level variance component, via maximization like a Delta method that uses a Normal distribution to obtain the approximate distribution of a function of a parameter with its MLE and observed information plugged-in.
-The ADM is more appropriate than the Delta method (or REML) because the support of each shrinkage factor is between 0 and 1, not ($-\infty,~\infty$).
-Also, the ADM is free of boundary effects that REML suffers from (e.g.
-a zero estimate for the second-level variance component).
-Using the approximate estimates for the posterior mean and variance of the shrinkage factors, \pkg{Rgbp} obtains  approximate posterior mean and variance of the random effect.
-Finally, \pkg{Rgbp} approximates the posterior distributions of random effects by a Pearson family distribution whose two parameters are matched to the estimated posterior mean and variance of random effects.
+When it comes to fitting the model, \pkg{Rgbp} adopts the adjustment for density maximization \citep{carl1988, morris1997, tang2011} (ADM), a Pearson family approximation via maximization.
+For example, a Delta method is a special case of ADM that uses a Normal distribution to obtain an approximate distribution of a function of a parameter with its MLE and observed information plugged-in.
+In this article, the ADM uses Beta distributions to approximate the posterior distributions of shrinkage factors, functions of the second-level variance component, via maximization.
+For this approximation, the ADM  is more appropriate than the Delta method because the support of each shrinkage factor is between 0 and 1, not ($-\infty,~\infty$).
+Also, the ADM is free of a boundary effect that leads to a zero estimate for the second-level variance component  which a restricted MLE \citep{patterson1971recovery} (REML) sometimes suffers from.
+Using the approximate posterior distributions of shrinkage factors, \pkg{Rgbp} estimates the first two (three for the Gaussian case) posterior moments of the random effects.
+Finally, \pkg{Rgbp} approximates the posterior distribution of each random effect by a skewed Normal distribution for a Gaussian case, a Gamma distribution for a Poisson case, and a Beta distribution for a Binomial case whose two (three for the Gaussian case) parameters are matched to the estimated posterior moments of the random effects.
 
-For the Gaussian hierarchical model, \pkg{Rgbp} approximates the posterior distribution of the random effects by a skewed Normal distribution whose three parameters are matched to the first three posterior moment estimates for random effects.
-For the Binomial  model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters including second-level variance component, logistic regression coefficients, and random effects,  via an acceptance-rejection method instead of the approximate tool.
+For the Binomial  model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters via an acceptance-rejection method instead of the approximate tool.
 
-In addition to fitting hierarchical models, \pkg{Rgbp} provides a quick way to evaluate the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects.
-It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for similar multilevel models, such as \pkg{hglm} for conjugate hierarchical generalized models, \pkg{arm} for Bayesian hierarchical models, and \pkg{hbsae} for hierarchical Bayesian small area estimation.
-The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping that generates mock data sets given hyper-parameter values and estimates the coverage rates.
+In addition to fitting hierarchical models, \pkg{Rgbp} provides a quick way to evaluate the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects \citep{morris1997, daniels1999prior, tang2002fitting, tang2011, morris2012}.
+It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages  such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models and \pkg{arm} \citep{gelman2014arm} for Bayesian hierarchical models with proper hyper-prior distributions.
+The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping that generates mock data sets given the values of hyper-parameters and estimates the coverage rates.
 
-%This package is useful for both frequentist and Bayesian.
-Bayesians are able to use the package to see results for a non-informative reference prior before and after constructing their own Bayesian hierarchical model and frequentists are provided with a procedure with good repeated sampling properties.
+The rest of this paper is organized as follows.
+We specify the Bayesian hierarchical models and discuss their posterior propriety in Section \ref{sec2} We describe the estimation procedures including the ADM and the acceptance-rejection method in Section  \ref{sec3}, and the frequency method checking in Section \ref{sec4}.
+We explain the usages of main functions in \pkg{Rgbp} in Section \ref{sec5}, and apply them to three examples in Section \ref{sec6}.
 
-\section[Hierarchical Structure]{Hierarchical structure} \label{hierarchical}
+\section[Hierarchical Structure]{Hierarchical structure} \label{sec2}
 A two-level or multilevel model is a powerful tool for exploring the hierarchical structure in data.
@@
 
-\section[Estimation]{Estimation}
+\section[Estimation]{Eestimation}\label{sec3}
 
@@
 
-\section[Frequency method checking]{Frequency Method Checking}
+\section[Frequency method checking]{Frequency Method Checking}\label{sec4}
 Like the two sides of the same coin, checking a statistical model comes hand in hand with fitting the model.
@@
 
-\section[Examples]{Examples}
+\section[packageoverview]{Main Functions in \pkg{Rgbp}}\label{sec5}
+
+\section[Examples]{Examples}\label{sec6}
 \subsection[Known Second-level Mean]{Data of 31 hospitals with a known second-level mean}

### 2015-05-05 jss/article_v2.tex
abstract and introduction

@@
 \Abstract{
-\pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data and evaluates repeated sampling frequency property of the resulting approximate Bayesian interval estimates for random effects.
-The main goal of \pkg{Rgb} is to produce Bayesian interval estimates for the random effects that meet the nominal confidence level, and the package uses special improper hyper-prior distributions for that purpose.
-The data that \pkg{Rgbp} assumes comprise observed sufficient statistics for each random effect, such as averages or proportions, without population-level data.
+\pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data.
+The data that \pkg{Rgbp} assumes comprise observed sufficient statistics for each random effect, such as averages or proportions, possibly together with covariates of each group but without population-level data.
+The main goal of \pkg{Rgb} is to produce approximate Bayesian interval estimates for the random effects that meet their nominal confidence level, and the package uses special improper hyper-prior distributions for that purpose.
 The approximate Bayesian tool equipped with the adjustment for density maximization produces approximate point and interval estimates for model parameters including second-level variance component, regression coefficients, and random effects.
 For the Binomial data, the package provides an option to produce  posterior samples of all the model parameters via the acceptance-rejection method.
-The package provides a quick way to check whether the resultant Bayesian interval estimates for the random effects meet the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
+\pkg{Rgbp} provides a quick way to check whether the resultant Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
+% and evaluates repeated sampling frequency property of the resulting approximate Bayesian interval estimates for random effects
 %It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.
@@
 \pkg{Rgbp} takes a Bayesian approach with our special improper hyper-prior distributions on hyper-parameters, the parameters of the conjugate prior distribution, to produce  Bayesian interval   estimates for the random effects that achieve nominal confidence levels.
-The hyper-prior distributions lead to Stein's harmonic prior known to produce good repeated sampling coverage properties of the Bayesian interval estimates for random effects in a two-level Gaussian hierarchical model \citep{tang2011, morris2012}.
+The hyper-prior distributions lead to Stein's harmonic prior known to produce good repeated sampling coverage rates of the Bayesian interval estimates for random effects in a two-level Gaussian hierarchical model \citep{tang2011, morris2012}.
 We apply the hyper-prior distributions to Poisson and Binomial hierarchical models.
@@
 In addition to fitting hierarchical models, \pkg{Rgbp} provides a quick way to evaluate the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects \citep{morris1997, daniels1999prior, tang2002fitting, tang2011, morris2012}.
-It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages  such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models and \pkg{arm} \citep{gelman2014arm} for Bayesian hierarchical models with proper hyper-prior distributions.
-The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping that generates mock data sets given the values of hyper-parameters and estimates the coverage rates.
+It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages doing the similar modeling work such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models and \pkg{arm} \citep{gelman2014arm} for Bayesian hierarchical regression models with proper hyper-prior distributions.
+The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping that generates mock data sets given the values of the hyper-parameters and estimates the coverage rates.
 

### 2015-05-23 jss/article_v2.tex
title change

@@
 \pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data.
-The data that \pkg{Rgbp} assumes comprise observed sufficient statistics for each random effect, such as averages or proportions, possibly together with covariates of each group but without population-level data.
+The data that \pkg{Rgbp} assumes comprise of observed sufficient statistics for each random effect, such as averages or proportions, possibly together with covariates of each group but without population-level data.
+The approximate Bayesian tool equipped with the adjustment for density maximization produces point and interval estimates for each random effect, point estimates and standard errors for regression coefficients, and a point estimate and its standard error for a second-level variance component.
+For the Binomial data, the package provides an option to produce  posterior samples of all the model parameters via the acceptance-rejection method.
 The main goal of \pkg{Rgb} is to produce approximate Bayesian interval estimates for the random effects that meet their nominal confidence level, and the package uses special improper hyper-prior distributions for that purpose.
-The approximate Bayesian tool equipped with the adjustment for density maximization produces approximate point and interval estimates for model parameters including second-level variance component, regression coefficients, and random effects.
-For the Binomial data, the package provides an option to produce  posterior samples of all the model parameters via the acceptance-rejection method.
 \pkg{Rgbp} provides a quick way to check whether the resultant Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
@@
 Using the approximate posterior distributions of shrinkage factors, \pkg{Rgbp} estimates the first two (three for the Gaussian case) posterior moments of the random effects.
-Finally, \pkg{Rgbp} approximates the posterior distribution of each random effect by a skewed Normal distribution for a Gaussian case, a Gamma distribution for a Poisson case, and a Beta distribution for a Binomial case whose two (three for the Gaussian case) parameters are matched to the estimated posterior moments of the random effects.
+Finally, \pkg{Rgbp} approximates the posterior distribution of each random effect by a skewed Normal distribution for a Gaussian case, a Gamma distribution for a Poisson case, and a Beta distribution for a Binomial case whose two parameters (three for the skewed Normal distribution) are matched to the estimated posterior moments of the random effects.
 
@@
 In addition to fitting hierarchical models, \pkg{Rgbp} provides a quick way to evaluate the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects \citep{morris1997, daniels1999prior, tang2002fitting, tang2011, morris2012}.
-It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages doing the similar modeling work such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models and \pkg{arm} \citep{gelman2014arm} for Bayesian hierarchical regression models with proper hyper-prior distributions.
-The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping that generates mock data sets given the values of the hyper-parameters and estimates the coverage rates.
+It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for hierarchical modeling such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models and \pkg{arm} \citep{gelman2014arm} for Bayesian hierarchical regression models with proper hyper-prior distributions.
+The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping that generates mock data sets given the values of the hyper-parameters and estimates the coverage rates based on the simulated data sets.
 
 The rest of this paper is organized as follows.
-We specify the Bayesian hierarchical models and discuss their posterior propriety in Section \ref{sec2} We describe the estimation procedures including the ADM and the acceptance-rejection method in Section  \ref{sec3}, and the frequency method checking in Section \ref{sec4}.
+We specify the Bayesian hierarchical models and discuss their posterior propriety in Section \ref{sec2}.
+We describe the estimation procedures including the ADM and the acceptance-rejection method in Section  \ref{sec3}, and the frequency method checking in Section \ref{sec4}.
 We explain the usages of main functions in \pkg{Rgbp} in Section \ref{sec5}, and apply them to three examples in Section \ref{sec6}.

### 2015-06-06 jss/article_v2.tex
revision and changes

@@
 
+\DeclareMathOperator*{\argmax}{arg\,max}
 %% almost as usual
@@
 \Plaintitle{Rgbp: Hierarchical Modeling and Frequency Method Checking} %% without formatting
-\Shorttitle{\pkg{Rgbp}: Hierarchical Modeling and Frequency Method Checking on over dispersed data} %% a short title (if necessary)
+\Shorttitle{\pkg{Rgbp}: Hierarchical Modeling and Frequency Method Checking on Overdispersed Data} %% a short title (if necessary)
 %% an abstract and keywords
@@
 For the Binomial data, the package provides an option to produce  posterior samples of all the model parameters via the acceptance-rejection method.
-The main goal of \pkg{Rgb} is to produce approximate Bayesian interval estimates for the random effects that meet their nominal confidence level, and the package uses special improper hyper-prior distributions for that purpose.
+The main goal of \pkg{Rgb} is to produce approximate Bayesian interval estimates for the random effects that meet their nominal confidence levels, and the package uses unique improper hyper-prior distributions for that purpose.
 \pkg{Rgbp} provides a quick way to check whether the resultant Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
@@
 Gaussian, Poisson, or Binomial data from several independent groups sometimes have more variation than the assumed Gaussian, Poisson, or Binomial distributions of the first-level observed data.
-To account for the extra-variability, called overdispersion, a two-level hierarchical model regards first-level mean parameters as random effects that come from a population-level conjugate prior distribution.
-The conjugate prior distribution is exchangeable if no covariates are available and non-exchangeable if the model incorporates covariate information of each group via a linear, log-linear, or logistic regression according to the data type.
+To account for the extra-variability, called overdispersion, a  two-level conjugate hierarchical model regards first-level mean parameters as random effects that come from a population-level conjugate prior distribution.
+The conjugate prior distribution is non-exchangeable if the model incorporates covariate information of each group via a linear, log-linear, or logistic regression according to the data type, and exchangeable if no covariates are available with only an intercept term for the regression.
 
@@
 \pkg{Rgbp} takes a Bayesian approach with our special improper hyper-prior distributions on hyper-parameters, the parameters of the conjugate prior distribution, to produce  Bayesian interval   estimates for the random effects that achieve nominal confidence levels.
-The hyper-prior distributions lead to Stein's harmonic prior known to produce good repeated sampling coverage rates of the Bayesian interval estimates for random effects in a two-level Gaussian hierarchical model \citep{tang2011, morris2012}.
-We apply the hyper-prior distributions to Poisson and Binomial hierarchical models.
+The hyper-prior distributions lead to Stein's harmonic prior known to produce good repeated sampling coverage rates of the Bayesian interval estimates for random effects in a two-level Gaussian hierarchical model \citep{tang2011, morris2012, kelly2014advances}.
+We apply an analog to Stein's harmonic prior to Poisson and Binomial hierarchical models.
 %The main goal of our Bayesian hierarchical models is to compare random effects between groups by their Bayesian interval estimates that have good frequency properties.
@@
 In this article, the ADM uses Beta distributions to approximate the posterior distributions of shrinkage factors, functions of the second-level variance component, via maximization.
-For this approximation, the ADM  is more appropriate than the Delta method because the support of each shrinkage factor is between 0 and 1, not ($-\infty,~\infty$).
-Also, the ADM is free of a boundary effect that leads to a zero estimate for the second-level variance component  which a restricted MLE \citep{patterson1971recovery} (REML) sometimes suffers from.
-Using the approximate posterior distributions of shrinkage factors, \pkg{Rgbp} estimates the first two (three for the Gaussian case) posterior moments of the random effects.
-Finally, \pkg{Rgbp} approximates the posterior distribution of each random effect by a skewed Normal distribution for a Gaussian case, a Gamma distribution for a Poisson case, and a Beta distribution for a Binomial case whose two parameters (three for the skewed Normal distribution) are matched to the estimated posterior moments of the random effects.
-
-For the Binomial  model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters via an acceptance-rejection method instead of the approximate tool.
+For the approximation to the distributions of the shrinkage factors, the Beta distribution  is more appropriate than the Normal distribution (Delta method) because the support of each shrinkage factor is between 0 and 1, not ($-\infty,~\infty$).
+Also, the ADM is free of a boundary effect that a restricted MLE \citep{patterson1971recovery} (REML) sometimes suffers from, preventing a zero estimate for the second-level variance component.
+Using the approximate Beta posterior distributions of shrinkage factors, \pkg{Rgbp} estimates the first two (three for the Gaussian case) posterior moments of the random effects.
+Finally, \pkg{Rgbp} approximates the posterior distribution of each random effect by a skewed Normal distribution for a Gaussian case, a Gamma distribution for a Poisson case, and a Beta distribution for a Binomial case whose two parameters (three for the skewed Normal distribution) are matched to the previously estimated posterior moments of the random effects.
+
+For the Binomial  multilevel model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters via an acceptance-rejection method instead of the approximate tool.
 
 In addition to fitting hierarchical models, \pkg{Rgbp} provides a quick way to evaluate the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects \citep{morris1997, daniels1999prior, tang2002fitting, tang2011, morris2012}.
-It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for hierarchical modeling such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models and \pkg{arm} \citep{gelman2014arm} for Bayesian hierarchical regression models with proper hyper-prior distributions.
-The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping that generates mock data sets given the values of the hyper-parameters and estimates the coverage rates based on the simulated data sets.
+It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for hierarchical modeling such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models and \pkg{arm} \citep{gelman2014arm} for Bayesian hierarchical regression models.
+The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping that generates mock data sets given the values of the hyper-parameters and estimates the coverage rates based on the generated mock data sets.
 
@@
 
-\section[Hierarchical Structure]{Hierarchical structure} \label{sec2}
-A two-level or multilevel model is a powerful tool for exploring the hierarchical structure in data.
+\section[Hierarchical Structure]{Conjugate hierarchical modeling structure} \label{sec2}
+%A two-level  multilevel model is a powerful tool for exploring the hierarchical structure in data.
 For example, we can imagine that there exists a district-level hierarchy (bigger population) for observed school-level data, or a state-level hierarchy for observed hospital-level data in a certain state.
 
-\code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level has distributions of observed data and whose second-level has conjugate distributions on the first-level parameters.
-The \code{gbp} function allows users to choose one of three types of hierarchical models, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta.
+One of the functions in \pkg{Rgbp}, \code{gbp}, fits a conjugate hierarchical model whose first-level has distributions of observed data and whose second-level has conjugate distributions on the first-level mean parameters (random effects).
+The \code{gbp} function allows users to choose one of three types of hierarchical models according to the type of data, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta models.
 
@@
 For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known, and subscript \emph{j} indicates the \emph{j}-th group among \emph{k} groups in the dataset.
+For $j=1, 2, \ldots, k$,
 \begin{eqnarray}
-y_{j}\vert \mu_{j} & \stackrel{ind}{\sim} &\textrm{Normal}(\mu_{j}, V_{j}),\label{normalobs}\\
-\mu_{j}\vert \boldsymbol{\beta}, A & \stackrel{ind}{\sim} &\textrm{Normal}(\mu_{0j}, A),\label{normalprior}
+y_{j}\vert \mu_{j} & \stackrel{indep.}{\sim} &\textrm{Normal}(\mu_{j}, V_{j}),\label{normalobs}\\
+\mu_{j}\vert \boldsymbol{\beta}, A & \stackrel{indep.}{\sim} &\textrm{Normal}(\mu^E_{j}, A),\label{normalprior}
 \end{eqnarray}
 
-where $\mu_{0j} = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{0}+\beta_{1}x_{1, j} + \cdots + \beta_{m-1}x_{m-1, j}$, $j=1, 2, \ldots k$ and $m$ is the number of regression coefficients including an intercept term.
-The notation $\boldsymbol{x}_j^\top=(1, x_{1, j}, x_{2, j}, \ldots, x_{m-1, j})$ represents the $j$-th group's $1\times m$ covariate vector whose first element is 1 for the intercept term of regression coefficients.
-It is assumed that the second-level variance $A$ is unknown and that $\boldsymbol{\beta}_{(m\times1)}$ is also unknown unless otherwise specified.
-Note that if there are no covariates then $x_{j}=1$, ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution.
-For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, i.e., a prior mean.
-Based on this conjugate prior distribution it is easy to derive the corresponding posterior distribution
+where $\mu^E_{j} = E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$ is the expected random effect and $m$ is the number of regression coefficients to be estimated.
+The default of the function \code{gbp} is to set $x_{j, 1}$ to 1 for an intercept term, though \code{gbp} also provides a usage without the intercept term.
+It is assumed that the second-level variance $A$ is unknown and that the $m\times1$ regression coefficient vector $\boldsymbol{\beta}$ is also unknown unless otherwise specified.
+If no covariates are available with an intercept term, then $\boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_1$ ($m=1$) and thus $\mu^E_{j}=\mu^E=\beta_1$ for all $j$, resulting in an exchangeable conjugate prior distribution for the random effects.
+Based on these conjugate prior distributions for random effects, it is easy to derive the conditional posterior distributions of the random effects.
+For $j=1, 2, \ldots, k$,
 
 \begin{equation} \label{normalpost}
-\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}~),
-\end{equation}
-where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkage factors.
-
-%By integrating over $\mu_{j}$ for $j = 1 \ldots k$ a marginal distribution, useful for model checking (Section \ref{discussion}), can be derived
-%\begin{equation} \label{normalmarginal}
-%y_{j}\vert \boldsymbol{\beta}, A \stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, V_{j} + A). 
-%\end{equation}
+\mu_{j}\vert  \boldsymbol{\beta}, A, \boldsymbol{y} \stackrel{indep.}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu^E_{j},~(1-B_{j})V_{j}~),
+\end{equation}
+where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkage factors, and $\boldsymbol{y}^T=(y_1, y_2, \ldots, y_k)$.
+Note that the conditional posterior mean of the random effect, $\mu^\ast_j\equiv E(\mu_{j}\vert \boldsymbol{\beta}, A, \boldsymbol{y} )=(1-B_{j})y_{j} + B_{j}\mu^E_{j}$,  is a convex combination of the observed sufficient statistic $y_j$ and the expected random effect $\mu^E_j$ weighted by the shrinkage factor $B_j$.
+If the variance of the conjugate prior distribution, $A$, is smaller than the variance of the observed distribution, $V_j$, then we expect the posterior mean to borrow more information from the more accurate second-level conjugate prior distribution.
 
 \subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}\label{poissonsubsec}
-\code{gbp} is also capable of estimating a Poisson-Gamma hierarchical model, though its usage is limited to the case where the second-level mean is known ($m=0$).
-For notational consistency, let's define $\bar{y}_{j}\equiv y_{j} / n_{j}$ as the unbiased estimate of $\lambda_{j}$ for the $j$-th group, where  $y_{j}$ is the number of successes (or failures) out of $n_{j}$ trials.
-For this Poisson model $n_{j}$ can be interpreted as the exposure of the $j$-th group and is not necessarily an integer.
-The notation $r$ represents the amount of prior information and $n_{j}$ represents the amount of observed information.
-%Note that the constant, $1/r$, multiplied to the Gamma distribution below is a scaling factor and the square brackets indicates the [mean, variance] of a distribution. 
+The function \code{gbp} is also capable of estimating a conjugate Poisson-Gamma hierarchical model, though its usage is limited to the case where the expected random effects are known ($m=0$).
+For $j=1, 2, \ldots, k$,
 \begin{eqnarray}
 y_j\vert \lambda_j &\stackrel{indep.}{\sim} & \textrm{Poisson}(n_{j}\lambda_{j}),\\
-\lambda_{j}\vert r &\stackrel{i.i.d.}{\sim}& \textrm{Gamma}(r\lambda_{0}, r),
+\lambda_{j}\vert r &\stackrel{i.i.d.}{\sim}& \textrm{Gamma}(r\lambda^E, r),
 \end{eqnarray}
-where $\lambda_{0}$, the second-level mean, is known a priori and $r$ is the only unknown hyper-parameter. The posterior distribution of this Poisson-Gamma model given the hyper-parameter $r$ is
+where $n_{j}$ is the exposure of group $j$, which is not necessarily an integer, $\lambda^E=E(\lambda_j\vert r)$ is the known expected random effect, and $r$ is the unknown second-level variance component.
+The mean and variance of the conjugate Gamma prior distribution are $\lambda^E$ and $\lambda^E/r$, respectively.
+We interpret $r$ as the amount of prior information as $n_{j}$ represents the amount of observed information, which makes intuitive sense because the uncertainty of the conjugate prior distribution increases as $r$ decreases; in the limit of $r$ going to 0, the conjugate prior distribution gets flatter.
+The conditional posterior distribution of the random effect $\lambda_j$ for this Poisson-Gamma model is
 \begin{equation} \label{gammapost}
-\lambda_j\vert \boldsymbol{y}, r \stackrel{ind}{\sim}\textrm{Gamma}(r\lambda_{0} + n_{j}\bar{y}_{j}, r + n_j),\end{equation}
-where its posterior mean is $(1-B_{j})y_{j} + B_{j}\lambda_{0}$ and   $B_{j}\equiv r / (r+n_{j})$ for $j=1, 2, \ldots, k$.
-
-Note that the variance in (\ref{gammaprior}) is linear in the mean, whereas a slightly different Poisson-Gamma specification has been used elsewhere \citep{1997} that makes the variances in (\ref{gammaprior}) and (\ref{gammapost}) quadratic functions of the mean respectively .
+\lambda_j\vert r, \boldsymbol{y} \stackrel{indep.}{\sim}\textrm{Gamma}(r\lambda^E + n_j\bar{y}_{j},~ r + n_j),
+\end{equation}  
+whose $\bar{y}_j=y_j/n_j$. The mean and variance of the conditional posterior distribution are
+\begin{equation}\label{gammapost_mean_var}
+\lambda^\ast_j\equiv E(\lambda_j\vert r, \boldsymbol{y} )=(1-B_{j})\bar{y}_{j} + B_{j}\lambda^E~~\textrm{and}~~Var(\lambda_j\vert r, \boldsymbol{y})=\frac{\lambda^\ast_j}{r+n_j}.
+\end{equation}
+where $B_{j}\equiv r / (r+n_{j})$ for $j=1, 2, \ldots, k$.
+The conditional posterior mean is  a convex combination of the observed sufficient statistic $\bar{y}_{j} = y_j/n_j$ and the expected random effect  $\lambda^E$ weighted by the relative amount of information in the prior compared to the data, called a shrinkage factor $B_j=r / (r + n_j)$.
+If the conjugate prior distribution contains more information than the observed data have, \emph{i.e.}, ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the posterior mean shrinks  towards the prior mean by more than 50\%, borrowing more information from the prior distribution.
+
+Note that the conditional posterior variance in Equation \ref{gammapost_mean_var} is linear in the conditional posterior mean, whereas a slightly different Poisson-Gamma model specification has been used elsewhere \citep{morris1997} that makes the variances in the prior and conditional posterior distributions  quadratic functions of their means respectively.
 
@@
 The Binomial-Beta hierarchical model is the last model that \code{gbp} can fit.
-The notation $y_{j}$ is the number of successes (or failures) out of $n_{j}$ trials of the $j$-th group.
-Unlike the Poisson-Gamma model, the second-level mean is either known ($m=0$) or unknown ($m\ge1$) a priori.
+The notation $y_{j}$ is the number of successes (or failures) out of $n_{j}$ trials.
+Unlike the Poisson-Gamma model, the expected random effect is either known ($m=0$) or unknown ($m\ge1$) a priori.
 \begin{eqnarray}
 y_{j} \vert p_{j} &\stackrel{indep.}{\sim}& \textrm{Binomial}(n_{j}, ~p_{j}),\\
-p_{j} \vert \boldsymbol{\beta}, r &\stackrel{indep.}{\sim}&\textrm{Beta}(rp_{0j},~ r(1-p_{0j})),
+p_{j} \vert \boldsymbol{\beta}, r &\stackrel{indep.}{\sim}&\textrm{Beta}(rp^E_j,~ r(1-p^E_j)),
 \end{eqnarray}
 
-where $p_{0j}=\exp(\boldsymbol{x}_j^\top\boldsymbol{\beta})/(1+\exp(\boldsymbol{x}_j^\top\boldsymbol{\beta}))$ for $j=1, 2, \ldots, k$.
-The hyper-parameters $\boldsymbol{\beta}_{(m\times1)}$ and $r$ are unknown.
-Then the corresponding posterior distribution of random effect $j$ given  data, $\boldsymbol{\beta}_{(m\times1)}$, and $r$ is
+where $p^E_j\equiv E(p_j\vert \boldsymbol{\beta}, r)=\exp(\boldsymbol{x}_j^\top\boldsymbol{\beta})/(1+\exp(\boldsymbol{x}_j^\top\boldsymbol{\beta}))$ is the expected random effect  of group $j$ ($j=1, 2, \ldots, k$).
+The $m\times 1$ vector of the logistic regression coefficient $\boldsymbol{\beta}$ and the second-level variance component $r$ are unknown.
+The mean and variance of the conjugate Beta prior distribution for group $j$ are $p^E_j$ and $p^E_j(1-p^E_j)/(r+1)$, respectively.
+The resultant conditional posterior distribution of random effect $j$  is
 \begin{equation} \label{betapost}
-p_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}\bar{y}_{j},~r(1-p_{0j})+n_{j}(1-\bar{y}_{j})),
-\end{equation}
-where its posterior mean is $(1-B_{j})\bar{y}_{j}+B_{j}p_{0j}$, $B_{j}\equiv r/ (r+n_{j})$, and $\bar{y}_{j}\equiv y_{j} / n_{j}$.
-
-\subsection[Hyper-prior distribution]{Hyper-prior Distribution}
-A hyper-prior distribution is a distribution assigned to the second-level parameters.
-With the goal of objectivity in mind our choice for hyper-priors assumes the following non-informative distributions:
-\begin{equation}
-  \label{eq:hyper}
-\boldsymbol{\beta} \sim \textrm{Uniform on}~ \boldsymbol{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
-\end{equation}
-
-where $m$ is the number of regression coefficients.
-As for $\boldsymbol{\beta}$, the flat non-informative distribution above is a common choice to ensure good frequency properties.
-In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of random effects $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}.
-
-In the other two cases, Poisson and Binomial, the flat prior distribution on $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian.
-As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$), if any,  has full rank ($rank(X)=m$).
-
-The Poisson model with hyper-prior in (\ref{eq:hyper}) provides posterior propriety if there are two groups whose observed values exceed 0 and the second-level mean ($\lambda_0$) is known ($m=0$).
-However, if $\lambda_0$ is unknown $(m \geq 1)$ the posterior distribution for the Poisson model is improper with hyper-prior in (\ref{eq:hyper}) and this model should not be used.
-In cases where the Poisson model is used because it is an approximation to the Binomial, then we recommend staying with the Binomial model with the same hyper-prior distribution.
-The efficiency of these priors is explored in the examples in section 5.
-
-\section[Estimation]{Eestimation}\label{sec3}
-
-\subsection[Shrinkage estimation]{Shrinkage Estimation}
-Estimating the shrinkage factors ($B_1, \ldots, B_k$) is the key estimation problem with the hierarchical models \code{gbp} assumes.
-As we can see in (\ref{normalpost}), (\ref{gammapost}), and (\ref{betapost}), the posterior means are a linear function of the shrinkage factors ($B_{j}$) and the posterior variances are linear (Gaussian), quadratic (Poisson), and  approximately cubic (Binomial) functions of $B_{j}$.
-A natural method then to estimate $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$ is to first estimate the shrinkage factors.
-
-\subsection[ADM]{Approximation via adjustment for density maximization}\label{ADM}
-It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, i.e., $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
-A common approach to approximate the distribution of $B_{j}$ is to find its MLE $B_{j}(\hat{A}_{MLE})$ (or  $B_{j}(\hat{r}_{MLE})$) and to use its asymptotic Normality.
-This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $0 < B_{j} < 1$ and hence in small sample sizes this approximation can be quite flawed and can even result in point estimates lying on the boundary of the parameter space.
-
-To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of adjustment for density maximization (ADM) \citep{carl1988, 1997, tang2011}.
-For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, i.e.,  of $E(B_{j}\vert\boldsymbol{y})$ and $Var(B_{j}\vert\boldsymbol{y})$, where the notation $\boldsymbol{y}$ represents observed data, without the boundary issues that MLE encounters.
-See \cite{2011}.
-
-\subsection[Posterior moment estimation]{Posterior Moment Estimation}
-
-Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of the random effects given only the data ($\boldsymbol{y}$).
+p_{j}\vert  \boldsymbol{\beta}, r, \boldsymbol{y} \stackrel{indep.}{\sim}\textrm{Beta}(rp^E_j+n_{j}\bar{y}_{j},~r(1-p^E_j)+n_{j}(1-\bar{y}_{j})),
+\end{equation}
+whose $\bar{y}_j=y_j/n_j$ is the observed proportion of group $j$. The mean and variance of the conditional posterior distribution are
+\begin{equation}\label{betapost_mean_var}
+p_j^\ast\equiv E(p_j\vert \boldsymbol{\beta}, r, \boldsymbol{y} )=(1-B_{j})\bar{y}_{j} + B_{j}p^E_j~~\textrm{and}~~Var(p_j\vert  \boldsymbol{\beta}, r,  \boldsymbol{y})=\frac{p_j^\ast(1-p_j^\ast)}{r+n_j+1}.
+\end{equation}
+The conditional posterior mean is  a convex combination of the observed sufficient statistic $\bar{y}_{j} = y_j/n_j$ and the expected random effect  $p^E_j$ weighted by the relative amount of information in the prior compared to the data (a shrinkage factor) $B_j\equiv r / (r + n_j)$ like the Poisson-Gamma model.
+If the conjugate prior distribution contains more information than the observed distribution does ($r>n_j$), then the resulting conditional posterior mean shrinks towards the expected random effect by more than 50\%.
+
+\subsection[Hyper-prior distributions]{Hyper-prior Distribution}
+Hyper-prior distributions are the distributions assigned to the second-level parameters called hyper-parameters. With the goal of objectivity in mind, our choice for the hyper-prior distributions is
+\begin{equation}\label{eq:hyper}
+\boldsymbol{\beta} \sim \textrm{Uniform on}~ \textbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
+\end{equation}
+
+where $m$ is the number of the regression coefficients to be estimated.
+The improper flat hyper-prior distribution on $\boldsymbol{\beta}$ is a common non-informative choice.
+In the Gaussian case, the flat hyper-prior distribution on the second-level variance $A$ produces good repeated sampling coverage properties of the Bayesian interval estimates for the random effects.
+The resulting full posterior distribution of the random effects and hyper-parameters is proper if $k\ge m+3$ \citep{tang2011, kelly2014advances}.
+% The improper uniform distribution on the second-level variance component over the positive real line is to ensure good frequency properties.
+
+In the other two cases, Poisson-Gamma and Binomial-Beta, the flat prior distribution on $1/r$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian case.
+The resultant full posterior distribution of random effects and hyper-parameters for the Binomial case is data-dependent.
+Let's define an ``interior group'' as the group whose number of successes $y_j$ are neither 0 nor $n_j$ and $k_y$ as the number of interior groups among the entire $k$ groups.
+Then, the full posterior distribution of random effects and hyper-parameters is proper if and only if there are at least two interior groups in the data and the $k_y\times m$ covariate matrix of the interior groups is of full rank $m$ \citep{tak2016propriety}.
+
+The Poisson-Gamma model with the hyper-prior distributions in Equation \ref{eq:hyper} provides posterior propriety if and only if there are at least two groups whose observed values $y_j$ are non-zero  and the expected random effect $\lambda^E$ is a completely known constant ($m=0$).
+If the expected random effect is unknown a priori,  then we recommend staying with the Binomial-Beta model with the same hyper-prior distributions because the Poisson-Gamma model is actually an approximation to the Binomial-Beta model.
+
+\section[Estimation]{Inference via the adjustment for density maximization}\label{sec3}
+
+Obtaining point and interval estimates of each random effect is our primary inferential interest.
+The approximate Bayesian tool assumes that the unconditional posterior distribution of each random effect follows a skewed-Normal distribution for the Gaussian case,  a Gamma distribution for the Poisson case, or a Beta distribution for the Binomial case whose parameters are matched to the estimated unconditional posterior moments of each random effect.
+We use these assumed unconditional posterior distributions to make point and interval estimates of each random effect.
+
+We illustrate our estimation procedure equipped with the adjustment for density maximization (hereafter ADM) \citep{carl1988, morris1997, tang2011}, a distributional approximation to a Pearson family distribution via derivatives, using the Binomial and Poisson hierarchical models.
+The ADM procedure for the Gaussian hierarchical model used in  \pkg{Rgbp} has been well-documented in \cite{kelly2014advances}.
+
+\subsection[Inference]{The inferential model}\label{inference}
+
+The likelihood function of hyper-parameters $r$ ($A$ for the Gaussian model) and $\boldsymbol{\beta}$ for the Binomial hierarchical model is derived from the independent Beta-Binomial marginal distributions of the observed data with random effects integrated out \citep{skellam1948}.
+%For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
+\begin{equation}\label{marginal_binomial}
+L(r, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k f(y_j\vert r, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k\binom{n_j}{y_j}\frac{B(y_j+rp^E_j, ~n_j-y_j+r(1-p^E_j))}{B(rp^E_j, ~r(1-p^E_j))},
+\end{equation}
+where the notation $B(a, b)~(\equiv\int_0^1 v^{a-1}(1-v)^{b-1}dv)$ indicates a beta function for positive constants $a$ and $b$.
+Similarly, the likelihood function of $r$ for the Poisson hierarchical model comes from the independent Negative-Binomial marginal distributions of the observed data with the random effects integrated out;
+\begin{equation}\label{marginal_poisson}
+L(r)=\prod_{j=1}^k f(y_j\vert r)=\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E+y_j)}{\Gamma(r\lambda^E)(y_j!)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E}.
+\end{equation}
+
+%If all the observed data are extreme, i.e., $y_j$ is either 0 or $n_j$ for all $j$, the likelihood becomes a decreasing function with respect to $r$ for finite values of $\boldsymbol{\beta}$.
+In this case, the MLE of $r$ is 0.
+
+The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial hierarchical model is proportional to their likelihood functions in Equation \ref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in Equation \ref{eq:hyper} as follows;
+\begin{equation}\label{marginal_post}
+f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L(r, \boldsymbol{\boldsymbol{\beta}})d\boldsymbol{\beta}dr/r^2.
+\end{equation}
+The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in Equation \ref{marginal_poisson} times the hyper-prior density function of $r$, $dr/r^2$;
+\begin{equation}\label{marginal_post}
+f(r \vert \boldsymbol{y})\propto L(r)dr/r^2.
+\end{equation}
+
+Our goal is to obtain the point and interval estimates of the random effects from their unconditional posterior distributions; for the Binomial case, 
+\begin{equation}\label{mcintegration}
+f(\boldsymbol{p}\vert \boldsymbol{y})=\int  f(\boldsymbol{p}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\cdot f(r, \boldsymbol{\beta}\vert \boldsymbol{y})dr d\boldsymbol{\beta},
+\end{equation}
+and for the Poisson case, 
+\begin{equation}\label{mcintegration}
+f(\boldsymbol{\lambda}\vert \boldsymbol{y})=\int  f(\boldsymbol{\lambda}\vert r, \boldsymbol{y})\cdot f(r\vert \boldsymbol{y})dr.
+\end{equation}
+
+\subsection[shrinkage]{Estimation for shrinkage factors and expected random effects}\label{shrinkage}
+
+Obtaining the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$, and those of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ (or $\lambda^E$ for the Poisson model), is the most important estimation problem for the hierarchical models that \code{gbp} assumes.
+This is because these unconditional posterior moments are used to calculate the unconditional posterior moments of the random effects, $p_1, p_2, \ldots, p_k$ (or $\lambda_1, \lambda_2, \ldots, \lambda_k$ for the Poisson model).
+Taking the Binomial-Beta model as an example, with the assumption that hyper-parameters $r$ (or $A$ for the Gaussian model) and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ of the Binomial hierarchical model are
+\begin{eqnarray}
+E(p_{j}\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})E(p^E_{j}\vert  \boldsymbol{y})\label{postmean} \\
+~~~~~~Var(p_{j}\vert \boldsymbol{y}) &=&  E(Var(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+Var(E(p_{j}\vert r, \boldsymbol{\beta},\boldsymbol{y})\vert \boldsymbol{y})\label{postvar}\\
+&=& E\big(p^{\ast}_{j}(1-p^{\ast}_{j})/ (r+n_{j}+1)\vert  \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big) \\
+&\approx&E\big(p^{\ast}_{j}(1-p^{\ast}_{j})(1-\textrm{B}_{j})/n_{i}\vert \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big)\\
+&=&g(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}), E(B^3_j\vert\boldsymbol{y}),  E(p^E_{j}\vert\boldsymbol{y}), E((p^E_{j})^2\vert\boldsymbol{y})).\label{approximate_var}
+\end{eqnarray}
+Note that the unconditional posterior mean and approximate variance of random effect $j$ in Equation \ref{postmean}  and \ref{approximate_var}  are functions of the unconditional posterior moments of shrinkage factors and expected random effects.
+We specify the function $g$ in Equation \ref{approximate_var} in Appendix \ref{apppostvar}.
+
+We assumed that hyper-parameters $r$ and  $\boldsymbol{\beta}$ were independent a posteriori, considering that they are independent a posteriori in the limit of $k$ going to infinity  because they are asymptotically Normally distributed.
+%Also, \cite{morris1997} used the Poisson model empirically showed that their covariance in observed information matrix of the Poisson-Gamma model was close to 0 in a small sample setting.
+
+For the Poisson model, the unconditional posterior mean and variance of random effect $j$ are
+\begin{eqnarray}
+E(\lambda_j\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})E(\lambda^E\vert  \boldsymbol{y})\label{postmean_poisson} \\
+~~~~~~Var(\lambda_{j}\vert \boldsymbol{y}) &=&  E(Var(p_{j}\vert r,  \boldsymbol{y})\vert \boldsymbol{y})+Var(E(\lambda_{j}\vert r, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_poisson}\\
+&=& E\big(\lambda^{\ast}_{j}/ (r+n_{j})\vert  \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-\lambda^E_{j})\vert \boldsymbol{y}\big) \\
+&=&h(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}) ).\label{approximate_var_poisson}
+\end{eqnarray}
+We specify the function $h$ in Equation \ref{approximate_var_poisson} in Appendix \ref{apppostvar_poisson}.
+%conditional posterior means of  random effect $j$ in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are a linear function of the shrinkage factor $B_{j}$ and the conditional posterior variances in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are linear (Gaussian), quadratic (Poisson), and  approximately cubic (Binomial) functions of $B_{j}$, considering $r+n_j=n_j/(1-B_j)$.
+Thus, the unconditional posterior mean and variance of the random effect are the functions of the unconditional posterior moments of the shrinkage factors.
+
+Next, we estimate the unconditional posterior moments of the shrinkage factors and expected random effects after approximating their unconditional posterior distributions by Beta distributions via the ADM.
+
+\subsubsection{Unconditional posterior moments of shrinkage factors.}  It is noted that  the shrinkage factors ($B_1, \ldots B_k$) are a function of $r$, i.e., $B_{j}= r/(r+n_{j})=B_{j}(r)$.
+One way to approximate the distribution of $B_{j}$ is to find the maximum likelihood estimate of $r$, $\hat{r}_{MLE}$, with its Hessian value and to use a Delta method for an asymptotic Normal distribution of $B_{j}(\hat{r}_{MLE})$.
+This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $B_{j}$ lies on the unit interval between 0 and 1, and hence in small sample sizes this approximation can be quite flawed and can even result in point estimates lying on the boundary of the parameter space \citep{tang2011}.
+
+To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of the ADM \citep{carl1988, morris1997, tang2011}.
+The ADM approximates the distribution of the function of the parameter of interest by one of the Pearson family distributions using the first two derivatives as the MLE with the Delta method does.
+For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, i.e.,  of $E(B_{j}\vert\boldsymbol{y})$ and $Var(B_{j}\vert\boldsymbol{y})$.
+\citet{morris1997} showed that the Beta approximation for the shrinkage factors worked better than Normal approximation in Poisson-Gamma multilevel modeling when the sample size was small, and \citet{tang2011} showed that  in Normal-Normal hierarchical modeling.
+
+The ADM assumes the shrinkage factors follow Beta distributions a posteriori as
+\begin{equation}\label{admshrinkage}
+B_j\vert\boldsymbol{y}\sim Beta(a_{1j}, a_{0j}), ~\textrm{for}~j=1, 2, \ldots, k,
+\end{equation}
+%The estimated Beta distribution with the estimates $\hat{a}_{1j}$ and $\hat{a}_{0j}$ will be used to approximate the posterior moments of the shrinkage factors. 
+% and $h(B_j)=\log(H(B_j))$Hessian
+%whose mean and variance are estimated via two derivatives of an adjusted posterior density and %matched to the two parameters of the Beta distribution, $a_{1j}$ and $a_{0j}$.
+
+Note that the mean of Beta distribution $a_{1j}/(a_{1j}+a_{0j})$ is not the same as its mode $(a_{j1}-1)/(a_{j1}+a_{j0}-2)$.
+ADM works on an adjusted posterior distribution $A(B_j\vert \boldsymbol{y})dB_j\propto B_j(1-B_j)f(B_j\vert \boldsymbol{y})dB_j$ so that its mode is the same as the mean of the original Beta distribution.
+The assumed posterior mean and variance of shrinkage factor are
+\begin{eqnarray}
+E(B_j\vert\boldsymbol{y})&=&\frac{a_{1j}}{a_{1j}+a_{0j}}=\argmax_{B_j}~ A(B_j\vert \boldsymbol{y})\equiv B^\ast_j,\label{admmean}\\
+Var(B_j\vert\boldsymbol{y})&=&\frac{B^\ast_j(1-B^\ast_j)}{a_{1j}+a_{0j}+1}=\frac{B^\ast_j(1-B^\ast_j)}{B^\ast_j(1-B^\ast_j)[-\frac{d^2}{dB^2_j}\log(A(B_j\vert \boldsymbol{y}))\vert_{B_j=B^\ast_j}] +1}.\label{admvar}
+\end{eqnarray}
+
+ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \cite{berger1999integrated} for the integrated likelihood in detail.
+Considering that Equation \ref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on $\alpha=-log(r)$ scale because the distribution of $\alpha$ is more symmetric than that of $r$ and $\alpha$ is defined on a real line without any boundary issues.
+Since $A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto e^\alpha L(\alpha)$, the estimated posterior mean in Equation \ref{admmean} is
+\begin{equation}\label{meaninvariance}
+\hat{B}^\ast_j=exp(-\hat{\alpha})/(n_j+exp(-\hat{\alpha})),
+\end{equation}
+
+%This is because the marginal posterior distribution of the shrinkage factor, $p(B_j\vert\boldsymbol{y})dB_j \propto L(B_j)dB_j/B^2_j$ can be obtained via its variable transformation.
+
+in which $\hat{\alpha}$ is the mode of $f(\alpha\vert\boldsymbol{y})$, \emph{i.e.}, $\argmax_{\alpha}\{\alpha+\log(L(\alpha))\}$ .
+%Next, a variable transformation gives us .
+
+We need the invariance information \citep{tang2011} to estimate the variance in Equation \ref{admvar}, which is defined as 
+\begin{eqnarray}
+\textrm{inv.info} &\equiv& -\frac{d^2 \log(A(B_j\vert \boldsymbol{y}))}{d[logit(B_j)]^2}\bigg\vert_{B_j=\hat{B}^\ast_j}=-\frac{d^2 \log(A(B_j(r)\vert \boldsymbol{y}))}{d[\log(r)]^2}\bigg\vert_{r=\hat{r}}\label{invariance}\\
+&=& -\frac{d^2 \log(A(B_j(r(\alpha))\vert \boldsymbol{y}))}{d\alpha^2}\bigg\vert_{\alpha=\hat{\alpha}}\nonumber
+\end{eqnarray}
+
+Note that this invariance information is  the negative Hessian value of $\alpha+\log(L(\alpha))$ at the mode $\hat{\alpha}$.
+Using the invariance information, we  estimate the posterior variance in Equation \ref{admvar} as
+\begin{equation}\label{varianceinvariance}
+\widehat{Var}(B_j\vert\boldsymbol{y})=\frac{\hat{B}^{\ast2}_j(1-\hat{B}^\ast_j)^2}{inv.info +\hat{B}^\ast_j(1-\hat{B}^\ast_j)}.
+\end{equation}
+
+After matching the unconditional posterior mean and variance of shrinkage factor $j$ in Equation \ref{meaninvariance} and \ref{varianceinvariance} to the two parameters of the Beta distribution in Equation \ref{admshrinkage}, i.e., $a_{1j}$ and $a_{0j}$, we get their estimates as
+\begin{equation}\label{admpara}
+\hat{a}_{1j}=\textrm{inv.info}/(1-\hat{B}^\ast_j)~~\textrm{and}~~\hat{a}_{0j}=\textrm{inv.info}/\hat{B}^\ast_j.
+\end{equation}
+
+The moments of the Beta distribution are well defined as a function of $a_{1j}$ and $a_{0j}$; $E(B^c_j\vert\boldsymbol{y})=B(a_{1j} + c, a_{0j})/B(a_{1j}, a_{0j})$ for $c\ge0$. Their estimates are 
+\begin{equation}\label{shrinkagemoments}
+\widehat{E}(B^c_j\vert\boldsymbol{y})= B(\hat{a}_{1j} + c, \hat{a}_{0j})/B(\hat{a}_{1j}, \hat{a}_{0j}),
+\end{equation}
+
+and the approximation gets better if the true posterior distribution of the shrinkage factor is closer to the Beta distribution.
+
+\subsubsection{Unconditional posterior moments of expected random effects for the Binomial model.}
+We approximate the unconditional posterior distribution of each expected random effect by the Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ \citep{carl1988}.
+A motivation is that the moments of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involve an intractable integration such as
+\begin{equation}\label{priormoment1}
+E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{e^{x_j^\top\beta}}{1+e^{x_j^\top\beta}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{e^{x_j^\top\beta}}{1+e^{x_j^\top\beta}}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\beta
+\end{equation}
+
+Considering that the expected random effects are a function of logistic regression coefficients $\boldsymbol{\beta}$, we can use the Delta method for the asymptotic Normal distribution of $p^E_{j}(\hat{\beta}_{MLE})$.
+However, the Normal approximation goes through the same support and boundary issues as the shrinkage factors do.
+Instead, we approximate the posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ by a Beta distribution using $\hat{\beta}_{MLE}$ and the Hessian value at the MLE.
+
+We assume the expected random effect has a Beta distribution a posteriori as follows;
+\begin{equation}\label{admpriormean}
+p^E_{j}\vert\hat{\alpha}, \boldsymbol{y}=\frac{e^{x_j^\top\beta}}{1+e^{x_j^\top\beta}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\sim \textrm{Beta}(b_{1j}, b_{0j})\sim \frac{G(b_{1j})}{G(b_{1j})+G(b_{0j})},
+\end{equation}
+
+where $G(b_{1j})$ is a random variable following a Gamma$(b_{1j}, 1)$ distribution with a unit scale and independently $G(b_{0j})$ has a Gamma($b_{0j}, 1)$ distribution.
+Note that the representation in Equation (\ref{admpriormean}) is equivalent to saying $e^{x_j^\top\beta}\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables.
+Its mean and variance are
+\begin{eqnarray}
+E(e^{x_j^\top\beta}\vert\hat{\alpha}, \boldsymbol{y})&=&E\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{b_{1j}}{b_{0j}-1}\equiv\eta_j,\label{priormean1}\\
+~~~~~Var(e^{x_j^\top\beta}\vert\hat{\alpha}, \boldsymbol{y})&=&Var\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{\eta_j(1+\eta_j)}{b_{0j}-2}.\label{priorvariance1}
+\end{eqnarray}
+
+In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ follows $N[\hat{\beta}, \hat{\Sigma}]$, where $\hat{\beta}$ is the mode of $p(\beta\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode.
+Then the posterior distribution of $x_j^\top\beta$ is also Normal with mean $x_j^\top\hat{\beta}$ and variance $x_j^\top\hat{\Sigma} x_j$.
+
+Using the property of the log-Normal distribution, we get the estimates of posterior mean and variance in Equation (\ref{priormean1}) and (\ref{priorvariance1}) as
+\begin{eqnarray}
+\eta^\ast_j&=&e^{x_j^\top\hat{\beta}+x_j^\top\hat{\Sigma} x_j/2},\label{priormean2}\\
+~~~~~\widehat{Var}(e^{x_j^\top\beta}\vert\boldsymbol{y})&=&\eta^{\ast 2}_j\big(e^{x_j^{T}\hat{\Sigma} x_j}-1\big).\label{priorvariance2}
+\end{eqnarray}
+
+By matching the estimated mean and variance in Equation (\ref{priormean2}) and (\ref{priorvariance2}) to $b_{1j}$ and $b_{0j}$ in Equation (\ref{priormean1}) and (\ref{priorvariance1}), we obtain the estimates of $b_{1j}$ and $b_{0j}$ as follows;
+\begin{equation}\label{priormeanpara}
+\hat{b}_{1j}=\eta^\ast_j+\frac{\eta^\ast_j + 1}{e^{x_j^{T}\hat{\Sigma} x_j}-1}~~\textrm{and}~~\hat{b}_{0j}=\frac{\eta^\ast_j + 1}{\eta^\ast_j(e^{x_j^{T}\hat{\Sigma} x_j}-1)}+2.
+\end{equation}
+
+The unconditional posterior moments of expected random effects can be estimated similarly to those of shrinkage factors; since $E((p^E_{j})^d\vert\boldsymbol{y})=B(b_{1j} + d, b_{0j})/B(b_{1j}, b_{0j})$ for $d\ge0$,
+\begin{equation}\label{priormeanmoments}
+\widehat{E}((p^E_{j})^d\vert\boldsymbol{y})= B(\hat{b}_{1j} + d, \hat{b}_{0j})/B(\hat{b}_{1j}, \hat{b}_{0j}).
+\end{equation}
+
+%Considering the histogram in the middle of Fig \ref{fig2},  we can see that the ADM approximation (density line) to 20,000 posterior samples of $p_{01}$ obtained via grid-sampling based on 18 baseball data look satisfactory.
+
+\subsection{Estimation for random effects}
+It is intractable to derive the unconditional posterior distribution of each random effect analytically for both Binomial and Poisson models.
+Instead, we again assume that each random effect of the Binomial model has a Beta distribution as
+\begin{equation}\label{truebeta}
+p_j\vert \boldsymbol{y} \sim \textrm{Beta}(t_{1j}, t_{0j}),~\textrm{for}~ j=1, 2, \ldots, k,
+\end{equation}
+and each random effect of the Poisson model has a Gamma distribution as
+\begin{equation}\label{truebeta_poisson}
+\lambda_j\vert \boldsymbol{y} \sim \textrm{Gamma}(s_{1j}, s_{0j}),~\textrm{for}~ j=1, 2, \ldots, k.
+\end{equation}
+
+The unconditional posterior mean and variance for the Binomial model specified in Equation \ref{postmean} and \ref{approximate_var} and those for the Poisson model in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}  are functions of the unconditional posterior moments of shrinkage factors and expected random effect.
+Once we plug-in the estimated unconditional posterior moments of shrinkage factors in Equation \ref{shrinkagemoments} and those of expected random effect in Equation \ref{priormeanmoments}, we get the estimates of the mean and variance in Equation \ref{postmean}  and \ref{postvar}, i.e., $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
+For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimates of the mean and variance in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}.
+The estimates of two parameters $t_{1j}$ and $t_{0j}$ in Equation \ref{truebeta} come as follows;
+\begin{equation}\label{posttrueprob}
+\hat{t}_{1j}=\bigg(\frac{\hat{\mu}_{p_j}(1-\hat{\mu}_{p_j})}{\hat{\sigma}^2_{p_j}}-1\bigg)\hat{\mu}_{p_j},~\textrm{and}~~\hat{t}_{0j}=\bigg(\frac{\hat{\mu}_{p_j}(1-\hat{\mu}_{p_j})}{\hat{\sigma}^2_{p_j}}-1\bigg)(1-\hat{\mu}_{p_j}).
+\end{equation}
+The estimates of two parameters $s_{1j}$ and $s_{0j}$ in Equation \ref{truebeta_poisson} are
+\begin{equation}\label{posttrueprob}
+\hat{s}_{1j}=\frac{\hat{\mu}_{\lambda_j}^2}{\hat{\sigma}^2_{\lambda_j}},~\textrm{and}~~\hat{s}_{0j}=\frac{\hat{\mu}_{\lambda_j}}{\hat{\sigma}^2_{\lambda_j}}.
+\end{equation}
+
+Finally, the approximate posterior distribution of random effect $j$ for the Binomial model is
+\begin{equation}\label{trueapprox}
+p_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{Beta}(\hat{t}_{1j}, \hat{t}_{0j}),
+\end{equation}
+and that for the Poisson model is
+\begin{equation}\label{trueapprox_poisson}
+\lambda_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{Gamma}(\hat{s}_{1j}, \hat{s}_{0j}).
+\end{equation}
+
+The ADM approximation is accurate if the true distribution of $p_j$ is close to the the Beta distribution \citep{tang2011, morris2012}.
+
+%The histogram on the right in Fig \ref{fig2} shows the ADM approximation to the 20,000 posterior samples of the true probability of the first player $p_1$ obtained via grid-sampling.
+In this case, the  approximation by the Beta distribution was not complete enough to catch the right-skewness of posterior distribution, the effect called the regression towards the mean.
+See section \ref{baseballex} for detailed analysis.
+
+%\subsection[ADM]{The adjustment for density maximization}\label{ADM}
+
+%\subsection[Posterior moment estimation]{Posterior Moment Estimation}
+
+%Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of the random effects given only the data ($\boldsymbol{y}$).
 Taking the Normal-Normal model as an example, it estimates $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$ by the following identities
-\begin{eqnarray}
-E(\mu_{j}\vert \boldsymbol{y}) & = & E(E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y}), \\
-Var(\mu_{j}\vert \boldsymbol{y}) & = & E(Var(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y})+Var(E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y}),
-\end{eqnarray}  
-where both $E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)$ and $Var(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}).
+%\begin{eqnarray}
+%E(\mu_{j}\vert \boldsymbol{y}) & = & E(E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y}), \\
+%Var(\mu_{j}\vert \boldsymbol{y}) & = & E(Var(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y})+Var(E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y}),
+%\end{eqnarray}  
+%where both $E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)$ and $Var(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}).
 We then estimate $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$ by plugging-in the approximately estimated two posterior moments of shrinkage factors.
 
-\subsection[Approximation to posterior distribution by moment matching]{Approximation to Posterior Distribution via Matching Moments}
-After estimating the two posterior moments, for example $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$, \code{gbp} approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
+%\subsection[Approximation to posterior distribution by moment matching]{Approximation to Posterior Distribution via Matching Moments}
+%After estimating the two posterior moments, for example $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$, \code{gbp} approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
 For the Normal-Normal model we actually estimate the first three moments and approximate $\pi(\mu_{j}\vert \boldsymbol{y})$ with a skewed-Normal distribution \citep{sn2013}.
@@
 
-\section[packageoverview]{Main Functions in \pkg{Rgbp}}\label{sec5}
+\section[packageoverview]{Usage of functions in \pkg{Rgbp}}\label{sec5}
 
@@
 
+\appendix
+\section{Unconditional posterior variance of the Binomial model}\label{apppostvar}
+
+\section{Unconditional posterior variance of the Poisson model}\label{apppostvar_poisson}
+
 \bibliography{bibliography}

### 2015-06-07 jss/article_v2.tex
package and paper

@@
 
-We illustrate our estimation procedure equipped with the adjustment for density maximization (hereafter ADM) \citep{carl1988, morris1997, tang2011}, a distributional approximation to a Pearson family distribution via derivatives, using the Binomial and Poisson hierarchical models.
-The ADM procedure for the Gaussian hierarchical model used in  \pkg{Rgbp} has been well-documented in \cite{kelly2014advances}.
+We illustrate our estimation procedure equipped with the adjustment for density maximization (hereafter ADM) \citep{carl1988, morris1997, tang2011}, a way to  approximate a distribution of the parameter of interest by one of Pearson family distributions based on derivatives like the Delta method, using the Binomial and Poisson hierarchical models.
+The ADM procedure for the Gaussian hierarchical model adopted in  \pkg{Rgbp} has been well-documented in \cite{kelly2014advances}.
 
@@
 
-Obtaining the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$, and those of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ (or $\lambda^E$ for the Poisson model), is the most important estimation problem for the hierarchical models that \code{gbp} assumes.
-This is because these unconditional posterior moments are used to calculate the unconditional posterior moments of the random effects, $p_1, p_2, \ldots, p_k$ (or $\lambda_1, \lambda_2, \ldots, \lambda_k$ for the Poisson model).
-Taking the Binomial-Beta model as an example, with the assumption that hyper-parameters $r$ (or $A$ for the Gaussian model) and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ of the Binomial hierarchical model are
+Estimating the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$, and the conditional posterior moments of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ (or $\lambda^E$ for the Poisson model), is the most important estimation problem for the hierarchical models that \code{gbp} assumes.
+This is because these moment estimates are used to approximate the unconditional posterior moments of the random effects, $p_1, p_2, \ldots, p_k$ (or $\lambda_1, \lambda_2, \ldots, \lambda_k$ for the Poisson model).
+Taking the Binomial-Beta model as an example, with the assumption that hyper-parameters $r$ (or $A$ for the Gaussian model) and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ are
 \begin{eqnarray}
@@
 We assumed that hyper-parameters $r$ and  $\boldsymbol{\beta}$ were independent a posteriori, considering that they are independent a posteriori in the limit of $k$ going to infinity  because they are asymptotically Normally distributed.
-%Also, \cite{morris1997} used the Poisson model empirically showed that their covariance in observed information matrix of the Poisson-Gamma model was close to 0 in a small sample setting.
+Also, \cite{morris1997}  empirically showed that their covariance from the observed information matrix of the Poisson-Gamma model, though with a different parametrization, was close to 0 in a small sample setting.
 
@@
 \begin{eqnarray}
-E(\lambda_j\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})E(\lambda^E\vert  \boldsymbol{y})\label{postmean_poisson} \\
+E(\lambda_j\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})\lambda^E\label{postmean_poisson} \\
 ~~~~~~Var(\lambda_{j}\vert \boldsymbol{y}) &=&  E(Var(p_{j}\vert r,  \boldsymbol{y})\vert \boldsymbol{y})+Var(E(\lambda_{j}\vert r, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_poisson}\\
@@
 \end{eqnarray}
+The unconditional posterior mean and variance of random effect $j$ under the Poisson model are also functions of the unconditional posterior moments of the shrinkage factors.
 We specify the function $h$ in Equation \ref{approximate_var_poisson} in Appendix \ref{apppostvar_poisson}.
@@
 One way to approximate the distribution of $B_{j}$ is to find the maximum likelihood estimate of $r$, $\hat{r}_{MLE}$, with its Hessian value and to use a Delta method for an asymptotic Normal distribution of $B_{j}(\hat{r}_{MLE})$.
-This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $B_{j}$ lies on the unit interval between 0 and 1, and hence in small sample sizes this approximation can be quite flawed and can even result in point estimates lying on the boundary of the parameter space \citep{tang2011}.
+This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $B_{j}$ lies on the unit interval between 0 and 1, and hence in small sample sizes this approximation can be quite flawed and can even result in point estimates lying on the boundary of the parameter space, from which the restricted MLE procedure sometimes suffers \citep{tang2011, kelly2014advances}.
 
 To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of the ADM \citep{carl1988, morris1997, tang2011}.
-The ADM approximates the distribution of the function of the parameter of interest by one of the Pearson family distributions using the first two derivatives as the MLE with the Delta method does.
-For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, i.e.,  of $E(B_{j}\vert\boldsymbol{y})$ and $Var(B_{j}\vert\boldsymbol{y})$.
-\citet{morris1997} showed that the Beta approximation for the shrinkage factors worked better than Normal approximation in Poisson-Gamma multilevel modeling when the sample size was small, and \citet{tang2011} showed that  in Normal-Normal hierarchical modeling.
-
-The ADM assumes the shrinkage factors follow Beta distributions a posteriori as
+The ADM approximates the distribution of the function of the parameter of interest by one of the Pearson family distributions using the first two derivatives as the Delta method does; the Delta method is a special case of the ADM based on the Normal distribution.
+For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, i.e.,  of $E(B_{j}^c\vert\boldsymbol{y})$ for $c\ge0$.
+\citet{morris1997} showed that the Beta approximation for the shrinkage factors worked better than Normal approximation using the Poisson hierarchical model when the sample size was small, and \citet{tang2011} showed that  using the Normal hierarchical model.
+
+The ADM assumes that the shrinkage factors follow Beta distributions a posteriori as
 \begin{equation}\label{admshrinkage}
@@
 \end{equation}
+and the ADM estimates the two parameters of the Beta distribution, i.e., $a_{1j}$ and $a_{0j}$.
 %The estimated Beta distribution with the estimates $\hat{a}_{1j}$ and $\hat{a}_{0j}$ will be used to approximate the posterior moments of the shrinkage factors. 
@@
 ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \cite{berger1999integrated} for the integrated likelihood in detail.
-Considering that Equation \ref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on $\alpha=-log(r)$ scale because the distribution of $\alpha$ is more symmetric than that of $r$ and $\alpha$ is defined on a real line without any boundary issues.
+Considering that Equation \ref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-log(r)$, because the distribution of $\alpha$ is more symmetric than that of $r$ and $\alpha$ is defined on a real line without any boundary issues.
 Since $A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto e^\alpha L(\alpha)$, the estimated posterior mean in Equation \ref{admmean} is
 \begin{equation}\label{meaninvariance}
-\hat{B}^\ast_j=exp(-\hat{\alpha})/(n_j+exp(-\hat{\alpha})),
+\hat{B}^\ast_j=\frac{e^{-\hat{\alpha}}}{n_j+e^{-\hat{\alpha}}},
 \end{equation}
@@
 
-After matching the unconditional posterior mean and variance of shrinkage factor $j$ in Equation \ref{meaninvariance} and \ref{varianceinvariance} to the two parameters of the Beta distribution in Equation \ref{admshrinkage}, i.e., $a_{1j}$ and $a_{0j}$, we get their estimates as
+After matching the estimated unconditional posterior mean and variance of shrinkage factor $j$ in Equation \ref{meaninvariance} and \ref{varianceinvariance} to the two parameters of the Beta distribution in Equation \ref{admshrinkage}, i.e., $a_{1j}$ and $a_{0j}$, we get their estimates as
 \begin{equation}\label{admpara}
-\hat{a}_{1j}=\textrm{inv.info}/(1-\hat{B}^\ast_j)~~\textrm{and}~~\hat{a}_{0j}=\textrm{inv.info}/\hat{B}^\ast_j.
+\hat{a}_{1j}=\frac{\textrm{inv.info}}{1-\hat{B}^\ast_j}~~\textrm{and}~~\hat{a}_{0j}=\frac{\textrm{inv.info}}{\hat{B}^\ast_j}.
 \end{equation}
@@
 \begin{equation}\label{shrinkagemoments}
-\widehat{E}(B^c_j\vert\boldsymbol{y})= B(\hat{a}_{1j} + c, \hat{a}_{0j})/B(\hat{a}_{1j}, \hat{a}_{0j}),
-\end{equation}
-
-and the approximation gets better if the true posterior distribution of the shrinkage factor is closer to the Beta distribution.
+\widehat{E}(B^c_j\vert\boldsymbol{y})= \frac{B(\hat{a}_{1j} + c, \hat{a}_{0j})}{B(\hat{a}_{1j}, \hat{a}_{0j})},
+\end{equation}
+
+and the approximation gets better if the true posterior distribution of the shrinkage factor is closer to the Beta distribution \citep{morris1997, tang2011, morris2012}.
 
 \subsubsection{Unconditional posterior moments of expected random effects for the Binomial model.}
-We approximate the unconditional posterior distribution of each expected random effect by the Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ \citep{carl1988}.
-A motivation is that the moments of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involve an intractable integration such as
+We assume that the conditional posterior distribution of each expected random effect given $\hat{\alpha}$ follows a Beta distribution, and estimate the assumed Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$.
+We estimate the conditional posterior moments of the expected random effects and treat them as their estimated unconditional posterior moments obtained by the (Laplace) approximate marginal likelihood function of $\boldsymbol{\beta}$.
+We found that the conditional and unconditional posterior moment estimates were almost identical due to their small covariance between $r$ and $\boldsymbol{\beta}$ in the observed information matrix.
+In addition, calculating the conditional posterior moments was computationally less burdensome.
+
+The moments of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involve an intractable integration. For example, the first conditional posterior moment is
 \begin{equation}\label{priormoment1}
-E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{e^{x_j^\top\beta}}{1+e^{x_j^\top\beta}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{e^{x_j^\top\beta}}{1+e^{x_j^\top\beta}}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\beta
-\end{equation}
-
-Considering that the expected random effects are a function of logistic regression coefficients $\boldsymbol{\beta}$, we can use the Delta method for the asymptotic Normal distribution of $p^E_{j}(\hat{\beta}_{MLE})$.
+E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\boldsymbol{\beta}.
+\end{equation}
+
+Considering that the expected random effects are a function of logistic regression coefficients $\boldsymbol{\beta}$, we can use the Delta method for the asymptotic Normal distribution of $p^E_{j}(\hat{\boldsymbol{\beta}}_{MLE})$.
 However, the Normal approximation goes through the same support and boundary issues as the shrinkage factors do.
-Instead, we approximate the posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ by a Beta distribution using $\hat{\beta}_{MLE}$ and the Hessian value at the MLE.
-
-We assume the expected random effect has a Beta distribution a posteriori as follows;
+Instead, we approximate the conditional posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ by a Beta distribution using $\hat{\beta}_{MLE}$ and the Hessian value at the MLE.
+
+We assume the conditional posterior distribution of expected random effect $j$ is a Beta distribution as follows;
 \begin{equation}\label{admpriormean}
-p^E_{j}\vert\hat{\alpha}, \boldsymbol{y}=\frac{e^{x_j^\top\beta}}{1+e^{x_j^\top\beta}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\sim \textrm{Beta}(b_{1j}, b_{0j})\sim \frac{G(b_{1j})}{G(b_{1j})+G(b_{0j})},
+p^E_{j}\vert\hat{\alpha}, \boldsymbol{y}=\frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\sim \textrm{Beta}(b_{1j}, b_{0j})\sim \frac{G(b_{1j})}{G(b_{1j})+G(b_{0j})},
 \end{equation}
@@
 where $G(b_{1j})$ is a random variable following a Gamma$(b_{1j}, 1)$ distribution with a unit scale and independently $G(b_{0j})$ has a Gamma($b_{0j}, 1)$ distribution.
-Note that the representation in Equation (\ref{admpriormean}) is equivalent to saying $e^{x_j^\top\beta}\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables.
+Note that the representation in Equation (\ref{admpriormean}) is equivalent to saying $e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables.
 Its mean and variance are
 \begin{eqnarray}
-E(e^{x_j^\top\beta}\vert\hat{\alpha}, \boldsymbol{y})&=&E\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{b_{1j}}{b_{0j}-1}\equiv\eta_j,\label{priormean1}\\
-~~~~~Var(e^{x_j^\top\beta}\vert\hat{\alpha}, \boldsymbol{y})&=&Var\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{\eta_j(1+\eta_j)}{b_{0j}-2}.\label{priorvariance1}
+E(e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y})&=&E\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{b_{1j}}{b_{0j}-1}\equiv\eta_j,\label{priormean1}\\
+~~~~~Var(e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y})&=&Var\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{\eta_j(1+\eta_j)}{b_{0j}-2}.\label{priorvariance1}
 \end{eqnarray}
 
-In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ follows $N[\hat{\beta}, \hat{\Sigma}]$, where $\hat{\beta}$ is the mode of $p(\beta\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode.
-Then the posterior distribution of $x_j^\top\beta$ is also Normal with mean $x_j^\top\hat{\beta}$ and variance $x_j^\top\hat{\Sigma} x_j$.
+In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ follows $N[\hat{\beta}, \hat{\Sigma}]$, where $\hat{\boldsymbol{\beta}}$ is the mode of $p(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode.
+Then the posterior distribution of $x_j^\top\boldsymbol{\beta}$ is also Normal with mean $x_j^\top\hat{\boldsymbol{\beta}}$ and variance $x_j^\top\hat{\Sigma} x_j$.
 
@@
 \begin{eqnarray}
-\eta^\ast_j&=&e^{x_j^\top\hat{\beta}+x_j^\top\hat{\Sigma} x_j/2},\label{priormean2}\\
-~~~~~\widehat{Var}(e^{x_j^\top\beta}\vert\boldsymbol{y})&=&\eta^{\ast 2}_j\big(e^{x_j^{T}\hat{\Sigma} x_j}-1\big).\label{priorvariance2}
+\hat{\eta}_j&=&e^{x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2},\label{priormean2}\\
+~~~~~\widehat{Var}(e^{x_j^\top\boldsymbol{\beta}}\vert\boldsymbol{y})&=&\hat{\eta}^2_j\big(e^{x_j^{T}\hat{\Sigma} x_j}-1\big).\label{priorvariance2}
 \end{eqnarray}
@@
 \begin{equation}\label{priormeanpara}
-\hat{b}_{1j}=\eta^\ast_j+\frac{\eta^\ast_j + 1}{e^{x_j^{T}\hat{\Sigma} x_j}-1}~~\textrm{and}~~\hat{b}_{0j}=\frac{\eta^\ast_j + 1}{\eta^\ast_j(e^{x_j^{T}\hat{\Sigma} x_j}-1)}+2.
-\end{equation}
-
-The unconditional posterior moments of expected random effects can be estimated similarly to those of shrinkage factors; since $E((p^E_{j})^d\vert\boldsymbol{y})=B(b_{1j} + d, b_{0j})/B(b_{1j}, b_{0j})$ for $d\ge0$,
+\hat{b}_{1j}=\hat{\eta}_j+\frac{\hat{\eta}_j + 1}{e^{x_j^{T}\hat{\Sigma} x_j}-1}~~\textrm{and}~~\hat{b}_{0j}=\frac{\hat{\eta}_j + 1}{\hat{\eta}_j(e^{x_j^{T}\hat{\Sigma} x_j}-1)}+2.
+\end{equation}
+
+The conditional posterior moments of expected random effects can be estimated similarly to those of shrinkage factors;  $E((p^E_{j})^d\vert\hat{\alpha}, \boldsymbol{y})=B(b_{1j} + d, b_{0j})/B(b_{1j}, b_{0j})$ for $d\ge0$.
+Finally, we estimate the unconditional posterior moments of expected random effects by their estimated conditional posterior moments as follows.
 \begin{equation}\label{priormeanmoments}
-\widehat{E}((p^E_{j})^d\vert\boldsymbol{y})= B(\hat{b}_{1j} + d, \hat{b}_{0j})/B(\hat{b}_{1j}, \hat{b}_{0j}).
+\widehat{E}((p^E_{j})^d\vert\boldsymbol{y})= \frac{B(\hat{b}_{1j} + d, \hat{b}_{0j})}{B(\hat{b}_{1j}, \hat{b}_{0j})}.
 \end{equation}
@@
 
-The unconditional posterior mean and variance for the Binomial model specified in Equation \ref{postmean} and \ref{approximate_var} and those for the Poisson model in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}  are functions of the unconditional posterior moments of shrinkage factors and expected random effect.
-Once we plug-in the estimated unconditional posterior moments of shrinkage factors in Equation \ref{shrinkagemoments} and those of expected random effect in Equation \ref{priormeanmoments}, we get the estimates of the mean and variance in Equation \ref{postmean}  and \ref{postvar}, i.e., $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
-For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimates of the mean and variance in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}.
+The unconditional posterior mean and variance of each random effect for the Binomial model specified in Equation \ref{postmean} and \ref{approximate_var} and those for the Poisson model in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}  are functions of the unconditional posterior moments of shrinkage factors and expected random effect.
+Once we plug-in the estimated unconditional posterior moments of shrinkage factors in Equation \ref{shrinkagemoments} and those of expected random effect in Equation \ref{priormeanmoments}, we get the estimates of the unconditional posterior mean and variance of each random effect in Equation \ref{postmean}  and \ref{postvar} denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
+For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimates of the unconditional posterior mean and variance in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}.
 The estimates of two parameters $t_{1j}$ and $t_{0j}$ in Equation \ref{truebeta} come as follows;
@@
 
-Finally, the approximate posterior distribution of random effect $j$ for the Binomial model is
+Finally, the approximate unconditional posterior distribution of random effect $j$ for the Binomial model is
 \begin{equation}\label{trueapprox}
@@
 
-The ADM approximation is accurate if the true distribution of $p_j$ is close to the the Beta distribution \citep{tang2011, morris2012}.
+The ADM approximation is accurate if the true distribution of $p_j$ is close to the the Beta distribution \citep{morris1997, tang2011, morris2012}.
+
+We use the posterior mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the posterior distribution in Equation \ref{trueapprox} for the Binomial model or in Equation \ref{trueapprox_poisson} for the Poisson model as the point and interval estimates of the random effect.
 
@@
 
-\section[Frequency method checking]{Frequency Method Checking}\label{sec4}
-Like the two sides of the same coin, checking a statistical model comes hand in hand with fitting the model.
-If a fitted model cannot pass a validation or checking process, we usually go back and forth from estimation and checking steps iteratively.
-In this sense, checking a fitted model is an interactive procedure for the model justification.
-
-There are two kinds of model justification processes; one is model checking and the other is method checking.
-The model checking is for the justification of the hierarchical model on a specific dataset.
-One possible question is, ``Can this dataset benefit from such hierarchical modeling?'' \cite{modelchecking1996} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy.
-They found that their data had more variation than expected of the first-level Poisson distribution and two-level Poisson hierarchical model could successfully account for such additional variation.
-
-Once we make sure that the hierarchical model is appropriate for our data, the following question will be about the validity of the interval estimates, ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating pseudo-datasets and estimating coverage probabilities.
+\section[Estimation]{The acceptance-rejection method for the Binomial model}\label{sec_accept}
+As for the Binomial model, the package \pkg{Rgbp} also provides a way to  independently draw exact posterior samples of random effects and hyper-parameters via the acceptance-rejection method.
+We continue working on a logarithmic scale of $r$, $\alpha=\log(1/r)=-\log(r)$.
+The joint posterior density function of $\alpha$ and $\boldsymbol{\beta}$ based on their joint hyper-prior density function in Equation \ref{eq:hyper} is
+\begin{equation}
+f(\alpha, \boldsymbol{\beta} \vert \boldsymbol{y})\propto f(\alpha, \boldsymbol{\beta})L(\alpha, \boldsymbol{\beta})\propto e^{\alpha}L(\alpha, \boldsymbol{\beta})d\alpha d\boldsymbol{\beta}.
+\end{equation}
+
+The Acceptance-Rejection (A-R) method \citep{everson2000inference, tang2002fitting} is useful when it is difficult to sample a parameter of interest $\theta$ directly from its target probability density $f(\theta)$, which is known up to a normalizing constant, but an easy-to-sample envelope function $g(\theta)$ is available.
+The A-R method samples $\theta$  from the envelope $g(\theta)$ and accepts it with a probability $\frac{f(\theta)}{Mg(\theta)}$, where $M$ is a constant making $f(\theta)/g(\theta)\le M$ for all $\theta$.
+The distribution of the accepted $\theta$ exactly follows $f(\theta)$.
+The A-R method is stable as long as the tails of the envelop function are thicker than those of the target density function.
+
+The goal of the A-R method  for the  Binomial model is to independently draw  posterior samples of hyper-parameters from $f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})$, using an easy-to-sample envelop function $g(\alpha, \boldsymbol{\beta})$ that has thicker tails than the target density function.
+
+We factor the envelope function into two parts, $g(\alpha, \boldsymbol{\beta})=g_1(\alpha)g_2(\boldsymbol{\beta})$ to model the tails of each function separately.
+We consider the tail behavior of the conditional posterior density function $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ to come up with $g_1(\alpha)$; $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ behaves as $e^{-\alpha(k-1)}$ when $\alpha$ goes to $\infty$ and as $e^{\alpha}$ when $\alpha$ goes to $-\infty$.
+It indicates that $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ is skewed to the left because the right tail touches the $x$-axis faster than the left tail does it as long as $k>1$.
+A skewed $t$-distribution  is a good candidate for $g_1(\alpha)$ because it behaves as a power law on both tails, leading to thicker tails than those of $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$.
+
+It is too complicated to figure out the tail behaviors of $f(\boldsymbol{\beta} \vert \alpha,  \boldsymbol{y})$.
+However, since $f(\boldsymbol{\beta} \vert \alpha,  \boldsymbol{y})$ of the approximate Gaussian counterpart has a multivariate Gaussian density function \citep{tang2011, kelly2014advances}, we consider a multivariate $t$-distribution with 4  degrees of freedom as a good candidate for $g_2(\boldsymbol{\beta})$.
+
+Specifically, we assume
+\begin{eqnarray}\label{env}
+g_1(\alpha) &=& g_1(\alpha; \mu, \sigma, a, b)~\equiv~\textrm{Skewed-}t(\alpha\vert\mu, \sigma, a, b),\\
+g_2(\boldsymbol{\beta}) &=& g_2(\boldsymbol{\beta}; \boldsymbol{\mu}^\ast, S_{(m\times m)})~\equiv~t_{4}(\boldsymbol{\beta}\vert \boldsymbol{\mu}^\ast, S),\label{g2approx}
+\end{eqnarray}
+where the notation Skewed-$t(\alpha\vert\mu, \sigma, a, b)$ represents a density function of a skewed $t$-distribution  at $\alpha$ with location $\mu$, scale $\sigma$, degree of freedom $a+b$, and skewness $a-b$ for any positive constants $a$ and $b$ \citep{jones2003skew}.
+The article of \cite{jones2003skew} derives the mode of $g_1(\alpha)$ as
+\begin{equation}\label{mode}
+\mu+\frac{(a-b)\sqrt{a+b}}{\sqrt{(2a+1)(2b+1)}}.
+\end{equation} 
+It shows that the tails follow a power law as $\alpha^{-(2a+1)}$ on the left and $\alpha^{-(2b+1)}$ on the right when $b>a$.
+It also provides a representation to generate the random variable following their skewed-$t$ distribution as
+\begin{equation}
+\alpha\sim \mu+\sigma\frac{\sqrt{a+b}(2T-1)}{2\sqrt{T(1-T)}}, ~\textrm{where}~ T\sim \textrm{Beta}(a, b).
+\end{equation}
+The notation $t_{4}(\boldsymbol{\beta}\vert\boldsymbol{\mu}^\ast, S)$ in Equation \ref{g2approx} indicates a density function of a multivariate $t$-distribution at $\boldsymbol{\beta}$ with 4 degrees of freedom, a location vector $\boldsymbol{\mu}^\ast$, and a $m\times m$ scale matrix $S$ that leads to the variance-covariance matrix $2S$.
+
+We set the parameters of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$, i.e., $\mu$, $\sigma$, $a$, $b$, $\boldsymbol{\mu}^\ast$, and $S$, to make the product of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$ similar to the target joint posterior density $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$.
+First, we obtain the  mode of $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$ and the inverse of the  negative Hessian matrix at the modes, $-H^{-1}$.
+Let $(\hat{\alpha}, \hat{\boldsymbol{\beta}})$ denote the modes of $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$, $-H^{-1}_{\hat{\alpha}}$ indicate (1, 1) element of $-H^{-1}$, and $-H^{-1}_{\hat{\boldsymbol{\beta}}}$ represent  $-H^{-1}$ without the first row and  column.
+%(1, 1)  and $(2:(m+1), 2:(m+1))$ elements of the  inverse of the negative Hessian matrix at the modes, respectively.
+% $f(\alpha, \boldsymbol{\beta} \vert \boldsymbol{y})\propto e^\alpha L(\alpha, \boldsymbol{\beta})d\alpha d\boldsymbol{\beta}$.
+
+Next, we set ($a,~ b$) to $(k,~ 2k)$ if $k<10$ (or otherwise $(\log(k),~ 2\log(k))$)   to maintain a left-skewness of $g_1(\alpha)$ and to keep  $a$ and $b$ small enough for thick tails.
+We match the mode of $g_1(\alpha)$ specified in Equation \ref{mode} to $\hat{\alpha}$ by fixing the location parameter $\mu$ at $\hat{\alpha}-(a-b)\sqrt{a+b}/\sqrt{(2a+1)(2b+1)}$.
+We set  the scale parameter $\sigma$ to $(-H^{-1}_{\hat{\alpha}})^{0.5}\eta$, where $\eta$ is a tuning parameter; $\eta=1.3$ is the default.
+When the A-R method produces extreme values of weights defined in Equation \ref{weight} below, we increase the value of $\eta$.
+%To summarize, we use
+%\begin{equation}
+%g_1(\alpha)\equiv\textrm{Skewed-}t(\alpha\vert\mu=\hat{\alpha}+\zeta, \sigma=(-H^{-1}_{\hat{\alpha}})^{0.5}\eta, a=\log(k), b=2\log(k)),
+%\end{equation}
+%where $\zeta$ is a mode correction term defined as $-(a-b)\sqrt{a+b}/\sqrt{(2a+1)(2b+1)}$. 
+%It is desirable to have a larger $\delta$ when $c$ in the class of hyper-prior distributions is closer to 0 because a smaller $c$ makes a thicker left tail of $\alpha$ a priori.
+%, considering an asymptotic normality of the target density as $k$ increases. 
+%In case of using the hyper-prior distribution $dr/r^{1.5}$, whose right tail is thicker than $dr/r^2$ a priori, we set a larger scale $\phi=5*\sqrt{-H^{-1}_{\hat{\alpha}}}$ to cover its thicker tail.
+The multiplication constants were chosen after simulation studies.
+We fix the skewness parameter $\delta$ at -2 because in many cases, combined with a large scale parameter, it helped the skewed-normal density cover a long left-tail of the marginal distribution of $\alpha$, known to have a left skewness \citep{morris2012shrinkage}.
+
+As for $g_2(\boldsymbol{\beta})$, we matches the location vector $\boldsymbol{\mu}^\ast$ to the mode $\hat{\boldsymbol{\beta}}$ and the scale matrix $S$ to $-H^{-1}_{\hat{\boldsymbol{\beta}}}/2$ so that the variance-covariance matrix becomes $-H^{-1}_{\hat{\boldsymbol{\beta}}}$;
+\begin{equation}
+g_2(\boldsymbol{\beta})\equiv t_4(\boldsymbol{\beta}\vert \boldsymbol{\mu}^\ast=\hat{\boldsymbol{\beta}}, S=-H^{-1}_{\hat{\boldsymbol{\beta}}}/2).
+\end{equation}
+%; when the sample size was small, it increased the acceptance rate of the A-R method
+
+For the  implementation of the acceptance-rejection method, we obtain four times more trial samples than the desired number of samples $N$ independently from $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$.
+We calculate $4N$ weights, each of which is defined as
+\begin{equation}\label{weight}
+w_i\equiv w(\alpha^{(i)}, \boldsymbol{\beta}^{(i)})=\frac{f(\alpha^{(i)}, \boldsymbol{\beta}^{(i)}\vert \boldsymbol{y})}{g_1(\alpha^{(i)})g_2( \boldsymbol{\beta}^{(i)})}, ~\textrm{for}~ i=1, 2, \ldots, 4N.
+\end{equation}
+We accept each pair of $(\alpha^{(i)}, \boldsymbol{\beta}^{(i)})$ with a probability $w_i/M$ where $M$ is set to the maximum of all the $4N$ weights.
+The usual acceptance rates from  our data examples are around 25\%.
+In a case where we accept more than the desired number of samples $N$, we discard the redundant.
+If the number of accepted samples is smaller than $N$, then we sample additional pairs (6 times more than the shortage) and calculate a new maximum $M'$ from all the previous and new weights, accepting or rejecting the entire pairs again with new probabilities $w_i/M'$.
+
+%Using the A-R method, for example, we fit the  Bayesian BBLR with $drd\beta_1/r^2$ on the data of 18 baseball players with $\boldsymbol{x}^T_j\boldsymbol{\beta}=\beta_1$ \citep{efron1975data}.
+To obtain 5,000 posterior samples of $(\alpha, \beta_1)$, we sample 20,000 trial pairs and make sure that there are not extremely large weights via the histogram of the 20,000 weights in the first plot of Figure \ref{fig1}.
+The method accepts 5,504 pairs out of 20,000 (27.52\%) based on the probabilities $w_i/M$ for $i=1, 2, \ldots, 20,000$.
+The histograms of posterior samples of  $\alpha$ and $\beta_1$ and their scatter plot follow in Figure \ref{fig1}.
+For a comparison, we draw red density curves  representing 20,000 posterior samples of $(\alpha, \beta_1)$ obtained via a two-dimensional grid sampling method \citep{gelman2013bayesian}.
+The red contour lines in the scatter plot whose levels are $(0.05, 0.25, 0.50, 0.75, 0.95)$  indicate the target joint posterior density $\pi_{hyp.post}(\alpha, \beta_1\vert \boldsymbol{y})$.
+The whole procedure of the A-R method takes less than a second to produce these posterior samples.
+
+%\begin{figure}[h!]
+%\includegraphics[scale = 0.4]{fig1_1.png}
+%\caption[]{The result of fitting the Bayesian BBLR with $drd\boldsymbol{\beta}/r^2$  via the A-R method on the data of 18 baseball players  without any covariates.
+We display histograms of 20,000 weights (1st plot), the histograms of the posterior samples of $\alpha$ (2nd) and $\beta_1$ (3rd), and their scatter plot (4th).
+The red density curves in the histograms of $\alpha$ and $\beta_1$ represent 20,000 posterior samples obtained via a grid sampling method.
+The red contour lines whose levels are (0.05, 0.25, 0.50, 0.75, 0.95) in the scatter plot indicate the joint posterior density $f(\alpha, \beta_1\vert\boldsymbol{y})$.
+}
+%\label{fig1}
+%\end{figure}
+
+Once we have posterior samples of hyper-parameters, it is easy to obtain posterior samples of random effects via a Monte Carlo integration below.
+\begin{equation}\label{mcintegration}
+f(\boldsymbol{p}\vert \boldsymbol{y})=\int  f(\boldsymbol{p}\vert \alpha, \boldsymbol{\beta}, \boldsymbol{y})\cdot f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})d\alpha d\boldsymbol{\beta}.
+\end{equation}
+The integration can be done by sampling $(p_1, p_2, \ldots, p_k)$ from the independent Beta conditional posterior distributions $f(p_j\vert \boldsymbol{\beta}, r, \boldsymbol{y})$ in Equation \ref{betapost}  given $r~(=e^{-\alpha})$ and $\boldsymbol{\beta}$ already sampled from $f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})$ via the A-R method.
+
+\section{Frequency method checking}\label{sec4}
+Whether the 95\%  interval estimates of random effects obtained by a specific model achieve the nominal 95\% confidence level  for any true parameter values is one of the key model evaluation criteria.
+A frequency method checking is a procedure to evaluate it, which is different from a model checking that tests whether a two-level model is appropriate for data (overdispersion exists in data) \citep{dean1992testing, modelchecking1996}.
+Conditioning that the two-level model is appropriate, the frequency method checking   generates pseudo-data sets given specific values of hyper-parameters (a parametric bootstrapping) and estimates unknown coverage probabilities based on these mock data sets.
 
@@
 
-\subsection{Pseudo-data generation process}
-Figure \ref{fig:pseudo} will be helpful to understand this process.
-As we can see in (\ref{normalprior}), the distribution of each parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\boldsymbol{\beta}_{(m\times1)}$.
-So, once we fix these hyper-parameters at specific values, we can generate as many parameters as we want.
-Suppose we generated an $N_{sim}$ (default: $N_{sim} = 100$) number of {\boldmath $\mu$}$_{(k\times1)}$'s, (i.e., \{{\boldmath $\mu$}$^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$), from the prior distribution in (\ref{normalprior}), where values of $A$ and $\boldsymbol{\beta}$ are specifically given and the superscript $(i)$ indicates the $i$-th simulation.
-Then using the distribution of observed data in (\ref{normalobs}), we can also generate $\{\boldsymbol{y}^{(i)}_{(k\times1)},~i=1, \ldots, N_{sim}\}$ given each {\boldmath$\mu$}$^{(i)}_{(k\times1)}$.
-Note that we generate one dataset per one parameter set.
+\subsection{Pseudo-data generation}\label{data_generation}
+Figure \ref{fig:pseudo} displays the process of generating pseudo-data sets.
+It is noted that  the conjugate prior distribution of each random effect in Equation \ref{normalprior} is completely determined by two hyper-parameters, $A$ and $\boldsymbol{\beta}$.
+Fixing these hyper-parameters at specific values, we generate  $N_{sim}$ sets of random effects from the conjugate prior distribution, i.e., \{{\boldmath $\mu$}$^{(i)},~i=1, \ldots, N_{sim}\}$, where the superscript $(i)$ indicates the $i$-th simulation.
+Next, using the distribution of observed data in Equation \ref{normalobs}, we generate $N_{sim}$ sets of observed data sets $\{\boldsymbol{y}^{(i)},~i=1, \ldots, N_{sim}\}$ given each {\boldmath$\mu$}$^{(i)}$.
+Note that we generate one observed data set per one set of random effects.
 
@@
 
-\subsection{Coverage estimation process}
-Next, \code{coverage} fits the Normal-Normal model  $N_{sim}$ number of times using the $N_{sim}$ pseudo-datasets in order to obtain $N_{sim}$ $\times k$ interval estimates,  \{$(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, N_{sim}$\}.
-Here, we introduce both simple and Rao-Blackwellized unbiased coverage estimators but the function \code{coverage} in \pkg{Rgbp} displays only the Rao-Blackwellized one.
-
-\subsubsection{Simple unbiased coverage estimates}
-Let's define an indicator variable, $I^{(i)}_{j}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu^{(i)}_{j}$ and 0 otherwise.
-Then \code{coverage} estimates the coverage probability via the sample mean of these indicator variables for each group $j$, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ for given $A$ and $\boldsymbol{\beta}$.
+\subsection{Coverage probability estimation}
+After fitting a Normal-Normal model on each simulated data set, we obtain interval estimates of random effects $\boldsymbol{\mu}$.
+Let $(\hat{\mu}^{(l)}_{j, ~low}, ~\hat{\mu}^{(l)}_{j, ~upp})$ represent the lower and upper bounds of the interval estimate of random effect $j$ based on the $i$-th simulated data set given a specific confidence level.
+Let's define a coverage indicator of random effect $j$ on the $i$-th mock data set as
+\begin{equation}\label{coverage_indicator}
+I_{A, \boldsymbol{\beta}}(\mu_j^{(i)}) = \left\{ \begin{array}{ll}
+1, & \textrm{if $\mu_j^{(i)}\in(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp})$}\\
+0, & \textrm{otherwise}
+\end{array} \right.
+\end{equation}
+We consider the coverage indicators as functions of $A$ and $\boldsymbol{\beta}$ because outcomes of indicators depend on the simulated random effects and mock data generated by these hyper-parameters.
+
+%Let's suppress the subscript $(r, \boldsymbol{\beta})$ from the coverage indicator for simplicity.
+
+%B$^3$LM model to $N_{sim}$ pseudo-datasets in order to obtain $k\times N_{sim}$ interval estimates,  \{$(\hat{p}^{(l)}_{j, ~low}, ~\hat{p}^{(l)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, N_{sim}$\}.
+
+%The simple and Rao-Blackwellized unbiased coverage estimators and their unbiased variance estimators for the coverage evaluation.
+
+\subsubsection{Simple unbiased coverage estimator.}
+When the confidence level is 95\%, the proportion of 95\% interval estimates that contain random effect $j$ is an intuitive choice for  the coverage rate estimator of random effect $j$.
+This estimator  implicitly assumes that there exist $k$ unknown coverage probabilities of random effects, denoted by $C_{A, \boldsymbol{\beta}}(\mu_j)$ for $j=1, 2, \ldots, k$, depending on the values of the hyper-parameters that generate random effects and mock data sets.
+The coverage indicators for random effect $j$ in Equation \ref{coverage_indicator} follow an independent and identically distributed  Bernoulli distribution given the unknown coverage rate $C_{A, \boldsymbol{\beta}}(\mu_j)$.
+The sample mean of these coverage indicators is a simple unbiased coverage estimator for $C_{A, \boldsymbol{\beta}}(\mu_j)$.
+%estimates the coverage probability via the sample mean of these indicator variables for each group $j$,
 \begin{equation}
-\bar{I}_{j}\equiv \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{j},~ j=1, 2, \ldots, k.
-\end{equation}
-
-This provides $k$ simple unbiased coverage estimates.
-For example, $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, N_{sim},$ given specific values of $A$ and $\boldsymbol{\beta}$.
-
-Each indicator has an independent and identically distributed (\emph{iid}) Bernoulli($p_{cov, j}$) distribution, where $p_{cov, j}$ is the true coverage probability for the $j$-th group depending on specific values of $A$ and $\boldsymbol{\beta}$.
+\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)= \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I_{A, \boldsymbol{\beta}}(\mu_j^{(i)}),~ j=1, 2, \ldots, k.
+\end{equation}
+Note that $\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)$ averages over possible values of $\mu_{j}$ and $y_{j}$ generated by specific values of $A$ and $\boldsymbol{\beta}$.
+
+ %true coverage probability for the $j$th group depending on specific values of $(r, \boldsymbol{\beta})$. 
 %For reference, even if we sample $L$ datasets per one parameter set, $L\cdot N_{sim}$ indicators $I^{(i, l)}_{j}, i = 1, \ldots, N_{sim}, l = 1, \ldots, L$, have still $iid$ Bernoulli($p_{cov, j}$) distribution.
 
-Then, its unbiased variance estimator  for $Var(\bar{I}_{j})$ is simply the sample variance of indicators over the number of simulations.
+The unbiased variance estimator of $Var(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))$ is 
 \begin{equation}\label{svar}
-\widehat{Var}(\bar{I}_{j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}(I^{(i)}_{j}-\bar{I}_{j})^{2},~ j=1, 2, \ldots, k.
-\end{equation}
-
-\subsubsection{Rao-Blackwellized unbiased coverage estimates}
-Rao-Blackwellization improves accuracy of an unbiased estimator by taking more information (the sufficient statistic) into account.
-Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \boldsymbol{\beta}$), where $A$ and $\boldsymbol{\beta}$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset.
-\begin{equation}\label{RB}
-\bar{I}_{RB, j}\equiv \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \boldsymbol{\beta}),~ j=1, 2, \ldots, k.
-\end{equation}
-
-The expectation part in (\ref{RB}) is Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \boldsymbol{\beta})$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset.
-We can calculate this probability  because we know the distribution of ($\mu^{(i)}_{j} \vert y^{(i)}_{j}, A, \boldsymbol{\beta}$) in (\ref{normalpost}).
-Note that conditioning on $y^{(i)}_{j}$ is equivalent to conditioning on $\boldsymbol{y}^{(i)}_{(k\times1)}$ as long as $A$ and $\boldsymbol{\beta}$ are known.
-
-For example, we estimate the first group's true coverage probability $p_{cov, 1}$ (which depends on specific values of $A$ and $\boldsymbol{\beta}$) by $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \boldsymbol{\beta})$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I^{(i)}_{1}$.
-
-Under the setting where one dataset ($\boldsymbol{y}^{(i)}_{(k\times1)}$) is simulated per one true parameter set ({\boldmath $\mu$}$^{(i)}_{(k\times1)})$, the unbiased variance estimator for Var($\bar{I}_{RB, j}$) follows.
+\widehat{Var}(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))=\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})-\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))^{2},~ j=1, 2, \ldots, k.
+\end{equation}
+
+\subsubsection{Rao-Blackwellized unbiased coverage estimator.}
+The frequency method checking is computationally expensive in nature because it  fits a model on every mock data set.
+The situation deteriorates if the number of simulations or the size of data is large, or the estimation method is computationally demanding.
+\citet{morris1997} and \cite{tang2002fitting} used a Rao-Blackwellized (RB) unbiased coverage estimator for the unknown coverage rate of each random effects, which is more efficient than the simple indicator-based coverage estimator.
+For $j=1, 2, \ldots, k$,
+\begin{equation}\label{RB_theory}
+C_{A, \boldsymbol{\beta}}(\mu_j)=E(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)\vert A, \boldsymbol{\beta})=E\bigg[\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})\vert A, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})\bigg\vert A, \boldsymbol{\beta}\bigg],
+\end{equation}
+where the sample mean of conditional expectations inside the outer expectation is the RB unbiased coverage estimator. To be specific,
+\begin{eqnarray}\label{RB}
+\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) &=& \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})\vert A, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})\\
+&=& \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}} Pr(\mu_j^{(i)}\in(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp})\vert A, \boldsymbol{\beta},  \boldsymbol{y}^{(i)}).\nonumber
+\end{eqnarray}
+We  can easily compute the above conditional posterior probabilities using the cumulative density function of the Normal conditional posterior distribution of each random effect in Equation \ref{normalpost}.
+The variance of  $\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j)$ is smaller than or equal to the variance of a simple coverage estimator $\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)$ \citep{radhakrishna1945information, blackwell1947conditional}.
+
+%, i.e., $Pr(p_j^{(l)}<\hat{p}^{(l)}_{j, ~upp}\vert r, \boldsymbol{\beta}, \boldsymbol{y}^{(l)})-Pr(p_j^{(l)}<\hat{p}^{(l)}_{j, ~low},\vert r, \boldsymbol{\beta}, \boldsymbol{y}^{(l)})$.
+
+If one dataset $\boldsymbol{y}^{(l)}$ is simulated per one set of random effects $\boldsymbol{\mu}^{(l)}$, the variance estimator below is an unbiased estimator of $Var(\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) )$.
+For $j=1, 2, \ldots, k,$
 \begin{equation}\label{RBvar}
-\widehat{Var}(\bar{I}_{RB, j})\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}\bigg(E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \boldsymbol{\beta})-\bar{I}_{RB, j}\bigg)^{2},~ j=1, 2, \ldots, k.
+\widehat{Var}(\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) )\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}\bigg(E(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})\vert A, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})-\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) \bigg)^{2}.
 \end{equation}
@@
 \section[packageoverview]{Usage of functions in \pkg{Rgbp}}\label{sec5}
+In this section, we describe the usage of the two main functions of \pkg{Rgbp}, i.e., \code{gbp} for model fitting and \code{coverage} for frequency method checking.
+
+The basic usage of fitting a Normal-Normal model via the function \code{gbp} is simply
+\begin{CodeChunk}
+\begin{CodeInput}
+R> output <- gbp(y, se, model = "gaussian")
+\end{CodeInput}
+\end{CodeChunk}
+
+The argument \code{y} is a vector of $k$ observed sufficient statistics, the argument  \code{se} for the Normal model is a vector of $k$ standard errors of the corresponding sufficient statistics, and the argument \code{model} indicates that  \code{gbp} fits a Normal-Normal model.
+
+There are many optional arguments for \code{gbp}.
 

### 2015-06-07 Rgbp/R/gbp.R

@@ -8,11 +8,16 @@ gbp.default <- function(x, w, covariates, mean.PriorDist, model = "gaussian",
                         normal.CI = FALSE, t = 0, u = 1) {
 
   ##input checks
-  if(model == "poisson" & missing(mean.PriorDist))
+  if(model == "poisson" & missing(mean.PriorDist)) {
     warning("Model is Poisson and the prior mean is unknown. This program can not yet give reliable results for this data. If the Poisson is being used as an approximation to the Binomial and the exposures are known then please assume a Binomial model")
+  }  
   
+  if(intercept == "FALSE" & missing(covariates)) {
+    warning("When there are no covariates and no intercept term, model cannot fit the model")
+    quit()
+  }  
   
-######
+  ######
   res <- switch(model, 
        gaussian = gr(x, w, X = covariates, mu = mean.PriorDist, Alpha = Alpha, intercept = intercept, 
                      normal.CI = normal.CI), 

### 2015-06-07 Rgbp/R/gbp.R
package

@@ -13,7 +13,7 @@ gbp.default <- function(x, w, covariates, mean.PriorDist, model = "gaussian",
   }  
   
   if(intercept == "FALSE" & missing(covariates)) {
-    warning("When there are no covariates and no intercept term, model cannot fit the model")
+    warning("When there are no covariates and no intercept term, model cannot fit the model. Please set the argument mean.PriorDist or use the intercept term.")
     quit()
   }  
   

### 2015-06-07 Rgbp/R/gbp.R
package error message

@@ -14,7 +14,7 @@ gbp.default <- function(x, w, covariates, mean.PriorDist, model = "gaussian",
   
   if(intercept == "FALSE" & missing(covariates)) {
     warning("When there are no covariates and no intercept term, model cannot fit the model. Please set the argument mean.PriorDist or use the intercept term.")
-    quit()
+    stop()
   }  
   
   ######

### 2015-06-08 jss/article_v2.tex
gbp usage

@@
 
-\section[Estimation]{Inference via the adjustment for density maximization}\label{sec3}
-
-Obtaining point and interval estimates of each random effect is our primary inferential interest.
+\section[Inference]{The inferential model}\label{inference}
+
+The likelihood function of hyper-parameters $A$ and $\boldsymbol{\beta}$ for the Gaussian hierarchical model is derived from the independent Normal marginal distributions of the observed data with random effects, $\mu_1, \mu_2, \ldots, \mu_k$, integrated out as follows; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
+\begin{equation}\label{marginal_normal}
+L_g(A, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k f(y_j\vert A, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k \frac{1}{\sqrt{2\pi (A+V_j)}}\exp\big(-\frac{(y_j-\mu^E_j)^2}{2(A+V_j)}\big),
+\end{equation}
+where $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$.
+The likelihood function of hyper-parameters $r$ and $\boldsymbol{\beta}$ for the Binomial hierarchical model is derived from the independent Beta-Binomial marginal distributions of the observed data with random effects, $p_1, p_2, \ldots, p_k$, integrated out \citep{skellam1948}; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
+\begin{equation}\label{marginal_binomial}
+L_b(r, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k f(y_j\vert r, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k\binom{n_j}{y_j}\frac{B(y_j+rp^E_j, ~n_j-y_j+r(1-p^E_j))}{B(rp^E_j, ~r(1-p^E_j))},
+\end{equation}
+where $p^E_j=\exp(\boldsymbol{x}^\top\boldsymbol{\beta})/(1+\exp(\boldsymbol{x}^\top\boldsymbol{\beta}))$ and the notation $B(a, b)~(\equiv\int_0^1 v^{a-1}(1-v)^{b-1}dv)$ indicates a beta function for positive constants $a$ and $b$.
+Similarly, the likelihood function of $r$ for the Poisson hierarchical model, without a regression coefficient (a known expected random effect, $\lambda^E$), comes from the independent Negative-Binomial marginal distributions of the observed data with the random effects, $\lambda_1, \lambda_2, \ldots, \lambda_k$, integrated out;
+\begin{equation}\label{marginal_poisson}
+L_p(r)=\prod_{j=1}^k f(y_j\vert r)=\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E+y_j)}{\Gamma(r\lambda^E)(y_j!)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E},
+\end{equation}
+where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}e^{x}dx$ for a positive constant $a$.
+
+%If all the observed data are extreme, i.e., $y_j$ is either 0 or $n_j$ for all $j$, the likelihood becomes a decreasing function with respect to $r$ for finite values of $\boldsymbol{\beta}$.
+In this case, the MLE of $r$ is 0.
+
+The joint posterior density  function of hyper-parameters $f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Gaussian hierarchical model is proportional to their likelihood functions in Equation \ref{marginal_normal} because we use flat improper hyper-prior density functions for $A$ and $\boldsymbol{\beta}$ shown in Equation \ref{eq:hyper};
+\begin{equation}\label{marginal_post_normal}
+f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L_g(A, \boldsymbol{\boldsymbol{\beta}})d\boldsymbol{\beta}dA.
+\end{equation}
+The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial hierarchical model is proportional to their likelihood functions in Equation \ref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in Equation \ref{eq:hyper} as follows;
+\begin{equation}\label{marginal_post_binomial}
+f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L_b(r, \boldsymbol{\boldsymbol{\beta}})d\boldsymbol{\beta}dr/r^2.
+\end{equation}
+The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in Equation \ref{marginal_poisson} times the hyper-prior density function of $r$, $dr/r^2$;
+\begin{equation}\label{marginal_post_poisson}
+f(r \vert \boldsymbol{y})\propto L_p(r)dr/r^2.
+\end{equation}
+
+Our goal is to obtain the point and interval estimates of the random effects from their unconditional posterior distributions; for the Gaussian hierarchical model, 
+\begin{equation}\label{mcintegration_normal}
+f(\boldsymbol{\mu}\vert \boldsymbol{y})=\int  f(\boldsymbol{\mu}\vert A, \boldsymbol{\beta}, \boldsymbol{y})\cdot f(A, \boldsymbol{\beta}\vert \boldsymbol{y})dA d\boldsymbol{\beta},
+\end{equation}
+for the Binomial hierarchical model, 
+\begin{equation}\label{mcintegration_binomial}
+f(\boldsymbol{p}\vert \boldsymbol{y})=\int  f(\boldsymbol{p}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\cdot f(r, \boldsymbol{\beta}\vert \boldsymbol{y})dr d\boldsymbol{\beta},
+\end{equation}
+and lastly for the Poisson hierarchical model, 
+\begin{equation}\label{mcintegration_poisson}
+f(\boldsymbol{\lambda}\vert \boldsymbol{y})=\int  f(\boldsymbol{\lambda}\vert r, \boldsymbol{y})\cdot f(r\vert \boldsymbol{y})dr.
+\end{equation}
+
+\section[Estimation]{Estimation via the adjustment for density maximization}\label{sec3}
+
+In this section, we illustrate our estimation procedure equipped with the adjustment for density maximization (hereafter ADM) \citep{carl1988, morris1997, tang2011}, a way to  approximate a distribution of the parameter of interest by one of Pearson family distributions based on derivatives (like the Delta method).
+The illustration is based mainly on the Binomial model.
+We briefly describe the Gaussian and Poisson models if these models have unique aspects different from the Binomial model.
+See \cite{kelly2014advances} for the details about the ADM procedure of the Gaussian model adopted in  \pkg{Rgbp}.
+
+Overall, obtaining point and interval estimates of each random effect is our primary inferential interest.
 The approximate Bayesian tool assumes that the unconditional posterior distribution of each random effect follows a skewed-Normal distribution for the Gaussian case,  a Gamma distribution for the Poisson case, or a Beta distribution for the Binomial case whose parameters are matched to the estimated unconditional posterior moments of each random effect.
@@
 
-We illustrate our estimation procedure equipped with the adjustment for density maximization (hereafter ADM) \citep{carl1988, morris1997, tang2011}, a way to  approximate a distribution of the parameter of interest by one of Pearson family distributions based on derivatives like the Delta method, using the Binomial and Poisson hierarchical models.
-The ADM procedure for the Gaussian hierarchical model adopted in  \pkg{Rgbp} has been well-documented in \cite{kelly2014advances}.
-
-\subsection[Inference]{The inferential model}\label{inference}
-
-The likelihood function of hyper-parameters $r$ ($A$ for the Gaussian model) and $\boldsymbol{\beta}$ for the Binomial hierarchical model is derived from the independent Beta-Binomial marginal distributions of the observed data with random effects integrated out \citep{skellam1948}.
-%For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
-\begin{equation}\label{marginal_binomial}
-L(r, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k f(y_j\vert r, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k\binom{n_j}{y_j}\frac{B(y_j+rp^E_j, ~n_j-y_j+r(1-p^E_j))}{B(rp^E_j, ~r(1-p^E_j))},
-\end{equation}
-where the notation $B(a, b)~(\equiv\int_0^1 v^{a-1}(1-v)^{b-1}dv)$ indicates a beta function for positive constants $a$ and $b$.
-Similarly, the likelihood function of $r$ for the Poisson hierarchical model comes from the independent Negative-Binomial marginal distributions of the observed data with the random effects integrated out;
-\begin{equation}\label{marginal_poisson}
-L(r)=\prod_{j=1}^k f(y_j\vert r)=\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E+y_j)}{\Gamma(r\lambda^E)(y_j!)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E}.
-\end{equation}
-
-%If all the observed data are extreme, i.e., $y_j$ is either 0 or $n_j$ for all $j$, the likelihood becomes a decreasing function with respect to $r$ for finite values of $\boldsymbol{\beta}$.
-In this case, the MLE of $r$ is 0.
-
-The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial hierarchical model is proportional to their likelihood functions in Equation \ref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in Equation \ref{eq:hyper} as follows;
-\begin{equation}\label{marginal_post}
-f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L(r, \boldsymbol{\boldsymbol{\beta}})d\boldsymbol{\beta}dr/r^2.
-\end{equation}
-The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in Equation \ref{marginal_poisson} times the hyper-prior density function of $r$, $dr/r^2$;
-\begin{equation}\label{marginal_post}
-f(r \vert \boldsymbol{y})\propto L(r)dr/r^2.
-\end{equation}
-
-Our goal is to obtain the point and interval estimates of the random effects from their unconditional posterior distributions; for the Binomial case, 
-\begin{equation}\label{mcintegration}
-f(\boldsymbol{p}\vert \boldsymbol{y})=\int  f(\boldsymbol{p}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\cdot f(r, \boldsymbol{\beta}\vert \boldsymbol{y})dr d\boldsymbol{\beta},
-\end{equation}
-and for the Poisson case, 
-\begin{equation}\label{mcintegration}
-f(\boldsymbol{\lambda}\vert \boldsymbol{y})=\int  f(\boldsymbol{\lambda}\vert r, \boldsymbol{y})\cdot f(r\vert \boldsymbol{y})dr.
-\end{equation}
-
 \subsection[shrinkage]{Estimation for shrinkage factors and expected random effects}\label{shrinkage}
 
-Estimating the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$, and the conditional posterior moments of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ (or $\lambda^E$ for the Poisson model), is the most important estimation problem for the hierarchical models that \code{gbp} assumes.
-This is because these moment estimates are used to approximate the unconditional posterior moments of the random effects, $p_1, p_2, \ldots, p_k$ (or $\lambda_1, \lambda_2, \ldots, \lambda_k$ for the Poisson model).
-Taking the Binomial-Beta model as an example, with the assumption that hyper-parameters $r$ (or $A$ for the Gaussian model) and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ are
+Estimating the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$ ($B_j\equiv V_j/(V_j+A)$ for the Gaussian model), and the conditional posterior moments of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ ($\mu^E_1, \mu^E_2, \ldots, \mu^E_k$ for the Gaussian model or $\lambda^E$ for the Poisson model), is the main estimation problem for the hierarchical models that \code{gbp} assumes.
+This is because these moment estimates are used to estimate the unconditional posterior moments of the random effects, $p_1, p_2, \ldots, p_k$ ($\mu_1, \mu_2, \ldots, \mu_k$ for the Gaussian model or $\lambda_1, \lambda_2, \ldots, \lambda_k$ for the Poisson model).
+Taking the Binomial-Beta model as an example, with the assumption that hyper-parameters $r$ and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ are
 \begin{eqnarray}
@@
 &\approx&E\big(p^{\ast}_{j}(1-p^{\ast}_{j})(1-\textrm{B}_{j})/n_{i}\vert \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big)\\
-&=&g(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}), E(B^3_j\vert\boldsymbol{y}),  E(p^E_{j}\vert\boldsymbol{y}), E((p^E_{j})^2\vert\boldsymbol{y})).\label{approximate_var}
+&=&h_b(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}), E(B^3_j\vert\boldsymbol{y}),  E(p^E_{j}\vert\boldsymbol{y}), E((p^E_{j})^2\vert\boldsymbol{y})).\label{approximate_var}
 \end{eqnarray}
 Note that the unconditional posterior mean and approximate variance of random effect $j$ in Equation \ref{postmean}  and \ref{approximate_var}  are functions of the unconditional posterior moments of shrinkage factors and expected random effects.
-We specify the function $g$ in Equation \ref{approximate_var} in Appendix \ref{apppostvar}.
-
-We assumed that hyper-parameters $r$ and  $\boldsymbol{\beta}$ were independent a posteriori, considering that they are independent a posteriori in the limit of $k$ going to infinity  because they are asymptotically Normally distributed.
+We specify the function $h_b$ in Equation \ref{approximate_var} in Appendix \ref{apppostvar}.
+
+We assumed that hyper-parameters $r$ ($A$ for the Gaussian model) and  $\boldsymbol{\beta}$ were independent a posteriori for the Binomial model, considering that they are independent a posteriori in the limit of $k$ going to infinity  because they are asymptotically Normally distributed.
 Also, \cite{morris1997}  empirically showed that their covariance from the observed information matrix of the Poisson-Gamma model, though with a different parametrization, was close to 0 in a small sample setting.
+%For the Gaussian model we do not assume the posterior independence between $A$ and $\boldsymbol{\beta}$ because the conditional posterior variance of the random effect is a constant function of the conditional posterior mean, which is much simpler than that of the Binomial model.
+
+The unconditional posterior mean and variance of random effect $j$ of the Gaussian model are
+\begin{eqnarray}
+E(\mu_j\vert \boldsymbol{y}) &=&E(E(\mu_{j}\vert A, \boldsymbol{\beta}, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))y_j + E(B_j\vert  \boldsymbol{y})E(\mu^E_j\vert  \boldsymbol{y})\label{postmean_normal} \\
+Var(\mu_{j}\vert \boldsymbol{y}) &=&  E(Var(\mu_{j}\vert A,  \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+Var(E(\mu_{j}\vert A, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_normal}\\
+&=&  (1-V_j)E(B_j\vert  \boldsymbol{y})+Var\big(\textrm{B}_{j}(y_{j}-\mu^E_{j})\vert \boldsymbol{y}\big) \\
+&=&h_g(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}),  E(\mu^E_j\vert\boldsymbol{y}), E((\mu^E_j)^2\vert\boldsymbol{y})).\label{approximate_var_normal}
+\end{eqnarray}
+The unconditional posterior mean and variance of random effect $j$ under the Gaussian model are also functions of the unconditional posterior moments of the shrinkage factors and expected random effects.
+We specify the function $h_g$ in Appendix \ref{apppostvar_normal}.
 
@@
 \begin{eqnarray}
-E(\lambda_j\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})\lambda^E\label{postmean_poisson} \\
-~~~~~~Var(\lambda_{j}\vert \boldsymbol{y}) &=&  E(Var(p_{j}\vert r,  \boldsymbol{y})\vert \boldsymbol{y})+Var(E(\lambda_{j}\vert r, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_poisson}\\
+E(\lambda_j\vert \boldsymbol{y}) &=&E(E(\lambda_{j}\vert r, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})\lambda^E\label{postmean_poisson} \\
+Var(\lambda_{j}\vert \boldsymbol{y}) &=&  E(Var(\lambda_{j}\vert r,  \boldsymbol{y})\vert \boldsymbol{y})+Var(E(\lambda_{j}\vert r, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_poisson}\\
 &=& E\big(\lambda^{\ast}_{j}/ (r+n_{j})\vert  \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-\lambda^E_{j})\vert \boldsymbol{y}\big) \\
-&=&h(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}) ).\label{approximate_var_poisson}
+&=&h_p(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}) ).\label{approximate_var_poisson}
 \end{eqnarray}
 The unconditional posterior mean and variance of random effect $j$ under the Poisson model are also functions of the unconditional posterior moments of the shrinkage factors.
-We specify the function $h$ in Equation \ref{approximate_var_poisson} in Appendix \ref{apppostvar_poisson}.
+We specify the function $h_p$ in Equation \ref{approximate_var_poisson} in Appendix \ref{apppostvar_poisson}.
 %conditional posterior means of  random effect $j$ in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are a linear function of the shrinkage factor $B_{j}$ and the conditional posterior variances in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are linear (Gaussian), quadratic (Poisson), and  approximately cubic (Binomial) functions of $B_{j}$, considering $r+n_j=n_j/(1-B_j)$.
@@
 
-\subsubsection{Unconditional posterior moments of shrinkage factors.}  It is noted that  the shrinkage factors ($B_1, \ldots B_k$) are a function of $r$, i.e., $B_{j}= r/(r+n_{j})=B_{j}(r)$.
+\subsubsection{Unconditional posterior moments of shrinkage factors}  It is noted that  the shrinkage factors ($B_1, \ldots B_k$) are a function of $r$, i.e., $B_{j}= r/(r+n_{j})=B_{j}(r)$ (or a function of $A$ for the Gaussian model).
 One way to approximate the distribution of $B_{j}$ is to find the maximum likelihood estimate of $r$, $\hat{r}_{MLE}$, with its Hessian value and to use a Delta method for an asymptotic Normal distribution of $B_{j}(\hat{r}_{MLE})$.
@@
 
-The ADM assumes that the shrinkage factors follow Beta distributions a posteriori as
+The ADM specified in \cite{tang2011} assumes that the shrinkage factors follow Beta distributions a posteriori as
 \begin{equation}\label{admshrinkage}
@@
 Note that the mean of Beta distribution $a_{1j}/(a_{1j}+a_{0j})$ is not the same as its mode $(a_{j1}-1)/(a_{j1}+a_{j0}-2)$.
-ADM works on an adjusted posterior distribution $A(B_j\vert \boldsymbol{y})dB_j\propto B_j(1-B_j)f(B_j\vert \boldsymbol{y})dB_j$ so that its mode is the same as the mean of the original Beta distribution.
+The ADM works on an adjusted posterior distribution $A(B_j\vert \boldsymbol{y})dB_j\propto B_j(1-B_j)f(B_j\vert \boldsymbol{y})dB_j$ so that its mode is the same as the mean of the original Beta distribution.
 The assumed posterior mean and variance of shrinkage factor are
@@
 
-ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \cite{berger1999integrated} for the integrated likelihood in detail.
-Considering that Equation \ref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-log(r)$, because the distribution of $\alpha$ is more symmetric than that of $r$ and $\alpha$ is defined on a real line without any boundary issues.
+The ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \cite{berger1999integrated} for the integrated likelihood in detail.
+For the Gaussian model, the marginal likelihood function of $A$ is available in a closed form with $\boldsymbol{\beta}$ integrated out, see  \cite{tang2011}.
+
+Considering that Equation \ref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-\log(r)$ (or $\alpha=\log(A)$ for the Gaussian model), because the distribution of $\alpha$ is more symmetric than that of $r$ and $\alpha$ is defined on a real line without any boundary issues.
 Since $A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto e^\alpha L(\alpha)$, the estimated posterior mean in Equation \ref{admmean} is
@@
 
-We need the invariance information \citep{tang2011} to estimate the variance in Equation \ref{admvar}, which is defined as 
+We need the invariance information introduced in \cite{tang2011} to estimate the variance in Equation \ref{admvar}, which is defined as 
 \begin{eqnarray}
@@
 
-\subsubsection{Unconditional posterior moments of expected random effects for the Binomial model.}
-We assume that the conditional posterior distribution of each expected random effect given $\hat{\alpha}$ follows a Beta distribution, and estimate the assumed Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$.
-We estimate the conditional posterior moments of the expected random effects and treat them as their estimated unconditional posterior moments obtained by the (Laplace) approximate marginal likelihood function of $\boldsymbol{\beta}$.
-We found that the conditional and unconditional posterior moment estimates were almost identical due to their small covariance between $r$ and $\boldsymbol{\beta}$ in the observed information matrix.
-In addition, calculating the conditional posterior moments was computationally less burdensome.
-
-The moments of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involve an intractable integration. For example, the first conditional posterior moment is
+\subsubsection{Unconditional posterior moments of expected random effects}
+The Gaussian and Binomial models need to estimate the unconditional moments of expected random effects.
+We estimate them using their relationship to the conditional posterior moments.
+For a non-negative constant $c$, the unconditional posterior moments are
+\begin{equation}
+E((\mu^E_j)^c\vert\boldsymbol{y})=E(E((\mu^E_j)^c\vert A, \boldsymbol{y})\vert\boldsymbol{y})~~\textrm{and}~~E((p^E_j)^c\vert\boldsymbol{y})=E(E((p^E_j)^c\vert r, \boldsymbol{y})\vert\boldsymbol{y}).
+\end{equation}
+We estimate the unconditional posterior moments by the estimated conditional posterior moments that we obtain from the conditional posterior distribution of $\mu^E_j\vert A, \boldsymbol{y}$ or that of $p^E_j\vert r, \boldsymbol{y}$ with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.
+
+To be specific, we use another ADM for the Binomial model, assuming that the conditional posterior distribution of each expected random effect given $\hat{\alpha}$ follows a Beta distribution.
+This is because the moments of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involve an intractable integration.
+For example, the first conditional posterior moment is
 \begin{equation}\label{priormoment1}
@@
 \end{equation}
-
+%We estimate the assumed Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$.
+We estimate the conditional posterior moments of the expected random effects and treat them as their estimated unconditional posterior moments obtained by the (Laplace) approximate marginal likelihood function of $\boldsymbol{\beta}$.
+% The conditional and unconditional posterior moment estimates are almost identical due to the small covariance between $r$ and $\boldsymbol{\beta}$ in the observed information matrix.
+In addition, calculating the conditional posterior moments is computationally less burdensome.
 Considering that the expected random effects are a function of logistic regression coefficients $\boldsymbol{\beta}$, we can use the Delta method for the asymptotic Normal distribution of $p^E_{j}(\hat{\boldsymbol{\beta}}_{MLE})$.
 However, the Normal approximation goes through the same support and boundary issues as the shrinkage factors do.
-Instead, we approximate the conditional posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ by a Beta distribution using $\hat{\beta}_{MLE}$ and the Hessian value at the MLE.
+Instead, we approximate the conditional posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ by a Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$.
 
@@
 where $G(b_{1j})$ is a random variable following a Gamma$(b_{1j}, 1)$ distribution with a unit scale and independently $G(b_{0j})$ has a Gamma($b_{0j}, 1)$ distribution.
-Note that the representation in Equation (\ref{admpriormean}) is equivalent to saying $e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables.
+Note that the representation in Equation \ref{admpriormean} is equivalent to saying $e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables.
 Its mean and variance are
@@
 
-In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ follows $N[\hat{\beta}, \hat{\Sigma}]$, where $\hat{\boldsymbol{\beta}}$ is the mode of $p(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode.
+In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$ follows $N[\hat{\beta}, \hat{\Sigma}]$, where $\hat{\boldsymbol{\beta}}$ is the mode of $p(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode.
 Then the posterior distribution of $x_j^\top\boldsymbol{\beta}$ is also Normal with mean $x_j^\top\hat{\boldsymbol{\beta}}$ and variance $x_j^\top\hat{\Sigma} x_j$.
 
-Using the property of the log-Normal distribution, we get the estimates of posterior mean and variance in Equation (\ref{priormean1}) and (\ref{priorvariance1}) as
+Using the property of the log-Normal distribution, we get the numerical values of the posterior mean and variance in Equation \ref{priormean1} and \ref{priorvariance1} as
 \begin{eqnarray}
-\hat{\eta}_j&=&e^{x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2},\label{priormean2}\\
-~~~~~\widehat{Var}(e^{x_j^\top\boldsymbol{\beta}}\vert\boldsymbol{y})&=&\hat{\eta}^2_j\big(e^{x_j^{T}\hat{\Sigma} x_j}-1\big).\label{priorvariance2}
+\eta_j&=&e^{x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2},\label{priormean2}\\
+~~~~~\widehat{Var}(e^{x_j^\top\boldsymbol{\beta}}\vert\boldsymbol{y})&=&\eta^2_j\big(e^{x_j^{T}\hat{\Sigma} x_j}-1\big).\label{priorvariance2}
 \end{eqnarray}
 
-By matching the estimated mean and variance in Equation (\ref{priormean2}) and (\ref{priorvariance2}) to $b_{1j}$ and $b_{0j}$ in Equation (\ref{priormean1}) and (\ref{priorvariance1}), we obtain the estimates of $b_{1j}$ and $b_{0j}$ as follows;
+By matching the  mean and variance in Equation \ref{priormean2} and \ref{priorvariance2} to $b_{1j}$ and $b_{0j}$ in Equation \ref{priormean1} and \ref{priorvariance1}, we obtain the values of $b_{1j}$ and $b_{0j}$ as follows;
 \begin{equation}\label{priormeanpara}
-\hat{b}_{1j}=\hat{\eta}_j+\frac{\hat{\eta}_j + 1}{e^{x_j^{T}\hat{\Sigma} x_j}-1}~~\textrm{and}~~\hat{b}_{0j}=\frac{\hat{\eta}_j + 1}{\hat{\eta}_j(e^{x_j^{T}\hat{\Sigma} x_j}-1)}+2.
-\end{equation}
-
-The conditional posterior moments of expected random effects can be estimated similarly to those of shrinkage factors;  $E((p^E_{j})^d\vert\hat{\alpha}, \boldsymbol{y})=B(b_{1j} + d, b_{0j})/B(b_{1j}, b_{0j})$ for $d\ge0$.
-Finally, we estimate the unconditional posterior moments of expected random effects by their estimated conditional posterior moments as follows.
-\begin{equation}\label{priormeanmoments}
-\widehat{E}((p^E_{j})^d\vert\boldsymbol{y})= \frac{B(\hat{b}_{1j} + d, \hat{b}_{0j})}{B(\hat{b}_{1j}, \hat{b}_{0j})}.
-\end{equation}
+b_{1j}=\eta_j+\frac{\eta_j + 1}{e^{x_j^{T}\hat{\Sigma} x_j}-1}~~\textrm{and}~~b_{0j}=\frac{\eta_j + 1}{\eta_j(e^{x_j^{T}\hat{\Sigma} x_j}-1)}+2.
+\end{equation}
+
+Finally we estimate the unconditional posterior moments of the expected random effects, $E((p^E_{j})^c\vert\boldsymbol{y})$, by $E((p^E_{j})^c\vert\hat{\alpha}, \boldsymbol{y})=B(b_{1j} + c, b_{0j})/B(b_{1j}, b_{0j})$ for $c\ge0$.
+%\begin{equation}\label{priormeanmoments}
+%\widehat{E}((p^E_{j})^c\vert\boldsymbol{y})= \frac{B(\hat{b}_{1j} + c, \hat{b}_{0j})}{B(\hat{b}_{1j}, \hat{b}_{0j})}.
+%\end{equation}
 
@@
 
+For the Gaussian model \citep{tang2011}, the distribution of $\boldsymbol{\beta}$ given $\hat{A}$ and $\boldsymbol{y}$ is Normal whose mean and variance matrix are
+\begin{equation}
+(X^\top D^{-1}_{V+\hat{A}} X)^{-1}X^\top D^{-1}_{V+\hat{A}}\boldsymbol{y}~~ \textrm{and}~~ (X^\top D^{-1}_{V+\hat{A}} X)^{-1}, ~\textrm{respectively},
+\end{equation}
+where $X\equiv (\boldsymbol{x}_1, \boldsymbol{x}_2, \ldots, \boldsymbol{x}_k)^\top$ is a $k \times m$ covariate matrix and $D_{V+\hat{A}}$ is $k \times k$ diagonal matrix with the $j$-th diagonal element $V_j+\hat{A}$.
+Because $\boldsymbol{x}^\top\boldsymbol{\beta}$ given $\hat{A}$ and $\boldsymbol{y}$ is also Normally distributed, we obtain the conditional posterior moments of $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$ with ease and use them to estimate the unconditional posterior moments.
+
 \subsection{Estimation for random effects}
-It is intractable to derive the unconditional posterior distribution of each random effect analytically for both Binomial and Poisson models.
-Instead, we again assume that each random effect of the Binomial model has a Beta distribution as
-\begin{equation}\label{truebeta}
-p_j\vert \boldsymbol{y} \sim \textrm{Beta}(t_{1j}, t_{0j}),~\textrm{for}~ j=1, 2, \ldots, k,
-\end{equation}
-and each random effect of the Poisson model has a Gamma distribution as
-\begin{equation}\label{truebeta_poisson}
-\lambda_j\vert \boldsymbol{y} \sim \textrm{Gamma}(s_{1j}, s_{0j}),~\textrm{for}~ j=1, 2, \ldots, k.
-\end{equation}
+It is intractable to derive the unconditional posterior distribution of each random effect analytically for all three models.
+Instead, we  assume again that each random effect has a skewed Normal distribution \cite{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
+\begin{eqnarray}
+\mu_j\vert\boldsymbol{y} &\sim& \textrm{skewed-Normal}(\phi, \omega, \delta),\label{skewnormal}\\
+p_j\vert \boldsymbol{y} &\sim& \textrm{Beta}(t_{1j}, t_{0j}),\label{betapost}\\
+\lambda_j\vert \boldsymbol{y} &\sim& \textrm{Gamma}(s_{1j}, s_{0j}).\label{gammapost}
+\end{eqnarray}
+
+\cite{kelly2014advances}  matches estimated three unconditional posterior  moments of the random effects to the three parameters $(\phi, \omega, \delta$) of the skewed-Normal distribution in Equation \ref{skewnormal}.
 
 The unconditional posterior mean and variance of each random effect for the Binomial model specified in Equation \ref{postmean} and \ref{approximate_var} and those for the Poisson model in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}  are functions of the unconditional posterior moments of shrinkage factors and expected random effect.
-Once we plug-in the estimated unconditional posterior moments of shrinkage factors in Equation \ref{shrinkagemoments} and those of expected random effect in Equation \ref{priormeanmoments}, we get the estimates of the unconditional posterior mean and variance of each random effect in Equation \ref{postmean}  and \ref{postvar} denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
-For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimates of the unconditional posterior mean and variance in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}.
-The estimates of two parameters $t_{1j}$ and $t_{0j}$ in Equation \ref{truebeta} come as follows;
+By plugging-in the estimated unconditional posterior moments of shrinkage factors and those of expected random effect, we obtain the estimates of the unconditional posterior mean and variance of each random effect, denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
+For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimates of the unconditional posterior mean and variance.
+The estimates of two parameters $t_{1j}$ and $t_{0j}$ in Equation \ref{betapost} come as follows;
 \begin{equation}\label{posttrueprob}
@@
 \end{equation}
-The estimates of two parameters $s_{1j}$ and $s_{0j}$ in Equation \ref{truebeta_poisson} are
+The estimates of two parameters $s_{1j}$ and $s_{0j}$ in Equation \ref{gammapost} are
 \begin{equation}\label{posttrueprob}
@@
 
-The ADM approximation is accurate if the true distribution of $p_j$ is close to the the Beta distribution \citep{morris1997, tang2011, morris2012}.
-
-We use the posterior mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the posterior distribution in Equation \ref{trueapprox} for the Binomial model or in Equation \ref{trueapprox_poisson} for the Poisson model as the point and interval estimates of the random effect.
+%The ADM approximation is accurate if the true distribution of $p_j$ is close to the the Beta distribution \citep{morris1997, tang2011, morris2012}.
+
+We use the  mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the estimated approximate posterior distribution, a skewed Normal distribution for the Gaussian model, a Beta distribution in Equation \ref{trueapprox} for the Binomial model, or a Gamma distribution in Equation \ref{trueapprox_poisson} for the Poisson model, as the point and interval estimates of the random effect.
 
@@
 We match the mode of $g_1(\alpha)$ specified in Equation \ref{mode} to $\hat{\alpha}$ by fixing the location parameter $\mu$ at $\hat{\alpha}-(a-b)\sqrt{a+b}/\sqrt{(2a+1)(2b+1)}$.
-We set  the scale parameter $\sigma$ to $(-H^{-1}_{\hat{\alpha}})^{0.5}\eta$, where $\eta$ is a tuning parameter; $\eta=1.3$ is the default.
-When the A-R method produces extreme values of weights defined in Equation \ref{weight} below, we increase the value of $\eta$.
+We set  the scale parameter $\sigma$ to $(-H^{-1}_{\hat{\alpha}})^{0.5}\psi$, where $\psi$ is a tuning parameter; $\psi=1.3$ is the default.
+When the A-R method produces extreme values of weights defined in Equation \ref{weight} below, we increase the value of $\psi$.
 %To summarize, we use
@@
 
-The basic usage of fitting a Normal-Normal model via the function \code{gbp} is simply
-\begin{CodeChunk}
-\begin{CodeInput}
-R> output <- gbp(y, se, model = "gaussian")
-\end{CodeInput}
-\end{CodeChunk}
-
-The argument \code{y} is a vector of $k$ observed sufficient statistics, the argument  \code{se} for the Normal model is a vector of $k$ standard errors of the corresponding sufficient statistics, and the argument \code{model} indicates that  \code{gbp} fits a Normal-Normal model.
-
-There are many optional arguments for \code{gbp}.
+\subsection{Model fitting}
+The function \code{gbp} creates an G3 object ``gbp'' which provides three relevant functions \code{plot}, \code{print}, and \code{summary}.
+To use these relevant functions, we need to save the outcome of \code{gbp} into an object (see the code below).
+
+There are two cases according to whether covariates are available or not.
+When no covariates are available, the function \code{gbp} requires fitting an intercept term  or knowing the value of the  the expected random effect, meaning that the intercept term must be either estimated or known.
+The default of \code{gbp} in this case is to fit an intercept term.
+We can assign the value of the known expected random effect through an optional argument \code{mean.PriorDist}.
+Note that \code{gbp} can fit the Poisson model only when the value of expected random effect, $\lambda^E$, is known.
+The usage of \code{gbp} to  fit each model without any covariates is
+\begin{CodeChunk}
+\begin{CodeInput}
+R> g.output <- gbp(y, se.or.n, model = "gaussian")
+R> b.output <- gbp(y, se.or.n, model = "binomial")
+R> p.output <- gbp(y, se.or.n, mean.PriorDist, model = "poisson")
+\end{CodeInput}
+\end{CodeChunk}
+
+The argument \code{y} is a vector of $k$ observed sufficient statistics, i.e., $k$ observed sample means for the Gaussian model, $k$ observed numbers of successful outcomes for the Binomial model, and $k$ observed numbers of events happening for the Poisson model.
+The argument  \code{se.or.n} is a vector of $k$ standard errors of the sample mean for the Gaussian model, $k$ numbers of trials for the Binomial model, and $k$ exposures for the Poisson model.
+If we want to designate a known value of the expected random effect $\mu^E=\beta_1$ for the Gaussian model or $p^E=\exp(\beta_1)/(1+\exp(\beta_1))$ for the Binomial model, then we put that value into \code{gbp} using an argument \code{mean.PriorDist}.
+For example, if the $\mu^E$ is known as 10, then we use the following code.
+The usage of the Binomial model is the same.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> g.output <- gbp(y, se.or.n, mean.PriorDist = 10, model = "gaussian")
+\end{CodeInput}
+\end{CodeChunk}
+
+If covariate information for each group is available, we can fit the Gaussian and Binomial models, using the following codes.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> g.output <- gbp(y, se.or.n, X, model = "gaussian")
+R> b.output <- gbp(y, se.or.n, X, model = "binomial")
+\end{CodeInput}
+\end{CodeChunk}
+
+The argument \code{X} is a matrix of covariate(s) each column of which corresponds to one covariate for $k$ groups.
+For example, if we have two covariates for each group, the argument \code{X} must be $k\times2$ matrix to estimate three regression coefficients $\boldsymbol{\beta}=(\beta_1, \beta_2, \beta_3)$ including an intercept term as a default.
+If we do not want to include an intercept term, estimating two regression coefficients for the two covariates, we add an optional argument \code{intercept} as follows.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> g.output <- gbp(y, se.or.n, X, model = "gaussian", intercept = FALSE)
+\end{CodeInput}
+\end{CodeChunk}
+
+The function \code{gbp} contains several optional arguments.
+The argument \code{Alpha}, whose default is 0.95, sets the confidence level, producing $100\times$\code{Alpha}\% interval estimates of the random effects.
+For the Gaussian model, setting the argument \code{normal.CI} to \code{TRUE} makes \code{gbp} use a Normal approximation to the unconditional posterior distribution of the random effect.
+The default of \code{normal.CI} is \code{FALSE} for the skewed Normal approximation.
+
+The function \code{gbp} uses the acceptance-rejection method to fit the Binomial model if we assign the desired number of posterior samples ($N$ in Equation \ref{weight}) to the argument \code{n.AR}; its default value is 0.
+There are several arguments related to the acceptance-rejection method.
+The argument \code{n.AR.factor} determines how many trial samples the method draws; its default value is 4, meaning that the method draws \code{n.AR} $\times4$ trial samples and accepts some of them.
+The argument \code{trial.scale} is $\psi$ determining the scale parameter of the skewed-$t$ distribution (the envelope function); its default value is 1.3.
+The argument \code{save.result} indicates whether we save the whole posterior samples of the random effects and hyper-parameters; its default value is \code{TRUE}.
+The two arguments \code{t} and \code{u}, taking on positive values, allow users to chose the joint hyper-prior distribution $f(r, \boldsymbol{\beta})\propto d\boldsymbol{\beta}dr/(t+r)^{u+1}$; the default values for \code{t} and \code{u} are 0 and 1 for the joint hyper-prior distribution specified in Equation \ref{eq:hyper}.
+For example, when there are two covariates, the following code produces 2,000 posterior samples of random effects and hyper-parameters, $r$ and $\boldsymbol{\beta}_{3\times1}$ including an intercept term, via the acceptance-rejection method with 8,000 trial samples.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> b.output <- gbp(y, se.or.n, X, model = "binomial", n.AR = 2000)
+\end{CodeInput}
+\end{CodeChunk}
+
+The G3 object ``gbp'', for example \code{b.output} above, contains detailed outcomes.
+The function \code{names} will show the list of outcomes (too many to be listed in this article); see the document of \code{gbp} to check the details of the items.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> names(b.output)
+R> ?gbp
+\end{CodeInput}
+\end{CodeChunk}
+
+The G3 object makes use of some functions, \code{print}, \code{summary}, and \code{plot}.
+The estimation result for all the random effects pops up if we type the ``gbp'' object at the \proglang{R} console, which is the same as the following function \code{print} with its default argument ``\code{sort = TRUE}'' that prints out the estimation result for all the groups in the ascending order of $n$ for the Binomial and Poisson model and the descending order of standard errors for the Gaussian model.
+When the argument \code{sort} is \code{FALSE}, the estimation result comes out as the order of data input.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> b.output
+R> print(b.output, sort = FALSE)
+\end{CodeInput}
+\end{CodeChunk}
+
+The function \code{summary} prints a detailed estimation summary, including the estimation result for the hyper-parameters.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> summary(b.output)
+\end{CodeInput}
+\end{CodeChunk}
+
+The function \code{plot} draws a shrinkage plot and $100\times$\code{Alpha}\% interval plot for random effects with its default argument ``\code{sort = TRUE}'' that draws the $100\times$\code{Alpha}\% interval plot in the ascending order of $n$ for the Binomial and Poisson model and the descending order of standard errors for the Gaussian model.
+When the argument \code{sort} is set to \code{FALSE} the the $100\times$\code{Alpha}\% will be based on the order of data input.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> plot(b.output)
+R> plot(b.output, sort = FALSE)
+\end{CodeInput}
+\end{CodeChunk}
+
+\subsection{Frequency method checking}
+The function \code{coverage} conducts a frequency method checking that estimates the coverage probabilities of  random effects, conditioning on the values of the hyper-parameters that generate random effects and  mock data sets.
+The basic usage of \code{coverage} contains a ``gbp'' object, such as \code{b.output} above, as the first argument as follows.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> cov <- coverage(b.output, nsim = 1000)
+\end{CodeInput}
+\end{CodeChunk}
+
+The argument \code{sim} sets the number of simulations $N_{sim}$ defined in Section \ref{sec4}.
+If we do not assign values of the hyper-parameters by the arguments \code{A.or.r} and \code{reg.coef} as above, then the function \code{coverage} automatically sets the estimated posterior modes of hyper-parameters saved in the ``gbp'' object (or their posterior medians if the acceptance-rejection method for the Binomial model is used) to the generative values of hyper-parameters.
+If we want to conduct the frequency method checking with different generated values of hyper-parameters, for example, $r=100$ and $\boldsymbol{\beta}^\top=(2, 5)$ when one covariate was used (including an intercept term) to create the ``gbp'' object, then we specify the code as
+\begin{CodeChunk}
+\begin{CodeInput}
+R> cov <- coverage(b.output, A.or.r = 100, reg.coef = c(2, 5), nsim = 1000)
+\end{CodeInput}
+\end{CodeChunk}
+
+When we fit a model with a known value of the expected random effect, we may want to conduct the frequency method checking with a different value for the expected random effect.
+In this case, the argument \code{mean.PriorDist} enables it.
+For example, when we obtain the ``gbp'' object \code{p.output}   after fitting a Poisson model with a specific value of  $\lambda^E$, if we want to conduct the frequency method checking with the same specific value of  $\lambda^E$, then we do not specify the argument \code{mean.PriorDist} in \code{coverage}.
+Once we specify the argument \code{mean.PriorDist} in \code{coverage}, for example 30 as below, the frequency method checking will be based on the estimated posterior mode of $r$ and the newly specified value of $\lambda^E$, 30.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> cov <- coverage(p.output, mean.PriorDist = 30, nsim = 1000)
+\end{CodeInput}
+\end{CodeChunk}
+
+%  So, in order to generate pseudo-datasets, \code{coverage} needs parameters of prior distribution,  
+%  (\emph{A} (or \emph{r}) and \eqn{\beta} (\code{reg.coef})) 
+%  or (\emph{A} (or \emph{r}) and \eqn{\mu_{0}}{\mu0}). From here, we have four options to run \code{coverage}.
+
+%  First, if any values related to the prior distribution are not designated like 
+%  \code{coverage(b, nsim = 10)}, then \code{coverage} will regard estimated values (or known prior mean, \eqn{\mu_{0}}{\mu0}) in \code{b} (\code{gbp.object}) as given true values when it generates lots of pseudo-datasets.
+After sampling \eqn{\theta_{(i)}}{\theta_(i)} from the prior distribution determined by these estimated values (or known prior mean) in \code{b} (\code{gbp.object}), \code{coverage} creates an \emph{i}-th pseudo-dataset based on \eqn{\theta_{(i)}}{\theta_(i)} just sampled.
+
+%  Second, \code{coverage} allows us to try different true values in generating datasets.
+Suppose \code{gbp.object} is based on the model with a known prior mean, \eqn{\mu_{0}}{\mu0}.
+Then, we can try either different \code{A.or.r} or \code{mean.PriorDist}.
+For example, \code{coverage(b, A.or.r = 20, nsim = 10)},
+%\code{coverage(b, mean.PriorDist = 0.5, nsim = 10)}, or 
+%\code{coverage(b, A.or.r = 20, mean.PriorDist = 0.5, nsim = 10)}. Note that we cannot set \code{reg.coef} because the second-level mean (prior mean) is known in \code{gbp.object} to begin with.
+
+%  Suppose \code{gbp.object} is based on the model with an unknown prior mean.
+In this case, \code{gbp.object} has the estimation result of regression model, linear regression for Normal-Normal, log-linear regression for Poisson-Gamma, or logistic regression for Binomial-Beta, (only intercept term if there is no covariate) to estimate the unknown prior mean.
+Then, we can try some options: one or two of (\code{A.or.r}, \code{mean.PriorDist}, \code{reg.coef}).
+For example, \code{coverage(b, A.or.r = 20, nsim = 10)}, \code{coverage(b, mean.PriorDist = 0.5, nsim = 10)}, or \code{coverage(b, reg.coef = 0.1, nsim = 10)} with no covariate where \code{reg.coef} is a designated intercept term.
+Estimates in \code{gbp.object} will be used for undesignated values.
+Also, we can try appropriate combinations of two arguments.
+For example, \code{coverage(b, A.or.r = 20, mean.PriorDist = 0.5, nsim = 10)} and
+%\code{coverage(b, A.or.r = 20, reg.coef = 0.1, nsim = 10)}.
+If we have one covariate, a 2 by 1 vector should be designated for \code{reg.coef}, one for an intercept term and the other for a regression coefficient of the covariate.
+Note that the two arguments, \code{mean.PriorDist} and \code{reg.coef}, cannot be assigned together because we do not need \code{reg.coef} given \code{mean.PriorDist}.
+
+%  The simple unbiased estimator of coverage probability in \emph{j}-th group is a sample mean of indicators over all simulated datasets.
+The \emph{j}-th indicator in \emph{i}-th simulation is 1 if the estimated interval of the \emph{j}-th group on \emph{i}-th simulated dataset contains a true parameter
+%  \eqn{\theta_{(i)j}}{\theta_(i)j} that generated the observed value of the \emph{j}-th group in the 
+%  \emph{i}-th dataset.
+
+%  Rao-Blackwellized unbiased estimator for group \emph{j} is a conditional expectation of the simple unbiased estimator given a sufficient statistic, \eqn{y_{j}}{y_j} for Gaussian or \eqn{z_{j}}{z_j} for Binomial and Poisson data.
 
@@
 \section{Unconditional posterior variance of the Binomial model}\label{apppostvar}
+\section{Unconditional posterior variance of the Gaussian model}\label{apppostvar_normal}
 

### 2015-06-09 jss/article_v2.tex
draft examples

@@
 
+\subsubsection{Rao-Blackwellized overall unbiased coverage estimator}\label{overallRB} Assuming that the unknown  coverage probabilities are the same for all random effects, we use the Rao-Blackwellized overall coverage estimator and its variance estimator as follows.
+\begin{equation}\label{RBoverall}
+\bar{\bar{I}}^{RB}_{r, \boldsymbol{\beta}} = \frac{1}{k}\sum_{j=1}^k\bar{I}^{RB}_{r, \boldsymbol{\beta}}(p_j)~~\textrm{and}~~ \widehat{Var}(\bar{\bar{I}}_{RB})=\frac{1}{k^2}\sum_{j=1}^k\widehat{Var}(\bar{I}^{RB}_{r, \boldsymbol{\beta}}(p_j)).
+\end{equation}
+
 \section[packageoverview]{Usage of functions in \pkg{Rgbp}}\label{sec5}
@@
 R> cov <- coverage(p.output, mean.PriorDist = 30, nsim = 1000)
+\end{CodeInput}
+\end{CodeChunk}
+
+Although the function \code{coverage} does not produce a G3 object, a detailed summary appears in a plot that automatically pops up after running the function \code{coverage}.
+In addition, the object \code{cov} that contains the result of \code{coverage} as shown above contains numerical details, see \code{names(cov)} for the list of detailed outcomes.
+If we save the result into an object such as \code{cov} above, then we can always recall the plot, using the function \code{coverage.plot}.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> names(cov)
+R> coverage.plot(cov)
 \end{CodeInput}
@@
 \section[Examples]{Examples}\label{sec6}
-\subsection[Known Second-level Mean]{Data of 31 hospitals with a known second-level mean}
+\subsection[Known Second-level Mean]{Data of 31 hospitals with a known expected random effect}
 \label{sec:ex:hosp}
-In this example we adopt the perspective of a person living in the state of New York (NY) who has been suffering from severe coronary heart disease.
-If this person must receive coronary artery bypass graft (CABG) surgery soon, he or she might want to find the most reliable hospital for such a procedure.
-
-For this purpose, data were gathered from 31 hospitals in NY composed of the number of deaths ($\textbf{z}_{(31\times1)}$) for a specified period after CABG surgeries and the total number of patients ($\textbf{n}_{(31\times1)}$) receiving CABG surgeries in each hospital.
-For reference, caseloads ($n_{j}$) can be interpreted as exposures.
-These data can be loaded into \proglang{R} using the following code where the symbol `\code{R>}' represents a command prompt and is not to be typed into \proglang{R}.
-
-\begin{CodeChunk}
-\begin{CodeInput}
-R> z <- c( 3,   2,   5,  11,   9,  12,  12,   4,  10,  13,  14,   7,  12,
-          11,  13,  22,  15,  11,  14,  11,  16,  14,   9,  15,  13,  35,
-          26,  25,  20,  35,  27)
-R> n <- c(67,  68, 210, 256, 269, 274, 278, 295, 347, 349, 358, 396, 431,
-         441, 477, 484, 494, 501, 505, 540, 563, 593, 602, 629, 636, 729,
-         849, 914, 940, 1193, 1340)
-\end{CodeInput}
-\end{CodeChunk}
-or
-\begin{CodeChunk}
-\begin{CodeInput}
-R> data(``hospital'')
-R> z <- hospital$d
+
+We analyze a data set of 31 hospitals in New York state comprising of the outcomes of the coronary artery bypass graft (CABG) surgery \citep{morris2012}.
+The data set contains the number of deaths, $\boldsymbol{y}$, for a specified period after CABG surgeries out of the total number of patients, $\boldsymbol{n}$, receiving CABG surgeries in each hospital.
+Health care providers may use these data to improve their care qualities, and patients may refer to the data to select a better hospital.
+Our goal is to obtain the point and interval estimates for the unknown true mortality rates of 31 hospitals (random effects) to evaluate  each hospital's reliability on the CABG surgery.
+We interpret the caseloads, $\boldsymbol{n}$,  as exposures and assume that the state-level death rate per exposure of this surgery is known as 0.030 ($\lambda^E$) to fit the Poisson model for an illustrative purpose.
+If covariate information is available or the expected random effect is not known, we recommend using the Binomial model for these data.
+
+These data can be loaded into \proglang{R} using the following code.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> library(Rgbp)
+R> data(hospital)
+R> y <- hospital$d
 R> n <- hospital$n
@@
 
-In addition, suppose one knows that the state-level death rate per exposure of this surgery is 0.030 ($\lambda_{0}$).
+%In addition, suppose one knows that the state-level death rate per exposure of this surgery is 0.030 ($\lambda_{0}$).
 Using these data and the known second-level mean ($\lambda_{0}$), \pkg{Rgbp} provides point and interval estimates of the true death rate ($\lambda_{j}$) so that one can evaluate each hospital's reliability.
 
-The independent Poisson distribution, i.e.,  $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be an ideal choice to describe these data based on the Poisson approximation when $\lambda$ is small and $n$ is relatively large.
-
-Next, \code{gbp} fits the Poisson hierarchical model with the Gamma conjugate prior distribution as the NY state-level population distribution of the death rates whose mean is 0.030 ($\lambda_{0}=0.030$).
-For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean (the second-level mean) via regression for this Poisson-Gamma model.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> p <- gbp(z, n, mean.PriorDist = 0.03, model = "poisson")
-R> p
+%The independent Poisson distribution, i.e.,  $y_j\vert \lambda_j\stackrel{indep.}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be an ideal choice to describe these data based on the Poisson approximation when $\lambda$ is small and $n$ is relatively large.
+
+The function \code{gbp} fits the Poisson hierarchical model with the Gamma conjugate prior distribution as a population distribution of the death rates in New York states whose mean ($\lambda^E$) is 0.030.
+The number of regression coefficients ($m$) is 0 because we do not need to estimate the expected random effect via a log-linear regression for this Poisson-Gamma model.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> p.output <- gbp(z, n, mean.PriorDist = 0.03, model = "poisson")
+R> p.output
 \end{CodeInput}
@@
 
-For reference, we need to type `\code{R> print(p, sort = FALSE)}' instead of `\code{R> p}' in order to list hospitals by the order of data input in the above output.
-`\code{R> p}' automatically sorts the output by the increasing order of caseload ($n_{j}$), as shown above.
-
-The output contains information about observed death rates ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds of interval estimates ($\hat{\lambda}_{j, low}$, 2.5\% percentiles of the approximate posterior distributions if 95\% confidence level is given), approximate posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \boldsymbol{y})$), upper bounds  of interval estimates ($\hat{\lambda}_{j, upp}$, 97.5\% percentiles of the approximate posterior distributions), and standard deviations of the approximate posterior distributions ($sd(\lambda_{j}\vert \boldsymbol{y})$).
-
-As we can see in (\ref{gammapost}), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a convex combination of the sample mean and prior mean ($\lambda_{0}=0.030$) with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight.
+The output contains information about the observed death rates $y_{j}$, caseloads $n_{j}$, known prior mean $\lambda^E$, shrinkage estimates $\hat{B}_{j}$, lower bounds of interval estimates $\hat{\lambda}_{j, low}$, posterior means $\hat{\lambda}_j\equiv E(\lambda_{j}\vert \boldsymbol{y})$, upper bounds  of interval estimates $\hat{\lambda}_{j, upp}$, and posterior standard deviations  for each random effect based on the assumed unconditional Gamma posterior distributions.
+%The lower and upper bounds of an interval estimate for a random effect are 2.5\% and 97.5\% percentiles of the assumed unconditional Gamma posterior distributions if 95\% confidence level is used.
+
+Note that the conditional posterior mean of random effect $j$ in Equation \ref{gammapost_mean_var} is $(1-B_{j})\bar{y}_{j} + B_{j}\lambda^E$,  a convex combination of the observed death rate and expected random effect with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight.
 This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree (sample sizes) of prior and observed information respectively.
 If the second level has more information than the first level, i.e., ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the estimator will shrink towards the prior mean more than 50\%.
-This is clear because, as caseload increases, shrinkage decreases, depending less on the NY state-level (second-level) information.
-
-A function \code{summary} shows selective information on hospitals and more detailed estimation results, as below.
-To be specific, it displays some hospitals (not all as above) with minimum, median, and maximum caseloads ($n_{j}$).
-On top of that, more specific estimation results, such as the posterior mode and standard deviation of $\alpha\equiv\log(1/r)$, follow.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> summary(p)
+This is clear because, as caseload increases, shrinkage decreases, depending less on the  state-level (second-level) conjugate Gamma prior distribution.
+
+A function \code{summary} shows selective information about hospitals with minimum, median, and maximum exposures and more detailed estimation results about the hyper-parameter $\alpha=-\log(r)$.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> summary(p.output)
 \end{CodeInput}
@@
 post.mode.alpha post.sd.alpha post.mode.r
-1           -6.53         0.576         684
+          -6.53         0.576         684
 \end{CodeOutput}
 \end{CodeChunk}
-The output of \code{summary} also provides $\hat{r}=\textrm{exp}(6.53)=684$, which is an indicator of how valuable and informative the hypothetical second-level hierarchy is.
+The output of \code{summary} also provides $\hat{r}=\textrm{exp}(6.53)=684$, which is an indicator of how valuable and informative the second-level hierarchy is.
 It means that observed sample means of hospitals whose caseloads are less than 684 will shrink toward the prior mean (0.030) more than 50\%.
 For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.911$) was calculated by 684 / (684 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.911)*0.0448 + 0.911 * 0.030=0.0313$.
-As for this hospital, using more information from the prior distribution is an appropriate choice because the observed amount of information (67) is far less than the amount of state-level information (684).
-
-To obtain a graphical summary the function \code{plot} can be used, as seen in Figure \ref{fig:hospshr}.
-
-\begin{CodeChunk}
-\begin{CodeInput}
-R> plot(p)
+As for this hospital, using more information from the conjugate prior distribution is an appropriate choice because the amount  of observed information (67) is far less than the amount of state-level information (684).
+
+To obtain a graphical summary, we use the function \code{plot}.%, as seen in Figure \ref{fig:hospshr}.
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> plot(p.output)
 \end{CodeInput}
@@
 
-In Figure \ref{fig:hospshr} the regression towards the mean (RTTM) is obvious in the first graph; the observed sample means, empty dots on the upper horizontal line, are shrinking towards the known second-level mean (a blue vertical line at 0.030) to the different extents.
-Note that some hospitals' ranks have changed by shrinking much harder towards 0.030 than others.
-For example, the empty square symbol at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that  the seemingly safest hospital among 31 hospitals in terms of the observed death rate is probably not the safest in terms of the estimated posterior means.
-
-Intuitively, switching ranks for these two hospitals makes sense.
-To be specific, their observed death rates ($y_{j}$, $j=8, 23$) are 0.0136 and 0.0150 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602 each.
+In Figure \ref{fig:hospshr} the regression towards the mean (RTTM) is obvious in the first graph; the observed death rates, denoted by empty dots on the upper horizontal line, are shrinking towards the known expected random effect, denoted by a blue vertical line at 0.030, to the different extents.
+Note that some hospitals' ranks have changed by shrinking much harder towards 0.030 than the others.
+For example, an empty square at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that  the seemingly safest hospital among 31 hospitals in terms of the observed death rate is probably not the safest in terms of the estimated posterior mean accounting for the different caseloads of these two hospitals.
+
+Intuitively, switching ranks for these two hospitals is reasonable.
+To be specific, their observed death rates ($y_{j}$, $j=8, 23$) are 0.0136 and 0.0150 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602, respectively.
 Considering solely the observed death rates may lead to an unfair comparison because the latter hospital handled twice the caseload.
-\pkg{Rgbp} accounts for this caseload difference, making the death rate estimate for the former hospital shrink toward the state-level mean ($\lambda_{0}$=0.030) much harder than that for the latter hospital.
-
-Note that the point estimates are not enough to evaluate hospital reliability because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other.
-In the second plot of Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed.
-We see that each posterior mean (red dot) is between the sample mean (empty dot) and the second-level mean (a blue horizontal line).
-For reference, we could plot this 95\% interval plot by the order of data input via \code{plot(p, sort = FALSE)}.
-
-This 95\% interval plot reveals that the 31st hospital has the lowest upper bound even though its point estimate ($\hat{\lambda}_{31}=0.0235$) is slightly bigger than that of the 23rd hospital ($\hat{\lambda}_{23}=0.0230$).
+\pkg{Rgbp} accounts for this caseload difference, making the posterior mean for the random effect of the former hospital shrink toward the state-level mean ($\lambda^E$=0.030) much harder than that for of the latter hospital.
+
+Note that the point estimates are not enough to evaluate hospital reliability because one hospital may have a lower point estimate but  larger uncertainty (variance) than the other.
+The second plot of Figure \ref{fig:hospshr} displays the estimated 95\% intervals.
+We see that each posterior mean (red dot) is between the sample mean (empty dot) and the known expected random effect (a blue horizontal line).
+%For reference, we could plot this 95\% interval plot by the order of data input via \code{plot(p, sort = FALSE)}.
+
+This 95\% interval plot reveals that the 31st hospital has the lowest upper bound even though its point estimate ($\hat{\lambda}_{31}=0.0235$) is slightly larger than that of the 23rd hospital ($\hat{\lambda}_{23}=0.0230$).
 The observed death rates for these two hospitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
-The 31st hospital has twice the caseload, which leads to borrowing less information from the NY state-level hierarchy (or shrinking less toward the state-level mean, 0.030) with smaller variance.
+The 31st hospital has twice the caseload, which leads to borrowing less information from the New York state-level hierarchy (or shrinking less toward the state-level mean, 0.030) with smaller variance.
 Based on the point and interval estimates, the 31st hospital seems the most reliable one among all candidates.
@@
 When fitting a model it is always a good idea to question how reliable the estimation procedure is.
-For example, does our procedure generate interval estimates that have good repeated sampling properties?
-To answer this question the \code{coverage} function generates pseudo-datasets assuming the estimated $r~(=683.53)$ is a true value.
-For reference, we can designate any other value of $r$, for example $r=600$, by adding another argument, \code{A.or.r = 600}, into the code below; \code{R> pcv <- coverage(p, A.or.r = 600, nsim = 1000)}.
-
-In addition, \code{gbp} also provides interval estimates with different confidence levels, for example 90\%.
+The function \code{coverage}  generates pseudo-datasets given the estimated value of $r$, 683.53, as a generative value.
+For reference, we can designate any generative values of $r$ and $\lambda^E$ by adding two arguments into the code below, for example, \code{A.or.r = 600} and \code{mean.PriorDist = 0.05}.
+%; \code{R> pcv <- coverage(p, A.or.r = 600, nsim = 1000)}.
+%For example, does our procedure generate interval estimates that have good repeated sampling properties? To answer this question
+
+%In addition, \code{gbp} also provides interval estimates with different confidence levels, for example 90\%.
 For this, we need to go back to the code for fitting the model, adding another argument, \code{Alpha = 0.9}; \code{R> p <- gbp(z, n, Alpha = 0.9, mean.PriorDist = 0.03, model = "poisson")}.
@@
 \begin{CodeInput}
-R> pcv <- coverage(p, nsim = 1000)
+R> p.coverage <- coverage(p.output, nsim = 1000)
 \end{CodeInput}
@@
 
-In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level and the red circles indicate Rao-Blackwellized (RB) unbiased coverage estimates for 31 hospitals.
-The overall RB unbiased coverage estimate across all the hospitals is 0.953.
-And none of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads ($n_{j}$).
-This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling.
-Note that these estimates depend on the given true value of $r$, the known prior mean, and the assumption that the model is true.
-
-The following code provides 31 RB unbiased coverage estimates for each hospital.
+In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level (\code{Alpha = 0.95} as a default) and the red circles indicate Rao-Blackwellized (RB) unbiased coverage estimates, $\bar{I}^{RB}_{r, \lambda^E}(\lambda_j)$ for $j=1, 2, \ldots, 31$.
+The overall RB unbiased coverage estimate across all the hospitals is 0.955.
+None of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads ($n_{j}$).
+This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence level.
+
+%Note that these estimates depend on the given true value of $r$ the known prior mean, and the assumption that the model is true.
+
+The following code provides specific values of the 31 RB unbiased coverage estimates and their standard errors for each hospital.
 \begin{CodeChunk}
@@
 R> pcv$coverageRB
-\end{CodeInput}
-\begin{CodeOutput}
- [1] 0.955 0.954 0.955 0.954 0.954 0.954 0.954 0.954 0.954 0.954 0.954 0.954
-[13] 0.954 0.953 0.953 0.954 0.953 0.954 0.954 0.953 0.953 0.953 0.954 0.953
-[25] 0.953 0.953 0.952 0.953 0.952 0.952 0.952
-\end{CodeOutput}
-\end{CodeChunk}
-
-And the code below shows 31 simple unbiased coverage estimates for each hospital.
+R> pcv$se.coverageRB
+\end{CodeInput}
+%\begin{CodeOutput}
+% [1] 0.955 0.954 0.955 0.954 0.954 0.954 0.954 0.954 0.954 0.954 0.954 0.954
+%[13] 0.954 0.953 0.953 0.954 0.953 0.954 0.954 0.953 0.953 0.953 0.954 0.953
+%[25] 0.953 0.953 0.952 0.953 0.952 0.952 0.952
+%\end{CodeOutput}
+\end{CodeChunk}
+
+And the code below shows 31 simple unbiased coverage estimates and their standard errors for each hospital.
 \begin{CodeChunk}
@@
 R> pcv$coverageS
-\end{CodeInput}
-\begin{CodeOutput}
- [1] 0.949 0.960 0.958 0.958 0.950 0.945 0.960 0.953 0.960 0.956 0.955 0.946 
-[13] 0.955 0.954 0.960 0.965 0.955 0.952 0.960 0.956 0.959 0.955 0.964 0.960 
-[25] 0.945 0.942 0.947 0.960 0.940 0.946 0.956
-\end{CodeOutput}
-\end{CodeChunk}
-
-The function \code{coverage} also calculates the standard errors for each hospital's RB unbiased coverage estimate defined in (\ref{RBvar}).
+R> pcv$se.coverageS
+\end{CodeInput}
+%\begin{CodeOutput}
+% [1] 0.949 0.960 0.958 0.958 0.950 0.945 0.960 0.953 0.960 0.956 0.955 0.946 
+%[13] 0.955 0.954 0.960 0.965 0.955 0.952 0.960 0.956 0.959 0.955 0.964 0.960 
+%[25] 0.945 0.942 0.947 0.960 0.940 0.946 0.956
+%\end{CodeOutput}
+\end{CodeChunk}
+
+%The function \code{coverage} also calculates the standard errors for each hospital's RB unbiased coverage estimate defined in (\ref{RBvar}).
 The following code provides 31 standard errors for RB estimates.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> pcv$se.coverageRB
-\end{CodeInput}
-\begin{CodeOutput}
- [1] 0.0016 0.0016 0.0014 0.0014 0.0013 0.0013 0.0013 0.0013 0.0012 0.0013 0.0012 
-[12] 0.0012 0.0011 0.0011 0.00110.0011 0.0011 0.0011 0.0011 0.0011 0.0010 0.0010 
-[23] 0.0010 0.0010 0.0010 0.0009 0.0009 0.0008 0.0008 0.0007 0.0007
-\end{CodeOutput}
-\end{CodeChunk}
-Similarly, 31 standard errors for each simple unbiased coverage estimate defined in (\ref{svar}) are
-\begin{CodeChunk}
-\begin{CodeInput}
-R> pcv$se.coverageS
-\end{CodeInput}
-\begin{CodeOutput}
- [1] 0.0070 0.0062 0.0063 0.0063 0.0069 0.0072 0.0062 0.0067 0.0062 0.0065 0.0066
-[12] 0.0072 0.0066 0.0066 0.0062 0.0058 0.0066 0.0068 0.0062 0.0065 0.0063 0.0066 
-[23] 0.0059 0.0062 0.0072 0.0074 0.0071 0.0062 0.0075 0.0072 0.0065
-\end{CodeOutput}
-\end{CodeChunk}
-
-Taking the first hospital as an example, the variance estimate of RB unbiased coverage estimate is about 19 times smaller than that of simple one.
-It means that 1,000 RB unbiased coverage estimates are as precise as 19,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital, $p_{cov, 1}$.
-
-For reference, two $31 \times 1,000$ matrices \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual estimates, $I^{(i)}_{j}$ and $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \boldsymbol{\beta})$.
-
-\cite{1995} also investigated a similar ranking problem in hierarchical modeling, taking shrinkage into account.
-
-\subsection[Unknown Second-level Mean and No Covariate]{Data of 8 schools with unknown second-level mean with no covariates} \label{sec:ex:8schools}
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%\end{CodeInput}
+%\begin{CodeOutput}
+% [1] 0.0016 0.0016 0.0014 0.0014 0.0013 0.0013 0.0013 0.0013 0.0012 0.0013 0.0012 
+%[12] 0.0012 0.0011 0.0011 0.00110.0011 0.0011 0.0011 0.0011 0.0011 0.0010 0.0010 
+%[23] 0.0010 0.0010 0.0010 0.0009 0.0009 0.0008 0.0008 0.0007 0.0007
+%\end{CodeOutput}
+%\end{CodeChunk}
+%Similarly, 31 standard errors for each simple unbiased coverage estimate defined in (\ref{svar}) are
+%\begin{CodeChunk}
+%\begin{CodeInput}
+
+%\end{CodeInput}
+%\begin{CodeOutput}
+% [1] 0.0070 0.0062 0.0063 0.0063 0.0069 0.0072 0.0062 0.0067 0.0062 0.0065 0.0066
+%[12] 0.0072 0.0066 0.0066 0.0062 0.0058 0.0066 0.0068 0.0062 0.0065 0.0063 0.0066 
+%[23] 0.0059 0.0062 0.0072 0.0074 0.0071 0.0062 0.0075 0.0072 0.0065
+%\end{CodeOutput}
+%\end{CodeChunk}
+
+It turns out that the variance estimate of the RB unbiased coverage estimate for the first hospital ($0.0016^2$) is about 19 times smaller than that of the simple one ($0.0070^2$).
+It means that the RB unbiased coverage estimates based on 1,000 simulations ($N_{sim}$) are as precise as the simple unbiased coverage estimates based on 19,000 simulations in terms of estimating the coverage probability for the first hospital, $C_{r, \lambda^E}(\lambda_1)$.
+
+%For reference, two $31 \times 1,000$ matrices \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual estimates, $I^{(i)}_{j}$ and $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \boldsymbol{\beta})$.
+
+See \cite{1995} for a similar ranking problem using a Poisson hierarchical modeling with a different parametrization.
+
+\subsection[Unknown Second-level Mean and No Covariate]{Data of 8 schools with unknown expected random effect and no covariates} \label{sec:ex:8schools}
 
@@
 The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \citep{1981}.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
-R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
-\end{CodeInput}
-\end{CodeChunk}
-or
-\begin{CodeChunk}
-\begin{CodeInput}
-R> data(``schools'')
+We can load this data set into \proglang{R} by the following codes.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> library(Rgbp)
+R> data(schools)
 R> y  <- schools$y
@@
 
-Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, i.e., standard error of each school is assumed to be known.
-At the second hierarchy, the mean for each school is assumed to be drawn from a common Normal distribution and hence, we can use the Gaussian component of \code{gbp} to fit this Normal-Normal hierarchical model.
-
-\begin{CodeChunk}
-\begin{CodeInput}
-R> g <- gbp(y, se, model = "gaussian")
-R> g
+Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, i.e., standard error of each school is completely known.
+At the second hierarchy, the mean for each school is assumed to be drawn from a common Normal distribution and hence, we can use the Gaussian component of \code{gbp} to fit this Gaussian hierarchical model.
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> g.output <- gbp(y, se, model = "gaussian")
+R> g.output
 \end{CodeInput}
@@
 This output from \code{gbp} summarizes the results.
-In this Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_j = V_j/(V_j + A)$.
+In this Gaussian hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_j = V_j/(V_j + A)$.
 As such, schools whose variation within the school ($V_{j}$) is less than the between school variation ($A$) will shrink greater than $50\%$.

### 2015-06-09 Rgbp/R/gbp.R

@@ -276,11 +276,8 @@ summary.gbp <- function(object, ...) {
   
   if (any(is.na(object$prior.mean))) {
     estimate <- as.vector(object$beta.new)
-    if (object$intercept == TRUE) {
-      names(estimate) <- paste("beta", 0 : (length(estimate) - 1), sep = "")
-    } else {
-      names(estimate) <- paste("beta", 1 : (length(estimate)), sep = "")
-    }
+    names(estimate) <- paste("beta", 1 : length(estimate), sep = "")
+
     if ((sum(is.na(object$weight)) == 1)) {
       se <- as.vector(sqrt(diag(object$beta.var)))
     } else {

### 2015-06-09 jss/article_v2.tex
draft example done

@@
 The G3 object makes use of some functions, \code{print}, \code{summary}, and \code{plot}.
-The estimation result for all the random effects pops up if we type the ``gbp'' object at the \proglang{R} console, which is the same as the following function \code{print} with its default argument ``\code{sort = TRUE}'' that prints out the estimation result for all the groups in the ascending order of $n$ for the Binomial and Poisson model and the descending order of standard errors for the Gaussian model.
+The estimation result for all the random effects pops up if we type the ``gbp'' object at the \proglang{R} console, which is the same as the following function \code{print} with its default argument ``\code{sort = TRUE}'' that prints out the estimation result for all the groups in the ascending order of $n$ for the Binomial and Poisson model and the ascending order of standard errors for the Gaussian model.
 When the argument \code{sort} is \code{FALSE}, the estimation result comes out as the order of data input.
@@
 \begin{CodeInput}
-R> pcv$coverageRB
-R> pcv$se.coverageRB
+R> p.coverage$coverageRB
+R> p.coverage$se.coverageRB
 \end{CodeInput}
@@
 \begin{CodeInput}
-R> pcv$coverageS
-R> pcv$se.coverageS
+R> p.coverage$coverageS
+R> p.coverage$se.coverageS
 \end{CodeInput}
@@
 \begin{CodeInput}
-R> summary(g)
+R> summary(g.output)
 \end{CodeInput}
@@
 post.mode.alpha post.sd.alpha post.mode.A
-1            4.77          1.14         118
+           4.77          1.14         118
 
@@
       estimate   se z.val p.val
-beta0    8.168 5.73 1.425 0.154
+beta1    8.168 5.73 1.425 0.154
 \end{CodeOutput}
@@
 The summary provides results regarding the second level hierarchy parameters.
-It can be seen that the estimate of the second level mean, \code{beta0}, is not significantly different from 0 suggesting that there was no effect of the coaching program on SAT math scores.
+It can be seen that the estimate of the expected random effect, $\mu^E$ (\code{beta1}), is not significantly different from 0 suggesting that there was no effect of the coaching program on SAT math scores.
 
@@
 \begin{CodeInput}
-R> plot(g)
+R> plot(g.output)
 \end{CodeInput}
@@
 
-The frequency method checking, assuming the model is correct, generates new pseudo-data from our assumed model.
-Unless otherwise specified, the procedure fixes the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\boldsymbol{\beta}}_0$ in this example) and then simulates ``true'' $\theta_j$ for each group $j$.
-The model is then estimated and this is repeated an \code{nsim} number of times to estimate the coverage probabilities of the procedure.
-
-\begin{CodeChunk}
-\begin{CodeInput}
-R> gcv <- coverage(g, nsim = 1000)
+The frequency method checking generates new pseudo-data from our assumed model.
+Unless otherwise specified, the procedure fixes the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\boldsymbol{\beta}}_1$ in this example) and then simulates random effects $\theta_j$ for each group $j$.
+The model is then estimated and this is repeated an $N_{sim}$ (\code{nsim}) number of times to estimate the coverage probabilities of the procedure.
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> g.coverage <- coverage(g.output, nsim = 1000)
 \end{CodeInput}
@@
 
-As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (black horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example.
-Note that all the coverage estimates depend on the chosen true values of $A$ and $\beta_{0}$, and the assumption that the model is valid.
+As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence level (black horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example.
+Note that all the coverage estimates depend on the chosen generative values of $A$ and $\beta_{1}$, and the assumption that the model is valid.
 
@@
 \begin{CodeInput}
-R> gcv$coverageRB
+R> g.coverage$coverageRB
 \end{CodeInput}
@@
 \begin{CodeInput}
-R> gcv$se.coverageRB
+R> g.coverage$se.coverageRB
 \end{CodeInput}
@@
 
-All the individual RB coverage estimates are saved in the $8\times1,000$ matrix, \code{gcv$raw.resultRB}, each row of which is about each school.
+All the individual RB coverage estimates are saved in the $8\times1,000$ matrix, each row of which is about each school. We can load this matrix by the following code.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> g.coverage$raw.resultRB 
+\end{CodeInput}
+\end{CodeChunk}
 
@@
 
-\subsection[Unknown Second-level Mean and One Covariate]{Data of 18 baseball players with unknown second-level mean and one covariate}
-
-The following dataset from the New York Times published on 26 April 1970 contains information on the batting averages and positions (outfielder=1,otherwise=0) of 18 major league baseball players through their first 45 official at-bats of the 1970 season \citep{1975}.
-
-\begin{CodeChunk}
-\begin{CodeInput}
-R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
-R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
-R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
-\end{CodeInput}
-\end{CodeChunk}
-or
-\begin{CodeChunk}
-\begin{CodeInput}
-R> data(``baseball'')
-R> z <- baseball$Hits
+\subsection[Unknown Second-level Mean and One Covariate]{Data of 18 baseball players with unknown expected random effect and one covariate}
+
+The data of 18 major league baseball players contain the batting averages through their first 45 official at-bats of the 1970 season \citep{1975}.
+We add a covariate about their outfielder indicators taking on 1 if a player is an outfielder and 0 otherwise.
+We can load the data into \proglang{R} with the following codes.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> library(Rgbp)
+R> data(baseball)
+R> y <- baseball$Hits
 R> n <- baseball$At.Bats
@@
 %$
-Conditioning on the true batting average for each player we assume that the at-bats are independent and therefore, $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
-Our goal is to obtain point and interval estimates of the true batting average, $p_{j}$, for each player, whilst considering the additional information on whether the player is an outfielder or not.
-\code{gbp} provides a way to incorporate such covariate information seamlessly into the second-level hierarchy such that information is shared and regression towards the mean (RTTM) occurs within outfielders and non-outfielders separately.
+Conditioning on the unknown true batting average (random effect) for each player we assume that the at-bats are independent and therefore, $y_{j}\vert p_{j}\stackrel{indep.}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
+Our goal is to obtain point and interval estimates of each random effect, $p_j$, whilst considering the additional information on whether the player is an outfielder or not.
+The function \code{gbp} provides a way to incorporate such covariate information seamlessly into the conjugate Beta prior distribution so that the regression towards the mean (RTTM) occurs within outfielders and non-outfielders separately.
 %For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
@@
 \begin{CodeInput}
-R> b <- gbp(z, n, x, model = "binomial")
-R> b
+R> b.output <- gbp(z, n, x, model = "binomial")
+R> b.output
 \end{CodeInput}
@@
 % Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233. Also
-Note that the shrinkage estimates are the same for all players due to the fact that they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($\hat{B}_{j}\equiv \hat{r} / (\hat{r}+45)$ = $113 / (113+45)$ = 0.715).
-
-\begin{CodeChunk}
-\begin{CodeInput}
-R> summary(b)
+
+Note that the shrinkage estimates are the same for all players because all players have the same 45 at-bats.
+%they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($\hat{B}_{j}\equiv \hat{r} / (\hat{r}+45)$ = $113 / (113+45)$ = 0.715).
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> summary(b.output)
 \end{CodeInput}
@@
 post.mode.alpha post.sd.alpha post.mode.r
-1           -4.73         0.957         113
+          -4.73         0.957         113
 
@@
       estimate    se  z.val p.val
-beta0   -1.194 0.131 -9.129 0.000
-beta1    0.389 0.187  2.074 0.038
+beta1   -1.194 0.131 -9.129 0.000
+beta2    0.389 0.187  2.074 0.038
 \end{CodeOutput}
@@
 
-From the \code{Regression Summary}, one of the outputs of \code{summary}, we see that the two prior means distinguishing outfielders from other positions are significantly different (p-value for $\hat{\beta}_1$= 0.038).
-Also, the positive sign of $\hat{\beta}_{1}$ indicates that the population mean batting average for all outfielders tends to be higher than that for those in the other positions (estimated odds ratio = exp(0.389)=1.48).
-
-\begin{CodeChunk}
-\begin{CodeInput}
-R> plot(b)
-\end{CodeInput}
-\end{CodeChunk}
-\begin{figure}[h]
+The regression coefficient for the outfielder indicator is significant, considering that p-value for $\hat{\beta}_2$ is 0.038.
+It means that the  two estimates for the expected random effects for the outfielders and infielders are significantly different.
+Also, the positive sign of $\hat{\beta}_{2}$ indicates that the population batting average for all outfielders tends to be higher than that for infielders.
+The  estimated odds ratio is $\exp(0.389)=1.48$.
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> plot(b.output)
+\end{CodeInput}
+\end{CodeChunk}
+\begin{figure}[h!]
 \begin{center}
@@
 
-It is evident in the shrinkage plot in Figure \ref{fig:baseball} that shrinkage occurs from the sample means (empty dots) on the upper horizontal line towards the two prior means, 0.233 and 0.310.
-For reference, the short red line symbols on dots are for when two or more points have the same mean and are plotted over each other.
-For example, five players (from the 11th player to the 15th) have the same sample mean (0.222) and at this point on the upper horizontal line, there are short red lines toward five directions.
+It is evident in the shrinkage plot in Figure \ref{fig:baseball} that shrinkage occurs from the observed batting averages (empty dots) on the upper horizontal line towards the two prior means, 0.233 and 0.310.
+The short red line symbols near some empty dots are for when two or more points have the same mean and are plotted over each other.
+For example, five players (from the 11th player to the 15th) have the same batting average, 0.222, and at this point on the upper horizontal line, there are short red lines toward five directions.
 
@@
 The 10th, 14th, and 15th players, for example, are outfielders but their observed batting averages are far lower than the first five outfielders.
-This can likely be attributed to their bad luck because their observed batting averages are close to the lower bounds of their interval estimates.
-RTTM suggests that their batting averages will shrink towards the expected prior mean of outfielders (0.310) in the long run.
-
-As in the previous examples in Section \ref{sec:ex:hosp} and \ref{sec:ex:8schools}, in order to check the level of trust in these interval estimates, we can proceed to frequency method checking by assuming the estimates, 112.95 for $\hat{r}$ and (-1.194, ~0.389) for $\hat{\boldsymbol{\beta}}$, are given values.
-
-\begin{CodeChunk}
-\begin{CodeInput}
-R> bcv <- coverage(b, nsim = 1000) 
-\end{CodeInput}
-\end{CodeChunk}
-\begin{figure}[h]
+This can  be attributed to their bad luck because their observed batting averages are close to the lower bounds of their interval estimates.
+The RTTM suggests that their batting averages will shrink towards the expected random effect of outfielders (0.310) in the long run.
+
+To check the level of trust in these interval estimates, we  proceed to frequency method checking by assuming the estimates, 112.95 for $\hat{r}$ and (-1.194, ~0.389) for $\hat{\boldsymbol{\beta}}$, are given generative values.
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> b.coverage <- coverage(b.output, nsim = 1000) 
+\end{CodeInput}
+\end{CodeChunk}
+\begin{figure}[h!]
 \begin{center}
@@
 
-For reference, to do the frequency method checking at different true values, we need to specify additional arguments in the coverage function.
+%For reference, to do the frequency method checking at different true values, we need to specify additional arguments in the coverage function.
 For example, if we want to try different true values, either 100 for $r$ or (-1, 0.2) for $(\beta_{0}, \beta_{1})$, the additional arguments are \code{A.or.r = 100} and \code{reg.coef = c(-1, 0.2)}; \code{coverage(b, A.or.r = 100, reg.coef = c(-1, 0.2), nsim = 1000)}.
 
-Finally, in Figure \ref{fig:baseball2}, we see that the overall Rao-Blackwellized unbiased coverage estimate is 0.972 (across all the players), conservatively satisfying the definition of the 95\% confidence interval.
-Note that each coverage estimate depends on given true values of $r$ and $\beta_{(2\times1)}$, and the assumption that the model is valid.
-
-The Rao-Blackwellized unbiased coverage estimates and their standard errors for each player follow.
+In Figure \ref{fig:baseball2},  the estimated coverage probabilities for random effects are beyond 0.95, conservatively satisfying the definition of the 95\% confidence interval.
+The Rao-Blackwellized (RB) overall unbiased coverage estimate is 0.972 (across all the players).
+Note that each coverage estimate depends on given true values of $r$ and $\boldsymbol{\beta}_{(2\times1)}$, and the assumption that the model is valid (overdispersion exists).
+
+The RB unbiased coverage estimates and their standard errors for each player follow.
 \begin{CodeChunk}
@@
 
-All the simulation results are saved in the $18\times1,000$ matrix, \code{bcv$raw.resultRB}, each row of which is for each player.
+%All the simulation results are saved in the $18\times1,000$ matrix, each row of which is for each player.
 
@@
 As an alternative to other maximization based estimation methods such as MLE and REML, \pkg{Rgbp} provides point and interval estimates of parameters via ADM.
-Using the ADM approach, with our specified choice of priors, protects from cases of overshrinkage and undercoverage from which the aforementioned methods suffer from \citep{accuracy1988}.
-
-A benefit of \pkg{Rgbp} is that it produces non-random output and so results are easily reproduced and compared across studies.
+Using the ADM approach, with our specified choice of priors, protects from cases of overshrinkage and undercoverage from which the aforementioned methods suffer  \citep{accuracy1988}.
+
+A benefit of \pkg{Rgbp} is that it produces non-random output (except the acceptance-rejection method for the Binomial model) and so results are easily reproduced and compared across studies.
 In addition to being a standalone analysis tool the package can be used as an aid in a broader estimation procedure.
@@
 
-In addition to the built in ``frequency method checking'' procedure the package can be used to undergo ``model checking''.
-For example, in the Gaussian hierarchical model, the assumed marginal distribution of the data is given in (\ref{normalmarginal}).
+In addition to the built-in ``frequency method checking'' procedure, we may use the package to undergo ``model checking''.
+For example, in the Gaussian hierarchical model, the assumed marginal distribution of the data is given in Equation \ref{marginal_normal} as part of the likelihood function.
 By substituting the point estimates of $A$ and $\boldsymbol{\beta}$ from the package into this marginal distribution a test can be constructed to see whether the data follow the marginal distribution suggested by the hierarchical model.

### 2015-06-10 jss/article_v2.tex
draft done

@@
 For the Binomial data, the package provides an option to produce  posterior samples of all the model parameters via the acceptance-rejection method.
-The main goal of \pkg{Rgb} is to produce approximate Bayesian interval estimates for the random effects that meet their nominal confidence levels, and the package uses unique improper hyper-prior distributions for that purpose.
-\pkg{Rgbp} provides a quick way to check whether the resultant Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
+The main goal of \pkg{Rgb} is to produce approximate Bayesian interval estimates for the random effects that meet their nominal confidence levels.
+For this purpose, our models adopt unique improper hyper-prior distributions and \pkg{Rgbp} provides a quick way to check whether the resultant Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
 % and evaluates repeated sampling frequency property of the resulting approximate Bayesian interval estimates for random effects
@@
 It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for hierarchical modeling such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models and \pkg{arm} \citep{gelman2014arm} for Bayesian hierarchical regression models.
-The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping that generates mock data sets given the values of the hyper-parameters and estimates the coverage rates based on the generated mock data sets.
+The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping, a Monte Carlo simulation, that generates mock data sets given the values of the hyper-parameters and estimates the coverage rates based on the generated mock data sets.
 
@@
 
-One of the functions in \pkg{Rgbp}, \code{gbp}, fits a conjugate hierarchical model whose first-level has distributions of observed data and whose second-level has conjugate distributions on the first-level mean parameters (random effects).
+One of the functions in \pkg{Rgbp}, \code{gbp}, fits a conjugate hierarchical model in which the first-level has distributions of observed data and the second-level has conjugate distributions on the first-level mean parameters (random effects) without any observed data on this level.
+Specifically, the observed data of the first-level are sufficient statistics, sample mean or proportions, for random effects with an assumption of the homogeneity within each group.
+These data appear often in a biological analysis on litter data, a meta analysis on independent studies, or small area estimation problems.
 The \code{gbp} function allows users to choose one of three types of hierarchical models according to the type of data, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta models.
+There are possibly more hierarchical models depending on the types of data such as Exponential-Gamma \citep{tang2002fitting}, but we choose the three models because these are the most commonly-used models.
+
+In this section, we specify the modeling details.
+Our motivation for the parametrization is to provide an intuitive shrinkage interpretation in inference and to facilitate the estimation procedure, considering that the shrinkage factors under our parametrization are a function of only a second-level variance component.
 
@@
 The following is the general Normal-Normal hierarchical model assumed by \code{gbp}.
-For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known, and subscript \emph{j} indicates the \emph{j}-th group among \emph{k} groups in the dataset.
+The subscript \emph{j} below indicates the \emph{j}-th group among \emph{k} groups in the dataset.
 For $j=1, 2, \ldots, k$,
@@
 
-where $\mu^E_{j} = E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$ is the expected random effect and $m$ is the number of regression coefficients to be estimated.
+where $y_j$ is an observed unbiased estimate (sample mean) for random effect $j$, $V_{j}~(\equiv \sigma^{2}/n_{j})$ is a completely known standard error of $y_j$, $\mu^E_{j}$ is an expected random effect defined as $E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$, and $m$ is the number of regression coefficients to be estimated.
 The default of the function \code{gbp} is to set $x_{j, 1}$ to 1 for an intercept term, though \code{gbp} also provides a usage without the intercept term.
@@
 \subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}\label{poissonsubsec}
-The function \code{gbp} is also capable of estimating a conjugate Poisson-Gamma hierarchical model, though its usage is limited to the case where the expected random effects are known ($m=0$).
+The function \code{gbp} is also capable of estimating a conjugate Poisson-Gamma hierarchical model, though its usage is limited to the case where the expected random effects are known ($m=0$), for example, we may have some information about the mean of the population (second-level) from which we collect the first-level group data.
 For $j=1, 2, \ldots, k$,
@@
 Note that the conditional posterior variance in Equation \ref{gammapost_mean_var} is linear in the conditional posterior mean, whereas a slightly different Poisson-Gamma model specification has been used elsewhere \citep{morris1997} that makes the variances in the prior and conditional posterior distributions  quadratic functions of their means respectively.
+The parametrization of the Poisson-Gamma model adopted in \pkg{Rgbp} makes shrinkage factors as a function of only the hyper-parameter $r$, while the shrinkage factors based on the parametrization in \cite{morris1997} are functions of $r$ and $\boldsymbol{\beta}$.
+Thus, the estimation procedure and the interpretation of the shrinkage factors are more intuitive under the parametrization in \pkg{Rgbp}.
 
@@
 where $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$.
+The joint posterior density  function of hyper-parameters $f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Gaussian hierarchical model is proportional to their likelihood functions in Equation \ref{marginal_normal} because we use flat improper hyper-prior density functions for $A$ and $\boldsymbol{\beta}$ in Equation \ref{eq:hyper};
+\begin{equation}\label{marginal_post_normal}
+f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L_g(A, \boldsymbol{\boldsymbol{\beta}})d\boldsymbol{\beta}dA.
+\end{equation}
+
 The likelihood function of hyper-parameters $r$ and $\boldsymbol{\beta}$ for the Binomial hierarchical model is derived from the independent Beta-Binomial marginal distributions of the observed data with random effects, $p_1, p_2, \ldots, p_k$, integrated out \citep{skellam1948}; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
@@
 where $p^E_j=\exp(\boldsymbol{x}^\top\boldsymbol{\beta})/(1+\exp(\boldsymbol{x}^\top\boldsymbol{\beta}))$ and the notation $B(a, b)~(\equiv\int_0^1 v^{a-1}(1-v)^{b-1}dv)$ indicates a beta function for positive constants $a$ and $b$.
+The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial hierarchical model is proportional to their likelihood functions in Equation \ref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in Equation \ref{eq:hyper} as follows;
+\begin{equation}\label{marginal_post_binomial}
+f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L_b(r, \boldsymbol{\boldsymbol{\beta}})d\boldsymbol{\beta}dr/r^2.
+\end{equation}
+
 Similarly, the likelihood function of $r$ for the Poisson hierarchical model, without a regression coefficient (a known expected random effect, $\lambda^E$), comes from the independent Negative-Binomial marginal distributions of the observed data with the random effects, $\lambda_1, \lambda_2, \ldots, \lambda_k$, integrated out;
@@
 where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}e^{x}dx$ for a positive constant $a$.
-
-%If all the observed data are extreme, i.e., $y_j$ is either 0 or $n_j$ for all $j$, the likelihood becomes a decreasing function with respect to $r$ for finite values of $\boldsymbol{\beta}$.
-In this case, the MLE of $r$ is 0.
-
-The joint posterior density  function of hyper-parameters $f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Gaussian hierarchical model is proportional to their likelihood functions in Equation \ref{marginal_normal} because we use flat improper hyper-prior density functions for $A$ and $\boldsymbol{\beta}$ shown in Equation \ref{eq:hyper};
-\begin{equation}\label{marginal_post_normal}
-f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L_g(A, \boldsymbol{\boldsymbol{\beta}})d\boldsymbol{\beta}dA.
-\end{equation}
-The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial hierarchical model is proportional to their likelihood functions in Equation \ref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in Equation \ref{eq:hyper} as follows;
-\begin{equation}\label{marginal_post_binomial}
-f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L_b(r, \boldsymbol{\boldsymbol{\beta}})d\boldsymbol{\beta}dr/r^2.
-\end{equation}
 The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in Equation \ref{marginal_poisson} times the hyper-prior density function of $r$, $dr/r^2$;
@@
 \end{equation}
+
+%If all the observed data are extreme, i.e., $y_j$ is either 0 or $n_j$ for all $j$, the likelihood becomes a decreasing function with respect to $r$ for finite values of $\boldsymbol{\beta}$.
+In this case, the MLE of $r$ is 0.
 
@@
 \subsection{Estimation for random effects}
-It is intractable to derive the unconditional posterior distribution of each random effect analytically for all three models.
-Instead, we  assume again that each random effect has a skewed Normal distribution \cite{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
+It is intractable to derive analytically the unconditional posterior distribution of each random effect  for our three models, which motivate us to assume again that each random effect has a skewed Normal distribution \cite{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
 \begin{eqnarray}
@@
 
-\cite{kelly2014advances}  matches estimated three unconditional posterior  moments of the random effects to the three parameters $(\phi, \omega, \delta$) of the skewed-Normal distribution in Equation \ref{skewnormal}.
+\cite{kelly2014advances}  matches the estimated three unconditional posterior  moments of the random effects to the three parameters $(\phi, \omega, \delta$) of the skewed-Normal distribution in Equation \ref{skewnormal}, i.e., location parameter $\phi$, scale parameter $\omega$, and a skewness parameter $\delta$.
+\cite{kelly2014advances} also shows that the skewed-Normal approximation improves the Normal approximation \citep{tang2011, morris2012} in terms of the repeated sampling coverage rates of random effects.
 
@@
 \end{equation} 
-It shows that the tails follow a power law as $\alpha^{-(2a+1)}$ on the left and $\alpha^{-(2b+1)}$ on the right when $b>a$.
+The article also show that the tails of the skewed-$t$ density function  follow a power law as $\alpha^{-(2a+1)}$ on the left and $\alpha^{-(2b+1)}$ on the right when $b>a$.
 It also provides a representation to generate the random variable following their skewed-$t$ distribution as
@@
 \subsection{Model fitting}
-The function \code{gbp} creates an G3 object ``gbp'' which provides three relevant functions \code{plot}, \code{print}, and \code{summary}.
+The function \code{gbp} creates an S3 object ``gbp'' on which  three generic functions \code{plot}, \code{print}, and \code{summary} are defined.
 To use these relevant functions, we need to save the outcome of \code{gbp} into an object (see the code below).
@@
 The argument \code{Alpha}, whose default is 0.95, sets the confidence level, producing $100\times$\code{Alpha}\% interval estimates of the random effects.
-For the Gaussian model, setting the argument \code{normal.CI} to \code{TRUE} makes \code{gbp} use a Normal approximation to the unconditional posterior distribution of the random effect.
-The default of \code{normal.CI} is \code{FALSE} for the skewed Normal approximation.
+For the Gaussian model, setting the argument \code{normal.CI} to \code{TRUE} lets the function \code{gbp} to use a Normal approximation to the unconditional posterior distribution of the random effect \citep{tang2011}.
+The default of \code{normal.CI} is \code{FALSE} for the skewed Normal approximation \citep{kelly2014advances}.
 
@@
 
-The G3 object ``gbp'', for example \code{b.output} above, contains detailed outcomes.
+The S3 object ``gbp'', for example \code{b.output} above, contains detailed outcomes.
 The function \code{names} will show the list of outcomes (too many to be listed in this article); see the document of \code{gbp} to check the details of the items.
@@
 
-The G3 object makes use of some functions, \code{print}, \code{summary}, and \code{plot}.
+The S3 object makes use of some functions, \code{print}, \code{summary}, and \code{plot}.
 The estimation result for all the random effects pops up if we type the ``gbp'' object at the \proglang{R} console, which is the same as the following function \code{print} with its default argument ``\code{sort = TRUE}'' that prints out the estimation result for all the groups in the ascending order of $n$ for the Binomial and Poisson model and the ascending order of standard errors for the Gaussian model.
@@
 
-Although the function \code{coverage} does not produce a G3 object, a detailed summary appears in a plot that automatically pops up after running the function \code{coverage}.
+Although the function \code{coverage} does not produce the S3 object, a detailed summary appears in a plot that automatically pops up after running the function \code{coverage}.
 In addition, the object \code{cov} that contains the result of \code{coverage} as shown above contains numerical details, see \code{names(cov)} for the list of detailed outcomes.
@@
 
-We analyze a data set of 31 hospitals in New York state comprising of the outcomes of the coronary artery bypass graft (CABG) surgery \citep{morris2012}.
+We analyze a data set of 31 hospitals in New York state comprising of the outcomes of the coronary artery bypass graft (CABG) surgery \citep{morris2012}\footnote{Visit \emph{http://www.health.ny.gov/statistics/diseases/cardiovascular/} for more profile data of the CABG surgery in New York state.}.
 The data set contains the number of deaths, $\boldsymbol{y}$, for a specified period after CABG surgeries out of the total number of patients, $\boldsymbol{n}$, receiving CABG surgeries in each hospital.
@@
 
-The following code provides specific values of the 31 RB unbiased coverage estimates and their standard errors for each hospital.
+The following code provides specific values of the 31 RB unbiased coverage estimates and their standard errors for each hospital (the output is omitted for a space concern).
 \begin{CodeChunk}
@@
 
+If we want to draw 2,000 posterior samples of random effects and hyper-parameters from their full posterior distribution via the acceptance-rejection method, we use the following \proglang{R} code.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> b.output <- gbp(y, n, x, model = "binomial", n.AR = 2000)
+\end{CodeInput}
+\end{CodeChunk}
+The ``gbp'' object \code{b.output} contains 2,000 posterior samples of $\alpha$ (\code{b.output$alpha}), a $2,000\times2$ matrix of $\beta$ (\code{b.output$beta}) with each column corresponding to posterior samples of each regression coefficient, and a $k\times2,000$ matrix of random effects with each row contains posterior samples of each random effect.
+
+If we run the frequency method checking using this ``gbp'' object obtained via the acceptance-rejection method, the $N_{sim}$ simulations also run the acceptance-rejection method.
+
 \section[Discussion]{Discussion and summary} \label{discussion}

### 2015-06-10 jss/article_v2.tex
draft revision 2

@@
 The data that \pkg{Rgbp} assumes comprise of observed sufficient statistics for each random effect, such as averages or proportions, possibly together with covariates of each group but without population-level data.
-The approximate Bayesian tool equipped with the adjustment for density maximization produces point and interval estimates for each random effect, point estimates and standard errors for regression coefficients, and a point estimate and its standard error for a second-level variance component.
-For the Binomial data, the package provides an option to produce  posterior samples of all the model parameters via the acceptance-rejection method.
-The main goal of \pkg{Rgb} is to produce approximate Bayesian interval estimates for the random effects that meet their nominal confidence levels.
+The approximate Bayesian tool equipped with the adjustment for density maximization produces point and interval estimates for each random effect, point estimates and their standard errors for regression coefficients, and a point estimate and its standard error for a second-level variance component.
+For the Binomial data, the package provides an option to draw independent  posterior samples of all the model parameters from their  posterior distributions via the acceptance-rejection method.
+The main goal of \pkg{Rgb} is to produce approximate, or exact for the Binomial model, Bayesian interval estimates for the random effects that meet their nominal confidence levels.
 For this purpose, our models adopt unique improper hyper-prior distributions and \pkg{Rgbp} provides a quick way to check whether the resultant Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
@@
 %It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.
-\Keywords{overdispersion, hierarchical model, adjustment for density maximization, repeated sampling coverage evaluation, \proglang{R}}
+\Keywords{overdispersion, hierarchical model, adjustment for density maximization, acceptance-rejection method, repeated sampling coverage evaluation, frequency method checking, \proglang{R}}
 \Plainkeywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, R} 
@@
 When it comes to fitting the model, \pkg{Rgbp} adopts the adjustment for density maximization \citep{carl1988, morris1997, tang2011} (ADM), a Pearson family approximation via maximization.
-For example, a Delta method is a special case of ADM that uses a Normal distribution to obtain an approximate distribution of a function of a parameter with its MLE and observed information plugged-in.
+For example, a Delta method is a Normal case of the ADM that uses a Normal distribution to obtain an approximate distribution of a function of a parameter with its MLE and observed information plugged-in.
 In this article, the ADM uses Beta distributions to approximate the posterior distributions of shrinkage factors, functions of the second-level variance component, via maximization.
-For the approximation to the distributions of the shrinkage factors, the Beta distribution  is more appropriate than the Normal distribution (Delta method) because the support of each shrinkage factor is between 0 and 1, not ($-\infty,~\infty$).
-Also, the ADM is free of a boundary effect that a restricted MLE \citep{patterson1971recovery} (REML) sometimes suffers from, preventing a zero estimate for the second-level variance component.
 Using the approximate Beta posterior distributions of shrinkage factors, \pkg{Rgbp} estimates the first two (three for the Gaussian case) posterior moments of the random effects.
@@
 
-For the Binomial  multilevel model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters via an acceptance-rejection method instead of the approximate tool.
+%For the approximation to the distributions of the shrinkage factors, the Beta distribution  is more appropriate than the Normal distribution (Delta method) because the support of each shrinkage factor is between 0 and 1, not ($-\infty,~\infty$).
+Also, the ADM is free of a boundary effect that a restricted MLE \citep{patterson1971recovery} (REML) sometimes suffers from, preventing a zero estimate for the second-level variance component.
+
+For the Binomial  hierarchical model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters from their posterior distributions via an acceptance-rejection method instead of the approximate Bayesian tool.
 
@@
 
+%:
 The rest of this paper is organized as follows.
 We specify the Bayesian hierarchical models and discuss their posterior propriety in Section \ref{sec2}.
-We describe the estimation procedures including the ADM and the acceptance-rejection method in Section  \ref{sec3}, and the frequency method checking in Section \ref{sec4}.
+In Section \ref{inference}, we explain the inferential models used to estimate the model parameters.
+We describe the estimation procedures including the ADM and the acceptance-rejection method in Section  \ref{sec3} and \ref{sec_accept}, respectively.
+We introduce the frequency method checking in Section \ref{sec4}.
 We explain the usages of main functions in \pkg{Rgbp} in Section \ref{sec5}, and apply them to three examples in Section \ref{sec6}.
@@
 
-One of the functions in \pkg{Rgbp}, \code{gbp}, fits a conjugate hierarchical model in which the first-level has distributions of observed data and the second-level has conjugate distributions on the first-level mean parameters (random effects) without any observed data on this level.
-Specifically, the observed data of the first-level are sufficient statistics, sample mean or proportions, for random effects with an assumption of the homogeneity within each group.
+One of the functions in \pkg{Rgbp}, \code{gbp}, fits a conjugate hierarchical model in which the first-level has distributions of observed data and the second-level has conjugate distributions on the first-level mean parameters (random effects) without any observed data on this second-level.
+Specifically, with an assumption of the homogeneity within each group, the observed data of the first-level are sufficient statistics  for random effects such as sample means or numbers of successful outcomes.
 These data appear often in a biological analysis on litter data, a meta analysis on independent studies, or small area estimation problems.
-The \code{gbp} function allows users to choose one of three types of hierarchical models according to the type of data, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta models.
+The function \code{gbp}  allows users to choose one of three hierarchical models according to the type of data, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta models.
 There are possibly more hierarchical models depending on the types of data such as Exponential-Gamma \citep{tang2002fitting}, but we choose the three models because these are the most commonly-used models.
@@
 \subsection[Normal-Normal]{Normal-Normal (``g''=Gaussian data)}
-The following is the general Normal-Normal hierarchical model assumed by \code{gbp}.
+The following is the general Normal-Normal hierarchical model (hereafter the Gaussian model) assumed by \pkg{Rgbp}.
 The subscript \emph{j} below indicates the \emph{j}-th group among \emph{k} groups in the dataset.
@@
 
-where $y_j$ is an observed unbiased estimate (sample mean) for random effect $j$, $V_{j}~(\equiv \sigma^{2}/n_{j})$ is a completely known standard error of $y_j$, $\mu^E_{j}$ is an expected random effect defined as $E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$, and $m$ is the number of regression coefficients to be estimated.
+where $y_j$ is an observed unbiased estimate, sample mean, for random effect $j$, $V_{j}$ is a completely known standard error of $y_j$, $\mu^E_{j}$ is an expected random effect defined as $E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$, and $m$ is the number of regression coefficients to be estimated.
 The default of the function \code{gbp} is to set $x_{j, 1}$ to 1 for an intercept term, though \code{gbp} also provides a usage without the intercept term.
@@
 where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkage factors, and $\boldsymbol{y}^T=(y_1, y_2, \ldots, y_k)$.
-Note that the conditional posterior mean of the random effect, $\mu^\ast_j\equiv E(\mu_{j}\vert \boldsymbol{\beta}, A, \boldsymbol{y} )=(1-B_{j})y_{j} + B_{j}\mu^E_{j}$,  is a convex combination of the observed sufficient statistic $y_j$ and the expected random effect $\mu^E_j$ weighted by the shrinkage factor $B_j$.
+Note that the conditional posterior mean of the random effect, $\mu^\ast_j\equiv E(\mu_{j}\vert \boldsymbol{\beta}, A, \boldsymbol{y} )=(1-B_{j})y_{j} + B_{j}\mu^E_{j}$,  is a convex combination of the observed sample mean $y_j$ and the expected random effect $\mu^E_j$ weighted by the shrinkage factor $B_j$.
 If the variance of the conjugate prior distribution, $A$, is smaller than the variance of the observed distribution, $V_j$, then we expect the posterior mean to borrow more information from the more accurate second-level conjugate prior distribution.
@@
 \subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}\label{poissonsubsec}
-The function \code{gbp} is also capable of estimating a conjugate Poisson-Gamma hierarchical model, though its usage is limited to the case where the expected random effects are known ($m=0$), for example, we may have some information about the mean of the population (second-level) from which we collect the first-level group data.
+The function \code{gbp} is also capable of estimating a conjugate Poisson-Gamma hierarchical model (hereafter the Poisson model), though its usage is limited to the case where the expected random effects are known ($m=0$).
+For instance,  from previous studies we may be able to obtain some information about the mean of the population  from which we collect the first-level group data.
 For $j=1, 2, \ldots, k$,
@@
 \end{eqnarray}
-where $n_{j}$ is the exposure of group $j$, which is not necessarily an integer, $\lambda^E=E(\lambda_j\vert r)$ is the known expected random effect, and $r$ is the unknown second-level variance component.
+where $y_j$ is the number of events happening, $n_{j}$ is the exposure of group $j$, which is not necessarily an integer, $\lambda^E=E(\lambda_j\vert r)$ is the known expected random effect, and $r$ is the unknown second-level variance component.
 The mean and variance of the conjugate Gamma prior distribution are $\lambda^E$ and $\lambda^E/r$, respectively.
@@
 \end{equation}  
-whose $\bar{y}_j=y_j/n_j$. The mean and variance of the conditional posterior distribution are
+where $\bar{y}_j\equiv y_j/n_j$. The mean and variance of the conditional posterior distribution are
 \begin{equation}\label{gammapost_mean_var}
@@
 \end{equation}
-where $B_{j}\equiv r / (r+n_{j})$ for $j=1, 2, \ldots, k$.
-The conditional posterior mean is  a convex combination of the observed sufficient statistic $\bar{y}_{j} = y_j/n_j$ and the expected random effect  $\lambda^E$ weighted by the relative amount of information in the prior compared to the data, called a shrinkage factor $B_j=r / (r + n_j)$.
-If the conjugate prior distribution contains more information than the observed data have, \emph{i.e.}, ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the posterior mean shrinks  towards the prior mean by more than 50\%, borrowing more information from the prior distribution.
-
-Note that the conditional posterior variance in Equation \ref{gammapost_mean_var} is linear in the conditional posterior mean, whereas a slightly different Poisson-Gamma model specification has been used elsewhere \citep{morris1997} that makes the variances in the prior and conditional posterior distributions  quadratic functions of their means respectively.
-The parametrization of the Poisson-Gamma model adopted in \pkg{Rgbp} makes shrinkage factors as a function of only the hyper-parameter $r$, while the shrinkage factors based on the parametrization in \cite{morris1997} are functions of $r$ and $\boldsymbol{\beta}$.
+where $B_{j}\equiv r / (r+n_{j})$ is the shrinkage factor, the relative amount of information in the prior compared to the data.
+The conditional posterior mean is  a convex combination of the unbiased estimate  $\bar{y}_{j} = y_j/n_j$ and the known expected random effect  $\lambda^E$ weighted by $B_j$.
+If the conjugate prior distribution contains more information than the observed data have, \emph{i.e.}, ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the posterior mean shrinks  towards the prior mean by more than 50\%, borrowing more information from the second-level distribution.
+
+Note that the conditional posterior variance in Equation \ref{gammapost_mean_var} is linear in the conditional posterior mean, whereas a slightly different Poisson-Gamma model specification has been used elsewhere \citep{morris1997} that makes the variances  quadratic functions of their means.
+The parametrization of the Poisson model adopted in \pkg{Rgbp} makes shrinkage factors as a function of only the hyper-parameter $r$, while the shrinkage factors based on the parametrization in \cite{morris1997} are functions of $r$ and $\boldsymbol{\beta}$.
 Thus, the estimation procedure and the interpretation of the shrinkage factors are more intuitive under the parametrization in \pkg{Rgbp}.
+%in the prior and conditional posterior distributions
 
@@
 The Binomial-Beta hierarchical model is the last model that \code{gbp} can fit.
-The notation $y_{j}$ is the number of successes (or failures) out of $n_{j}$ trials.
-Unlike the Poisson-Gamma model, the expected random effect is either known ($m=0$) or unknown ($m\ge1$) a priori.
+The notation $y_{j}$ below is the number of successes (or failures) out of $n_{j}$ trials.
+Unlike the Poisson model, the expected random effect is either known ($m=0$) or unknown ($m\ge1$) a priori.
 \begin{eqnarray}
@@
 \end{equation}
-whose $\bar{y}_j=y_j/n_j$ is the observed proportion of group $j$. The mean and variance of the conditional posterior distribution are
+where $\bar{y}_j=y_j/n_j$ is the observed proportion of group $j$. The mean and variance of the conditional posterior distribution are
 \begin{equation}\label{betapost_mean_var}
@@
 \end{equation}
-The conditional posterior mean is  a convex combination of the observed sufficient statistic $\bar{y}_{j} = y_j/n_j$ and the expected random effect  $p^E_j$ weighted by the relative amount of information in the prior compared to the data (a shrinkage factor) $B_j\equiv r / (r + n_j)$ like the Poisson-Gamma model.
+The conditional posterior mean is  a convex combination of the unbiased estimate $\bar{y}_{j} = y_j/n_j$ and the expected random effect  $p^E_j$ weighted by $B_j\equiv r / (r + n_j)$ like the Poisson model.
 If the conjugate prior distribution contains more information than the observed distribution does ($r>n_j$), then the resulting conditional posterior mean shrinks towards the expected random effect by more than 50\%.
@@
 
-In the other two cases, Poisson-Gamma and Binomial-Beta, the flat prior distribution on $1/r$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian case.
+In the other two cases, Poisson and Binomial, the flat prior distribution on $1/r$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with the Uniform($0, \infty$) for the Gaussian case.
 The resultant full posterior distribution of random effects and hyper-parameters for the Binomial case is data-dependent.
-Let's define an ``interior group'' as the group whose number of successes $y_j$ are neither 0 nor $n_j$ and $k_y$ as the number of interior groups among the entire $k$ groups.
+Let's define an ``interior group'' as the group whose number of successes $y_j$ are neither 0 nor $n_j$, and $k_y$ as the number of interior groups among the entire $k$ groups.
 Then, the full posterior distribution of random effects and hyper-parameters is proper if and only if there are at least two interior groups in the data and the $k_y\times m$ covariate matrix of the interior groups is of full rank $m$ \citep{tak2016propriety}.
 
-The Poisson-Gamma model with the hyper-prior distributions in Equation \ref{eq:hyper} provides posterior propriety if and only if there are at least two groups whose observed values $y_j$ are non-zero  and the expected random effect $\lambda^E$ is a completely known constant ($m=0$).
-If the expected random effect is unknown a priori,  then we recommend staying with the Binomial-Beta model with the same hyper-prior distributions because the Poisson-Gamma model is actually an approximation to the Binomial-Beta model.
+The Poisson model with the hyper-prior distributions in Equation \ref{eq:hyper} provides posterior propriety if and only if there are at least two groups whose observed values $y_j$ are non-zero  and the expected random effect $\lambda^E$ is a completely known constant ($m=0$).
+If the expected random effect is unknown a priori,  then we recommend staying with the Binomial model with the same hyper-prior distributions because the Poisson model is actually an approximation to the Binomial model.
 
@@
 
-The likelihood function of hyper-parameters $A$ and $\boldsymbol{\beta}$ for the Gaussian hierarchical model is derived from the independent Normal marginal distributions of the observed data with random effects, $\mu_1, \mu_2, \ldots, \mu_k$, integrated out as follows; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
+The likelihood function of hyper-parameters $A$ and $\boldsymbol{\beta}$ for the Gaussian  model is derived from the independent Normal marginal distributions of the observed data with random effects, $\mu_1, \mu_2, \ldots, \mu_k$, integrated; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
 \begin{equation}\label{marginal_normal}
@@
 where $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$.
-The joint posterior density  function of hyper-parameters $f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Gaussian hierarchical model is proportional to their likelihood functions in Equation \ref{marginal_normal} because we use flat improper hyper-prior density functions for $A$ and $\boldsymbol{\beta}$ in Equation \ref{eq:hyper};
+The joint posterior density  function of hyper-parameters $f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Gaussian hierarchical model is proportional to their likelihood function in Equation \ref{marginal_normal} because we use flat improper hyper-prior density functions for $A$ and $\boldsymbol{\beta}$;
 \begin{equation}\label{marginal_post_normal}
@@
 
-The likelihood function of hyper-parameters $r$ and $\boldsymbol{\beta}$ for the Binomial hierarchical model is derived from the independent Beta-Binomial marginal distributions of the observed data with random effects, $p_1, p_2, \ldots, p_k$, integrated out \citep{skellam1948}; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
+The likelihood function of hyper-parameters $r$ and $\boldsymbol{\beta}$ for the Binomial  model is derived from the independent Beta-Binomial marginal distributions of the observed data with random effects, $p_1, p_2, \ldots, p_k$, integrated out \citep{skellam1948}; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
 \begin{equation}\label{marginal_binomial}
@@
 where $p^E_j=\exp(\boldsymbol{x}^\top\boldsymbol{\beta})/(1+\exp(\boldsymbol{x}^\top\boldsymbol{\beta}))$ and the notation $B(a, b)~(\equiv\int_0^1 v^{a-1}(1-v)^{b-1}dv)$ indicates a beta function for positive constants $a$ and $b$.
-The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial hierarchical model is proportional to their likelihood functions in Equation \ref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in Equation \ref{eq:hyper} as follows;
+The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial  model is proportional to their likelihood function in Equation \ref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in Equation \ref{eq:hyper} as follows;
 \begin{equation}\label{marginal_post_binomial}
@@
 
-Similarly, the likelihood function of $r$ for the Poisson hierarchical model, without a regression coefficient (a known expected random effect, $\lambda^E$), comes from the independent Negative-Binomial marginal distributions of the observed data with the random effects, $\lambda_1, \lambda_2, \ldots, \lambda_k$, integrated out;
+Similarly, the likelihood function of $r$ for the Poisson hierarchical model  comes from the independent Negative-Binomial marginal distributions of the observed data with the random effects, $\lambda_1, \lambda_2, \ldots, \lambda_k$, integrated out;
 \begin{equation}\label{marginal_poisson}
@@
 
-Our goal is to obtain the point and interval estimates of the random effects from their unconditional posterior distributions; for the Gaussian hierarchical model, 
+Our goal is to obtain the point and interval estimates of the random effects from their unconditional posterior distributions; for the Gaussian  model, 
 \begin{equation}\label{mcintegration_normal}
@@
 \end{equation}
-for the Binomial hierarchical model, 
+for the Binomial  model, 
 \begin{equation}\label{mcintegration_binomial}
@@
 \end{equation}
-and lastly for the Poisson hierarchical model, 
+and lastly for the Poisson  model, 
 \begin{equation}\label{mcintegration_poisson}
@@
 
-In this section, we illustrate our estimation procedure equipped with the adjustment for density maximization (hereafter ADM) \citep{carl1988, morris1997, tang2011}, a way to  approximate a distribution of the parameter of interest by one of Pearson family distributions based on derivatives (like the Delta method).
-The illustration is based mainly on the Binomial model.
-We briefly describe the Gaussian and Poisson models if these models have unique aspects different from the Binomial model.
-See \cite{kelly2014advances} for the details about the ADM procedure of the Gaussian model adopted in  \pkg{Rgbp}.
+In this section, we illustrate our estimation procedure equipped with the adjustment for density maximization (hereafter ADM) \citep{carl1988, morris1997, tang2011}, a way to  approximate a distribution of the parameter of interest by one of Pearson family distributions based on derivatives like the Delta method.
+%As for the ADM procedure for the Gaussian model, \cite{kelly2014advances} for the details about the ADM procedure of the Gaussian model adopted in  \pkg{Rgbp}.
 
 Overall, obtaining point and interval estimates of each random effect is our primary inferential interest.
-The approximate Bayesian tool assumes that the unconditional posterior distribution of each random effect follows a skewed-Normal distribution for the Gaussian case,  a Gamma distribution for the Poisson case, or a Beta distribution for the Binomial case whose parameters are matched to the estimated unconditional posterior moments of each random effect.
+The approximate Bayesian tool assumes that the unconditional posterior distribution of each random effect follows a skewed-Normal distribution for the Gaussian case,  a Beta distribution for the Binomial case, or a Gamma distribution for the Poisson case, whose parameters are matched to the estimated unconditional posterior moments of each random effect.
 We use these assumed unconditional posterior distributions to make point and interval estimates of each random effect.
 
+Because the ADM procedure for the Gaussian model and its frequency property are well documented in \cite{kelly2014advances}, we describe  the ADM procedure mainly for the Binomial model.
+
 \subsection[shrinkage]{Estimation for shrinkage factors and expected random effects}\label{shrinkage}
 
-Estimating the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$ ($B_j\equiv V_j/(V_j+A)$ for the Gaussian model), and the conditional posterior moments of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ ($\mu^E_1, \mu^E_2, \ldots, \mu^E_k$ for the Gaussian model or $\lambda^E$ for the Poisson model), is the main estimation problem for the hierarchical models that \code{gbp} assumes.
+Estimating the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$ ($B_j\equiv V_j/(V_j+A)$ for the Gaussian model) and the conditional posterior moments of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ ($\mu^E_1, \mu^E_2, \ldots, \mu^E_k$ for the Gaussian model or $\lambda^E$ for the Poisson model), is the main estimation problem for the  models that \code{gbp} assumes.
 This is because these moment estimates are used to estimate the unconditional posterior moments of the random effects, $p_1, p_2, \ldots, p_k$ ($\mu_1, \mu_2, \ldots, \mu_k$ for the Gaussian model or $\lambda_1, \lambda_2, \ldots, \lambda_k$ for the Poisson model).
-Taking the Binomial-Beta model as an example, with the assumption that hyper-parameters $r$ and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ are
+Taking the Binomial model as an example, with the assumption that hyper-parameters $r$ and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ are
 \begin{eqnarray}
@@
 Note that the unconditional posterior mean and approximate variance of random effect $j$ in Equation \ref{postmean}  and \ref{approximate_var}  are functions of the unconditional posterior moments of shrinkage factors and expected random effects.
-We specify the function $h_b$ in Equation \ref{approximate_var} in Appendix \ref{apppostvar}.
+We specify the function $h_b$  in Appendix \ref{apppostvar}.
 
 We assumed that hyper-parameters $r$ ($A$ for the Gaussian model) and  $\boldsymbol{\beta}$ were independent a posteriori for the Binomial model, considering that they are independent a posteriori in the limit of $k$ going to infinity  because they are asymptotically Normally distributed.
-Also, \cite{morris1997}  empirically showed that their covariance from the observed information matrix of the Poisson-Gamma model, though with a different parametrization, was close to 0 in a small sample setting.
+Also, \cite{morris1997}  empirically showed that their covariance from the observed information matrix of the Poisson model, though with a different parametrization, was close to 0 in a small sample setting.
 %For the Gaussian model we do not assume the posterior independence between $A$ and $\boldsymbol{\beta}$ because the conditional posterior variance of the random effect is a constant function of the conditional posterior mean, which is much simpler than that of the Binomial model.
@@
 \end{eqnarray}
-The unconditional posterior mean and variance of random effect $j$ under the Poisson model are also functions of the unconditional posterior moments of the shrinkage factors.
+The unconditional posterior mean and variance of random effect $j$ under the Poisson model are  functions of the unconditional posterior moments of the shrinkage factors.
 We specify the function $h_p$ in Equation \ref{approximate_var_poisson} in Appendix \ref{apppostvar_poisson}.
@@
 
-Next, we estimate the unconditional posterior moments of the shrinkage factors and expected random effects after approximating their unconditional posterior distributions by Beta distributions via the ADM.
+Next, we estimate the unconditional posterior moments of the shrinkage factors after approximating their unconditional posterior distributions by Beta distributions via the ADM. 
+%Next, we estimate the unconditional posterior moments of the shrinkage factors and expected random effects after approximating their unconditional posterior distributions by Beta distributions via the ADM.
 
@@
 One way to approximate the distribution of $B_{j}$ is to find the maximum likelihood estimate of $r$, $\hat{r}_{MLE}$, with its Hessian value and to use a Delta method for an asymptotic Normal distribution of $B_{j}(\hat{r}_{MLE})$.
-This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $B_{j}$ lies on the unit interval between 0 and 1, and hence in small sample sizes this approximation can be quite flawed and can even result in point estimates lying on the boundary of the parameter space, from which the restricted MLE procedure sometimes suffers \citep{tang2011, kelly2014advances}.
-
-To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of the ADM \citep{carl1988, morris1997, tang2011}.
+This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $B_{j}$ lies on the unit interval between 0 and 1, and hence in small sample sizes the Delta method can result in point estimates lying on the boundary of the parameter space, from which the restricted MLE procedure sometimes suffers \citep{tang2011, kelly2014advances}.
+
+To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of the ADM.
 The ADM approximates the distribution of the function of the parameter of interest by one of the Pearson family distributions using the first two derivatives as the Delta method does; the Delta method is a special case of the ADM based on the Normal distribution.
-For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, i.e.,  of $E(B_{j}^c\vert\boldsymbol{y})$ for $c\ge0$.
-\citet{morris1997} showed that the Beta approximation for the shrinkage factors worked better than Normal approximation using the Poisson hierarchical model when the sample size was small, and \citet{tang2011} showed that  using the Normal hierarchical model.
-
-The ADM specified in \cite{tang2011} assumes that the shrinkage factors follow Beta distributions a posteriori as
+
+%The ADM assumes that the unconditional posterior distribution of a shrinkage factor follows a Beta distribution, which allows us to obtain estimates of the unconditional posterior moments, i.e.,  of $E(B_{j}^c\vert\boldsymbol{y})$ for $c\ge0$.
+\citet{morris1997} using a Poisson hierarchical model showed that the Beta approximation to the shrinkage factors worked better than Normal approximation, and \citet{tang2011} showed it  using a Gaussian  hierarchical model.
+
+The ADM procedure specified in \cite{tang2011} assumes that the unconditional posterior distribution of a shrinkage factor follows a Beta distribution as
 \begin{equation}\label{admshrinkage}
@@
 The ADM works on an adjusted posterior distribution $A(B_j\vert \boldsymbol{y})dB_j\propto B_j(1-B_j)f(B_j\vert \boldsymbol{y})dB_j$ so that its mode is the same as the mean of the original Beta distribution.
-The assumed posterior mean and variance of shrinkage factor are
+The assumed posterior mean and variance of the shrinkage factor are
 \begin{eqnarray}
@@
 
-The ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \cite{berger1999integrated} for the integrated likelihood in detail.
+The ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via the Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \cite{berger1999integrated} for the integrated likelihood in detail.
 For the Gaussian model, the marginal likelihood function of $A$ is available in a closed form with $\boldsymbol{\beta}$ integrated out, see  \cite{tang2011}.
@@
 \begin{equation}\label{shrinkagemoments}
-\widehat{E}(B^c_j\vert\boldsymbol{y})= \frac{B(\hat{a}_{1j} + c, \hat{a}_{0j})}{B(\hat{a}_{1j}, \hat{a}_{0j})},
-\end{equation}
-
-and the approximation gets better if the true posterior distribution of the shrinkage factor is closer to the Beta distribution \citep{morris1997, tang2011, morris2012}.
+\widehat{E}(B^c_j\vert\boldsymbol{y})= \frac{B(\hat{a}_{1j} + c, \hat{a}_{0j})}{B(\hat{a}_{1j}, \hat{a}_{0j})}.
+\end{equation}
+
+The distributional approximation of the ADM gets better if the true posterior distribution of the shrinkage factor is closer to the Beta distribution \citep{morris1997, tang2011, morris2012}.
 
 \subsubsection{Unconditional posterior moments of expected random effects}
-The Gaussian and Binomial models need to estimate the unconditional moments of expected random effects.
+The Gaussian and Binomial models need to estimate the unconditional posterior moments of expected random effects.
 We estimate them using their relationship to the conditional posterior moments.
@@
 \end{equation}
-We estimate the unconditional posterior moments by the estimated conditional posterior moments that we obtain from the conditional posterior distribution of $\mu^E_j\vert A, \boldsymbol{y}$ or that of $p^E_j\vert r, \boldsymbol{y}$ with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.
-
-To be specific, we use another ADM for the Binomial model, assuming that the conditional posterior distribution of each expected random effect given $\hat{\alpha}$ follows a Beta distribution.
-This is because the moments of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involve an intractable integration.
+We use the ADM to estimate the conditional expectations inside, and plug-in $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ to estimate the outer unconditional expectations.
+%We estimate the unconditional posterior moments by the estimated conditional posterior moments that we obtain from the conditional posterior distribution of $\mu^E_j\vert A, \boldsymbol{y}$ or that of $p^E_j\vert r, \boldsymbol{y}$ with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.
+
+To be specific, the ADM for the Binomial model assumes that the conditional posterior distribution of each expected random effect given $\hat{\alpha}$ follows a Beta distribution  because the moment calculation of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involves an intractable integration.
 For example, the first conditional posterior moment is
@@
 In addition, calculating the conditional posterior moments is computationally less burdensome.
-Considering that the expected random effects are a function of logistic regression coefficients $\boldsymbol{\beta}$, we can use the Delta method for the asymptotic Normal distribution of $p^E_{j}(\hat{\boldsymbol{\beta}}_{MLE})$.
+%Considering that the expected random effects are a function of logistic regression coefficients $\boldsymbol{\beta}$, we can use the Delta method for the asymptotic Normal distribution of $p^E_{j}(\hat{\boldsymbol{\beta}}_{MLE})$.
 However, the Normal approximation goes through the same support and boundary issues as the shrinkage factors do.
-Instead, we approximate the conditional posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ by a Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$.
+Instead, the ADM assumes that the conditional posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ follows a Beta distribution, using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$.
 
@@
 
-In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$ follows $N[\hat{\beta}, \hat{\Sigma}]$, where $\hat{\boldsymbol{\beta}}$ is the mode of $p(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode.
-Then the posterior distribution of $x_j^\top\boldsymbol{\beta}$ is also Normal with mean $x_j^\top\hat{\boldsymbol{\beta}}$ and variance $x_j^\top\hat{\Sigma} x_j$.
-
-Using the property of the log-Normal distribution, we get the numerical values of the posterior mean and variance in Equation \ref{priormean1} and \ref{priorvariance1} as
+In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$ follows Normal$[\hat{\beta}, \hat{\Sigma}]$, where $\hat{\boldsymbol{\beta}}$ is the mode of $p(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode.
+Thus, the posterior distribution of $x_j^\top\boldsymbol{\beta}$ is also Normal with mean $x_j^\top\hat{\boldsymbol{\beta}}$ and variance $x_j^\top\hat{\Sigma} x_j$.
+
+Using the property of the log-Normal distribution for $\exp(x_j^\top\boldsymbol{\beta})$, we get the numerical values of the posterior mean and variance in Equation \ref{priormean1} and \ref{priorvariance1} as
 \begin{eqnarray}
@@
 \end{equation}
-where $X\equiv (\boldsymbol{x}_1, \boldsymbol{x}_2, \ldots, \boldsymbol{x}_k)^\top$ is a $k \times m$ covariate matrix and $D_{V+\hat{A}}$ is $k \times k$ diagonal matrix with the $j$-th diagonal element $V_j+\hat{A}$.
-Because $\boldsymbol{x}^\top\boldsymbol{\beta}$ given $\hat{A}$ and $\boldsymbol{y}$ is also Normally distributed, we obtain the conditional posterior moments of $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$ with ease and use them to estimate the unconditional posterior moments.
+where $X\equiv (\boldsymbol{x}_1, \boldsymbol{x}_2, \ldots, \boldsymbol{x}_k)^\top$ is a $k \times m$ covariate matrix and $D_{V+\hat{A}}$ is a $k \times k$ diagonal matrix with the $j$-th diagonal element equal to $V_j+\hat{A}$.
+Because $\boldsymbol{x}^\top\boldsymbol{\beta}$ given $\hat{A}$ and $\boldsymbol{y}$ is also Normally distributed, we obtain the conditional posterior moments of $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$ with ease and use them to estimate their unconditional posterior moments.
 
 \subsection{Estimation for random effects}
-It is intractable to derive analytically the unconditional posterior distribution of each random effect  for our three models, which motivate us to assume again that each random effect has a skewed Normal distribution \cite{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
+It is intractable to derive analytically the unconditional posterior distribution of each random effect  for our three models, which motivates us to assume again that each random effect has a skewed Normal distribution \citep{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
 \begin{eqnarray}
@@
 
-\cite{kelly2014advances}  matches the estimated three unconditional posterior  moments of the random effects to the three parameters $(\phi, \omega, \delta$) of the skewed-Normal distribution in Equation \ref{skewnormal}, i.e., location parameter $\phi$, scale parameter $\omega$, and a skewness parameter $\delta$.
-\cite{kelly2014advances} also shows that the skewed-Normal approximation improves the Normal approximation \citep{tang2011, morris2012} in terms of the repeated sampling coverage rates of random effects.
-
-The unconditional posterior mean and variance of each random effect for the Binomial model specified in Equation \ref{postmean} and \ref{approximate_var} and those for the Poisson model in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}  are functions of the unconditional posterior moments of shrinkage factors and expected random effect.
+\cite{kelly2014advances}  matches the  three estimated unconditional posterior  moments of the random effects to the three parameters $(\phi, \omega, \delta$) of the skewed-Normal distribution in Equation \ref{skewnormal}, i.e., location parameter $\phi$, scale parameter $\omega$, and a skewness parameter $\delta$.
+(Hey Joey, could you add a brief description about how to match moments?) \cite{kelly2014advances} also shows that the skewed-Normal approximation improves a Normal approximation \citep{tang2011, morris2012} in terms of the frequency properties   of random effects.
+
+We know that the unconditional posterior mean and variance of each random effect for the Binomial model specified in Equation \ref{postmean} and \ref{approximate_var} are functions of the unconditional posterior moments of shrinkage factors and expected random effect.
 By plugging-in the estimated unconditional posterior moments of shrinkage factors and those of expected random effect, we obtain the estimates of the unconditional posterior mean and variance of each random effect, denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
-For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimates of the unconditional posterior mean and variance.
 The estimates of two parameters $t_{1j}$ and $t_{0j}$ in Equation \ref{betapost} come as follows;
@@
 \end{equation}
-The estimates of two parameters $s_{1j}$ and $s_{0j}$ in Equation \ref{gammapost} are
+
+ For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimated unconditional posterior mean and variance, respectively, with the estimated unconditional posterior moments of shrinkage factors plugged-in to Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}.
+The estimates of the two parameters $s_{1j}$ and $s_{0j}$ in Equation \ref{gammapost} are
 \begin{equation}\label{posttrueprob}
@@
 
-We use the  mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the estimated approximate posterior distribution, a skewed Normal distribution for the Gaussian model, a Beta distribution in Equation \ref{trueapprox} for the Binomial model, or a Gamma distribution in Equation \ref{trueapprox_poisson} for the Poisson model, as the point and interval estimates of the random effect.
+We use the  mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the estimated approximate posterior distribution, a skewed Normal distribution for the Gaussian model, a Beta distribution in Equation \ref{trueapprox} for the Binomial model, or a Gamma distribution in Equation \ref{trueapprox_poisson} for the Poisson model, as the point and interval estimates of  random effects.
 
@@
 
-From now on, the explanation will be based on the Normal-Normal model because the idea can be easily applied to the other two models.
+From now on, the explanation will be based on the Gaussian model because the idea can be easily applied to the other two models.
 
@@
 The function \code{gbp} creates an S3 object ``gbp'' on which  three generic functions \code{plot}, \code{print}, and \code{summary} are defined.
-To use these relevant functions, we need to save the outcome of \code{gbp} into an object (see the code below).
+To use these relevant functions, we need to save the outcome of \code{gbp} into an object such as \code{g.output} in the code below).
 
@@
 
-The argument \code{y} is a vector of $k$ observed sufficient statistics, i.e., $k$ observed sample means for the Gaussian model, $k$ observed numbers of successful outcomes for the Binomial model, and $k$ observed numbers of events happening for the Poisson model.
-The argument  \code{se.or.n} is a vector of $k$ standard errors of the sample mean for the Gaussian model, $k$ numbers of trials for the Binomial model, and $k$ exposures for the Poisson model.
+The argument \code{y} is a vector of $k$ observed sample means  for the Gaussian model, $k$ observed numbers of successful outcomes for the Binomial model, and $k$ observed numbers of events happening for the Poisson model.
+The argument  \code{se.or.n} is a vector of $k$ standard errors of each sample mean for the Gaussian model, $k$ numbers of trials for the Binomial model, and $k$ exposures for the Poisson model.
 If we want to designate a known value of the expected random effect $\mu^E=\beta_1$ for the Gaussian model or $p^E=\exp(\beta_1)/(1+\exp(\beta_1))$ for the Binomial model, then we put that value into \code{gbp} using an argument \code{mean.PriorDist}.
 For example, if the $\mu^E$ is known as 10, then we use the following code.
-The usage of the Binomial model is the same.
+%The usage of the Binomial model is the same.
 \begin{CodeChunk}
@@
 The function \code{gbp} contains several optional arguments.
-The argument \code{Alpha}, whose default is 0.95, sets the confidence level, producing $100\times$\code{Alpha}\% interval estimates of the random effects.
-For the Gaussian model, setting the argument \code{normal.CI} to \code{TRUE} lets the function \code{gbp} to use a Normal approximation to the unconditional posterior distribution of the random effect \citep{tang2011}.
-The default of \code{normal.CI} is \code{FALSE} for the skewed Normal approximation \citep{kelly2014advances}.
-
-The function \code{gbp} uses the acceptance-rejection method to fit the Binomial model if we assign the desired number of posterior samples ($N$ in Equation \ref{weight}) to the argument \code{n.AR}; its default value is 0.
+The argument \code{Alpha}, whose default is 0.95, sets the confidence level, producing $100\times$\code{Alpha}\% interval estimates for the random effects.
+For the Gaussian model, setting the argument \code{normal.CI} to \code{TRUE} lets the function \code{gbp}  use a Normal approximation to the unconditional posterior distribution of the random effect \citep{tang2011}.
+The default of \code{normal.CI} is \code{FALSE} for the skewed-Normal approximation \citep{kelly2014advances}.
+
+The function \code{gbp} uses the acceptance-rejection method to fit the Binomial model if we assign the desired number of posterior samples ($N$ in Equation \ref{weight}) through the argument \code{n.AR}; its default value is 0.
 There are several arguments related to the acceptance-rejection method.
-The argument \code{n.AR.factor} determines how many trial samples the method draws; its default value is 4, meaning that the method draws \code{n.AR} $\times4$ trial samples and accepts some of them.
+The argument \code{n.AR.factor} determines how many trial samples the method draws; its default value is 4, meaning that the method draws \code{n.AR} $\times4$ trial samples and accepts or rejects them.
 The argument \code{trial.scale} is $\psi$ determining the scale parameter of the skewed-$t$ distribution (the envelope function); its default value is 1.3.
 The argument \code{save.result} indicates whether we save the whole posterior samples of the random effects and hyper-parameters; its default value is \code{TRUE}.
-The two arguments \code{t} and \code{u}, taking on positive values, allow users to chose the joint hyper-prior distribution $f(r, \boldsymbol{\beta})\propto d\boldsymbol{\beta}dr/(t+r)^{u+1}$; the default values for \code{t} and \code{u} are 0 and 1 for the joint hyper-prior distribution specified in Equation \ref{eq:hyper}.
+The two arguments \code{t} and \code{u}, taking on positive values, allow users to chose the joint hyper-prior distribution $f(r, \boldsymbol{\beta})\propto d\boldsymbol{\beta}dr/(t+r)^{u+1}$; the default values for \code{t} and \code{u} are 0 and 1, respectively, for the joint hyper-prior distribution specified in Equation \ref{eq:hyper}.
+
 For example, when there are two covariates, the following code produces 2,000 posterior samples of random effects and hyper-parameters, $r$ and $\boldsymbol{\beta}_{3\times1}$ including an intercept term, via the acceptance-rejection method with 8,000 trial samples.
@@
 
-The S3 object ``gbp'', for example \code{b.output} above, contains detailed outcomes.
-The function \code{names} will show the list of outcomes (too many to be listed in this article); see the document of \code{gbp} to check the details of the items.
+The object \code{b.output} above contains detailed outcomes.
+The function \code{names} will show the list of outcomes (too many to be listed in this article); see the document of \code{gbp} to check the details of the items saved.
 \begin{CodeChunk}
@@
 
-The S3 object makes use of some functions, \code{print}, \code{summary}, and \code{plot}.
-The estimation result for all the random effects pops up if we type the ``gbp'' object at the \proglang{R} console, which is the same as the following function \code{print} with its default argument ``\code{sort = TRUE}'' that prints out the estimation result for all the groups in the ascending order of $n$ for the Binomial and Poisson model and the ascending order of standard errors for the Gaussian model.
+The S3 object ``gbp'' benefits from three generic functions, \code{print}, \code{summary}, and \code{plot}.
+The estimation result for all the random effects pops up if we type the ``gbp'' object at the \proglang{R} console, which plays the same role of the function \code{print} with its default argument ``\code{sort = TRUE}''.
+When the argument \code{sort} is set to \code{TRUE}, the function \code{print} prints out the estimation result for all the groups in the ascending order of $n$ for the Binomial and Poisson model and the ascending order of standard errors for the Gaussian model.
 When the argument \code{sort} is \code{FALSE}, the estimation result comes out as the order of data input.
@@
 
-The function \code{summary} prints a detailed estimation summary, including the estimation result for the hyper-parameters.
+The function \code{summary} prints a detailed estimation result, including the estimation result for the hyper-parameters.
 \begin{CodeChunk}
@@
 
-The function \code{plot} draws a shrinkage plot and $100\times$\code{Alpha}\% interval plot for random effects with its default argument ``\code{sort = TRUE}'' that draws the $100\times$\code{Alpha}\% interval plot in the ascending order of $n$ for the Binomial and Poisson model and the descending order of standard errors for the Gaussian model.
-When the argument \code{sort} is set to \code{FALSE} the the $100\times$\code{Alpha}\% will be based on the order of data input.
+The function \code{plot} draws a shrinkage plot and $100\times$\code{Alpha}\% interval plot for random effects with its default argument ``\code{sort = TRUE}'' that draws the $100\times$\code{Alpha}\% interval plot in the ascending order of $n$ for the Binomial and Poisson model and the ascending order of standard errors for the Gaussian model.
+When the argument \code{sort} is set to \code{FALSE}  the $100\times$\code{Alpha}\% interval plot will be plotted in the order of data input.
 \begin{CodeChunk}
@@
 The function \code{coverage} conducts a frequency method checking that estimates the coverage probabilities of  random effects, conditioning on the values of the hyper-parameters that generate random effects and  mock data sets.
-The basic usage of \code{coverage} contains a ``gbp'' object, such as \code{b.output} above, as the first argument as follows.
+The basic usage of \code{coverage} needs a ``gbp'' object, such as \code{b.output} above, as the first argument;
 \begin{CodeChunk}
@@
 
-Although the function \code{coverage} does not produce the S3 object, a detailed summary appears in a plot that automatically pops up after running the function \code{coverage}.
-In addition, the object \code{cov} that contains the result of \code{coverage} as shown above contains numerical details, see \code{names(cov)} for the list of detailed outcomes.
+Although the function \code{coverage} does not produce an S3 object, a detailed summary appears in a plot that automatically pops up after running the function \code{coverage}.
+In addition, the object \code{cov} that contains the result of \code{coverage} contains numerical details, see \code{names(cov)} or type ``\code{?coverage}'' for the list of detailed outcomes.
 If we save the result into an object such as \code{cov} above, then we can always recall the plot, using the function \code{coverage.plot}.
@@
 \begin{CodeInput}
-R> names(cov)
 R> coverage.plot(cov)
@@
 Our goal is to obtain the point and interval estimates for the unknown true mortality rates of 31 hospitals (random effects) to evaluate  each hospital's reliability on the CABG surgery.
-We interpret the caseloads, $\boldsymbol{n}$,  as exposures and assume that the state-level death rate per exposure of this surgery is known as 0.030 ($\lambda^E$) to fit the Poisson model for an illustrative purpose.
-If covariate information is available or the expected random effect is not known, we recommend using the Binomial model for these data.
+We interpret the caseloads, $\boldsymbol{n}$,  as exposures and assume that the state-level death rate per exposure of this surgery ($\lambda^E$) is known as 0.030 to fit the Poisson model for an illustrative purpose.
+If covariate information is available or the information about the expected random effect is unavailable a priori, we recommend using the Binomial model.
 
@@
 The function \code{gbp} fits the Poisson hierarchical model with the Gamma conjugate prior distribution as a population distribution of the death rates in New York states whose mean ($\lambda^E$) is 0.030.
-The number of regression coefficients ($m$) is 0 because we do not need to estimate the expected random effect via a log-linear regression for this Poisson-Gamma model.
+The number of regression coefficients ($m$) is 0 because we do not need to estimate them via  a log-linear regression.
 \begin{CodeChunk}
@@
 
-The output contains information about the observed death rates $y_{j}$, caseloads $n_{j}$, known prior mean $\lambda^E$, shrinkage estimates $\hat{B}_{j}$, lower bounds of interval estimates $\hat{\lambda}_{j, low}$, posterior means $\hat{\lambda}_j\equiv E(\lambda_{j}\vert \boldsymbol{y})$, upper bounds  of interval estimates $\hat{\lambda}_{j, upp}$, and posterior standard deviations  for each random effect based on the assumed unconditional Gamma posterior distributions.
+The output contains information about the observed death rates $\bar{y}_{j}$, caseloads $n_{j}$, known prior mean $\lambda^E$, shrinkage estimates $\hat{B}_{j}$, lower bounds of interval estimates $\hat{\lambda}_{j, low}$, posterior means $\hat{\lambda}_j\equiv E(\lambda_{j}\vert \boldsymbol{y})$, upper bounds  of interval estimates $\hat{\lambda}_{j, upp}$, and posterior standard deviations  for each random effect based on the assumed unconditional Gamma posterior distributions.
 %The lower and upper bounds of an interval estimate for a random effect are 2.5\% and 97.5\% percentiles of the assumed unconditional Gamma posterior distributions if 95\% confidence level is used.
 
-Note that the conditional posterior mean of random effect $j$ in Equation \ref{gammapost_mean_var} is $(1-B_{j})\bar{y}_{j} + B_{j}\lambda^E$,  a convex combination of the observed death rate and expected random effect with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight.
+%Note that the conditional posterior mean of random effect $j$ in Equation \ref{gammapost_mean_var} is $(1-B_{j})\bar{y}_{j} + B_{j}\lambda^E$,  a convex combination of the observed death rate and expected random effect with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight.
 This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree (sample sizes) of prior and observed information respectively.
@@
 \end{CodeChunk}
-The output of \code{summary} also provides $\hat{r}=\textrm{exp}(6.53)=684$, which is an indicator of how valuable and informative the second-level hierarchy is.
+The output of \code{summary} shows that $\hat{r}=\textrm{exp}(6.53)=684$, which is an indicator of how valuable and informative the second-level hierarchy is.
 It means that observed sample means of hospitals whose caseloads are less than 684 will shrink toward the prior mean (0.030) more than 50\%.
@@
 \begin{center}
-\includegraphics[width = 3.2in]{hospital1.png}
+\includegraphics[width = 2.5in]{hospital1.png}
 \caption{Shrinkage plot and 95\% interval plot for 31 hospitals}
@@
 \begin{center}
-\includegraphics[width = 3in]{hospital2.png}
+\includegraphics[width = 2.5in]{hospital2.png}
 \caption{Coverage plot via frequency method checking for 31 hospitals}
@@
 In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level (\code{Alpha = 0.95} as a default) and the red circles indicate Rao-Blackwellized (RB) unbiased coverage estimates, $\bar{I}^{RB}_{r, \lambda^E}(\lambda_j)$ for $j=1, 2, \ldots, 31$.
-The overall RB unbiased coverage estimate across all the hospitals is 0.955.
+The overall RB unbiased coverage estimate across all the hospitals ($\bar{\bar{I}}^{RB}_{r, \lambda^E}$) is 0.955.
 None of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads ($n_{j}$).
@@
 \begin{center}
-\includegraphics[width = 3.2in]{school1.png}
+\includegraphics[width = 2.5in]{school1.png}
 \caption{Shrinkage plot and 95\% interval plot for 8 schools}
@@
 \begin{center}
-\includegraphics[width = 3in]{school2.png}
+\includegraphics[width = 2.5in]{school2.png}
 \caption{Coverage plot via frequency method checking for 8 schools}
@@
 \begin{center}
-\includegraphics[width = 3.2in]{baseball1.png}
+\includegraphics[width = 2.5in]{baseball1.png}
 \caption{Shrinkage plot and 95\% interval plot for 18 baseball players}
@@
 \begin{center}
-\includegraphics[width = 3in]{baseball2.png}
+\includegraphics[width = 2.5in]{baseball2.png}
 \caption{Coverage plot via frequency method checking for 18 players}

### 2015-06-10 jss/article_v2.tex
any change?

@@
 \end{equation}
-where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}e^{x}dx$ for a positive constant $a$.
+where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}\exp(x)dx$ for a positive constant $a$.
 The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in Equation \ref{marginal_poisson} times the hyper-prior density function of $r$, $dr/r^2$;
@@
 Overall, obtaining point and interval estimates of each random effect is our primary inferential interest.
-The approximate Bayesian tool assumes that the unconditional posterior distribution of each random effect follows a skewed-Normal distribution for the Gaussian case,  a Beta distribution for the Binomial case, or a Gamma distribution for the Poisson case, whose parameters are matched to the estimated unconditional posterior moments of each random effect.
+The approximate Bayesian tool assumes that the unconditional posterior distribution of each random effect, such as $\mu_j\vert\boldsymbol{y}$, $p_j\vert\boldsymbol{y}$, or $\lambda_j\vert\boldsymbol{y}$,  follows a skewed-Normal distribution for the Gaussian case,  a Beta distribution for the Binomial case, or a Gamma distribution for the Poisson case.
+We match the parameters of the assumed distribution to the estimated unconditional posterior moments of each random effect, $\hat{E}(\mu_j^c\vert\boldsymbol{y}$), $\hat{E}(p_j^c\vert\boldsymbol{y}$), or $\hat{E}(\lambda_j^c\vert\boldsymbol{y}$) for a non-negative constant $c$.
 We use these assumed unconditional posterior distributions to make point and interval estimates of each random effect.
@@
 
-Estimating the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$ ($B_j\equiv V_j/(V_j+A)$ for the Gaussian model) and the conditional posterior moments of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ ($\mu^E_1, \mu^E_2, \ldots, \mu^E_k$ for the Gaussian model or $\lambda^E$ for the Poisson model), is the main estimation problem for the  models that \code{gbp} assumes.
-This is because these moment estimates are used to estimate the unconditional posterior moments of the random effects, $p_1, p_2, \ldots, p_k$ ($\mu_1, \mu_2, \ldots, \mu_k$ for the Gaussian model or $\lambda_1, \lambda_2, \ldots, \lambda_k$ for the Poisson model).
+Estimating the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$ (or $B_j\equiv V_j/(V_j+A)$ for the Gaussian model) and the conditional posterior moments of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ ($\mu^E_1, \mu^E_2, \ldots, \mu^E_k$ for the Gaussian model or $\lambda^E$ for the Poisson model), is the main estimation problem for the  models that \code{gbp} assumes.
+This is because we use these moment estimates to estimate the unconditional posterior moments of the random effects, $E(\mu_j^c\vert\boldsymbol{y}$), $E(p_j^c\vert\boldsymbol{y}$), or $E(\lambda_j^c\vert\boldsymbol{y}$) for a non-negative constant $c$.
 Taking the Binomial model as an example, with the assumption that hyper-parameters $r$ and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ are
@@
 
-We assumed that hyper-parameters $r$ ($A$ for the Gaussian model) and  $\boldsymbol{\beta}$ were independent a posteriori for the Binomial model, considering that they are independent a posteriori in the limit of $k$ going to infinity  because they are asymptotically Normally distributed.
-Also, \cite{morris1997}  empirically showed that their covariance from the observed information matrix of the Poisson model, though with a different parametrization, was close to 0 in a small sample setting.
+We assume that hyper-parameters $r$ ($A$ for the Gaussian model) and  $\boldsymbol{\beta}$ are independent a posteriori for the Binomial model.
+This is because in the limit of $k$ going to infinity  they are asymptotically Normally distributed, and \cite{morris1997}  empirically showed that their covariance from the observed information matrix of the Poisson model, though with a different parametrization, was close to 0 in a small sample setting.
 %For the Gaussian model we do not assume the posterior independence between $A$ and $\boldsymbol{\beta}$ because the conditional posterior variance of the random effect is a constant function of the conditional posterior mean, which is much simpler than that of the Binomial model.
@@
 Considering that Equation \ref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-\log(r)$ (or $\alpha=\log(A)$ for the Gaussian model), because the distribution of $\alpha$ is more symmetric than that of $r$ and $\alpha$ is defined on a real line without any boundary issues.
-Since $A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto e^\alpha L(\alpha)$, the estimated posterior mean in Equation \ref{admmean} is
+Since $A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto \exp(\alpha) L(\alpha)$, the estimated posterior mean in Equation \ref{admmean} is
 \begin{equation}\label{meaninvariance}
-\hat{B}^\ast_j=\frac{e^{-\hat{\alpha}}}{n_j+e^{-\hat{\alpha}}},
+\hat{B}^\ast_j=\frac{\exp(-\hat{\alpha})}{n_j+\exp(-\hat{\alpha})},
 \end{equation}
@@
 
-We need the invariance information introduced in \cite{tang2011} to estimate the variance in Equation \ref{admvar}, which is defined as 
+We need  invariance information introduced in \cite{tang2011} to estimate the variance in Equation \ref{admvar}, which is defined as 
 \begin{eqnarray}
@@
 Note that this invariance information is  the negative Hessian value of $\alpha+\log(L(\alpha))$ at the mode $\hat{\alpha}$.
-Using the invariance information, we  estimate the posterior variance in Equation \ref{admvar} as
+Using the invariance information, we  estimate the unconditional posterior variance of shrinkage factor in Equation \ref{admvar} as
 \begin{equation}\label{varianceinvariance}
@@
 \end{equation}
-We use the ADM to estimate the conditional expectations inside, and plug-in $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ to estimate the outer unconditional expectations.
+We use the ADM to estimate the conditional posterior moments inside with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in as the estimates of the unconditional moments.
 %We estimate the unconditional posterior moments by the estimated conditional posterior moments that we obtain from the conditional posterior distribution of $\mu^E_j\vert A, \boldsymbol{y}$ or that of $p^E_j\vert r, \boldsymbol{y}$ with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.
@@
 \begin{equation}\label{priormoment1}
-E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\boldsymbol{\beta}.
+E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\boldsymbol{\beta}.
 \end{equation}
@@
 
-We assume the conditional posterior distribution of expected random effect $j$ is a Beta distribution as follows;
+Thus, we assume the conditional posterior distribution of expected random effect $j$ is a Beta distribution as follows;
 \begin{equation}\label{admpriormean}
-p^E_{j}\vert\hat{\alpha}, \boldsymbol{y}=\frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\sim \textrm{Beta}(b_{1j}, b_{0j})\sim \frac{G(b_{1j})}{G(b_{1j})+G(b_{0j})},
+p^E_{j}\vert\hat{\alpha}, \boldsymbol{y}=\frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}\bigg\vert\hat{\alpha}, \boldsymbol{y}\sim \textrm{Beta}(b_{1j}, b_{0j})\sim \frac{G(b_{1j})}{G(b_{1j})+G(b_{0j})},
 \end{equation}
@@
 where $G(b_{1j})$ is a random variable following a Gamma$(b_{1j}, 1)$ distribution with a unit scale and independently $G(b_{0j})$ has a Gamma($b_{0j}, 1)$ distribution.
-Note that the representation in Equation \ref{admpriormean} is equivalent to saying $e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables.
+Note that the representation in Equation \ref{admpriormean} is equivalent to saying $\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables.
 Its mean and variance are
 \begin{eqnarray}
-E(e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y})&=&E\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{b_{1j}}{b_{0j}-1}\equiv\eta_j,\label{priormean1}\\
-~~~~~Var(e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y})&=&Var\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{\eta_j(1+\eta_j)}{b_{0j}-2}.\label{priorvariance1}
+E(\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y})&=&E\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{b_{1j}}{b_{0j}-1}\equiv\eta_j,\label{priormean1}\\
+~~~~~Var(\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y})&=&Var\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{\eta_j(1+\eta_j)}{b_{0j}-2}.\label{priorvariance1}
 \end{eqnarray}
 
-In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$ follows Normal$[\hat{\beta}, \hat{\Sigma}]$, where $\hat{\boldsymbol{\beta}}$ is the mode of $p(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode.
+In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$ follows Normal$(\hat{\beta}, \hat{\Sigma})$ distribution, where $\hat{\boldsymbol{\beta}}$ is the mode of $p(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode.
 Thus, the posterior distribution of $x_j^\top\boldsymbol{\beta}$ is also Normal with mean $x_j^\top\hat{\boldsymbol{\beta}}$ and variance $x_j^\top\hat{\Sigma} x_j$.
 
-Using the property of the log-Normal distribution for $\exp(x_j^\top\boldsymbol{\beta})$, we get the numerical values of the posterior mean and variance in Equation \ref{priormean1} and \ref{priorvariance1} as
+Using the property of the log-Normal distribution for $\exp(x_j^\top\boldsymbol{\beta})$, we estimate the posterior mean and variance in Equation \ref{priormean1} and \ref{priorvariance1} as
 \begin{eqnarray}
-\eta_j&=&e^{x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2},\label{priormean2}\\
-~~~~~\widehat{Var}(e^{x_j^\top\boldsymbol{\beta}}\vert\boldsymbol{y})&=&\eta^2_j\big(e^{x_j^{T}\hat{\Sigma} x_j}-1\big).\label{priorvariance2}
+\hat{\eta}_j&=&\exp(x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2),\label{priormean2}\\
+~~~~~\widehat{Var}(\exp(x_j^\top\boldsymbol{\beta})\vert\boldsymbol{y})&=&\hat{\eta}^2_j\big(\exp(x_j^{T}\hat{\Sigma} x_j)-1\big).\label{priorvariance2}
 \end{eqnarray}
 
-By matching the  mean and variance in Equation \ref{priormean2} and \ref{priorvariance2} to $b_{1j}$ and $b_{0j}$ in Equation \ref{priormean1} and \ref{priorvariance1}, we obtain the values of $b_{1j}$ and $b_{0j}$ as follows;
+By matching the  mean and variance in Equation \ref{priormean2} and \ref{priorvariance2} to $b_{1j}$ and $b_{0j}$ in Equation \ref{priormean1} and \ref{priorvariance1}, we estimate the values of $b_{1j}$ and $b_{0j}$ as follows;
 \begin{equation}\label{priormeanpara}
-b_{1j}=\eta_j+\frac{\eta_j + 1}{e^{x_j^{T}\hat{\Sigma} x_j}-1}~~\textrm{and}~~b_{0j}=\frac{\eta_j + 1}{\eta_j(e^{x_j^{T}\hat{\Sigma} x_j}-1)}+2.
-\end{equation}
-
-Finally we estimate the unconditional posterior moments of the expected random effects, $E((p^E_{j})^c\vert\boldsymbol{y})$, by $E((p^E_{j})^c\vert\hat{\alpha}, \boldsymbol{y})=B(b_{1j} + c, b_{0j})/B(b_{1j}, b_{0j})$ for $c\ge0$.
+\hat{b}_{1j}=\hat{\eta}_j+\frac{\hat{\eta}_j + 1}{\exp(x_j^{T}\hat{\Sigma} x_j)-1}~~\textrm{and}~~\hat{b}_{0j}=\frac{\hat{\eta}_j + 1}{\hat{\eta}_j(\exp(x_j^{T}\hat{\Sigma} x_j)-1)}+2.
+\end{equation}
+
+Finally we estimate the unconditional posterior moments of the expected random effects, $E((p^E_{j})^c\vert\boldsymbol{y})$, by $\hat{E}((p^E_{j})^c\vert\hat{\alpha}, \boldsymbol{y})=B(\hat{b}_{1j} + c, \hat{b}_{0j})/B(\hat{b}_{1j}, \hat{b}_{0j})$ for $c\ge0$.
 %\begin{equation}\label{priormeanmoments}
@@
 \subsection{Estimation for random effects}
-It is intractable to derive analytically the unconditional posterior distribution of each random effect  for our three models, which motivates us to assume again that each random effect has a skewed Normal distribution \citep{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
+It is intractable to derive analytically the unconditional posterior distribution of each random effect  for the three models, which motivates us to assume again that each random effect has a skewed Normal distribution \citep{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
 \begin{eqnarray}
@@
 \cite{kelly2014advances}  matches the  three estimated unconditional posterior  moments of the random effects to the three parameters $(\phi, \omega, \delta$) of the skewed-Normal distribution in Equation \ref{skewnormal}, i.e., location parameter $\phi$, scale parameter $\omega$, and a skewness parameter $\delta$.
-(Hey Joey, could you add a brief description about how to match moments?) \cite{kelly2014advances} also shows that the skewed-Normal approximation improves a Normal approximation \citep{tang2011, morris2012} in terms of the frequency properties   of random effects.
+For this matching, \cite{kelly2014advances} uses $E(\mu_j\vert \boldsymbol{y}) =\phi+\omega\delta\sqrt{2/\pi}$, Var$(\mu_j\vert \boldsymbol{y})=\omega^2(1-2\delta^2/\pi)$, and Skewness$(\mu_j\vert \boldsymbol{y})=(4-\pi)\delta^3/[2(\pi/2-\delta^2)^{3/2}]$ derived in \cite{azzalini1985class}.
+\cite{kelly2014advances} also shows that the skewed-Normal approximation improves a Normal approximation \citep{tang2011, morris2012} in terms of the frequency properties   of random effects.
 
@@
 
- For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimated unconditional posterior mean and variance, respectively, with the estimated unconditional posterior moments of shrinkage factors plugged-in to Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}.
+ For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimated unconditional posterior mean and variance in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}, respectively, with the estimated unconditional posterior moments of shrinkage factors plugged-in.
 The estimates of the two parameters $s_{1j}$ and $s_{0j}$ in Equation \ref{gammapost} are
@@
 
-Finally, the approximate unconditional posterior distribution of random effect $j$ for the Binomial model is
-\begin{equation}\label{trueapprox}
+Finally, the approximate unconditional posterior distribution of random effect $j$ for the Gaussian model is
+\begin{equation}\label{trueapprox_normal}
+\mu_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{skewed-Normal}(\hat{\phi}, \hat{\omega}, \hat{\delta}),
+\end{equation}
+that for the Binomial model is
+\begin{equation}\label{trueapprox_binomial}
 p_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{Beta}(\hat{t}_{1j}, \hat{t}_{0j}),
@@
 
-We use the  mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the estimated approximate posterior distribution, a skewed Normal distribution for the Gaussian model, a Beta distribution in Equation \ref{trueapprox} for the Binomial model, or a Gamma distribution in Equation \ref{trueapprox_poisson} for the Poisson model, as the point and interval estimates of  random effects.
+We use the  mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the estimated approximate posterior distribution, a skewed Normal distribution for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution  for the Poisson model, as the point and interval estimates of  random effects.
 
@@
 \begin{equation}
-f(\alpha, \boldsymbol{\beta} \vert \boldsymbol{y})\propto f(\alpha, \boldsymbol{\beta})L(\alpha, \boldsymbol{\beta})\propto e^{\alpha}L(\alpha, \boldsymbol{\beta})d\alpha d\boldsymbol{\beta}.
+f(\alpha, \boldsymbol{\beta} \vert \boldsymbol{y})\propto f(\alpha, \boldsymbol{\beta})L(\alpha, \boldsymbol{\beta})\propto \exp(\alpha)L(\alpha, \boldsymbol{\beta})d\alpha d\boldsymbol{\beta}.
 \end{equation}
@@
 We factor the envelope function into two parts, $g(\alpha, \boldsymbol{\beta})=g_1(\alpha)g_2(\boldsymbol{\beta})$ to model the tails of each function separately.
-We consider the tail behavior of the conditional posterior density function $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ to come up with $g_1(\alpha)$; $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ behaves as $e^{-\alpha(k-1)}$ when $\alpha$ goes to $\infty$ and as $e^{\alpha}$ when $\alpha$ goes to $-\infty$.
+We consider the tail behavior of the conditional posterior density function $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ to come up with $g_1(\alpha)$; $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ behaves as $\exp(-\alpha(k-1))$ when $\alpha$ goes to $\infty$ and as $\exp(\alpha)$ when $\alpha$ goes to $-\infty$.
 It indicates that $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ is skewed to the left because the right tail touches the $x$-axis faster than the left tail does it as long as $k>1$.
@@
 \end{equation}
-The integration can be done by sampling $(p_1, p_2, \ldots, p_k)$ from the independent Beta conditional posterior distributions $f(p_j\vert \boldsymbol{\beta}, r, \boldsymbol{y})$ in Equation \ref{betapost}  given $r~(=e^{-\alpha})$ and $\boldsymbol{\beta}$ already sampled from $f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})$ via the A-R method.
+The integration can be done by sampling $(p_1, p_2, \ldots, p_k)$ from the independent Beta conditional posterior distributions $f(p_j\vert \boldsymbol{\beta}, r, \boldsymbol{y})$ in Equation \ref{betapost}  given $r~(=\exp(-\alpha))$ and $\boldsymbol{\beta}$ already sampled from $f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})$ via the A-R method.
 

### 2015-07-01 .Rd2pdf11633/Rd2.tex
Rd2pdf

\documentclass[a4paper]{book}
\usepackage[times,inconsolata,hyper]{Rd}
\usepackage{makeidx}
\usepackage[utf8,latin1]{inputenc}
% \usepackage{graphicx} % @USE GRAPHICX@
\makeindex{}
\begin{document}
\chapter*{}
\begin{center}
{\textbf{\huge Package `Rgbp'}}
\par\bigskip{\large \today}
\end{center}
\begin{description}
\raggedright{}
\item[Version]\AsIs{1.0.7}
\item[Date]\AsIs{2014-09-02}
\item[Title]\AsIs{Gaussian, Poisson, and Binomial Hierarchical Modeling}
\item[Author]\AsIs{Joseph Kelly, Hyungsuk Tak, and Carl Morris}
\item[Maintainer]\AsIs{Joseph Kelly }\email{josephkelly@google.com}\AsIs{}
\item[Depends]\AsIs{R (>= 2.2.0), sn (>= 0.4-18), mnormt (>= 1.5-1)}
\item[Description]\AsIs{Rgbp is an R package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner. The main products of this package are point and interval estimates for the true parameters, whose good frequency properties can be validated via its repeated sampling procedure called frequency method checking. It is found that such Bayesian-frequentist reconciliation allows Rgbp to have attributes desirable both sides of the aisle, working well in small samples and yielding good coverage probabilities for its interval estimates.}
\item[License]\AsIs{GPL-2}
\item[BugReports]\AsIs{}\url{https://github.com/jyklly/Rgbp/issues}\AsIs{}
\end{description}
\Rdcontents{\R{} topics documented:}
\inputencoding{utf8}
\HeaderA{baseball}{Baseball Data}{baseball}
\keyword{datasets}{baseball}
%
\begin{Description}\relax
Batting averages of 18 major league players through their first 45 official at bats of the 1970 season. These batting averages were published weekly in the New York Times, and by April 26, 1970.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
data(baseball)
\end{verbatim}
\end{Usage}
%
\begin{Format}
A data set of 18 players with 12 covariates:
\begin{description}

\item[\code{FirstName}] each player's first name
\item[\code{LastName}] each player's last name
\item[\code{At.Bats}] number of times batted
\item[\code{Hits}] each player's number of hits among 45 at bats
\item[\code{BattingAverage}] batting averages among 45 at bats
\item[\code{RemainingAt.Bats}] number of times batted after 45 at bats until the end of season
\item[\code{RemainingAverage}] batting averages after 45 at bats until the end of season
\item[\code{SeasonAt.Bats}] number of times batted over the whole season
\item[\code{SeasonHits}] each player's number of hits over the whole season
\item[\code{SeasonAverage}] batting averages over the whole season
\item[\code{League}] 1 if a player is in the National league
\item[\code{Position}] each player's position

\end{description}

\end{Format}
%
\begin{Source}\relax
Efron, B. and Morris, C. (1975). Data Analysis Using Stein's Estimator and its Generalizations. \emph{Journal of the American Statistical Association}. \bold{70}. 311-319.
\end{Source}
%
\begin{Examples}
\begin{ExampleCode}
  data(baseball)
\end{ExampleCode}
\end{Examples}
\inputencoding{utf8}
\HeaderA{coverage}{Estimating Coverage Probability}{coverage}
\keyword{methods}{coverage}
%
\begin{Description}\relax
\code{coverage} estimates Rao-Blackwellized and simple unbiased coverage probabilities.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
coverage(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 100)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{gbp.object}] 
a resultant object of \code{gbp} function.

\item[\code{A.or.r}] 
(optional) a given true numeric value of \emph{A} for Gaussian data or of \emph{r} for Binomial and Poisson data. If not designated, the estimated value in the \code{gbp.object} object will be considered as a true value.

\item[\code{reg.coef}] 
(optional) a given true (\emph{m} by 1) vector for regression coefficients, \eqn{\beta}{}, where \emph{m} is the number of regression coefficients including an intercept. If not designated, the estimated value in the \code{gbp.object} object will be considered as a true value.

\item[\code{mean.PriorDist}] 
(optional) a given true numeric value for the mean of (second-level) prior distribution. If not designated, the previously known value in the \code{gbp.object} object will be considered as a known prior mean.

\item[\code{nsim}] 
number of datasets to be generated. Default is 100.

\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
As for the argument \code{gbp.object}, if the result of \code{gbp} is designated to 
\code{b}, for example \\{} "\code{b <- gbp(z, n, model = "binomial")}", the argument \code{gbp.object} indicates this \code{b}.

Data generating process is based on a second-level hierarchical model. The first-level hierarchy is 
a distribution of observed data and the second-level is a conjugate prior distribution 
on the first-level parameter.

To be specific, for Normal data, \code{gbp} constructs a two-level Normal-Normal 2-level model. \eqn{\sigma^{2}_{j}}{} below is assumed to be known or to be accurately estimated (\eqn{s^{2}_{j}}{}) and subscript \emph{j} indicates \emph{j}-th group in a dataset.
\deqn{(y_{j} | \theta_{j}) \stackrel{ind}{\sim} N(\theta_{j}, \sigma^{2}_{j})}{}
\deqn{(\theta_{j} |\mu_{0j} , A) \stackrel{ind}{\sim} N(\mu_{0j}, A)}{}
\deqn{\mu_{0j} = x_{j}'\beta}{}
for \eqn{j = 1, \ldots, k}{}, where \emph{k} is the number of groups (units) in a dataset.

For Poisson data, \code{gbp} builds a two-level Poisson-Gamma multi-level model. A square bracket below indicates [mean, variance] of distribution and a constant multiplied to the notation representing Gamma distribution (Gam) is a scale. Also, for consistent notation, \eqn{y_{j}=\frac{z_{j}}{n_{j}}}{} and \eqn{n_{j}}{} can be interpreted as \emph{j}-th group's exposure only in this Poisson-Gamma hierarchical model.
\deqn{(z_{j} | \theta_{j}) \stackrel{ind}{\sim} Pois(n_{j}\theta_{j})}{}
\deqn{(\theta_{j} | r, \mu_{0j}) \stackrel{ind}{\sim} \frac{1}{r}Gam(r\mu_{0j})\stackrel{ind}{\sim}Gam[\mu_{0j}, \mu_{0j} / r] }{}
\deqn{log(\mu_{0j}) = x_{j}'\beta}{}
for \eqn{j = 1, \ldots, k}{}, where \emph{k} is the number of groups (units) in a dataset.

For Binomial data, \code{gbp} sets a two-level Binomial-Beta multi-level model. For reference, a square bracket below indicates [mean, variance] of distribution and \eqn{y_{j} = \frac{z_{j}}{n_{j}}}{}.
\deqn{(z_{j} | \theta_{j}) \stackrel{ind}{\sim} Bin(n_{j}, \theta_{j})}{}
\deqn{(\theta_{j} | r, \mu_{0j}) \stackrel{ind}{\sim} Beta(r\mu_{0j}, r(1-\mu_{0j})) \stackrel{ind}{\sim} Beta[\mu_{0j}, \mu_{0j}(1 - \mu_{0j}) / (r + 1)]}{}
\deqn{logit(\mu_{0j}) = x_{j}'\beta}{}
for \eqn{j = 1, \ldots, k}{}, where \emph{k} is the number of groups (units) in a dataset.

From now on, the subscript \emph{(i)} means \emph{i}-th simulation and the subscript \emph{j} indicates \emph{j}-th group. So, notations with a subscript \emph{(i)} are (\emph{k} by 1) vectors, for example \eqn{\theta_{(i)}' = (\theta_{(i)1}, \theta_{(i)2}, \ldots, \theta_{(i)k})}{}.

Pseudo-data generating process starts from the second-level hierarchy to the first-level. \code{coverage} first generates true parameters (\eqn{\theta_{(i)}}{}) for \emph{k} groups at the second-level and then moves onto the first-level to simulate pseudo-data sets, \eqn{y_{(i)}}{} for Gaussian or \eqn{z_{(i)}}{} for Binomial and Poisson data, given previously generated true parameters (\eqn{\theta_{(i)}}{}).

So, in order to generate pseudo-datasets, \code{coverage} needs parameters of prior distribution,  
(\emph{A} (or \emph{r}) and \eqn{\beta}{} (\code{reg.coef})) 
or (\emph{A} (or \emph{r}) and \eqn{\mu_{0}}{}). From here, we have four options to run \code{coverage}.

First, if any values related to the prior distribution are not designated like 
\code{coverage(b, nsim = 10)}, then \code{coverage} will regard estimated values (or known prior mean, \eqn{\mu_{0}}{}) in \code{b} (\code{gbp.object}) as given true values when it generates lots of pseudo-datasets. After sampling \eqn{\theta_{(i)}}{} from the prior distribution determined by these estimated values (or known prior mean) in \code{b} (\code{gbp.object}), \code{coverage} creates an \emph{i}-th pseudo-dataset based on \eqn{\theta_{(i)}}{} just sampled.

Second, \code{coverage} allows us to try different true values in generating datasets. Suppose \code{gbp.object} is based on the model with a known prior mean, \eqn{\mu_{0}}{}. Then, we can try either different \code{A.or.r} or \code{mean.PriorDist}. For example, \code{coverage(b, A.or.r = 20, nsim = 10)}, \\{}
\code{coverage(b, mean.PriorDist = 0.5, nsim = 10)}, or \\{}
\code{coverage(b, A.or.r = 20, mean.PriorDist = 0.5, nsim = 10)}. Note that we cannot set \code{reg.coef} because the second-level mean (prior mean) is known in \code{gbp.object} to begin with.

Suppose \code{gbp.object} is based on the model with an unknown prior mean. In this case, \code{gbp.object} has the estimation result of regression model, linear regression for Normal-Normal, log-linear regression for Poisson-Gamma, or logistic regression for Binomial-Beta, (only intercept term if there is no covariate) to estimate the unknown prior mean. Then, we can try some options: one or two of (\code{A.or.r}, \code{mean.PriorDist}, \code{reg.coef}). For example, \code{coverage(b, A.or.r = 20, nsim = 10)}, \code{coverage(b, mean.PriorDist = 0.5, nsim = 10)}, or \code{coverage(b, reg.coef = 0.1, nsim = 10)} with no covariate where \code{reg.coef} is a designated intercept term. Estimates in \code{gbp.object} will be used for undesignated values. Also, we can try appropriate combinations of two arguments. For example, \code{coverage(b, A.or.r = 20, mean.PriorDist = 0.5, nsim = 10)} and \\{}
\code{coverage(b, A.or.r = 20, reg.coef = 0.1, nsim = 10)}. If we have one covariate, a 2 by 1 vector should be designated for \code{reg.coef}, one for an intercept term and the other for a regression coefficient of the covariate. Note that the two arguments, \code{mean.PriorDist} and \code{reg.coef}, cannot be assigned together because we do not need \code{reg.coef} given \code{mean.PriorDist}.

The simple unbiased estimator of coverage probability in \emph{j}-th group is a sample mean of indicators over all simulated datasets. The \emph{j}-th indicator in \emph{i}-th simulation is 1 if the estimated interval of the \emph{j}-th group on \emph{i}-th simulated dataset contains a true parameter 
\eqn{\theta_{(i)j}}{} that generated the observed value of the \emph{j}-th group in the 
\emph{i}-th dataset.

Rao-Blackwellized unbiased estimator for group \emph{j} is a conditional expectation of the simple unbiased estimator given a sufficient statistic, \eqn{y_{j}}{} for Gaussian or \eqn{z_{j}}{} for Binomial and Poisson data.
\end{Details}
%
\begin{Value}
\begin{ldescription}
\item[\code{coverageRB}] 
Rao-Blackwellized unbiased coverage estimate for each group averaged over all simulations.

\item[\code{coverageS}] 
Simple unbiased coverage estimate for each group averaged over all simulations.

\item[\code{average.coverageRB}] 
Overall Rao-Blackwellized unbiased coverage estimate across all the groups and simulations.

\item[\code{average.coverageS}] 
Overall simple unbiased coverage estimate across all the groups and simulations.

\item[\code{se.coverageRB}] 
Standard error of Rao-Blackwellized unbiased coverage estimate for each group.

\item[\code{se.coverageS}] 
Standard error of simple unbiased coverage estimate for each group.

\item[\code{raw.resultRB}] 
All the Rao-Blackwellized unbiased coverage estimates for every group and for every simulation.

\item[\code{raw.resultS}] 
All the simple unbiased coverage estimates for every group and for every simulation.

\item[\code{Alpha}] 
Nominal confidence level

\item[\code{effective.n}] 
The number of simulated data sets used to calculate the coverage estimates. The data sets may cause some errors in fitting models. For example, the data set may be against the conditions for the posteiror propriety in Binomial data.

\item[\code{model}] 
The model being used, "br", "pr", or "gr".

\item[\code{case}] 
One of the cases used to re-draw the coverage plot by \code{coverage.plot}.

\item[\code{betas}] 
The regression coefficient used to generate simulated data sets.

\item[\code{A.r}] 
The hyper-parameter value (A for Gaussian model, and r for both Binomial and Poisson models) used to generate simulated data sets.

\item[\code{priormeanused}] 
The value of the prior mean(s) used to generate simulated data sets.

\end{ldescription}
\end{Value}
%
\begin{Author}\relax
Hyungsuk Tak, Joseph Kelly, and Carl Morris
\end{Author}
%
\begin{References}\relax
Christiansen, C. and Morris, C. (1997). Hierarchical Poisson Regression Modeling. \emph{Journal of the American Statistical Association}. \bold{92}. 618-632.
\end{References}
%
\begin{Examples}
\begin{ExampleCode}

  # Loading datasets
  data(schools)
  y <- schools$y
  se <- schools$se

  # Arbitrary covariate for schools data
  x2 <- rep(c(-1, 0, 1, 2), 2)

  # baseball data where z is Hits and n is AtBats
  z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
  n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)

  # One covariate: 1 if a player is an outfielder and 0 otherwise
  x1 <- c(1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0)

  #################################################################
  # Gaussian Regression Interactive Multi-level Modeling (GRIMM) #
  #################################################################

    ####################################################################################
    # If we do not have any covariate and do not know a mean of the prior distribution #
    ####################################################################################

    g <- gbp(y, se, model = "gaussian")

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    gcv <- coverage(g, nsim = 10)

    ### gcv$coverageRB, gcv$coverageS, gcv$average.coverageRB, gcv$average.coverageS,
    ### gcv$minimum.coverageRB, gcv$raw.resultRB, gcv$raw.resultS

    ### gcv <- coverage(g, mean.PriorDist = 3, nsim = 100)
    ### gcv <- coverage(g, A.or.r = 150, nsim = 100)
    ### gcv <- coverage(g, reg.coef = 10, nsim = 100)
    ### gcv <- coverage(g, A.or.r = 150, mean.PriorDist = 3, nsim = 100)
    ### gcv <- coverage(g, A.or.r = 150, reg.coef = 10, nsim = 100)

    ##################################################################################
    # If we have one covariate and do not know a mean of the prior distribution yet, #
    ##################################################################################

    g <- gbp(y, se, x2, model = "gaussian")

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    gcv <- coverage(g, nsim = 10)

    ### gcv$coverageRB, gcv$coverageS, gcv$average.coverageRB, gcv$average.coverageS,
    ### gcv$minimum.coverageRB, gcv$raw.resultRB, gcv$raw.resultS

    ### gcv <- coverage(g, mean.PriorDist = 3, nsim = 100)
    ### gcv <- coverage(g, A.or.r = 200, nsim = 100)
    ### gcv <- coverage(g, reg.coef = c(10, 2), nsim = 100)
    ### gcv <- coverage(g, A.or.r = 200, mean.PriorDist = 3, nsim = 100)
    ### gcv <- coverage(g, A.or.r = 200, reg.coef = c(10, 2), nsim = 100)

    ################################################
    # If we know a mean of the prior distribution, #
    ################################################

    g <- gbp(y, se, mean.PriorDist = 8, model = "gaussian")

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    gcv <- coverage(g, nsim = 10)

    ### gcv$coverageRB, gcv$coverageS, gcv$average.coverageRB, gcv$average.coverageS,
    ### gcv$minimum.coverageRB, gcv$raw.resultRB, gcv$raw.resultS

    ### gcv <- coverage(g, mean.PriorDist = 3, nsim = 100)
    ### gcv <- coverage(g, A.or.r = 150, nsim = 100)
    ### gcv <- coverage(g, A.or.r = 150, mean.PriorDist = 3, nsim = 100)

  ################################################################
  # Binomial Regression Interactive Multi-level Modeling (BRIMM) #
  ################################################################

    ####################################################################################
    # If we do not have any covariate and do not know a mean of the prior distribution #
    ####################################################################################

    b <- gbp(z, n, model = "binomial")

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    bcv <- coverage(b, nsim = 10)

    ### bcv$coverageRB, bcv$coverageS, bcv$average.coverageRB, bcv$average.coverageS,
    ### bcv$minimum.coverageRB, bcv$raw.resultRB, bcv$raw.resultS

    ### bcv <- coverage(b, mean.PriorDist = 0.2, nsim = 100)
    ### bcv <- coverage(b, A.or.r = 50, nsim = 100)
    ### bcv <- coverage(b, reg.coef = -1.5, nsim = 100)
    ### bcv <- coverage(b, A.or.r = 50, mean.PriorDist = 0.2, nsim = 100)
    ### bcv <- coverage(b, A.or.r = 50, reg.coef = -1.5, nsim = 100)

    ##################################################################################
    # If we have one covariate and do not know a mean of the prior distribution yet, #
    ##################################################################################

    b <- gbp(z, n, x1, model = "binomial")

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    bcv <- coverage(b, nsim = 10)

    ### bcv$coverageRB, bcv$coverageS, bcv$average.coverageRB, bcv$average.coverageS,
    ### bcv$minimum.coverageRB, bcv$raw.resultRB, bcv$raw.resultS

    ### bcv <- coverage(b, mean.PriorDist = 0.2, nsim = 100)
    ### bcv <- coverage(b, A.or.r = 50, nsim = 100)
    ### bcv <- coverage(b, reg.coef = c(-1.5, 0), nsim = 100)
    ### bcv <- coverage(b, A.or.r = 40, mean.PriorDist = 0.2, nsim = 100)
    ### bcv <- coverage(b, A.or.r = 40, reg.coef = c(-1.5, 0), nsim = 100)

    ################################################
    # If we know a mean of the prior distribution, #
    ################################################

    b <- gbp(z, n, mean.PriorDist = 0.265, model = "binomial")

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    bcv <- coverage(b, nsim = 10)

    ### bcv$coverageRB, bcv$coverageS, bcv$average.coverageRB, bcv$average.coverageS,
    ### bcv$minimum.coverageRB, bcv$raw.resultRB, bcv$raw.resultS

    ### bcv <- coverage(b, mean.PriorDist = 0.2, nsim = 100)
    ### bcv <- coverage(b, A.or.r = 50, nsim = 100)
    ### bcv <- coverage(b, A.or.r = 40, mean.PriorDist = 0.2, nsim = 100)

  ###############################################################
  # Poisson Regression Interactive Multi-level Modeling (PRIMM) #
  ###############################################################

    ################################################
    # If we know a mean of the prior distribution, #
    ################################################

    p <- gbp(z, n, mean.PriorDist = 0.265, model = "poisson")

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    pcv <- coverage(p, nsim = 10)

    ### pcv$coverageRB, pcv$coverageS, pcv$average.coverageRB, pcv$average.coverageS,
    ### pcv$minimum.coverageRB, pcv$raw.resultRB, pcv$raw.resultS

    ### pcv <- coverage(p, mean.PriorDist = 0.265, nsim = 100)
    ### pcv <- coverage(p, A.or.r = 150, nsim = 100)
    ### pcv <- coverage(p, A.or.r = 150, mean.PriorDist = 0.265, nsim = 100)

\end{ExampleCode}
\end{Examples}
\inputencoding{utf8}
\HeaderA{coverage.plot}{Drawing the coverage plot}{coverage.plot}
\keyword{methods}{coverage.plot}
%
\begin{Description}\relax
In a case where users closed the default coverage plot that the \code{coverage} function generated, the function \code{coverage.plot} redraws the coverage plot using the coverage object.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
coverage.plot(cov)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{cov}] 
Any saved result of the \code{coverage} function.

\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
It is possible that a user want to redraw the coverage plot for any reasons. If the result of the \code{coverage} function was saved into a variable, this \code{coverage.plot} redraw the coverage plot using the saved result.
\end{Details}
%
\begin{Value}
The coverage plot will be displayed again.
\end{Value}
%
\begin{Author}\relax
Hyungsuk Tak, Joseph Kelly, and Carl Morris
\end{Author}
%
\begin{Examples}
\begin{ExampleCode}

  # baseball data where z is Hits and n is AtBats
  z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
  n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)

  b <- gbp(z, n, model = "binomial")
  cov <- coverage(b, nsim = 10)  
  coverage.plot(cov)

\end{ExampleCode}
\end{Examples}
\inputencoding{utf8}
\HeaderA{gbp}{Fitting Gaussian, Poisson, and Binomial Hierarchical Models}{gbp}
\methaliasA{gbp.default}{gbp}{gbp.default}
\keyword{methods}{gbp}
%
\begin{Description}\relax
\code{gbp} fits Bayesian hierarchical models using the Uniform distribution on the second level variance component (variance of the prior distribution), which enables good frequentist repeated sampling properties. 
\end{Description}
%
\begin{Usage}
\begin{verbatim}
## Default S3 method:
gbp(x, w, covariates, mean.PriorDist, model =
"gaussian", intercept = TRUE, Alpha = 0.95, n.AR = 0, n.AR.factor = 4,
trial.scale = NA, save.result = TRUE, normal.CI = FALSE, c = 0, u = 1)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{x}] 
a (\emph{k} by 1) vector of \emph{k} groups' sample means for Gaussian or of each group's number of successful trials for Binomial and Poisson data, where \emph{k} is the number of groups (or units) in a dataset.

\item[\code{w}] 
a (\emph{k} by 1) vector composed of the standard errors of all groups for Gaussian or 
of each group's total number of trials for Binomial and Poisson data.

\item[\code{covariates}] 
(optional) a matrix of covariate(s) each column of which corresponds to one covariate.

\item[\code{mean.PriorDist}] 
(optional) a numeric value for the second-level mean parameter, \emph{i.e.} the mean of prior
distribution, if you know this value a priori.

\item[\code{model}] 
a character string indicating which hierarchical model to fit. "gaussian" for Gaussian data, 
"poisson" for Poisson, and "binomial" for Binomial. Default is "gaussian"

\item[\code{intercept}] 
\code{TRUE} or \code{FALSE} flag indicating whether an intercept should be
included in the regression. Default is \code{TRUE}.

\item[\code{Alpha}] 
a \code{float} between 0 and 1 to estimate 100*Alpha\% intervals. Default is 0.95.

\item[\code{n.AR}] 
Only for Binomial model. If \code{n.AR = 1000}, all the results will be based on 1000 posterior samples using the acceptance-rejection sampling. Default is 0.

\item[\code{n.AR.factor}] 
Only for Binomial model. If \code{n.AR = 1000} and \code{n.AR.factor = 4}, then the acceptance-rejection method will sample 4 * 1000 trial samples, and accept or reject them until the method gets n.AR posterior samples. Default is 4.

\item[\code{trial.scale}] 
A scale used in the trial distribution of \eqn{\alpha}{}. If resultant weight has too mamy 0's, scale should be smaller than before. If resultant weight has too few 0's, scale should be larger than before. If there are relatively huge weights, scale should be larger than before. Default is NA.

\item[\code{save.result}] 
Only for Binomial model with the acceptance-rejection sampling. If \code{save.result} is TRUE, all the results of weights and posterior samples will be saved in the gbp object. Default is TRUE.

\item[\code{normal.CI}] 
Only applicable for Gaussian data. If \code{TRUE} then a Normal
approximation is used to construct intervals for the level 1 group
means. If \code{FALSE} (default) then a Skew-Normal distribution is
used. Setting the value to \code{TRUE} may result in speed
improvements but may lead to intervals that under cover.

\item[\code{c}] 
Non-negative constant to determine the hyper-prior distribution of r for the Binomial model with the acceptance-rejection method. If c is positive, then the hyper-prior distribution of r is proper, otherwise improper. \eqn{dr/(c + r)^{u+1}}{}.

\item[\code{u}] 
A positive constant to determine the hyper-prior distribution of r for the Binomial model with the acceptance-rejection method. \eqn{dr/(c + r)^{u+1}}{}.

\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
\code{gbp} fits a hierarchical model whose first-level hierarchy is a distribution of observed data and second-level is a conjugate prior distribution on the first-level parameter. To be specific, for Normal data, \code{gbp} constructs a two-level Normal-Normal multilevel model. \eqn{V_{j}}{} (=\eqn{\sigma^{2}/n_{j}}{}) is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th group 
(or unit) in a dataset.
\deqn{(y_{j} | \theta_{j}) \stackrel{ind}{\sim} N(\theta_{j}, \sigma^{2}_{j})}{}
\deqn{(\theta_{j} |\mu_{0j} , A) \stackrel{ind}{\sim} N(\mu_{0j}, A)}{}
\deqn{\mu_{0j} = x_{j}'\beta}{}
for \eqn{j = 1, \ldots, k}{}, where \emph{k} is the number of groups (units) in a dataset.

For Poisson data, \code{gbp} builds a two-level Poisson-Gamma multilevel model. A square bracket below indicates [mean, variance] of distribution, a constant multiplied to the notation representing Gamma distribution (Gam) is a scale, and \eqn{y_{j}=\frac{z_{j}}{n_{j}}}{}.
\deqn{(z_{j} | \theta_{j}) \stackrel{ind}{\sim} Pois(n_{j}\theta_{j})}{}
\deqn{(\theta_{j} | r, \mu_{0j}) \stackrel{ind}{\sim} \frac{1}{r}Gam(r\mu_{0j})\stackrel{ind}{\sim}Gam[\mu_{0j}, \mu_{0j} / r] }{}
\deqn{log(\mu_{0j}) = x_{j}'\beta}{}
for \eqn{j = 1, \ldots, k}{}, where \emph{k} is the number of groups (units) in a dataset.

For Binomial data, \code{gbp} sets a two-level Binomial-Beta multilevel model. A square bracket below indicates [mean, variance] of distribution and \eqn{y_{j} = \frac{z_{j}}{n_{j}}}{}.
\deqn{(z_{j} | \theta_{j}) \stackrel{ind}{\sim} Bin(n_{j}, \theta_{j})}{}
\deqn{(\theta_{j} | r, \mu_{0j}) \stackrel{ind}{\sim} Beta(r\mu_{0j}, r(1-\mu_{0j})) \stackrel{ind}{\sim} Beta[\mu_{0j}, \mu_{0j}(1 - \mu_{0j}) / (r + 1)]}{}
\deqn{logit(\mu_{0j}) = x_{j}'\beta}{}
for \eqn{j = 1, \ldots, k}{}, where \emph{k} is the number of groups (units) in a dataset.

For reference, based on the above notations, the Uniform prior distribution on the second level variance component (variance of the prior distribution) is \emph{dA} for Gaussian and \eqn{d(\frac{1}{r})}{} 
(= \eqn{\frac{dr}{r^{2}}}{}) for Binomial and Poisson data. The second level variance component can be interpreted as variation among the first-level parameters (\eqn{\theta_{j}}{}) or variance of ensemble information.

Under this setting, the argument \code{x} in \code{gbp} is a (\emph{k} by 1) vector of \emph{k} groups' sample means (\eqn{y_{j}'s}{} in the description of Normal-Normal model above) for Gaussian or of each group's number of successful trials (\eqn{z_{j}'s}{}) for Binomial and Poisson data, where \emph{k} is the number of groups (or units) in a dataset.

The argument \code{w} is a (\emph{k} by 1) vector composed of the standard errors (\eqn{V_{j}'s}{}) of all groups for Gaussian or of each group's total number of trials (\eqn{n_{j}'s}{}) for Binomial and Poisson data.

As for two optional arguments, \code{covariates} and \code{mean.PriorDist}, there are three feasible 
combinations of them to run \code{gbp}. The first situation is when we do not have any covariate and do not 
know a mean of the prior distribution (\eqn{\mu_{0}}{}) a priori. In this case, assigning none of two
optional arguments, such as "\code{gbp(z, n, model = "binomial")}", will lead to a correct model. \code{gbp} 
will automatically fit a regression with only an intercept term to estimate a common mean of the prior
distribution (exchangeability).

The second situation is when we have covariate(s) and do not know a mean of the prior distribution (\eqn{\mu_{0}}{}) a priori. In this case, assigning a matrix, \emph{X}, each column of which corresponds to one covariate, such as "\code{gbp(z, n, X, model = "poisson")}", will lead to a correct model. Default of \code{gbp} is to fit a regression including an intercept term to estimate a mean of the prior distribution. Double exchangeability will hold in this case.

The last case is when we know a mean of the prior distribution (\eqn{\mu_{0}}{}) a priori. Now, we do
not need to estimate regression coefficients at all because we know a true value of \eqn{\mu_{0}}{} (strong assumption).
Designating this value into the argument of \code{gbp} like 
"\code{gbp(y, se, mean.PriorDist = 3)}" is enough to account for it. For reference, 
\code{mean.PriorDist} has a stronger priority than \code{covariates}, which means that when both
arguments are designated, \code{gbp} will fit a hierarchical model using the known mean of prior distribution, \code{mean.PriorDist}.

\code{gbp} returns an object of class "\code{gbp}" which provides three relevant functions \code{plot}, \code{print}, and \code{summary}.
\end{Details}
%
\begin{Value}
An object of class \code{gbp} comprises of:
\begin{ldescription}
\item[\code{sample.mean}] sample mean of each group (or unit)
\item[\code{se}] if Gaussian data, standard error of sample mean in each group (or unit)
\item[\code{n}] if Binomial and Poisson data, total number of trials of each group (or unit)
\item[\code{prior.mean}] numeric if entered, NA if not entered
\item[\code{prior.mean.hat}] estimate of prior mean by a regression if prior mean is not assigned a priori
\item[\code{shrinkage}] shrinkage estimate of each group (adjusted posterior mean)
\item[\code{sd.shrinkage}] posterior standard deviation of shrinkage
\item[\code{post.mean}] posterior mean of each group
\item[\code{post.sd}] posterior standard deviation of each group
\item[\code{post.intv.low}] lower bound of 100*Alpha\% posterior interval (quantile of posterior distribution)
\item[\code{post.intv.upp}] upper bound of 100*Alpha\% posterior interval (quantile of posterior distribution)
\item[\code{model}] "gaussian" for Gaussian, "poisson" for Poisson, and "binomial" for Binomial data
\item[\code{X}] a covariate vector or matrix if designated. NA if not
\item[\code{beta.new}] regression coefficient estimates
\item[\code{beta.var}] estimated variance matrix of regression coefficient
\item[\code{intercept}] whether TRUE or FALSE
\item[\code{a.new}] a posterior mode of \eqn{\alpha}{} defined as log(\emph{A}) for Gaussian or log(\eqn{\frac{1}{r}}{}) for Binomial and Poisson data. Practical meaning (variation of ensemble information) of estimating \eqn{\alpha}{} will appear in \code{summary(gbp.object)}.
\item[\code{a.var}] posterior variance of \eqn{\alpha}{}
\item[\code{Alpha}] confidence level based on which confidence interval is constructed 
\item[\code{weight}] (only for Binomial model) weights for acceptance-rejection method
\item[\code{p}] (only for Binomial model) posterior samples of p based on the acceptance-rejection method, if this method was used. This is a (k by nsim) matrix. Each row contains posteiror samples of each random effect.
\item[\code{alpha}] (only for Binomial model) posterior samples of alpha based on the acceptance-rejection method, if this method was used
\item[\code{beta}] (only for Binomial model) posterior samples of beta based on the acceptance-rejection method, if this method was used
\item[\code{accept.rate}] (only for Binomial model) the acceptance rate of the acceptance-rejection method, if this method was used
\item[\code{n.AR}] (Only for Binomial model) If \code{n.AR = 1000}, all the results will be based on 1000 posterior samples using the acceptance-rejection sampling. Default is 0.

\item[\code{n.AR.factor}] (only for Binomial model) If \code{n.AR = 1000} and \code{n.AR.factor = 4}, then the acceptance-rejection method will sample 4 * 1000 trial posteior samples, and accept or reject them. Default is 4.
\end{ldescription}
\end{Value}
%
\begin{Author}\relax
Hyungsuk Tak, Joseph Kelly, and Carl Morris
\end{Author}
%
\begin{References}\relax
Morris, C. and Lysy, M. (2012). Shrinkage Estimation in Multilevel Normal Models. 
\emph{Statistical Science}. \bold{27}. 115-134.
\end{References}
%
\begin{Examples}
\begin{ExampleCode}

  # Loading datasets
  data(schools)
  y <- schools$y
  se <- schools$se

  # Arbitrary covariate for schools data
  x2 <- rep(c(-1, 0, 1, 2), 2)

  # baseball data where z is Hits and n is AtBats
  z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
  n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)

  # One covariate: 1 if a player is an outfielder and 0 otherwise
  x1 <- c(1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0)

  ################################################################
  # Gaussian Regression Interactive Multilevel Modeling (GRIMM) #
  ################################################################

    ####################################################################################
    # If we do not have any covariate and do not know a mean of the prior distribution #
    ####################################################################################

    g <- gbp(y, se, model = "gaussian")
    g
    print(g, sort = FALSE)
    summary(g)
    plot(g)
    plot(g, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    gcv <- coverage(g, nsim = 10)

    ### gcv$coverageRB, gcv$coverage10, gcv$average.coverageRB, gcv$average.coverage10,
    ### gcv$minimum.coverageRB, gcv$minimum.coverage10, gcv$raw.resultRB, gcv$raw.result10.

    ### when we want to simulate pseudo datasets based on different values of A
    ### and a regression coefficient (intercept), 
    ### not using estimated values as true ones.
    gcv <- coverage(g, A.or.r = 9, reg.coef = 10, nsim = 10)

    ##################################################################################
    # If we have one covariate and do not know a mean of the prior distribution yet, #
    ##################################################################################

    g <- gbp(y, se, x2, model = "gaussian")
    g
    print(g, sort = FALSE)
    summary(g)
    plot(g)
    plot(g, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    gcv <- coverage(g, nsim = 10)

    ### gcv$coverageRB, gcv$coverage10, gcv$average.coverageRB, gcv$average.coverage10,
    ### gcv$minimum.coverageRB, gcv$minimum.coverage10, gcv$raw.resultRB, gcv$raw.result10.

    ### when we want to simulate pseudo datasets based on different values of A
    ### and regression coefficients, not using estimated values 
    ### as true ones. Two values of reg.coef are for beta0 and beta1
    gcv <- coverage(g, A.or.r = 9, reg.coef = c(10, 1), nsim = 10)

    ################################################
    # If we know a mean of the prior distribution, #
    ################################################

    g <- gbp(y, se, mean.PriorDist = 8, model = "gaussian")
    g
    print(g, sort = FALSE)
    summary(g)
    plot(g)
    plot(g, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    gcv <- coverage(g, nsim = 10)

    ### gcv$coverageRB, gcv$coverage10, gcv$average.coverageRB, gcv$average.coverage10,
    ### gcv$minimum.coverageRB, gcv$minimum.coverage10, gcv$raw.resultRB, gcv$raw.result10.

    ### when we want to simulate pseudo datasets based on different values of A and
    ### 2nd level mean as true ones, not using estimated values as true ones.
    coverage(g, A.or.r = 9, mean.PriorDist = 5, nsim = 10)

  ###############################################################
  # Binomial Regression Interactive Multilevel Modeling (BRIMM) #
  ###############################################################

    ####################################################################################
    # If we do not have any covariate and do not know a mean of the prior distribution #
    ####################################################################################

    b <- gbp(z, n, model = "binomial")
    b
    print(b, sort = FALSE)
    summary(b)
    plot(b)
    plot(b, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    bcv <- coverage(b, nsim = 10)

    ### bcv$coverageRB, bcv$coverage10, bcv$average.coverageRB, bcv$average.coverage10,
    ### bcv$minimum.coverageRB, bcv$minimum.coverage10, bcv$raw.resultRB, bcv$raw.result10.

    ### when we want to simulate pseudo datasets based on different values of r
    ### and a regression coefficient (intercept), 
    ### not using estimated values as true ones.
    bcv <- coverage(b, A.or.r = 60, reg.coef = -1, nsim = 10)

    ##################################################################################
    # If we have one covariate and do not know a mean of the prior distribution yet, #
    ##################################################################################

    b <- gbp(z, n, x1, model = "binomial")
    b
    print(b, sort = FALSE)
    summary(b)
    plot(b)
    plot(b, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    bcv <- coverage(b, nsim = 10)

    ### bcv$coverageRB, bcv$coverage10, bcv$average.coverageRB, bcv$average.coverage10,
    ### bcv$minimum.coverageRB, bcv$minimum.coverage10, bcv$raw.resultRB, bcv$raw.result10.

    ### when we want to simulate pseudo datasets based on different values of r
    ### and regression coefficients, not using estimated values 
    ### as true ones. Two values of reg.coef are for beta0 and beta1
    bcv <- coverage(b, A.or.r = 60, reg.coef = c(-1, 0), nsim = 10)

    ################################################
    # If we know a mean of the prior distribution, #
    ################################################

    b <- gbp(z, n, mean.PriorDist = 0.265, model = "binomial")
    b
    print(b, sort = FALSE)
    summary(b)
    plot(b)
    plot(b, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    bcv <- coverage(b, nsim = 10)

    ### bcv$coverageRB, bcv$coverage10, bcv$average.coverageRB, bcv$average.coverage10,
    ### bcv$minimum.coverageRB, bcv$minimum.coverage10, bcv$raw.resultRB, bcv$raw.result10.

    ### when we want to simulate pseudo datasets based on different values of r and
    ### 2nd level mean as true ones, not using estimated values as true ones.
    bcv <- coverage(b, A.or.r = 60, mean.PriorDist = 0.3, nsim = 10)

  ##############################################################
  # Poisson Regression Interactive Multilevel Modeling (PRIMM) #
  ##############################################################

    ################################################
    # If we know a mean of the prior distribution, #
    ################################################

    p <- gbp(z, n, mean.PriorDist = 0.265, model = "poisson")
    p
    print(p, sort = FALSE)
    summary(p)
    plot(p)
    plot(p, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    pcv <- coverage(p, nsim = 10)

    ### pcv$coverageRB, pcv$coverage10, pcv$average.coverageRB, pcv$average.coverage10,
    ### pcv$minimum.coverageRB, pcv$minimum.coverage10, pcv$raw.resultRB, pcv$raw.result10.

    ### when we want to simulate pseudo datasets based on different values of r and
    ### 2nd level mean as true ones, not using estimated values as true ones.
    pcv <- coverage(p, A.or.r = 60, mean.PriorDist = 0.3, nsim = 10)

\end{ExampleCode}
\end{Examples}
\inputencoding{utf8}
\HeaderA{hospital}{Thirty-one Hospital Data}{hospital}
\keyword{datasets}{hospital}
%
\begin{Description}\relax
Medical profiling evaluation of 31 New York hospitals in 1992. We are to consider these as Normally-distributed indices of successful outcome rates for patients at these 31 hospitals following Coronary Artery Bypass Graft (CABG) surgeries. The indices are centered so that the New York statewide average outcome over all hospitals lies near 0. Larger estimates of \code{y} indicate hospitals that performed better for these surgeries.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
data(hospital)
\end{verbatim}
\end{Usage}
%
\begin{Format}
A dataset of 31 hospitals comprises of:
\begin{description}

\item[\code{y}] values obtained through a variance stabilizing transformation of the unbiased death rate estimates, \code{d} / \code{n}, assuming Binomial data. Details in the reference.
\item[\code{se}] approximated standard error of y.
\item[\code{d}] the number of deaths within a month of CABG surgeries in each hospital
\item[\code{n}] total number of patients receiving CABG surgeries (case load) in each hospital

\end{description}

\end{Format}
%
\begin{Source}\relax
Morris, C. and Lysy, M. (2012). Shrinkage Estimation in Multilevel Normal Models. \emph{Statistical Science}. \bold{27}. 115-134.
\end{Source}
%
\begin{Examples}
\begin{ExampleCode}
  data(hospital)
\end{ExampleCode}
\end{Examples}
\inputencoding{utf8}
\HeaderA{plot.gbp}{Drawing Shrinkage and Posterior Interval Plots}{plot.gbp}
\keyword{methods}{plot.gbp}
%
\begin{Description}\relax
\code{plot(gbp.object)} draws shrinkage and posterior interval plots
\end{Description}
%
\begin{Usage}
\begin{verbatim}
## S3 method for class 'gbp'
plot(x, sort = TRUE, ...)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{x}] 
a resultant object of \code{gbp} function.

\item[\code{sort}] 
\code{TRUE} or \code{FALSE} flag. If \code{TRUE}, the interval plot (second plot) will be drawn by the order of \code{se} for Gaussian, or of \code{n} for Binomial and Poisson data. If \code{FALSE}, it will be by the order of data input. Default is \code{TRUE}.

\item[\code{...}] 
further arguments passed to other methods.

\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
As for the argument \code{x}, if the result of \code{gbp} is designated to 
\code{b} like "\code{b <- gbp(z, n, model = "binomial")}", the argument \code{x} is supposed to be \code{b}.

This function produces two plots containing information about the prior, sample, and posterior means.

The first plot is a shrinkage plot representing sample means (black circle) on the
upper horizontal line and prior (blue line) and posterior means (red
circle) on the lower horizontal line. The aim of this plot is to get a sense of the
magnitude of the shrinkage and to observe if any change in ordering of the
groups has occurred. Crossovers (changes of order) are noted by a
black square as indicated in the legend. If the points plotted have
the same value then a sunflower plot is produced where each petal
(line protruding from the point) represent the count of points with
that value. The plot also aims to incorporate the uncertainty and the lengths of the violet and green lines are
proportional to the standard error and the posterior standard
deviation respectively.

The final plot shows interval estimates of all the groups (units) in a dataset. Two short horizontal ticks at both ends of each black vertical line indicate 97.5\% and 2.5\% quantiles of a posterior distribution for each group (Normal for Gaussian, Beta for Binomial, and Gamma for Poisson). Red dots (posterior mean) are between black circles (sample mean) and blue line(s) (prior mean) as a result of shrinkage (regression toward the mean).

If we want to see the interval plot (the second plot) NOT sorted by the order of \code{se} for Gaussian, or of \code{n} for Binomial and Poisson data, \code{plot(b, sort = FALSE)} will show this plot by the order of data input.
\end{Details}
%
\begin{Value}
Two plots described in \emph{details} will be displayed.
\end{Value}
%
\begin{Author}\relax
Hyungsuk Tak, Joseph Kelly, and Carl Morris
\end{Author}
%
\begin{Examples}
\begin{ExampleCode}

  data(hospital)

  z <- hospital$d
  n <- hospital$n
  y <- hospital$y
  se <- hospital$se

  ###################################################################################
  # We do not have any covariates and do not know a mean of the prior distribution. #
  ###################################################################################

    ###############################################################
    # Gaussian Regression Interactive Multilevel Modeling (GRIMM) #
    ###############################################################

    g <- gbp(y, se, model = "gaussian")
    plot(g)
    plot(g, sort = FALSE)

    ###############################################################
    # Binomial Regression Interactive Multilevel Modeling (BRIMM) #
    ###############################################################

    b <- gbp(z, n, model = "binomial")
    plot(b)
    plot(b, sort = FALSE)

    ##############################################################
    # Poisson Regression Interactive Multilevel Modeling (PRIMM) #
    ##############################################################

    p <- gbp(z, n, mean.PriorDist = 0.03, model = "poisson")
    plot(p)
    plot(p, sort = FALSE)

\end{ExampleCode}
\end{Examples}
\inputencoding{utf8}
\HeaderA{print.gbp}{Displaying 'gbp' Class}{print.gbp}
\keyword{methods}{print.gbp}
%
\begin{Description}\relax
\code{print.gbp} enables users to see a compact group-level (unit-level) estimation result of \code{gbp} function.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
## S3 method for class 'gbp'
print(x, sort = TRUE, ...)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{x}] 
a resultant object of \code{gbp} function.

\item[\code{sort}] 
\code{TRUE} or \code{FALSE} flag. If \code{TRUE}, the result will appear by the order of \code{se} for Gaussian, or of \code{n} for Binomial and Poisson data. If \code{FALSE}, it will do by the order of data input. Default is \code{TRUE}.

\item[\code{...}] 
further arguments passed to other methods.

\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
As for the argument \code{x}, if the result of \code{gbp} is designated to 
\code{b} like "\code{b <- gbp(z, n, model = "binomial")}", the argument \code{x} is supposed to be \code{b}.

We do not need to type "\code{print(b, sort = TRUE)}" but "\code{b}" itself is enough to call \code{print(b, sort = TRUE)}. But if we want to see the result NOT sorted by the order of \code{se} for Gaussian, or of \code{n} for Binomial and Poisson data, \code{print(b, sort = FALSE)} will show the result by the order of data input.
\end{Details}
%
\begin{Value}
\code{print(gbp.object)} will display:
\begin{ldescription}
\item[\code{obs.mean}] sample mean of each group
\item[\code{se}] if Gaussian data, standard error of each group
\item[\code{n}] if Binomial or Poisson data, total number of trials of each group
\item[\code{X}] a covariate vector or matrix if designated. NA if not
\item[\code{prior.mean}] numeric if entered, NA if not entered
\item[\code{prior.mean.hat}] estimate of prior mean by a regression if prior mean is not assigned a priori. The variable name on the display will be "prior.mean"
\item[\code{prior.mean.AR}] the posterior mean(s) of the expected random effects, if the acceptance-rejection method is used for the binomial model. The variable name on the display will be "prior.mean".
\item[\code{shrinkage}] shrinkage estimate of each group (adjusted posterior mean)
\item[\code{shrinkage.AR}] the posterior mean of the shrinkage factor, if the acceptance-rejection method is used for the binomial model. The variable name on the display will be "shrinkage".
\item[\code{low.intv}] lower bound of 100*Alpha\% posterior interval
\item[\code{post.mean}] posterior mean of each group
\item[\code{upp.intv}] upper bound of 100*Alpha\% posterior interval
\item[\code{post.sd}] posterior standard deviation of each group
\end{ldescription}
\end{Value}
%
\begin{Author}\relax
Hyungsuk Tak, Joseph Kelly, and Carl Morris
\end{Author}
%
\begin{Examples}
\begin{ExampleCode}

  data(hospital)

  z <- hospital$d
  n <- hospital$n
  y <- hospital$y
  se <- hospital$se

  ###################################################################################
  # We do not have any covariates and do not know a mean of the prior distribution. #
  ###################################################################################

    ###############################################################
    # Gaussian Regression Interactive Multilevel Modeling (GRIMM) #
    ###############################################################

    g <- gbp(y, se, model = "gaussian")
    g
    print(g, sort = FALSE)

    ###############################################################
    # Binomial Regression Interactive Multilevel Modeling (BRIMM) #
    ###############################################################

    b <- gbp(z, n, model = "binomial")
    b
    print(b, sort = FALSE)

    ##############################################################
    # Poisson Regression Interactive Multilevel Modeling (PRIMM) #
    ##############################################################

    p <- gbp(z, n, mean.PriorDist = 0.03, model = "poisson")
    p
    print(p, sort = FALSE)

\end{ExampleCode}
\end{Examples}
\inputencoding{utf8}
\HeaderA{print.summary.gbp}{Displaying 'summary.gbp' Class}{print.summary.gbp}
\keyword{methods}{print.summary.gbp}
%
\begin{Description}\relax
\code{summary(gbp.object)} enables users to see a compact summary of estimation result.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
## S3 method for class 'summary.gbp'
print(x, ...)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{x}] 
a resultant object of \code{gbp} function.

\item[\code{...}] 
further arguments passed to other methods.

\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
The summary has three parts depending on the model fitted by \code{gbp}; \code{Main Summary}, \\{}\code{Second-level Variance Component Estimation Summary}, and \code{Regression Summary} (if fitted).

A display of \code{Main Summary} changes depending on whether all the groups (units) has the same standard error for Gaussian data (or the same total number of trials for Binomial and Poisson data). If they are not the same, 
\code{Main Summary} lists groups (units) with minimum, median, and maximum values of the standard error for Gaussian data (or of the total number of trials for Binomial and Poisson data). And the last row of \code{Main Summary} is about the overall average for all the groups (units) within each column. Note that this last row is not an average over displayed groups (units) above.

If groups (units) have the same standard error for Gaussian (or the same total number of trials for Binomial and Poisson), \code{Main Summary} lists groups (units) with minimum, median, and maximum values of the sample mean.

For reference, if there are several units with the same median value, they will show up with numbering.

The second part is about the \code{Second-level Variance Component Estimation Summary}. For reference, the second level variance component can be interpreted as variation among the first-level parameters (\eqn{\theta_{j}}{}) or variance in ensemble information. It is \emph{A} for Gaussian, \eqn{\frac{\mu_{0j}}{r}}{} for Poisson, and \eqn{\frac{\mu_{0j}(1 - \mu_{0j})}{r}}{} for Binomial data. To be specific, this part shows estimate of \eqn{\alpha}{} (a posterior mode) defined as log(\emph{A}) for Gaussian or log(\eqn{\frac{1}{r}}{}) for Binomial and Poisson data, and its standard error.

The last part depends on whether \code{gbp} fitted a regression or not. For reference, \code{gbp} fits a regression if the second-level mean (\code{mean.PriorDist}) was not designated. In this case, \code{summary(gbp.object)} will display the result of regression fit.

\end{Details}
%
\begin{Value}
\code{summary(gbp.object)} shows a compact summary of estimation result such as:
\begin{ldescription}
\item[\code{Main summary}] 
\begin{description}

\item[Unit w/ min(se or n)] an estimation result of a group (unit) with the minimum standard error for Gaussian or the minimum total number of trials for Binomial and Poisson data.
\item[Unit w/ min(sample.mean)] appears instead of \code{Group w/ min(se or n)} when all the groups (units) have the same standard error for Gaussian or the same total number of trials for Binomial and Poisson data.
\item[Unit w/ median(se or n)] an estimation result of group(s) (unit(s)) with the median standard error for Gaussian or the median total number of trials for Binomial and Poisson data.
\item[Unit w/ median(sample.mean)] appears instead of \code{Group w/ median(se or n)} when all the groups (units) have the same standard error for Gaussian or the same total number of trials for Binomial and Poisson data.
\item[Unit w/ max(se or n)] an estimation result of a group (unit) with the maximum standard error for Gaussian or the maximum total number of trials for Binomial and Poisson data.
\item[Unit w/ max(sample.mean)] appears instead of \code{Group w/ max(se or n)} when all the groups (units) have the same standard error for Gaussian or the same total number of trials for Binomial and Poisson data.
\item[Overall Means] the overall average for all the groups (units) within each column.

\end{description}

\item[\code{Second-level Variance Component Estimation Summary}] 
\begin{description}

\item[post.mode.alpha] a posterior mode of \eqn{\alpha}{} defined as log(\emph{A}) for Gaussian or log(\eqn{\frac{1}{r}}{}) for Binomial and Poisson data.
\item[post.sd.alpha] standard deviation of the posterior distribution of alpha
\item[post.mode.r] posterior mode of either \eqn{r}{} for Bianomial and Poisson models or \eqn{A}{} for Gaussian model.
\item[post.median.alpha] posterior median of \eqn{\alpha}{} for Bianomial model, if the acceptance-rejection method is used.
\item[post.median.r] posterior median of \eqn{r}{} for Bianomial model, if the acceptance-rejection method is used.

\end{description}

\item[\code{Regression Summary (if fitted)}] 
\begin{description}

\item[estimate] regression coefficient estimates.
\item[se] estimated standard error of regression coefficients.
\item[z.val] estimate / se.
\item[p.val] two-sided p-values.

\end{description}

\end{ldescription}
\end{Value}
%
\begin{Author}\relax
Hyungsuk Tak, Joseph Kelly, and Carl Morris
\end{Author}
%
\begin{Examples}
\begin{ExampleCode}

  data(hospital)

  z <- hospital$d
  n <- hospital$n
  y <- hospital$y
  se <- hospital$se

  ###################################################################################
  # We do not have any covariates and do not know a mean of the prior distribution. #
  ###################################################################################

    ###############################################################
    # Gaussian Regression Interactive Multilevel Modeling (GRIMM) #
    ###############################################################

    g <- gbp(y, se, model = "gaussian")
    summary(g)

    ###############################################################
    # Binomial Regression Interactive Multilevel Modeling (BRIMM) #
    ###############################################################

    b <- gbp(z, n, model = "binomial")
    summary(b)

    ##############################################################
    # Poisson Regression Interactive Multilevel Modeling (PRIMM) #
    ##############################################################

    p <- gbp(z, n, mean.PriorDist = 0.03, model = "poisson")
    summary(p)

\end{ExampleCode}
\end{Examples}
\inputencoding{utf8}
\HeaderA{Rgbp}{Gaussian, Poisson, and Binomial Hierarchical Modeling}{Rgbp}
\aliasA{Rgbp-package}{Rgbp}{Rgbp.Rdash.package}
\keyword{package}{Rgbp}
%
\begin{Description}\relax
Bayesian-frequentist reconciliation via approximate Bayesian hierarchical modeling and frequency method checking for over-dispersed Gaussian, Binomial, and Poisson data.
\end{Description}
%
\begin{Details}\relax

\Tabular{ll}{
Package: & Rgbp\\{}
Type: & Package\\{}
Version: & 1.0.0\\{}
Date: & 2013-03-16\\{}
License: & GPL-2\\{}
Main functions: & \code{\LinkA{gbp}{gbp}}, \code{\LinkA{coverage}{coverage}}\\{}
}

\code{Rgbp} is an R package that utilizes approximate Bayesian machinery to provide a method of estimating two-level hierarchical models for Gaussian, Poisson, and Binomial data in a fast and computationally efficient manner. The main products of this package are point and interval estimates for the true parameters, whose good frequency properties can be validated via its repeated sampling procedure called frequency method checking.  It is found that such Bayesian-frequentist reconciliation allows \code{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.
\end{Details}
%
\begin{Author}\relax
Hyungsuk Tak, Joseph Kelly, and Carl Morris

Maintainer: Joseph Kelly <josephkelly@google.com>
\end{Author}
%
\begin{References}\relax
Morris, C. and Lysy, M. (2012). Shrinkage Estimation in Multilevel Normal Models. \emph{Statistical Science}. \bold{27}. 115-134.
\end{References}
%
\begin{Examples}
\begin{ExampleCode}

  # Loading datasets
  data(schools)
  y <- schools$y
  se <- schools$se

  # Arbitrary covariate for schools data
  x2 <- rep(c(-1, 0, 1, 2), 2)

  # baseball data where z is Hits and n is AtBats
  z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
  n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)

  # One covariate: 1 if a player is an outfielder and 0 otherwise
  x1 <- c(1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0)

  ################################################################
  # Gaussian Regression Interactive Multilevel Modeling (GRIMM) #
  ################################################################

    ####################################################################################
    # If we do not have any covariate and do not know a mean of the prior distribution #
    ####################################################################################

    g <- gbp(y, se, model = "gaussian")
    g
    print(g, sort = FALSE)
    summary(g)
    plot(g)
    plot(g, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    ### gcv <- coverage(g, nsim = 10)  
    ### more details in ?coverage

    ##################################################################################
    # If we have one covariate and do not know a mean of the prior distribution yet, #
    ##################################################################################

    g <- gbp(y, se, x2, model = "gaussian")
    g
    print(g, sort = FALSE)
    summary(g)
    plot(g)
    plot(g, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    ### gcv <- coverage(g, nsim = 10)  
    ### more details in ?coverage

    ################################################
    # If we know a mean of the prior distribution, #
    ################################################

    g <- gbp(y, se, mean.PriorDist = 8, model = "gaussian")
    g
    print(g, sort = FALSE)
    summary(g)
    plot(g)
    plot(g, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    ### gcv <- coverage(g, nsim = 10)  
    ### more details in ?coverage

  ###############################################################
  # Binomial Regression Interactive Multilevel Modeling (BRIMM) #
  ###############################################################

    ####################################################################################
    # If we do not have any covariate and do not know a mean of the prior distribution #
    ####################################################################################

    b <- gbp(z, n, model = "binomial")
    b
    print(b, sort = FALSE)
    summary(b)
    plot(b)
    plot(b, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    ### bcv <- coverage(b, nsim = 10)  
    ### more details in ?coverage

    ##################################################################################
    # If we have one covariate and do not know a mean of the prior distribution yet, #
    ##################################################################################

    b <- gbp(z, n, x1, model = "binomial")
    b
    print(b, sort = FALSE)
    summary(b)
    plot(b)
    plot(b, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    ### bcv <- coverage(b, nsim = 10)  
    ### more details in ?coverage

    ################################################
    # If we know a mean of the prior distribution, #
    ################################################

    b <- gbp(z, n, mean.PriorDist = 0.265, model = "binomial")
    b
    print(b, sort = FALSE)
    summary(b)
    plot(b)
    plot(b, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    ### bcv <- coverage(b, nsim = 10)  
    ### more details in ?coverage

  ##############################################################
  # Poisson Regression Interactive Multilevel Modeling (PRIMM) #
  ##############################################################

    ################################################
    # If we know a mean of the prior distribution, #
    ################################################

    p <- gbp(z, n, mean.PriorDist = 0.265, model = "poisson")
    p
    print(p, sort = FALSE)
    summary(p)
    plot(p)
    plot(p, sort = FALSE)

    ### when we want to simulate pseudo datasets considering the estimated values 
    ### as true ones.
    ### pcv <- coverage(p, nsim = 10)  
    ### more details in ?coverage

\end{ExampleCode}
\end{Examples}
\inputencoding{utf8}
\HeaderA{schools}{Eight Schools Data}{schools}
\keyword{datasets}{schools}
%
\begin{Description}\relax
Dataset as seen in Rubin (1981) which was an analysis of coaching
effects on SAT scores from eight schools.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
data(schools)
\end{verbatim}
\end{Usage}
%
\begin{Format}
A dataset of 8 schools containing
\begin{description}

\item[\code{y}] The observed coaching effect of each school
\item[\code{se}] The standard error of the coaching effect of each school.

\end{description}

\end{Format}
%
\begin{Source}\relax
Rubin, D. B. (1981). \emph{Estimation in parallel randomized
experiments.} Journal of Educational Statistics, 6:377-401.
\end{Source}
%
\begin{Examples}
\begin{ExampleCode}
  data(schools)
\end{ExampleCode}
\end{Examples}
\inputencoding{utf8}
\HeaderA{summary.gbp}{Summarizing Estimation Result}{summary.gbp}
\keyword{method}{summary.gbp}
%
\begin{Description}\relax
\code{summary.gbp} prepares a summary of estimation result saved in the object defined as "gbp" class creating "summary.gbp" class
\end{Description}
%
\begin{Usage}
\begin{verbatim}
## S3 method for class 'gbp'
summary(object, ...)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{object}] 
a resultant object of \code{gbp} function.

\item[\code{...}] 
further arguments passed to other methods.

\end{ldescription}
\end{Arguments}
%
\begin{Value}
\code{summary.gbp} prepares below contents:
\begin{ldescription}
\item[\code{main}] 
a table to be displayed by \code{summary(gbp.object)}. \code{\LinkA{print.summary.gbp}{print.summary.gbp}}.

\item[\code{sec.var}] 
a vector containing an estimation result of the second-level variance component. \code{\LinkA{print.summary.gbp}{print.summary.gbp}}.

\item[\code{reg}] 
a vector composed of a summary of regression fit (if fitted). \code{\LinkA{print.summary.gbp}{print.summary.gbp}}.

\end{ldescription}
\end{Value}
%
\begin{Author}\relax
Hyungsuk Tak, Joseph Kelly, and Carl Morris
\end{Author}
%
\begin{Examples}
\begin{ExampleCode}

  data(hospital)

  z <- hospital$d
  n <- hospital$n
  y <- hospital$y
  se <- hospital$se

  ###################################################################################
  # We do not have any covariates and do not know a mean of the prior distribution. #
  ###################################################################################

    ###############################################################
    # Gaussian Regression Interactive Multilevel Modeling (GRIMM) #
    ###############################################################

    g <- gbp(y, se, model = "gaussian")
    summary(g)

    ###############################################################
    # Binomial Regression Interactive Multilevel Modeling (BRIMM) #
    ###############################################################

    b <- gbp(z, n, model = "binomial")
    summary(b)

    ##############################################################
    # Poisson Regression Interactive Multilevel Modeling (PRIMM) #
    ##############################################################

    p <- gbp(z, n, mean.PriorDist = 0.03, model = "poisson")
    summary(p)

\end{ExampleCode}
\end{Examples}
\printindex{}
\end{document}

### 2015-07-01 Rgbp.Rcheck/Rgbp-Ex.R

@@ -1,0 +1,871 @@
+pkgname <- "Rgbp"
+source(file.path(R.home("share"), "R", "examples-header.R"))
+options(warn = 1)
+base::assign(".ExTimings", "Rgbp-Ex.timings", pos = 'CheckExEnv')
+base::cat("name\tuser\tsystem\telapsed\n", file=base::get(".ExTimings", pos = 'CheckExEnv'))
+base::assign(".format_ptime",
+function(x) {
+  if(!is.na(x[4L])) x[1L] <- x[1L] + x[4L]
+  if(!is.na(x[5L])) x[2L] <- x[2L] + x[5L]
+  options(OutDec = '.')
+  format(x[1L:3L], digits = 7L)
+},
+pos = 'CheckExEnv')
+
+### * </HEADER>
+library('Rgbp')
+
+base::assign(".oldSearch", base::search(), pos = 'CheckExEnv')
+cleanEx()
+nameEx("Rgbp-package")
+### * Rgbp-package
+
+flush(stderr()); flush(stdout())
+
+base::assign(".ptime", proc.time(), pos = "CheckExEnv")
+### Name: Rgbp
+### Title: Hierarchical Modeling and Frequency Method Checking on
+###   Overdispersed Gaussian, Poisson, and Binomial Data
+### Aliases: Rgbp-package Rgbp
+### Keywords: package
+
+### ** Examples
+
+
+  # Loading datasets
+  data(schools)
+  y <- schools$y
+  se <- schools$se
+
+  # Arbitrary covariate for schools data
+  x2 <- rep(c(-1, 0, 1, 2), 2)
+  
+  # baseball data where z is Hits and n is AtBats
+  z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
+  n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
+
+  # One covariate: 1 if a player is an outfielder and 0 otherwise
+  x1 <- c(1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0)
+
+  ################################################################
+  # Gaussian Regression Interactive Multilevel Modeling (GRIMM) #
+  ################################################################
+
+    ####################################################################################
+    # If we do not have any covariate and do not know a mean of the prior distribution #
[…]

### 2015-07-02 jss/article_v2.tex
draft and code

@@
 \Plainauthor{Hyungsuk Tak, Joseph Kelly, Carl Morris} %% comma-separated
-\Plaintitle{Rgbp: Hierarchical Modeling and Frequency Method Checking} %% without formatting
+\Plaintitle{Rgbp: An R Package for Conjugate Gaussian, Poisson, and Binomial Hierarchical Modeling and Frequency Method Checking on Overdispersed Data} %% without formatting
 \Shorttitle{\pkg{Rgbp}: Hierarchical Modeling and Frequency Method Checking on Overdispersed Data} %% a short title (if necessary)
@@
 
-\subsection[Hyper-prior distributions]{Hyper-prior Distribution}
+\subsection[Hyper-prior distributions]{Hyper-prior distribution}
 Hyper-prior distributions are the distributions assigned to the second-level parameters called hyper-parameters. With the goal of objectivity in mind, our choice for the hyper-prior distributions is
@@
 
-The ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via the Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \cite{berger1999integrated} for the integrated likelihood in detail.
+The ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via the Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \citep[see]{berger1999integrated} for the integrated likelihood in detail.
 For the Gaussian model, the marginal likelihood function of $A$ is available in a closed form with $\boldsymbol{\beta}$ integrated out, see  \cite{tang2011}.
@@
 \includegraphics[width=6cm]{process.png}
-\caption{Pseudo-data generating process}
+\caption{Pseudo-data generating process.}
 \label{fig:pseudo}
@@
 \begin{CodeInput}
-R> library(Rgbp)
-R> data(hospital)
+R> library(``Rgbp'')
+R> data(``hospital'')
 R> y <- hospital$d
@@
 31      0.0201 1340       0.03     0.338   0.0170    0.0235   0.0310 0.00360
-colMeans           517       0.03     0.600   0.0201    0.0293   0.0403 0.00517
+Mean            517       0.03     0.600   0.0201    0.0293   0.0403 0.00517
 \end{CodeOutput}
@@
 Second-level Variance Component Estimation Summary:
-alpha = log(A) for Gaussian or alpha = log(1/r) for Binomial and Poisson data:
+alpha=log(A) for Gaussian or alpha=log(1/r) for Binomial and Poisson data:
 
@@
 \begin{center}
-\includegraphics[width = 2.5in]{hospital1.png}
-\caption{Shrinkage plot and 95\% interval plot for 31 hospitals}
+\includegraphics[width = 2.8in]{hospital1.png}
+\caption{Shrinkage plot and 95\% interval plot for 31 hospitals.}
 \label{fig:hospshr}
@@
 \begin{center}
-\includegraphics[width = 2.5in]{hospital2.png}
-\caption{Coverage plot via frequency method checking for 31 hospitals}
+\includegraphics[width = 2.8in]{hospital2.png}
+\caption{Coverage plot via frequency method checking for 31 hospitals.}
 \label{fig:hospitalcoverage}
@@
 \begin{CodeInput}
-R> library(Rgbp)
-R> data(schools)
+R> library(``Rgbp'')
+R> data(``schools'')
 R> y  <- schools$y
@@
 8       12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
-colMeans          12.5      8.168     0.552   -9.163     8.168   25.723   8.900
+Mean          12.5      8.168     0.552   -9.163     8.168   25.723   8.900
 \end{CodeOutput}
@@
 Second-level Variance Component Estimation Summary:
-alpha = log(A) for Gaussian or alpha =  log(1/r) for Binomial and Poisson data:
+alpha=log(A) for Gaussian or alpha=log(1/r) for Binomial and Poisson data:
 
@@
 \begin{center}
-\includegraphics[width = 2.5in]{school1.png}
-\caption{Shrinkage plot and 95\% interval plot for 8 schools}
+\includegraphics[width = 2.8in]{school1.png}
+\caption{Shrinkage plot and 95\% interval plot for 8 schools.}
 \label{fig:8schoolsplot}
@@
 \begin{center}
-\includegraphics[width = 2.5in]{school2.png}
-\caption{Coverage plot via frequency method checking for 8 schools}
+\includegraphics[width = 2.8in]{school2.png}
+\caption{Coverage plot via frequency method checking for 8 schools.}
 \label{fig:schoolcoverage}
@@
 \begin{CodeInput}
-R> library(Rgbp)
-R> data(baseball)
+R> library(``Rgbp'')
+R> data(``baseball'')
 R> y <- baseball$Hits
@@
      obs.mean  n  X1 prior.mean shrinkage low.intv post.mean upp.intv post.sd
-1           0.400 45 1.00      0.310     0.715    0.248     0.335    0.429  0.0462
-2           0.378 45 1.00      0.310     0.715    0.244     0.329    0.420  0.0448
-3           0.356 45 1.00      0.310     0.715    0.240     0.323    0.411  0.0437
-4           0.333 45 1.00      0.310     0.715    0.236     0.316    0.403  0.0429
-5           0.311 45 1.00      0.310     0.715    0.230     0.310    0.396  0.0424
-6           0.311 45 0.00      0.233     0.715    0.179     0.256    0.341  0.0415
-7           0.289 45 0.00      0.233     0.715    0.175     0.249    0.331  0.0400
-8           0.267 45 0.00      0.233     0.715    0.171     0.243    0.323  0.0388
-9           0.244 45 0.00      0.233     0.715    0.166     0.237    0.315  0.0380
-10          0.244 45 1.00      0.310     0.715    0.210     0.291    0.379  0.0432
-11          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
-12          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
-13          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
-14          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375  0.0441
-15          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375  0.0441
-16          0.200 45 0.00      0.233     0.715    0.155     0.224    0.302  0.0377
-17          0.178 45 0.00      0.233     0.715    0.148     0.218    0.297  0.0381
-18          0.156 45 0.00      0.233     0.715    0.140     0.211    0.292  0.0389
-colMeans          45 0.44      0.267     0.715    0.191     0.267    0.351  0.0410
+1       0.400 45 1.0      0.310     0.715    0.248     0.335    0.429  0.0462
+2       0.378 45 1.0      0.310     0.715    0.244     0.329    0.420  0.0448
+3       0.356 45 1.0      0.310     0.715    0.240     0.323    0.411  0.0437
+4       0.333 45 1.0      0.310     0.715    0.236     0.316    0.403  0.0429
+5       0.311 45 1.0      0.310     0.715    0.230     0.310    0.396  0.0424
+6       0.311 45 0.0      0.233     0.715    0.179     0.256    0.341  0.0415
+7       0.289 45 0.0      0.233     0.715    0.175     0.249    0.331  0.0400
+8       0.267 45 0.0      0.233     0.715    0.171     0.243    0.323  0.0388
+9       0.244 45 0.0      0.233     0.715    0.166     0.237    0.315  0.0380
+10      0.244 45 1.0      0.310     0.715    0.210     0.291    0.379  0.0432
+11      0.222 45 0.0      0.233     0.715    0.161     0.230    0.308  0.0377
+12      0.222 45 0.0      0.233     0.715    0.161     0.230    0.308  0.0377
+13      0.222 45 0.0      0.233     0.715    0.161     0.230    0.308  0.0377
+14      0.222 45 1.0      0.310     0.715    0.202     0.285    0.375  0.0441
+15      0.222 45 1.0      0.310     0.715    0.202     0.285    0.375  0.0441
+16      0.200 45 0.0      0.233     0.715    0.155     0.224    0.302  0.0377
+17      0.178 45 0.0      0.233     0.715    0.148     0.218    0.297  0.0381
+18      0.156 45 0.0      0.233     0.715    0.140     0.211    0.292  0.0389
+Mean          45 0.4      0.267     0.715    0.191     0.267    0.351  0.0410
 \end{CodeOutput}
@@
 
-The regression coefficient for the outfielder indicator is significant, considering that p-value for $\hat{\beta}_2$ is 0.038.
+The regression coefficient for the outfielder indicator is significant, considering that $p$~value for $\hat{\beta}_2$ is 0.038.
 It means that the  two estimates for the expected random effects for the outfielders and infielders are significantly different.
@@
 \begin{center}
-\includegraphics[width = 2.5in]{baseball1.png}
-\caption{Shrinkage plot and 95\% interval plot for 18 baseball players}
+\includegraphics[width = 2.8in]{baseball1.png}
+\caption{Shrinkage plot and 95\% interval plot for 18 baseball players.}
 \label{fig:baseball}
@@
 \begin{center}
-\includegraphics[width = 2.5in]{baseball2.png}
-\caption{Coverage plot via frequency method checking for 18 players}
+\includegraphics[width = 2.8in]{baseball2.png}
+\caption{Coverage plot via frequency method checking for 18 players.}
 \label{fig:baseball2}
@@
 
-\section[acknowledgments]{Acknowledgments}
-The authors thank Professor Cindy Christiansen, Professor Phil Everson and the 2012 class of Harvard's Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
-
 \appendix
@@
 
+\section*{Acknowledgments}
+The authors thank Professor Cindy Christiansen, Professor Phil Everson and the 2012 class of Harvard's Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
+
 \bibliography{bibliography}

### 2015-07-02 Rgbp/R/gbp.R

@@ -80,11 +80,15 @@ print.gbp <- function(x, sort = TRUE, ...) {
   }
   
   if (sort == TRUE) {
-    temp <- temp[order(temp[, 2]), ]
+    if (x$model == "gr") {
+      temp <- temp[order(temp[, 2], decreasing = TRUE), ]
+    } else {
+      temp <- temp[order(temp[, 2]), ]
+    }
   }
 
   temp.mean <- colMeans(temp)
-  temp <- data.frame(rbind(temp, temp.mean), row.names = c(rownames(temp), "colMeans"))
+  temp <- data.frame(rbind(temp, temp.mean), row.names = c(rownames(temp), "Mean"))
   temp[, 1] <- format.default(temp[, 1], digits = 3)
   temp[dim(temp)[1], 1] <- ""
 
@@ -100,7 +104,7 @@ print.gbp <- function(x, sort = TRUE, ...) {
 
   if (sort == TRUE) {
     if (x$model == "gr") {
-      cat("Summary for each group (sorted by the ascending order of se): \n")
+      cat("Summary for each group (sorted by the descending order of se): \n")
     } else {
       cat("Summary for each group (sorted by  the ascending order of n): \n")
     }
@@ -347,7 +351,11 @@ plot.gbp <- function(x, sort = TRUE, ...) {
 
   if (sort == TRUE) {
     temp.data <- as.data.frame(cbind(y, se, pr.m, po.m, po.sd, po.low, po.upp))
-    temp.data <- temp.data[order(temp.data$se), ]
+    if (x$model == "gr") {
+      temp.data <- temp.data[order(temp.data$se, decreasing = TRUE), ]
+    } else
+      temp.data <- temp.data[order(temp.data$se), ]
+    }
     y <- temp.data$y
     se <- temp.data$se
     pr.m <- temp.data[, 3]
@@ -404,12 +412,12 @@ plot.gbp <- function(x, sort = TRUE, ...) {
 
   if (sort == TRUE) {
     if (x$model == "gr") {
-      xl <- c("Groups sorted by the ascending order of se")
+      xl <- c("Groups sorted by the descending order of se")
     } else {
       xl <- c("Groups sorted by the ascending order of n")
     }
   } else {
-    xl <- c("Groups sorted by the ascending order of n")
+    xl <- c("Groups in the order of data input")
   }
 
   plot(index, po.m, ylim = c(ylim.low, ylim.upp), xlab = xl, ylab = "",

### 2015-07-02 jss/article_v3.tex
draft v3

--- 2015-07-02 jss/article_v2.tex
@@
 \pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data.
-The data that \pkg{Rgbp} assumes comprise of observed sufficient statistics for each random effect, such as averages or proportions, possibly together with covariates of each group but without population-level data.
-The approximate Bayesian tool equipped with the adjustment for density maximization produces point and interval estimates for each random effect, point estimates and their standard errors for regression coefficients, and a point estimate and its standard error for a second-level variance component.
-For the Binomial data, the package provides an option to draw independent  posterior samples of all the model parameters from their  posterior distributions via the acceptance-rejection method.
-The main goal of \pkg{Rgb} is to produce approximate, or exact for the Binomial model, Bayesian interval estimates for the random effects that meet their nominal confidence levels.
-For this purpose, our models adopt unique improper hyper-prior distributions and \pkg{Rgbp} provides a quick way to check whether the resultant Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
+The data that \pkg{Rgbp} assumes comprise of observed sufficient statistics for each random effect, such as sample means, possibly together with covariates of each group.
+The approximate Bayesian tool equipped with the adjustment for density maximization estimates random effects, regression coefficients, and a second-level variance component.
+As for the Binomial model, the package has an option to draw their posterior samples via the acceptance-rejection method.
+The main goal of \pkg{Rgb} is to produce  Bayesian interval estimates for the random effects that meet their nominal confidence levels.
+For this purpose, our models adopt unique improper hyper-prior distributions.
+\pkg{Rgbp} provides a quick way to check whether the resulting Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
 % and evaluates repeated sampling frequency property of the resulting approximate Bayesian interval estimates for random effects
@@
 
-\section[Introduction]{Introduction}
+\section[Introduction]{Introduction (v3; 2 July 2015)}
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
 Gaussian, Poisson, or Binomial data from several independent groups sometimes have more variation than the assumed Gaussian, Poisson, or Binomial distributions of the first-level observed data.
-To account for the extra-variability, called overdispersion, a  two-level conjugate hierarchical model regards first-level mean parameters as random effects that come from a population-level conjugate prior distribution.
+To account for this extra-variability, called overdispersion, a  two-level conjugate hierarchical model regards first-level mean parameters as random effects that come from a population-level conjugate prior distribution.
 The conjugate prior distribution is non-exchangeable if the model incorporates covariate information of each group via a linear, log-linear, or logistic regression according to the data type, and exchangeable if no covariates are available with only an intercept term for the regression.
 
-With an assumption of homogeneity within each group, the observed data are sufficient statistics for the random effects, such as averages or proportions, possibly together with each group's covariate information.
+With an assumption of homogeneity within each group, the observed data are sufficient statistics for the random effects; each group's sample mean for the Gaussian model, each group's number of outcomes happening given some exposure for the Poisson data, and each group's number of successful outcomes out of total number of trials for the Binomial model.
+The data may contain each group's covariate information, though they do not use the population-level data.
 This type of  data is common for a biological analysis on litter data, a meta analysis on independent studies, or small area estimation problems.
-For these data, the two-level model that \pkg{Rgbp} assumes can be considered as a conjugate hierarchical generalized linear model \citep{lee1996hierarchical, hglm2006} where each random effect has a conjugate prior distribution.
-
-\pkg{Rgbp} takes a Bayesian approach with our special improper hyper-prior distributions on hyper-parameters, the parameters of the conjugate prior distribution, to produce  Bayesian interval   estimates for the random effects that achieve nominal confidence levels.
+For these data with  homogeneity within each group, the two-level model that \pkg{Rgbp} assumes can be considered as a conjugate hierarchical generalized linear model \citep{lee1996hierarchical, hglm2006} where each random effect has a conjugate prior distribution.
+
+\pkg{Rgbp} takes a Bayesian approach with our unique improper hyper-prior distributions on the parameters of the conjugate prior distribution, to produce  Bayesian interval   estimates for the random effects that achieve nominal confidence levels.
 The hyper-prior distributions lead to Stein's harmonic prior known to produce good repeated sampling coverage rates of the Bayesian interval estimates for random effects in a two-level Gaussian hierarchical model \citep{tang2011, morris2012, kelly2014advances}.
@@
 When it comes to fitting the model, \pkg{Rgbp} adopts the adjustment for density maximization \citep{carl1988, morris1997, tang2011} (ADM), a Pearson family approximation via maximization.
-For example, a Delta method is a Normal case of the ADM that uses a Normal distribution to obtain an approximate distribution of a function of a parameter with its MLE and observed information plugged-in.
-In this article, the ADM uses Beta distributions to approximate the posterior distributions of shrinkage factors, functions of the second-level variance component, via maximization.
+For example, a Delta method is a Gaussian case of the ADM that uses a Normal distribution to obtain an approximate distribution of a function of a parameter with its MLE and observed information plugged-in.
+In this article, the ADM uses Beta distributions mainly to approximate the posterior distributions of shrinkage factors, functions of the second-level variance component, via maximization.
 Using the approximate Beta posterior distributions of shrinkage factors, \pkg{Rgbp} estimates the first two (three for the Gaussian case) posterior moments of the random effects.
@@
 
-For the Binomial  hierarchical model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters from their posterior distributions via an acceptance-rejection method instead of the approximate Bayesian tool.
+For the Binomial  hierarchical model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters including random effects via an acceptance-rejection method instead of the approximate Bayesian tool.
 
@@
 It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for hierarchical modeling such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models and \pkg{arm} \citep{gelman2014arm} for Bayesian hierarchical regression models.
-The evaluation procedure which we call ``frequency method checking'' adopts a parametric bootstrapping, a Monte Carlo simulation, that generates mock data sets given the values of the hyper-parameters and estimates the coverage rates based on the generated mock data sets.
+The evaluation procedure which we call ``frequency method checking'' uses a parametric bootstrapping  that generates mock data sets given the values of the hyper-parameters and estimates the coverage rates based on the generated mock data sets.
 
@@
 
-One of the functions in \pkg{Rgbp}, \code{gbp}, fits a conjugate hierarchical model in which the first-level has distributions of observed data and the second-level has conjugate distributions on the first-level mean parameters (random effects) without any observed data on this second-level.
-Specifically, with an assumption of the homogeneity within each group, the observed data of the first-level are sufficient statistics  for random effects such as sample means or numbers of successful outcomes.
-These data appear often in a biological analysis on litter data, a meta analysis on independent studies, or small area estimation problems.
-The function \code{gbp}  allows users to choose one of three hierarchical models according to the type of data, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta models.
-There are possibly more hierarchical models depending on the types of data such as Exponential-Gamma \citep{tang2002fitting}, but we choose the three models because these are the most commonly-used models.
-
-In this section, we specify the modeling details.
-Our motivation for the parametrization is to provide an intuitive shrinkage interpretation in inference and to facilitate the estimation procedure, considering that the shrinkage factors under our parametrization are a function of only a second-level variance component.
-
-\subsection[Normal-Normal]{Normal-Normal (``g''=Gaussian data)}
-The following is the general Normal-Normal hierarchical model (hereafter the Gaussian model) assumed by \pkg{Rgbp}.
-The subscript \emph{j} below indicates the \emph{j}-th group among \emph{k} groups in the dataset.
+\pkg{Rgbp} allows users to choose one of three hierarchical models according to the type of data, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta models.
+Although there are possibly more hierarchical models such as Exponential-Gamma \citep{tang2002fitting}, we choose the three models because these are based on the most common data types we encounter in practice.
+
+Also, our parametrization of the three hierarchical models leads to an intuitive shrinkage interpretation in inference and  facilitates the estimation procedure because the shrinkage factors under our parametrization are a function of only a second-level variance component.
+
+\subsection[Normal-Normal]{Normal-Normal model for Gaussian data}
+The following is the Normal-Normal hierarchical model (or the Gaussian model) assumed by \pkg{Rgbp}.
+The subscript \emph{j} below indicates the \emph{j}th group among \emph{k} groups in the dataset.
 For $j=1, 2, \ldots, k$,
-\begin{eqnarray}
-y_{j}\vert \mu_{j} & \stackrel{indep.}{\sim} &\textrm{Normal}(\mu_{j}, V_{j}),\label{normalobs}\\
-\mu_{j}\vert \boldsymbol{\beta}, A & \stackrel{indep.}{\sim} &\textrm{Normal}(\mu^E_{j}, A),\label{normalprior}
-\end{eqnarray}
-
-where $y_j$ is an observed unbiased estimate, sample mean, for random effect $j$, $V_{j}$ is a completely known standard error of $y_j$, $\mu^E_{j}$ is an expected random effect defined as $E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$, and $m$ is the number of regression coefficients to be estimated.
-The default of the function \code{gbp} is to set $x_{j, 1}$ to 1 for an intercept term, though \code{gbp} also provides a usage without the intercept term.
+\begin{align}
+y_{j}\vert \mu_{j} & \stackrel{\textrm{indep.}}{\sim} \textrm{Normal}(\mu_{j}, V_{j}),\label{normalobs}\\
+\mu_{j}\vert \boldsymbol{\beta}, A & \stackrel{\textrm{indep.}}{\sim} \textrm{Normal}(\mu^E_{j}, A),\label{normalprior}
+\end{align}
+
+where $y_j$ is an observed unbiased estimate, e.g., sample mean, for random effect $\mu_j$, $V_{j}$ is a completely known standard error of $y_j$, $\mu^E_{j}$ is an expected random effect defined as $\E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$, and $m$ is the number of regression coefficients to be estimated.
+\pkg{Rgbp} sets $x_{j, 1}$ to 1 for an intercept term as a default, providing a usage without the intercept term, too.
 It is assumed that the second-level variance $A$ is unknown and that the $m\times1$ regression coefficient vector $\boldsymbol{\beta}$ is also unknown unless otherwise specified.
 If no covariates are available with an intercept term, then $\boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_1$ ($m=1$) and thus $\mu^E_{j}=\mu^E=\beta_1$ for all $j$, resulting in an exchangeable conjugate prior distribution for the random effects.
-Based on these conjugate prior distributions for random effects, it is easy to derive the conditional posterior distributions of the random effects.
+Based on these conjugate prior distributions for random effects, it is easy to derive the conditional posterior distributions of each random effect.
 For $j=1, 2, \ldots, k$,
@@
 \begin{equation} \label{normalpost}
-\mu_{j}\vert  \boldsymbol{\beta}, A, \boldsymbol{y} \stackrel{indep.}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu^E_{j},~(1-B_{j})V_{j}~),
-\end{equation}
-where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkage factors, and $\boldsymbol{y}^T=(y_1, y_2, \ldots, y_k)$.
-Note that the conditional posterior mean of the random effect, $\mu^\ast_j\equiv E(\mu_{j}\vert \boldsymbol{\beta}, A, \boldsymbol{y} )=(1-B_{j})y_{j} + B_{j}\mu^E_{j}$,  is a convex combination of the observed sample mean $y_j$ and the expected random effect $\mu^E_j$ weighted by the shrinkage factor $B_j$.
+\mu_{j}\vert  \boldsymbol{\beta}, A, \boldsymbol{y} \stackrel{\textrm{indep.}}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu^E_{j},~(1-B_{j})V_{j}~),
+\end{equation}
+where $B_{j}\equiv V_{j}/(V_{j} + A)$ is a shrinkage factor of group $j$ and $\boldsymbol{y}=(y_1, y_2, \ldots, y_k)^\top$.
+Note that the conditional posterior mean $\E(\mu_{j}\vert \boldsymbol{\beta}, A, \boldsymbol{y} )$, denoted by $\mu^\ast_j$,  is a convex combination of the observed sample mean $y_j$ and the expected random effect $\mu^E_j$ weighted by the shrinkage factor $B_j$.
 If the variance of the conjugate prior distribution, $A$, is smaller than the variance of the observed distribution, $V_j$, then we expect the posterior mean to borrow more information from the more accurate second-level conjugate prior distribution.
 
-\subsection[Poisson-Gamma]{Poisson-Gamma (``p''=Poisson data)}\label{poissonsubsec}
-The function \code{gbp} is also capable of estimating a conjugate Poisson-Gamma hierarchical model (hereafter the Poisson model), though its usage is limited to the case where the expected random effects are known ($m=0$).
-For instance,  from previous studies we may be able to obtain some information about the mean of the population  from which we collect the first-level group data.
+%; sometimes we may be able to obtain  information about the mean of the population from previous studies.
+%; in the limit of $r$ going to 0, the conjugate prior distribution gets flatter. 
+\subsection[Poisson-Gamma]{Poisson-Gamma model for Poisson data}\label{poissonsubsec}
+\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model), though its usage is limited to the case where the expected random effects are known ($m=0$).
 For $j=1, 2, \ldots, k$,
-\begin{eqnarray}
-y_j\vert \lambda_j &\stackrel{indep.}{\sim} & \textrm{Poisson}(n_{j}\lambda_{j}),\\
-\lambda_{j}\vert r &\stackrel{i.i.d.}{\sim}& \textrm{Gamma}(r\lambda^E, r),
-\end{eqnarray}
-where $y_j$ is the number of events happening, $n_{j}$ is the exposure of group $j$, which is not necessarily an integer, $\lambda^E=E(\lambda_j\vert r)$ is the known expected random effect, and $r$ is the unknown second-level variance component.
+\begin{align}
+y_j\vert \lambda_j &\stackrel{\textrm{indep.}}{\sim}  \textrm{Poisson}(n_{j}\lambda_{j}),\\
+\lambda_{j}\vert r &\stackrel{i.i.d.}{\sim} \textrm{Gamma}(r\lambda^E, r),
+\end{align}
+where $y_j$ is the number of events happening, $n_{j}$ is the exposure of group $j$, which is not necessarily an integer, $\lambda^E=\E(\lambda_j\vert r)$ is the known expected random effect, and $r$ is the unknown second-level variance component.
 The mean and variance of the conjugate Gamma prior distribution are $\lambda^E$ and $\lambda^E/r$, respectively.
-We interpret $r$ as the amount of prior information as $n_{j}$ represents the amount of observed information, which makes intuitive sense because the uncertainty of the conjugate prior distribution increases as $r$ decreases; in the limit of $r$ going to 0, the conjugate prior distribution gets flatter.
-The conditional posterior distribution of the random effect $\lambda_j$ for this Poisson-Gamma model is
+We interpret $r$ as the amount of prior information as $n_{j}$ represents the amount of observed information because the uncertainty of the conjugate prior distribution increases as $r$ decreases and vice versa.
+The conditional posterior distribution of the random effect $\lambda_j$ for this Poisson model is
 \begin{equation} \label{gammapost}
@@
 \begin{equation}\label{gammapost_mean_var}
-\lambda^\ast_j\equiv E(\lambda_j\vert r, \boldsymbol{y} )=(1-B_{j})\bar{y}_{j} + B_{j}\lambda^E~~\textrm{and}~~Var(\lambda_j\vert r, \boldsymbol{y})=\frac{\lambda^\ast_j}{r+n_j}.
-\end{equation}
-where $B_{j}\equiv r / (r+n_{j})$ is the shrinkage factor, the relative amount of information in the prior compared to the data.
-The conditional posterior mean is  a convex combination of the unbiased estimate  $\bar{y}_{j} = y_j/n_j$ and the known expected random effect  $\lambda^E$ weighted by $B_j$.
-If the conjugate prior distribution contains more information than the observed data have, \emph{i.e.}, ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the posterior mean shrinks  towards the prior mean by more than 50\%, borrowing more information from the second-level distribution.
-
-Note that the conditional posterior variance in Equation \ref{gammapost_mean_var} is linear in the conditional posterior mean, whereas a slightly different Poisson-Gamma model specification has been used elsewhere \citep{morris1997} that makes the variances  quadratic functions of their means.
-The parametrization of the Poisson model adopted in \pkg{Rgbp} makes shrinkage factors as a function of only the hyper-parameter $r$, while the shrinkage factors based on the parametrization in \cite{morris1997} are functions of $r$ and $\boldsymbol{\beta}$.
-Thus, the estimation procedure and the interpretation of the shrinkage factors are more intuitive under the parametrization in \pkg{Rgbp}.
+\lambda^\ast_j\equiv \E(\lambda_j\vert r, \boldsymbol{y} )=(1-B_{j})\bar{y}_{j} + B_{j}\lambda^E~~\textrm{and}~~\VAR(\lambda_j\vert r, \boldsymbol{y})=\frac{\lambda^\ast_j}{r+n_j}.
+\end{equation}
+where $B_{j}\equiv r / (r+n_{j})$ is the shrinkage factor of group $j$, the relative amount of information in the prior compared to the data.
+The conditional posterior mean is  a convex combination of $\bar{y}_{j}$ and  $\lambda^E$ weighted by $B_j$.
+If the conjugate prior distribution contains more information than the observed data have, \emph{i.e.}, ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the posterior mean shrinks  towards the prior mean by more than 50\%.%, borrowing more information from the second-level distribution.
+
+Note that the conditional posterior variance in  \eqref{gammapost_mean_var} is linear in the conditional posterior mean, whereas a slightly different Poisson-Gamma model specification has been used elsewhere \citep{morris1997} that makes the variances  quadratic functions of their means.
+The parametrization of the Poisson model adopted in \pkg{Rgbp} makes shrinkage factors as a function of only the hyper-parameter $r$, while the shrinkage factors based on the parametrization in \cite{morris1997} are functions of both $r$ and $\boldsymbol{\beta}$.
+%Thus, the estimation for shrinkage factors is easier and the interpretation of the shrinkage factors are more intuitive under the parametrization in \pkg{Rgbp}.
 %in the prior and conditional posterior distributions
 
-\subsection[Binomial-Beta]{Binomial-Beta (``b''=Binomial data)}
-The Binomial-Beta hierarchical model is the last model that \code{gbp} can fit.
-The notation $y_{j}$ below is the number of successes (or failures) out of $n_{j}$ trials.
-Unlike the Poisson model, the expected random effect is either known ($m=0$) or unknown ($m\ge1$) a priori.
-\begin{eqnarray}
-y_{j} \vert p_{j} &\stackrel{indep.}{\sim}& \textrm{Binomial}(n_{j}, ~p_{j}),\\
-p_{j} \vert \boldsymbol{\beta}, r &\stackrel{indep.}{\sim}&\textrm{Beta}(rp^E_j,~ r(1-p^E_j)),
-\end{eqnarray}
-
-where $p^E_j\equiv E(p_j\vert \boldsymbol{\beta}, r)=\exp(\boldsymbol{x}_j^\top\boldsymbol{\beta})/(1+\exp(\boldsymbol{x}_j^\top\boldsymbol{\beta}))$ is the expected random effect  of group $j$ ($j=1, 2, \ldots, k$).
+\subsection[Binomial-Beta]{Binomial-Beta model for Binomial data}
+\pkg{Rgbp} can fit a conjugate Binomial-Beta hierarchical model. Unlike the Poisson model, the expected random effect is either known ($m=0$) or unknown ($m\ge1$). For $j=1, 2, \ldots, k$,
+\begin{align}
+y_{j} \vert p_{j} &\stackrel{\textrm{indep.}}{\sim} \textrm{Binomial}(n_{j}, ~p_{j}),\\
+p_{j} \vert \boldsymbol{\beta}, r &\stackrel{\textrm{indep.}}{\sim} \textrm{Beta}(rp^E_j,~ r(1-p^E_j)),
+\end{align}
+
+where $y_{j}$  is the number of successes  out of $n_{j}$ trials, $p^E_j$ is the expected random effect  of group $j$ defined as $p^E_j\equiv \E(p_j\vert \boldsymbol{\beta}, r)=\exp(\boldsymbol{x}_j^\top\boldsymbol{\beta})/(1+\exp(\boldsymbol{x}_j^\top\boldsymbol{\beta}))$.
 The $m\times 1$ vector of the logistic regression coefficient $\boldsymbol{\beta}$ and the second-level variance component $r$ are unknown.
 The mean and variance of the conjugate Beta prior distribution for group $j$ are $p^E_j$ and $p^E_j(1-p^E_j)/(r+1)$, respectively.
-The resultant conditional posterior distribution of random effect $j$  is
+The resultant conditional posterior distribution of random effect $p_j$  is
 \begin{equation} \label{betapost}
-p_{j}\vert  \boldsymbol{\beta}, r, \boldsymbol{y} \stackrel{indep.}{\sim}\textrm{Beta}(rp^E_j+n_{j}\bar{y}_{j},~r(1-p^E_j)+n_{j}(1-\bar{y}_{j})),
+p_{j}\vert  \boldsymbol{\beta}, r, \boldsymbol{y} \stackrel{\textrm{indep.}}{\sim}\textrm{Beta}(n_{j}\bar{y}_{j}+rp^E_j,~n_{j}(1-\bar{y}_{j})+r(1-p^E_j)),
 \end{equation}
@@
 \begin{equation}\label{betapost_mean_var}
-p_j^\ast\equiv E(p_j\vert \boldsymbol{\beta}, r, \boldsymbol{y} )=(1-B_{j})\bar{y}_{j} + B_{j}p^E_j~~\textrm{and}~~Var(p_j\vert  \boldsymbol{\beta}, r,  \boldsymbol{y})=\frac{p_j^\ast(1-p_j^\ast)}{r+n_j+1}.
-\end{equation}
-The conditional posterior mean is  a convex combination of the unbiased estimate $\bar{y}_{j} = y_j/n_j$ and the expected random effect  $p^E_j$ weighted by $B_j\equiv r / (r + n_j)$ like the Poisson model.
-If the conjugate prior distribution contains more information than the observed distribution does ($r>n_j$), then the resulting conditional posterior mean shrinks towards the expected random effect by more than 50\%.
-
+p_j^\ast\equiv \E(p_j\vert \boldsymbol{\beta}, r, \boldsymbol{y} )=(1-B_{j})\bar{y}_{j} + B_{j}p^E_j~~\textrm{and}~~\VAR(p_j\vert  \boldsymbol{\beta}, r,  \boldsymbol{y})=\frac{p_j^\ast(1-p_j^\ast)}{r+n_j+1}.
+\end{equation}
+The conditional posterior mean $p_j^\ast$ is  a convex combination of $\bar{y}_{j}$ and $p^E_j$ weighted by $B_j\equiv r / (r + n_j)$ like the Poisson model.
+If the conjugate prior distribution contains more information than the observed distribution does ($r>n_j$), then the resulting conditional posterior mean borrows more information from the conjugate Beta prior distribution.
+
+%where $m$ is the number of the regression coefficients to be estimated. 
 \subsection[Hyper-prior distributions]{Hyper-prior distribution}
-Hyper-prior distributions are the distributions assigned to the second-level parameters called hyper-parameters. With the goal of objectivity in mind, our choice for the hyper-prior distributions is
+Hyper-prior distributions are the distributions assigned to the second-level parameters called hyper-parameters. Our choice for the hyper-prior distributions is
 \begin{equation}\label{eq:hyper}
-\boldsymbol{\beta} \sim \textrm{Uniform on}~ \textbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
-\end{equation}
-
-where $m$ is the number of the regression coefficients to be estimated.
+\boldsymbol{\beta} \sim \textrm{Uniform on}~ \textbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)).
+\end{equation}
 The improper flat hyper-prior distribution on $\boldsymbol{\beta}$ is a common non-informative choice.
-In the Gaussian case, the flat hyper-prior distribution on the second-level variance $A$ produces good repeated sampling coverage properties of the Bayesian interval estimates for the random effects.
+In the Gaussian case, the flat hyper-prior distribution on the second-level variance $A$ is known to produce good repeated sampling coverage properties of the Bayesian interval estimates for the random effects \citep{tang2011, morris2012, kelly2014advances}.
 The resulting full posterior distribution of the random effects and hyper-parameters is proper if $k\ge m+3$ \citep{tang2011, kelly2014advances}.
@@
 In the other two cases, Poisson and Binomial, the flat prior distribution on $1/r$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with the Uniform($0, \infty$) for the Gaussian case.
-The resultant full posterior distribution of random effects and hyper-parameters for the Binomial case is data-dependent.
-Let's define an ``interior group'' as the group whose number of successes $y_j$ are neither 0 nor $n_j$, and $k_y$ as the number of interior groups among the entire $k$ groups.
-Then, the full posterior distribution of random effects and hyper-parameters is proper if and only if there are at least two interior groups in the data and the $k_y\times m$ covariate matrix of the interior groups is of full rank $m$ \citep{tak2016propriety}.
-
-The Poisson model with the hyper-prior distributions in Equation \ref{eq:hyper} provides posterior propriety if and only if there are at least two groups whose observed values $y_j$ are non-zero  and the expected random effect $\lambda^E$ is a completely known constant ($m=0$).
-If the expected random effect is unknown a priori,  then we recommend staying with the Binomial model with the same hyper-prior distributions because the Poisson model is actually an approximation to the Binomial model.
+The Poisson model with this hyper-prior distribution on $r$, i.e., $dr/r^2$,  provides posterior propriety if there are at least two groups whose observed values $y_j$ are non-zero  and the expected random effect, $\lambda^E$, is a completely known constant ($m=0$), see Appendix \ref{propriety_poisson} for its proof.
+If $\lambda^E$ is unknown,  we recommend using the Binomial model with the same hyper-prior distributions because the Poisson model is actually an approximation to the Binomial model when $n_j$ is large and $p_j$ is small.
+
+As for posterior propriety of the Binomial model, let's define an ``interior group'' as the group whose number of successes $y_j$ are neither 0 nor $n_j$, and $k_y$ as the number of interior groups among $k$ groups.
+The full posterior distribution of random effects and hyper-parameters is proper if and only if there are at least two interior groups in the data and the $k_y\times m$ covariate matrix of the interior groups is of full rank $m$ \citep{tak2016propriety}.
 
@@
 
-The likelihood function of hyper-parameters $A$ and $\boldsymbol{\beta}$ for the Gaussian  model is derived from the independent Normal marginal distributions of the observed data with random effects, $\mu_1, \mu_2, \ldots, \mu_k$, integrated; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
+The likelihood function of hyper-parameters, $A$ and $\boldsymbol{\beta}$, for the Gaussian  model is derived from the independent Normal distributions of the observed data with random effects integrated out; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
 \begin{equation}\label{marginal_normal}
-L_g(A, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k f(y_j\vert A, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k \frac{1}{\sqrt{2\pi (A+V_j)}}\exp\big(-\frac{(y_j-\mu^E_j)^2}{2(A+V_j)}\big),
+L(A, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k f(y_j\vert A, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k \frac{1}{\sqrt{2\pi (A+V_j)}}\exp\left(-\frac{(y_j-\mu^E_j)^2}{2(A+V_j)}\right),
 \end{equation}
 where $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$.
-The joint posterior density  function of hyper-parameters $f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Gaussian hierarchical model is proportional to their likelihood function in Equation \ref{marginal_normal} because we use flat improper hyper-prior density functions for $A$ and $\boldsymbol{\beta}$;
+The joint posterior density  function of hyper-parameters $f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Gaussian  model is proportional to their likelihood function in  \eqref{marginal_normal} because we use flat improper hyper-prior density functions for $A$ and $\boldsymbol{\beta}$;
 \begin{equation}\label{marginal_post_normal}
-f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L_g(A, \boldsymbol{\boldsymbol{\beta}})d\boldsymbol{\beta}dA.
-\end{equation}
-
-The likelihood function of hyper-parameters $r$ and $\boldsymbol{\beta}$ for the Binomial  model is derived from the independent Beta-Binomial marginal distributions of the observed data with random effects, $p_1, p_2, \ldots, p_k$, integrated out \citep{skellam1948}; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
+f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L(A, \boldsymbol{\boldsymbol{\beta}})dAd\boldsymbol{\beta}.
+\end{equation}
+
+The likelihood function of hyper-parameters $r$ and $\boldsymbol{\beta}$ for the Binomial  model is derived from the independent Beta-Binomial  distributions of the observed data with random effects integrated out \citep{skellam1948}; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
 \begin{equation}\label{marginal_binomial}
-L_b(r, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k f(y_j\vert r, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k\binom{n_j}{y_j}\frac{B(y_j+rp^E_j, ~n_j-y_j+r(1-p^E_j))}{B(rp^E_j, ~r(1-p^E_j))},
-\end{equation}
-where $p^E_j=\exp(\boldsymbol{x}^\top\boldsymbol{\beta})/(1+\exp(\boldsymbol{x}^\top\boldsymbol{\beta}))$ and the notation $B(a, b)~(\equiv\int_0^1 v^{a-1}(1-v)^{b-1}dv)$ indicates a beta function for positive constants $a$ and $b$.
-The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial  model is proportional to their likelihood function in Equation \ref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in Equation \ref{eq:hyper} as follows;
+L(r, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k f(y_j\vert r, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k\binom{n_j}{y_j}\frac{B(y_j+rp^E_j, ~n_j-y_j+r(1-p^E_j))}{B(rp^E_j, ~r(1-p^E_j))},
+\end{equation}
+where the notation $B(a, b)~(\equiv\int_0^1 v^{a-1}(1-v)^{b-1}dv)$ indicates a beta function for positive constants $a$ and $b$.
+The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial  model is proportional to their likelihood function in \eqref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in  \eqref{eq:hyper} as follows;
 \begin{equation}\label{marginal_post_binomial}
-f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L_b(r, \boldsymbol{\boldsymbol{\beta}})d\boldsymbol{\beta}dr/r^2.
-\end{equation}
-
-Similarly, the likelihood function of $r$ for the Poisson hierarchical model  comes from the independent Negative-Binomial marginal distributions of the observed data with the random effects, $\lambda_1, \lambda_2, \ldots, \lambda_k$, integrated out;
+f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L(r, \boldsymbol{\boldsymbol{\beta}})d\boldsymbol{\beta}dr/r^2.
+\end{equation}
+
+Similarly, the likelihood function of $r$ for the Poisson  model  comes from the independent Negative-Binomial marginal distributions of the observed data with the random effects integrated out;
 \begin{equation}\label{marginal_poisson}
-L_p(r)=\prod_{j=1}^k f(y_j\vert r)=\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E+y_j)}{\Gamma(r\lambda^E)(y_j!)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E},
+L(r)=\prod_{j=1}^k f(y_j\vert r)=\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E+y_j)}{\Gamma(r\lambda^E)(y_j!)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E},
 \end{equation}
 where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}\exp(x)dx$ for a positive constant $a$.
-The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in Equation \ref{marginal_poisson} times the hyper-prior density function of $r$, $dr/r^2$;
+The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in  \eqref{marginal_poisson} times the hyper-prior density function of $r$, i.e., $dr/r^2$;
 \begin{equation}\label{marginal_post_poisson}
-f(r \vert \boldsymbol{y})\propto L_p(r)dr/r^2.
+f(r \vert \boldsymbol{y})\propto L(r)dr/r^2.
 \end{equation}
@@
 \section[Estimation]{Estimation via the adjustment for density maximization}\label{sec3}
-
-In this section, we illustrate our estimation procedure equipped with the adjustment for density maximization (hereafter ADM) \citep{carl1988, morris1997, tang2011}, a way to  approximate a distribution of the parameter of interest by one of Pearson family distributions based on derivatives like the Delta method.
 %As for the ADM procedure for the Gaussian model, \cite{kelly2014advances} for the details about the ADM procedure of the Gaussian model adopted in  \pkg{Rgbp}.
 
-Overall, obtaining point and interval estimates of each random effect is our primary inferential interest.
-The approximate Bayesian tool assumes that the unconditional posterior distribution of each random effect, such as $\mu_j\vert\boldsymbol{y}$, $p_j\vert\boldsymbol{y}$, or $\lambda_j\vert\boldsymbol{y}$,  follows a skewed-Normal distribution for the Gaussian case,  a Beta distribution for the Binomial case, or a Gamma distribution for the Poisson case.
-We match the parameters of the assumed distribution to the estimated unconditional posterior moments of each random effect, $\hat{E}(\mu_j^c\vert\boldsymbol{y}$), $\hat{E}(p_j^c\vert\boldsymbol{y}$), or $\hat{E}(\lambda_j^c\vert\boldsymbol{y}$) for a non-negative constant $c$.
+%Overall, obtaining point and interval estimates of each random effect is our primary inferential interest.
+The approximate Bayesian tool assumes that the unconditional posterior distribution of each random effect, i.e., $\mu_j\vert\boldsymbol{y}$, $p_j\vert\boldsymbol{y}$, or $\lambda_j\vert\boldsymbol{y}$,  follows a skewed-Normal distribution for the Gaussian case,  a Beta distribution for the Binomial case, or a Gamma distribution for the Poisson case.
+We match the parameters of the assumed distribution to the estimated unconditional posterior moments of each random effect, $\hat{\E}(\mu_j^c\vert\boldsymbol{y}$), $\hat{\E}(p_j^c\vert\boldsymbol{y}$), or $\hat{\E}(\lambda_j^c\vert\boldsymbol{y}$) for a non-negative constant $c$.
 We use these assumed unconditional posterior distributions to make point and interval estimates of each random effect.
 
-Because the ADM procedure for the Gaussian model and its frequency property are well documented in \cite{kelly2014advances}, we describe  the ADM procedure mainly for the Binomial model.
+In this section, we illustrate our estimation procedure equipped with the adjustment for density maximization (ADM) \citep{carl1988, morris1997, tang2011}, a way to  approximate a distribution of the parameter of interest by one of Pearson family distributions based on derivatives.
+Because the ADM procedure for the Gaussian model adopted in \pkg{Rgbp} is well documented in \cite{kelly2014advances}, we describe  the ADM procedure  based mainly on the Poisson and Binomial model.
 
@@
 
-Estimating the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$ (or $B_j\equiv V_j/(V_j+A)$ for the Gaussian model) and the conditional posterior moments of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ ($\mu^E_1, \mu^E_2, \ldots, \mu^E_k$ for the Gaussian model or $\lambda^E$ for the Poisson model), is the main estimation problem for the  models that \code{gbp} assumes.
-This is because we use these moment estimates to estimate the unconditional posterior moments of the random effects, $E(\mu_j^c\vert\boldsymbol{y}$), $E(p_j^c\vert\boldsymbol{y}$), or $E(\lambda_j^c\vert\boldsymbol{y}$) for a non-negative constant $c$.
-Taking the Binomial model as an example, with the assumption that hyper-parameters $r$ and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ are
-\begin{eqnarray}
-E(p_{j}\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})E(p^E_{j}\vert  \boldsymbol{y})\label{postmean} \\
-~~~~~~Var(p_{j}\vert \boldsymbol{y}) &=&  E(Var(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+Var(E(p_{j}\vert r, \boldsymbol{\beta},\boldsymbol{y})\vert \boldsymbol{y})\label{postvar}\\
-&=& E\big(p^{\ast}_{j}(1-p^{\ast}_{j})/ (r+n_{j}+1)\vert  \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big) \\
-&\approx&E\big(p^{\ast}_{j}(1-p^{\ast}_{j})(1-\textrm{B}_{j})/n_{i}\vert \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big)\\
-&=&h_b(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}), E(B^3_j\vert\boldsymbol{y}),  E(p^E_{j}\vert\boldsymbol{y}), E((p^E_{j})^2\vert\boldsymbol{y})).\label{approximate_var}
-\end{eqnarray}
-Note that the unconditional posterior mean and approximate variance of random effect $j$ in Equation \ref{postmean}  and \ref{approximate_var}  are functions of the unconditional posterior moments of shrinkage factors and expected random effects.
-We specify the function $h_b$  in Appendix \ref{apppostvar}.
-
-We assume that hyper-parameters $r$ ($A$ for the Gaussian model) and  $\boldsymbol{\beta}$ are independent a posteriori for the Binomial model.
-This is because in the limit of $k$ going to infinity  they are asymptotically Normally distributed, and \cite{morris1997}  empirically showed that their covariance from the observed information matrix of the Poisson model, though with a different parametrization, was close to 0 in a small sample setting.
-%For the Gaussian model we do not assume the posterior independence between $A$ and $\boldsymbol{\beta}$ because the conditional posterior variance of the random effect is a constant function of the conditional posterior mean, which is much simpler than that of the Binomial model.
-
-The unconditional posterior mean and variance of random effect $j$ of the Gaussian model are
-\begin{eqnarray}
-E(\mu_j\vert \boldsymbol{y}) &=&E(E(\mu_{j}\vert A, \boldsymbol{\beta}, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))y_j + E(B_j\vert  \boldsymbol{y})E(\mu^E_j\vert  \boldsymbol{y})\label{postmean_normal} \\
-Var(\mu_{j}\vert \boldsymbol{y}) &=&  E(Var(\mu_{j}\vert A,  \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+Var(E(\mu_{j}\vert A, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_normal}\\
-&=&  (1-V_j)E(B_j\vert  \boldsymbol{y})+Var\big(\textrm{B}_{j}(y_{j}-\mu^E_{j})\vert \boldsymbol{y}\big) \\
-&=&h_g(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}),  E(\mu^E_j\vert\boldsymbol{y}), E((\mu^E_j)^2\vert\boldsymbol{y})).\label{approximate_var_normal}
-\end{eqnarray}
-The unconditional posterior mean and variance of random effect $j$ under the Gaussian model are also functions of the unconditional posterior moments of the shrinkage factors and expected random effects.
-We specify the function $h_g$ in Appendix \ref{apppostvar_normal}.
-
-For the Poisson model, the unconditional posterior mean and variance of random effect $j$ are
-\begin{eqnarray}
-E(\lambda_j\vert \boldsymbol{y}) &=&E(E(\lambda_{j}\vert r, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})\lambda^E\label{postmean_poisson} \\
-Var(\lambda_{j}\vert \boldsymbol{y}) &=&  E(Var(\lambda_{j}\vert r,  \boldsymbol{y})\vert \boldsymbol{y})+Var(E(\lambda_{j}\vert r, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_poisson}\\
-&=& E\big(\lambda^{\ast}_{j}/ (r+n_{j})\vert  \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-\lambda^E_{j})\vert \boldsymbol{y}\big) \\
-&=&h_p(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}) ).\label{approximate_var_poisson}
-\end{eqnarray}
-The unconditional posterior mean and variance of random effect $j$ under the Poisson model are  functions of the unconditional posterior moments of the shrinkage factors.
-We specify the function $h_p$ in Equation \ref{approximate_var_poisson} in Appendix \ref{apppostvar_poisson}.
-%conditional posterior means of  random effect $j$ in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are a linear function of the shrinkage factor $B_{j}$ and the conditional posterior variances in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are linear (Gaussian), quadratic (Poisson), and  approximately cubic (Binomial) functions of $B_{j}$, considering $r+n_j=n_j/(1-B_j)$.
-Thus, the unconditional posterior mean and variance of the random effect are the functions of the unconditional posterior moments of the shrinkage factors.
-
-Next, we estimate the unconditional posterior moments of the shrinkage factors after approximating their unconditional posterior distributions by Beta distributions via the ADM. 
-%Next, we estimate the unconditional posterior moments of the shrinkage factors and expected random effects after approximating their unconditional posterior distributions by Beta distributions via the ADM.
-
-\subsubsection{Unconditional posterior moments of shrinkage factors}  It is noted that  the shrinkage factors ($B_1, \ldots B_k$) are a function of $r$, i.e., $B_{j}= r/(r+n_{j})=B_{j}(r)$ (or a function of $A$ for the Gaussian model).
-One way to approximate the distribution of $B_{j}$ is to find the maximum likelihood estimate of $r$, $\hat{r}_{MLE}$, with its Hessian value and to use a Delta method for an asymptotic Normal distribution of $B_{j}(\hat{r}_{MLE})$.
+Estimating the unconditional posterior moments of the shrinkage factors and the expected random effects is crucial because we use their estimated moments to estimate the unconditional posterior moments of the random effects in the end.
+
+\subsubsection{Unconditional posterior moments of shrinkage factors}  It is noted that  the shrinkage factors  are a function of $r$, i.e., $B_{j}= B_{j}(r)=r/(r+n_{j})$ (or a function of $A$ for the Gaussian model).
+One way to approximate the distribution of $B_{j}$ is to find the maximum likelihood estimate of $r$, $\hat{r}_{MLE}$, with its Hessian value and to use a Delta method for an asymptotic Normal distribution of $\hat{B}_{j}(\hat{r}_{MLE})$.
 This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $B_{j}$ lies on the unit interval between 0 and 1, and hence in small sample sizes the Delta method can result in point estimates lying on the boundary of the parameter space, from which the restricted MLE procedure sometimes suffers \citep{tang2011, kelly2014advances}.
@@
 
-The ADM procedure specified in \cite{tang2011} assumes that the unconditional posterior distribution of a shrinkage factor follows a Beta distribution as
+The ADM procedure specified in \cite{tang2011} assumes that the unconditional posterior distribution of a shrinkage factor follows a Beta distribution; for $j=1, 2, \ldots, k$,
 \begin{equation}\label{admshrinkage}
-B_j\vert\boldsymbol{y}\sim Beta(a_{1j}, a_{0j}), ~\textrm{for}~j=1, 2, \ldots, k,
-\end{equation}
-and the ADM estimates the two parameters of the Beta distribution, i.e., $a_{1j}$ and $a_{0j}$.
+B_j\vert\boldsymbol{y}\sim \textrm{Beta}(a_{1j},~ a_{0j}).
+\end{equation}
+%and the ADM estimates the two parameters of this Beta distribution, i.e., $a_{1j}$ and $a_{0j}$.
 %The estimated Beta distribution with the estimates $\hat{a}_{1j}$ and $\hat{a}_{0j}$ will be used to approximate the posterior moments of the shrinkage factors. 
@@
 Note that the mean of Beta distribution $a_{1j}/(a_{1j}+a_{0j})$ is not the same as its mode $(a_{j1}-1)/(a_{j1}+a_{j0}-2)$.
-The ADM works on an adjusted posterior distribution $A(B_j\vert \boldsymbol{y})dB_j\propto B_j(1-B_j)f(B_j\vert \boldsymbol{y})dB_j$ so that its mode is the same as the mean of the original Beta distribution.
+The ADM works on an adjusted posterior distribution $f^A(B_j\vert \boldsymbol{y})dB_j\propto B_j(1-B_j)f(B_j\vert \boldsymbol{y})dB_j$ so that the mode of $f^A(B_j\vert \boldsymbol{y})$ is the same as the mean of the original Beta distribution.
 The assumed posterior mean and variance of the shrinkage factor are
-\begin{eqnarray}
-E(B_j\vert\boldsymbol{y})&=&\frac{a_{1j}}{a_{1j}+a_{0j}}=\argmax_{B_j}~ A(B_j\vert \boldsymbol{y})\equiv B^\ast_j,\label{admmean}\\
-Var(B_j\vert\boldsymbol{y})&=&\frac{B^\ast_j(1-B^\ast_j)}{a_{1j}+a_{0j}+1}=\frac{B^\ast_j(1-B^\ast_j)}{B^\ast_j(1-B^\ast_j)[-\frac{d^2}{dB^2_j}\log(A(B_j\vert \boldsymbol{y}))\vert_{B_j=B^\ast_j}] +1}.\label{admvar}
-\end{eqnarray}
-
-The ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via the Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \citep[see]{berger1999integrated} for the integrated likelihood in detail.
-For the Gaussian model, the marginal likelihood function of $A$ is available in a closed form with $\boldsymbol{\beta}$ integrated out, see  \cite{tang2011}.
-
-Considering that Equation \ref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-\log(r)$ (or $\alpha=\log(A)$ for the Gaussian model), because the distribution of $\alpha$ is more symmetric than that of $r$ and $\alpha$ is defined on a real line without any boundary issues.
-Since $A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto \exp(\alpha) L(\alpha)$, the estimated posterior mean in Equation \ref{admmean} is
+\begin{align}
+\E(B_j\vert\boldsymbol{y})&=\frac{a_{1j}}{a_{1j}+a_{0j}}=\argmax_{B_j}~ f^A(B_j\vert \boldsymbol{y})\equiv B^\ast_j,\label{admmean}\\
+\VAR(B_j\vert\boldsymbol{y})&=\frac{B^\ast_j(1-B^\ast_j)}{a_{1j}+a_{0j}+1}=\frac{B^\ast_j(1-B^\ast_j)}{B^\ast_j(1-B^\ast_j)[-\frac{d^2}{dB^2_j}\log(A(B_j\vert \boldsymbol{y}))\vert_{B_j=B^\ast_j}] +1}.\label{admvar}
+\end{align}
+
+The ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood, $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$, for the Binomial model is obtained via the Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in  \eqref{marginal_poisson}.
+%For the Gaussian model, the marginal likelihood function of $A$ is available in a closed form with $\boldsymbol{\beta}$ integrated out  \citep{tang2011, kelly2014advances}.
+%; see \cite{berger1999integrated} for the integrated likelihood in detail
+
+Considering that  \eqref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-\log(r)$ (or $\alpha=\log(A)$ for the Gaussian model), because the distribution of $\alpha$ is more symmetric than that of $r$, and $\alpha$ is defined on a real line without any boundary issues.
+Because $f^A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto \exp(\alpha) L(\alpha)d\alpha$ \citep{tang2011}, the  posterior mean in  \eqref{admmean} is estimated by
 \begin{equation}\label{meaninvariance}
@@
 
-in which $\hat{\alpha}$ is the mode of $f(\alpha\vert\boldsymbol{y})$, \emph{i.e.}, $\argmax_{\alpha}\{\alpha+\log(L(\alpha))\}$ .
+where $\hat{\alpha}$ is the mode of $f(\alpha\vert\boldsymbol{y})$, \emph{i.e.}, $\argmax_{\alpha}\{\alpha+\log(L(\alpha))\}$ .
 %Next, a variable transformation gives us .
 
-We need  invariance information introduced in \cite{tang2011} to estimate the variance in Equation \ref{admvar}, which is defined as 
+We need  invariance information introduced in \cite{tang2011} to estimate the variance in  \eqref{admvar}, which is defined as 
 \begin{eqnarray}
-\textrm{inv.info} &\equiv& -\frac{d^2 \log(A(B_j\vert \boldsymbol{y}))}{d[logit(B_j)]^2}\bigg\vert_{B_j=\hat{B}^\ast_j}=-\frac{d^2 \log(A(B_j(r)\vert \boldsymbol{y}))}{d[\log(r)]^2}\bigg\vert_{r=\hat{r}}\label{invariance}\\
-&=& -\frac{d^2 \log(A(B_j(r(\alpha))\vert \boldsymbol{y}))}{d\alpha^2}\bigg\vert_{\alpha=\hat{\alpha}}\nonumber
+I_\textrm{inv} &\equiv& -\frac{d^2 \log(f^A(B_j\vert \boldsymbol{y}))}{d[\textrm{logit}(B_j)]^2}\bigg\vert_{B_j=\hat{B}^\ast_j}=-\frac{d^2 \log(f^A(B_j(r)\vert \boldsymbol{y}))}{d[\log(r)]^2}\bigg\vert_{r=\hat{r}}\label{invariance}\\
+&=& -\frac{d^2 \log(f^A(B_j(r(\alpha))\vert \boldsymbol{y}))}{d\alpha^2}\bigg\vert_{\alpha=\hat{\alpha}}\nonumber
 \end{eqnarray}
@@
 Note that this invariance information is  the negative Hessian value of $\alpha+\log(L(\alpha))$ at the mode $\hat{\alpha}$.
-Using the invariance information, we  estimate the unconditional posterior variance of shrinkage factor in Equation \ref{admvar} as
+Using the invariance information, we  estimate the unconditional posterior variance of shrinkage factor in  \eqref{admvar} by
 \begin{equation}\label{varianceinvariance}
-\widehat{Var}(B_j\vert\boldsymbol{y})=\frac{\hat{B}^{\ast2}_j(1-\hat{B}^\ast_j)^2}{inv.info +\hat{B}^\ast_j(1-\hat{B}^\ast_j)}.
-\end{equation}
-
-After matching the estimated unconditional posterior mean and variance of shrinkage factor $j$ in Equation \ref{meaninvariance} and \ref{varianceinvariance} to the two parameters of the Beta distribution in Equation \ref{admshrinkage}, i.e., $a_{1j}$ and $a_{0j}$, we get their estimates as
+\widehat{\VAR}(B_j\vert\boldsymbol{y})=\frac{\hat{B}^{\ast2}_j(1-\hat{B}^\ast_j)^2}{I_\textrm{inv} +\hat{B}^\ast_j(1-\hat{B}^\ast_j)}.
+\end{equation}
+
+We obtain the estimates of $a_{1j}$ and $a_{0j}$, the two parameters of the Beta distribution in  \eqref{admshrinkage}, by matching them to the estimated unconditional posterior mean and variance of $B_j$ specified in  \eqref{meaninvariance} and \eqref{varianceinvariance};
+%After matching to the two parameters of the Beta distribution in Equation \ref{admshrinkage}, i.e., $a_{1j}$ and $a_{0j}$, we obtain the estimates of $a_{1j}$ and $a_{0j}$ as
 \begin{equation}\label{admpara}
-\hat{a}_{1j}=\frac{\textrm{inv.info}}{1-\hat{B}^\ast_j}~~\textrm{and}~~\hat{a}_{0j}=\frac{\textrm{inv.info}}{\hat{B}^\ast_j}.
-\end{equation}
-
-The moments of the Beta distribution are well defined as a function of $a_{1j}$ and $a_{0j}$; $E(B^c_j\vert\boldsymbol{y})=B(a_{1j} + c, a_{0j})/B(a_{1j}, a_{0j})$ for $c\ge0$. Their estimates are 
+\hat{a}_{1j}=\frac{I_\textrm{inv}}{1-\hat{B}^\ast_j}~~\textrm{and}~~\hat{a}_{0j}=\frac{I_\textrm{inv}}{\hat{B}^\ast_j}.
+\end{equation}
+
+The moments of the Beta distribution are well defined as a function of $a_{1j}$ and $a_{0j}$, i.e.,  $\E(B^c_j\vert\boldsymbol{y})=B(a_{1j} + c, a_{0j})/B(a_{1j}, a_{0j})$ for $c\ge0$.
+Their estimates are
 \begin{equation}\label{shrinkagemoments}
-\widehat{E}(B^c_j\vert\boldsymbol{y})= \frac{B(\hat{a}_{1j} + c, \hat{a}_{0j})}{B(\hat{a}_{1j}, \hat{a}_{0j})}.
-\end{equation}
-
-The distributional approximation of the ADM gets better if the true posterior distribution of the shrinkage factor is closer to the Beta distribution \citep{morris1997, tang2011, morris2012}.
+\widehat{\E}(B^c_j\vert\boldsymbol{y})= \frac{B(\hat{a}_{1j} + c,~ \hat{a}_{0j})}{B(\hat{a}_{1j},~ \hat{a}_{0j})}.
+\end{equation}
+
+The distributional approximation of the ADM gets better if the true posterior distribution of the shrinkage factor is closer to the Beta distribution \citep{carl1988, morris1997, tang2011, morris2012}.
 
 \subsubsection{Unconditional posterior moments of expected random effects}
-The Gaussian and Binomial models need to estimate the unconditional posterior moments of expected random effects.
-We estimate them using their relationship to the conditional posterior moments.
+We estimate the unconditional posterior moments of expected random effects using their relationship to the conditional posterior moments.
 For a non-negative constant $c$, the unconditional posterior moments are
 \begin{equation}
-E((\mu^E_j)^c\vert\boldsymbol{y})=E(E((\mu^E_j)^c\vert A, \boldsymbol{y})\vert\boldsymbol{y})~~\textrm{and}~~E((p^E_j)^c\vert\boldsymbol{y})=E(E((p^E_j)^c\vert r, \boldsymbol{y})\vert\boldsymbol{y}).
-\end{equation}
-We use the ADM to estimate the conditional posterior moments inside with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in as the estimates of the unconditional moments.
+\E((p^E_j)^c\vert\boldsymbol{y})=\E(\E((p^E_j)^c\vert r, \boldsymbol{y})\vert\boldsymbol{y}).
+\end{equation}
+Instead of averaging over $r$, we estimate the unconditional posterior moments by the conditional posterior moments with $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.
 %We estimate the unconditional posterior moments by the estimated conditional posterior moments that we obtain from the conditional posterior distribution of $\mu^E_j\vert A, \boldsymbol{y}$ or that of $p^E_j\vert r, \boldsymbol{y}$ with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.
 
-To be specific, the ADM for the Binomial model assumes that the conditional posterior distribution of each expected random effect given $\hat{\alpha}$ follows a Beta distribution  because the moment calculation of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involves an intractable integration.
-For example, the first conditional posterior moment is
+However, calculating conditional posterior moments of each expected random effect involves an intractable integration. For example, the first conditional posterior moment of $p^E_j$ is
 \begin{equation}\label{priormoment1}
-E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\boldsymbol{\beta}.
-\end{equation}
-%We estimate the assumed Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$.
-We estimate the conditional posterior moments of the expected random effects and treat them as their estimated unconditional posterior moments obtained by the (Laplace) approximate marginal likelihood function of $\boldsymbol{\beta}$.
-% The conditional and unconditional posterior moment estimates are almost identical due to the small covariance between $r$ and $\boldsymbol{\beta}$ in the observed information matrix.
-In addition, calculating the conditional posterior moments is computationally less burdensome.
-%Considering that the expected random effects are a function of logistic regression coefficients $\boldsymbol{\beta}$, we can use the Delta method for the asymptotic Normal distribution of $p^E_{j}(\hat{\boldsymbol{\beta}}_{MLE})$.
-However, the Normal approximation goes through the same support and boundary issues as the shrinkage factors do.
-Instead, the ADM assumes that the conditional posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ follows a Beta distribution, using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$.
-
-Thus, we assume the conditional posterior distribution of expected random effect $j$ is a Beta distribution as follows;
+\E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\boldsymbol{\beta},
+\end{equation}
+which is not an easy integration. Thus, we use another ADM, assuming the conditional posterior distribution of each expected random effect is a Beta distribution as follows;
 \begin{equation}\label{admpriormean}
-p^E_{j}\vert\hat{\alpha}, \boldsymbol{y}=\frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}\bigg\vert\hat{\alpha}, \boldsymbol{y}\sim \textrm{Beta}(b_{1j}, b_{0j})\sim \frac{G(b_{1j})}{G(b_{1j})+G(b_{0j})},
-\end{equation}
-
-where $G(b_{1j})$ is a random variable following a Gamma$(b_{1j}, 1)$ distribution with a unit scale and independently $G(b_{0j})$ has a Gamma($b_{0j}, 1)$ distribution.
-Note that the representation in Equation \ref{admpriormean} is equivalent to saying $\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables.
+p^E_{j}\vert\hat{\alpha}, \boldsymbol{y}=\frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}\bigg\vert\hat{\alpha}, \boldsymbol{y}\sim \textrm{Beta}(b_{1j},~ b_{0j})\sim \frac{G(b_{1j})}{G(b_{1j})+G(b_{0j})},
+\end{equation}
+
+where $G(b_{1j})$ is a random variable following a Gamma$(b_{1j}, 1)$ distribution and independently $G(b_{0j})$ has a Gamma($b_{0j}, 1)$ distribution.
+Note that the representation in  \eqref{admpriormean} is equivalent to saying $\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables.
 Its mean and variance are
-\begin{eqnarray}
-E(\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y})&=&E\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{b_{1j}}{b_{0j}-1}\equiv\eta_j,\label{priormean1}\\
-~~~~~Var(\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y})&=&Var\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{\eta_j(1+\eta_j)}{b_{0j}-2}.\label{priorvariance1}
-\end{eqnarray}
-
-In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$ follows Normal$(\hat{\beta}, \hat{\Sigma})$ distribution, where $\hat{\boldsymbol{\beta}}$ is the mode of $p(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode.
+\begin{align}
+\E(\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y})&=E\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{b_{1j}}{b_{0j}-1}\equiv\eta_j,\label{priormean1}\\
+~~~~~\VAR(\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y})&=\VAR\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{\eta_j(1+\eta_j)}{b_{0j}-2}.\label{priorvariance1}
+\end{align}
+
+In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$ follows a Normal distribution with mean $\hat{\boldsymbol{\beta}}$ and variance-covariance matrix $\hat{\Sigma}$, where $\hat{\boldsymbol{\beta}}$ is the mode of $f(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is an inversed negative Hessian matrix at the mode.
 Thus, the posterior distribution of $x_j^\top\boldsymbol{\beta}$ is also Normal with mean $x_j^\top\hat{\boldsymbol{\beta}}$ and variance $x_j^\top\hat{\Sigma} x_j$.
 
-Using the property of the log-Normal distribution for $\exp(x_j^\top\boldsymbol{\beta})$, we estimate the posterior mean and variance in Equation \ref{priormean1} and \ref{priorvariance1} as
-\begin{eqnarray}
-\hat{\eta}_j&=&\exp(x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2),\label{priormean2}\\
-~~~~~\widehat{Var}(\exp(x_j^\top\boldsymbol{\beta})\vert\boldsymbol{y})&=&\hat{\eta}^2_j\big(\exp(x_j^{T}\hat{\Sigma} x_j)-1\big).\label{priorvariance2}
-\end{eqnarray}
-
-By matching the  mean and variance in Equation \ref{priormean2} and \ref{priorvariance2} to $b_{1j}$ and $b_{0j}$ in Equation \ref{priormean1} and \ref{priorvariance1}, we estimate the values of $b_{1j}$ and $b_{0j}$ as follows;
+Using the property of the log-Normal distribution for $\exp(x_j^\top\boldsymbol{\beta})$, we estimate the posterior mean and variance in  \eqref{priormean1} and \eqref{priorvariance1} as
+\begin{align}
+\hat{\eta}_j&=\exp(x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2),\label{priormean2}\\
+\widehat{\VAR}(\exp(x_j^\top\boldsymbol{\beta})\vert\boldsymbol{y})&=\hat{\eta}^2_j\big(\exp(x_j^{T}\hat{\Sigma} x_j)-1\big).\label{priorvariance2}
+\end{align}
+
+We estimate the values of $b_{1j}$ and $b_{0j}$  by matching them to the estimated  mean and variance in  \eqref{priormean2} and \eqref{priorvariance2};
 \begin{equation}\label{priormeanpara}
-\hat{b}_{1j}=\hat{\eta}_j+\frac{\hat{\eta}_j + 1}{\exp(x_j^{T}\hat{\Sigma} x_j)-1}~~\textrm{and}~~\hat{b}_{0j}=\frac{\hat{\eta}_j + 1}{\hat{\eta}_j(\exp(x_j^{T}\hat{\Sigma} x_j)-1)}+2.
-\end{equation}
-
-Finally we estimate the unconditional posterior moments of the expected random effects, $E((p^E_{j})^c\vert\boldsymbol{y})$, by $\hat{E}((p^E_{j})^c\vert\hat{\alpha}, \boldsymbol{y})=B(\hat{b}_{1j} + c, \hat{b}_{0j})/B(\hat{b}_{1j}, \hat{b}_{0j})$ for $c\ge0$.
+\hat{b}_{1j}=\hat{\eta}_j(\hat{b}_{0j}-1)~~\textrm{and}~~\hat{b}_{0j}=\frac{1+\hat{\eta}_j}{\hat{\eta}_j(\exp(x_j^{T}\hat{\Sigma} x_j)-1)}+2.
+\end{equation}
+
+Finally, we estimate the unconditional posterior moments of the expected random effects, $\E((p^E_{j})^c\vert\boldsymbol{y})$, by $\hat{\E}((p^E_{j})^c\vert\hat{\alpha}, \boldsymbol{y})=B(\hat{b}_{1j} + c, \hat{b}_{0j})/B(\hat{b}_{1j}, \hat{b}_{0j})$ for $c\ge0$.
 %\begin{equation}\label{priormeanmoments}
-%\widehat{E}((p^E_{j})^c\vert\boldsymbol{y})= \frac{B(\hat{b}_{1j} + c, \hat{b}_{0j})}{B(\hat{b}_{1j}, \hat{b}_{0j})}.
+%\widehat{\E}((p^E_{j})^c\vert\boldsymbol{y})= \frac{B(\hat{b}_{1j} + c, \hat{b}_{0j})}{B(\hat{b}_{1j}, \hat{b}_{0j})}.
 %\end{equation}
@@
 
-For the Gaussian model \citep{tang2011}, the distribution of $\boldsymbol{\beta}$ given $\hat{A}$ and $\boldsymbol{y}$ is Normal whose mean and variance matrix are
+For the Gaussian model \citep{tang2011}, the conditional posterior distribution of $\boldsymbol{\beta}$ given $\hat{A}$ and $\boldsymbol{y}$ is Normal whose mean and variance-covariance matrix are
 \begin{equation}
-(X^\top D^{-1}_{V+\hat{A}} X)^{-1}X^\top D^{-1}_{V+\hat{A}}\boldsymbol{y}~~ \textrm{and}~~ (X^\top D^{-1}_{V+\hat{A}} X)^{-1}, ~\textrm{respectively},
-\end{equation}
-where $X\equiv (\boldsymbol{x}_1, \boldsymbol{x}_2, \ldots, \boldsymbol{x}_k)^\top$ is a $k \times m$ covariate matrix and $D_{V+\hat{A}}$ is a $k \times k$ diagonal matrix with the $j$-th diagonal element equal to $V_j+\hat{A}$.
-Because $\boldsymbol{x}^\top\boldsymbol{\beta}$ given $\hat{A}$ and $\boldsymbol{y}$ is also Normally distributed, we obtain the conditional posterior moments of $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$ with ease and use them to estimate their unconditional posterior moments.
+(X^\top D^{-1}_{V+\hat{A}} X)^{-1}X^\top D^{-1}_{V+\hat{A}}\boldsymbol{y}~~ \textrm{and}~~ (X^\top D^{-1}_{V+\hat{A}} X)^{-1},
+\end{equation}
+respectively, where $X\equiv (\boldsymbol{x}_1, \boldsymbol{x}_2, \ldots, \boldsymbol{x}_k)^\top$ is a $k \times m$ covariate matrix and $D_{V+\hat{A}}$ is a $k \times k$ diagonal matrix with the $j$-th diagonal element equal to $V_j+\hat{A}$.
+Because $\boldsymbol{x}^\top\boldsymbol{\beta}$ given $\hat{A}$ and $\boldsymbol{y}$ is also Normally distributed, we easily obtain the conditional posterior moments of $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$ and use them to estimate unconditional posterior moments of $\mu^E_j$.
 
@@
 It is intractable to derive analytically the unconditional posterior distribution of each random effect  for the three models, which motivates us to assume again that each random effect has a skewed Normal distribution \citep{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
-\begin{eqnarray}
-\mu_j\vert\boldsymbol{y} &\sim& \textrm{skewed-Normal}(\phi, \omega, \delta),\label{skewnormal}\\
-p_j\vert \boldsymbol{y} &\sim& \textrm{Beta}(t_{1j}, t_{0j}),\label{betapost}\\
-\lambda_j\vert \boldsymbol{y} &\sim& \textrm{Gamma}(s_{1j}, s_{0j}).\label{gammapost}
-\end{eqnarray}
-
-\cite{kelly2014advances}  matches the  three estimated unconditional posterior  moments of the random effects to the three parameters $(\phi, \omega, \delta$) of the skewed-Normal distribution in Equation \ref{skewnormal}, i.e., location parameter $\phi$, scale parameter $\omega$, and a skewness parameter $\delta$.
-For this matching, \cite{kelly2014advances} uses $E(\mu_j\vert \boldsymbol{y}) =\phi+\omega\delta\sqrt{2/\pi}$, Var$(\mu_j\vert \boldsymbol{y})=\omega^2(1-2\delta^2/\pi)$, and Skewness$(\mu_j\vert \boldsymbol{y})=(4-\pi)\delta^3/[2(\pi/2-\delta^2)^{3/2}]$ derived in \cite{azzalini1985class}.
-\cite{kelly2014advances} also shows that the skewed-Normal approximation improves a Normal approximation \citep{tang2011, morris2012} in terms of the frequency properties   of random effects.
-
-We know that the unconditional posterior mean and variance of each random effect for the Binomial model specified in Equation \ref{postmean} and \ref{approximate_var} are functions of the unconditional posterior moments of shrinkage factors and expected random effect.
-By plugging-in the estimated unconditional posterior moments of shrinkage factors and those of expected random effect, we obtain the estimates of the unconditional posterior mean and variance of each random effect, denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
-The estimates of two parameters $t_{1j}$ and $t_{0j}$ in Equation \ref{betapost} come as follows;
+\begin{align}
+\mu_j\vert\boldsymbol{y} &\sim \textrm{skewed-Normal}(\phi,~ \omega,~ \delta),\label{skewnormal}\\
+p_j\vert \boldsymbol{y} &\sim \textrm{Beta}(t_{1j},~ t_{0j}),\label{betapost}\\
+\lambda_j\vert \boldsymbol{y} &\sim \textrm{Gamma}(s_{1j},~ s_{0j}),\label{gammapost}
+\end{align}
+where $(\phi, \omega, \delta)$ of the skewed-Normal distribution  are location,  scale, and skewness parameters, respectively.
+
+\cite{kelly2014advances} uses  the results derived in \cite{azzalini1985class}, i.e., $\E(\mu_j\vert \boldsymbol{y}) =\phi+\omega\delta\sqrt{2/\pi}$, Var$(\mu_j\vert \boldsymbol{y})=\omega^2(1-2\delta^2/\pi)$, and Skewness$(\mu_j\vert \boldsymbol{y})=(4-\pi)\delta^3/[2(\pi/2-\delta^2)^{3/2}]$, and estimates three parameters of the skewed-Normal distribution using  three approximately estimated unconditional posterior  moments of each random effect; see \cite{kelly2014advances} for details.
+\cite{kelly2014advances} also shows that the skewed-Normal approximation improves a Normal approximation ($\mu_j\vert\boldsymbol{y}\sim \textrm{Normal}$) used in  \cite{tang2011, morris2012} in terms of the repeated sampling coverage properties of random effects.
+
+%; in the limit of $k$ going to infinity, they are Normally distributed, and \cite{morris1997}  empirically showed that their covariance derived from matrix had the observed information matrix of the Poisson model, though with a different parametrization, was close to 0 in a small sample setting.
+%With the assumption that hyper-parameters $A$ and $\boldsymbol{\beta}$ are independent \emph{a posteriori}, 
+To estimate the unconditional posterior moments of random effects in the Binomial model, we assume that hyper-parameters $r$  and  $\boldsymbol{\beta}$ are independent \emph{a posteriori}.
+With this assumption,  the unconditional posterior mean and variance of random effect $p_j$ are
+\begin{align}
+\E(p_{j}\vert \boldsymbol{y}) &=\E(\E(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert\boldsymbol{y})=(1-\E(B_j\vert\boldsymbol{y}))\bar{y}_j + \E(B_j\vert  \boldsymbol{y})\E(p^E_{j}\vert  \boldsymbol{y}),\label{postmean_binom} \\
+~~~~~~\VAR(p_{j}\vert \boldsymbol{y}) &=  \E(\VAR(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+\VAR(\E(p_{j}\vert r, \boldsymbol{\beta},\boldsymbol{y})\vert \boldsymbol{y})\label{postvar}\\
+&= E\big(p^{\ast}_{j}(1-p^{\ast}_{j})/ (r+n_{j}+1)\vert  \boldsymbol{y}\big)+\VAR\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big) \\
+&\approx E\big(p^{\ast}_{j}(1-p^{\ast}_{j})(1-\textrm{B}_{j})/n_{i}\vert \boldsymbol{y}\big)+\VAR\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big)\\
+&=h(\E(B_j\vert\boldsymbol{y}), \E(B^2_j\vert\boldsymbol{y}), \E(B^3_j\vert\boldsymbol{y}),  \E(p^E_{j}\vert\boldsymbol{y}), \E((p^E_{j})^2\vert\boldsymbol{y})),\label{approximate_var}
+\end{align}
+where the function $h$ in the last equation is specified in Appendix \ref{apppostvar}.
+By plugging-in the estimated unconditional posterior moments of shrinkage factors and those of expected random effect into   \eqref{postmean_binom} and \eqref{approximate_var}, we obtain the estimates of the unconditional posterior mean and variance of each random effect, denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
+Finally, we obtain the estimates of two parameters $t_{1j}$ and $t_{0j}$ in  \eqref{betapost} as follows;
 \begin{equation}\label{posttrueprob}
@@
 
- For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimated unconditional posterior mean and variance in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}, respectively, with the estimated unconditional posterior moments of shrinkage factors plugged-in.
-The estimates of the two parameters $s_{1j}$ and $s_{0j}$ in Equation \ref{gammapost} are
+The unconditional posterior mean and variance of random effect $\lambda_j$ in the Poisson model are
+\begin{align}
+\E(\lambda_j\vert \boldsymbol{y}) &=\E(\E(\lambda_{j}\vert r, \boldsymbol{y})\vert\boldsymbol{y})=(1-\E(B_j\vert\boldsymbol{y}))\bar{y}_j + \E(B_j\vert  \boldsymbol{y})\lambda^E,\label{postmean_poisson} \\
+\VAR(\lambda_{j}\vert \boldsymbol{y}) &=  \E(\VAR(\lambda_{j}\vert r,  \boldsymbol{y})\vert \boldsymbol{y})+\VAR(\E(\lambda_{j}\vert r, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_poisson}\\
+&= E\big(\lambda^{\ast}_{j}/ (r+n_{j})\vert  \boldsymbol{y}\big)+\VAR\big(\textrm{B}_{j}(\bar{y}_{j}-\lambda^E_{j})\vert \boldsymbol{y}\big) \\
+&=\frac{1}{n_j}\left[\bar{y}_j\E\left((1-B_j)^2\vert \boldsymbol{y}\right)+\lambda^E\E\left((1-B_j)B_j\vert \boldsymbol{y}\right)\right]+(\bar{y}_{j}-\lambda^E_{j})^2\VAR\big(\textrm{B}_{j}\vert \boldsymbol{y}\big).\label{approximate_var_poisson}
+\end{align}
+Let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimated unconditional posterior mean and variance in  \eqref{postmean_poisson} and \eqref{approximate_var_poisson}, respectively, with the estimated unconditional posterior moments of shrinkage factors plugged-in.
+The estimates of the two parameters $s_{1j}$ and $s_{0j}$ in  \eqref{gammapost} are
 \begin{equation}\label{posttrueprob}
@@
 
-Finally, the approximate unconditional posterior distribution of random effect $j$ for the Gaussian model is
+Finally, the assumed unconditional posterior distribution of random effect for the Gaussian model is
 \begin{equation}\label{trueapprox_normal}
-\mu_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{skewed-Normal}(\hat{\phi}, \hat{\omega}, \hat{\delta}),
+\mu_j\vert \boldsymbol{y} \sim \textrm{skewed-Normal}(\hat{\phi}, \hat{\omega}, \hat{\delta}),
 \end{equation}
@@
 \begin{equation}\label{trueapprox_binomial}
-p_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{Beta}(\hat{t}_{1j}, \hat{t}_{0j}),
+p_j\vert \boldsymbol{y} \sim \textrm{Beta}(\hat{t}_{1j}, \hat{t}_{0j}),
 \end{equation}
@@
 \begin{equation}\label{trueapprox_poisson}
-\lambda_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{Gamma}(\hat{s}_{1j}, \hat{s}_{0j}).
-\end{equation}
-
-%The ADM approximation is accurate if the true distribution of $p_j$ is close to the the Beta distribution \citep{morris1997, tang2011, morris2012}.
-
-We use the  mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the estimated approximate posterior distribution, a skewed Normal distribution for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution  for the Poisson model, as the point and interval estimates of  random effects.
+\lambda_j\vert \boldsymbol{y} \sim \textrm{Gamma}(\hat{s}_{1j}, \hat{s}_{0j}).
+\end{equation}
+Our point and interval estimates of each random effect are the  mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the assumed unconditional posterior distribution in  \eqref{trueapprox_normal}, \ref{trueapprox_binomial}, or \ref{trueapprox_poisson} depending on the type of data.
 
@@
 %Using the posterior mean and variance estimates of $B_{j}$, \pkg{Rgbp} estimates the posterior mean and variance of the random effects given only the data ($\boldsymbol{y}$).
-Taking the Normal-Normal model as an example, it estimates $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$ by the following identities
+Taking the Normal-Normal model as an example, it estimates $E(\mu_{j}\vert \boldsymbol{y})$ and $\VAR(\mu_{j}\vert \boldsymbol{y})$ by the following identities
 %\begin{eqnarray}
 %E(\mu_{j}\vert \boldsymbol{y}) & = & E(E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y}), \\
-%Var(\mu_{j}\vert \boldsymbol{y}) & = & E(Var(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y})+Var(E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y}),
+%\VAR(\mu_{j}\vert \boldsymbol{y}) & = & E(\VAR(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y})+\VAR(E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)\vert \boldsymbol{y}),
 %\end{eqnarray}  
-%where both $E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)$ and $Var(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}).
-We then estimate $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$ by plugging-in the approximately estimated two posterior moments of shrinkage factors.
+%where both $E(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)$ and $\VAR(\mu_{j}\vert \boldsymbol{y}, \boldsymbol{\beta}, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}).
+We then estimate $E(\mu_{j}\vert \boldsymbol{y})$ and $\VAR(\mu_{j}\vert \boldsymbol{y})$ by plugging-in the approximately estimated two posterior moments of shrinkage factors.
 
 %\subsection[Approximation to posterior distribution by moment matching]{Approximation to Posterior Distribution via Matching Moments}
-%After estimating the two posterior moments, for example $E(\mu_{j}\vert \boldsymbol{y})$ and $Var(\mu_{j}\vert \boldsymbol{y})$, \code{gbp} approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
+%After estimating the two posterior moments, for example $E(\mu_{j}\vert \boldsymbol{y})$ and $\VAR(\mu_{j}\vert \boldsymbol{y})$, \code{gbp} approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments.
 For the Normal-Normal model we actually estimate the first three moments and approximate $\pi(\mu_{j}\vert \boldsymbol{y})$ with a skewed-Normal distribution \citep{sn2013}.
@@
 \section[Estimation]{The acceptance-rejection method for the Binomial model}\label{sec_accept}
-As for the Binomial model, the package \pkg{Rgbp} also provides a way to  independently draw exact posterior samples of random effects and hyper-parameters via the acceptance-rejection method.
-We continue working on a logarithmic scale of $r$, $\alpha=\log(1/r)=-\log(r)$.
-The joint posterior density function of $\alpha$ and $\boldsymbol{\beta}$ based on their joint hyper-prior density function in Equation \ref{eq:hyper} is
+As for the Binomial model, the package \pkg{Rgbp} also provides a way to draw posterior samples of random effects and hyper-parameters via the acceptance-rejection (A-R) method.
+We continue working on a logarithmic scale of $r$, i.e., $\alpha=\log(1/r)$.
+The joint posterior density function of $\alpha$ and $\boldsymbol{\beta}$ based on their joint hyper-prior density function in  \eqref{eq:hyper} is
 \begin{equation}
@@
 
-The Acceptance-Rejection (A-R) method \citep{everson2000inference, tang2002fitting} is useful when it is difficult to sample a parameter of interest $\theta$ directly from its target probability density $f(\theta)$, which is known up to a normalizing constant, but an easy-to-sample envelope function $g(\theta)$ is available.
+The A-R method \citep{everson2000inference, tang2002fitting} is useful when it is difficult to sample a parameter of interest $\theta$ directly from its target probability density $f(\theta)$, which is known up to a normalizing constant, but an easy-to-sample envelope function $g(\theta)$ is available.
 The A-R method samples $\theta$  from the envelope $g(\theta)$ and accepts it with a probability $\frac{f(\theta)}{Mg(\theta)}$, where $M$ is a constant making $f(\theta)/g(\theta)\le M$ for all $\theta$.
@@
 
-The goal of the A-R method  for the  Binomial model is to independently draw  posterior samples of hyper-parameters from $f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})$, using an easy-to-sample envelop function $g(\alpha, \boldsymbol{\beta})$ that has thicker tails than the target density function.
+The goal of the A-R method  for the  Binomial model is to  draw  posterior samples of hyper-parameters from $f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})$, using an easy-to-sample envelop function $g(\alpha, \boldsymbol{\beta})$ that has thicker tails than the target density function.
 
@@
 We consider the tail behavior of the conditional posterior density function $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ to come up with $g_1(\alpha)$; $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ behaves as $\exp(-\alpha(k-1))$ when $\alpha$ goes to $\infty$ and as $\exp(\alpha)$ when $\alpha$ goes to $-\infty$.
-It indicates that $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ is skewed to the left because the right tail touches the $x$-axis faster than the left tail does it as long as $k>1$.
+It indicates that $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ is skewed to the left because the right tail touches the $x$-axis faster than the left tail does as long as $k>1$.
 A skewed $t$-distribution  is a good candidate for $g_1(\alpha)$ because it behaves as a power law on both tails, leading to thicker tails than those of $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$.
@@
 It is too complicated to figure out the tail behaviors of $f(\boldsymbol{\beta} \vert \alpha,  \boldsymbol{y})$.
-However, since $f(\boldsymbol{\beta} \vert \alpha,  \boldsymbol{y})$ of the approximate Gaussian counterpart has a multivariate Gaussian density function \citep{tang2011, kelly2014advances}, we consider a multivariate $t$-distribution with 4  degrees of freedom as a good candidate for $g_2(\boldsymbol{\beta})$.
+However, because $f(\boldsymbol{\beta} \vert \alpha,  \boldsymbol{y})$ of the Gaussian hierarchical model has a multivariate Gaussian density function \citep{tang2011, kelly2014advances}, we consider a multivariate $t$-distribution with 4  degrees of freedom as a good candidate for $g_2(\boldsymbol{\beta})$.
 
@@
 \end{equation}
-The notation $t_{4}(\boldsymbol{\beta}\vert\boldsymbol{\mu}^\ast, S)$ in Equation \ref{g2approx} indicates a density function of a multivariate $t$-distribution at $\boldsymbol{\beta}$ with 4 degrees of freedom, a location vector $\boldsymbol{\mu}^\ast$, and a $m\times m$ scale matrix $S$ that leads to the variance-covariance matrix $2S$.
-
-We set the parameters of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$, i.e., $\mu$, $\sigma$, $a$, $b$, $\boldsymbol{\mu}^\ast$, and $S$, to make the product of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$ similar to the target joint posterior density $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$.
+The notation $t_{4}(\boldsymbol{\beta}\vert\boldsymbol{\mu}^\ast, S)$ in  \eqref{g2approx} indicates a density function of a multivariate $t$-distribution at $\boldsymbol{\beta}$ with 4 degrees of freedom, a location vector $\boldsymbol{\mu}^\ast$, and a $m\times m$ scale matrix $S$ that leads to the variance-covariance matrix $2S$.
+
+We determine the parameters of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$, i.e., $\mu$, $\sigma$, $a$, $b$, $\boldsymbol{\mu}^\ast$, and $S$, to make the product of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$ similar to the target joint posterior density $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$.
 First, we obtain the  mode of $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$ and the inverse of the  negative Hessian matrix at the modes, $-H^{-1}$.
@@
 Next, we set ($a,~ b$) to $(k,~ 2k)$ if $k<10$ (or otherwise $(\log(k),~ 2\log(k))$)   to maintain a left-skewness of $g_1(\alpha)$ and to keep  $a$ and $b$ small enough for thick tails.
-We match the mode of $g_1(\alpha)$ specified in Equation \ref{mode} to $\hat{\alpha}$ by fixing the location parameter $\mu$ at $\hat{\alpha}-(a-b)\sqrt{a+b}/\sqrt{(2a+1)(2b+1)}$.
-We set  the scale parameter $\sigma$ to $(-H^{-1}_{\hat{\alpha}})^{0.5}\psi$, where $\psi$ is a tuning parameter; $\psi=1.3$ is the default.
-When the A-R method produces extreme values of weights defined in Equation \ref{weight} below, we increase the value of $\psi$.
+We match the mode of $g_1(\alpha)$ specified in  \eqref{mode} to $\hat{\alpha}$ by setting the location parameter $\mu$ to $\hat{\alpha}-(a-b)\sqrt{a+b}/\sqrt{(2a+1)(2b+1)}$.
+We set  the scale parameter $\sigma$ to $(-H^{-1}_{\hat{\alpha}})^{0.5}\psi$, where $\psi$ is a tuning parameter with 1.3 as a default value\footnote{When the A-R method produces extreme weights defined in  \eqref{weight}, we increase the value of $\psi$.}.
 %To summarize, we use
@@
 
-For the  implementation of the acceptance-rejection method, we obtain four times more trial samples than the desired number of samples $N$ independently from $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$.
+For the  implementation of the acceptance-rejection method, we obtain four times more trial samples than the desired number of samples, denoted by $N$, independently from $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$.
 We calculate $4N$ weights, each of which is defined as
@@
 We accept each pair of $(\alpha^{(i)}, \boldsymbol{\beta}^{(i)})$ with a probability $w_i/M$ where $M$ is set to the maximum of all the $4N$ weights.
-The usual acceptance rates from  our data examples are around 25\%.
+The typical acceptance rates from  our data examples are around 27\%.
 In a case where we accept more than the desired number of samples $N$, we discard the redundant.
-If the number of accepted samples is smaller than $N$, then we sample additional pairs (6 times more than the shortage) and calculate a new maximum $M'$ from all the previous and new weights, accepting or rejecting the entire pairs again with new probabilities $w_i/M'$.
+If the number of accepted samples is smaller than $N$, then we additionally sample  6 times more pairs than the shortage and calculate a new maximum $M'$ from all the previous and new weights, accepting or rejecting the entire pairs again with new probabilities $w_i/M'$.
 
@@
 \end{equation}
-The integration can be done by sampling $(p_1, p_2, \ldots, p_k)$ from the independent Beta conditional posterior distributions $f(p_j\vert \boldsymbol{\beta}, r, \boldsymbol{y})$ in Equation \ref{betapost}  given $r~(=\exp(-\alpha))$ and $\boldsymbol{\beta}$ already sampled from $f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})$ via the A-R method.
+The integration can be done by sampling $(p_1, p_2, \ldots, p_k)$ from the independent Beta conditional posterior distributions, i.e., $f(p_j\vert \boldsymbol{\beta}, r, \boldsymbol{y})$ specified in  \eqref{betapost},  given $r~(=\exp(-\alpha))$ and $\boldsymbol{\beta}$ that are already sampled from $f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})$ via the A-R method.
 
@@
 Whether the 95\%  interval estimates of random effects obtained by a specific model achieve the nominal 95\% confidence level  for any true parameter values is one of the key model evaluation criteria.
-A frequency method checking is a procedure to evaluate it, which is different from a model checking that tests whether a two-level model is appropriate for data (overdispersion exists in data) \citep{dean1992testing, modelchecking1996}.
+A \emph{frequency method checking} is a procedure to evaluate it, which is different from a model checking that tests whether a two-level model is appropriate for data  \citep{dean1992testing, modelchecking1996}.
 Conditioning that the two-level model is appropriate, the frequency method checking generates pseudo-data sets given specific values of hyper-parameters (a parametric bootstrapping) and estimates unknown coverage probabilities based on these mock data sets.
-
-From now on, the explanation will be based on the Gaussian model because the idea can be easily applied to the other two models.
+We will describe the frequency method checking based on the Gaussian model because the idea can be easily applied to the other two models.
 
@@
 Figure \ref{fig:pseudo} displays the process of generating pseudo-data sets.
-It is noted that  the conjugate prior distribution of each random effect in Equation \ref{normalprior} is completely determined by two hyper-parameters, $A$ and $\boldsymbol{\beta}$.
-Fixing these hyper-parameters at specific values, we generate  $N_{sim}$ sets of random effects from the conjugate prior distribution, i.e., \{{\boldmath $\mu$}$^{(i)},~i=1, \ldots, N_{sim}\}$, where the superscript $(i)$ indicates the $i$-th simulation.
-Next, using the distribution of observed data in Equation \ref{normalobs}, we generate $N_{sim}$ sets of observed data sets $\{\boldsymbol{y}^{(i)},~i=1, \ldots, N_{sim}\}$ given each {\boldmath$\mu$}$^{(i)}$.
+It is noted that  the conjugate prior distribution of each random effect in  \eqref{normalprior} is completely determined by two hyper-parameters, $A$ and $\boldsymbol{\beta}$.
+Fixing these hyper-parameters at specific values, we generate  $N_{\textrm{sim}}$ sets of random effects from the conjugate prior distribution, i.e., \{{\boldmath $\mu$}$^{(i)},~i=1, \ldots, N_{\textrm{sim}}\}$, where the superscript $(i)$ indicates the $i$-th simulation.
+Next, using the distribution of observed data in  \eqref{normalobs}, we generate $N_{\textrm{sim}}$ sets of observed data sets $\{\boldsymbol{y}^{(i)},~i=1, \ldots, N_{\textrm{sim}}\}$ given each {\boldmath$\mu$}$^{(i)}$.
 Note that we generate one observed data set per one set of random effects.
 
-\begin{figure}[h]
+\begin{figure}[t]
 \begin{center}
-\includegraphics[width=6cm]{process.png}
+\includegraphics[width=5cm]{process.png}
 \caption{Pseudo-data generating process.}
@@
 \subsection{Coverage probability estimation}
-After fitting a Normal-Normal model on each simulated data set, we obtain interval estimates of random effects $\boldsymbol{\mu}$.
-Let $(\hat{\mu}^{(l)}_{j, ~low}, ~\hat{\mu}^{(l)}_{j, ~upp})$ represent the lower and upper bounds of the interval estimate of random effect $j$ based on the $i$-th simulated data set given a specific confidence level.
+After fitting the Gaussian model on each simulated data set, we obtain interval estimates of random effects $\boldsymbol{\mu}$.
+Let $(\hat{\mu}^{(i)}_{j, ~\textrm{low}}, ~\hat{\mu}^{(i)}_{j, ~\textrm{upp}})$ represent the lower and upper bounds of the interval estimate of random effect $j$ based on the $i$-th simulated data set given a specific confidence level.
 Let's define a coverage indicator of random effect $j$ on the $i$-th mock data set as
@@
 I_{A, \boldsymbol{\beta}}(\mu_j^{(i)}) = \left\{ \begin{array}{ll}
-1, & \textrm{if $\mu_j^{(i)}\in(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp})$}\\
+1, & \textrm{if $\mu_j^{(i)}\in(\hat{\mu}^{(i)}_{j, ~\textrm{low}}, ~\hat{\mu}^{(i)}_{j, ~\textrm{upp}})$}\\
 0, & \textrm{otherwise}
@@
 
-%B$^3$LM model to $N_{sim}$ pseudo-datasets in order to obtain $k\times N_{sim}$ interval estimates,  \{$(\hat{p}^{(l)}_{j, ~low}, ~\hat{p}^{(l)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, N_{sim}$\}.
+%B$^3$LM model to $N_{\textrm{sim}}$ pseudo-datasets in order to obtain $k\times N_{\textrm{sim}}$ interval estimates,  \{$(\hat{p}^{(i)}_{j, ~low}, ~\hat{p}^{(i)}_{j, ~upp}), ~j=1,\ldots, k,~ i=1, \ldots, N_{\textrm{sim}}$\}.
 
@@
 \subsubsection{Simple unbiased coverage estimator.}
-When the confidence level is 95\%, the proportion of 95\% interval estimates that contain random effect $j$ is an intuitive choice for  the coverage rate estimator of random effect $j$.
+When the confidence level is 95\%, the proportion of 95\% interval estimates that contain random effect $j$ is an intuitive choice for  the coverage rate estimator for random effect $j$.
 This estimator  implicitly assumes that there exist $k$ unknown coverage probabilities of random effects, denoted by $C_{A, \boldsymbol{\beta}}(\mu_j)$ for $j=1, 2, \ldots, k$, depending on the values of the hyper-parameters that generate random effects and mock data sets.
-The coverage indicators for random effect $j$ in Equation \ref{coverage_indicator} follow an independent and identically distributed  Bernoulli distribution given the unknown coverage rate $C_{A, \boldsymbol{\beta}}(\mu_j)$.
-The sample mean of these coverage indicators is a simple unbiased coverage estimator for $C_{A, \boldsymbol{\beta}}(\mu_j)$.
-%estimates the coverage probability via the sample mean of these indicator variables for each group $j$,
+The coverage indicators for random effect $j$ in  \eqref{coverage_indicator} is assumed to follow an independent and identically distributed  Bernoulli distribution given the unknown coverage rate $C_{A, \boldsymbol{\beta}}(\mu_j)$.
+The sample mean of these coverage indicators is a simple unbiased coverage estimator for $C_{A, \boldsymbol{\beta}}(\mu_j)$;  %estimates the coverage probability via the sample mean of these indicator variables for each group $j$,
 \begin{equation}
-\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)= \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}I_{A, \boldsymbol{\beta}}(\mu_j^{(i)}),~ j=1, 2, \ldots, k.
+\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)= \frac{1}{N_{\textrm{sim}}}\sum_{i=1}^{N_{\textrm{sim}}}I_{A, \boldsymbol{\beta}}(\mu_j^{(i)}),~ j=1, 2, \ldots, k.
 \end{equation}
@@
  %true coverage probability for the $j$th group depending on specific values of $(r, \boldsymbol{\beta})$. 
-%For reference, even if we sample $L$ datasets per one parameter set, $L\cdot N_{sim}$ indicators $I^{(i, l)}_{j}, i = 1, \ldots, N_{sim}, l = 1, \ldots, L$, have still $iid$ Bernoulli($p_{cov, j}$) distribution.
-
-The unbiased variance estimator of $Var(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))$ is 
+%For reference, even if we sample $L$ datasets per one parameter set, $L\cdot N_{\textrm{sim}}$ indicators $I^{(i, l)}_{j}, i = 1, \ldots, N_{\textrm{sim}}, l = 1, \ldots, L$, have still $iid$ Bernoulli($p_{cov, j}$) distribution.
+
+For $j=1, 2, \ldots, k$, the unbiased variance estimator of $\VAR(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))$ is 
 \begin{equation}\label{svar}
-\widehat{Var}(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))=\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})-\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))^{2},~ j=1, 2, \ldots, k.
+\widehat{\VAR}(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))=\frac{1}{N_{\textrm{sim}}(N_{\textrm{sim}}-1)}\sum_{i=1}^{N_{\textrm{sim}}}(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})-\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))^{2}.
 \end{equation}
@@
 The situation deteriorates if the number of simulations or the size of data is large, or the estimation method is computationally demanding.
-\citet{morris1997} and \cite{tang2002fitting} used a Rao-Blackwellized (RB) unbiased coverage estimator for the unknown coverage rate of each random effects, which is more efficient than the simple indicator-based coverage estimator.
+\citet{morris1997} and \cite{tang2002fitting} used a Rao-Blackwellized (RB) unbiased coverage estimator for the unknown coverage rate of each random effect, which is more efficient than the simple unbiased coverage estimator.
 For $j=1, 2, \ldots, k$,
 \begin{equation}\label{RB_theory}
-C_{A, \boldsymbol{\beta}}(\mu_j)=E(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)\vert A, \boldsymbol{\beta})=E\bigg[\frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})\vert A, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})\bigg\vert A, \boldsymbol{\beta}\bigg],
-\end{equation}
-where the sample mean of conditional expectations inside the outer expectation is the RB unbiased coverage estimator. To be specific,
-\begin{eqnarray}\label{RB}
-\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) &=& \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}}E(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})\vert A, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})\\
-&=& \frac{1}{N_{sim}}\sum_{i=1}^{N_{sim}} Pr(\mu_j^{(i)}\in(\hat{\mu}^{(i)}_{j, ~low}, ~\hat{\mu}^{(i)}_{j, ~upp})\vert A, \boldsymbol{\beta},  \boldsymbol{y}^{(i)}).\nonumber
-\end{eqnarray}
-We  can easily compute the above conditional posterior probabilities using the cumulative density function of the Normal conditional posterior distribution of each random effect in Equation \ref{normalpost}.
-The variance of  $\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j)$ is smaller than or equal to the variance of a simple coverage estimator $\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)$ \citep{radhakrishna1945information, blackwell1947conditional}.
-
-%, i.e., $Pr(p_j^{(l)}<\hat{p}^{(l)}_{j, ~upp}\vert r, \boldsymbol{\beta}, \boldsymbol{y}^{(l)})-Pr(p_j^{(l)}<\hat{p}^{(l)}_{j, ~low},\vert r, \boldsymbol{\beta}, \boldsymbol{y}^{(l)})$.
-
-If one dataset $\boldsymbol{y}^{(l)}$ is simulated per one set of random effects $\boldsymbol{\mu}^{(l)}$, the variance estimator below is an unbiased estimator of $Var(\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) )$.
+C_{A, \boldsymbol{\beta}}(\mu_j)=\E(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)\vert A, \boldsymbol{\beta})=E\bigg[\frac{1}{N_{\textrm{sim}}}\sum_{i=1}^{N_{\textrm{sim}}}\E(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})\vert A, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})\bigg\vert A, \boldsymbol{\beta}\bigg],
+\end{equation}
+where the sample mean of the conditional expectations inside the outer expectation is the RB unbiased coverage estimator. To be specific,
+\begin{align}\label{RB}
+\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) &= \frac{1}{N_{\textrm{sim}}}\sum_{i=1}^{N_{\textrm{sim}}}\E(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})\vert A, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})\\
+&= \frac{1}{N_{\textrm{sim}}}\sum_{i=1}^{N_{\textrm{sim}}} \Prob(\mu_j^{(i)}\in(\hat{\mu}^{(i)}_{j, ~\textrm{low}}, ~\hat{\mu}^{(i)}_{j, ~upp})\vert A, \boldsymbol{\beta},  \boldsymbol{y}^{(i)}).
+\end{align}
+We  can easily compute the above conditional posterior probabilities using the cumulative density function of the Normal conditional posterior distribution of each random effect in  \eqref{normalpost}.
+The variance of  $\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j)$ does not exceed the variance of a simple unbiased coverage estimator $\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)$ \citep{radhakrishna1945information, blackwell1947conditional}.
+
+%, i.e., $Pr(p_j^{(i)}<\hat{p}^{(i)}_{j, ~upp}\vert r, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})-Pr(p_j^{(i)}<\hat{p}^{(i)}_{j, ~low},\vert r, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})$.
+
+If one dataset $\boldsymbol{y}^{(i)}$ is simulated per one set of random effects $\boldsymbol{\mu}^{(i)}$, the variance estimator below is an unbiased estimator of $\VAR(\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) )$.
 For $j=1, 2, \ldots, k,$
 \begin{equation}\label{RBvar}
-\widehat{Var}(\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) )\equiv\frac{1}{N_{sim}(N_{sim}-1)}\sum_{i=1}^{N_{sim}}\bigg(E(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})\vert A, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})-\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) \bigg)^{2}.
-\end{equation}
-
-\subsubsection{Rao-Blackwellized overall unbiased coverage estimator}\label{overallRB} Assuming that the unknown  coverage probabilities are the same for all random effects, we use the Rao-Blackwellized overall coverage estimator and its variance estimator as follows.
+\widehat{\VAR}(\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) )\equiv\frac{1}{N_{\textrm{sim}}(N_{\textrm{sim}}-1)}\sum_{i=1}^{N_{\textrm{sim}}}\bigg(\E(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})\vert A, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})-\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) \bigg)^{2}.
+\end{equation}
+
+\subsubsection{Rao-Blackwellized overall unbiased coverage estimator}\label{overallRB} Assuming that the unknown  coverage probabilities are the same for all random effects, we use the Rao-Blackwellized overall unbiased coverage estimator and its variance estimator;
 \begin{equation}\label{RBoverall}
-\bar{\bar{I}}^{RB}_{r, \boldsymbol{\beta}} = \frac{1}{k}\sum_{j=1}^k\bar{I}^{RB}_{r, \boldsymbol{\beta}}(p_j)~~\textrm{and}~~ \widehat{Var}(\bar{\bar{I}}_{RB})=\frac{1}{k^2}\sum_{j=1}^k\widehat{Var}(\bar{I}^{RB}_{r, \boldsymbol{\beta}}(p_j)).
+\bar{\bar{I}}^{RB}_{r, \boldsymbol{\beta}} = \frac{1}{k}\sum_{j=1}^k\bar{I}^{RB}_{r, \boldsymbol{\beta}}(p_j)~~\textrm{and}~~ \widehat{\VAR}(\bar{\bar{I}}_{RB})=\frac{1}{k^2}\sum_{j=1}^k\widehat{\VAR}(\bar{I}^{RB}_{r, \boldsymbol{\beta}}(p_j)).
 \end{equation}
@@
 The function \code{gbp} creates an S3 object ``gbp'' on which  three generic functions \code{plot}, \code{print}, and \code{summary} are defined.
-To use these relevant functions, we need to save the outcome of \code{gbp} into an object such as \code{g.output} in the code below).
+%To use these relevant functions, we need to save the outcome of \code{gbp} into an object such as \code{g.output} in the code below).
 
@@
 If we want to designate a known value of the expected random effect $\mu^E=\beta_1$ for the Gaussian model or $p^E=\exp(\beta_1)/(1+\exp(\beta_1))$ for the Binomial model, then we put that value into \code{gbp} using an argument \code{mean.PriorDist}.
-For example, if the $\mu^E$ is known as 10, then we use the following code.
+For example, if  $\mu^E$ is known as 10, then we use the following code.
 %The usage of the Binomial model is the same.
@@
 The function \code{gbp} contains several optional arguments.
-The argument \code{Alpha}, whose default is 0.95, sets the confidence level, producing $100\times$\code{Alpha}\% interval estimates for the random effects.
+The argument \code{Alpha}, whose default value is 0.95, sets the confidence level, producing $100\times$\code{Alpha}\% interval estimates for the random effects.
 For the Gaussian model, setting the argument \code{normal.CI} to \code{TRUE} lets the function \code{gbp}  use a Normal approximation to the unconditional posterior distribution of the random effect \citep{tang2011}.
-The default of \code{normal.CI} is \code{FALSE} for the skewed-Normal approximation \citep{kelly2014advances}.
-
-The function \code{gbp} uses the acceptance-rejection method to fit the Binomial model if we assign the desired number of posterior samples ($N$ in Equation \ref{weight}) through the argument \code{n.AR}; its default value is 0.
-There are several arguments related to the acceptance-rejection method.
+The default value of \code{normal.CI} is \code{FALSE} for the skewed-Normal approximation \citep{kelly2014advances}.
+
+The function \code{gbp} uses the A-R method to fit the Binomial model if we assign the desired number of posterior samples ($N$ in  \eqref{weight}) through the argument \code{n.AR}; its default value is 0.
+There are several arguments related to the A-R method.
 The argument \code{n.AR.factor} determines how many trial samples the method draws; its default value is 4, meaning that the method draws \code{n.AR} $\times4$ trial samples and accepts or rejects them.
@@
 The argument \code{save.result} indicates whether we save the whole posterior samples of the random effects and hyper-parameters; its default value is \code{TRUE}.
-The two arguments \code{t} and \code{u}, taking on positive values, allow users to chose the joint hyper-prior distribution $f(r, \boldsymbol{\beta})\propto d\boldsymbol{\beta}dr/(t+r)^{u+1}$; the default values for \code{t} and \code{u} are 0 and 1, respectively, for the joint hyper-prior distribution specified in Equation \ref{eq:hyper}.
-
-For example, when there are two covariates, the following code produces 2,000 posterior samples of random effects and hyper-parameters, $r$ and $\boldsymbol{\beta}_{3\times1}$ including an intercept term, via the acceptance-rejection method with 8,000 trial samples.
+The two arguments \code{t} and \code{u}, taking on positive values, allow users to chose the joint hyper-prior distribution $f(r, \boldsymbol{\beta})\propto d\boldsymbol{\beta}dr/(t+r)^{u+1}$; the default values for \code{t} and \code{u} are 0 and 1, respectively, for the joint hyper-prior distribution specified in  \eqref{eq:hyper}.
+
+For example, when there are two covariates, the following code produces 2,000 posterior samples of random effects and hyper-parameters, $r$ and $\boldsymbol{\beta}_{(3\times1)}$ including an intercept term, via the A-R method with 8,000 trial samples.
 \begin{CodeChunk}
@@
 The object \code{b.output} above contains detailed outcomes.
-The function \code{names} will show the list of outcomes (too many to be listed in this article); see the document of \code{gbp} to check the details of the items saved.
+The function \code{names} will show the list of outcomes (too many to be listed here); see the document of \code{gbp} to check the details of the items saved as follows.
 \begin{CodeChunk}
@@
 The S3 object ``gbp'' benefits from three generic functions, \code{print}, \code{summary}, and \code{plot}.
-The estimation result for all the random effects pops up if we type the ``gbp'' object at the \proglang{R} console, which plays the same role of the function \code{print} with its default argument ``\code{sort = TRUE}''.
+The estimation result for all the random effects appears if we type the ``gbp'' object at the \proglang{R} console, which plays the same role of the function \code{print} with its default argument ``\code{sort = TRUE}''.
 When the argument \code{sort} is set to \code{TRUE}, the function \code{print} prints out the estimation result for all the groups in the ascending order of $n$ for the Binomial and Poisson model and the ascending order of standard errors for the Gaussian model.
@@
 
-The function \code{summary} prints a detailed estimation result, including the estimation result for the hyper-parameters.
+The function \code{summary} prints a detailed estimation result, including the estimation result for the hyper-parameters, $A$ (or $r$) and $\boldsymbol{\beta}$.
 \begin{CodeChunk}
@@
 
-The argument \code{sim} sets the number of simulations $N_{sim}$ defined in Section \ref{sec4}.
+The argument \code{sim} sets the number of simulations $N_{\textrm{sim}}$ defined in Section \ref{sec4}.
 If we do not assign values of the hyper-parameters by the arguments \code{A.or.r} and \code{reg.coef} as above, then the function \code{coverage} automatically sets the estimated posterior modes of hyper-parameters saved in the ``gbp'' object (or their posterior medians if the acceptance-rejection method for the Binomial model is used) to the generative values of hyper-parameters.
@@
 
-The output contains information about the observed death rates $\bar{y}_{j}$, caseloads $n_{j}$, known prior mean $\lambda^E$, shrinkage estimates $\hat{B}_{j}$, lower bounds of interval estimates $\hat{\lambda}_{j, low}$, posterior means $\hat{\lambda}_j\equiv E(\lambda_{j}\vert \boldsymbol{y})$, upper bounds  of interval estimates $\hat{\lambda}_{j, upp}$, and posterior standard deviations  for each random effect based on the assumed unconditional Gamma posterior distributions.
+The output contains information about the observed death rates $\bar{y}_{j}$, caseloads $n_{j}$, known prior mean $\lambda^E$, shrinkage estimates $\hat{B}_{j}$, lower bounds of interval estimates $\hat{\lambda}_{j, low}$, posterior means $\hat{\lambda}_j\equiv \E(\lambda_{j}\vert \boldsymbol{y})$, upper bounds  of interval estimates $\hat{\lambda}_{j, upp}$, and posterior standard deviations  for each random effect based on the assumed unconditional Gamma posterior distributions.
 %The lower and upper bounds of an interval estimate for a random effect are 2.5\% and 97.5\% percentiles of the assumed unconditional Gamma posterior distributions if 95\% confidence level is used.
@@
 
-In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level (\code{Alpha = 0.95} as a default) and the red circles indicate Rao-Blackwellized (RB) unbiased coverage estimates, $\bar{I}^{RB}_{r, \lambda^E}(\lambda_j)$ for $j=1, 2, \ldots, 31$.
+In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level (\code{Alpha = 0.95} as a default) and the red circles indicate Rao-Blackwellized (RB) unbiased coverage estimates, $\bar{I}^{RB}_{r, \lambda^\E}(\lambda_j)$ for $j=1, 2, \ldots, 31$.
 The overall RB unbiased coverage estimate across all the hospitals ($\bar{\bar{I}}^{RB}_{r, \lambda^E}$) is 0.955.
@@
 It turns out that the variance estimate of the RB unbiased coverage estimate for the first hospital ($0.0016^2$) is about 19 times smaller than that of the simple one ($0.0070^2$).
-It means that the RB unbiased coverage estimates based on 1,000 simulations ($N_{sim}$) are as precise as the simple unbiased coverage estimates based on 19,000 simulations in terms of estimating the coverage probability for the first hospital, $C_{r, \lambda^E}(\lambda_1)$.
+It means that the RB unbiased coverage estimates based on 1,000 simulations ($N_{\textrm{sim}}$) are as precise as the simple unbiased coverage estimates based on 19,000 simulations in terms of estimating the coverage probability for the first hospital, $C_{r, \lambda^\E}(\lambda_1)$.
 
@@
 Unless otherwise specified, the procedure fixes the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\boldsymbol{\beta}}_1$ in this example) and then simulates random effects $\theta_j$ for each group $j$.
-The model is then estimated and this is repeated an $N_{sim}$ (\code{nsim}) number of times to estimate the coverage probabilities of the procedure.
+The model is then estimated and this is repeated an $N_{\textrm{sim}}$ (\code{nsim}) number of times to estimate the coverage probabilities of the procedure.
 
@@
 
-If we run the frequency method checking using this ``gbp'' object obtained via the acceptance-rejection method, the $N_{sim}$ simulations also run the acceptance-rejection method.
+If we run the frequency method checking using this ``gbp'' object obtained via the acceptance-rejection method, the $N_{\textrm{sim}}$ simulations also run the acceptance-rejection method.
 
@@
 In addition to the built-in ``frequency method checking'' procedure, we may use the package to undergo ``model checking''.
-For example, in the Gaussian hierarchical model, the assumed marginal distribution of the data is given in Equation \ref{marginal_normal} as part of the likelihood function.
+For example, in the Gaussian hierarchical model, the assumed marginal distribution of the data is given in  \eqref{marginal_normal} as part of the likelihood function.
 By substituting the point estimates of $A$ and $\boldsymbol{\beta}$ from the package into this marginal distribution a test can be constructed to see whether the data follow the marginal distribution suggested by the hierarchical model.
@@
 \appendix
+\section{Posterior propriety of the Poisson model}\label{propriety_poisson}
 \section{Unconditional posterior variance of the Binomial model}\label{apppostvar}
-\section{Unconditional posterior variance of the Gaussian model}\label{apppostvar_normal}
-
-\section{Unconditional posterior variance of the Poisson model}\label{apppostvar_poisson}
+%\section{Unconditional posterior variance of the Gaussian model}\label{apppostvar_normal}
+
+%\section{Unconditional posterior variance of the Poisson model}\label{apppostvar_poisson}
 
@@
 \end{document}
+%For the Gaussian model we do not assume the posterior independence between $A$ and $\boldsymbol{\beta}$ because the conditional posterior variance of the random effect is a constant function of the conditional posterior mean, which is much simpler than that of the Binomial model.
+
+The unconditional posterior mean and variance of random effect $j$ of the Gaussian model are
+\begin{eqnarray}
+\E(\mu_j\vert \boldsymbol{y}) &=&\E(\E(\mu_{j}\vert A, \boldsymbol{\beta}, \boldsymbol{y})\vert\boldsymbol{y})=(1-\E(B_j\vert\boldsymbol{y}))y_j + \E(B_j\vert  \boldsymbol{y})\E(\mu^E_j\vert  \boldsymbol{y})\label{postmean_normal} \\
+\VAR(\mu_{j}\vert \boldsymbol{y}) &=&  \E(\VAR(\mu_{j}\vert A,  \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+\VAR(\E(\mu_{j}\vert A, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_normal}\\
+&=&  (1-V_j)\E(B_j\vert  \boldsymbol{y})+\VAR\big(\textrm{B}_{j}(y_{j}-\mu^E_{j})\vert \boldsymbol{y}\big) \\
+&=&h_g(\E(B_j\vert\boldsymbol{y}), \E(B^2_j\vert\boldsymbol{y}),  \E(\mu^E_j\vert\boldsymbol{y}), \E((\mu^E_j)^2\vert\boldsymbol{y})).\label{approximate_var_normal}
+\end{eqnarray}
+The unconditional posterior mean and variance of random effect $j$ under the Gaussian model are also functions of the unconditional posterior moments of the shrinkage factors and expected random effects.
+We specify the function $h_g$ in Appendix \ref{apppostvar_normal}.
+
+%conditional posterior means of  random effect $j$ in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are a linear function of the shrinkage factor $B_{j}$ and the conditional posterior variances in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are linear (Gaussian), quadratic (Poisson), and  approximately cubic (Binomial) functions of $B_{j}$, considering $r+n_j=n_j/(1-B_j)$.
+Thus, the unconditional posterior mean and variance of the random effect are the functions of the unconditional posterior moments of the shrinkage factors.
+
+Next, we estimate the unconditional posterior moments of the shrinkage factors after approximating their unconditional posterior distributions by Beta distributions via the ADM. 
+%Next, we estimate the unconditional posterior moments of the shrinkage factors and expected random effects after approximating their unconditional posterior distributions by Beta distributions via the ADM.

### 2015-07-02 Rgbp.Rcheck/Rgbp-Ex.R
error

@@ -1,871 +1,0 @@
-pkgname <- "Rgbp"
-source(file.path(R.home("share"), "R", "examples-header.R"))
-options(warn = 1)
-base::assign(".ExTimings", "Rgbp-Ex.timings", pos = 'CheckExEnv')
-base::cat("name\tuser\tsystem\telapsed\n", file=base::get(".ExTimings", pos = 'CheckExEnv'))
-base::assign(".format_ptime",
-function(x) {
-  if(!is.na(x[4L])) x[1L] <- x[1L] + x[4L]
-  if(!is.na(x[5L])) x[2L] <- x[2L] + x[5L]
-  options(OutDec = '.')
-  format(x[1L:3L], digits = 7L)
-},
-pos = 'CheckExEnv')
-
-### * </HEADER>
-library('Rgbp')
-
-base::assign(".oldSearch", base::search(), pos = 'CheckExEnv')
-cleanEx()
-nameEx("Rgbp-package")
-### * Rgbp-package
-
-flush(stderr()); flush(stdout())
-
-base::assign(".ptime", proc.time(), pos = "CheckExEnv")
-### Name: Rgbp
-### Title: Hierarchical Modeling and Frequency Method Checking on
-###   Overdispersed Gaussian, Poisson, and Binomial Data
-### Aliases: Rgbp-package Rgbp
-### Keywords: package
-
-### ** Examples
-
-
-  # Loading datasets
-  data(schools)
-  y <- schools$y
-  se <- schools$se
-
-  # Arbitrary covariate for schools data
-  x2 <- rep(c(-1, 0, 1, 2), 2)
-  
-  # baseball data where z is Hits and n is AtBats
-  z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
-  n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
-
-  # One covariate: 1 if a player is an outfielder and 0 otherwise
-  x1 <- c(1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0)
-
-  ################################################################
-  # Gaussian Regression Interactive Multilevel Modeling (GRIMM) #
-  ################################################################
-
-    ####################################################################################
-    # If we do not have any covariate and do not know a mean of the prior distribution #
[…]

### 2015-07-02 Rgbp/R/gbp.R

@@ -353,7 +353,7 @@ plot.gbp <- function(x, sort = TRUE, ...) {
     temp.data <- as.data.frame(cbind(y, se, pr.m, po.m, po.sd, po.low, po.upp))
     if (x$model == "gr") {
       temp.data <- temp.data[order(temp.data$se, decreasing = TRUE), ]
-    } else
+    } else {
       temp.data <- temp.data[order(temp.data$se), ]
     }
     y <- temp.data$y

### 2015-07-02 jss/article_v3.tex
draft v3

@@
 The estimation result for all the random effects appears if we type the ``gbp'' object at the \proglang{R} console, which plays the same role of the function \code{print} with its default argument ``\code{sort = TRUE}''.
-When the argument \code{sort} is set to \code{TRUE}, the function \code{print} prints out the estimation result for all the groups in the ascending order of $n$ for the Binomial and Poisson model and the ascending order of standard errors for the Gaussian model.
-When the argument \code{sort} is \code{FALSE}, the estimation result comes out as the order of data input.
+When the argument \code{sort} is set to \code{TRUE}, the function \code{print} prints out the estimation result for all the groups in the ascending order of $n$ for the Binomial and Poisson model and the descending order of standard errors for the Gaussian model.
+When the argument \code{sort} is \code{FALSE}, the estimation result comes out in the order of data input.
 \begin{CodeChunk}
@@
 
-The function \code{plot} draws a shrinkage plot and $100\times$\code{Alpha}\% interval plot for random effects with its default argument ``\code{sort = TRUE}'' that draws the $100\times$\code{Alpha}\% interval plot in the ascending order of $n$ for the Binomial and Poisson model and the ascending order of standard errors for the Gaussian model.
+The function \code{plot} draws a shrinkage plot and $100\times$\code{Alpha}\% interval plot for random effects with its default argument ``\code{sort = TRUE}'' that draws the $100\times$\code{Alpha}\% interval plot in the ascending order of $n$ for the Binomial and Poisson model and the descending order of standard errors for the Gaussian model.
 When the argument \code{sort} is set to \code{FALSE}  the $100\times$\code{Alpha}\% interval plot will be plotted in the order of data input.
@@
 
-The argument \code{sim} sets the number of simulations $N_{\textrm{sim}}$ defined in Section \ref{sec4}.
-If we do not assign values of the hyper-parameters by the arguments \code{A.or.r} and \code{reg.coef} as above, then the function \code{coverage} automatically sets the estimated posterior modes of hyper-parameters saved in the ``gbp'' object (or their posterior medians if the acceptance-rejection method for the Binomial model is used) to the generative values of hyper-parameters.
-If we want to conduct the frequency method checking with different generated values of hyper-parameters, for example, $r=100$ and $\boldsymbol{\beta}^\top=(2, 5)$ when one covariate was used (including an intercept term) to create the ``gbp'' object, then we specify the code as
+The argument \code{nsim} sets the number of simulations, $N_{\textrm{sim}}$.
+If we do not assign values of the hyper-parameters through the arguments \code{A.or.r} and \code{reg.coef}, then the function \code{coverage} automatically sets the estimated posterior modes of hyper-parameters saved in the ``gbp'' object (or their posterior medians if the acceptance-rejection method for the Binomial model is used) as the generative values of hyper-parameters.
+If we want to conduct the frequency method checking with different generated values of hyper-parameters, for example, $r=100$ and $\boldsymbol{\beta}=(2, 5)^\top$ when one covariate was used with an intercept term, then we specify them via the arguments \code{A.or.r} and \code{reg.coef};
 \begin{CodeChunk}
@@
 
-When we fit a model with a known value of the expected random effect, we may want to conduct the frequency method checking with a different value for the expected random effect.
-In this case, the argument \code{mean.PriorDist} enables it.
-For example, when we obtain the ``gbp'' object \code{p.output}   after fitting a Poisson model with a specific value of  $\lambda^E$, if we want to conduct the frequency method checking with the same specific value of  $\lambda^E$, then we do not specify the argument \code{mean.PriorDist} in \code{coverage}.
-Once we specify the argument \code{mean.PriorDist} in \code{coverage}, for example 30 as below, the frequency method checking will be based on the estimated posterior mode of $r$ and the newly specified value of $\lambda^E$, 30.
+When we fit a model with a known value of the expected random effect, the code \code{coverage} conducts the frequency method checking based on the known value.
+However, we may sometimes want to conduct the frequency method checking with a different value for the expected random effect.
+For example, if we want to try a different value of the expected random effect, e.g., 30, we add the argument \code{mean.PriorDist} as follows.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
-
-Although the function \code{coverage} does not produce an S3 object, a detailed summary appears in a plot that automatically pops up after running the function \code{coverage}.
-In addition, the object \code{cov} that contains the result of \code{coverage} contains numerical details, see \code{names(cov)} or type ``\code{?coverage}'' for the list of detailed outcomes.
-If we save the result into an object such as \code{cov} above, then we can always recall the plot, using the function \code{coverage.plot}.
+The frequency method checking will be based on the estimated posterior mode of $r$ and the newly specified value of the expected random effect, 30.
+
+Although the function \code{coverage} does not produce an S3 object, a detailed summary appears in a plot that automatically pops up.
+In addition, the object \code{cov} that we used to save the result of \code{coverage} as above contains numerical details.
+We can use the function \code{names} or check the document of \code{coverage} to see the list of numerical details.
+\begin{CodeChunk}
+\begin{CodeInput}
+R> names(cov)
+R> ?coverage
+\end{CodeInput}
+\end{CodeChunk}
+
+If we save the result into an object such as \code{cov} above, then we can always recall the coverage plot, using the function \code{coverage.plot}.
 \begin{CodeChunk}
@@
 
-We analyze a data set of 31 hospitals in New York state comprising of the outcomes of the coronary artery bypass graft (CABG) surgery \citep{morris2012}\footnote{Visit \emph{http://www.health.ny.gov/statistics/diseases/cardiovascular/} for more profile data of the CABG surgery in New York state.}.
+We analyze a data set of 31 hospitals in New York state comprising of the outcomes of the coronary artery bypass graft (CABG) surgery \citep{morris2012}.
 The data set contains the number of deaths, $\boldsymbol{y}$, for a specified period after CABG surgeries out of the total number of patients, $\boldsymbol{n}$, receiving CABG surgeries in each hospital.
 Health care providers may use these data to improve their care qualities, and patients may refer to the data to select a better hospital.
-Our goal is to obtain the point and interval estimates for the unknown true mortality rates of 31 hospitals (random effects) to evaluate  each hospital's reliability on the CABG surgery.
-We interpret the caseloads, $\boldsymbol{n}$,  as exposures and assume that the state-level death rate per exposure of this surgery ($\lambda^E$) is known as 0.030 to fit the Poisson model for an illustrative purpose.
-If covariate information is available or the information about the expected random effect is unavailable a priori, we recommend using the Binomial model.
+Our goal is to obtain the point and interval estimates for the unknown true mortality rates (random effects) of 31 hospitals to evaluate  each hospital's reliability on the CABG surgery.
+We interpret the caseloads, $\boldsymbol{n}$,  as exposures and assume that the state-level death rate per exposure of this surgery ($\lambda^E$) is known as 0.03 to fit the Poisson model for an illustrative purpose.
+If covariate information is available or the information about the expected random effect is unknown, we recommend using the Binomial model.
+%\footnote{Visit \emph{http://www.health.ny.gov/statistics/diseases/cardiovascular/} for more profile data of the CABG surgery in New York state.}
 
@@
 \begin{CodeInput}
-R> library(``Rgbp'')
-R> data(``hospital'')
+R> library("Rgbp")
+R> data("hospital")
 R> y <- hospital$d
@@
 
-The function \code{gbp} fits the Poisson hierarchical model with the Gamma conjugate prior distribution as a population distribution of the death rates in New York states whose mean ($\lambda^E$) is 0.030.
-The number of regression coefficients ($m$) is 0 because we do not need to estimate them via  a log-linear regression.
+The function \code{gbp} fits the Poisson model with a Gamma conjugate prior distribution as the population distribution of the death rates in New York states whose mean ($\lambda^E$) is 0.030.
+The number of regression coefficients ($m$) is 0 because we do not estimate them via  a log-linear regression.
 \begin{CodeChunk}
@@
 
-The output contains information about the observed death rates $\bar{y}_{j}$, caseloads $n_{j}$, known prior mean $\lambda^E$, shrinkage estimates $\hat{B}_{j}$, lower bounds of interval estimates $\hat{\lambda}_{j, low}$, posterior means $\hat{\lambda}_j\equiv \E(\lambda_{j}\vert \boldsymbol{y})$, upper bounds  of interval estimates $\hat{\lambda}_{j, upp}$, and posterior standard deviations  for each random effect based on the assumed unconditional Gamma posterior distributions.
+The output contains information about the observed death rates $\bar{y}_{j}$, caseloads $n_{j}$, known prior mean $\lambda^E$, shrinkage estimates $\hat{B}_{j}$, lower bounds of interval estimates $\hat{\lambda}_{j, \textrm{low}}$, posterior means $\hat{\lambda}_j$, upper bounds  of interval estimates $\hat{\lambda}_{j, \textrm{upp}}$, and posterior standard deviations  for each random effect based on the assumed unconditional Gamma posterior distributions.
 %The lower and upper bounds of an interval estimate for a random effect are 2.5\% and 97.5\% percentiles of the assumed unconditional Gamma posterior distributions if 95\% confidence level is used.
@@
 
-A function \code{summary} shows selective information about hospitals with minimum, median, and maximum exposures and more detailed estimation results about the hyper-parameter $\alpha=-\log(r)$.
-\begin{CodeChunk}
+A function \code{summary} shows selective information about hospitals with minimum, median, and maximum exposures and the estimation result of the hyper-parameter $\alpha=-\log(r)$.  \begin{CodeChunk}
 \begin{CodeInput}
@@
 For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.911$) was calculated by 684 / (684 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.911)*0.0448 + 0.911 * 0.030=0.0313$.
-As for this hospital, using more information from the conjugate prior distribution is an appropriate choice because the amount  of observed information (67) is far less than the amount of state-level information (684).
+As for this hospital, using more information from the conjugate prior distribution is an appropriate choice because the amount  of observed information (67) is much less than the amount of state-level information (684).
 
@@
 
-In Figure \ref{fig:hospshr} the regression towards the mean (RTTM) is obvious in the first graph; the observed death rates, denoted by empty dots on the upper horizontal line, are shrinking towards the known expected random effect, denoted by a blue vertical line at 0.030, to the different extents.
-Note that some hospitals' ranks have changed by shrinking much harder towards 0.030 than the others.
-For example, an empty square at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that  the seemingly safest hospital among 31 hospitals in terms of the observed death rate is probably not the safest in terms of the estimated posterior mean accounting for the different caseloads of these two hospitals.
-
-Intuitively, switching ranks for these two hospitals is reasonable.
+In Figure \ref{fig:hospshr} the regression towards the mean (RTTM) is obvious in the first plot; the observed death rates, denoted by empty dots on the upper horizontal line, are shrinking towards the known expected random effect, denoted by a blue vertical line at 0.03, to the different extents.
+Note that some hospitals' ranks have changed by shrinking much harder towards 0.03 than the others.
+For example, an empty square at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that  the seemingly safest hospital in terms of the observed death rate is probably not the safest in terms of the estimated posterior mean accounting for the different caseloads of these two hospitals.
+
+%Intuitively, switching ranks for these two hospitals is reasonable. 
 To be specific, their observed death rates ($y_{j}$, $j=8, 23$) are 0.0136 and 0.0150 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602, respectively.
 Considering solely the observed death rates may lead to an unfair comparison because the latter hospital handled twice the caseload.
-\pkg{Rgbp} accounts for this caseload difference, making the posterior mean for the random effect of the former hospital shrink toward the state-level mean ($\lambda^E$=0.030) much harder than that for of the latter hospital.
+\pkg{Rgbp} accounts for this caseload difference, making the posterior mean for the random effect of the former hospital shrink toward the state-level mean ($\lambda^E$=0.03) much harder than that for the latter hospital.
 
 Note that the point estimates are not enough to evaluate hospital reliability because one hospital may have a lower point estimate but  larger uncertainty (variance) than the other.
-The second plot of Figure \ref{fig:hospshr} displays the estimated 95\% intervals.
-We see that each posterior mean (red dot) is between the sample mean (empty dot) and the known expected random effect (a blue horizontal line).
+The second plot of Figure \ref{fig:hospshr} displays the 95\% interval estimates.
+Note that each posterior mean (red dot) is between the sample mean (empty dot) and the known expected random effect (a blue horizontal line).
 %For reference, we could plot this 95\% interval plot by the order of data input via \code{plot(p, sort = FALSE)}.
@@
 The observed death rates for these two hospitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
-The 31st hospital has twice the caseload, which leads to borrowing less information from the New York state-level hierarchy (or shrinking less toward the state-level mean, 0.030) with smaller variance.
-Based on the point and interval estimates, the 31st hospital seems the most reliable one among all candidates.
-
-When fitting a model it is always a good idea to question how reliable the estimation procedure is.
+The 31st hospital has twice the caseload, which leads to borrowing less information from the New York state-level hierarchy (or shrinking less toward the state-level mean, 0.03) with smaller variance.
+Based on the point and interval estimates, the 31st hospital seems the most reliable one.
+
+We conduct the frequency method checking to question how reliable the estimation procedure is.
 The function \code{coverage}  generates pseudo-datasets given the estimated value of $r$, 683.53, as a generative value.
-For reference, we can designate any generative values of $r$ and $\lambda^E$ by adding two arguments into the code below, for example, \code{A.or.r = 600} and \code{mean.PriorDist = 0.05}.
+For reference, we can designate any generative values of $r$ and $\lambda^E$ by adding two arguments, \code{A.or.r} and \code{mean.PriorDist}, into the code below.
 %; \code{R> pcv <- coverage(p, A.or.r = 600, nsim = 1000)}.
@@
 
-In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level (\code{Alpha = 0.95} as a default) and the red circles indicate Rao-Blackwellized (RB) unbiased coverage estimates, $\bar{I}^{RB}_{r, \lambda^\E}(\lambda_j)$ for $j=1, 2, \ldots, 31$.
+In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level  and the red circles indicate RB unbiased coverage estimates, $\bar{I}^{RB}_{r, \lambda^\E}(\lambda_j)$ for $j=1, 2, \ldots, 31$.
 The overall RB unbiased coverage estimate across all the hospitals ($\bar{\bar{I}}^{RB}_{r, \lambda^E}$) is 0.955.
-None of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads ($n_{j}$).
+None of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads.
 This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence level.
@@
 
-See \cite{1995} for a similar ranking problem using a Poisson hierarchical modeling with a different parametrization.
+%See \cite{1995} for a similar ranking problem using a Poisson hierarchical modeling with a different parametrization.
 
@@
 \begin{CodeInput}
-R> library(``Rgbp'')
-R> data(``schools'')
+R> library("Rgbp")
+R> data("schools")
 R> y  <- schools$y
@@
 \begin{CodeOutput}
-Summary for each unit (sorted by se):
+Summary for each group (sorted by the descending order of se):
 
      obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
-5       -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
-2        8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
-7       18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
-4        7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
-6        1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
-1       28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
-3       -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
-8       12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
-Mean          12.5      8.168     0.552   -9.163     8.168   25.723   8.900
+8       12.00 18.0       8.17     0.734   -10.21      9.19     29.9   10.23
+3       -3.00 16.0       8.17     0.685   -17.13      4.65     22.5   10.10
+1       28.00 15.0       8.17     0.657    -2.32     14.98     38.8   10.56
+4        7.00 11.0       8.17     0.507    -8.78      7.59     23.6    8.26
+6        1.00 11.0       8.17     0.507   -13.03      4.63     20.1    8.44
+2        8.00 10.0       8.17     0.459    -7.25      8.08     23.4    7.81
+7       18.00 10.0       8.17     0.459    -1.29     13.48     30.8    8.18
+5       -1.00  9.0       8.17     0.408   -13.30      2.74     16.7    7.63
+Mean          12.5       8.17     0.552    -9.16      8.17     25.7    8.90
 \end{CodeOutput}
@@
 The summary provides results regarding the second level hierarchy parameters.
-It can be seen that the estimate of the expected random effect, $\mu^E$ (\code{beta1}), is not significantly different from 0 suggesting that there was no effect of the coaching program on SAT math scores.
+It can be seen that the estimate of the expected random effect, $\mu^E=\beta_1$ (\code{beta1}), is not significantly different from 0 suggesting that there was no effect of the coaching program on SAT math scores.
 
@@
 \end{CodeChunk}
-\begin{figure}[h] 
+\begin{figure}[t!] 
 \begin{center}
@@
 
-As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence level (black horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example.
+As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence level, denoted by a black horizontal line at 0.95, is achieved for each school in this example.
 Note that all the coverage estimates depend on the chosen generative values of $A$ and $\beta_{1}$, and the assumption that the model is valid.
@@
 The data of 18 major league baseball players contain the batting averages through their first 45 official at-bats of the 1970 season \citep{1975}.
-We add a covariate about their outfielder indicators taking on 1 if a player is an outfielder and 0 otherwise.
+We add a binary covariate that takes on one if a player is an outfielder and zero otherwise.
 We can load the data into \proglang{R} with the following codes.
@@
 \begin{CodeInput}
-R> library(``Rgbp'')
-R> data(``baseball'')
+R> library("Rgbp")
+R> data("baseball")
 R> y <- baseball$Hits
@@
 %$
-Conditioning on the unknown true batting average (random effect) for each player we assume that the at-bats are independent and therefore, $y_{j}\vert p_{j}\stackrel{indep.}{\sim} \textrm{Binomial}(45, p_{j}), ~j=1, \ldots, 18$.
-Our goal is to obtain point and interval estimates of each random effect, $p_j$, whilst considering the additional information on whether the player is an outfielder or not.
-The function \code{gbp} provides a way to incorporate such covariate information seamlessly into the conjugate Beta prior distribution so that the regression towards the mean (RTTM) occurs within outfielders and non-outfielders separately.
+Conditioning on the unknown true batting average (random effect) of each player we assume that the at-bats are independent and therefore, $y_{j}\vert p_{j}\stackrel{\textrm{indep.}}{\sim} \textrm{Binomial}(45,~ p_{j}), ~j=1, \ldots, 18$.
+Our goal is to obtain point and interval estimates of each random effect whilst considering the additional information on whether the player is an outfielder or not.
+The function \code{gbp} provides a way to incorporate such covariate information seamlessly into the model so that the regression towards the mean (RTTM) occurs within outfielders and non-outfielders separately.
 %For reference, we can also assume the Normal distribution using $y_{j}=z_{j} / n_{j}$ and $V_{j}=\bar{y}(1-\bar{y})/n$, where $\bar{y}=\sum_{j} z_{j} / \sum_{j} n_{j}$, $j=1,\ldots, 18$.
@@
 
-It is evident in the shrinkage plot in Figure \ref{fig:baseball} that shrinkage occurs from the observed batting averages (empty dots) on the upper horizontal line towards the two prior means, 0.233 and 0.310.
+The shrinkage plot in Figure \ref{fig:baseball} shows that  the observed batting averages (empty dots) on the upper horizontal line shrink towards the two expected random effects, 0.233 and 0.310.
 The short red line symbols near some empty dots are for when two or more points have the same mean and are plotted over each other.
@@
 
-The 95\% interval plot shows the range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups.
+The 95\% interval plot in Figure \ref{fig:baseball} shows the range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups.
 The 10th, 14th, and 15th players, for example, are outfielders but their observed batting averages are far lower than the first five outfielders.
@@
 
-To check the level of trust in these interval estimates, we  proceed to frequency method checking by assuming the estimates, 112.95 for $\hat{r}$ and (-1.194, ~0.389) for $\hat{\boldsymbol{\beta}}$, are given generative values.
+To check the level of trust in these interval estimates, we  proceed to frequency method checking by assuming the estimates, 112.95 for $\hat{r}$ and (-1.194, ~0.389) for $\hat{\boldsymbol{\beta}}$, are the generative values.
 
@@
 
-In Figure \ref{fig:baseball2},  the estimated coverage probabilities for random effects are beyond 0.95, conservatively satisfying the definition of the 95\% confidence interval.
-The Rao-Blackwellized (RB) overall unbiased coverage estimate is 0.972 (across all the players).
+In Figure \ref{fig:baseball2},  the estimated coverage probabilities for random effects are beyond 0.95, conservatively satisfying the 95\% confidence level.
+The RB overall unbiased coverage estimate across all the players is 0.972.
 Note that each coverage estimate depends on given true values of $r$ and $\boldsymbol{\beta}_{(2\times1)}$, and the assumption that the model is valid (overdispersion exists).
 
-The RB unbiased coverage estimates and their standard errors for each player follow.
+We can check the RB unbiased coverage estimates and their standard errors for each player.
 \begin{CodeChunk}
@@
 
-If we want to draw 2,000 posterior samples of random effects and hyper-parameters from their full posterior distribution via the acceptance-rejection method, we use the following \proglang{R} code.
+If we want to draw 2,000 posterior samples of random effects and hyper-parameters from their full posterior distribution via the A-R method, we use the following \proglang{R} code.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
-The ``gbp'' object \code{b.output} contains 2,000 posterior samples of $\alpha$ (\code{b.output$alpha}), a $2,000\times2$ matrix of $\beta$ (\code{b.output$beta}) with each column corresponding to posterior samples of each regression coefficient, and a $k\times2,000$ matrix of random effects with each row contains posterior samples of each random effect.
-
-If we run the frequency method checking using this ``gbp'' object obtained via the acceptance-rejection method, the $N_{\textrm{sim}}$ simulations also run the acceptance-rejection method.
-
-\section[Discussion]{Discussion and summary} \label{discussion}
-\pkg{Rgbp} is an \proglang{R} package for estimating and validating two-level Gaussian, Binomial and Poisson hierarchical models.
+The ``gbp'' object \code{b.output} contains 2,000 posterior samples of $\alpha$ (\code{b.output$alpha}), a $2,000\times2$ matrix of $\beta$ (\code{b.output$beta}) with each column corresponding to 2,000 posterior samples of each regression coefficient, and a $k\times2,000$ matrix of random effects (\code{b.output$p}) with each row contains posterior samples of each random effect.
+
+If we run the frequency method checking using this ``gbp'' object obtained via the A-R method, the $N_{\textrm{sim}}$ simulations also run the A-R method each time.
+
+\section[Discussion]{Discussion} \label{discussion}
+\pkg{Rgbp} is an \proglang{R} package for estimating and validating two-level Gaussian, Poisson, and Binomial hierarchical models.
 The package aims to provide a procedure that is computationally efficient with good frequency properties and includes ``frequency method checking'' functionality to examine repeated sampling properties and to test that the method is valid at specified hyper-parameter values.
 
-As an alternative to other maximization based estimation methods such as MLE and REML, \pkg{Rgbp} provides point and interval estimates of parameters via ADM.
+As an alternative to other maximization based estimation methods such as MLE and REML, \pkg{Rgbp} provides approximate point and interval estimates of parameters via ADM.
 Using the ADM approach, with our specified choice of priors, protects from cases of overshrinkage and undercoverage from which the aforementioned methods suffer  \citep{accuracy1988}.
 
-A benefit of \pkg{Rgbp} is that it produces non-random output (except the acceptance-rejection method for the Binomial model) and so results are easily reproduced and compared across studies.
+A benefit of \pkg{Rgbp} is that it produces non-random output (except the A-R method for the Binomial model) and so results are easily reproduced and compared across studies.
 In addition to being a standalone analysis tool the package can be used as an aid in a broader estimation procedure.
-For example, by checking the similarity of output of \pkg{Rgbp} and that of another estimation procedure (such as MCMC) the package can be used as a confirmatory tool to check whether the alternative procedure has been programmed correctly.
+For example, by checking the similarity of output of \pkg{Rgbp} and that of another estimation procedure such as MCMC (Markov Chain Monte Carlor), the package can be used as a confirmatory tool to check whether the alternative procedure has been programmed correctly.
 In addition, the parameter estimates obtained via \pkg{Rgbp} can be used to initialize a MCMC thus decreasing time to convergence.
-% Note, however, that this is only valid when the same model under both procedures is assumed.
-
-Due to its speed and ease of use, \pkg{Rgbp} can be used as a method of preliminary data analysis.
+Lastly, due to its speed and ease of use, \pkg{Rgbp} can be used as a method of preliminary data analysis.
 Such results may tell statisticians and practitioners alike whether a more intensive method in terms of implementation and computational time, such as MCMC, is needed.
 
-In addition to the built-in ``frequency method checking'' procedure, we may use the package to undergo ``model checking''.
+%In addition to the built-in ``frequency method checking'' procedure, we may use the package to undergo ``model checking''.
 For example, in the Gaussian hierarchical model, the assumed marginal distribution of the data is given in  \eqref{marginal_normal} as part of the likelihood function.
-By substituting the point estimates of $A$ and $\boldsymbol{\beta}$ from the package into this marginal distribution a test can be constructed to see whether the data follow the marginal distribution suggested by the hierarchical model.
+By substituting the point estimates of $A$ and $\boldsymbol{\beta}$ obtained from the package into this marginal distribution, a test can be constructed to see whether the data follow the marginal distribution suggested by the hierarchical model.
 

### 2015-07-24 jss/article_v3.tex
revision

@@
 The data that \pkg{Rgbp} assumes comprise of observed sufficient statistics for each random effect, such as sample means, possibly together with covariates of each group.
-The approximate Bayesian tool equipped with the adjustment for density maximization estimates random effects, regression coefficients, and a second-level variance component.
+The approximate Bayesian tool equipped with the adjustment for density maximization estimates random effects and hyper-parameters in the conjugate prior distributions.
 As for the Binomial model, the package has an option to draw their posterior samples via the acceptance-rejection method.
 The main goal of \pkg{Rgb} is to produce  Bayesian interval estimates for the random effects that meet their nominal confidence levels.
-For this purpose, our models adopt unique improper hyper-prior distributions.
-\pkg{Rgbp} provides a quick way to check whether the resulting Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
+For this purpose, we adopt unique improper hyper-prior distributions.
+\pkg{Rgbp} provides a tool to check quickly whether the resulting Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
 % and evaluates repeated sampling frequency property of the resulting approximate Bayesian interval estimates for random effects
@@
 To account for this extra-variability, called overdispersion, a  two-level conjugate hierarchical model regards first-level mean parameters as random effects that come from a population-level conjugate prior distribution.
-The conjugate prior distribution is non-exchangeable if the model incorporates covariate information of each group via a linear, log-linear, or logistic regression according to the data type, and exchangeable if no covariates are available with only an intercept term for the regression.
-
-With an assumption of homogeneity within each group, the observed data are sufficient statistics for the random effects; each group's sample mean for the Gaussian model, each group's number of outcomes happening given some exposure for the Poisson data, and each group's number of successful outcomes out of total number of trials for the Binomial model.
-The data may contain each group's covariate information, though they do not use the population-level data.
-This type of  data is common for a biological analysis on litter data, a meta analysis on independent studies, or small area estimation problems.
+
+%The conjugate prior distribution is non-exchangeable if the model incorporates covariate information of each group via a linear, log-linear, or logistic regression according to the data type, and exchangeable if no covariates are available with only an intercept term for the regression.
+
+With an assumption of homogeneity within each group, the observed data are sufficient statistics for the random effects without the population-level data; each group's sample mean for the Gaussian model, each group's number of outcomes happening given some exposure for the Poisson data, and each group's number of successful outcomes out of total number of trials for the Binomial model.
+The data may contain each group's covariate information.
+This type of  data is common for a biological analysis on litter data \citep{tamura1987stabilized}, a meta analysis on independent studies \citep{gelman2014bayesian}, or small area estimation problems \citep{rao2003small}.
 For these data with  homogeneity within each group, the two-level model that \pkg{Rgbp} assumes can be considered as a conjugate hierarchical generalized linear model \citep{lee1996hierarchical, hglm2006} where each random effect has a conjugate prior distribution.
@@
 When it comes to fitting the model, \pkg{Rgbp} adopts the adjustment for density maximization \citep{carl1988, morris1997, tang2011} (ADM), a Pearson family approximation via maximization.
-For example, a Delta method is a Gaussian case of the ADM that uses a Normal distribution to obtain an approximate distribution of a function of a parameter with its MLE and observed information plugged-in.
+For example, a Delta method is a Gaussian case of the ADM that uses a Normal distribution to obtain an approximate distribution of a function of a parameter with its MLE and negative Hessian at the MLE plugged-in.
 In this article, the ADM uses Beta distributions mainly to approximate the posterior distributions of shrinkage factors, functions of the second-level variance component, via maximization.
@@
 
-For the Binomial  hierarchical model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters including random effects via an acceptance-rejection method instead of the approximate Bayesian tool.
-
-In addition to fitting hierarchical models, \pkg{Rgbp} provides a quick way to evaluate the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects \citep{morris1997, daniels1999prior, tang2002fitting, tang2011, morris2012}.
+For the Binomial  hierarchical model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters including random effects via an acceptance-rejection method \citep{everson2000inference, tang2002fitting} instead of the approximate Bayesian tool.
+
+In addition to fitting hierarchical models, \pkg{Rgbp} evaluates the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects \citep{morris1997, daniels1999prior, tang2002fitting, tang2011, morris2012}.
 It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for hierarchical modeling such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models and \pkg{arm} \citep{gelman2014arm} for Bayesian hierarchical regression models.
@@
 
-Also, our parametrization of the three hierarchical models leads to an intuitive shrinkage interpretation in inference and  facilitates the estimation procedure because the shrinkage factors under our parametrization are a function of only a second-level variance component.
+Our parametrization of the three hierarchical models leads to an intuitive shrinkage interpretation in inference and  facilitates the estimation procedure because the shrinkage factors under our parametrization are a function of only a second-level variance component.
 
@@
 where $y_j$ is an observed unbiased estimate, e.g., sample mean, for random effect $\mu_j$, $V_{j}$ is a completely known standard error of $y_j$, $\mu^E_{j}$ is an expected random effect defined as $\E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$, and $m$ is the number of regression coefficients to be estimated.
-\pkg{Rgbp} sets $x_{j, 1}$ to 1 for an intercept term as a default, providing a usage without the intercept term, too.
+\pkg{Rgbp} sets $x_{j, 1}$ to 1 for an intercept term as a default.
+It also provides a usage without the intercept term.
 It is assumed that the second-level variance $A$ is unknown and that the $m\times1$ regression coefficient vector $\boldsymbol{\beta}$ is also unknown unless otherwise specified.
 If no covariates are available with an intercept term, then $\boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_1$ ($m=1$) and thus $\mu^E_{j}=\mu^E=\beta_1$ for all $j$, resulting in an exchangeable conjugate prior distribution for the random effects.
-Based on these conjugate prior distributions for random effects, it is easy to derive the conditional posterior distributions of each random effect.
+Based on these conjugate prior distributions for random effects, it is easy to derive the conditional posterior distribution of each random effect.
 For $j=1, 2, \ldots, k$,
@@
 Note that the conditional posterior mean $\E(\mu_{j}\vert \boldsymbol{\beta}, A, \boldsymbol{y} )$, denoted by $\mu^\ast_j$,  is a convex combination of the observed sample mean $y_j$ and the expected random effect $\mu^E_j$ weighted by the shrinkage factor $B_j$.
-If the variance of the conjugate prior distribution, $A$, is smaller than the variance of the observed distribution, $V_j$, then we expect the posterior mean to borrow more information from the more accurate second-level conjugate prior distribution.
+If the variance of the conjugate prior distribution, $A$, is smaller than the variance of the observed distribution, $V_j$, then we expect the posterior mean to borrow more information from the second-level conjugate prior distribution.
 
@@
 \end{align}
-where $y_j$ is the number of events happening, $n_{j}$ is the exposure of group $j$, which is not necessarily an integer, $\lambda^E=\E(\lambda_j\vert r)$ is the known expected random effect, and $r$ is the unknown second-level variance component.
+where $y_j$ is the number of events happening, $n_{j}$ is the exposure of group $j$, which is not necessarily an integer, $\lambda^E=\E(\lambda_j\vert r)$ is the known expected random effect ($m=0$), and $r$ is the unknown second-level variance component.
 The mean and variance of the conjugate Gamma prior distribution are $\lambda^E$ and $\lambda^E/r$, respectively.
-We interpret $r$ as the amount of prior information as $n_{j}$ represents the amount of observed information because the uncertainty of the conjugate prior distribution increases as $r$ decreases and vice versa.
+\cite{albert1988computational} interprets $r$ as the amount of prior information as $n_{j}$ represents the amount of observed information because the uncertainty of the conjugate prior distribution increases as $r$ decreases and vice versa.
 The conditional posterior distribution of the random effect $\lambda_j$ for this Poisson model is
 \begin{equation} \label{gammapost}
-\lambda_j\vert r, \boldsymbol{y} \stackrel{indep.}{\sim}\textrm{Gamma}(r\lambda^E + n_j\bar{y}_{j},~ r + n_j),
+\lambda_j\vert r, \boldsymbol{y} \stackrel{\textrm{indep.}}{\sim}\textrm{Gamma}(r\lambda^E + n_j\bar{y}_{j},~ r + n_j),
 \end{equation}  
@@
 
-Note that the conditional posterior variance in  \eqref{gammapost_mean_var} is linear in the conditional posterior mean, whereas a slightly different Poisson-Gamma model specification has been used elsewhere \citep{morris1997} that makes the variances  quadratic functions of their means.
-The parametrization of the Poisson model adopted in \pkg{Rgbp} makes shrinkage factors as a function of only the hyper-parameter $r$, while the shrinkage factors based on the parametrization in \cite{morris1997} are functions of both $r$ and $\boldsymbol{\beta}$.
-%Thus, the estimation for shrinkage factors is easier and the interpretation of the shrinkage factors are more intuitive under the parametrization in \pkg{Rgbp}.
+Note that the conditional posterior variance in  \eqref{gammapost_mean_var} is linear in the conditional posterior mean, whereas a slightly different Poisson-Gamma model specification has been used elsewhere \citep{morris1997} that makes the variances  quadratic functions of means.
+
+%Moreover, the parametrization of the Poisson model that we adopt in \pkg{Rgbp} makes shrinkage factors as a function of only the hyper-parameter $r$, while the shrinkage factors based on the parametrization in \cite{morris1997} are functions of both $r$ and $\boldsymbol{\beta}$.
+Thus, the estimation for shrinkage factors is easier and the interpretation of the shrinkage factors are more intuitive under the parametrization in \pkg{Rgbp}.
 %in the prior and conditional posterior distributions
@@
 \subsection[Hyper-prior distributions]{Hyper-prior distribution}
-Hyper-prior distributions are the distributions assigned to the second-level parameters called hyper-parameters. Our choice for the hyper-prior distributions is
+Hyper-prior distributions are the distributions assigned to the second-level parameters called hyper-parameters. Our choices for the hyper-prior distributions are
 \begin{equation}\label{eq:hyper}
@@
 In the other two cases, Poisson and Binomial, the flat prior distribution on $1/r$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with the Uniform($0, \infty$) for the Gaussian case.
-The Poisson model with this hyper-prior distribution on $r$, i.e., $dr/r^2$,  provides posterior propriety if there are at least two groups whose observed values $y_j$ are non-zero  and the expected random effect, $\lambda^E$, is a completely known constant ($m=0$), see Appendix \ref{propriety_poisson} for its proof.
-If $\lambda^E$ is unknown,  we recommend using the Binomial model with the same hyper-prior distributions because the Poisson model is actually an approximation to the Binomial model when $n_j$ is large and $p_j$ is small.
+The Poisson model with this hyper-prior distribution on $r$, i.e., $dr/r^2$,  provides posterior propriety if there are at least two groups whose observed values $y_j$ are non-zero  and the expected random effect, $\lambda^E$, is a completely known constant ($m=0$); see Appendix \ref{propriety_poisson} for its proof.
+If $\lambda^E$ is unknown,  we recommend using the Binomial model with the same hyper-prior distributions because the Poisson model is  an approximation to the Binomial model when $n_j$ is large and $p_j$ is small.
 
 As for posterior propriety of the Binomial model, let's define an ``interior group'' as the group whose number of successes $y_j$ are neither 0 nor $n_j$, and $k_y$ as the number of interior groups among $k$ groups.
-The full posterior distribution of random effects and hyper-parameters is proper if and only if there are at least two interior groups in the data and the $k_y\times m$ covariate matrix of the interior groups is of full rank $m$ \citep{tak2016propriety}.
+The full posterior distribution of random effects and hyper-parameters is proper if and only if there are at least two interior groups in the data and the $k_y\times m$ covariate matrix of the interior groups is of full rank $m$ ($k_y\ge m$) \citep{tak2016propriety}.
 
@@
 \begin{equation}\label{marginal_post_normal}
-f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L(A, \boldsymbol{\boldsymbol{\beta}})dAd\boldsymbol{\beta}.
+f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L_g(A, \boldsymbol{\boldsymbol{\beta}})dAd\boldsymbol{\beta}.
 \end{equation}
@@
 where the notation $B(a, b)~(\equiv\int_0^1 v^{a-1}(1-v)^{b-1}dv)$ indicates a beta function for positive constants $a$ and $b$.
-The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial  model is proportional to their likelihood function in \eqref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in  \eqref{eq:hyper} as follows;
+The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial  model is proportional to their likelihood function in \eqref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in  \eqref{eq:hyper};
 \begin{equation}\label{marginal_post_binomial}
@@
 
-Similarly, the likelihood function of $r$ for the Poisson  model  comes from the independent Negative-Binomial marginal distributions of the observed data with the random effects integrated out;
+Similarly, the likelihood function of $r$ for the Poisson  model  comes from the independent Negative-Binomial  distributions of the observed data with the random effects integrated out;
 \begin{equation}\label{marginal_poisson}
@@
 where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}\exp(x)dx$ for a positive constant $a$.
-The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in  \eqref{marginal_poisson} times the hyper-prior density function of $r$, i.e., $dr/r^2$;
+The posterior density function of $r$, $f_{\textrm{hyp.post}}(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in  \eqref{marginal_poisson} times the hyper-prior density function of $r$, i.e., $dr/r^2$;
 \begin{equation}\label{marginal_post_poisson}
-f(r \vert \boldsymbol{y})\propto L(r)dr/r^2.
+f(r \vert \boldsymbol{y})\propto L_p(r)dr/r^2.
 \end{equation}
@@
 
-In this section, we illustrate our estimation procedure equipped with the adjustment for density maximization (ADM) \citep{carl1988, morris1997, tang2011}, a way to  approximate a distribution of the parameter of interest by one of Pearson family distributions based on derivatives.
-Because the ADM procedure for the Gaussian model adopted in \pkg{Rgbp} is well documented in \cite{kelly2014advances}, we describe  the ADM procedure  based mainly on the Poisson and Binomial model.
+In this section, we illustrate our estimation procedure equipped with the adjustment for density maximization (ADM) \citep{carl1988, morris1997, tang2011}, a way to  approximate a distribution of the parameter of interest by one of Pearson family distributions via maximization.
+Because the ADM procedure for the Gaussian model adopted in \pkg{Rgbp} is well documented in \cite{kelly2014advances}, we describe  the ADM procedure  using the Poisson and Binomial model.
 
@@
 The ADM works on an adjusted posterior distribution $f^A(B_j\vert \boldsymbol{y})dB_j\propto B_j(1-B_j)f(B_j\vert \boldsymbol{y})dB_j$ so that the mode of $f^A(B_j\vert \boldsymbol{y})$ is the same as the mean of the original Beta distribution.
-The assumed posterior mean and variance of the shrinkage factor are
+The assumed posterior mean and variance of the $j$th shrinkage factor are
 \begin{align}
@@
 
-Considering that  \eqref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-\log(r)$ (or $\alpha=\log(A)$ for the Gaussian model), because the distribution of $\alpha$ is more symmetric than that of $r$, and $\alpha$ is defined on a real line without any boundary issues.
+Considering that  \eqref{admmean} and  \eqref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-\log(r)$ (or $\alpha=\log(A)$ for the Gaussian model), because the distribution of $\alpha$ is more symmetric than that of $r$, and $\alpha$ is defined on a real line without any boundary issues.
 Because $f^A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto \exp(\alpha) L(\alpha)d\alpha$ \citep{tang2011}, the  posterior mean in  \eqref{admmean} is estimated by
@@
 
-The distributional approximation of the ADM gets better if the true posterior distribution of the shrinkage factor is closer to the Beta distribution \citep{carl1988, morris1997, tang2011, morris2012}.
+The ADM approximation to the shrinkage factors via Beta distributions is empirically proven to be more accurate than a Laplace approximation \citep{carl1988, morris1997, tang2011, morris2012}.
 
@@
 \end{equation}
-Instead of averaging over $r$, we estimate the unconditional posterior moments by the conditional posterior moments with $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.
+Instead of averaging over $r$, we approximate the unconditional posterior moments by the conditional posterior moments with $\hat{r}=\exp(-\hat{\alpha})$ plugged-in \citep{kass1989approximate}.
 %We estimate the unconditional posterior moments by the estimated conditional posterior moments that we obtain from the conditional posterior distribution of $\mu^E_j\vert A, \boldsymbol{y}$ or that of $p^E_j\vert r, \boldsymbol{y}$ with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.
@@
 \begin{equation}\label{priormoment1}
-\E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\boldsymbol{\beta},
-\end{equation}
-which is not an easy integration. Thus, we use another ADM, assuming the conditional posterior distribution of each expected random effect is a Beta distribution as follows;
+\E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\boldsymbol{\beta}.
+\end{equation}
+Thus, we use another ADM, assuming the conditional posterior distribution of each expected random effect is a Beta distribution as follows;
 \begin{equation}\label{admpriormean}
@@
 
-In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$ follows a Normal distribution with mean $\hat{\boldsymbol{\beta}}$ and variance-covariance matrix $\hat{\Sigma}$, where $\hat{\boldsymbol{\beta}}$ is the mode of $f(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is an inversed negative Hessian matrix at the mode.
+In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$ follows a Normal distribution with mean $\hat{\boldsymbol{\beta}}$ and variance-covariance matrix $\hat{\Sigma}$, where $\hat{\boldsymbol{\beta}}$ is the mode of $f(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is an inverse of the negative Hessian matrix at the mode.
 Thus, the posterior distribution of $x_j^\top\boldsymbol{\beta}$ is also Normal with mean $x_j^\top\hat{\boldsymbol{\beta}}$ and variance $x_j^\top\hat{\Sigma} x_j$.
@@
 
-We estimate the values of $b_{1j}$ and $b_{0j}$  by matching them to the estimated  mean and variance in  \eqref{priormean2} and \eqref{priorvariance2};
+We estimate the values of $b_{1j}$ and $b_{0j}$  by matching them to the estimated unconditional posterior mean and variance of $\exp(x_j^\top\boldsymbol{\beta})$ in  \eqref{priormean2} and \eqref{priorvariance2};
 \begin{equation}\label{priormeanpara}
@@
 Finally, we estimate the unconditional posterior moments of the expected random effects, $\E((p^E_{j})^c\vert\boldsymbol{y})$, by $\hat{\E}((p^E_{j})^c\vert\hat{\alpha}, \boldsymbol{y})=B(\hat{b}_{1j} + c, \hat{b}_{0j})/B(\hat{b}_{1j}, \hat{b}_{0j})$ for $c\ge0$.
+
+The ADM approximation to a log-Normal density via a F$^\ast$ distribution (represented by a ratio of two independent Gamma random variables) is known to be more accurate than the Laplace approximation \citep{carl1988}.
 %\begin{equation}\label{priormeanmoments}
@@
 \subsection{Estimation for random effects}
-It is intractable to derive analytically the unconditional posterior distribution of each random effect  for the three models, which motivates us to assume again that each random effect has a skewed Normal distribution \citep{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
+It is intractable to derive analytically the unconditional posterior distribution of each random effect  for the three models.
+This motivates us to use the ADM again by assuming that each random effect has a skewed Normal distribution \citep{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
 \begin{align}
@@
 \cite{kelly2014advances} uses  the results derived in \cite{azzalini1985class}, i.e., $\E(\mu_j\vert \boldsymbol{y}) =\phi+\omega\delta\sqrt{2/\pi}$, Var$(\mu_j\vert \boldsymbol{y})=\omega^2(1-2\delta^2/\pi)$, and Skewness$(\mu_j\vert \boldsymbol{y})=(4-\pi)\delta^3/[2(\pi/2-\delta^2)^{3/2}]$, and estimates three parameters of the skewed-Normal distribution using  three approximately estimated unconditional posterior  moments of each random effect; see \cite{kelly2014advances} for details.
-\cite{kelly2014advances} also shows that the skewed-Normal approximation improves a Normal approximation ($\mu_j\vert\boldsymbol{y}\sim \textrm{Normal}$) used in  \cite{tang2011, morris2012} in terms of the repeated sampling coverage properties of random effects.
+\cite{kelly2014advances} also shows that the skewed-Normal approximation improves a Normal approximation ($\mu_j\vert\boldsymbol{y}\sim \textrm{Normal}$) used in  \citet{tang2011} and \cite{morris2012} in terms of the repeated sampling coverage properties of random effects.
 
@@
 ~~~~~~\VAR(p_{j}\vert \boldsymbol{y}) &=  \E(\VAR(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+\VAR(\E(p_{j}\vert r, \boldsymbol{\beta},\boldsymbol{y})\vert \boldsymbol{y})\label{postvar}\\
-&= E\big(p^{\ast}_{j}(1-p^{\ast}_{j})/ (r+n_{j}+1)\vert  \boldsymbol{y}\big)+\VAR\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big) \\
-&\approx E\big(p^{\ast}_{j}(1-p^{\ast}_{j})(1-\textrm{B}_{j})/n_{i}\vert \boldsymbol{y}\big)+\VAR\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big)\\
-&=h(\E(B_j\vert\boldsymbol{y}), \E(B^2_j\vert\boldsymbol{y}), \E(B^3_j\vert\boldsymbol{y}),  \E(p^E_{j}\vert\boldsymbol{y}), \E((p^E_{j})^2\vert\boldsymbol{y})),\label{approximate_var}
+&= \E\big(p^{\ast}_{j}(1-p^{\ast}_{j})/ (r+n_{j}+1)\vert  \boldsymbol{y}\big)+\VAR\big(B_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big) \\
+&\approx \E\big(p^{\ast}_{j}(1-p^{\ast}_{j})(1-B_{j})/n_{i}\vert \boldsymbol{y}\big)+\VAR\big(B_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big)\label{taylor}\\
+&=\big\{(1-\bar{y}_j)\bar{y}_j[1-\E(B_j\vert \boldsymbol{y})]+(2\bar{y}_j-1)\E(B_j(1-B_j) \vert \boldsymbol{y})(\bar{y}_j-\E(p^E_j\vert\boldsymbol{y}))\nonumber\\
+&~~~~+\E(B_j^2(1-B_j) \vert \boldsymbol{y})\E((\bar{y}_j-p^E_j)^2\vert\boldsymbol{y})\big\}/n_j+\VAR\big(B_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big),\label{approximate_var}
 \end{align}
-where the function $h$ in the last equation is specified in Appendix \ref{apppostvar}.
+where the approximation in \eqref{taylor} is a first-order Taylor approximation.
 By plugging-in the estimated unconditional posterior moments of shrinkage factors and those of expected random effect into   \eqref{postmean_binom} and \eqref{approximate_var}, we obtain the estimates of the unconditional posterior mean and variance of each random effect, denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
@@
 \VAR(\lambda_{j}\vert \boldsymbol{y}) &=  \E(\VAR(\lambda_{j}\vert r,  \boldsymbol{y})\vert \boldsymbol{y})+\VAR(\E(\lambda_{j}\vert r, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_poisson}\\
-&= E\big(\lambda^{\ast}_{j}/ (r+n_{j})\vert  \boldsymbol{y}\big)+\VAR\big(\textrm{B}_{j}(\bar{y}_{j}-\lambda^E_{j})\vert \boldsymbol{y}\big) \\
-&=\frac{1}{n_j}\left[\bar{y}_j\E\left((1-B_j)^2\vert \boldsymbol{y}\right)+\lambda^E\E\left((1-B_j)B_j\vert \boldsymbol{y}\right)\right]+(\bar{y}_{j}-\lambda^E_{j})^2\VAR\big(\textrm{B}_{j}\vert \boldsymbol{y}\big).\label{approximate_var_poisson}
+&= \E\big(\lambda^{\ast}_{j}/ (r+n_{j})\vert  \boldsymbol{y}\big)+\VAR\big(B_{j}(\bar{y}_{j}-\lambda^E_{j})\vert \boldsymbol{y}\big) \\
+&=\frac{1}{n_j}\left[\bar{y}_j\E\left((1-B_j)^2\vert \boldsymbol{y}\right)+\lambda^E\E\left((1-B_j)B_j\vert \boldsymbol{y}\right)\right]+(\bar{y}_{j}-\lambda^E_{j})^2\VAR\big(B_{j}\vert \boldsymbol{y}\big).\label{approximate_var_poisson}
 \end{align}
@@
 \end{equation}
-Our point and interval estimates of each random effect are the  mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the assumed unconditional posterior distribution in  \eqref{trueapprox_normal}, \ref{trueapprox_binomial}, or \ref{trueapprox_poisson} depending on the type of data.
+Our point and interval estimates of each random effect are the  mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the assumed unconditional posterior distribution in  \eqref{trueapprox_normal}, \eqref{trueapprox_binomial}, or \eqref{trueapprox_poisson} depending on the type of data.
 
@@
 As for the Binomial model, the package \pkg{Rgbp} also provides a way to draw  posterior samples of random effects and hyper-parameters via the acceptance-rejection (A-R) method.
+Unlike the approximate Bayesian machinery specified in the previous section, this method does not assume that hyper-parameters are independent \emph{a posteriori}.
 We continue working on a logarithmic scale of $r$, i.e., $\alpha=\log(1/r)$.
@@
 \begin{equation}
-f(\alpha, \boldsymbol{\beta} \vert \boldsymbol{y})\propto f(\alpha, \boldsymbol{\beta})L(\alpha, \boldsymbol{\beta})\propto \exp(\alpha)L(\alpha, \boldsymbol{\beta})d\alpha d\boldsymbol{\beta}.
-\end{equation}
-
-The A-R method \citep{everson2000inference, tang2002fitting} is useful when it is difficult to sample a parameter of interest $\theta$ directly from its target probability density $f(\theta)$, which is known up to a normalizing constant, but an easy-to-sample envelope function $g(\theta)$ is available.
+f(\alpha, \boldsymbol{\beta} \vert \boldsymbol{y})\propto f(\alpha, \boldsymbol{\beta})L(\alpha, \boldsymbol{\beta})\propto \exp(\alpha)L_b(\alpha, \boldsymbol{\beta})d\alpha d\boldsymbol{\beta}.
+\end{equation}
+
+The A-R method \citep{everson2000inference, tang2002fitting, robert2013monte} is useful when it is difficult to sample a parameter of interest $\theta$ directly from its target probability density $f(\theta)$, which is known up to a normalizing constant, but an easy-to-sample envelope function $g(\theta)$ is available.
 The A-R method samples $\theta$  from the envelope $g(\theta)$ and accepts it with a probability $\frac{f(\theta)}{Mg(\theta)}$, where $M$ is a constant making $f(\theta)/g(\theta)\le M$ for all $\theta$.
@@
 We accept each pair of $(\alpha^{(i)}, \boldsymbol{\beta}^{(i)})$ with a probability $w_i/M$ where $M$ is set to the maximum of all the $4N$ weights.
-The typical acceptance rates from  our data examples are around 27\%.
 In a case where we accept more than the desired number of samples $N$, we discard the redundant.
 If the number of accepted samples is smaller than $N$, then we additionally sample  6 times more pairs than the shortage and calculate a new maximum $M'$ from all the previous and new weights, accepting or rejecting the entire pairs again with new probabilities $w_i/M'$.
+
+% The typical acceptance rates from  our data examples are around 27\%.
 
@@
 %\end{figure}
+%f_{\textrm{rand.post}}(\boldsymbol{p}\vert \boldsymbol{y})=\int  f_{\textrm{rand.cond.post}}(\boldsymbol{p}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\cdot f_{\textrm{hyp.post}}(r, \boldsymbol{\beta}\vert \boldsymbol{y})dr d\boldsymbol{\beta},
 
@@
 A \emph{frequency method checking} is a procedure to evaluate it, which is different from a model checking that tests whether a two-level model is appropriate for data  \citep{dean1992testing, modelchecking1996}.
-Conditioning that the two-level model is appropriate, the frequency method checking generates pseudo-data sets given specific values of hyper-parameters (a parametric bootstrapping) and estimates unknown coverage probabilities based on these mock data sets.
-We will describe the frequency method checking based on the Gaussian model because the idea can be easily applied to the other two models.
+Conditioning that the two-level model is appropriate, the frequency method checking generates pseudo-data sets given specific values of hyper-parameters  and estimates unknown coverage probabilities based on these mock data sets (a parametric bootstrapping).
+We  describe the frequency method checking based on the Gaussian model because the idea can be easily applied to the other two models.
 
@@
 After fitting the Gaussian model on each simulated data set, we obtain interval estimates of random effects $\boldsymbol{\mu}$.
-Let $(\hat{\mu}^{(i)}_{j, ~\textrm{low}}, ~\hat{\mu}^{(i)}_{j, ~\textrm{upp}})$ represent the lower and upper bounds of the interval estimate of random effect $j$ based on the $i$-th simulated data set given a specific confidence level.
+Let $(\hat{\mu}^{(i)}_{j, ~\textrm{low}}, ~\hat{\mu}^{(i)}_{j, ~\textrm{upp}})$ represent the lower and upper bounds of the interval estimate of random effect $j$ based on the $i$-th simulation given a specific confidence level.
 Let's define a coverage indicator of random effect $j$ on the $i$-th mock data set as
@@
 \end{equation}
-We consider the coverage indicators as functions of $A$ and $\boldsymbol{\beta}$ because outcomes of indicators depend on the simulated random effects and mock data generated by these hyper-parameters.
+Note that an outcome of the coverage indicator depends on the simulated random effects and mock data generated by $A$ and $\boldsymbol{\beta}$.
 
@@
 Note that $\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)$ averages over possible values of $\mu_{j}$ and $y_{j}$ generated by specific values of $A$ and $\boldsymbol{\beta}$.
-
- %true coverage probability for the $j$th group depending on specific values of $(r, \boldsymbol{\beta})$. 
-%For reference, even if we sample $L$ datasets per one parameter set, $L\cdot N_{\textrm{sim}}$ indicators $I^{(i, l)}_{j}, i = 1, \ldots, N_{\textrm{sim}}, l = 1, \ldots, L$, have still $iid$ Bernoulli($p_{cov, j}$) distribution.
-
 For $j=1, 2, \ldots, k$, the unbiased variance estimator of $\VAR(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))$ is
@@
 The argument \code{X} is a matrix of covariate(s) each column of which corresponds to one covariate for $k$ groups.
-For example, if we have two covariates for each group, the argument \code{X} must be $k\times2$ matrix to estimate three regression coefficients $\boldsymbol{\beta}=(\beta_1, \beta_2, \beta_3)$ including an intercept term as a default.
-If we do not want to include an intercept term, estimating two regression coefficients for the two covariates, we add an optional argument \code{intercept} as follows.
+For example, if we have two covariates for each group, the argument \code{X} must be $k\times2$ matrix to estimate three regression coefficients $\boldsymbol{\beta}=(\beta_1, \beta_2, \beta_3)$ including an intercept term, $\beta_1$, as a default.
+If we do not want to include an intercept term ($\beta_1=0$), estimating two regression coefficients for the two covariates, we add an optional argument \code{intercept} as follows.
 \begin{CodeChunk}
@@
 The argument \code{Alpha}, whose default value is 0.95, sets the confidence level, producing $100\times$\code{Alpha}\% interval estimates for the random effects.
-For the Gaussian model, setting the argument \code{normal.CI} to \code{TRUE} lets the function \code{gbp}  use a Normal approximation to the unconditional posterior distribution of the random effect \citep{tang2011}.
+For the Gaussian model, setting the argument \code{normal.CI} to \code{TRUE} lets \code{gbp}  use a Normal approximation to the unconditional posterior distribution of the random effect \citep{tang2011}.
 The default value of \code{normal.CI} is \code{FALSE} for the skewed-Normal approximation \citep{kelly2014advances}.
@@
 The argument \code{save.result} indicates whether we save the whole posterior samples of the random effects and hyper-parameters; its default value is \code{TRUE}.
-The two arguments \code{t} and \code{u}, taking on positive values, allow users to chose the joint hyper-prior distribution $f(r, \boldsymbol{\beta})\propto d\boldsymbol{\beta}dr/(t+r)^{u+1}$; the default values for \code{t} and \code{u} are 0 and 1, respectively, for the joint hyper-prior distribution specified in  \eqref{eq:hyper}.
+The two arguments \code{t} and \code{u}, taking on positive values, allow users to choose the joint hyper-prior distribution $f(r, \boldsymbol{\beta})\propto d\boldsymbol{\beta}dr/(t+r)^{u+1}$; the default values for \code{t} and \code{u} are 0 and 1, respectively, for the joint hyper-prior distribution specified in  \eqref{eq:hyper}.
 
@@
 
-The object \code{b.output} above contains detailed outcomes.
-The function \code{names} will show the list of outcomes (too many to be listed here); see the document of \code{gbp} to check the details of the items saved as follows.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> names(b.output)
-R> ?gbp
-\end{CodeInput}
-\end{CodeChunk}
+The object \code{b.output} above contains 8,000 weights (\code{b.output$weight}), 2,000 posterior samples of $\alpha$ (\code{b.output$alpha}), a $2,000\times3$ matrix of $\beta$ (\code{b.output$beta})  each column of which corresponds to 2,000 posterior samples of each regression coefficient, and a $k\times2,000$ matrix of random effects (\code{b.output$p}) each row of which has posterior samples of each random effect.
+
+%The function \code{names} shows the list of outcomes (too many to be listed here); see the document of \code{gbp} to check the detailed list of outcomes.
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%R> names(b.output)
+%R> ?gbp
+%\end{CodeInput}
+%\end{CodeChunk}
 
@@
 The function \code{plot} draws a shrinkage plot and $100\times$\code{Alpha}\% interval plot for random effects with its default argument ``\code{sort = TRUE}'' that draws the $100\times$\code{Alpha}\% interval plot in the ascending order of $n$ for the Binomial and Poisson model and the descending order of standard errors for the Gaussian model.
-When the argument \code{sort} is set to \code{FALSE}  the $100\times$\code{Alpha}\% interval plot will be plotted in the order of data input.
+When the argument \code{sort} is set to \code{FALSE}  the $100\times$\code{Alpha}\% interval plot is displayed in the order of data input.
 \begin{CodeChunk}
@@
 
-The argument \code{nsim} sets the number of simulations, $N_{\textrm{sim}}$.
+The argument \code{nsim} sets the number of simulations, $N_{\textrm{sim}}$, defined in Section \ref{data_generation}.
 If we do not assign values of the hyper-parameters through the arguments \code{A.or.r} and \code{reg.coef}, then the function \code{coverage} automatically sets the estimated posterior modes of hyper-parameters saved in the ``gbp'' object (or their posterior medians if the acceptance-rejection method for the Binomial model is used) as the generative values of hyper-parameters.
@@
 
-When we fit a model with a known value of the expected random effect, the code \code{coverage} conducts the frequency method checking based on the known value.
+When we fit a model with a known value of the expected random effect, \code{coverage} conducts the frequency method checking based on the known value.
 However, we may sometimes want to conduct the frequency method checking with a different value for the expected random effect.
@@
 \end{CodeChunk}
-The frequency method checking will be based on the estimated posterior mode of $r$ and the newly specified value of the expected random effect, 30.
+The resulting frequency method checking is based on the estimated posterior mode of $r$ and the newly specified value of the expected random effect, 30.
 
 Although the function \code{coverage} does not produce an S3 object, a detailed summary appears in a plot that automatically pops up.
-In addition, the object \code{cov} that we used to save the result of \code{coverage} as above contains numerical details.
-We can use the function \code{names} or check the document of \code{coverage} to see the list of numerical details.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> names(cov)
-R> ?coverage
-\end{CodeInput}
-\end{CodeChunk}
+In addition, the variable \code{cov}  where we save  the result of \code{coverage} as above contains numerical details; $k$ RB coverage estimates (\code{cov$coverageRB}) and their standard errors (\code{cov$se.coverageRB}), $k$ simple coverage estimates (\code{cov$coverageS}) and their standard errors (\code{cov$se.coverageS}), etc.
 
@@
 The output of \code{summary} shows that $\hat{r}=\textrm{exp}(6.53)=684$, which is an indicator of how valuable and informative the second-level hierarchy is.
-It means that observed sample means of hospitals whose caseloads are less than 684 will shrink toward the prior mean (0.030) more than 50\%.
+It means that observed sample means of hospitals whose caseloads are less than 684 shrink toward the prior mean (0.030) more than 50\%.
 For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.911$) was calculated by 684 / (684 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.911)*0.0448 + 0.911 * 0.030=0.0313$.
@@
 \end{CodeChunk}
-\begin{figure}[t!] 
+\begin{figure}[h!] 
 \begin{center}
@@
 This can  be attributed to their bad luck because their observed batting averages are close to the lower bounds of their interval estimates.
-The RTTM suggests that their batting averages will shrink towards the expected random effect of outfielders (0.310) in the long run.
+The RTTM indicates that their batting averages  shrink towards the expected random effect of outfielders (0.310) in the long run.
 
@@
 \end{CodeChunk}
-The ``gbp'' object \code{b.output} contains 2,000 posterior samples of $\alpha$ (\code{b.output$alpha}), a $2,000\times2$ matrix of $\beta$ (\code{b.output$beta}) with each column corresponding to 2,000 posterior samples of each regression coefficient, and a $k\times2,000$ matrix of random effects (\code{b.output$p}) with each row contains posterior samples of each random effect.
+The ``gbp'' object \code{b.output} contains 8,000 weights (\code{b.output$weight}), 2,000 posterior samples of $\alpha$ (\code{b.output$alpha}), a $2,000\times2$ matrix of $\beta$ (\code{b.output$beta})  each column of which corresponds to 2,000 posterior samples of each regression coefficient, and a $k\times2,000$ matrix of random effects (\code{b.output$p}) each row of which has posterior samples of each random effect.
 
@@
 \section{Posterior propriety of the Poisson model}\label{propriety_poisson}
-\section{Unconditional posterior variance of the Binomial model}\label{apppostvar}
-%\section{Unconditional posterior variance of the Gaussian model}\label{apppostvar_normal}
-
-%\section{Unconditional posterior variance of the Poisson model}\label{apppostvar_poisson}
+If the posterior distribution of $r$ is proper, then the full posterior distribution of random effects and $r$ is also proper because 
+\begin{equation}
+f(\boldsymbol{\lambda}, r\vert \boldsymbol{y})=f(\boldsymbol{\lambda}\vert \boldsymbol{y})\cdot f(r\vert \boldsymbol{y}),
+\end{equation} 
+where $f(\boldsymbol{\lambda}\vert \boldsymbol{y})$ is a product of $k$ proper conditional posterior density function in \eqref{gammapost}.
+Thus, our goal is to show that $\int_0^\infty f(r\vert \boldsymbol{y})dr<\infty$;
+\begin{align}
+f(r\vert\boldsymbol{y})&\propto \frac{1}{r^2}L(r)\propto\frac{1}{r^2}\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E+y_j)}{\Gamma(r\lambda^E)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E}\\
+&=\frac{1}{r^2}\left[r^{\sum_{j=1}^ky_j}+\cdots+a_k r^{k}\right]\exp\left(-r\lambda^E\sum_{j=1}^k\log(1+n_j/r)\right)\prod_{j=1}^k\left(\frac{n_j}{n_j+r}\right)^{y_j} \label{final_post_proper},
+\end{align}
+where the polynomial function of $r$ in the bracket has constant coefficients.
+
+If there are at least two groups whose observed values $y_j$ are non-zero, then $f(r\vert\boldsymbol{y})$ goes to zero as $r$ goes to 0 due to the polynomial function of $r$ in \eqref{final_post_proper}; the following two factors in \eqref{final_post_proper} approach one.
+As $r$ becomes infinite, $f(r\vert\boldsymbol{y})$ touches zero exponentially fast due to the exponential term in the middle of \eqref{final_post_proper}.
+Thus, the integration of $f(r\vert\boldsymbol{y})$ must be finite.
 
@@
 \end{document}
-%For the Gaussian model we do not assume the posterior independence between $A$ and $\boldsymbol{\beta}$ because the conditional posterior variance of the random effect is a constant function of the conditional posterior mean, which is much simpler than that of the Binomial model.
-
-The unconditional posterior mean and variance of random effect $j$ of the Gaussian model are
-\begin{eqnarray}
-\E(\mu_j\vert \boldsymbol{y}) &=&\E(\E(\mu_{j}\vert A, \boldsymbol{\beta}, \boldsymbol{y})\vert\boldsymbol{y})=(1-\E(B_j\vert\boldsymbol{y}))y_j + \E(B_j\vert  \boldsymbol{y})\E(\mu^E_j\vert  \boldsymbol{y})\label{postmean_normal} \\
-\VAR(\mu_{j}\vert \boldsymbol{y}) &=&  \E(\VAR(\mu_{j}\vert A,  \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+\VAR(\E(\mu_{j}\vert A, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_normal}\\
-&=&  (1-V_j)\E(B_j\vert  \boldsymbol{y})+\VAR\big(\textrm{B}_{j}(y_{j}-\mu^E_{j})\vert \boldsymbol{y}\big) \\
-&=&h_g(\E(B_j\vert\boldsymbol{y}), \E(B^2_j\vert\boldsymbol{y}),  \E(\mu^E_j\vert\boldsymbol{y}), \E((\mu^E_j)^2\vert\boldsymbol{y})).\label{approximate_var_normal}
-\end{eqnarray}
-The unconditional posterior mean and variance of random effect $j$ under the Gaussian model are also functions of the unconditional posterior moments of the shrinkage factors and expected random effects.
-We specify the function $h_g$ in Appendix \ref{apppostvar_normal}.
-
-%conditional posterior means of  random effect $j$ in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are a linear function of the shrinkage factor $B_{j}$ and the conditional posterior variances in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are linear (Gaussian), quadratic (Poisson), and  approximately cubic (Binomial) functions of $B_{j}$, considering $r+n_j=n_j/(1-B_j)$.
-Thus, the unconditional posterior mean and variance of the random effect are the functions of the unconditional posterior moments of the shrinkage factors.
-
-Next, we estimate the unconditional posterior moments of the shrinkage factors after approximating their unconditional posterior distributions by Beta distributions via the ADM. 
-%Next, we estimate the unconditional posterior moments of the shrinkage factors and expected random effects after approximating their unconditional posterior distributions by Beta distributions via the ADM.

### 2015-07-24 jss/article_v3.tex
revisions

@@
 To account for this extra-variability, called overdispersion, a  two-level conjugate hierarchical model regards first-level mean parameters as random effects that come from a population-level conjugate prior distribution.
+The main  goal of our two-level conjugate modeling is to estimate these random effects for a comparison between groups.
 
@@
 
-With an assumption of homogeneity within each group, the observed data are sufficient statistics for the random effects without the population-level data; each group's sample mean for the Gaussian model, each group's number of outcomes happening given some exposure for the Poisson data, and each group's number of successful outcomes out of total number of trials for the Binomial model.
+With an assumption of homogeneity within each group, the observed data are group-level aggregate data from independent $k$ groups, composed of sufficient statistics for the random effects without the population-level data.
+Specifically, the data for the Gaussian model comprise of each group's sample mean and its standard error, those for the Poisson model have each group's number of outcomes happening given some exposure for the Poisson data, and those for the Binomial model contain each group's number of successful outcomes out of total number of trials.
 The data may contain each group's covariate information.
-This type of  data is common for a biological analysis on litter data \citep{tamura1987stabilized}, a meta analysis on independent studies \citep{gelman2014bayesian}, or small area estimation problems \citep{rao2003small}.
-For these data with  homogeneity within each group, the two-level model that \pkg{Rgbp} assumes can be considered as a conjugate hierarchical generalized linear model \citep{lee1996hierarchical, hglm2006} where each random effect has a conjugate prior distribution.
+This type of  data is common for a biological analysis on litter data \citep{tamura1987stabilized}, a meta analysis on independent studies (Chapter 5 in \cite{gelman2014bayesian}), or small area estimation problems \citep{ghosh1994small, rao2003small}.
+
+For these data with the assumption of homogeneity within each group, the two-level model that \pkg{Rgbp} assumes can be considered as a conjugate hierarchical generalized linear model (HGLM) \citep{lee1996hierarchical, hglm2006} where each random effect has a conjugate prior distribution.
+However, the HGLM mainly focuses on estimating regression coefficients to explore associations between covariates and observed data, while we are more concerned about estimating random effects.
 
@@
 In addition to fitting hierarchical models, \pkg{Rgbp} evaluates the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects \citep{morris1997, daniels1999prior, tang2002fitting, tang2011, morris2012}.
-It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for hierarchical modeling such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models and \pkg{arm} \citep{gelman2014arm} for Bayesian hierarchical regression models.
+It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for similar hierarchical modeling such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models.
 The evaluation procedure which we call ``frequency method checking'' uses a parametric bootstrapping  that generates mock data sets given the values of the hyper-parameters and estimates the coverage rates based on the generated mock data sets.
@@
 \pkg{Rgbp} allows users to choose one of three hierarchical models according to the type of data, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta models.
-Although there are possibly more hierarchical models such as Exponential-Gamma \citep{tang2002fitting}, we choose the three models because these are based on the most common data types we encounter in practice.
+Although there are possibly more hierarchical models such as Exponential-Gamma \citep{tang2002fitting}, we choose the three models because these are based on the most common data types we may encounter in practice and the conjugacy leads to a simple posterior computation.
 
@@
 \subsection[Normal-Normal]{Normal-Normal model for Gaussian data}
-The following is the Normal-Normal hierarchical model (or the Gaussian model) assumed by \pkg{Rgbp}.
+The following Normal-Normal hierarchical model (or the Gaussian model) assumed by \pkg{Rgbp} is useful when the group-level aggregate data from independent $k$ groups are continuous variables with known standard errors.
 The subscript \emph{j} below indicates the \emph{j}th group among \emph{k} groups in the dataset.
@@
 \subsection[Poisson-Gamma]{Poisson-Gamma model for Poisson data}\label{poissonsubsec}
-\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model), though its usage is limited to the case where the expected random effects are known ($m=0$).
+\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model) when the group-level aggregate data from independent $k$ groups comprise of non-negative count data without upper limitation.
+However, its usage is limited to the case where the expected random effect is known ($m=0$); we may obtain its information from the past studies or from experts.
 For $j=1, 2, \ldots, k$,
@@
 \subsection[Binomial-Beta]{Binomial-Beta model for Binomial data}
-\pkg{Rgbp} can fit a conjugate Binomial-Beta hierarchical model. Unlike the Poisson model, the expected random effect is either known ($m=0$) or unknown ($m\ge1$). For $j=1, 2, \ldots, k$,
+\pkg{Rgbp} can fit a conjugate Binomial-Beta hierarchical model when the group-level aggregate data from independent $k$ groups are composed of each group's number of successes out of total number of trials.
+Unlike the Poisson model, the expected random effect is either known ($m=0$) or unknown ($m\ge1$).
+For $j=1, 2, \ldots, k$,
 \begin{align}
@@
 \begin{align}
-\E(B_j\vert\boldsymbol{y})&=\frac{a_{1j}}{a_{1j}+a_{0j}}=\argmax_{B_j}~ f^A(B_j\vert \boldsymbol{y})\equiv B^\ast_j,\label{admmean}\\
-\VAR(B_j\vert\boldsymbol{y})&=\frac{B^\ast_j(1-B^\ast_j)}{a_{1j}+a_{0j}+1}=\frac{B^\ast_j(1-B^\ast_j)}{B^\ast_j(1-B^\ast_j)[-\frac{d^2}{dB^2_j}\log(A(B_j\vert \boldsymbol{y}))\vert_{B_j=B^\ast_j}] +1}.\label{admvar}
+\E(B_j\vert\boldsymbol{y})&=\frac{a_{1j}}{a_{1j}+a_{0j}}=\argmax_{B_j}~ f^A(B_j\vert \boldsymbol{y})\equiv B'_j,\label{admmean}\\
+\VAR(B_j\vert\boldsymbol{y})&=\frac{B'_j(1-B'_j)}{a_{1j}+a_{0j}+1}=\frac{B'_j(1-B'_j)}{B'_j(1-B'_j)[-\frac{d^2}{dB^2_j}\log(A(B_j\vert \boldsymbol{y}))\vert_{B_j=B'_j}] +1}.\label{admvar}
 \end{align}
@@
 \begin{equation}\label{meaninvariance}
-\hat{B}^\ast_j=\frac{\exp(-\hat{\alpha})}{n_j+\exp(-\hat{\alpha})},
+\hat{B}'_j=\frac{\exp(-\hat{\alpha})}{n_j+\exp(-\hat{\alpha})},
 \end{equation}
@@
 \begin{eqnarray}
-I_\textrm{inv} &\equiv& -\frac{d^2 \log(f^A(B_j\vert \boldsymbol{y}))}{d[\textrm{logit}(B_j)]^2}\bigg\vert_{B_j=\hat{B}^\ast_j}=-\frac{d^2 \log(f^A(B_j(r)\vert \boldsymbol{y}))}{d[\log(r)]^2}\bigg\vert_{r=\hat{r}}\label{invariance}\\
+I_\textrm{inv} &\equiv& -\frac{d^2 \log(f^A(B_j\vert \boldsymbol{y}))}{d[\textrm{logit}(B_j)]^2}\bigg\vert_{B_j=\hat{B}'_j}=-\frac{d^2 \log(f^A(B_j(r)\vert \boldsymbol{y}))}{d[\log(r)]^2}\bigg\vert_{r=\hat{r}}\label{invariance}\\
 &=& -\frac{d^2 \log(f^A(B_j(r(\alpha))\vert \boldsymbol{y}))}{d\alpha^2}\bigg\vert_{\alpha=\hat{\alpha}}\nonumber
@@
 \begin{equation}\label{varianceinvariance}
-\widehat{\VAR}(B_j\vert\boldsymbol{y})=\frac{\hat{B}^{\ast2}_j(1-\hat{B}^\ast_j)^2}{I_\textrm{inv} +\hat{B}^\ast_j(1-\hat{B}^\ast_j)}.
+\widehat{\VAR}(B_j\vert\boldsymbol{y})=\frac{(\hat{B}'_j)^2(1-\hat{B}'_j)^2}{I_\textrm{inv} +\hat{B}'_j(1-\hat{B}'_j)}.
 \end{equation}
@@
 \begin{equation}\label{admpara}
-\hat{a}_{1j}=\frac{I_\textrm{inv}}{1-\hat{B}^\ast_j}~~\textrm{and}~~\hat{a}_{0j}=\frac{I_\textrm{inv}}{\hat{B}^\ast_j}.
+\hat{a}_{1j}=\frac{I_\textrm{inv}}{1-\hat{B}'_j}~~\textrm{and}~~\hat{a}_{0j}=\frac{I_\textrm{inv}}{\hat{B}'_j}.
 \end{equation}
@@
 
-The ADM approximation to a log-Normal density via a F$^\ast$ distribution (represented by a ratio of two independent Gamma random variables) is known to be more accurate than the Laplace approximation \citep{carl1988}.
+The ADM approximation to a log-Normal density via a F distribution (represented by a ratio of two independent Gamma random variables) is known to be more accurate than the Laplace approximation \citep{carl1988}.
 %\begin{equation}\label{priormeanmoments}
@@
 g_1(\alpha) &=& g_1(\alpha; \mu, \sigma, a, b)~\equiv~\textrm{Skewed-}t(\alpha\vert\mu, \sigma, a, b),\\
-g_2(\boldsymbol{\beta}) &=& g_2(\boldsymbol{\beta}; \boldsymbol{\mu}^\ast, S_{(m\times m)})~\equiv~t_{4}(\boldsymbol{\beta}\vert \boldsymbol{\mu}^\ast, S),\label{g2approx}
+g_2(\boldsymbol{\beta}) &=& g_2(\boldsymbol{\beta}; \boldsymbol{\xi}, S_{(m\times m)})~\equiv~t_{4}(\boldsymbol{\beta}\vert \boldsymbol{\xi}, S),\label{g2approx}
 \end{eqnarray}
@@
 \end{equation}
-The notation $t_{4}(\boldsymbol{\beta}\vert\boldsymbol{\mu}^\ast, S)$ in  \eqref{g2approx} indicates a density function of a multivariate $t$-distribution at $\boldsymbol{\beta}$ with 4 degrees of freedom, a location vector $\boldsymbol{\mu}^\ast$, and a $m\times m$ scale matrix $S$ that leads to the variance-covariance matrix $2S$.
-
-We determine the parameters of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$, i.e., $\mu$, $\sigma$, $a$, $b$, $\boldsymbol{\mu}^\ast$, and $S$, to make the product of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$ similar to the target joint posterior density $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$.
+The notation $t_{4}(\boldsymbol{\beta}\vert\boldsymbol{\xi}, S)$ in  \eqref{g2approx} indicates a density function of a multivariate $t$-distribution at $\boldsymbol{\beta}$ with 4 degrees of freedom, a location vector $\boldsymbol{\xi}$, and a $m\times m$ scale matrix $S$ that leads to the variance-covariance matrix $2S$.
+
+We determine the parameters of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$, i.e., $\mu$, $\sigma$, $a$, $b$, $\boldsymbol{\xi}$, and $S$, to make the product of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$ similar to the target joint posterior density $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$.
 First, we obtain the  mode of $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$ and the inverse of the  negative Hessian matrix at the modes, $-H^{-1}$.
@@
 
-As for $g_2(\boldsymbol{\beta})$, we matches the location vector $\boldsymbol{\mu}^\ast$ to the mode $\hat{\boldsymbol{\beta}}$ and the scale matrix $S$ to $-H^{-1}_{\hat{\boldsymbol{\beta}}}/2$ so that the variance-covariance matrix becomes $-H^{-1}_{\hat{\boldsymbol{\beta}}}$;
+As for $g_2(\boldsymbol{\beta})$, we matches the location vector $\boldsymbol{\xi}$ to the mode $\hat{\boldsymbol{\beta}}$ and the scale matrix $S$ to $-H^{-1}_{\hat{\boldsymbol{\beta}}}/2$ so that the variance-covariance matrix becomes $-H^{-1}_{\hat{\boldsymbol{\beta}}}$;
 \begin{equation}
-g_2(\boldsymbol{\beta})\equiv t_4(\boldsymbol{\beta}\vert \boldsymbol{\mu}^\ast=\hat{\boldsymbol{\beta}}, S=-H^{-1}_{\hat{\boldsymbol{\beta}}}/2).
+g_2(\boldsymbol{\beta})\equiv t_4(\boldsymbol{\beta}\vert \boldsymbol{\xi}=\hat{\boldsymbol{\beta}}, S=-H^{-1}_{\hat{\boldsymbol{\beta}}}/2).
 \end{equation}
@@
 Health care providers may use these data to improve their care qualities, and patients may refer to the data to select a better hospital.
-Our goal is to obtain the point and interval estimates for the unknown true mortality rates (random effects) of 31 hospitals to evaluate  each hospital's reliability on the CABG surgery.
+Our goal is to obtain the point and interval estimates for the unknown true mortality rates (random effects) of 31 hospitals to evaluate  each hospital's reliability on the CABG surgery (see \cite{morris1995} for the similar ranking problem).
 We interpret the caseloads, $\boldsymbol{n}$,  as exposures and assume that the state-level death rate per exposure of this surgery ($\lambda^E$) is known as 0.03 to fit the Poisson model for an illustrative purpose.

### 2015-07-27 jss/article_v4.tex
Carl revision

--- 2015-07-24 jss/article_v3.tex
@@
 
-\section[Introduction]{Introduction (v3; 2 July 2015)}
+\section[Introduction]{Introduction (v3; 27 July 2015)}
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
@@
 
-With an assumption of homogeneity within each group, the observed data are group-level aggregate data from independent $k$ groups, composed of sufficient statistics for the random effects without the population-level data.
-Specifically, the data for the Gaussian model comprise of each group's sample mean and its standard error, those for the Poisson model have each group's number of outcomes happening given some exposure for the Poisson data, and those for the Binomial model contain each group's number of successful outcomes out of total number of trials.
-The data may contain each group's covariate information.
-This type of  data is common for a biological analysis on litter data \citep{tamura1987stabilized}, a meta analysis on independent studies (Chapter 5 in \cite{gelman2014bayesian}), or small area estimation problems \citep{ghosh1994small, rao2003small}.
-
-For these data with the assumption of homogeneity within each group, the two-level model that \pkg{Rgbp} assumes can be considered as a conjugate hierarchical generalized linear model (HGLM) \citep{lee1996hierarchical, hglm2006} where each random effect has a conjugate prior distribution.
-However, the HGLM mainly focuses on estimating regression coefficients to explore associations between covariates and observed data, while we are more concerned about estimating random effects.
-
-\pkg{Rgbp} takes a Bayesian approach with our unique improper hyper-prior distributions on the parameters of the conjugate prior distribution, to produce  Bayesian interval   estimates for the random effects that achieve nominal confidence levels.
-The hyper-prior distributions lead to Stein's harmonic prior known to produce good repeated sampling coverage rates of the Bayesian interval estimates for random effects in a two-level Gaussian hierarchical model \citep{tang2011, morris2012, kelly2014advances}.
-We apply an analog to Stein's harmonic prior to Poisson and Binomial hierarchical models.
+With an assumption of homogeneity within each group, the observed data are group-level aggregate data from $k$ independent  groups, composed of sufficient statistics for their $k$ random effects without the population-level data.
+Specifically, the data for the Gaussian model comprise of each group's sample mean and its standard error, those for the Poisson model use each group's outcome count and an exposure measure, those for the Binomial model use the number of each group's  successful outcomes together with the total number of trials.
+The data analyzed by \pkg{Rgbp} may incorporate each group's covariate information.
+These types of  data are common, e.g., as for a biological analysis on litter data \citep{tamura1987stabilized}, a meta analysis on independent studies (Chapter 5 in \cite{gelman2014bayesian}), or small area estimation problems \citep{ghosh1994small, rao2003small}.
+
+For such data, assuming homogeneity within each group, \pkg{Rgbp}'s two-level model may be viewed as a conjugate hierarchical generalized linear model (HGLM) \citep{lee1996hierarchical, hglm2006} where each random effect has a conjugate prior distribution.
+However, the HGLM focuses on estimating regression coefficients to explore associations between covariates and observed data.
+While \pkg{Rgbp} does that too, its emphasis concerns making valid point and interval estimates for the $k$ random effects.
+
+\pkg{Rgbp} employs a Bayesian approach with our unique improper hyper-prior distributions placed on the second-level parameters of the conjugate prior distribution.
+The hyper-prior is chosen to produce Bayesian interval   estimates for the random effects that achieve nominal confidence levels.
+The hyper-prior distribution used in \pkg{Rgbp} is related to Stein's harmonic prior for two-level Gaussian models where it has been seen to produce good repeated sampling coverage rates for the Bayesian interval estimates for the $k$ random effects \citep{tang2011, morris2012, kelly2014advances}.
+This prior, as adapted further here for \pkg{Rgbp}'s Poisson and Binomial hierarchical models, has been seen for every data set tested thus far to meet (or exceed) the pre-assigned confidence level.
 %The main goal of our Bayesian hierarchical models is to compare random effects between groups by their Bayesian interval estimates that have good frequency properties.
 
-When it comes to fitting the model, \pkg{Rgbp} adopts the adjustment for density maximization \citep{carl1988, morris1997, tang2011} (ADM), a Pearson family approximation via maximization.
-For example, a Delta method is a Gaussian case of the ADM that uses a Normal distribution to obtain an approximate distribution of a function of a parameter with its MLE and negative Hessian at the MLE plugged-in.
-In this article, the ADM uses Beta distributions mainly to approximate the posterior distributions of shrinkage factors, functions of the second-level variance component, via maximization.
-Using the approximate Beta posterior distributions of shrinkage factors, \pkg{Rgbp} estimates the first two (three for the Gaussian case) posterior moments of the random effects.
-Finally, \pkg{Rgbp} approximates the posterior distribution of each random effect by a skewed Normal distribution for a Gaussian case, a Gamma distribution for a Poisson case, and a Beta distribution for a Binomial case whose two parameters (three for the skewed Normal distribution) are matched to the previously estimated posterior moments of the random effects.
+For fitting the hierarchical model, \pkg{Rgbp} uses ADM, i.e.
+``adjustment for density maximization'' \citep{carl1988, morris1997, tang2011}.
+ADM approximates a posterior density or a likelihood function by fitting a pre-specified (one dimensional) Pearson family, using the first two derivatives of the given function.
+When the Normal distribution is the chosen Pearson family, ADM produces exactly the same approximation as maximum likelihood estimation (MLE) does for fitting a Normal curve.
+Because shrinkage factors lie in [0,1], \pkg{Rgbp} approximates shrinkage factor distributions with Beta distributions because they are constrained to [0,1], unlike the Normal.
+
+\pkg{Rgbp} estimates the first two (actually, three in the Gaussian case) posterior moments of each random effect.
+Finally, \pkg{Rgbp} approximates the posterior distribution of each random effect by a skewed Normal distribution for Gaussian case, by a Gamma distribution for the Poisson case, and by a Beta distribution for the Binomial case.
 
@@
 
-For the Binomial  hierarchical model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters including random effects via an acceptance-rejection method \citep{everson2000inference, tang2002fitting} instead of the approximate Bayesian tool.
-
-In addition to fitting hierarchical models, \pkg{Rgbp} evaluates the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects \citep{morris1997, daniels1999prior, tang2002fitting, tang2011, morris2012}.
-It is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for similar hierarchical modeling such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models.
-The evaluation procedure which we call ``frequency method checking'' uses a parametric bootstrapping  that generates mock data sets given the values of the hyper-parameters and estimates the coverage rates based on the generated mock data sets.
+For the Binomial  hierarchical model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters, including random effects, via an acceptance-rejection method \citep{everson2000inference, tang2002fitting}.
+
+In addition to fitting the hierarchical models, \pkg{Rgbp} evaluates the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects \citep{morris1997, daniels1999prior, tang2002fitting, tang2011, morris2012}.
+This is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for similar hierarchical modeling such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models.
+The evaluation procedure which we use for this process of ``frequency method checking'' uses a parametric bootstrapping  method that many times generates mock data sets given the fitted values of the estimated hyper-parameters and uses the mock data to estimate the coverage rates.
 
@@
 In Section \ref{inference}, we explain the inferential models used to estimate the model parameters.
-We describe the estimation procedures including the ADM and the acceptance-rejection method in Section  \ref{sec3} and \ref{sec_accept}, respectively.
-We introduce the frequency method checking in Section \ref{sec4}.
-We explain the usages of main functions in \pkg{Rgbp} in Section \ref{sec5}, and apply them to three examples in Section \ref{sec6}.
+We describe the estimation procedures including  ADM and the acceptance-rejection method in Section  \ref{sec3} and \ref{sec_accept}, respectively.
+We introduce  frequency method checking techniques in Section \ref{sec4}.
+We explain the usages of \pkg{Rgbp}'s main functions in \pkg{Rgbp} in Section \ref{sec5}, and apply them to three data examples in Section \ref{sec6}.
 
@@
 \subsection[Normal-Normal]{Normal-Normal model for Gaussian data}
-The following Normal-Normal hierarchical model (or the Gaussian model) assumed by \pkg{Rgbp} is useful when the group-level aggregate data from independent $k$ groups are continuous variables with known standard errors.
+The following Normal-Normal hierarchical model (or the Gaussian model) assumed by \pkg{Rgbp} is useful when the group-level aggregate data from $k$ independent  groups are continuous variables with known standard errors.
 The subscript \emph{j} below indicates the \emph{j}th group among \emph{k} groups in the dataset.
@@
 \subsection[Poisson-Gamma]{Poisson-Gamma model for Poisson data}\label{poissonsubsec}
-\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model) when the group-level aggregate data from independent $k$ groups comprise of non-negative count data without upper limitation.
+\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model) when the group-level aggregate data from $k$ independent  groups comprise of non-negative count data without upper limitation.
 However, its usage is limited to the case where the expected random effect is known ($m=0$); we may obtain its information from the past studies or from experts.
@@
 \subsection[Binomial-Beta]{Binomial-Beta model for Binomial data}
-\pkg{Rgbp} can fit a conjugate Binomial-Beta hierarchical model when the group-level aggregate data from independent $k$ groups are composed of each group's number of successes out of total number of trials.
+\pkg{Rgbp} can fit a conjugate Binomial-Beta hierarchical model when the group-level aggregate data from $k$ independent  groups are composed of each group's number of successes out of total number of trials.
 Unlike the Poisson model, the expected random effect is either known ($m=0$) or unknown ($m\ge1$).

### 2015-07-28 jss/article_v4.tex
Joey revision

@@
 
-\section[Introduction]{Introduction (v3; 27 July 2015)}
+\section[Introduction]{Introduction (v4; 28 July 2015)}
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
@@
 \subsection[Poisson-Gamma]{Poisson-Gamma model for Poisson data}\label{poissonsubsec}
-\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model) when the group-level aggregate data from $k$ independent  groups comprise of non-negative count data without upper limitation.
+\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model) when the group-level aggregate data from $k$ independent  groups comprise of non-negative count data without upper limit.
 However, its usage is limited to the case where the expected random effect is known ($m=0$); we may obtain its information from the past studies or from experts.
@@
 
-%Overall, obtaining point and interval estimates of each random effect is our primary inferential interest.
-The approximate Bayesian tool assumes that the unconditional posterior distribution of each random effect, i.e., $\mu_j\vert\boldsymbol{y}$, $p_j\vert\boldsymbol{y}$, or $\lambda_j\vert\boldsymbol{y}$,  follows a skewed-Normal distribution for the Gaussian case,  a Beta distribution for the Binomial case, or a Gamma distribution for the Poisson case.
-We match the parameters of the assumed distribution to the estimated unconditional posterior moments of each random effect, $\hat{\E}(\mu_j^c\vert\boldsymbol{y}$), $\hat{\E}(p_j^c\vert\boldsymbol{y}$), or $\hat{\E}(\lambda_j^c\vert\boldsymbol{y}$) for a non-negative constant $c$.
-We use these assumed unconditional posterior distributions to make point and interval estimates of each random effect.
-
-In this section, we illustrate our estimation procedure equipped with the adjustment for density maximization (ADM) \citep{carl1988, morris1997, tang2011}, a way to  approximate a distribution of the parameter of interest by one of Pearson family distributions via maximization.
-Because the ADM procedure for the Gaussian model adopted in \pkg{Rgbp} is well documented in \cite{kelly2014advances}, we describe  the ADM procedure  using the Poisson and Binomial model.
+We illustrate our estimation procedure which utilizes adjustment for density maximization (ADM) \citep{carl1988, morris1997, tang2011}.
+ADM is a method  to  approximate a distribution by a member of Pearson family of distributions and obtain moment estimates via maximization.
+The ADM procedure for the Gaussian model adopted in \pkg{Rgbp} is well documented in \cite{kelly2014advances} and so in this section we will describe  the ADM procedure  using the Poisson and Binomial model.
 
@@
 
-Estimating the unconditional posterior moments of the shrinkage factors and the expected random effects is crucial because we use their estimated moments to estimate the unconditional posterior moments of the random effects in the end.
+Our goal here is to estimate the unconditional posterior moments of the shrinkage factors and the expected random effects because they are used to estimate the unconditional posterior moments of the random effects.
 
 \subsubsection{Unconditional posterior moments of shrinkage factors}  It is noted that  the shrinkage factors  are a function of $r$, i.e., $B_{j}= B_{j}(r)=r/(r+n_{j})$ (or a function of $A$ for the Gaussian model).
-One way to approximate the distribution of $B_{j}$ is to find the maximum likelihood estimate of $r$, $\hat{r}_{MLE}$, with its Hessian value and to use a Delta method for an asymptotic Normal distribution of $\hat{B}_{j}(\hat{r}_{MLE})$.
+A common method of estimation of $B_{j}$ is to approximate the likelihood of $r$ with two derivatives and use  a Delta method for an asymptotic Normal distribution of $\hat{B}_{j}(\hat{r}_{MLE})$.
 This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $B_{j}$ lies on the unit interval between 0 and 1, and hence in small sample sizes the Delta method can result in point estimates lying on the boundary of the parameter space, from which the restricted MLE procedure sometimes suffers \citep{tang2011, kelly2014advances}.
 
-To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of the ADM.
+To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of  ADM.
 The ADM approximates the distribution of the function of the parameter of interest by one of the Pearson family distributions using the first two derivatives as the Delta method does; the Delta method is a special case of the ADM based on the Normal distribution.
@@
 \end{equation} 
-The article also show that the tails of the skewed-$t$ density function  follow a power law as $\alpha^{-(2a+1)}$ on the left and $\alpha^{-(2b+1)}$ on the right when $b>a$.
+and shows that the tails of the skewed-$t$ density function  follow a power law with $\alpha^{-(2a+1)}$ on the left and $\alpha^{-(2b+1)}$ on the right when $b>a$.
 It also provides a representation to generate the random variable following their skewed-$t$ distribution as
@@
 \section{Frequency method checking}\label{sec4}
-Whether the 95\%  interval estimates of random effects obtained by a specific model achieve the nominal 95\% confidence level  for any true parameter values is one of the key model evaluation criteria.
-A \emph{frequency method checking} is a procedure to evaluate it, which is different from a model checking that tests whether a two-level model is appropriate for data  \citep{dean1992testing, modelchecking1996}.
+The question as to whether the interval estimates of random effects for given confidence level obtained by a specific model achieve the nominal coverage rate  for any true parameter values is one of the key model evaluation criteria.
+Unlike standard model checking methods that test whether a two-level model is appropriate for data  \citep{dean1992testing, modelchecking1996}, \emph{frequency method checking} is a procedure to evaluate the coverage properties of the model.
 Conditioning that the two-level model is appropriate, the frequency method checking generates pseudo-data sets given specific values of hyper-parameters  and estimates unknown coverage probabilities based on these mock data sets (a parametric bootstrapping).

### 2015-07-29 jss/article_v4.tex
D-6

@@
 The evaluation procedure which we use for this process of ``frequency method checking'' uses a parametric bootstrapping  method that many times generates mock data sets given the fitted values of the estimated hyper-parameters and uses the mock data to estimate the coverage rates.
+Using this procedure, we show that the coverage rates of the random effects obtained by our model achieve (or exceed) the nominal confidence level.
 
@@
 \pkg{Rgbp} allows users to choose one of three hierarchical models according to the type of data, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta models.
-Although there are possibly more hierarchical models such as Exponential-Gamma \citep{tang2002fitting}, we choose the three models because these are based on the most common data types we may encounter in practice and the conjugacy leads to a simple posterior computation.
+Although there are possibly more hierarchical models such as Exponential-Gamma \citep{tang2002fitting}, we choose the three models because these are based on the most common types of  data we may encounter in practice.
+Also, the conjugacy leads to a simple posterior computation.
 
@@
 \subsection[Normal-Normal]{Normal-Normal model for Gaussian data}
-The following Normal-Normal hierarchical model (or the Gaussian model) assumed by \pkg{Rgbp} is useful when the group-level aggregate data from $k$ independent  groups are continuous variables with known standard errors.
+The following Normal-Normal hierarchical model (or the Gaussian model) assumed by \pkg{Rgbp} is useful when the group-level aggregate data from $k$ independent  groups are continuous (or approximately continuous) variables with known standard errors.
 The subscript \emph{j} below indicates the \emph{j}th group among \emph{k} groups in the dataset.
@@
 \pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model) when the group-level aggregate data from $k$ independent  groups comprise of non-negative count data without upper limit.
-However, its usage is limited to the case where the expected random effect is known ($m=0$); we may obtain its information from the past studies or from experts.
+However, its usage is limited to the case where the expected random effect is known ($m=0$); we may be able to obtain this information from the past studies or from experts.
 For $j=1, 2, \ldots, k$,
@@
 
-\cite{kelly2014advances} uses  the results derived in \cite{azzalini1985class}, i.e., $\E(\mu_j\vert \boldsymbol{y}) =\phi+\omega\delta\sqrt{2/\pi}$, Var$(\mu_j\vert \boldsymbol{y})=\omega^2(1-2\delta^2/\pi)$, and Skewness$(\mu_j\vert \boldsymbol{y})=(4-\pi)\delta^3/[2(\pi/2-\delta^2)^{3/2}]$, and estimates three parameters of the skewed-Normal distribution using  three approximately estimated unconditional posterior  moments of each random effect; see \cite{kelly2014advances} for details.
-\cite{kelly2014advances} also shows that the skewed-Normal approximation improves a Normal approximation ($\mu_j\vert\boldsymbol{y}\sim \textrm{Normal}$) used in  \citet{tang2011} and \cite{morris2012} in terms of the repeated sampling coverage properties of random effects.
+\cite{morris2012} first note that the unconditional posterior distribution of the random effect in a two-level conjugate Gaussian model may be skewed.
+\cite{kelly2014advances}  shows that the skewed-Normal approximation to the unconditional posterior distribution of the random effect is better than a Normal approximation ($\mu_j\vert\boldsymbol{y}\sim \textrm{Normal}$) in terms of the repeated sampling coverage properties of random effects.
+\cite{kelly2014advances} uses  the results derived in \cite{azzalini1985class}, i.e., $\E(\mu_j\vert \boldsymbol{y}) =\phi+\omega\delta\sqrt{2/\pi}$, Var$(\mu_j\vert \boldsymbol{y})=\omega^2(1-2\delta^2/\pi)$, and Skewness$(\mu_j\vert \boldsymbol{y})=(4-\pi)\delta^3/[2(\pi/2-\delta^2)^{3/2}]$.
+He estimates three parameters of the skewed-Normal distribution using  three approximately estimated unconditional posterior  moments of each random effect; see \cite{kelly2014advances} for details.
 
@@
 Health care providers may use these data to improve their care qualities, and patients may refer to the data to select a better hospital.
-Our goal is to obtain the point and interval estimates for the unknown true mortality rates (random effects) of 31 hospitals to evaluate  each hospital's reliability on the CABG surgery (see \cite{morris1995} for the similar ranking problem).
+Our goal is to obtain the point and interval estimates for the unknown true mortality rates (random effects) of 31 hospitals to evaluate  each hospital's reliability on the CABG surgery (\cite{morris1995} use a similar Poisson model to handle these hospital profile data).
 We interpret the caseloads, $\boldsymbol{n}$,  as exposures and assume that the state-level death rate per exposure of this surgery ($\lambda^E$) is known as 0.03 to fit the Poisson model for an illustrative purpose.

### 2015-07-31 jss/article_v4.tex
any

@@
 \pkg{Rgbp} allows users to choose one of three hierarchical models according to the type of data, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta models.
-Although there are possibly more hierarchical models such as Exponential-Gamma \citep{tang2002fitting}, we choose the three models because these are based on the most common types of  data we may encounter in practice.
-Also, the conjugacy leads to a simple posterior computation.
+Although there are more hierarchical models, we choose the three models because these are based on the most common types of  data we may encounter in practice.
+Also, their conjugacy leads to linear posterior means simplifying computations.
 
@@
 It is assumed that the second-level variance $A$ is unknown and that the $m\times1$ regression coefficient vector $\boldsymbol{\beta}$ is also unknown unless otherwise specified.
-If no covariates are available with an intercept term, then $\boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_1$ ($m=1$) and thus $\mu^E_{j}=\mu^E=\beta_1$ for all $j$, resulting in an exchangeable conjugate prior distribution for the random effects.
+If no covariates are available, but with an unknown intercept term, then $\boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_1$ ($m=1$) and thus $\mu^E_{j}=\mu^E=\beta_1$ for all $j$, resulting in an exchangeable conjugate prior distribution for the random effects.
 Based on these conjugate prior distributions for random effects, it is easy to derive the conditional posterior distribution of each random effect.
@@
 \subsection[Poisson-Gamma]{Poisson-Gamma model for Poisson data}\label{poissonsubsec}
-\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model) when the group-level aggregate data from $k$ independent  groups comprise of non-negative count data without upper limit.
-However, its usage is limited to the case where the expected random effect is known ($m=0$); we may be able to obtain this information from the past studies or from experts.
+\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model) when the group-level aggregate data from $k$ independent  groups are comprised of non-negative count data without upper limit.
+However, in this case its usage is limited to the case where the expected random effect is known ($m=0$); we may be able to obtain this information from the past studies or from experts.
 For $j=1, 2, \ldots, k$,
@@
 where $y_j$ is the number of events happening, $n_{j}$ is the exposure of group $j$, which is not necessarily an integer, $\lambda^E=\E(\lambda_j\vert r)$ is the known expected random effect ($m=0$), and $r$ is the unknown second-level variance component.
-The mean and variance of the conjugate Gamma prior distribution are $\lambda^E$ and $\lambda^E/r$, respectively.
+The mean and variance of this conjugate Gamma prior distribution are $\lambda^E$ and $\lambda^E/r$, respectively.
 \cite{albert1988computational} interprets $r$ as the amount of prior information as $n_{j}$ represents the amount of observed information because the uncertainty of the conjugate prior distribution increases as $r$ decreases and vice versa.
@@
 \pkg{Rgbp} can fit a conjugate Binomial-Beta hierarchical model when the group-level aggregate data from $k$ independent  groups are composed of each group's number of successes out of total number of trials.
-Unlike the Poisson model, the expected random effect is either known ($m=0$) or unknown ($m\ge1$).
+Unlike the Poisson model, which is for the case with a known second-level mean ($m=0$), the expected random effect in the Binomial model is either known ($m=0$) or unknown ($m\ge1$).
 For $j=1, 2, \ldots, k$,
@@
 \begin{equation}\label{marginal_post_normal}
-f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L_g(A, \boldsymbol{\boldsymbol{\beta}})dAd\boldsymbol{\beta}.
+f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L(A, \boldsymbol{\boldsymbol{\beta}})dAd\boldsymbol{\beta}.
 \end{equation}
@@
 where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}\exp(x)dx$ for a positive constant $a$.
-The posterior density function of $r$, $f_{\textrm{hyp.post}}(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in  \eqref{marginal_poisson} times the hyper-prior density function of $r$, i.e., $dr/r^2$;
+The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in  \eqref{marginal_poisson} times the hyper-prior density function of $r$, i.e., $dr/r^2$;
 \begin{equation}\label{marginal_post_poisson}
@@
 
-Our goal is to obtain the point and interval estimates of the random effects from their unconditional posterior distributions; for the Gaussian  model, 
+Our goal is to obtain the point and interval estimates of the random effects from their unconditional posterior distributions.
+With subscripts suppressed, the strategy is to compute by using these formulas:  for the Gaussian  model,
 \begin{equation}\label{mcintegration_normal}
@@
 
-If there are at least two groups whose observed values $y_j$ are non-zero, then $f(r\vert\boldsymbol{y})$ goes to zero as $r$ goes to 0 due to the polynomial function of $r$ in \eqref{final_post_proper}; the following two factors in \eqref{final_post_proper} approach one.
+If there are at least two groups whose observed values $y_j$ are non-zero, then $f(r\vert\boldsymbol{y})$ goes to zero as $r$ goes to zero due to the polynomial function of $r$ in \eqref{final_post_proper}; the following two factors in \eqref{final_post_proper} approach one.
 As $r$ becomes infinite, $f(r\vert\boldsymbol{y})$ touches zero exponentially fast due to the exponential term in the middle of \eqref{final_post_proper}.

### 2015-07-31 jss/article_v6.tex
v6

--- 2015-07-31 jss/article_v4.tex
@@
 
-\section[Hierarchical Structure]{Conjugate hierarchical modeling structure} \label{sec2}
-%A two-level  multilevel model is a powerful tool for exploring the hierarchical structure in data.
-For example, we can imagine that there exists a district-level hierarchy (bigger population) for observed school-level data, or a state-level hierarchy for observed hospital-level data in a certain state.
-
 \pkg{Rgbp} allows users to choose one of three hierarchical models according to the type of data, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta models.
@@
 \subsection{Estimation for random effects}
-It is intractable to derive analytically the unconditional posterior distribution of each random effect  for the three models.
-This motivates us to use the ADM again by assuming that each random effect has a skewed Normal distribution \citep{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
+It is intractable to derive analytically the unconditional posterior
+distribution of each random effect for the three models. Thus we approximate the
+distributions by matching the estimated posterior moments with a skewed-Normal distribution \citep{azzalini1985class} for
+the Gaussian model, a Beta distribution for the Binomial model and a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
 \begin{align}
@@
 
-\cite{morris2012} first note that the unconditional posterior distribution of the random effect in a two-level conjugate Gaussian model may be skewed.
-\cite{kelly2014advances}  shows that the skewed-Normal approximation to the unconditional posterior distribution of the random effect is better than a Normal approximation ($\mu_j\vert\boldsymbol{y}\sim \textrm{Normal}$) in terms of the repeated sampling coverage properties of random effects.
-\cite{kelly2014advances} uses  the results derived in \cite{azzalini1985class}, i.e., $\E(\mu_j\vert \boldsymbol{y}) =\phi+\omega\delta\sqrt{2/\pi}$, Var$(\mu_j\vert \boldsymbol{y})=\omega^2(1-2\delta^2/\pi)$, and Skewness$(\mu_j\vert \boldsymbol{y})=(4-\pi)\delta^3/[2(\pi/2-\delta^2)^{3/2}]$.
-He estimates three parameters of the skewed-Normal distribution using  three approximately estimated unconditional posterior  moments of each random effect; see \cite{kelly2014advances} for details.
+\cite{morris2012} first note that the unconditional posterior distribution of
+the random effect in a two-level conjugate Gaussian model may be
+skewed. \cite{kelly2014advances}  shows that the skewed-Normal approximation to
+the unconditional posterior distribution of the random effect is better than a
+Normal approximation ($\mu_j\vert\boldsymbol{y}\sim \textrm{Normal}$) in terms
+of the repeated sampling coverage properties of random
+effects. \cite{kelly2014advances} estimates the first three moments of
+the random-effects by noting that $\mu_j | \mathbf{y}, B_{j}$ is normally
+distributed and thus estimates the moments by using the ADM approximation of
+the shrinkage factors, $B_{j}$, and the law of third cumulants \cite{brill}. The
+three estimated moments are then matched to the first three moments of the
+skewed-Normal distribution, $\E(\mu_j\vert \boldsymbol{y})
+=\phi+\omega\delta\sqrt{2/\pi}$, Var$(\mu_j\vert
+\boldsymbol{y})=\omega^2(1-2\delta^2/\pi)$, and Skewness$(\mu_j\vert
+\boldsymbol{y})=(4-\pi)\delta^3/[2(\pi/2-\delta^2)^{3/2}]$
+\cite{azzalini1985class}. The full derivation can be found in \cite{kelly2014advances}.
 
@@
 
-The S3 object ``gbp'' benefits from three generic functions, \code{print}, \code{summary}, and \code{plot}.
-The estimation result for all the random effects appears if we type the ``gbp'' object at the \proglang{R} console, which plays the same role of the function \code{print} with its default argument ``\code{sort = TRUE}''.
-When the argument \code{sort} is set to \code{TRUE}, the function \code{print} prints out the estimation result for all the groups in the ascending order of $n$ for the Binomial and Poisson model and the descending order of standard errors for the Gaussian model.
-When the argument \code{sort} is \code{FALSE}, the estimation result comes out in the order of data input.
+The S3 object ``gbp'' benefits from three generic functions, \code{print},
+\code{summary}, and \code{plot}. The estimation result for all the random
+effects appears if we type the ``gbp'' object at the \proglang{R} console, which
+plays the same role of the function \code{print} with its default argument
+``\code{sort = TRUE}''. When the argument \code{sort} is set to \code{TRUE}, the
+function \code{print} prints out the estimation result for all the groups in the
+ascending order of $n$ for the Binomial and Poisson model and the descending
+order of standard errors for the Gaussian model. When the argument \code{sort}
+is \code{FALSE}, the estimation result is returned in the order of data input.
 \begin{CodeChunk}
@@
 \subsection{Frequency method checking}
-The function \code{coverage} conducts a frequency method checking that estimates the coverage probabilities of  random effects, conditioning on the values of the hyper-parameters that generate random effects and  mock data sets.
+The function \code{coverage} conducts frequency method checking. It estimates
+the coverage properties for our estimators of the random effects at
+a particular value of the hyperparameters by averaging the coverage over many simulated datasets.
 The basic usage of \code{coverage} needs a ``gbp'' object, such as \code{b.output} above, as the first argument;
@@
 
-These data can be loaded into \proglang{R} using the following code.
+The following code
 \begin{CodeChunk}
@@
 \end{CodeChunk}
+can be used to load these data into \proglang{R}.
 
@@
 
-The function \code{gbp} fits the Poisson model with a Gamma conjugate prior distribution as the population distribution of the death rates in New York states whose mean ($\lambda^E$) is 0.030.
-The number of regression coefficients ($m$) is 0 because we do not estimate them via  a log-linear regression.
+The function \code{gbp} can then be used to fit a Poisson-Gamma to the death
+rates in New York states with prior mean, ($\lambda^E$), equal to 0.030 and the
+number of regression coefficients ($m$) set to 0.
+
 \begin{CodeChunk}
@@
 
-The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (groups) to test whether students (units) SAT scores are effected by coaching.
-The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \citep{1981}.
-We can load this data set into \proglang{R} by the following codes.
+The Education Testing Service (ETS) conducted randomized experiments in eight
+separate schools (groups) to test whether students (units) SAT scores are
+effected by coaching. The dataset contains the estimated coaching effects on SAT
+scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$)
+of the eight schools \citep{1981}. These data are contained in the package and can be loaded into \proglang{R}
 \begin{CodeChunk}
@@
 
-The data of 18 major league baseball players contain the batting averages through their first 45 official at-bats of the 1970 season \citep{1975}.
-We add a binary covariate that takes on one if a player is an outfielder and zero otherwise.
-We can load the data into \proglang{R} with the following codes.
+The data of 18 major league baseball players contain the batting averages
+through their first 45 official at-bats of the 1970 season \citep{1975}. A
+binary covariate is created that takes on the value one if a player is an
+outfielder and zero otherwise. The data can be loaded into \proglang{R} with the following code
 \begin{CodeChunk}
@@
 %$
-Conditioning on the unknown true batting average (random effect) of each player we assume that the at-bats are independent and therefore, $y_{j}\vert p_{j}\stackrel{\textrm{indep.}}{\sim} \textrm{Binomial}(45,~ p_{j}), ~j=1, \ldots, 18$.
+Conditional on the unknown true batting average (random effect) of each player
+it is assumed that the at-bats are independent and therefore, $y_{j}\vert p_{j}\stackrel{\textrm{indep.}}{\sim} \textrm{Binomial}(45,~ p_{j}), ~j=1, \ldots, 18$.
 Our goal is to obtain point and interval estimates of each random effect whilst considering the additional information on whether the player is an outfielder or not.
@@
 
-If there are at least two groups whose observed values $y_j$ are non-zero, then $f(r\vert\boldsymbol{y})$ goes to zero as $r$ goes to zero due to the polynomial function of $r$ in \eqref{final_post_proper}; the following two factors in \eqref{final_post_proper} approach one.
+If there are at least two groups whose observed values $y_j$ are non-zero, then $f(r\vert\boldsymbol{y})$ goes to zero as $r$ goes to 0 due to the polynomial function of $r$ in \eqref{final_post_proper}; the following two factors in \eqref{final_post_proper} approach one.
 As $r$ becomes infinite, $f(r\vert\boldsymbol{y})$ touches zero exponentially fast due to the exponential term in the middle of \eqref{final_post_proper}.
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2015-08-02 jss/article_v4.tex
code error

@@
 \pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model) when the group-level aggregate data from $k$ independent  groups are comprised of non-negative count data without upper limit.
-However, in this case its usage is limited to the case where the expected random effect is known ($m=0$); we may be able to obtain this information from the past studies or from experts.
+However, its usage is limited to the case where the expected random effect is known (or equivalently all the regression coefficients in $\lambda^E_j=\exp(\boldsymbol{x}_j^\top \boldsymbol{\beta})$ is known ($m=0$)); we may be able to obtain this information from the past studies or from experts.
 For $j=1, 2, \ldots, k$,
@@
 \pkg{Rgbp} can fit a conjugate Binomial-Beta hierarchical model when the group-level aggregate data from $k$ independent  groups are composed of each group's number of successes out of total number of trials.
-Unlike the Poisson model, which is for the case with a known second-level mean ($m=0$), the expected random effect in the Binomial model is either known ($m=0$) or unknown ($m\ge1$).
+The expected random effect in the Binomial model is either known ($m=0$) or unknown ($m\ge1$).
 For $j=1, 2, \ldots, k$,

### 2015-08-02 jss/article_v6.tex
code error

@@
 
-With an assumption of homogeneity within each group, the observed data are group-level aggregate data from $k$ independent  groups, composed of sufficient statistics for their $k$ random effects without the population-level data.
-Specifically, the data for the Gaussian model comprise of each group's sample mean and its standard error, those for the Poisson model use each group's outcome count and an exposure measure, those for the Binomial model use the number of each group's  successful outcomes together with the total number of trials.
+With an assumption of homogeneity within each group, the observed data are group-level aggregate data from $k$ independent  groups, composed of sufficient statistics for their $k$ random effects (without the population-level data).
+Specifically, the data for the Gaussian model comprise of each group's sample mean and its standard error, those for the Poisson model use each group's outcome count and an exposure measure, and those for the Binomial model use the number of each group's  successful outcomes together with the total number of trials.
 The data analyzed by \pkg{Rgbp} may incorporate each group's covariate information.
@@
 
-\pkg{Rgbp} employs a Bayesian approach with our unique improper hyper-prior distributions placed on the second-level parameters of the conjugate prior distribution.
-The hyper-prior is chosen to produce Bayesian interval   estimates for the random effects that achieve nominal confidence levels.
-The hyper-prior distribution used in \pkg{Rgbp} is related to Stein's harmonic prior for two-level Gaussian models where it has been seen to produce good repeated sampling coverage rates for the Bayesian interval estimates for the $k$ random effects \citep{tang2011, morris2012, kelly2014advances}.
-This prior, as adapted further here for \pkg{Rgbp}'s Poisson and Binomial hierarchical models, has been seen for every data set tested thus far to meet (or exceed) the pre-assigned confidence level.
+\pkg{Rgbp} combines Bayesian tools with our special improper hyper-prior distributions  on the second-level parameters chosen to produce posterior interval   estimates to achieve nominal confidence levels for the random effects.
+This hyper-prior distribution  is related to Stein's harmonic prior for two-level Gaussian models where it has been seen to produce good repeated sampling coverage rates for the Bayesian interval estimates for the $k$ random effects \citep{tang2011, morris2012, kelly2014advances}.
+This prior, as extended here for \pkg{Rgbp}'s Poisson and Binomial hierarchical models, has been seen for every data set tested thus far to meet (or exceed) the pre-assigned confidence level.
 %The main goal of our Bayesian hierarchical models is to compare random effects between groups by their Bayesian interval estimates that have good frequency properties.
@@
 ``adjustment for density maximization'' \citep{carl1988, morris1997, tang2011}.
-ADM approximates a posterior density or a likelihood function by fitting a pre-specified (one dimensional) Pearson family, using the first two derivatives of the given function.
-When the Normal distribution is the chosen Pearson family, ADM produces exactly the same approximation as maximum likelihood estimation (MLE) does for fitting a Normal curve.
-Because shrinkage factors lie in [0,1], \pkg{Rgbp} approximates shrinkage factor distributions with Beta distributions because they are constrained to [0,1], unlike the Normal.
+ADM approximates a posterior density or a likelihood function by fitting a selected (one dimensional) Pearson family, based on the first two derivatives of the given density function.
+When the Normal distribution is the chosen Pearson family, ADM reduces to maximum likelihood estimation.
+Because shrinkage factors lie in [0,1], \pkg{Rgbp} approximates shrinkage factor distributions with Beta distributions because these are constrained to [0,1], unlike the Normal.
 
@@
 
-For the Binomial  hierarchical model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters, including random effects, via an acceptance-rejection method \citep{everson2000inference, tang2002fitting}.
+For the Binomial  hierarchical model, \pkg{Rgbp} provides an option to draw independent posterior samples of all the model parameters, including random effects, via an acceptance-rejection method \citep{robert2013monte}.
+%everson2000inference, tang2002fitting
 
 In addition to fitting the hierarchical models, \pkg{Rgbp} evaluates the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects \citep{morris1997, daniels1999prior, tang2002fitting, tang2011, morris2012}.
-This is a unique procedure that distinguishes \pkg{Rgbp}  from any other \proglang{R} packages for similar hierarchical modeling such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models.
+This procedure distinguishes \pkg{Rgbp}  from  other \proglang{R} packages for similar hierarchical models such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models.
 The evaluation procedure which we use for this process of ``frequency method checking'' uses a parametric bootstrapping  method that many times generates mock data sets given the fitted values of the estimated hyper-parameters and uses the mock data to estimate the coverage rates.
@@
 
+\section[Hierarchical Structure]{Conjugate hierarchical modeling structure} \label{sec2}
+%A two-level  multilevel model is a powerful tool for exploring the hierarchical structure in data.
+For example, we can imagine that there exists a district-level hierarchy (bigger population) for observed school-level data, or a state-level hierarchy for observed hospital-level data in a certain state.
+
 \pkg{Rgbp} allows users to choose one of three hierarchical models according to the type of data, namely Normal-Normal, Poisson-Gamma, and Binomial-Beta models.
@@
 
-Our parametrization of the three hierarchical models leads to an intuitive shrinkage interpretation in inference and  facilitates the estimation procedure because the shrinkage factors under our parametrization are a function of only a second-level variance component.
+Our parametrization of the three hierarchical models leads to an intuitive shrinkage interpretation in inference and  facilitates the estimation procedure because the shrinkage factors under our parametrization are a function of  a second-level variance component \citep{morris1983natural}.
 
 \subsection[Normal-Normal]{Normal-Normal model for Gaussian data}
-The following Normal-Normal hierarchical model (or the Gaussian model) assumed by \pkg{Rgbp} is useful when the group-level aggregate data from $k$ independent  groups are continuous (or approximately continuous) variables with known standard errors.
+The following Normal-Normal hierarchical model (hereafter the Gaussian model) assumed by \pkg{Rgbp} is useful when the group-level aggregate data from $k$ independent  groups are continuous (or approximately continuous) variables with known standard errors.
 The subscript \emph{j} below indicates the \emph{j}th group among \emph{k} groups in the dataset.
@@
 
-where $y_j$ is an observed unbiased estimate, e.g., sample mean, for random effect $\mu_j$, $V_{j}$ is a completely known standard error of $y_j$, $\mu^E_{j}$ is an expected random effect defined as $\E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$, and $m$ is the number of regression coefficients to be estimated.
+where $y_j$ is an observed unbiased estimate, e.g., sample mean, for random effect $\mu_j$, $V_{j}$ is a completely known standard error of $y_j$, $\mu^E_{j}$ is an expected random effect defined as $\E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$, and $m$ is the number of unknown regression coefficients.
 \pkg{Rgbp} sets $x_{j, 1}$ to 1 for an intercept term as a default.
@@
 \subsection[Poisson-Gamma]{Poisson-Gamma model for Poisson data}\label{poissonsubsec}
-\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (or the Poisson model) when the group-level aggregate data from $k$ independent  groups are comprised of non-negative count data without upper limit.
-However, in this case its usage is limited to the case where the expected random effect is known ($m=0$); we may be able to obtain this information from the past studies or from experts.
+\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (hereafter the Poisson model) when the group-level aggregate data from $k$ independent  groups are comprised of non-negative count data without upper limit.
+However, its usage is limited to the case where the expected random effect, $\lambda^E_j=\exp(\boldsymbol{x}_j^\top \boldsymbol{\beta})$,  is known  (or equivalently all the regression coefficients are known ($m=0$)); we may be able to obtain this information from the past studies or from experts.
 For $j=1, 2, \ldots, k$,
@@
 y_j\vert \lambda_j &\stackrel{\textrm{indep.}}{\sim}  \textrm{Poisson}(n_{j}\lambda_{j}),\\
-\lambda_{j}\vert r &\stackrel{i.i.d.}{\sim} \textrm{Gamma}(r\lambda^E, r),
+\lambda_{j}\vert r &\stackrel{\textrm{indep.}}{\sim} \textrm{Gamma}(r\lambda^E_j, r),\label{gamma_prior}
 \end{align}
-where $y_j$ is the number of events happening, $n_{j}$ is the exposure of group $j$, which is not necessarily an integer, $\lambda^E=\E(\lambda_j\vert r)$ is the known expected random effect ($m=0$), and $r$ is the unknown second-level variance component.
-The mean and variance of this conjugate Gamma prior distribution are $\lambda^E$ and $\lambda^E/r$, respectively.
+where $y_j$ is the number of events happening, $n_{j}$ is the exposure of group $j$, which is not necessarily an integer, $\lambda^E_j=\E(\lambda_j\vert r)$ is the known expected random effect ($m=0$), and $r$ is the unknown second-level variance component.
+The mean and variance of this conjugate Gamma prior distribution are $\lambda^E$ and $\lambda^E/r$, respectively\footnote{The density function of this Gamma prior distribution in \eqref{gamma_prior} is $f(\lambda_j\vert r)\propto \lambda_j^{r\lambda^E_j - 1}\exp(-r\lambda_j)$}.
 \cite{albert1988computational} interprets $r$ as the amount of prior information as $n_{j}$ represents the amount of observed information because the uncertainty of the conjugate prior distribution increases as $r$ decreases and vice versa.
 The conditional posterior distribution of the random effect $\lambda_j$ for this Poisson model is
-\begin{equation} \label{gammapost}
-\lambda_j\vert r, \boldsymbol{y} \stackrel{\textrm{indep.}}{\sim}\textrm{Gamma}(r\lambda^E + n_j\bar{y}_{j},~ r + n_j),
+\begin{equation} \label{gamma_post}
+\lambda_j\vert r, \boldsymbol{y} \stackrel{\textrm{indep.}}{\sim}\textrm{Gamma}(r\lambda^E_j + n_j\bar{y}_{j},~ r + n_j),
 \end{equation}  
@@
 \begin{equation}\label{gammapost_mean_var}
-\lambda^\ast_j\equiv \E(\lambda_j\vert r, \boldsymbol{y} )=(1-B_{j})\bar{y}_{j} + B_{j}\lambda^E~~\textrm{and}~~\VAR(\lambda_j\vert r, \boldsymbol{y})=\frac{\lambda^\ast_j}{r+n_j}.
+\lambda^\ast_j\equiv \E(\lambda_j\vert r, \boldsymbol{y} )=(1-B_{j})\bar{y}_{j} + B_{j}\lambda^E_j~~\textrm{and}~~\VAR(\lambda_j\vert r, \boldsymbol{y})=\frac{\lambda^\ast_j}{r+n_j}.
 \end{equation}
 where $B_{j}\equiv r / (r+n_{j})$ is the shrinkage factor of group $j$, the relative amount of information in the prior compared to the data.
-The conditional posterior mean is  a convex combination of $\bar{y}_{j}$ and  $\lambda^E$ weighted by $B_j$.
+The conditional posterior mean is  a convex combination of $\bar{y}_{j}$ and  $\lambda^E_j$ weighted by $B_j$.
 If the conjugate prior distribution contains more information than the observed data have, \emph{i.e.}, ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the posterior mean shrinks  towards the prior mean by more than 50\%.%, borrowing more information from the second-level distribution.
@@
 \subsection[Binomial-Beta]{Binomial-Beta model for Binomial data}
-\pkg{Rgbp} can fit a conjugate Binomial-Beta hierarchical model when the group-level aggregate data from $k$ independent  groups are composed of each group's number of successes out of total number of trials.
-Unlike the Poisson model, which is for the case with a known second-level mean ($m=0$), the expected random effect in the Binomial model is either known ($m=0$) or unknown ($m\ge1$).
+\pkg{Rgbp} can fit a conjugate Binomial-Beta hierarchical model (hereafter the Binomial model) when the group-level aggregate data from $k$ independent  groups are composed of each group's number of successes out of total number of trials.
+The expected random effect in the Binomial model is either known ($m=0$) or unknown ($m\ge1$).
 For $j=1, 2, \ldots, k$,
@@
 The resultant conditional posterior distribution of random effect $p_j$  is
-\begin{equation} \label{betapost}
+\begin{equation} \label{beta_post}
 p_{j}\vert  \boldsymbol{\beta}, r, \boldsymbol{y} \stackrel{\textrm{indep.}}{\sim}\textrm{Beta}(n_{j}\bar{y}_{j}+rp^E_j,~n_{j}(1-\bar{y}_{j})+r(1-p^E_j)),
@@
 
-In the other two cases, Poisson and Binomial, the flat prior distribution on $1/r$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with the Uniform($0, \infty$) for the Gaussian case.
-The Poisson model with this hyper-prior distribution on $r$, i.e., $dr/r^2$,  provides posterior propriety if there are at least two groups whose observed values $y_j$ are non-zero  and the expected random effect, $\lambda^E$, is a completely known constant ($m=0$); see Appendix \ref{propriety_poisson} for its proof.
-If $\lambda^E$ is unknown,  we recommend using the Binomial model with the same hyper-prior distributions because the Poisson model is  an approximation to the Binomial model when $n_j$ is large and $p_j$ is small.
+In the other two cases, Poisson and Binomial, the flat prior distribution on $1/r$ induces the same improper prior distribution on shrinkages ($f(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with the Uniform($0, \infty$) for the Gaussian case.
+The Poisson model with this hyper-prior distribution on $r$, i.e., $dr/r^2$,  provides posterior propriety if there are at least two groups whose observed values $y_j$ are non-zero  and the expected random effects, $\lambda^E_j$, are known ($m=0$); see Appendix \ref{propriety_poisson} for its proof.
+If $\lambda^E_j$ is unknown, \pkg{Rgbp} cannot yet give reliable results because we have not verified posterior propriety.
+If the Poisson is being used as an approximation to the Binomial and the exposures are known integer values, then we recommend using the Binomial model with the same hyper-prior distributions.
 
@@
 \begin{equation}\label{marginal_normal}
-L(A, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k f(y_j\vert A, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k \frac{1}{\sqrt{2\pi (A+V_j)}}\exp\left(-\frac{(y_j-\mu^E_j)^2}{2(A+V_j)}\right),
-\end{equation}
-where $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$.
-The joint posterior density  function of hyper-parameters $f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Gaussian  model is proportional to their likelihood function in  \eqref{marginal_normal} because we use flat improper hyper-prior density functions for $A$ and $\boldsymbol{\beta}$;
+L(A, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k f(y_j\vert A, \boldsymbol{\boldsymbol{\beta}})=\prod_{j=1}^k \frac{1}{\sqrt{2\pi (A+V_j)}}\exp\left(-\frac{(y_j-\mu^E_j)^2}{2(A+V_j)}\right).
+\end{equation}
+The joint posterior density  function of hyper-parameters for the Gaussian  model is proportional to their likelihood function in  \eqref{marginal_normal} because we use flat improper hyper-prior density functions for $A$ and $\boldsymbol{\beta}$;
 \begin{equation}\label{marginal_post_normal}
 f(A, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})\propto L(A, \boldsymbol{\boldsymbol{\beta}})dAd\boldsymbol{\beta}.
+\end{equation}
+
+The likelihood function of $r$ for the Poisson  model  comes from the independent Negative-Binomial  distributions of the observed data with the random effects integrated out;
+\begin{equation}\label{marginal_poisson}
+L(r)=\prod_{j=1}^k f(y_j\vert r)=\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E_j+y_j)}{\Gamma(r\lambda^E_j)(y_j!)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E_j},
+\end{equation}
+where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}\exp(x)dx$ for a positive constant $a$.
+The posterior density function of $r$  for the Poisson  model is  the likelihood function in  \eqref{marginal_poisson} times the hyper-prior density function of $r$, i.e., $dr/r^2$;
+\begin{equation}\label{marginal_post_poisson}
+f(r \vert \boldsymbol{y})\propto L(r)dr/r^2.
 \end{equation}
@@
 
-Similarly, the likelihood function of $r$ for the Poisson  model  comes from the independent Negative-Binomial  distributions of the observed data with the random effects integrated out;
-\begin{equation}\label{marginal_poisson}
-L(r)=\prod_{j=1}^k f(y_j\vert r)=\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E+y_j)}{\Gamma(r\lambda^E)(y_j!)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E},
-\end{equation}
-where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}\exp(x)dx$ for a positive constant $a$.
-The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in  \eqref{marginal_poisson} times the hyper-prior density function of $r$, i.e., $dr/r^2$;
-\begin{equation}\label{marginal_post_poisson}
-f(r \vert \boldsymbol{y})\propto L_p(r)dr/r^2.
-\end{equation}
-
 %If all the observed data are extreme, i.e., $y_j$ is either 0 or $n_j$ for all $j$, the likelihood becomes a decreasing function with respect to $r$ for finite values of $\boldsymbol{\beta}$.
@@
 
-Our goal is to obtain the point and interval estimates of the random effects from their unconditional posterior distributions.
-With subscripts suppressed, the strategy is to compute by using these formulas:  for the Gaussian  model,
+Our goal is to obtain the point and interval estimates of the random effects from their joint unconditional posterior density which can be expressed as for the Gaussian  model
 \begin{equation}\label{mcintegration_normal}
@@
 \end{equation}
-for the Binomial  model, 
+where $\boldsymbol{\mu}=(\mu_1, \mu_2, \ldots, \mu_k)^\top$ and the distributions in the integrand  are given in \eqref{normalpost} and \eqref{marginal_post_normal}.
+For the Poisson  model, the joint unconditional posterior density for the random effects is
+\begin{equation}\label{mcintegration_poisson}
+f(\boldsymbol{\lambda}\vert \boldsymbol{y})=\int  f(\boldsymbol{\lambda}\vert r, \boldsymbol{y})\cdot f(r\vert \boldsymbol{y})dr,
+\end{equation}
+where  $\boldsymbol{\lambda}=(\lambda_1, \lambda_2, \ldots, \lambda_k)^\top$ and  the distributions in the integrand  are given in \eqref{gamma_post} and \eqref{marginal_post_poisson}.
+Lastly, for the Binomial  model, the joint unconditional posterior density for the random effects is
 \begin{equation}\label{mcintegration_binomial}
@@
 \end{equation}
-and lastly for the Poisson  model, 
-\begin{equation}\label{mcintegration_poisson}
-f(\boldsymbol{\lambda}\vert \boldsymbol{y})=\int  f(\boldsymbol{\lambda}\vert r, \boldsymbol{y})\cdot f(r\vert \boldsymbol{y})dr.
-\end{equation}
+where $\boldsymbol{p}=(p_1, p_2, \ldots, p_k)^\top$ and  the distributions in the integrand  are given in \eqref{beta_post} and \eqref{marginal_post_binomial}.
 
@@
 ADM is a method  to  approximate a distribution by a member of Pearson family of distributions and obtain moment estimates via maximization.
-The ADM procedure for the Gaussian model adopted in \pkg{Rgbp} is well documented in \cite{kelly2014advances} and so in this section we will describe  the ADM procedure  using the Poisson and Binomial model.
+The ADM procedure for the Gaussian model adopted in \pkg{Rgbp} is well documented in \cite{kelly2014advances} and so in this section we  describe  the ADM procedure  using the Poisson and Binomial model.
 
@@
 \E(B_j\vert\boldsymbol{y})&=\frac{a_{1j}}{a_{1j}+a_{0j}}=\argmax_{B_j}~ f^A(B_j\vert \boldsymbol{y})\equiv B'_j,\label{admmean}\\
-\VAR(B_j\vert\boldsymbol{y})&=\frac{B'_j(1-B'_j)}{a_{1j}+a_{0j}+1}=\frac{B'_j(1-B'_j)}{B'_j(1-B'_j)[-\frac{d^2}{dB^2_j}\log(A(B_j\vert \boldsymbol{y}))\vert_{B_j=B'_j}] +1}.\label{admvar}
+\VAR(B_j\vert\boldsymbol{y})&=\frac{B'_j(1-B'_j)}{a_{1j}+a_{0j}+1}=\frac{B'_j(1-B'_j)}{B'_j(1-B'_j)[-\frac{d^2}{dB^2_j}\log(f^A(B_j\vert \boldsymbol{y}))\vert_{B_j=B'_j}] +1}.\label{admvar}
 \end{align}
 
-The ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood, $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$, for the Binomial model is obtained via the Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in  \eqref{marginal_poisson}.
+The ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$.
+The marginal likelihood, $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$, for the Binomial model is obtained via the Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in  \eqref{marginal_poisson}.
 %For the Gaussian model, the marginal likelihood function of $A$ is available in a closed form with $\boldsymbol{\beta}$ integrated out  \citep{tang2011, kelly2014advances}.
@@
 \begin{equation}
-\E((p^E_j)^c\vert\boldsymbol{y})=\E(\E((p^E_j)^c\vert r, \boldsymbol{y})\vert\boldsymbol{y}).
-\end{equation}
-Instead of averaging over $r$, we approximate the unconditional posterior moments by the conditional posterior moments with $\hat{r}=\exp(-\hat{\alpha})$ plugged-in \citep{kass1989approximate}.
+\E((p^E_j)^c\vert\boldsymbol{y})=\E(\E((p^E_j)^c\vert \alpha, \boldsymbol{y})\vert\boldsymbol{y}).
+\end{equation}
+We approximate the unconditional posterior moments on the left hand side by the conditional posterior moments with $\hat{\alpha}$ plugged-in \citep{kass1989approximate}, i.e., by $\E((p^E_j)^c\vert \hat{\alpha}, \boldsymbol{y})$.
 %We estimate the unconditional posterior moments by the estimated conditional posterior moments that we obtain from the conditional posterior distribution of $\mu^E_j\vert A, \boldsymbol{y}$ or that of $p^E_j\vert r, \boldsymbol{y}$ with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.
@@
 \end{equation}
-
 where $G(b_{1j})$ is a random variable following a Gamma$(b_{1j}, 1)$ distribution and independently $G(b_{0j})$ has a Gamma($b_{0j}, 1)$ distribution.
-Note that the representation in  \eqref{admpriormean} is equivalent to saying $\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables.
+Note that the representation in  \eqref{admpriormean} is equivalent to  $\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables.
 Its mean and variance are
@@
 \begin{align}
-\hat{\eta}_j&=\exp(x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2),\label{priormean2}\\
+\hat{\E}(\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y})&=\exp(x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2)=\hat{\eta}_j,\label{priormean2}\\
 \widehat{\VAR}(\exp(x_j^\top\boldsymbol{\beta})\vert\boldsymbol{y})&=\hat{\eta}^2_j\big(\exp(x_j^{T}\hat{\Sigma} x_j)-1\big).\label{priorvariance2}
@@
 
-Finally, we estimate the unconditional posterior moments of the expected random effects, $\E((p^E_{j})^c\vert\boldsymbol{y})$, by $\hat{\E}((p^E_{j})^c\vert\hat{\alpha}, \boldsymbol{y})=B(\hat{b}_{1j} + c, \hat{b}_{0j})/B(\hat{b}_{1j}, \hat{b}_{0j})$ for $c\ge0$.
+Finally, we estimate the unconditional posterior moments of the expected random effects by
+\begin{equation}\label{est_exp_randomeffect}
+ \hat{\E}((p^E_{j})^c\vert\hat{\alpha}, \boldsymbol{y})=\frac{B(\hat{b}_{1j} + c, \hat{b}_{0j})}{B(\hat{b}_{1j}, \hat{b}_{0j})} \textrm{ for } c\ge0.
+\end{equation}
 
@@
 respectively, where $X\equiv (\boldsymbol{x}_1, \boldsymbol{x}_2, \ldots, \boldsymbol{x}_k)^\top$ is a $k \times m$ covariate matrix and $D_{V+\hat{A}}$ is a $k \times k$ diagonal matrix with the $j$-th diagonal element equal to $V_j+\hat{A}$.
-Because $\boldsymbol{x}^\top\boldsymbol{\beta}$ given $\hat{A}$ and $\boldsymbol{y}$ is also Normally distributed, we easily obtain the conditional posterior moments of $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$ and use them to estimate unconditional posterior moments of $\mu^E_j$.
+Because $\boldsymbol{x}^\top\boldsymbol{\beta}$ given $\hat{A}$ and $\boldsymbol{y}$ is also Normally distributed, we easily obtain the conditional posterior moments of $\mu^E_j=\boldsymbol{x}^\top\boldsymbol{\beta}$ given $\hat{A}$ and use them to estimate unconditional posterior moments of $\mu^E_j$.
 
@@
 \mu_j\vert\boldsymbol{y} &\sim \textrm{skewed-Normal}(\phi,~ \omega,~ \delta),\label{skewnormal}\\
-p_j\vert \boldsymbol{y} &\sim \textrm{Beta}(t_{1j},~ t_{0j}),\label{betapost}\\
-\lambda_j\vert \boldsymbol{y} &\sim \textrm{Gamma}(s_{1j},~ s_{0j}),\label{gammapost}
+\lambda_j\vert \boldsymbol{y} &\sim \textrm{Gamma}(s_{1j},~ s_{0j}),\label{gammapost}\\
+p_j\vert \boldsymbol{y} &\sim \textrm{Beta}(t_{1j},~ t_{0j}),\label{betapost}
 \end{align}
@@
 
-\cite{morris2012} first note that the unconditional posterior distribution of
-the random effect in a two-level conjugate Gaussian model may be
+\cite{morris2012} first noted that the unconditional posterior distribution of
+the random effect in a two-level conjugate Gaussian model might be
 skewed. \cite{kelly2014advances}  shows that the skewed-Normal approximation to
 the unconditional posterior distribution of the random effect is better than a
-Normal approximation ($\mu_j\vert\boldsymbol{y}\sim \textrm{Normal}$) in terms
+Normal approximation ($\mu_j\vert\boldsymbol{y}\stackrel{.}{\sim} \textrm{Normal}$) in terms
 of the repeated sampling coverage properties of random
 effects. \cite{kelly2014advances} estimates the first three moments of
-the random-effects by noting that $\mu_j | \mathbf{y}, B_{j}$ is normally
+the random effects by noting that $\mu_j | \mathbf{y}, B_{j}$ is Normally
 distributed and thus estimates the moments by using the ADM approximation of
-the shrinkage factors, $B_{j}$, and the law of third cumulants \cite{brill}. The
+the shrinkage factors, $B_{j}$, and the law of third cumulants \citep{brill}. The
 three estimated moments are then matched to the first three moments of the
@@
 \boldsymbol{y})=(4-\pi)\delta^3/[2(\pi/2-\delta^2)^{3/2}]$
-\cite{azzalini1985class}. The full derivation can be found in \cite{kelly2014advances}.
+\citep{azzalini1985class}. The full derivation can be found in \cite{kelly2014advances}.
+
+The unconditional posterior mean and variance of random effect $\lambda_j$ in the Poisson model are
+\begin{align}
+\E(\lambda_j\vert \boldsymbol{y}) &=\E(\E(\lambda_{j}\vert r, \boldsymbol{y})\vert\boldsymbol{y})=(1-\E(B_j\vert\boldsymbol{y}))\bar{y}_j + \E(B_j\vert  \boldsymbol{y})\lambda^E_j,\label{postmean_poisson} \\
+\VAR(\lambda_{j}\vert \boldsymbol{y}) &=  \E(\VAR(\lambda_{j}\vert r,  \boldsymbol{y})\vert \boldsymbol{y})+\VAR(\E(\lambda_{j}\vert r, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_poisson}\\
+&= \E\big(\lambda^{\ast}_{j}/ (r+n_{j})\vert  \boldsymbol{y}\big)+\VAR\big(B_{j}(\bar{y}_{j}-\lambda^E_{j})\vert \boldsymbol{y}\big) \\
+&=\frac{1}{n_j}\left[\bar{y}_j\E\left((1-B_j)^2\vert \boldsymbol{y}\right)+\lambda^E_j\E\left((1-B_j)B_j\vert \boldsymbol{y}\right)\right]+(\bar{y}_{j}-\lambda^E_{j})^2\VAR\big(B_{j}\vert \boldsymbol{y}\big).\label{approximate_var_poisson}
+\end{align}
+To estimate these, we plug  the estimated unconditional posterior moments of shrinkage factors in \eqref{shrinkagemoments} into both \eqref{postmean_poisson} and \eqref{approximate_var_poisson}.
+Let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimated unconditional posterior mean and variance, respectively.
+The estimates of the two parameters $s_{1j}$ and $s_{0j}$ in  \eqref{gammapost} are
+\begin{equation}\label{posttrueprob}
+\hat{s}_{1j}=\frac{\hat{\mu}_{\lambda_j}^2}{\hat{\sigma}^2_{\lambda_j}},~\textrm{and}~~\hat{s}_{0j}=\frac{\hat{\mu}_{\lambda_j}}{\hat{\sigma}^2_{\lambda_j}}.
+\end{equation}
 
@@
 where the approximation in \eqref{taylor} is a first-order Taylor approximation.
-By plugging-in the estimated unconditional posterior moments of shrinkage factors and those of expected random effect into   \eqref{postmean_binom} and \eqref{approximate_var}, we obtain the estimates of the unconditional posterior mean and variance of each random effect, denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
+By plugging the estimated unconditional posterior moments of shrinkage factors in \eqref{shrinkagemoments} and those of expected random effect in \eqref{est_exp_randomeffect} into  both \eqref{postmean_binom} and \eqref{approximate_var}, we obtain the estimates of the unconditional posterior mean and variance of each random effect, denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
 Finally, we obtain the estimates of two parameters $t_{1j}$ and $t_{0j}$ in  \eqref{betapost} as follows;
@@
 
-The unconditional posterior mean and variance of random effect $\lambda_j$ in the Poisson model are
-\begin{align}
-\E(\lambda_j\vert \boldsymbol{y}) &=\E(\E(\lambda_{j}\vert r, \boldsymbol{y})\vert\boldsymbol{y})=(1-\E(B_j\vert\boldsymbol{y}))\bar{y}_j + \E(B_j\vert  \boldsymbol{y})\lambda^E,\label{postmean_poisson} \\
-\VAR(\lambda_{j}\vert \boldsymbol{y}) &=  \E(\VAR(\lambda_{j}\vert r,  \boldsymbol{y})\vert \boldsymbol{y})+\VAR(\E(\lambda_{j}\vert r, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_poisson}\\
-&= \E\big(\lambda^{\ast}_{j}/ (r+n_{j})\vert  \boldsymbol{y}\big)+\VAR\big(B_{j}(\bar{y}_{j}-\lambda^E_{j})\vert \boldsymbol{y}\big) \\
-&=\frac{1}{n_j}\left[\bar{y}_j\E\left((1-B_j)^2\vert \boldsymbol{y}\right)+\lambda^E\E\left((1-B_j)B_j\vert \boldsymbol{y}\right)\right]+(\bar{y}_{j}-\lambda^E_{j})^2\VAR\big(B_{j}\vert \boldsymbol{y}\big).\label{approximate_var_poisson}
-\end{align}
-Let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimated unconditional posterior mean and variance in  \eqref{postmean_poisson} and \eqref{approximate_var_poisson}, respectively, with the estimated unconditional posterior moments of shrinkage factors plugged-in.
-The estimates of the two parameters $s_{1j}$ and $s_{0j}$ in  \eqref{gammapost} are
-\begin{equation}\label{posttrueprob}
-\hat{s}_{1j}=\frac{\hat{\mu}_{\lambda_j}^2}{\hat{\sigma}^2_{\lambda_j}},~\textrm{and}~~\hat{s}_{0j}=\frac{\hat{\mu}_{\lambda_j}}{\hat{\sigma}^2_{\lambda_j}}.
-\end{equation}
-
 Finally, the assumed unconditional posterior distribution of random effect for the Gaussian model is
@@
 \end{equation}
-Our point and interval estimates of each random effect are the  mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the assumed unconditional posterior distribution in  \eqref{trueapprox_normal}, \eqref{trueapprox_binomial}, or \eqref{trueapprox_poisson} depending on the type of data.
+Our point and interval estimates of each random effect are the mean and (2.5\%, 97.5\%) quantiles (if we assign 95\% confidence level) of the assumed unconditional posterior distribution in  \eqref{trueapprox_normal}, \eqref{trueapprox_binomial}, or \eqref{trueapprox_poisson}.
 
@@
 \section[Estimation]{The acceptance-rejection method for the Binomial model}\label{sec_accept}
-As for the Binomial model, the package \pkg{Rgbp} also provides a way to draw  posterior samples of random effects and hyper-parameters via the acceptance-rejection (A-R) method.
+As for the Binomial model, the package \pkg{Rgbp} also provides a way to draw  posterior samples of random effects and hyper-parameters via the acceptance-rejection (A-R) method \citep{robert2013monte}.
 Unlike the approximate Bayesian machinery specified in the previous section, this method does not assume that hyper-parameters are independent \emph{a posteriori}.
-We continue working on a logarithmic scale of $r$, i.e., $\alpha=\log(1/r)$.
-The joint posterior density function of $\alpha$ and $\boldsymbol{\beta}$ based on their joint hyper-prior density function in  \eqref{eq:hyper} is
-\begin{equation}
-f(\alpha, \boldsymbol{\beta} \vert \boldsymbol{y})\propto f(\alpha, \boldsymbol{\beta})L(\alpha, \boldsymbol{\beta})\propto \exp(\alpha)L_b(\alpha, \boldsymbol{\beta})d\alpha d\boldsymbol{\beta}.
-\end{equation}
-
-The A-R method \citep{everson2000inference, tang2002fitting, robert2013monte} is useful when it is difficult to sample a parameter of interest $\theta$ directly from its target probability density $f(\theta)$, which is known up to a normalizing constant, but an easy-to-sample envelope function $g(\theta)$ is available.
+The joint posterior density function of $\alpha=-\log(r)$ and $\boldsymbol{\beta}$ based on their joint hyper-prior density function in  \eqref{eq:hyper} is
+\begin{equation}\label{ar_target}
+f(\alpha, \boldsymbol{\beta} \vert \boldsymbol{y})\propto f(\alpha, \boldsymbol{\beta})L(\alpha, \boldsymbol{\beta})\propto \exp(\alpha)L(\alpha, \boldsymbol{\beta})d\alpha d\boldsymbol{\beta}.
+\end{equation}
+
+The A-R method  is useful when it is difficult to sample a parameter of interest $\theta$ directly from its target probability density $f(\theta)$, which is known up to a normalizing constant, but an easy-to-sample envelope function $g(\theta)$ is available.
 The A-R method samples $\theta$  from the envelope $g(\theta)$ and accepts it with a probability $\frac{f(\theta)}{Mg(\theta)}$, where $M$ is a constant making $f(\theta)/g(\theta)\le M$ for all $\theta$.
@@
 
-The goal of the A-R method  for the  Binomial model is to  draw  posterior samples of hyper-parameters from $f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})$, using an easy-to-sample envelop function $g(\alpha, \boldsymbol{\beta})$ that has thicker tails than the target density function.
+The goal of the A-R method  for the  Binomial model is to  draw  posterior samples of hyper-parameters from \eqref{ar_target}, using an easy-to-sample envelop function $g(\alpha, \boldsymbol{\beta})$ that has thicker tails than the target density function.
 
@@
 It is too complicated to figure out the tail behaviors of $f(\boldsymbol{\beta} \vert \alpha,  \boldsymbol{y})$.
-However, because $f(\boldsymbol{\beta} \vert \alpha,  \boldsymbol{y})$ of the Gaussian hierarchical model has a multivariate Gaussian density function \citep{tang2011, kelly2014advances}, we consider a multivariate $t$-distribution with 4  degrees of freedom as a good candidate for $g_2(\boldsymbol{\beta})$.
+However, because $f(\boldsymbol{\beta} \vert \alpha,  \boldsymbol{y})$ in the Gaussian  model (as an approximation) has a multivariate Gaussian density function \citep{tang2011, kelly2014advances}, we consider a multivariate $t$-distribution with 4  degrees of freedom as a good candidate for $g_2(\boldsymbol{\beta})$.
 
@@
 \end{eqnarray}
-where the notation Skewed-$t(\alpha\vert\mu, \sigma, a, b)$ represents a density function of a skewed $t$-distribution  at $\alpha$ with location $\mu$, scale $\sigma$, degree of freedom $a+b$, and skewness $a-b$ for any positive constants $a$ and $b$ \citep{jones2003skew}.
-The article of \cite{jones2003skew} derives the mode of $g_1(\alpha)$ as
+where Skewed-$t(\alpha\vert\mu, \sigma, a, b)$ represents a density function of a skewed $t$-distribution  at $\alpha$ with location $\mu$, scale $\sigma$, degree of freedom $a+b$, and skewness $a-b$ for any positive constants $a$ and $b$ \citep{jones2003skew}.
+\cite{jones2003skew} derive the mode of $g_1(\alpha)$ as
 \begin{equation}\label{mode}
-\mu+\frac{(a-b)\sqrt{a+b}}{\sqrt{(2a+1)(2b+1)}}.
-\end{equation} 
-and shows that the tails of the skewed-$t$ density function  follow a power law with $\alpha^{-(2a+1)}$ on the left and $\alpha^{-(2b+1)}$ on the right when $b>a$.
-It also provides a representation to generate the random variable following their skewed-$t$ distribution as
+\mu+\frac{(a-b)\sqrt{a+b}}{\sqrt{(2a+1)(2b+1)}},
+\end{equation} 
+and provide a  representation to generate  random variables that follows Skewed-$t(\alpha\vert\mu, \sigma, a, b)$;
 \begin{equation}
@@
 \end{equation}
+
+They also show that the tails of the skewed-$t$ density function  follow a power law with $\alpha^{-(2a+1)}$ on the left and $\alpha^{-(2b+1)}$ on the right when $b>a$.
+
 The notation $t_{4}(\boldsymbol{\beta}\vert\boldsymbol{\xi}, S)$ in  \eqref{g2approx} indicates a density function of a multivariate $t$-distribution at $\boldsymbol{\beta}$ with 4 degrees of freedom, a location vector $\boldsymbol{\xi}$, and a $m\times m$ scale matrix $S$ that leads to the variance-covariance matrix $2S$.
 
-We determine the parameters of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$, i.e., $\mu$, $\sigma$, $a$, $b$, $\boldsymbol{\xi}$, and $S$, to make the product of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$ similar to the target joint posterior density $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$.
-First, we obtain the  mode of $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$ and the inverse of the  negative Hessian matrix at the modes, $-H^{-1}$.
+\pkg{Rgbp} determines the parameters of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$, i.e., $\mu$, $\sigma$, $a$, $b$, $\boldsymbol{\xi}$, and $S$, to make the product of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$ similar to the target joint posterior density $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$.
+First, \pkg{Rgbp} obtains the  mode of $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$ and the inverse of the  negative Hessian matrix at the modes, $-H^{-1}$.
 Let $(\hat{\alpha}, \hat{\boldsymbol{\beta}})$ denote the modes of $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$, $-H^{-1}_{\hat{\alpha}}$ indicate (1, 1) element of $-H^{-1}$, and $-H^{-1}_{\hat{\boldsymbol{\beta}}}$ represent  $-H^{-1}$ without the first row and  column.
-%(1, 1)  and $(2:(m+1), 2:(m+1))$ elements of the  inverse of the negative Hessian matrix at the modes, respectively.
-% $f(\alpha, \boldsymbol{\beta} \vert \boldsymbol{y})\propto e^\alpha L(\alpha, \boldsymbol{\beta})d\alpha d\boldsymbol{\beta}$.
-
-Next, we set ($a,~ b$) to $(k,~ 2k)$ if $k<10$ (or otherwise $(\log(k),~ 2\log(k))$)   to maintain a left-skewness of $g_1(\alpha)$ and to keep  $a$ and $b$ small enough for thick tails.
-We match the mode of $g_1(\alpha)$ specified in  \eqref{mode} to $\hat{\alpha}$ by setting the location parameter $\mu$ to $\hat{\alpha}-(a-b)\sqrt{a+b}/\sqrt{(2a+1)(2b+1)}$.
-We set  the scale parameter $\sigma$ to $(-H^{-1}_{\hat{\alpha}})^{0.5}\psi$, where $\psi$ is a tuning parameter with 1.3 as a default value\footnote{When the A-R method produces extreme weights defined in  \eqref{weight}, we increase the value of $\psi$.}.
+
+For $g_1(\alpha)$, \pkg{Rgbp} sets ($a,~ b$) to $(k,~ 2k)$ if $k$ is less than 10 (or otherwise to $(\log(k),~ 2\log(k))$)   for a left-skewness  and for small values of $a$ and $b$ (thick tails).
+\pkg{Rgbp} matches the mode of $g_1(\alpha)$ specified in  \eqref{mode} to $\hat{\alpha}$ by setting the location parameter $\mu$ to $\hat{\alpha}-(a-b)\sqrt{a+b}/\sqrt{(2a+1)(2b+1)}$.
+\pkg{Rgbp} sets  the scale parameter $\sigma$ to $(-H^{-1}_{\hat{\alpha}})^{0.5}\psi$, where $\psi$ is a tuning parameter; when the A-R method produces extreme weights defined in  \eqref{weight} below, we need enlarge the value of $\psi$.
 %To summarize, we use
@@
 
-As for $g_2(\boldsymbol{\beta})$, we matches the location vector $\boldsymbol{\xi}$ to the mode $\hat{\boldsymbol{\beta}}$ and the scale matrix $S$ to $-H^{-1}_{\hat{\boldsymbol{\beta}}}/2$ so that the variance-covariance matrix becomes $-H^{-1}_{\hat{\boldsymbol{\beta}}}$;
-\begin{equation}
-g_2(\boldsymbol{\beta})\equiv t_4(\boldsymbol{\beta}\vert \boldsymbol{\xi}=\hat{\boldsymbol{\beta}}, S=-H^{-1}_{\hat{\boldsymbol{\beta}}}/2).
-\end{equation}
+For $g_2(\boldsymbol{\beta})$,  \pkg{Rgbp} sets the location vector $\boldsymbol{\xi}$ to the mode $\hat{\boldsymbol{\beta}}$ and the scale matrix $S$ to $-H^{-1}_{\hat{\boldsymbol{\beta}}}/2$ so that the variance-covariance matrix becomes $-H^{-1}_{\hat{\boldsymbol{\beta}}}$.
+%\begin{equation}
+%g_2(\boldsymbol{\beta})\equiv t_4(\boldsymbol{\beta}\vert \boldsymbol{\xi}=\hat{\boldsymbol{\beta}}, S=-H^{-1}_{\hat{\boldsymbol{\beta}}}/2).
+%\end{equation}
 %; when the sample size was small, it increased the acceptance rate of the A-R method
 
-For the  implementation of the acceptance-rejection method, we obtain four times more trial samples than the desired number of samples, denoted by $N$, independently from $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$.
-We calculate $4N$ weights, each of which is defined as
+For the  implementation of the acceptance-rejection method, \pkg{Rgbp} draws four times more trial samples than the desired number of samples, denoted by $N$, independently from $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$.
+\pkg{Rgbp} calculates $4N$ weights, each of which is defined as
 \begin{equation}\label{weight}
@@
 \end{equation}
-We accept each pair of $(\alpha^{(i)}, \boldsymbol{\beta}^{(i)})$ with a probability $w_i/M$ where $M$ is set to the maximum of all the $4N$ weights.
-In a case where we accept more than the desired number of samples $N$, we discard the redundant.
-If the number of accepted samples is smaller than $N$, then we additionally sample  6 times more pairs than the shortage and calculate a new maximum $M'$ from all the previous and new weights, accepting or rejecting the entire pairs again with new probabilities $w_i/M'$.
+\pkg{Rgbp} accepts each pair of $(\alpha^{(i)}, \boldsymbol{\beta}^{(i)})$ with a probability $w_i/M$ where $M$ is set to the maximum of all the $4N$ weights.
+When \pkg{Rgbp} accepts more than  $N$ pairs, it discards the redundant.
+If \pkg{Rgbp} accepts less than $N$ pairs, then it additionally draws   $N'$ (six times the shortage) pairs    and calculates a new maximum $M'$ from all the previous and new weights; \pkg{Rgbp} accepts or rejects the entire pairs again with new probabilities $w_j/M'$, $j=1, 2, \ldots, 4N+N'$.
 
@@
 
-Once we have posterior samples of hyper-parameters, it is easy to obtain posterior samples of random effects via a Monte Carlo integration below.
-\begin{equation}\label{mcintegration}
-f(\boldsymbol{p}\vert \boldsymbol{y})=\int  f(\boldsymbol{p}\vert \alpha, \boldsymbol{\beta}, \boldsymbol{y})\cdot f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})d\alpha d\boldsymbol{\beta}.
-\end{equation}
-The integration can be done by sampling $(p_1, p_2, \ldots, p_k)$ from the independent Beta conditional posterior distributions, i.e., $f(p_j\vert \boldsymbol{\beta}, r, \boldsymbol{y})$ specified in  \eqref{betapost},  given $r~(=\exp(-\alpha))$ and $\boldsymbol{\beta}$ that are already sampled from $f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})$ via the A-R method.
+After obtaining posterior samples of hyper-parameters, \pkg{Rgbp} draws posterior samples of random effects from $f(\boldsymbol{p}\vert \boldsymbol{y})$ in \eqref{mcintegration_binomial}.
+The integration on the right hand side of \eqref{mcintegration_binomial} can be done by sampling $\boldsymbol{p}$ from $f(p_j\vert \boldsymbol{\beta}, r, \boldsymbol{y})$  for $j=1, 2, \ldots, k$ in  \eqref{betapost},  given $r=\exp(-\alpha)$ and $\boldsymbol{\beta}$ that are already sampled from $f(\alpha, \boldsymbol{\beta}\vert \boldsymbol{y})$ via the A-R method.
 
@@
 
-\begin{figure}[t]
+\begin{figure}[b!]
 \begin{center}
@@
 \end{equation}
-Note that an outcome of the coverage indicator depends on the simulated random effects and mock data generated by $A$ and $\boldsymbol{\beta}$.
+The subscript, $A$ and $\boldsymbol{\beta}$, indicates that an outcome of the coverage indicator depends on the simulated random effects and mock data generated by $A$ and $\boldsymbol{\beta}$.
 
@@
 \begin{equation}
-\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)= \frac{1}{N_{\textrm{sim}}}\sum_{i=1}^{N_{\textrm{sim}}}I_{A, \boldsymbol{\beta}}(\mu_j^{(i)}),~ j=1, 2, \ldots, k.
+\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)= \frac{1}{N_{\textrm{sim}}}\sum_{i=1}^{N_{\textrm{sim}}}I_{A, \boldsymbol{\beta}}(\mu_j^{(i)}),~\textrm{for } j=1, 2, \ldots, k.
 \end{equation}
 Note that $\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)$ averages over possible values of $\mu_{j}$ and $y_{j}$ generated by specific values of $A$ and $\boldsymbol{\beta}$.
-For $j=1, 2, \ldots, k$, the unbiased variance estimator of $\VAR(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))$ is
+The unbiased variance estimator of $\VAR(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))$ is
 \begin{equation}\label{svar}
-\widehat{\VAR}(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))=\frac{1}{N_{\textrm{sim}}(N_{\textrm{sim}}-1)}\sum_{i=1}^{N_{\textrm{sim}}}(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})-\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))^{2}.
+\widehat{\VAR}(\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))=\frac{1}{N_{\textrm{sim}}(N_{\textrm{sim}}-1)}\sum_{i=1}^{N_{\textrm{sim}}}(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})-\bar{I}_{A, \boldsymbol{\beta}}(\mu_j))^{2},~\textrm{for } j=1, 2, \ldots, k.
 \end{equation}
@@
 \end{equation}
-where the sample mean of the conditional expectations inside the outer expectation is the RB unbiased coverage estimator. To be specific,
-\begin{align}\label{RB}
-\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) &= \frac{1}{N_{\textrm{sim}}}\sum_{i=1}^{N_{\textrm{sim}}}\E(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})\vert A, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})\\
-&= \frac{1}{N_{\textrm{sim}}}\sum_{i=1}^{N_{\textrm{sim}}} \Prob(\mu_j^{(i)}\in(\hat{\mu}^{(i)}_{j, ~\textrm{low}}, ~\hat{\mu}^{(i)}_{j, ~upp})\vert A, \boldsymbol{\beta},  \boldsymbol{y}^{(i)}).
+where the sample mean of the interior conditional expectations in \eqref{RB_theory} is the RB unbiased coverage estimator.  Specifically,
+\begin{align}
+\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j) &= \frac{1}{N_{\textrm{sim}}}\sum_{i=1}^{N_{\textrm{sim}}}\E(I_{A, \boldsymbol{\beta}}(\mu_j^{(i)})\vert A, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})\label{RB1}\\
+&= \frac{1}{N_{\textrm{sim}}}\sum_{i=1}^{N_{\textrm{sim}}} \Prob(\mu_j^{(i)}\in(\hat{\mu}^{(i)}_{j, ~\textrm{low}}, ~\hat{\mu}^{(i)}_{j, ~upp})\vert A, \boldsymbol{\beta},  \boldsymbol{y}^{(i)}).\label{RB2}
 \end{align}
-We  can easily compute the above conditional posterior probabilities using the cumulative density function of the Normal conditional posterior distribution of each random effect in  \eqref{normalpost}.
-The variance of  $\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j)$ does not exceed the variance of a simple unbiased coverage estimator $\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)$ \citep{radhakrishna1945information, blackwell1947conditional}.
+We  can easily compute the above conditional posterior probabilities in \eqref{RB2} using the cumulative density function of the Gaussian conditional posterior distribution of each random effect in  \eqref{normalpost}.
+The variance of  $\bar{I}^{RB}_{A, \boldsymbol{\beta}}(\mu_j)$ does not exceed the variance of a simple unbiased coverage estimator, $\bar{I}_{A, \boldsymbol{\beta}}(\mu_j)$ \citep{radhakrishna1945information, blackwell1947conditional}.
 
@@
 There are two cases according to whether covariates are available or not.
-When no covariates are available, the function \code{gbp} requires fitting an intercept term  or knowing the value of the  the expected random effect, meaning that the intercept term must be either estimated or known.
-The default of \code{gbp} in this case is to fit an intercept term.
-We can assign the value of the known expected random effect through an optional argument \code{mean.PriorDist}.
-Note that \code{gbp} can fit the Poisson model only when the value of expected random effect, $\lambda^E$, is known.
+When no covariates are available, the function \code{gbp} requires fitting an intercept term  or designating known values of   the expected random effects, i.e., the intercept term must be either estimated or known.
+The default of \code{gbp}  is to fit an intercept term.
+The value(s) of the known expected random effect(s) can be assigned through an optional argument \code{mean.PriorDist}, either a constant when all expected random effects are the same or a $k\times1$ vector.
+Note that \code{gbp} can fit the Poisson model only when the values of expected random effects, $\lambda^E_j$, are known.
 The usage of \code{gbp} to  fit each model without any covariates is
@@
 
-%  So, in order to generate pseudo-datasets, \code{coverage} needs parameters of prior distribution,  
-%  (\emph{A} (or \emph{r}) and \eqn{\beta} (\code{reg.coef})) 
-%  or (\emph{A} (or \emph{r}) and \eqn{\mu_{0}}{\mu0}). From here, we have four options to run \code{coverage}.
-
-%  First, if any values related to the prior distribution are not designated like 
-%  \code{coverage(b, nsim = 10)}, then \code{coverage} will regard estimated values (or known prior mean, \eqn{\mu_{0}}{\mu0}) in \code{b} (\code{gbp.object}) as given true values when it generates lots of pseudo-datasets.
-After sampling \eqn{\theta_{(i)}}{\theta_(i)} from the prior distribution determined by these estimated values (or known prior mean) in \code{b} (\code{gbp.object}), \code{coverage} creates an \emph{i}-th pseudo-dataset based on \eqn{\theta_{(i)}}{\theta_(i)} just sampled.
-
-%  Second, \code{coverage} allows us to try different true values in generating datasets.
-Suppose \code{gbp.object} is based on the model with a known prior mean, \eqn{\mu_{0}}{\mu0}.
-Then, we can try either different \code{A.or.r} or \code{mean.PriorDist}.
-For example, \code{coverage(b, A.or.r = 20, nsim = 10)},
-%\code{coverage(b, mean.PriorDist = 0.5, nsim = 10)}, or 
-%\code{coverage(b, A.or.r = 20, mean.PriorDist = 0.5, nsim = 10)}. Note that we cannot set \code{reg.coef} because the second-level mean (prior mean) is known in \code{gbp.object} to begin with.
-
-%  Suppose \code{gbp.object} is based on the model with an unknown prior mean.
-In this case, \code{gbp.object} has the estimation result of regression model, linear regression for Normal-Normal, log-linear regression for Poisson-Gamma, or logistic regression for Binomial-Beta, (only intercept term if there is no covariate) to estimate the unknown prior mean.
-Then, we can try some options: one or two of (\code{A.or.r}, \code{mean.PriorDist}, \code{reg.coef}).
-For example, \code{coverage(b, A.or.r = 20, nsim = 10)}, \code{coverage(b, mean.PriorDist = 0.5, nsim = 10)}, or \code{coverage(b, reg.coef = 0.1, nsim = 10)} with no covariate where \code{reg.coef} is a designated intercept term.
-Estimates in \code{gbp.object} will be used for undesignated values.
-Also, we can try appropriate combinations of two arguments.
-For example, \code{coverage(b, A.or.r = 20, mean.PriorDist = 0.5, nsim = 10)} and
-%\code{coverage(b, A.or.r = 20, reg.coef = 0.1, nsim = 10)}.
-If we have one covariate, a 2 by 1 vector should be designated for \code{reg.coef}, one for an intercept term and the other for a regression coefficient of the covariate.
-Note that the two arguments, \code{mean.PriorDist} and \code{reg.coef}, cannot be assigned together because we do not need \code{reg.coef} given \code{mean.PriorDist}.
-
-%  The simple unbiased estimator of coverage probability in \emph{j}-th group is a sample mean of indicators over all simulated datasets.
-The \emph{j}-th indicator in \emph{i}-th simulation is 1 if the estimated interval of the \emph{j}-th group on \emph{i}-th simulated dataset contains a true parameter
-%  \eqn{\theta_{(i)j}}{\theta_(i)j} that generated the observed value of the \emph{j}-th group in the 
-%  \emph{i}-th dataset.
-
-%  Rao-Blackwellized unbiased estimator for group \emph{j} is a conditional expectation of the simple unbiased estimator given a sufficient statistic, \eqn{y_{j}}{y_j} for Gaussian or \eqn{z_{j}}{z_j} for Binomial and Poisson data.
-
 \section[Examples]{Examples}\label{sec6}
-\subsection[Known Second-level Mean]{Data of 31 hospitals with a known expected random effect}
+Applications to three data sets: Medical profiling of 31 hospitals with Poisson distributed fatality counts; Educational assessment of 8 schools with Normally distributed data; and evaluation of 18 baseball hitters with Binomial success rates and one covariate.
+For each example, we use 95\% confidence level as a default.
+
+\subsection[Known Second-level Mean]{Poisson data with 31 hospitals: Known expected random effect}
 \label{sec:ex:hosp}
@@
 Health care providers may use these data to improve their care qualities, and patients may refer to the data to select a better hospital.
-Our goal is to obtain the point and interval estimates for the unknown true mortality rates (random effects) of 31 hospitals to evaluate  each hospital's reliability on the CABG surgery (\cite{morris1995} use a similar Poisson model to handle these hospital profile data).
-We interpret the caseloads, $\boldsymbol{n}$,  as exposures and assume that the state-level death rate per exposure of this surgery ($\lambda^E$) is known as 0.03 to fit the Poisson model for an illustrative purpose.
-If covariate information is available or the information about the expected random effect is unknown, we recommend using the Binomial model.
+A goal would be to obtain the point and interval estimates for the unknown true mortality rates (random effects) of 31 hospitals to evaluate  each hospital's reliability on the CABG surgery (\cite{morris1995} use a similar Poisson model to handle these hospital profile data).
+We interpret the caseloads, $\boldsymbol{n}$,  as exposures and assume that the state-level fatality rate per exposure of this surgery  is known, $\lambda^E_j= 0.03$ ($m=0$).
+
 %\footnote{Visit \emph{http://www.health.ny.gov/statistics/diseases/cardiovascular/} for more profile data of the CABG surgery in New York state.}
@@
 
-The function \code{gbp} can then be used to fit a Poisson-Gamma to the death
-rates in New York states with prior mean, ($\lambda^E$), equal to 0.030 and the
-number of regression coefficients ($m$) set to 0.
+The function \code{gbp} can then be used to fit a Poisson-Gamma to the fatality
+rates in New York states with prior mean, $\lambda^E_j$, equal to 0.03.
 
@@
 
-The output contains information about the observed death rates $\bar{y}_{j}$, caseloads $n_{j}$, known prior mean $\lambda^E$, shrinkage estimates $\hat{B}_{j}$, lower bounds of interval estimates $\hat{\lambda}_{j, \textrm{low}}$, posterior means $\hat{\lambda}_j$, upper bounds  of interval estimates $\hat{\lambda}_{j, \textrm{upp}}$, and posterior standard deviations  for each random effect based on the assumed unconditional Gamma posterior distributions.
+The output contains information about the observed death rates $\bar{y}_{j}$, caseloads $n_{j}$, known prior mean $\lambda^E_j$, shrinkage estimates $\hat{B}_{j}$, lower bounds (2.5\%) of interval estimates $\hat{\lambda}_{j, \textrm{low}}$, posterior means $\hat{\lambda}_j$, upper bounds  (97.5\%) of interval estimates $\hat{\lambda}_{j, \textrm{upp}}$, and posterior standard deviations  for each random effect based on the assumed unconditional Gamma posterior distributions.
 %The lower and upper bounds of an interval estimate for a random effect are 2.5\% and 97.5\% percentiles of the assumed unconditional Gamma posterior distributions if 95\% confidence level is used.
 
-%Note that the conditional posterior mean of random effect $j$ in Equation \ref{gammapost_mean_var} is $(1-B_{j})\bar{y}_{j} + B_{j}\lambda^E$,  a convex combination of the observed death rate and expected random effect with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight.
+%Note that the conditional posterior mean of random effect $j$ in Equation \ref{gammapost_mean_var} is $(1-B_{j})\bar{y}_{j} + B_{j}\lambda^E_j$,  a convex combination of the observed death rate and expected random effect with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight.
 This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree (sample sizes) of prior and observed information respectively.
@@
 The output of \code{summary} shows that $\hat{r}=\textrm{exp}(6.53)=684$, which is an indicator of how valuable and informative the second-level hierarchy is.
-It means that observed sample means of hospitals whose caseloads are less than 684 shrink toward the prior mean (0.030) more than 50\%.
+It means that the 25 hospitals with caseload less than 684 patients shrink their sample means towards the prior mean (0.03) more than 50\%.
 For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.911$) was calculated by 684 / (684 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.911)*0.0448 + 0.911 * 0.030=0.0313$.
@@
 \includegraphics[width = 2.8in]{hospital1.png}
-\caption{Shrinkage plot and 95\% interval plot for 31 hospitals.}
+\caption{Shrinkage plot and 95\% interval plot for fatality rates at 31 hospitals sorted by their caseloads.}
 \label{fig:hospshr}
@@
 Considering solely the observed death rates may lead to an unfair comparison because the latter hospital handled twice the caseload.
-\pkg{Rgbp} accounts for this caseload difference, making the posterior mean for the random effect of the former hospital shrink toward the state-level mean ($\lambda^E$=0.03) much harder than that for the latter hospital.
+\pkg{Rgbp} accounts for this caseload difference, making the posterior mean for the random effect of the former hospital shrink toward the state-level mean ($\lambda^E_j$=0.03) much harder than that for the latter hospital.
 
@@
 The second plot of Figure \ref{fig:hospshr} displays the 95\% interval estimates.
-Note that each posterior mean (red dot) is between the sample mean (empty dot) and the known expected random effect (a blue horizontal line).
+Each posterior mean (red dot) is between the sample mean (empty dot) and the known expected random effect (a blue horizontal line).
 %For reference, we could plot this 95\% interval plot by the order of data input via \code{plot(p, sort = FALSE)}.
@@
 
-We conduct the frequency method checking to question how reliable the estimation procedure is.
-The function \code{coverage}  generates pseudo-datasets given the estimated value of $r$, 683.53, as a generative value.
-For reference, we can designate any generative values of $r$ and $\lambda^E$ by adding two arguments, \code{A.or.r} and \code{mean.PriorDist}, into the code below.
+Next, we do frequency method checking to question how reliable the estimation procedure is, assuming $r$ equals its estimated value $\hat{r}=683.53$.
+The function \code{coverage}  generates pseudo-datasets starting with the estimated value of $r$  as a generative value.
+For reference, we could designate other generative values of $r$ and $\lambda^E_j$ by adding two arguments, \code{A.or.r} and \code{mean.PriorDist}, into the code below.
 %; \code{R> pcv <- coverage(p, A.or.r = 600, nsim = 1000)}.
@@
 In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level  and the red circles indicate RB unbiased coverage estimates, $\bar{I}^{RB}_{r, \lambda^\E}(\lambda_j)$ for $j=1, 2, \ldots, 31$.
-The overall RB unbiased coverage estimate across all the hospitals ($\bar{\bar{I}}^{RB}_{r, \lambda^E}$) is 0.955.
-None of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads.
-This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence level.
+The overall RB unbiased coverage estimate across all the hospitals ($\bar{\bar{I}}^{RB}_{r, \lambda^E_j}$) is 0.955.
+None of RB unbiased coverage estimates for the 31 hospitals are less than 0.95 regardless of their caseloads, which range from 67 for hospital 1 to 1,340 for hospital 31.
+This result shows that the interval estimates for this particular dataset adequately achieves a 95\% confidence level if $r=\hat{r}$.
 
@@
 
-The following code provides specific values of the 31 RB unbiased coverage estimates and their standard errors for each hospital (the output is omitted for a space concern).
+The following code provides specific values of the 31 RB unbiased coverage estimates and their standard errors for each hospital (the output is omitted for space reasons).
 \begin{CodeChunk}
@@
 
-And the code below shows 31 simple unbiased coverage estimates and their standard errors for each hospital.
+The code below produces 31 simple unbiased coverage estimates and their standard errors for each hospital.
 \begin{CodeChunk}
@@
 
-\subsection[Unknown Second-level Mean and No Covariate]{Data of 8 schools with unknown expected random effect and no covariates} \label{sec:ex:8schools}
+\subsection[Unknown Second-level Mean and No Covariate]{Gaussian data with 8 schools: Unknown expected random effect and no covariates} \label{sec:ex:8schools}
 
@@
 
-Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, i.e., standard error of each school is completely known.
-At the second hierarchy, the mean for each school is assumed to be drawn from a common Normal distribution and hence, we can use the Gaussian component of \code{gbp} to fit this Gaussian hierarchical model.
+Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with approximately known sampling variances, based on large sample consideration.
+At the second hierarchy, the mean for each school is assumed to be drawn from a common Normal distribution.
 
@@
 
-\subsection[Unknown Second-level Mean and One Covariate]{Data of 18 baseball players with unknown expected random effect and one covariate}
+\subsection[Unknown Second-level Mean and One Covariate]{Binomial data with 18 baseball players:  unknown expected random effect and one covariate}
 
@@
 \begin{align}
-f(r\vert\boldsymbol{y})&\propto \frac{1}{r^2}L(r)\propto\frac{1}{r^2}\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E+y_j)}{\Gamma(r\lambda^E)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E}\\
-&=\frac{1}{r^2}\left[r^{\sum_{j=1}^ky_j}+\cdots+a_k r^{k}\right]\exp\left(-r\lambda^E\sum_{j=1}^k\log(1+n_j/r)\right)\prod_{j=1}^k\left(\frac{n_j}{n_j+r}\right)^{y_j} \label{final_post_proper},
+f(r\vert\boldsymbol{y})&\propto \frac{1}{r^2}L(r)\propto\frac{1}{r^2}\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E_j+y_j)}{\Gamma(r\lambda^E_j)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E_j}\\
+&=\frac{1}{r^2}\left[r^{\sum_{j=1}^ky_j}+\cdots+a_k r^{k}\right]\exp\left(-r\sum_{j=1}^k\lambda^E_j\log(1+n_j/r)\right)\prod_{j=1}^k\left(\frac{n_j}{n_j+r}\right)^{y_j} \label{final_post_proper},
 \end{align}

### 2015-08-02 Rgbp/R/br.R

@@ -707,7 +707,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
   given <- list(z = z, n = n, sample.mean = z / n, x.ini = X,
                 prior.mean = prior.mean, intercept = intercept, Alpha = Alpha)
 
-  if (is.na(prior.mean)) {
+  if (missing(prior.mean)) {
     ini <- BRInitialValue2ndLevelMeanUnknown(given)
   } else {
     ini <- BRInitialValue2ndLevelMeanKnown(given)
@@ -715,7 +715,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
 
   if (n.AR == 0) {
 
-    a.res <- if (is.na(prior.mean)) {
+    a.res <- if (missing(prior.mean)) {
                BRAlphaBetaEst2ndLevelMeanUnknown(given, ini)
              } else {
                BRAlphaEst2ndLevelMeanKnown(given, ini)
@@ -723,7 +723,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
 
     B.res <- BRShrinkageEst(a.res, given)
 
-    if (is.na(prior.mean)) {
+    if (missing(prior.mean)) {
       post.res <- BRPosteriorEst2ndLevelMeanUnknown(B.res, a.res, ini, given)
     } else {
       post.res <- BRPosteriorEst2ndLevelMeanKnown(B.res,given)
@@ -741,7 +741,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
 
   } else {
 
-    if (is.na(prior.mean)) {
+    if (missing(prior.mean)) {
       res <- BRAR(given, ini, n.AR = n.AR, trial.scale = trial.scale, 
                   n.AR.factor = n.AR.factor, t = t, u = u)
     } else {
@@ -749,13 +749,13 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
                                    n.AR.factor = n.AR.factor, t = t, u = u)
     }
 
-    if (is.na(prior.mean)) {
+    if (missing(prior.mean)) {
       p0.mean <- res$prior.mean.hat
     } else {
       p0.mean <- given$prior.mean
     }
 
[…]

### 2015-08-02 Rgbp/R/br.R
code error poisson

@@ -2,7 +2,7 @@ BRInitialValue2ndLevelMeanKnown <- function(given) {
   # This function makes the initial values needed to run BRIMM.
   # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
 
-  if (given$prior.mean == 0) {
+  if (any(given$prior.mean == 0)) {
     if(all(given$sample.mean == mean(given$sample.mean))) {
       r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / (var(given$sample.mean) + 0.1)
     } else {

### 2015-08-02 Rgbp/R/pr.R

@@ -265,13 +265,13 @@ pr <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95) {
   given <- list(z = z, n = n, sample.mean = z/n, x.ini = X, 
                 prior.mean = prior.mean, intercept = intercept, Alpha = Alpha)
 
-  if (is.na(prior.mean)) {
+  if (missing(prior.mean)) {
     ini <- PRInitialValue2ndLevelMeanUnknown(given)
   }else{
     ini <- PRInitialValue2ndLevelMeanKnown(given)
   }
 
-  a.res <- if (is.na(prior.mean)) {
+  a.res <- if (missing(prior.mean)) {
              PRAlphaBetaEst2ndLevelMeanUnknown(given, ini)
            } else {
              PRAlphaEst2ndLevelMeanKnown(given, ini)
@@ -279,7 +279,7 @@ pr <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95) {
 
   B.res <- PRShrinkageEst(a.res, given)
 
-  if (is.na(prior.mean)) {
+  if (missing(prior.mean)) {
     post.res <- PRPosteriorEst2ndLevelMeanUnknown(B.res, a.res, ini, given)
   }else{
     post.res <- PRPosteriorEst2ndLevelMeanKnown(B.res, given)

### 2015-08-02 Rgbp/R/br.R
code error binomial2

@@ -2,7 +2,7 @@ BRInitialValue2ndLevelMeanKnown <- function(given) {
   # This function makes the initial values needed to run BRIMM.
   # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
 
-  if (any(given$prior.mean == 0)) {
+  if (all(given$prior.mean == 0)) {
     if(all(given$sample.mean == mean(given$sample.mean))) {
       r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / (var(given$sample.mean) + 0.1)
     } else {

### 2015-08-02 Rgbp/R/br.R
code error binomial3

@@ -2,7 +2,7 @@ BRInitialValue2ndLevelMeanKnown <- function(given) {
   # This function makes the initial values needed to run BRIMM.
   # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
 
-  if (all(given$prior.mean == 0)) {
+  if (any(given$prior.mean == 0)) {
     if(all(given$sample.mean == mean(given$sample.mean))) {
       r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / (var(given$sample.mean) + 0.1)
     } else {

### 2015-08-02 Rgbp/R/br.R
code error binomial4

@@ -2,7 +2,7 @@ BRInitialValue2ndLevelMeanKnown <- function(given) {
   # This function makes the initial values needed to run BRIMM.
   # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
 
-  if (any(given$prior.mean == 0)) {
+  if (all(given$prior.mean == 0)) {
     if(all(given$sample.mean == mean(given$sample.mean))) {
       r.ini <- mean(given$sample.mean) * (1 - mean(given$sample.mean)) / (var(given$sample.mean) + 0.1)
     } else {
@@ -707,7 +707,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
   given <- list(z = z, n = n, sample.mean = z / n, x.ini = X,
                 prior.mean = prior.mean, intercept = intercept, Alpha = Alpha)
 
-  if (missing(prior.mean)) {
+  if (is.na(prior.mean)) {
     ini <- BRInitialValue2ndLevelMeanUnknown(given)
   } else {
     ini <- BRInitialValue2ndLevelMeanKnown(given)
@@ -715,7 +715,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
 
   if (n.AR == 0) {
 
-    a.res <- if (missing(prior.mean)) {
+    a.res <- if (is.na(prior.mean)) {
                BRAlphaBetaEst2ndLevelMeanUnknown(given, ini)
              } else {
                BRAlphaEst2ndLevelMeanKnown(given, ini)
@@ -723,7 +723,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
 
     B.res <- BRShrinkageEst(a.res, given)
 
-    if (missing(prior.mean)) {
+    if (is.na(prior.mean)) {
       post.res <- BRPosteriorEst2ndLevelMeanUnknown(B.res, a.res, ini, given)
     } else {
       post.res <- BRPosteriorEst2ndLevelMeanKnown(B.res,given)
@@ -741,7 +741,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
 
   } else {
 
-    if (missing(prior.mean)) {
+    if (is.na(prior.mean)) {
       res <- BRAR(given, ini, n.AR = n.AR, trial.scale = trial.scale, 
[…]

### 2015-08-02 Rgbp/R/br.R
code error binomial5

@@ -707,7 +707,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
   given <- list(z = z, n = n, sample.mean = z / n, x.ini = X,
                 prior.mean = prior.mean, intercept = intercept, Alpha = Alpha)
 
-  if (is.na(prior.mean)) {
+  if (any(is.na(prior.mean))) {
     ini <- BRInitialValue2ndLevelMeanUnknown(given)
   } else {
     ini <- BRInitialValue2ndLevelMeanKnown(given)
@@ -723,7 +723,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
 
     B.res <- BRShrinkageEst(a.res, given)
 
-    if (is.na(prior.mean)) {
+    if (any(is.na(prior.mean))) {
       post.res <- BRPosteriorEst2ndLevelMeanUnknown(B.res, a.res, ini, given)
     } else {
       post.res <- BRPosteriorEst2ndLevelMeanKnown(B.res,given)
@@ -741,7 +741,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
 
   } else {
 
-    if (is.na(prior.mean)) {
+    if (any(is.na(prior.mean))) {
       res <- BRAR(given, ini, n.AR = n.AR, trial.scale = trial.scale, 
                   n.AR.factor = n.AR.factor, t = t, u = u)
     } else {
@@ -749,13 +749,13 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
                                    n.AR.factor = n.AR.factor, t = t, u = u)
     }
 
-    if (is.na(prior.mean)) {
+    if (any(is.na(prior.mean))) {
       p0.mean <- res$prior.mean.hat
     } else {
       p0.mean <- given$prior.mean
     }
 
-    if (is.na(prior.mean)) {
+    if (any(is.na(prior.mean))) {
       b.mean <- res$beta.new
       b.var <- res$beta.var
       beta <- res$beta.sample

### 2015-08-02 Rgbp/R/pr.R
code error poisson2

@@ -265,7 +265,7 @@ pr <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95) {
   given <- list(z = z, n = n, sample.mean = z/n, x.ini = X, 
                 prior.mean = prior.mean, intercept = intercept, Alpha = Alpha)
 
-  if (missing(prior.mean)) {
+  if (any(is.na(prior.mean))) {
     ini <- PRInitialValue2ndLevelMeanUnknown(given)
   }else{
     ini <- PRInitialValue2ndLevelMeanKnown(given)
@@ -279,7 +279,7 @@ pr <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95) {
 
   B.res <- PRShrinkageEst(a.res, given)
 
-  if (missing(prior.mean)) {
+  if (any(is.na(prior.mean))) {
     post.res <- PRPosteriorEst2ndLevelMeanUnknown(B.res, a.res, ini, given)
   }else{
     post.res <- PRPosteriorEst2ndLevelMeanKnown(B.res, given)

### 2015-08-02 Rgbp/R/br.R
code error poisson binomial

@@ -10,9 +10,9 @@ BRInitialValue2ndLevelMeanKnown <- function(given) {
     }
   } else {
     if(all(given$sample.mean == mean(given$sample.mean))) {
-      r.ini <- given$prior.mean * (1 - given$prior.mean) / (var(given$sample.mean) + 0.1)
+      r.ini <- mean(given$prior.mean) * (1 - mean(given$prior.mean)) / (var(given$sample.mean) + 0.1)
     } else {
-      r.ini <- given$prior.mean * (1 - given$prior.mean) / var(given$sample.mean)
+      r.ini <- mean(given$prior.mean) * (1 - mean(given$prior.mean)) / var(given$sample.mean)
     }
   }
   list(r.ini = r.ini, a.ini = -log(r.ini))

### 2015-08-02 Rgbp/R/pr.R

@@ -3,9 +3,9 @@ PRInitialValue2ndLevelMeanKnown <- function(given) {
   # "Kn" means the descriptive second level mean (mean of Beta distribution) is known.
  
   if (all(given$sample.mean == mean(given$sample.mean))) {
-    r.ini <- given$prior.mean / (var(given$sample.mean) + 1)
+    r.ini <- mean(given$prior.mean) / (var(given$sample.mean) + 1)
   } else {
-    r.ini <- given$prior.mean / var(given$sample.mean)
+    r.ini <- mean(given$prior.mean) / var(given$sample.mean)
   }
 
   list(a.ini = -log(r.ini))

### 2015-08-02 Rgbp/R/br.R
code error binomial6

@@ -715,7 +715,7 @@ br <- function(z, n, X, prior.mean, intercept = TRUE, Alpha = 0.95, t = 0, u = 1
 
   if (n.AR == 0) {
 
-    a.res <- if (is.na(prior.mean)) {
+    a.res <- if (any(is.na(prior.mean))) {
                BRAlphaBetaEst2ndLevelMeanUnknown(given, ini)
              } else {
                BRAlphaEst2ndLevelMeanKnown(given, ini)

### 2015-08-02 jss/article_v6.tex
coverage

@@
 The default of \code{gbp}  is to fit an intercept term.
-The value(s) of the known expected random effect(s) can be assigned through an optional argument \code{mean.PriorDist}, either a constant when all expected random effects are the same or a $k\times1$ vector.
+The value(s) of the known expected random effect(s) can be assigned through an optional argument \code{mean.PriorDist}.
 Note that \code{gbp} can fit the Poisson model only when the values of expected random effects, $\lambda^E_j$, are known.
@@
 
-The argument \code{y} is a vector of $k$ observed sample means  for the Gaussian model, $k$ observed numbers of successful outcomes for the Binomial model, and $k$ observed numbers of events happening for the Poisson model.
+The argument \code{y} is a vector of $k$ observed sample means  for the Gaussian model, $k$ observed numbers of successful outcomes for the Binomial model, and $k$ observed outcome counts  for the Poisson model.
 The argument  \code{se.or.n} is a vector of $k$ standard errors of each sample mean for the Gaussian model, $k$ numbers of trials for the Binomial model, and $k$ exposures for the Poisson model.
-If we want to designate a known value of the expected random effect $\mu^E=\beta_1$ for the Gaussian model or $p^E=\exp(\beta_1)/(1+\exp(\beta_1))$ for the Binomial model, then we put that value into \code{gbp} using an argument \code{mean.PriorDist}.
+The argument \code{mean.PriorDist} is either a constant (if all the known expected random effects are the same) or a $k\times1$ vector of known expected random effects.
+
+%If we want to designate known values of the expected random effects, then we put that value into \code{gbp} using an argument \code{mean.PriorDist}.
 For example, if  $\mu^E$ is known as 10, then we use the following code.
 %The usage of the Binomial model is the same.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> g.output <- gbp(y, se.or.n, mean.PriorDist = 10, model = "gaussian")
-\end{CodeInput}
-\end{CodeChunk}
-
-If covariate information for each group is available, we can fit the Gaussian and Binomial models, using the following codes.
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%R> g.output <- gbp(y, se.or.n, mean.PriorDist = 10, model = "gaussian")
+%\end{CodeInput}
+%\end{CodeChunk}
+
+If covariate information for each group is available, users can fit the Gaussian and Binomial models, using the following codes.
 \begin{CodeChunk}
@@
 The argument \code{X} is a matrix of covariate(s) each column of which corresponds to one covariate for $k$ groups.
-For example, if we have two covariates for each group, the argument \code{X} must be $k\times2$ matrix to estimate three regression coefficients $\boldsymbol{\beta}=(\beta_1, \beta_2, \beta_3)$ including an intercept term, $\beta_1$, as a default.
-If we do not want to include an intercept term ($\beta_1=0$), estimating two regression coefficients for the two covariates, we add an optional argument \code{intercept} as follows.
+For example, if users have two covariates for each group, the argument \code{X} must be $k\times2$ matrix to estimate three regression coefficients $\boldsymbol{\beta}=(\beta_1, \beta_2, \beta_3)$ including an intercept term, $\beta_1$, as a default.
+If users do not want to include an intercept term ($\beta_1=0$), estimating two regression coefficients for the two covariates, users can add an optional argument \code{intercept} as follows.
 \begin{CodeChunk}
@@
 
-The function \code{gbp} uses the A-R method to fit the Binomial model if we assign the desired number of posterior samples ($N$ in  \eqref{weight}) through the argument \code{n.AR}; its default value is 0.
+The function \code{gbp} uses the A-R method to fit the Binomial model if users assign the desired number of posterior samples ($N$ in  \eqref{weight}) through the argument \code{n.AR}; its default value is 0.
 There are several arguments related to the A-R method.
-The argument \code{n.AR.factor} determines how many trial samples the method draws; its default value is 4, meaning that the method draws \code{n.AR} $\times4$ trial samples and accepts or rejects them.
-The argument \code{trial.scale} is $\psi$ determining the scale parameter of the skewed-$t$ distribution (the envelope function); its default value is 1.3.
-The argument \code{save.result} indicates whether we save the whole posterior samples of the random effects and hyper-parameters; its default value is \code{TRUE}.
-The two arguments \code{t} and \code{u}, taking on positive values, allow users to choose the joint hyper-prior distribution $f(r, \boldsymbol{\beta})\propto d\boldsymbol{\beta}dr/(t+r)^{u+1}$; the default values for \code{t} and \code{u} are 0 and 1, respectively, for the joint hyper-prior distribution specified in  \eqref{eq:hyper}.
+The argument \code{n.AR.factor} determines how many trial samples the method draws; its default value is 4, meaning that the function \code{gbp} draws \code{n.AR} $\times4$ trial samples and accepts or rejects them.
+The argument \code{trial.scale} is $\psi$ determining the scale parameter of the skewed-$t$ distribution; its default value is 1.3.
+The argument \code{save.result} indicates whether \code{gbp} saves the whole posterior samples of the random effects and hyper-parameters; its default value is \code{TRUE}.
+The two arguments \code{t} and \code{u}, taking on positive values, allow users to choose the joint hyper-prior density function, $f(r, \boldsymbol{\beta})\propto d\boldsymbol{\beta}dr/(t+r)^{u+1}$; the default values for \code{t} and \code{u} are 0 and 1, respectively, for the joint hyper-prior density function specified in  \eqref{eq:hyper}.
 
@@
 \code{summary}, and \code{plot}. The estimation result for all the random
-effects appears if we type the ``gbp'' object at the \proglang{R} console, which
+effects appears if users type the ``gbp'' object in the \proglang{R} console, which
 plays the same role of the function \code{print} with its default argument
@@
 
-The function \code{plot} draws a shrinkage plot and $100\times$\code{Alpha}\% interval plot for random effects with its default argument ``\code{sort = TRUE}'' that draws the $100\times$\code{Alpha}\% interval plot in the ascending order of $n$ for the Binomial and Poisson model and the descending order of standard errors for the Gaussian model.
+The function \code{plot} draws a shrinkage plot and $100\times$\code{Alpha}\% interval plot for random effects.
+Its default argument ``\code{sort = TRUE}'' displays the $100\times$\code{Alpha}\% interval plot in the ascending order of $n$ for the Binomial and Poisson model and the descending order of standard errors for the Gaussian model.
 When the argument \code{sort} is set to \code{FALSE}  the $100\times$\code{Alpha}\% interval plot is displayed in the order of data input.
@@
 The argument \code{nsim} sets the number of simulations, $N_{\textrm{sim}}$, defined in Section \ref{data_generation}.
-If we do not assign values of the hyper-parameters through the arguments \code{A.or.r} and \code{reg.coef}, then the function \code{coverage} automatically sets the estimated posterior modes of hyper-parameters saved in the ``gbp'' object (or their posterior medians if the acceptance-rejection method for the Binomial model is used) as the generative values of hyper-parameters.
-If we want to conduct the frequency method checking with different generated values of hyper-parameters, for example, $r=100$ and $\boldsymbol{\beta}=(2, 5)^\top$ when one covariate was used with an intercept term, then we specify them via the arguments \code{A.or.r} and \code{reg.coef};
+If users do not assign values of the hyper-parameters through the arguments \code{A.or.r} and \code{reg.coef}, then the function \code{coverage} automatically sets the estimated posterior modes of hyper-parameters saved in the ``gbp'' object (or their posterior medians if the acceptance-rejection method for the Binomial model is used) as the generative values of hyper-parameters.
+If users want to conduct the frequency method checking with different generated values of hyper-parameters, for example, $r=100$ and $\boldsymbol{\beta}=(2, 5)^\top$ when one covariate was used with an intercept term, then users can specify them via the arguments \code{A.or.r} and \code{reg.coef};
 \begin{CodeChunk}
@@
 
-When we fit a model with a known value of the expected random effect, \code{coverage} conducts the frequency method checking based on the known value.
-However, we may sometimes want to conduct the frequency method checking with a different value for the expected random effect.
-For example, if we want to try a different value of the expected random effect, e.g., 30, we add the argument \code{mean.PriorDist} as follows.
+When users fit a model with a known value of the expected random effect, \code{coverage} conducts the frequency method checking based on the known value.
+However, users might want to conduct the frequency method checking with different values of the expected random effects.
+For example, if users want to try  a different value of the expected random effect, e.g., 30 (or can be a vector of different values), we add the argument \code{mean.PriorDist} as follows.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
-The resulting frequency method checking is based on the estimated posterior mode of $r$ and the newly specified value of the expected random effect, 30.
+The resulting frequency method checking is based on the estimated posterior mode of $r$ (because it is not specified through \code{A.or.r}) and the newly specified value of the expected random effect, 30.
 
 Although the function \code{coverage} does not produce an S3 object, a detailed summary appears in a plot that automatically pops up.
-In addition, the variable \code{cov}  where we save  the result of \code{coverage} as above contains numerical details; $k$ RB coverage estimates (\code{cov$coverageRB}) and their standard errors (\code{cov$se.coverageRB}), $k$ simple coverage estimates (\code{cov$coverageS}) and their standard errors (\code{cov$se.coverageS}), etc.
+In addition, the variable \code{cov}  where we save  the result of \code{coverage} as above contains numerical details; $k$ RB coverage estimates (\code{cov$coverageRB}) and their standard errors (\code{cov$se.coverageRB}), $k$ simple coverage estimates (\code{cov$coverageS}) and their standard errors (\code{cov$se.coverageS}), overall RB coverage estimate (\code{cov$average.coverageRB}) and its standard error (\code{cov$average.coverageRB}), etc.
 

### 2015-08-02 Rgbp/R/coverage.R

@@ -698,6 +698,7 @@ coverage <- function(gbp.object, A.or.r, reg.coef, mean.PriorDist, nsim = 100) {
   # print output
   output <- list(coverageRB = result, coverageS = result2, 
                  average.coverageRB = avr.cov, average.coverageS = avr.cov2, 
+                 overall.coverageRB = avr.cov, se.overal.coverageRB = avr.se.cov,
                  se.coverageRB = se.cov, se.coverageS = se.cov2, 
                  raw.resultRB = coverageRB, raw.resultS = coverageS,
                  Alpha = gbp.object$Alpha, effective.n = effective.n, 

### 2015-08-02 jss/article_v6.tex
final revision

@@
 \end{equation}
-that for the Binomial model is
+that for the Poisson model is
+\begin{equation}\label{trueapprox_poisson}
+\lambda_j\vert \boldsymbol{y} \sim \textrm{Gamma}(\hat{s}_{1j}, \hat{s}_{0j}).
+\end{equation}
+and that for the Binomial model is
 \begin{equation}\label{trueapprox_binomial}
 p_j\vert \boldsymbol{y} \sim \textrm{Beta}(\hat{t}_{1j}, \hat{t}_{0j}),
-\end{equation}
-and that for the Poisson model is
-\begin{equation}\label{trueapprox_poisson}
-\lambda_j\vert \boldsymbol{y} \sim \textrm{Gamma}(\hat{s}_{1j}, \hat{s}_{0j}).
 \end{equation}
@@
 
-Although the function \code{coverage} does not produce an S3 object, a detailed summary appears in a plot that automatically pops up.
-In addition, the variable \code{cov}  where we save  the result of \code{coverage} as above contains numerical details; $k$ RB coverage estimates (\code{cov$coverageRB}) and their standard errors (\code{cov$se.coverageRB}), $k$ simple coverage estimates (\code{cov$coverageS}) and their standard errors (\code{cov$se.coverageS}), overall RB coverage estimate (\code{cov$average.coverageRB}) and its standard error (\code{cov$average.coverageRB}), etc.
-
-If we save the result into an object such as \code{cov} above, then we can always recall the coverage plot, using the function \code{coverage.plot}.
+Though the function \code{coverage} does not produce an S3 object,  the result of \code{coverage} contains various numerical details; $k$ RB coverage estimates (\code{cov$coverageRB}) and their standard errors (\code{cov$se.coverageRB}),   RB overall coverage estimate (\code{cov$overall.coverageRB}) and its standard error (\code{cov$se.overall.coverageRB}), etc.
+
+A coverage plot summarizing the result of \code{coverage} automatically appears.
+If the result is saved in a variable such as \code{cov} above, then users can  recall the coverage plot, using the function \code{coverage.plot}.
 \begin{CodeChunk}
@@
 Applications to three data sets: Medical profiling of 31 hospitals with Poisson distributed fatality counts; Educational assessment of 8 schools with Normally distributed data; and evaluation of 18 baseball hitters with Binomial success rates and one covariate.
-For each example, we use 95\% confidence level as a default.
+For each example, we use 95\% confidence level.
 
@@
 
+%Health care providers may use these data to improve their care qualities, and patients may refer to the data to select a better hospital.
+
 We analyze a data set of 31 hospitals in New York state comprising of the outcomes of the coronary artery bypass graft (CABG) surgery \citep{morris2012}.
 The data set contains the number of deaths, $\boldsymbol{y}$, for a specified period after CABG surgeries out of the total number of patients, $\boldsymbol{n}$, receiving CABG surgeries in each hospital.
-Health care providers may use these data to improve their care qualities, and patients may refer to the data to select a better hospital.
-A goal would be to obtain the point and interval estimates for the unknown true mortality rates (random effects) of 31 hospitals to evaluate  each hospital's reliability on the CABG surgery (\cite{morris1995} use a similar Poisson model to handle these hospital profile data).
+A goal would be to obtain the point and interval estimates for the unknown true fatality rates (random effects) of 31 hospitals to evaluate  each hospital's reliability on the CABG surgery (\cite{morris1995} use a similar Poisson model to handle these hospital profile data).
 We interpret the caseloads, $\boldsymbol{n}$,  as exposures and assume that the state-level fatality rate per exposure of this surgery  is known, $\lambda^E_j= 0.03$ ($m=0$).
@@
 
-The following code
+The following code can be used to load these data into \proglang{R}.
 \begin{CodeChunk}
@@
 \end{CodeChunk}
-can be used to load these data into \proglang{R}.
 
@@
 The function \code{gbp} can then be used to fit a Poisson-Gamma to the fatality
-rates in New York states with prior mean, $\lambda^E_j$, equal to 0.03.
+rates in New York states with the expected random effect, $\lambda^E_j$, equal to 0.03.
 
@@
 
-The output contains information about the observed death rates $\bar{y}_{j}$, caseloads $n_{j}$, known prior mean $\lambda^E_j$, shrinkage estimates $\hat{B}_{j}$, lower bounds (2.5\%) of interval estimates $\hat{\lambda}_{j, \textrm{low}}$, posterior means $\hat{\lambda}_j$, upper bounds  (97.5\%) of interval estimates $\hat{\lambda}_{j, \textrm{upp}}$, and posterior standard deviations  for each random effect based on the assumed unconditional Gamma posterior distributions.
+The output contains information about  (from the left) the observed fatality rates $\bar{y}_{j}$, caseloads $n_{j}$, known expected random effect $\lambda^E_j$, shrinkage estimates $\hat{B}'_{j}$, lower bounds (2.5\%) of posterior interval estimates $\hat{\lambda}_{j, \textrm{low}}$, posterior means $\hat{\E}(\lambda_j\vert\boldsymbol{y})$, upper bounds  (97.5\%) of posterior interval estimates $\hat{\lambda}_{j, \textrm{upp}}$, and posterior standard deviations $\widehat{\textrm{SD}}(\lambda_j\vert\boldsymbol{y})$ for  random effects based on the assumed unconditional Gamma posterior distributions in \eqref{trueapprox_poisson}.
 %The lower and upper bounds of an interval estimate for a random effect are 2.5\% and 97.5\% percentiles of the assumed unconditional Gamma posterior distributions if 95\% confidence level is used.
@@
 It means that the 25 hospitals with caseload less than 684 patients shrink their sample means towards the prior mean (0.03) more than 50\%.
-For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.911$) was calculated by 684 / (684 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.911)*0.0448 + 0.911 * 0.030=0.0313$.
+For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.911$) was calculated by 684 / (684 + 67), where 67 is its caseload ($n_{1}$).
 As for this hospital, using more information from the conjugate prior distribution is an appropriate choice because the amount  of observed information (67) is much less than the amount of state-level information (684).
+
+%, and its posterior mean is $(1-0.911)*0.0448 + 0.911 * 0.030=0.0313$
 
@@
 
-In Figure \ref{fig:hospshr} the regression towards the mean (RTTM) is obvious in the first plot; the observed death rates, denoted by empty dots on the upper horizontal line, are shrinking towards the known expected random effect, denoted by a blue vertical line at 0.03, to the different extents.
+In Figure \ref{fig:hospshr} the regression towards the mean (RTTM) is obvious in the first plot; the observed fatality rates, denoted by empty dots on the upper horizontal line, are shrinking towards the known expected random effect, denoted by a blue vertical line at 0.03, to the different extents.
 Note that some hospitals' ranks have changed by shrinking much harder towards 0.03 than the others.
-For example, an empty square at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that  the seemingly safest hospital in terms of the observed death rate is probably not the safest in terms of the estimated posterior mean accounting for the different caseloads of these two hospitals.
+For example, an empty square at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that  the seemingly safest hospital in terms of the observed mortality rate is probably not the safest in terms of the estimated posterior mean accounting for the different caseloads of these two hospitals.
 
 %Intuitively, switching ranks for these two hospitals is reasonable. 
-To be specific, their observed death rates ($y_{j}$, $j=8, 23$) are 0.0136 and 0.0150 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602, respectively.
-Considering solely the observed death rates may lead to an unfair comparison because the latter hospital handled twice the caseload.
+To be specific, their observed fatality rates ($y_{j}$, $j=8, 23$) are 0.0136 and 0.0150 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602, respectively.
+Considering solely the observed fatality rates may lead to an unfair comparison because the latter hospital handled twice the caseload.
 \pkg{Rgbp} accounts for this caseload difference, making the posterior mean for the random effect of the former hospital shrink toward the state-level mean ($\lambda^E_j$=0.03) much harder than that for the latter hospital.
@@
 This 95\% interval plot reveals that the 31st hospital has the lowest upper bound even though its point estimate ($\hat{\lambda}_{31}=0.0235$) is slightly larger than that of the 23rd hospital ($\hat{\lambda}_{23}=0.0230$).
-The observed death rates for these two hospitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
+The observed  mortality rates for these two hospitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
 The 31st hospital has twice the caseload, which leads to borrowing less information from the New York state-level hierarchy (or shrinking less toward the state-level mean, 0.03) with smaller variance.
@@
 
-Next, we do frequency method checking to question how reliable the estimation procedure is, assuming $r$ equals its estimated value $\hat{r}=683.53$.
+Next, we do frequency method checking to question how reliable the estimation procedure is, assuming $r$ equals its estimated value, $\hat{r}=683.53$.
 The function \code{coverage}  generates pseudo-datasets starting with the estimated value of $r$  as a generative value.
@@
 In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level  and the red circles indicate RB unbiased coverage estimates, $\bar{I}^{RB}_{r, \lambda^\E}(\lambda_j)$ for $j=1, 2, \ldots, 31$.
-The overall RB unbiased coverage estimate across all the hospitals ($\bar{\bar{I}}^{RB}_{r, \lambda^E_j}$) is 0.955.
+The  RB overall unbiased coverage estimate across all the hospitals ($\bar{\bar{I}}^{RB}_{r, \lambda^E}$) is 0.955.
 None of RB unbiased coverage estimates for the 31 hospitals are less than 0.95 regardless of their caseloads, which range from 67 for hospital 1 to 1,340 for hospital 31.
@@
 
-The following code provides specific values of the 31 RB unbiased coverage estimates and their standard errors for each hospital (the output is omitted for space reasons).
+The following code provides 31 RB unbiased coverage estimates and their standard errors  (the output is omitted for space reasons).
 \begin{CodeChunk}
@@
 
-The code below produces 31 simple unbiased coverage estimates and their standard errors for each hospital.
+The code below produces 31 simple unbiased coverage estimates and their standard errors.
 \begin{CodeChunk}
@@
 Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with approximately known sampling variances, based on large sample consideration.
-At the second hierarchy, the mean for each school is assumed to be drawn from a common Normal distribution.
+At the second hierarchy, the mean for each school is assumed to be drawn from a common Normal distribution ($m=1$).
 
@@
 This output from \code{gbp} summarizes the results.
-In this Gaussian hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_j = V_j/(V_j + A)$.
+In this Gaussian  model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_j = V_j/(V_j + A)$.
 As such, schools whose variation within the school ($V_{j}$) is less than the between school variation ($A$) will shrink greater than $50\%$.
@@
 
-In addition, Rao-Blackwellized (RB) unbiased coverage estimate and its standard error for each school can be gotten with the command below.
+In addition, RB unbiased coverage estimate and its standard error for each school can be gotten with the command below.
 \begin{CodeChunk}
@@
 
-All the individual RB coverage estimates are saved in the $8\times1,000$ matrix, each row of which is about each school. We can load this matrix by the following code.
-\begin{CodeChunk}
-\begin{CodeInput}
-R> g.coverage$raw.resultRB 
-\end{CodeInput}
-\end{CodeChunk}
+%All the individual RB coverage estimates are saved in the $8\times1,000$ matrix, each row of which is about each school. We can load this matrix by the following code.
+%\begin{CodeChunk}
+%\begin{CodeInput}
+%R> g.coverage$raw.resultRB 
+%\end{CodeInput}
+%\end{CodeChunk}
 
@@
 
-\subsection[Unknown Second-level Mean and One Covariate]{Binomial data with 18 baseball players:  unknown expected random effect and one covariate}
+\subsection[Unknown Second-level Mean and One Covariate]{Binomial data with 18 baseball players:  Unknown expected random effect and one covariate}
 
@@
 It means that the  two estimates for the expected random effects for the outfielders and infielders are significantly different.
-Also, the positive sign of $\hat{\beta}_{2}$ indicates that the population batting average for all outfielders tends to be higher than that for infielders.
+Also, the positive sign of $\hat{\beta}_{2}$ indicates that the population batting average for  outfielders tends to be higher than that for infielders.
 The  estimated odds ratio is $\exp(0.389)=1.48$.
@@
 
-In Figure \ref{fig:baseball2},  the estimated coverage probabilities for random effects are beyond 0.95, conservatively satisfying the 95\% confidence level.
+In Figure \ref{fig:baseball2},  the estimated coverage probabilities for random effects are beyond 0.95, conservatively satisfying the 95\% confidence level if $r=\hat{r}$ and $\boldsymbol{\beta}=\hat{\boldsymbol{\beta}}$.
 The RB overall unbiased coverage estimate across all the players is 0.972.
-Note that each coverage estimate depends on given true values of $r$ and $\boldsymbol{\beta}_{(2\times1)}$, and the assumption that the model is valid (overdispersion exists).
+%Note that each coverage estimate depends on given true values of $r$ and $\boldsymbol{\beta}_{(2\times1)}$, and the assumption that the model is valid (overdispersion exists).
 

### 2015-08-03 jss/article_v6.tex
final2
revision_Steve

@@
 \Plainauthor{Hyungsuk Tak, Joseph Kelly, Carl Morris} %% comma-separated
-\Plaintitle{Rgbp: An R Package for Conjugate Gaussian, Poisson, and Binomial Hierarchical Modeling and Frequency Method Checking on Overdispersed Data} %% without formatting
+\Plaintitle{\pkg{Rgbp}: An R Package for Conjugate Gaussian, Poisson, and Binomial Hierarchical Modeling and Frequency Method Checking on Overdispersed Data} %% without formatting
 \Shorttitle{\pkg{Rgbp}: Hierarchical Modeling and Frequency Method Checking on Overdispersed Data} %% a short title (if necessary)
@@
 \pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data.
-The data that \pkg{Rgbp} assumes comprise of observed sufficient statistics for each random effect, such as sample means, possibly together with covariates of each group.
+The data that \pkg{Rgbp} assumes consist of observed sufficient statistics for each random effect, such as sample means, possibly together with covariates of each group.
 The approximate Bayesian tool equipped with the adjustment for density maximization estimates random effects and hyper-parameters in the conjugate prior distributions.
@@
   1 Oxford Street, Cambridge, MA\\
-  E-mail: \email{morris@fas.harvard.edu}\\
+  E-mail: \email{morris@stat.harvard.edu}\\
 }
@@
 
-\section[Introduction]{Introduction (v4; 28 July 2015)}
+\section[Introduction]{Introduction}
 %% Note: If there is markup in \(sub)section, then it has to be escape as above.
 Gaussian, Poisson, or Binomial data from several independent groups sometimes have more variation than the assumed Gaussian, Poisson, or Binomial distributions of the first-level observed data.
-To account for this extra-variability, called overdispersion, a  two-level conjugate hierarchical model regards first-level mean parameters as random effects that come from a population-level conjugate prior distribution.
+To account for this extra variability, called overdispersion, a  two-level conjugate hierarchical model regards first-level mean parameters as random effects that come from a population-level conjugate prior distribution.
 The main  goal of our two-level conjugate modeling is to estimate these random effects for a comparison between groups.
@@
 With an assumption of homogeneity within each group, the observed data are group-level aggregate data from $k$ independent  groups, composed of sufficient statistics for their $k$ random effects (without the population-level data).
-Specifically, the data for the Gaussian model comprise of each group's sample mean and its standard error, those for the Poisson model use each group's outcome count and an exposure measure, and those for the Binomial model use the number of each group's  successful outcomes together with the total number of trials.
+Specifically, the data for the Gaussian model consist of each group's sample mean and its standard error, those for the Poisson model use each group's outcome count and an exposure measure, and those for the Binomial model use the number of each group's  successful outcomes together with the total number of trials.
 The data analyzed by \pkg{Rgbp} may incorporate each group's covariate information.
-These types of  data are common, e.g., as for a biological analysis on litter data \citep{tamura1987stabilized}, a meta analysis on independent studies (Chapter 5 in \cite{gelman2014bayesian}), or small area estimation problems \citep{ghosh1994small, rao2003small}.
-
-For such data, assuming homogeneity within each group, \pkg{Rgbp}'s two-level model may be viewed as a conjugate hierarchical generalized linear model (HGLM) \citep{lee1996hierarchical, hglm2006} where each random effect has a conjugate prior distribution.
+These types of  data are common, \emph{e.g.}, as for a biological analysis on litter data \citep{tamura1987stabilized}, a meta analysis on independent studies (Chapter 5 in \cite{gelman2014bayesian}), or small area estimation problems \citep{ghosh1994small, rao2003small}.
+
+For such data, assuming homogeneity within each group, \pkg{Rgbp}'s two-level model may be viewed as a conjugate hierarchical generalized linear model (HGLM) \citep{lee1996hierarchical} where each random effect has a conjugate prior distribution.
 However, the HGLM focuses on estimating regression coefficients to explore associations between covariates and observed data.
@@
 
-For fitting the hierarchical model, \pkg{Rgbp} uses ADM, i.e.
-``adjustment for density maximization'' \citep{carl1988, morris1997, tang2011}.
+For fitting the hierarchical model, \pkg{Rgbp} uses ADM, \emph{i.e.}, ``adjustment for density maximization'' \citep{carl1988, morris1997, tang2011}.
 ADM approximates a posterior density or a likelihood function by fitting a selected (one dimensional) Pearson family, based on the first two derivatives of the given density function.
@@
 In addition to fitting the hierarchical models, \pkg{Rgbp} evaluates the repeated sampling coverage rates of the resulting Bayesian interval estimates for random effects \citep{morris1997, daniels1999prior, tang2002fitting, tang2011, morris2012}.
-This procedure distinguishes \pkg{Rgbp}  from  other \proglang{R} packages for similar hierarchical models such as \pkg{hglm} \citep{hglm2010, ronnegaard2011hglm} for conjugate hierarchical generalized models.
+This procedure distinguishes \pkg{Rgbp}  from  other \proglang{R} packages for similar hierarchical models such as \pkg{hglm} \citep{ronnegaard2011hglm} for conjugate hierarchical generalized models.
 The evaluation procedure which we use for this process of ``frequency method checking'' uses a parametric bootstrapping  method that many times generates mock data sets given the fitted values of the estimated hyper-parameters and uses the mock data to estimate the coverage rates.
@@
 
-where $y_j$ is an observed unbiased estimate, e.g., sample mean, for random effect $\mu_j$, $V_{j}$ is a completely known standard error of $y_j$, $\mu^E_{j}$ is an expected random effect defined as $\E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$, and $m$ is the number of unknown regression coefficients.
+where $y_j$ is an observed unbiased estimate, \emph{e.g.}, sample mean, for random effect $\mu_j$, $V_{j}$ is a completely known standard error of $y_j$, $\mu^E_{j}$ is an expected random effect defined as $\E(\mu_j\vert \boldsymbol{\beta}, A) = \boldsymbol{x}_j^\top \boldsymbol{\beta}=\beta_{1}x_{j, 1}+\beta_{2}x_{j, 2} + \cdots + \beta_{m}x_{j, m}$, and $m$ is the number of unknown regression coefficients.
 \pkg{Rgbp} sets $x_{j, 1}$ to 1 for an intercept term as a default.
@@
 \subsection[Poisson-Gamma]{Poisson-Gamma model for Poisson data}\label{poissonsubsec}
-\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (hereafter the Poisson model) when the group-level aggregate data from $k$ independent  groups are comprised of non-negative count data without upper limit.
+\pkg{Rgbp} can estimate a conjugate Poisson-Gamma hierarchical model (hereafter the Poisson model) when the group-level aggregate data from $k$ independent  groups consist of non-negative count data without upper limit.
 However, its usage is limited to the case where the expected random effect, $\lambda^E_j=\exp(\boldsymbol{x}_j^\top \boldsymbol{\beta})$,  is known  (or equivalently all the regression coefficients are known ($m=0$)); we may be able to obtain this information from the past studies or from experts.
@@
 In the other two cases, Poisson and Binomial, the flat prior distribution on $1/r$ induces the same improper prior distribution on shrinkages ($f(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with the Uniform($0, \infty$) for the Gaussian case.
-The Poisson model with this hyper-prior distribution on $r$, i.e., $dr/r^2$,  provides posterior propriety if there are at least two groups whose observed values $y_j$ are non-zero  and the expected random effects, $\lambda^E_j$, are known ($m=0$); see Appendix \ref{propriety_poisson} for its proof.
+The Poisson model with this hyper-prior distribution on $r$, \emph{i.e.}, $dr/r^2$,  provides posterior propriety if there are at least two groups whose observed values $y_j$ are non-zero  and the expected random effects, $\lambda^E_j$, are known ($m=0$); see Appendix \ref{propriety_poisson} for its proof.
 If $\lambda^E_j$ is unknown, \pkg{Rgbp} cannot yet give reliable results because we have not verified posterior propriety.
@@
 
-As for posterior propriety of the Binomial model, let's define an ``interior group'' as the group whose number of successes $y_j$ are neither 0 nor $n_j$, and $k_y$ as the number of interior groups among $k$ groups.
+As for posterior propriety of the Binomial model, let us define an ``interior group'' as the group whose number of successes $y_j$ are neither 0 nor $n_j$, and $k_y$ as the number of interior groups among $k$ groups.
 The full posterior distribution of random effects and hyper-parameters is proper if and only if there are at least two interior groups in the data and the $k_y\times m$ covariate matrix of the interior groups is of full rank $m$ ($k_y\ge m$) \citep{tak2016propriety}.
@@
 
-The likelihood function of hyper-parameters, $A$ and $\boldsymbol{\beta}$, for the Gaussian  model is derived from the independent Normal distributions of the observed data with random effects integrated out; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
+The likelihood function of hyper-parameters, $A$ and $\boldsymbol{\beta}$, for the Gaussian  model is derived from the independent Normal distributions of the observed data with random effects integrated out: %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
 \begin{equation}\label{marginal_normal}
@@
 \end{equation}
-The joint posterior density  function of hyper-parameters for the Gaussian  model is proportional to their likelihood function in  \eqref{marginal_normal} because we use flat improper hyper-prior density functions for $A$ and $\boldsymbol{\beta}$;
+The joint posterior density  function of hyper-parameters for the Gaussian  model is proportional to their likelihood function in  \eqref{marginal_normal} because we use flat improper hyper-prior density functions for $A$ and $\boldsymbol{\beta}$:
 \begin{equation}\label{marginal_post_normal}
@@
 
-The likelihood function of $r$ for the Poisson  model  comes from the independent Negative-Binomial  distributions of the observed data with the random effects integrated out;
+The likelihood function of $r$ for the Poisson  model  comes from the independent Negative-Binomial  distributions of the observed data with the random effects integrated out:
 \begin{equation}\label{marginal_poisson}
@@
 where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}\exp(x)dx$ for a positive constant $a$.
-The posterior density function of $r$  for the Poisson  model is  the likelihood function in  \eqref{marginal_poisson} times the hyper-prior density function of $r$, i.e., $dr/r^2$;
+The posterior density function of $r$  for the Poisson  model is  the likelihood function in  \eqref{marginal_poisson} times the hyper-prior density function of $r$, \emph{i.e.}, $dr/r^2$:
 \begin{equation}\label{marginal_post_poisson}
@@
 
-The likelihood function of hyper-parameters $r$ and $\boldsymbol{\beta}$ for the Binomial  model is derived from the independent Beta-Binomial  distributions of the observed data with random effects integrated out \citep{skellam1948}; %For reference, the marginal distribution of the observed datum for the Normal model  still follows a Normal distribution and that for the Poisson model follows a Negative-Binomial distribution.
+The likelihood function of hyper-parameters $r$ and $\boldsymbol{\beta}$ for the Binomial  model is derived from the independent Beta-Binomial  distributions of the observed data with random effects integrated out \citep{skellam1948}:
 \begin{equation}\label{marginal_binomial}
@@
 where the notation $B(a, b)~(\equiv\int_0^1 v^{a-1}(1-v)^{b-1}dv)$ indicates a beta function for positive constants $a$ and $b$.
-The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial  model is proportional to their likelihood function in \eqref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in  \eqref{eq:hyper};
+The joint posterior density  function of hyper-parameters $f(r, \boldsymbol{\boldsymbol{\beta}}\vert \boldsymbol{y})$ for the Binomial  model is proportional to their likelihood function in \eqref{marginal_binomial} multiplied by the hyper-prior density functions of $r$ and $\boldsymbol{\beta}$ in  \eqref{eq:hyper}:
 \begin{equation}\label{marginal_post_binomial}
@@
 
-%If all the observed data are extreme, i.e., $y_j$ is either 0 or $n_j$ for all $j$, the likelihood becomes a decreasing function with respect to $r$ for finite values of $\boldsymbol{\beta}$.
+%If all the observed data are extreme, \emph{i.e.}, $y_j$ is either 0 or $n_j$ for all $j$, the likelihood becomes a decreasing function with respect to $r$ for finite values of $\boldsymbol{\beta}$.
 In this case, the MLE of $r$ is 0.
 
-Our goal is to obtain the point and interval estimates of the random effects from their joint unconditional posterior density which can be expressed as for the Gaussian  model
+Our goal is to obtain the point and interval estimates of the random effects from their joint unconditional posterior density which, for the Gaussian  model, can be expressed as 
 \begin{equation}\label{mcintegration_normal}
@@
 
-\subsubsection{Unconditional posterior moments of shrinkage factors}  It is noted that  the shrinkage factors  are a function of $r$, i.e., $B_{j}= B_{j}(r)=r/(r+n_{j})$ (or a function of $A$ for the Gaussian model).
+\subsubsection{Unconditional posterior moments of shrinkage factors}  It is noted that  the shrinkage factors  are a function of $r$, \emph{i.e.}, $B_{j}= B_{j}(r)=r/(r+n_{j})$ (or a function of $A$ for the Gaussian model).
 A common method of estimation of $B_{j}$ is to approximate the likelihood of $r$ with two derivatives and use  a Delta method for an asymptotic Normal distribution of $\hat{B}_{j}(\hat{r}_{MLE})$.
@@
 
-%The ADM assumes that the unconditional posterior distribution of a shrinkage factor follows a Beta distribution, which allows us to obtain estimates of the unconditional posterior moments, i.e.,  of $E(B_{j}^c\vert\boldsymbol{y})$ for $c\ge0$.
+%The ADM assumes that the unconditional posterior distribution of a shrinkage factor follows a Beta distribution, which allows us to obtain estimates of the unconditional posterior moments, \emph{i.e.},  of $E(B_{j}^c\vert\boldsymbol{y})$ for $c\ge0$.
 \citet{morris1997} using a Poisson hierarchical model showed that the Beta approximation to the shrinkage factors worked better than Normal approximation, and \citet{tang2011} showed it  using a Gaussian  hierarchical model.
@@
 \end{equation}
-%and the ADM estimates the two parameters of this Beta distribution, i.e., $a_{1j}$ and $a_{0j}$.
+%and the ADM estimates the two parameters of this Beta distribution, \emph{i.e.}, $a_{1j}$ and $a_{0j}$.
 %The estimated Beta distribution with the estimates $\hat{a}_{1j}$ and $\hat{a}_{0j}$ will be used to approximate the posterior moments of the shrinkage factors. 
@@
 
-Considering that  \eqref{admmean} and  \eqref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-\log(r)$ (or $\alpha=\log(A)$ for the Gaussian model), because the distribution of $\alpha$ is more symmetric than that of $r$, and $\alpha$ is defined on a real line without any boundary issues.
+Considering that  \eqref{admmean} and  \eqref{admvar} involve  maximization and Hessian calculation, we work on a logarithmic scale of $r$, \emph{i.e.}, $\alpha=-\log(r)$ (or $\alpha=\log(A)$ for the Gaussian model), because the distribution of $\alpha$ is more symmetric than that of $r$, and $\alpha$ is defined on a real line without any boundary issues.
 Because $f^A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto \exp(\alpha) L(\alpha)d\alpha$ \citep{tang2011}, the  posterior mean in  \eqref{admmean} is estimated by
@@
 I_\textrm{inv} &\equiv& -\frac{d^2 \log(f^A(B_j\vert \boldsymbol{y}))}{d[\textrm{logit}(B_j)]^2}\bigg\vert_{B_j=\hat{B}'_j}=-\frac{d^2 \log(f^A(B_j(r)\vert \boldsymbol{y}))}{d[\log(r)]^2}\bigg\vert_{r=\hat{r}}\label{invariance}\\
-&=& -\frac{d^2 \log(f^A(B_j(r(\alpha))\vert \boldsymbol{y}))}{d\alpha^2}\bigg\vert_{\alpha=\hat{\alpha}}\nonumber
+&=& -\frac{d^2 \log(f^A(B_j(r(\alpha))\vert \boldsymbol{y}))}{d\alpha^2}\bigg\vert_{\alpha=\hat{\alpha}}.\nonumber
 \end{eqnarray}
@@
 
-We obtain the estimates of $a_{1j}$ and $a_{0j}$, the two parameters of the Beta distribution in  \eqref{admshrinkage}, by matching them to the estimated unconditional posterior mean and variance of $B_j$ specified in  \eqref{meaninvariance} and \eqref{varianceinvariance};
-%After matching to the two parameters of the Beta distribution in Equation \ref{admshrinkage}, i.e., $a_{1j}$ and $a_{0j}$, we obtain the estimates of $a_{1j}$ and $a_{0j}$ as
+We obtain the estimates of $a_{1j}$ and $a_{0j}$, the two parameters of the Beta distribution in  \eqref{admshrinkage}, by matching them to the estimated unconditional posterior mean and variance of $B_j$ specified in  \eqref{meaninvariance} and \eqref{varianceinvariance}:
+%After matching to the two parameters of the Beta distribution in Equation \ref{admshrinkage}, \emph{i.e.}, $a_{1j}$ and $a_{0j}$, we obtain the estimates of $a_{1j}$ and $a_{0j}$ as
 \begin{equation}\label{admpara}
@@
 
-The moments of the Beta distribution are well defined as a function of $a_{1j}$ and $a_{0j}$, i.e.,  $\E(B^c_j\vert\boldsymbol{y})=B(a_{1j} + c, a_{0j})/B(a_{1j}, a_{0j})$ for $c\ge0$.
+The moments of the Beta distribution are well defined as a function of $a_{1j}$ and $a_{0j}$, \emph{i.e.},  $\E(B^c_j\vert\boldsymbol{y})=B(a_{1j} + c, a_{0j})/B(a_{1j}, a_{0j})$ for $c\ge0$.
 Their estimates are
@@
 \end{equation}
-We approximate the unconditional posterior moments on the left hand side by the conditional posterior moments with $\hat{\alpha}$ plugged-in \citep{kass1989approximate}, i.e., by $\E((p^E_j)^c\vert \hat{\alpha}, \boldsymbol{y})$.
+We approximate the unconditional posterior moments on the left hand side by the conditional posterior moments with $\hat{\alpha}$ inserted \citep{kass1989approximate}, \emph{i.e.}, by $\E((p^E_j)^c\vert \hat{\alpha}, \boldsymbol{y})$.
 %We estimate the unconditional posterior moments by the estimated conditional posterior moments that we obtain from the conditional posterior distribution of $\mu^E_j\vert A, \boldsymbol{y}$ or that of $p^E_j\vert r, \boldsymbol{y}$ with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.
@@
 \end{equation}
-Thus, we use another ADM, assuming the conditional posterior distribution of each expected random effect is a Beta distribution as follows;
+Thus, we use another ADM, assuming the conditional posterior distribution of each expected random effect is a Beta distribution as follows:
 \begin{equation}\label{admpriormean}
@@
 
-We estimate the values of $b_{1j}$ and $b_{0j}$  by matching them to the estimated unconditional posterior mean and variance of $\exp(x_j^\top\boldsymbol{\beta})$ in  \eqref{priormean2} and \eqref{priorvariance2};
+We estimate the values of $b_{1j}$ and $b_{0j}$  by matching them to the estimated unconditional posterior mean and variance of $\exp(x_j^\top\boldsymbol{\beta})$ in  \eqref{priormean2} and \eqref{priorvariance2}:
 \begin{equation}\label{priormeanpara}
@@
 \end{align}
-To estimate these, we plug  the estimated unconditional posterior moments of shrinkage factors in \eqref{shrinkagemoments} into both \eqref{postmean_poisson} and \eqref{approximate_var_poisson}.
+To estimate these, we insert  the estimated unconditional posterior moments of shrinkage factors in \eqref{shrinkagemoments} into both \eqref{postmean_poisson} and \eqref{approximate_var_poisson}.
 Let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimated unconditional posterior mean and variance, respectively.
@@
 where the approximation in \eqref{taylor} is a first-order Taylor approximation.
-By plugging the estimated unconditional posterior moments of shrinkage factors in \eqref{shrinkagemoments} and those of expected random effect in \eqref{est_exp_randomeffect} into  both \eqref{postmean_binom} and \eqref{approximate_var}, we obtain the estimates of the unconditional posterior mean and variance of each random effect, denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
-Finally, we obtain the estimates of two parameters $t_{1j}$ and $t_{0j}$ in  \eqref{betapost} as follows;
+By inserting the estimated unconditional posterior moments of shrinkage factors in \eqref{shrinkagemoments} and those of expected random effect in \eqref{est_exp_randomeffect} into  both \eqref{postmean_binom} and \eqref{approximate_var}, we obtain the estimates of the unconditional posterior mean and variance of each random effect, denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively.
+We thus obtain the estimates of two parameters $t_{1j}$ and $t_{0j}$ in  \eqref{betapost} as follows:
 \begin{equation}\label{posttrueprob}
@@
 We factor the envelope function into two parts, $g(\alpha, \boldsymbol{\beta})=g_1(\alpha)g_2(\boldsymbol{\beta})$ to model the tails of each function separately.
-We consider the tail behavior of the conditional posterior density function $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ to come up with $g_1(\alpha)$; $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ behaves as $\exp(-\alpha(k-1))$ when $\alpha$ goes to $\infty$ and as $\exp(\alpha)$ when $\alpha$ goes to $-\infty$.
+We consider the tail behavior of the conditional posterior density function $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ to establish $g_1(\alpha)$; $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ behaves as $\exp(-\alpha(k-1))$ when $\alpha$ goes to $\infty$ and as $\exp(\alpha)$ when $\alpha$ goes to $-\infty$.
 It indicates that $f(\alpha \vert \boldsymbol{\beta},  \boldsymbol{y})$ is skewed to the left because the right tail touches the $x$-axis faster than the left tail does as long as $k>1$.
@@
 
-\pkg{Rgbp} determines the parameters of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$, i.e., $\mu$, $\sigma$, $a$, $b$, $\boldsymbol{\xi}$, and $S$, to make the product of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$ similar to the target joint posterior density $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$.
+\pkg{Rgbp} determines the parameters of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$, \emph{i.e.}, $\mu$, $\sigma$, $a$, $b$, $\boldsymbol{\xi}$, and $S$, to make the product of $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$ similar to the target joint posterior density $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$.
 First, \pkg{Rgbp} obtains the  mode of $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$ and the inverse of the  negative Hessian matrix at the modes, $-H^{-1}$.
-Let $(\hat{\alpha}, \hat{\boldsymbol{\beta}})$ denote the modes of $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$, $-H^{-1}_{\hat{\alpha}}$ indicate (1, 1) element of $-H^{-1}$, and $-H^{-1}_{\hat{\boldsymbol{\beta}}}$ represent  $-H^{-1}$ without the first row and  column.
+Let $(\hat{\alpha}, \hat{\boldsymbol{\beta}})$ denote the modes of $f(\alpha, \boldsymbol{\beta} \vert  \boldsymbol{y})$, $-H^{-1}_{\hat{\alpha}}$ indicate (1, 1)$^{\textrm{th}}$ element of $-H^{-1}$, and $-H^{-1}_{\hat{\boldsymbol{\beta}}}$ represent  $-H^{-1}$ without the first row and  column.
 
@@
 
-For the  implementation of the acceptance-rejection method, \pkg{Rgbp} draws four times more trial samples than the desired number of samples, denoted by $N$, independently from $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$.
+For  implementation of the acceptance-rejection method, \pkg{Rgbp} draws four times more trial samples than the desired number of samples, denoted by $N$, independently from $g_1(\alpha)$ and $g_2(\boldsymbol{\beta})$.
 \pkg{Rgbp} calculates $4N$ weights, each of which is defined as
@@
 It is noted that  the conjugate prior distribution of each random effect in  \eqref{normalprior} is completely determined by two hyper-parameters, $A$ and $\boldsymbol{\beta}$.
-Fixing these hyper-parameters at specific values, we generate  $N_{\textrm{sim}}$ sets of random effects from the conjugate prior distribution, i.e., \{{\boldmath $\mu$}$^{(i)},~i=1, \ldots, N_{\textrm{sim}}\}$, where the superscript $(i)$ indicates the $i$-th simulation.
+Fixing these hyper-parameters at specific values, we generate  $N_{\textrm{sim}}$ sets of random effects from the conjugate prior distribution, \emph{i.e.}, \{{\boldmath $\mu$}$^{(i)},~i=1, \ldots, N_{\textrm{sim}}\}$, where the superscript $(i)$ indicates the $i$-th simulation.
 Next, using the distribution of observed data in  \eqref{normalobs}, we generate $N_{\textrm{sim}}$ sets of observed data sets $\{\boldsymbol{y}^{(i)},~i=1, \ldots, N_{\textrm{sim}}\}$ given each {\boldmath$\mu$}$^{(i)}$.
@@
 Let $(\hat{\mu}^{(i)}_{j, ~\textrm{low}}, ~\hat{\mu}^{(i)}_{j, ~\textrm{upp}})$ represent the lower and upper bounds of the interval estimate of random effect $j$ based on the $i$-th simulation given a specific confidence level.
-Let's define a coverage indicator of random effect $j$ on the $i$-th mock data set as
+Let us define a coverage indicator of random effect $j$ on the $i$-th mock data set as
 \begin{equation}\label{coverage_indicator}
 I_{A, \boldsymbol{\beta}}(\mu_j^{(i)}) = \left\{ \begin{array}{ll}
-1, & \textrm{if $\mu_j^{(i)}\in(\hat{\mu}^{(i)}_{j, ~\textrm{low}}, ~\hat{\mu}^{(i)}_{j, ~\textrm{upp}})$}\\
-0, & \textrm{otherwise}
+1, & \textrm{if $\mu_j^{(i)}\in(\hat{\mu}^{(i)}_{j, ~\textrm{low}}, ~\hat{\mu}^{(i)}_{j, ~\textrm{upp}})$,}\\
+0, & \textrm{otherwise.}
 \end{array} \right.
@@
 
-%, i.e., $Pr(p_j^{(i)}<\hat{p}^{(i)}_{j, ~upp}\vert r, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})-Pr(p_j^{(i)}<\hat{p}^{(i)}_{j, ~low},\vert r, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})$.
+%, \emph{i.e.}, $Pr(p_j^{(i)}<\hat{p}^{(i)}_{j, ~upp}\vert r, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})-Pr(p_j^{(i)}<\hat{p}^{(i)}_{j, ~low},\vert r, \boldsymbol{\beta}, \boldsymbol{y}^{(i)})$.
 
@@
 
-\subsubsection{Rao-Blackwellized overall unbiased coverage estimator}\label{overallRB} Assuming that the unknown  coverage probabilities are the same for all random effects, we use the Rao-Blackwellized overall unbiased coverage estimator and its variance estimator;
+\subsubsection{Rao-Blackwellized overall unbiased coverage estimator}\label{overallRB} Assuming that the unknown  coverage probabilities are the same for all random effects, we use the Rao-Blackwellized overall unbiased coverage estimator and its variance estimator:
 \begin{equation}\label{RBoverall}
@@
 \section[packageoverview]{Usage of functions in \pkg{Rgbp}}\label{sec5}
-In this section, we describe the usage of the two main functions of \pkg{Rgbp}, i.e., \code{gbp} for model fitting and \code{coverage} for frequency method checking.
+In this section, we describe the usage of the two main functions of \pkg{Rgbp}, \emph{i.e.}, \code{gbp} for model fitting and \code{coverage} for frequency method checking.
 
@@
 There are two cases according to whether covariates are available or not.
-When no covariates are available, the function \code{gbp} requires fitting an intercept term  or designating known values of   the expected random effects, i.e., the intercept term must be either estimated or known.
+When no covariates are available, the function \code{gbp} requires fitting an intercept term  or designating known values of   the expected random effects, \emph{i.e.}, the intercept term must be either estimated or known.
 The default of \code{gbp}  is to fit an intercept term.
@@
 The argument \code{X} is a matrix of covariate(s) each column of which corresponds to one covariate for $k$ groups.
-For example, if users have two covariates for each group, the argument \code{X} must be $k\times2$ matrix to estimate three regression coefficients $\boldsymbol{\beta}=(\beta_1, \beta_2, \beta_3)$ including an intercept term, $\beta_1$, as a default.
+For example, if users have two covariates for each group, the argument \code{X} must be a $k\times2$ matrix to estimate three regression coefficients $\boldsymbol{\beta}=(\beta_1, \beta_2, \beta_3)$ including an intercept term, $\beta_1$, as a default.
 If users do not want to include an intercept term ($\beta_1=0$), estimating two regression coefficients for the two covariates, users can add an optional argument \code{intercept} as follows.
@@
 
-The object \code{b.output} above contains 8,000 weights (\code{b.output$weight}), 2,000 posterior samples of $\alpha$ (\code{b.output$alpha}), a $2,000\times3$ matrix of $\beta$ (\code{b.output$beta})  each column of which corresponds to 2,000 posterior samples of each regression coefficient, and a $k\times2,000$ matrix of random effects (\code{b.output$p}) each row of which has posterior samples of each random effect.
+The object \code{b.output} above contains 8,000 weights (\code{b.output$weight}), 2,000 posterior samples of $\alpha$ (\code{b.output$alpha}), a 2,000$\times3$ matrix of $\beta$ (\code{b.output$beta})  each column of which corresponds to 2,000 posterior samples of each regression coefficient, and a $k\times$2,000 matrix of random effects (\code{b.output$p}) each row of which has posterior samples of each random effect.
 
@@
 ``\code{sort = TRUE}''. When the argument \code{sort} is set to \code{TRUE}, the
-function \code{print} prints out the estimation result for all the groups in the
+function \code{print} displays the estimation result for all the groups in the
 ascending order of $n$ for the Binomial and Poisson model and the descending
@@
 However, users might want to conduct the frequency method checking with different values of the expected random effects.
-For example, if users want to try  a different value of the expected random effect, e.g., 30 (or can be a vector of different values), we add the argument \code{mean.PriorDist} as follows.
+For example, if users want to try  a different value of the expected random effect, \emph{e.g.}, 30 (or can be a vector of different values), we add the argument \code{mean.PriorDist} as follows.
 \begin{CodeChunk}
@@
 
-We analyze a data set of 31 hospitals in New York state comprising of the outcomes of the coronary artery bypass graft (CABG) surgery \citep{morris2012}.
+We analyze a data set of 31 hospitals in New York State consisting of the outcomes of the coronary artery bypass graft (CABG) surgery \citep{morris2012}.
 The data set contains the number of deaths, $\boldsymbol{y}$, for a specified period after CABG surgeries out of the total number of patients, $\boldsymbol{n}$, receiving CABG surgeries in each hospital.
@@
 
-%The independent Poisson distribution, i.e.,  $y_j\vert \lambda_j\stackrel{indep.}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be an ideal choice to describe these data based on the Poisson approximation when $\lambda$ is small and $n$ is relatively large.
+%The independent Poisson distribution, \emph{i.e.},  $y_j\vert \lambda_j\stackrel{indep.}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ would be an ideal choice to describe these data based on the Poisson approximation when $\lambda$ is small and $n$ is relatively large.
 
 The function \code{gbp} can then be used to fit a Poisson-Gamma to the fatality
-rates in New York states with the expected random effect, $\lambda^E_j$, equal to 0.03.
+rates in New York States with the expected random effect, $\lambda^E_j$, equal to 0.03.
 
@@
 This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree (sample sizes) of prior and observed information respectively.
-If the second level has more information than the first level, i.e., ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the estimator will shrink towards the prior mean more than 50\%.
+If the second level has more information than the first level, \emph{i.e.}, ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the estimator will shrink towards the prior mean more than 50\%.
 This is clear because, as caseload increases, shrinkage decreases, depending less on the  state-level (second-level) conjugate Gamma prior distribution.
@@
 In Figure \ref{fig:hospshr} the regression towards the mean (RTTM) is obvious in the first plot; the observed fatality rates, denoted by empty dots on the upper horizontal line, are shrinking towards the known expected random effect, denoted by a blue vertical line at 0.03, to the different extents.
-Note that some hospitals' ranks have changed by shrinking much harder towards 0.03 than the others.
+Note that some hospitals' ranks have changed by shrinking more sharply towards 0.03 than the others.
 For example, an empty square at the crossing point of the two left-most lines (8th and 23rd hospitals on the list above) indicates that  the seemingly safest hospital in terms of the observed mortality rate is probably not the safest in terms of the estimated posterior mean accounting for the different caseloads of these two hospitals.
@@
 Considering solely the observed fatality rates may lead to an unfair comparison because the latter hospital handled twice the caseload.
-\pkg{Rgbp} accounts for this caseload difference, making the posterior mean for the random effect of the former hospital shrink toward the state-level mean ($\lambda^E_j$=0.03) much harder than that for the latter hospital.
+\pkg{Rgbp} accounts for this caseload difference, making the posterior mean for the random effect of the former hospital shrink toward the state-level mean ($\lambda^E_j$=0.03) more rapidly than that for the latter hospital.
 
@@
 The observed  mortality rates for these two hospitals ($y_{j}, j=23, 31$) are 0.0150 and 0.0201 and the caseloads ($n_{j}, j =23, 31$) are 602 and 1340 each.
-The 31st hospital has twice the caseload, which leads to borrowing less information from the New York state-level hierarchy (or shrinking less toward the state-level mean, 0.03) with smaller variance.
+The 31st hospital has twice the caseload, which leads to borrowing less information from the New York State-level hierarchy (or shrinking less toward the state-level mean, 0.03) with smaller variance.
 Based on the point and interval estimates, the 31st hospital seems the most reliable one.
 
-Next, we do frequency method checking to question how reliable the estimation procedure is, assuming $r$ equals its estimated value, $\hat{r}=683.53$.
+Next, we perform frequency method checking to question how reliable the estimation procedure is, assuming $r$ equals its estimated value, $\hat{r}=683.53$.
 The function \code{coverage}  generates pseudo-datasets starting with the estimated value of $r$  as a generative value.
@@
 separate schools (groups) to test whether students (units) SAT scores are
-effected by coaching. The dataset contains the estimated coaching effects on SAT
+affected by coaching. The dataset contains the estimated coaching effects on SAT
 scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$)
-of the eight schools \citep{1981}. These data are contained in the package and can be loaded into \proglang{R}
+of the eight schools \citep{1981}. These data are contained in the package and can be loaded into \proglang{R}:
 \begin{CodeChunk}
@@
 The summary provides results regarding the second level hierarchy parameters.
-It can be seen that the estimate of the expected random effect, $\mu^E=\beta_1$ (\code{beta1}), is not significantly different from 0 suggesting that there was no effect of the coaching program on SAT math scores.
+It can be seen that the estimate of the expected random effect, $\mu^E=\beta_1$ (\code{beta1}), is not significantly different from 0 suggesting that there is no effect of the coaching program on SAT math scores.
 
@@
 
-In addition, RB unbiased coverage estimate and its standard error for each school can be gotten with the command below.
+In addition, RB unbiased coverage estimate and its standard error for each school can be calculated with the command below.
 \begin{CodeChunk}
@@
 through their first 45 official at-bats of the 1970 season \citep{1975}. A
-binary covariate is created that takes on the value one if a player is an
+binary covariate is created that is equal to the value one if a player is an
 outfielder and zero otherwise. The data can be loaded into \proglang{R} with the following code
@@
 \end{CodeChunk}
-% Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233. Also
+% Our model reflects on the additional information, \emph{\emph{i.e.}}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233. Also
 
@@
 \end{CodeChunk}
-The ``gbp'' object \code{b.output} contains 8,000 weights (\code{b.output$weight}), 2,000 posterior samples of $\alpha$ (\code{b.output$alpha}), a $2,000\times2$ matrix of $\beta$ (\code{b.output$beta})  each column of which corresponds to 2,000 posterior samples of each regression coefficient, and a $k\times2,000$ matrix of random effects (\code{b.output$p}) each row of which has posterior samples of each random effect.
+The ``gbp'' object \code{b.output} contains 8,000 weights (\code{b.output$weight}), 2,000 posterior samples of $\alpha$ (\code{b.output$alpha}), a 2,000$\times2$ matrix of $\beta$ (\code{b.output$beta})  each column of which corresponds to 2,000 posterior samples of each regression coefficient, and a $k\times$2,000 matrix of random effects (\code{b.output$p}) each row of which has posterior samples of each random effect.
 
@@
 A benefit of \pkg{Rgbp} is that it produces non-random output (except the A-R method for the Binomial model) and so results are easily reproduced and compared across studies.
-In addition to being a standalone analysis tool the package can be used as an aid in a broader estimation procedure.
-For example, by checking the similarity of output of \pkg{Rgbp} and that of another estimation procedure such as MCMC (Markov Chain Monte Carlor), the package can be used as a confirmatory tool to check whether the alternative procedure has been programmed correctly.
-In addition, the parameter estimates obtained via \pkg{Rgbp} can be used to initialize a MCMC thus decreasing time to convergence.
+In addition to being a stand-alone analysis tool the package can be used as an aid in a broader estimation procedure.
+For example, by checking the similarity of output of \pkg{Rgbp} and that of another estimation procedure such as MCMC (Markov Chain Monte Carlo), the package can be used as a confirmatory tool to check whether the alternative procedure has been programmed correctly.
+In addition, the parameter estimates obtained via \pkg{Rgbp} can be used to initialize an MCMC thus decreasing time to convergence.
 Lastly, due to its speed and ease of use, \pkg{Rgbp} can be used as a method of preliminary data analysis.
@@
 where $f(\boldsymbol{\lambda}\vert \boldsymbol{y})$ is a product of $k$ proper conditional posterior density function in \eqref{gammapost}.
-Thus, our goal is to show that $\int_0^\infty f(r\vert \boldsymbol{y})dr<\infty$;
+Thus, our goal is to show that $\int_0^\infty f(r\vert \boldsymbol{y})dr<\infty$:
 \begin{align}
@@
 \section*{Acknowledgments}
-The authors thank Professor Cindy Christiansen, Professor Phil Everson and the 2012 class of Harvard's Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
+The authors thank Professor Cindy Christiansen, Professor Phil Everson and the 2012 class of Harvard's Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs, and Steve Finch for proofreading.
 

### 2015-11-10 jss/article_v6.tex
test

@@
              Carl Morris\\ Harvard University}
-\title{\pkg{Rgbp}: An \proglang{R} Package for Conjugate Gaussian, Poisson, and Binomial Hierarchical Modeling and Frequency Method Checking on Overdispersed Data}
+\title{\pkg{Rgbp}: An \proglang{R} Package for  Gaussian, Poisson, \\and Binomial  Random Effects Models, \\with Frequency Coverage Evaluations}
 
@@
 \Plainauthor{Hyungsuk Tak, Joseph Kelly, Carl Morris} %% comma-separated
-\Plaintitle{\pkg{Rgbp}: An R Package for Conjugate Gaussian, Poisson, and Binomial Hierarchical Modeling and Frequency Method Checking on Overdispersed Data} %% without formatting
-\Shorttitle{\pkg{Rgbp}: Hierarchical Modeling and Frequency Method Checking on Overdispersed Data} %% a short title (if necessary)
+\Plaintitle{\pkg{Rgbp}: An R Package for  Gaussian, Poisson, and Binomial  Random Effects Modeling and Frequency Method Checking on Overdispersed Data} %% without formatting
+\Shorttitle{\pkg{Rgbp}: Random Effects Models, with Frequency Coverage Evaluations} %% a short title (if necessary)
 %% an abstract and keywords
 \Abstract{
-\pkg{Rgbp} is an \proglang{R} package that utilizes  approximate Bayesian machinery to fit two-level conjugate hierarchical models on overdispersed Gaussian, Poisson, and Binomial data.
-The data that \pkg{Rgbp} assumes consist of observed sufficient statistics for each random effect, such as sample means, possibly together with covariates of each group.
-The approximate Bayesian tool equipped with the adjustment for density maximization estimates random effects and hyper-parameters in the conjugate prior distributions.
-As for the Binomial model, the package has an option to draw their posterior samples via the acceptance-rejection method.
-The main goal of \pkg{Rgb} is to produce  Bayesian interval estimates for the random effects that meet their nominal confidence levels.
-For this purpose, we adopt unique improper hyper-prior distributions.
-\pkg{Rgbp} provides a tool to check quickly whether the resulting Bayesian interval estimates for the random effects achieve the nominal confidence levels via a repeated sampling coverage evaluation, which we call  ``frequency method checking."  }
+\pkg{Rgbp} is an \proglang{R} package whose primary goal is to provide estimates and verifiable confidence intervals for all $k$ second-level independent random effects in two-level conjugate hierarchical models for overdispersed Gaussian, Poisson, and Binomial data.
+It uses approximate Bayesian machinery with special frequency-justified improper priors for the population hyper-parameters.
+A special feature enabled by \pkg{Rgbp}'s speed is an option that draws many repeated samples needed to verify that the nominal confidence levels are met for all the estimated random effects.
+In general, \pkg{Rgbp} models data that are summarized by observed sufficient statistics for each random effect, such as sample means, with covariates also allowed for each group.
+Inference statistics are provided for the random effects and for the hyper-parameters.}
 % and evaluates repeated sampling frequency property of the resulting approximate Bayesian interval estimates for random effects
 %It is found that such Bayesian-frequentist reconciliation allows \pkg{Rgbp} to have attributes desirable from both perspectives, working well in small samples and yielding good coverage probabilities for its interval estimates.
-\Keywords{overdispersion, hierarchical model, adjustment for density maximization, acceptance-rejection method, repeated sampling coverage evaluation, frequency method checking, \proglang{R}}
+\Keywords{overdispersion, hierarchical model, adjustment for density maximization,  frequency method checking, \proglang{R}}
 \Plainkeywords{multilevel model, conjugate hierarchical generalized linear models, frequency method checking, coverage probability, shrinkage, R} 

### 2015-11-10 Rgbp/R/br.R

@@ -387,6 +387,7 @@ BRAR <- function(given, ini, n.AR = n.AR, trial.scale = trial.scale,
     a <- k
   }
 
+
   n.sample <- n.AR.factor * n.AR
   n.accept <- 0
 
